### 2018-02-02 code/calls/calls.Rmd
edits to paper and speed-of-light

---
title: "calls"
author: "John R. Lewis"
date: "2/2/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(brlm)
library(MASS)
library(mvtnorm)
library(coda)
library(MCMCpack)
log_scale  <- 1
```

## Analysis of calls

```{r data transformations}
phones$year<- phones$year - mean(phones$year)
phones <- bind_cols(phones)
if(log_scale) phones$calls <- log(phones$calls)
plot(phones$year, phones$calls)

```

## Prior specification

```{r prior}
n_prior <- 3
(fit <- lm(calls ~ year, data = phones[1:n_prior,]))

(lm_fit <- lm(calls ~ year, data = phones))
# prior parameters -----
g <- nrow(phones) - n_prior
mu0 <- fit$coefficients
X <- model.matrix(fit)
Sigma0 <- g*sigma(fit)^2*solve(t(X)%*%X)
a0 <- 2
b0 <- 1

```

## Restricted Likelihood Fit
```{r rl fit tukey with MAD, cache = TRUE}
y <- phones$calls[-c(1:n_prior)]
X_fit <- cbind(1, phones$year[-c(1:n_prior)])

# Importance Sampling 
# define statistic
rlm_tukey <- function(y, X){
  fit <- rlm(X, y, psi = psi.bisquare,  scale.est = 'MAD', maxit=1e4)
  c(fit$coefficients, fit$s)
}
# importance distribution parameters 
rlm_tukey(y, X_fit)

rlm_fit <- rlm(calls ~ year, data = phones[-c(1:n_prior),], psi = psi.bisquare, scale.est = 'MAD')
c(rlm_fit$coefficients, rlm_fit$s)
plot(phones$year, phones$calls)
lines(phones$year[-c(1:n_prior)], fitted(rlm_fit))

i <- 2
par(mfrow = c(2,1))
smp1 <- rnorm(1000, mu0[i], sqrt(Sigma0[i,i]))
smp2 <- rnorm(1000, rlm_fit$coefficients[i], sqrt(vcov(rlm_fit)[i,i]))
hist(smp1, xlim = range(smp1, smp2))
hist(smp2, xlim = range(smp1, smp2))
par(mfrow = c(1,1))

cov_b <- vcov(rlm_fit)
scale <- .25*rlm_fit$s

N <- 1e5
Nins <- 1e5
set.seed(125)
rl_fit <- rl_importance(y, X_fit, statistic = rlm_tukey, mu0 = mu0, Sigma0 = Sigma0, alpha = a0, beta = b0, cov_b = cov_b, scale = scale, smooth = 1, N = N,Nins = Nins)

# check weights -----
# plot(log(rl_fit$w + 1e-20), cex = .2)
plot(rl_fit$w, cex = .2)

write_rds(rl_fit, path = file.path(here::here(), 'rl_fit.rds'))

```

## T-Distribution Fit
```{r t-distribution fit, cache = TRUE}
#fit t - distribution ----
nkeep <- 1e5
nburn <- 3e4
nu <- 5
set.seed(126)
t_fit <-bayesTdistLm(y=y, X_fit, mu0, Sigma0, a0=a0, b0=((nu-2)/nu)*b0, parInit=c(rlm_fit$coefficients, (nu-2)*sigma(fit)^2/nu), nu=nu, nkeep=nkeep, nburn=nburn, rwTune=sigma(lm_fit)*5)

coda::traceplot(t_fit$mcmc)

write_rds(t_fit, path = file.path(here::here(), 't_fit.rds'))

# fit normal model on subset of the data.
nkeep <- 1e4
nburn <- 2e3
normal_ind <- c(4:13,21:24)
y_normal <- phones$calls[normal_ind]
X_normal <- cbind(1, phones$year[normal_ind])
set.seed(127)
normal_fit <- bayesLm(y_normal, X_normal, mu0, Sigma0, a0, b0, sigma2Int = rlm_fit$s^2, nkeep = nkeep, nburn = nburn)

coda::traceplot(normal_fit$mcmc,smooth = TRUE)
write_rds(normal_fit, path = file.path(here::here(), 'normal_fit.rds'))
```

### 2018-02-02 paper.tex
edits to paper and speed-of-light

\documentclass[11pt]{article}
%\documentclass[ba]{imsart}

\usepackage{fullpage,amsmath}% mathtools}
\usepackage{setspace}
\usepackage{graphicx, psfrag, amsfonts, float}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{hhline}
%\usepackage{color}
\usepackage[position=t,singlelinecheck=off]{subcaption}
\usepackage{caption, setspace}
%\usepackage[position=t,singlelinecheck=off]{subfigure}
 \pdfminorversion=4
\usepackage{rotating}
\def\bgam{\mbox{\boldmath $\gamma$}}
\def\bth{\mbox{\boldmath $\theta$}}
\def\bbeta{\mbox{\boldmath $\beta$}}
\def\blam{\mbox{\boldmath $\lambda$}}
\def\bmu{\mbox{\boldmath $\mu$}}

\newcommand{\bx}{\mbox{\boldmath $x$}}
\newcommand{\bu}{\mbox{\boldmath $u$}}
\newcommand{\bc}{\mbox{\boldmath $c$}}
\newcommand{\bs}{\mbox{\boldmath $s$}}
\newcommand{\by}{\mbox{\boldmath $y$}}
\newcommand{\bz}{\mbox{\boldmath $z$}}
\newcommand{\bv}{\mbox{\boldmath $v$}}
\newcommand{\bb}{\mbox{\boldmath $b$}}
\newcommand{\bzero}{\mbox{\boldmath $0$}}
\newcommand{\thstarj}{\mbox{$\theta^\star_j$}}
\newcommand{\bths}{\mbox{$\btheta^\star$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\uI}{\mathrm{I}}
\newcommand{\uP}{\mathrm{P}}
\newcommand{\up}{\mathrm{p}}
\newcommand{\mb}{\mathbf}
\newcommand{\mc}{\mathcal}

\newcommand{\Bern}{\mbox{Bern}}
\newcommand{\Nor}{\mbox{N}}
\newcommand{\Ga}{\mbox{Gamma}}
\newcommand{\Dir}{\mbox{Dir}}
\newcommand{\Ber}{\mbox{Ber}}
\newcommand{\Be}{\mbox{Be}}
\newcommand{\Unif}{\mbox{Unif}}
\newcommand{\Binom}{\mbox{Bin}}
\newcommand{\IG}{\mbox{IG}}

\newcommand{\Xs}{X^\star}
\newcommand{\Lc}{{\cal L}}

\usepackage[dvipsnames,usenames]{color}
\newcommand{\yy}{\color{magenta}\it}
\newcommand{\jj}{\color{Black}\rm}
\newcommand{\yjnote}[1]{\footnote{\color{Brown}\rm #1 \color{Black}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{\bf Definition}
\newtheorem{lemma}[theorem]{\bf Lemma}
\newtheorem{corollary}[theorem]{\bf Corollary}
\newtheorem{proposition}[theorem]{\bf Proposition}
\newtheorem{assumption}[theorem]{\bf Assumption}
\newtheorem{example}[theorem]{\bf Example}
\newtheorem{remark}[theorem]{\bf Remark}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\stackrel{indep}{\sim}}

\doublespacing
\setlength{\textwidth}{6 in}

% commands for for editing
\usepackage{color}
\usepackage{ulem} % \sout
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\brown}[1]{{\color{brown}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\graphicspath{{figures/}}

\makeatletter
\newcommand{\labitem}[2]{%
\def\@itemlabel{\textbf{#1}{.}}
\item
\def\@currentlabel{#1}\label{#2}}
\makeatother

\title{Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression}
\author{John R. Lewis, Steven N. MacEachern and  Yoonkyung Lee \\
{\small \it Department of Statistics, The Ohio State University, Columbus, Ohio 43210}\\
{\small lewis.865@osu.edu, snm@stat.osu.edu and yklee@stat.osu.edu}
\thanks{This research has been supported by Nationwide Insurance Company and by the NSF under grant numbers DMS-1007682 and DMS-1209194.  The views in this paper are not necessarily those of Nationwide Insurance or the NSF.}} 
\begin{document}
\date{}
\maketitle

\begin{abstract}
The \textit{restricted likelihood} is introduced as a method to address concerns about the miss-specification of the likelihood in Bayesian models. To apply, the data is summarized through a set of insufficient statistics,
targeting inferential quantities of interest, and the prior is updated with only the summary statistics. By a careful choice of the summary, we retain the main benefits of Bayesian methods while reducing the
sensitivity of the analysis to features of the data not captured by
the conditioning statistics. Examples specifically address reducing sensitivity to outliers,
where classical robust estimators (e.g., M-estimators) are natural choices
for conditioning statistics. With these choices, the method can be thought of as a blend of classical robust estimation and Bayesian methods.

A Markov chain Monte Carlo (MCMC) algorithm, applicable for the linear model and a wide range of choices for
summary statistics, is developed to overcome implementation challenges. The method is demonstrated with several examples including simulations and messy insurance agency data with many outliers. Success is manifested in better predictive
performance for data points of interest as compared to competing methods.

\noindent KEYWORDS: Approximate Bayesian computation, Markov chain
Monte Carlo, M-estimation, Robust regression.

\end{abstract}

\section{Introduction}
Bayesian methods are useful to a wide range of scientific problems, with their value
having been demonstrated both empirically and theoretically. However, these methods run into difficulties
for two major and prevalent classes of problems: handling data sets
with outliers and dealing with model misspecification. From Bayesian perspective the model refers to the prior, the likelihood, as well as the loss function when formal inference is required. While optimality of Bayesian methods is unquestioned if one accepts the validity of all three of these elements, healthy skepticism encourages us to question each.  Concern about the prior distribution has
been addressed through objective Bayesian methods \citep{berger2006} prior elicitation methods \citep{garthwaite2005, ohagan2006}. Concern about the loss function is reflected in the extensive literature on Bayesian hypothesis tests \citep{kass1995}.  Despite the common use of flat-tailed distributions \citep{berger1994} or nonparametric techniques \red{References?}, the sampling density has been given less attention from a specifically Bayesian view. The work on predictive diagnostics \citep{box1980} departs from classical
traditions.

The focus of this work is the development of techniques to handle imperfections in the sampling density.  These imperfections often show
themselves through the presence of outliers--cases not reflecting the phenomenon under
study. There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling
density with a mixture model which includes one component for the ``good'' data and a second 
component for the ``bad'' data.  The second approach replaces the
basic sampling density with a thick-tailed density in an attempt to discount outliers.  The third approach fits a flexible (typically nonparametric) model to the data, producing a Bayesian version of a density estimate for both good and bad data.  In recent 
development, inference is made through the use of robust inference functions \citep[][in press]{lee2013}.

The traditional strategies for handling outliers all have their drawbacks.  While we view the sampling 
density for the good data as stable, the outlier-generating processes 
may be transitory in nature, constantly shifting as the source of bad data changes.  This prevents
us from appealing to large-sample arguments to claim that, with enough data, we can nail down a
model for both good and bad data combined.  Instead of attempting to model both good and bad
data, we propose a new strategy. In a nutshell, we begin with a complete model   
as if all of the data are good. But rather than driving the move from prior distribution to posterior
distribution by the entire likelihood, we use only the likelihood driven by a
few summary statistics that target inferential quantities
of interest.  We call this the \textit{restricted likelihood}. The update is a formal update from prior distribution to posterior distribution, based on the sampling density of the summary statistics.

While the focus of this work is handling outliers, model miss-specification is more general. By focusing on robustly estimating quantities of interest and conditioning on these estimates, the restricted likelihood offers promiss in handling more general miss-specification issues in model building. The remainder of the paper.....develops Bayesian restricted likelihood (Section~\ref{restrictedlikelihood}), shows
how it can be applied to a Bayesian linear model (Section~\ref{BayesLinMod}), illustrates its use
on an insurance agencies data set with a novel twist on model evaluation (Section~\ref{Applications}), 
and wraps up with a discussion (Section~\ref{Conclusions}).  
A major contribution of this work is the computational strategy whose legitimacy is established 
in Section~\ref{BayesLinMod}.  The technical proofs are in the appendix.

\section{The Restricted Likelihood}
\label{restrictedlikelihood}

This sections describes the restricted likelihood using a pair of simple examples and the relates the method to the current literature. For the examples assume $\by=(y_1,\ldots,y_n)$ is a random sample
of size $n$ from a continuous distribution indexed by a parameter
vector $\bth$, with pdf $f(y| \bth)$.  The full-data, likelihood is $L(\bth | \by) = \prod_{i=1}^n f(y_i | \bth)$.

For the first example, consider that a known subset of the data is not informative about $\bth$.  This case mimics the setting where outlying observations  are identified and discarded before formal analysis. 
Labeling the good cases $1$ through $n-k$ and the bad cases $n-k+1$ through $n$.  
The relevant likelihood to be used to move from prior distribution to posterior distribution is 
$L(\bth | y_1, \ldots, y_{n-k}) = \prod_{i=1}^{n-k} f(y_i | \bth)$.  
Equivalently,  the full 
likelihood is rewritten as 
\begin{eqnarray}
\label{OutlyingCases}
L(\bth | \by)  
= \left( \prod_{i=1}^{n-k} f(y_i | \bth) \right) \left( \prod_{i=n-k+1}^{n} f(y_i | \bth) \right) .  
\end{eqnarray}
The second piece, which is independent of $\theta$,  is dropped to provide better inference on $\bth$.

A second example involves deliberate censoring of small and large observations.  This is
sometimes done as a precursor to the analysis of reaction time
experiments  \citep[e.g.,][]{ratcliff1993} where very short and long reaction times are usually explained as anticipation and inattention, respectively, and do not reflect the process being studied.
With lower and upper censoring times at $t_1$ and $t_2$, the post-censoring sampling distribution
is of mixed form, with masses $F(t_1|\bth)$ at $t_1$ and $1-F(t_2|\bth)$ at $t_2$,
and density $f(y | \bth)$ for $y \in (t_1, t_2)$.  Adjusting $y_i$,
with $c(y_i)$ where $c(y_i)= t_1$ if $y_i \leq t_1$, $c(y_i)=t_2$ 
if $y_i \geq t_2$, and $c(y_i)=y_i$ otherwise.  
The adjusted update is performed with $L(\bth |c(\by))$.  
With slightly non-standard notation, we let $g(t_1|\bth) = F(t_1|\bth)$,
$g(t_2 | \bth) = 1 - F(t_2|\bth)$, and $g(y|\bth)=f(y|\bth)$ for
$y \in (t_1, t_2)$. The full likelihood as the product of two pieces, 
\begin{eqnarray}
\label{Censoring}
L(\bth | \by) =  \left( \prod_{i=1}^n g(c(y_i)  | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth,c(y_i) ) \right) ,  
\end{eqnarray}
and only the first for the formal update.

Further example abound with more given in \cite{lewis2014}. To generalize, we write the full likelihood in two pieces
\begin{eqnarray}
\label{FullLikelihood}
L(\bth | \by)  & = & f(T(\by) | \bth) \,\, f(\by |\bth, T(\by)) .  
\end{eqnarray}
where $T(\by)$ is any statistic. Here,  $f(T(\by) | \bth)$ is the conditional pdf of $T(\by)$ given $\bth$ and $f(\by |\bth, T(\by))$ is the conditional pdf of $\by$ given $\bth$ and $T(\by)$.  In \eqref{OutlyingCases}, the conditioning statistic is $T(\by) = (y_1, \ldots, y_{n-k})$ and in \eqref{Censoring}, the conditioning statistic is $T(\by) = (c(y_1),\ldots,c(y_n))$.  We refer to 
$f(T(\by) | \bth)$ as the restricted likelihood and $L(\bth | \by)=f(\by|\bth)$ as the full likelihood.

$T(\by)$ is a well-defined random variable with a probability distribution indexed by $\bth$ and the update from prior  to posterior can be made using $f(T(\by)|\bth)$ rather than $f(\by|\bth)$.  This leads to the \textit{restricted likelihood posterior}
\begin{eqnarray}
\label{RestrictedPosterior}
\pi(\bth | T(\by)) & = & \frac{\pi(\bth) f(T(\by) | \bth)}{m(T(\by))} ,
\end{eqnarray}
where $\pi(\bth)$ is the prior distribution and $m(T(\by))$ is the marginal distribution of $T(\by)$ under prior. The associated predictive distribution for a single observation $\tilde y$ is
\begin{eqnarray}
\label{RestrictedpredDist}
f(\tilde y | T(\by)) = \int f(\tilde y | \bth) \pi(\bth | T(\by))\ d\bth .  
\end{eqnarray}

Direct use of restricted likelihood appears in many areas of the literature.  The motivation is often similar to ours:   
concern about outliers or, more generally, model misspecification.  The use of rank likelihoods is discussed by \cite{savage1969}, \cite{pettitt1983, pettitt1982}, and more recently by \cite{hoff2013}.  \cite{lewis2012} make use of robust regression estimators for $T(\by)$.
Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}. These asymptotic results asserts that under certain assumptions, posterior distribution resembles the asymptotic sampling distribution of the conditioning statistic.

Restricted likelihoods have been used as practical approximations to a full likelihood. For example, \cite{pratt1965} appeals to heuristic arguments regarding approximate sufficiency to justify the use of the restricted likelihood of the sample mean and standard deviation. Approximate sufficiency is also used in Approximate Bayesian Computation (ABC), which is related to our method.  
ABC has recently experienced success in applications to epidemiology, genetics, and quality control \citep[see, for example,][]{tavare1997, pritchard1999,  marjoram2003, fearnhead2012}. Interest typically lies in the full data posterior and ABC is used for computational convenience.  Consequently, effort is made to choose an approximately sufficient $T(\by)$ and update to the ABC posterior by using the likelihood $L(\bth| \mathcal{B}(\by))$, where $\mathcal{B}(\by)=\{\by^{*}|\rho(T(\by),T(\by^{*}))<\epsilon\}$, $\rho$ is a metric, and $\epsilon$ is a tolerance level. This is the likelihood conditioned on the collection of data sets close to $\by$ as measured by the summary statistic. By choosing an approximately sufficient $T(\cdot)$ and a small enough $\epsilon$ the claim $L(\bth|\mathcal{B}(\by))\approx L(\bth|T(\by))\approx L(\bth|\by)$. Consequently, the ABC posterior approximates the full data posterior. Efforts have been made to formalize what is meant by  approximate sufficiency \citep[e.g.,][]{joyce2008}.

ABC is related to our method in that conditioning is on something other than the full data. For technical reasons, the calculation proceeding from $\pi(\bth)$ to $\pi(\bth | \mathcal{B}(\by))$ is not a formal conditional update.  Simply put, if an external observer told $\mathcal{B}(\by)$ can supply $T(\by)$ and vice-versa, the information contained in $\mathcal{B}(\by)$ is exactly that contained in $T(\by)$ and proper conditioning will lead to identical posterior distributions.  This is not the case with a typical implementation of ABC.

% In a related, but distinctly different, approach which also takes advantage of summary statistics, the full data log likelihood is replaced by a loss function \citep[e.g.][]{bissiri2013} in an effort to concentrate inference only on parameters of interest. In contrast, the incomplete likelihood is formulated using a full probability model, allowing for a formal Bayesian update, while remaining robust to misspecification.

This work extends the development of Bayesian restricted likelihood by arguing that deliberate choice of $T(\by)$ is sound practice and also by expanding the class of conditioning statistics in which exact conditioning can be achieved. Our methods do not rely on asymptotic properties, approximate conditioning, nor do they need to correspond to artificial censoring to create incomplete or missing data \citep[e.g.,][]{albert1988, hoffwakefield2013}.  \green{Note - fix references here hoffwakefield for asymptotic; albert for ? .}

\red{ MOVE THIS PIECE OR REMOVE ---
The key to productive use of the restricted likelihood is the choice of $T(\by)$ and the development
of computational strategies that allow us to truly condition on the observed $T(\by)$ and 
fit the model in formal Bayesian fashion.  In this work, we focus
on robustness, and natural choices of $T(\by)$ for the one-sample problem include a set of middling order statistics, a trimmed
mean, or a classical robust estimator of location and/or scale.  
We have previously implemented several of these methods and have found them to perform well \citep[][]{lewis2012}. Versions most extensible to the linear model include the M-estimators in the tradition of \cite{huber1964}, least median squares (LMS), and least trimmed squares (LTS). For these choices the restricted likelihood is not available in closed form, making computation of the restricted posterior a challenge. For low-dimensional statistics $T(\by)$ and parameters $\bth$, the direct computational strategies described in \cite{lewis2014} can be used to estimate the incomplete posterior conditioned on essentially any statistic.  These strategies rely on generation of complete data sets from different values of $\bth$.  
Each complete data set leads to a statistic $T(\by)$ under $\bth$, and these generated statistics are used to estimate the density at $T(\by_{obs})$, where $\by_{obs}$ is the observed complete data. This estimate is fed into Bayes' theorem for the update from prior distribution to posterior distribution.  %For the example in the previous section, these strategies work well.
%\textcolor{blue}{Comment out `A variety of  variance reduction techniques which exploit\dots' because it seemed too vague and a bit off topic}
%In low dimensional settings (in $T(\by)$ and $\bth$) the incomplete posterior under each of these versions (and others) can be estimated by approximating the incomplete likelihood using kernel density estimation techniques \citep[for details see][]{lewis2014}.

These direct sampling techniques rely on density estimation and numerical integration. Density estimation becomes difficult for high dimensional $T(\by)$ and numerical integration breaks down for high dimensional $\bth$. For these settings, an MCMC algorithm is developed in Section \ref{highDim}. Software is available from the authors for use with simultaneous M-estimators of location and scale. At the present time, further software development is required to extend beyond simultaneous M-estimators.

%\textcolor{blue}{Added a bit about this to the discussion: Though we concentrate in this paper on applying incomplete likelihood inference for the mean of linear regression models, the computational strategies we devise in subsequent sections also allow us to apply the method to inference beyond the mean.  In particular, quantile regression falls within the framework we develop. }
%The next section develops the necessary computational strategies.  
}

\section{Examples}
\label{examples}
Before discussing computational details, the method is applied in a series of simple examples on well known datasets to demonstrate its effectiveness in situations where outliers are a major concern. The full model in each case fits into the Bayesian linear regression framework discussed in \ref{}. Specific details are left to the Appendix.

The first example is an analysis of Simon Necomb's 66 measurements of the speed of light; two of which are significant outliers in the lower tail. The full model is a standard location-scale Bayesian model assuming normally distributed errors. Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)   Tukey's M-estimator for location with Huber's 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale. Additionally, the common approach of assuming a t-distribution for the errors is also fit. The posteriors of $\beta$ under each model appear in \ref{fig:newcomb_beta}. As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy tailed model provides robustness against them. The restricted likelihood methods using the M-estimators and LTS statistics also achieve robustness against the outliers. Conditioning on LMS however, results in a posterior similar to the one under the normal model. The M-estimators provide the tightest posteriors in this case. They also provide more precise predictions than the heavy-tailed model as illustrated by the predictive distributions displayed in \ref{fig:newcomb_predictive} which are also dependent on the posterior for the scale parameter.
\begin{figure}
\centering
{\includegraphics[width=\textwidth]{figs/speed_of_light_beta.png}}
\label{fig:newcomb_beta}
\caption{Posteriors of the location parameter $\beta$ under each model for Newcomb's speed-of-light measurements.}
\end{figure}

\begin{figure}
\centering
{\includegraphics[width=\textwidth]{figs/speed_of_light_predictive.png}}
\label{fig:newcomb_predictive}
\caption{predit}
\end{figure}

%\begin{sidewaysfigure}
%\begin{subfigure}[b]{.5\linewidth}
%\captionsetup{justification=centering}
%\centering 
%\caption{}\label{fig:newcombBeta}
%\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}
%\end{subfigure}
%\quad
%\begin{subfigure}[b]{.5\linewidth}
%\captionsetup{justification=centering}
%\centering
%\caption{}\label{fig:newcombSig2}
%\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}
%\end{subfigure}
%\quad
%\begin{subfigure}[b]{.5\linewidth}
%\captionsetup{justification=centering}
%\centering
%\caption{}\label{fig:newcombPred}
%\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}
%\end{subfigure}

%\caption{Clockwise from top left: (a) marginal posteriors of $\beta$. (b) marginal posteriors for $\sigma^{2}$. (c) log predictive distributions.}
%\label{fig:newcomb}
%\end{sidewaysfigure}

%\textcolor{blue}{if we add the Newcomb and Belgium Calls data examples, this might be a good place to add them because they are low dimensional. I think it would be a good lead into the high dimensional computational strategies}

\section{Restricted Likelihood for the Linear Model}
\label{BayesLinMod}

\subsection{The Bayesian linear model}
We focus on the use of restricted likelihood for the Bayesian linear
model with a standard formulation: 
%\begin{eqnarray}
%\label{LinearModel}
%\bbeta & \sim & \pi_1(\bbeta); \qquad \sigma^2  \sim  \pi_2(\sigma^2)
%\nonumber\\
%y_i  & =  & x_i^\top \bbeta + \epsilon_i , \mbox{ for } i = 1, \ldots, n 
%\end{eqnarray}
\begin{eqnarray}
\label{LinearModel}
\bth&=&(\bbeta,\sigma^2) \sim  \pi(\bth) 
\nonumber\\
y_i  & =  & x_i^\top \bbeta + \epsilon_i , \mbox{ for } i = 1, \ldots, n 
\end{eqnarray}
where $x_i$ and $\bbeta \in \mathbb{R}^p$, \green{$\sigma^2 \in \mathbb{R}^+$}, 
and the $\epsilon_i$ are independent 
draws from a distribution with center $0$ and scale $\sigma$.
Two conditions are imposed on the model:
\begin{itemize}
\labitem{C1}{fullRank} The $n \times p$ design matrix, $X$, whose $i^{th}$ row is $x_i^\top$, 
is of full column rank.  
\labitem{C2}{supReal} The $\epsilon_i$ are a random sample from some distribution which has a density with 
respect to Lebesgue measure on the real line and for which the support is the real line.  
\end{itemize}

%\textcolor{blue}{commented out `Both conditions can be relaxed, although this would necessitate restating several later results.' and the paragraph here starting with `in the sequel'}
%In the sequel, we specifically consider both normal and $t$ distributions with
%mean $0$ and variance $\sigma^2$ for the $\epsilon_i$ 
%but note that our methods apply much more widely.  The prior distributions $\pi_1$ and $\pi_2$ can take
%many forms and may be joined to form a joint distribution for non-independent $\bbeta$
%and $\sigma^2$.  The conditionally conjugate normal/inverse gamma pair is a common 
%choice.  
%The methods we develop apply to the linear model in \eqref{LinearModel} and to many variations
%on it. For example, the prior distributions $\pi_1$ and $\pi_2$ can be joined to form a joint distribution for non-independent $\bbeta$
%and $\sigma^2$. 
As summary statistics for the data, we concentrate on robust estimators for the 
\green{regression} coefficients in the linear model and an associated 
estimator of the scale. In particular, we demonstrate the method using simultaneous M-estimators defined by \eqref{Mest} for the one-sample setting and easily extended to the linear model in \eqref{LinearModel}. The estimator of the \green{regression} coefficients is denoted by $\bb(X, \by)\in \mathbb R^{p}$ and that of the scale by \green{\sout{$s(X, \by)\in \mathbb R$} $s(X, \by)\in \{0\} \cup {\mathbb R}^+$} . Thus, $T(\by)=(\bb(X, \by), s(X, \by))$. The observed complete data is denoted by $\by_{obs}$ with observed statistic  denoted by $T(\by_{obs})=(\bb(X, \by_{obs}), s(X, \by_{obs}))$. %Assumption \ref{supReal} is important as it translates into a continuous distribution for $\bb(X, \by)$ and $s(X, \by)$ (with respect to $\by$), which is presumed for our computational strategy described below. The full column rank assumption \ref{fullRank} is made apparent by an examination of the proofs in the the appendix.

%These estimates convey information about $\bth=(\bbeta,\sigma)$
%while downweighting outliers.  The M-estimator of $\bbeta$ is determined by a $\rho$ function through the minimization
%\begin{eqnarray}
%\label{Mest}
%\bb(X,\by) & = & \argmin_{\bbeta} \sum_{i=1}^n \rho\left(\frac{y_i - x_i^\top \bbeta}{\sigma}\right) .  
%\end{eqnarray} 
%The scale estimator $s(X,\by)$ is determined simultaneously as another M-estimator or is determined through
%a separate calculation, for example the mean-absolute-deviation from an $\ell_1$ regression fit. Other estimators for the coefficients considered are least median squares (LMS) and least trimmed squares (LTS). LMS minimizes the median squared residual and LTS minimizes the sum of the $k$ smallest squared residuals where $k$ is chosen by the user. These estimators are also coupled with a scale estimator.% that is determined by the objective function evaluated at the minimum, appropriately scaled by a correction factor for consistency.

%which is presumed for our computational strategy. %Before deriving this strategy in section \ref{highDim}, we demonstrate the utility of the incomplete likelihood with a simple location and scale example. %The results we derive also apply to other estimators satisfying conditions \ref{asb}-\ref{scaleEq2Reg} below, not just M-estimators.

\subsection{Computational strategy}
\label{highDim}
%For low-dimensional statistics $T(\by)$ and $\bth$, the direct computational strategies described in \cite{lewis2014} can be used to evaluate the incomplete likelihood posterior.  
%These strategies rely on generation of complete data sets from different values of $\bth$.  
%Each complete data set leads to a statistic $T(\by)$ under $\bth$, and these generated statistics are used to estimate the density at $T(\by_{obs})$, where $\by_{obs}$ is the observed complete data. This estimate is fed into Bayes' theorem for the update from prior distribution to posterior distribution.  For the example in the previous section, these strategies work well.
%\textcolor{blue}{Comment out `A variety of  variance reduction techniques which exploit\dots' because it seemed too vague and a bit off topic}
%A variety of  variance reduction techniques which exploit 
%properties of the distribution of $\by$ 
%improve the performance of these strategies.

As mentioned above, direct computational strategies designed to approximate the restricted posterior break down for high-dimensional statistics $T(\by)$ or high-dimensional parameters $\bth$. %, direct computational strategies break down.  When the conditioning statistic is of high-dimension, density estimation becomes difficult and the associated approximate update in (\ref{RestrictedPosterior}) is unstable; when $\bth$is high dimensional, grid-based calculation and other numerical integration strategies fail.  
However, Markov chain Monte Carlo (MCMC) methods were developed for exactly these situations.  We turn to MCMC to 
fit the model in these circumstances.

%The general style of algorithm that we present relies on the decomposition of the sampling density in (\ref{FullLikelihood})
%into one piece involving only $T(\by)$ and a second piece for the
%complete data $\by$ given $T(\by)$. 
%Relying on the modularity of MCMC algorithms, we construct a data augmented Gibbs sampler targeting $\pi(\bth, \by | T(\by)=T(\by_{obs}))$, the joint posterior of $\bth$ and $\by$ conditioned on the summary statistic $T(\by_{obs})$ for observed data vector $\by_{obs}$. The Gibbs sampler iteratively samples from the full conditionals written as $\pi(\bth|\by T(\by)=T(\by_{obs})$ and $f(\by|\bth, T(\by)=T(\by_{obs})$
% \textcolor{blue}{some major changes from here to the end of the section}
The general style of algorithm that we present is a data augmented
MCMC algorithm targeting $f(\bth, \by |
T(\by)=T(\by_{obs}))$, the joint distribution of $\bth$ and the full
data given the summary statistic $T(\by_{obs})$.  % with $\by_{obs}$  representing the observed complete data. 
 The Gibbs sampler \citep{gelfand1990} iteratively samples from the
 full conditionals $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ and
 $f(\by|\bth, T(\by)=T(\by_{obs}))$.  
\green{Alternative algorithms substitute other generations for the full conditionals, such as the Metropolis-Hastings propose and accept/reject framework.  Our algorithms are based on the decomposition of the MCMC algorithm into conventional full data sampling steps where $\bth$ is generated given $\by$, and steps that allow us to complete the data set where $\by$ is generated given $\bth$ and $T(\by)$.  The latter generation relies on the conditioning set $\mathcal{A}=\{\by\in \mathbb{R}^n|T(\by)=T(\by_{obs})\}$.  The set $\mathcal{A}$ may contain more than one element (i.e., it is not degenerate) when $T(\by) : \by \rightarrow T(\by)$ is not a $1-1$ function.}
%\red{\sout{, where the two
%     conditioning sets are not degenerate (that is, $\by$ is such that
%     $T(\by)=T(\by_{obs})$).}}  \red{Unless $T(\by)=\by$, the set
%   $\mathcal{A}=\{\by\in \mathbb{R}^n|T(\by)=T(\by_{obs})\}$
%   is not degenerate, containing more elements than $\by_{obs}$ only.}

When $\by$ has the summary statistic \sout{$T(\by)$ matching $T(\by_{obs})$,} \green{$T(\by) = T(\by_{obs})$,}
the first full conditional, $\pi(\bth|\by, T(\by)=T(\by_{obs}))$, is
\red{the same as} the full data posterior
$\pi(\bth|\by)$. 
\green{In this case, the condition $T(\by) = T(\by_{obs})$ is redundant.  This allows us to make use of conventional MCMC steps for this generation.  For} 
\sout{In the case of} typical regression models, algorithms abound.  Details of the \green{recommended} algorithms depend on details of
the prior distribution and sampling density.  As examples, a normal
prior distribution and normal likelihood in the regression setting
allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
in the style of the 
hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
a scale parameter for each case and an extra stage where these scale parameters are generated.

%The other stage in the Gibbs sampler is the generation of complete data from the full conditional  $f(\by|\bth, T(\by)=T(\by_{obs}))$. %Condition \ref{supReal} above facilitates the extension of convergence proofs for the complete data algorithm to those for the incomplete data algorithm.  
%In this subsection, we focus exclusively this stage. 
%we begin with any conventional complete data algorithm.  In the case of typical regression models, these algorithms abound.  Details of the algorithm depend on details of
%the prior distribution and sampling density.  As examples, a normal
%prior distribution and normal likelihood in the regression setting
%allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
%leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
%in the style of the 
%hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
%$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
%a scale parameter for each case and an extra stage where these scale parameters are generated.  
%The additional stage needed to implement the incomplete likelihood analysis via MCMC 
%is a generation of the complete data given statistic ($T(\by_{obs})$) and parameter ($\bth$).  Condition \ref{supReal} facilitates the extension of convergence proofs for the complete data algorithm to those for the incomplete data algorithm.  
%In this subsection, we focus exclusively on the additional stage
%where we generate $\by | \bth, T(\by)$.  
For a typical model and conditioning statistic, the second full conditional $f(\by|\bth, T(\by)=T(\by_{obs}))\blue{ =f(\by|\bth, \by\in\mc A)}$ is not available in closed form.  
As a consequence, we turn to Metropolis-Hastings \citep{hastings1970},
using the strategy of proposing full data $\by$ \green{\sout{in the sample
space of the distribution} for which $T(\by) = T(\by_{obs})$} and either accepting or rejecting the
proposal. Let $\by_p$ and  $\by_c$ represent the proposed and current
full data, respectively.  \green{In subsequent algorithms, we propose only from the set $\mathcal{A}$}. Denote the proposal distribution for $\by_{p}$ by $p(\by_p|\bth,T(\by_p) = T(\by_{obs})) \green{ = p(\by_p|\bth,\by_p \in \mathcal{A}) = p(\by_p | \bth)}$.  
\green{The last equality follows from the fact that our $p(\cdot | \bth)$ assigns probability one to the event $\{ \by_p \in \mathcal{A} \}$.  These equalities still hold if the dummy argument $\by_p$ is replaced with $\by_c$.  The conditional density is
\begin{eqnarray*}
f(\by | \bth, \by \in \mathcal{A}) & = & \frac{f(\by | \bth) I(\by \in \mathcal{A} | \by, \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} \\
     & = & \frac{f(\by | \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} 
\end{eqnarray*}
for $\by \in \mathcal{A}$.  This includes both $\by_p$ and $\by_c$.  
}

The Metropolis-Hastings acceptance probability  is the minimum of 1 and $R$ where,
\begin{eqnarray}
\label{MHRatio}
R & = & \frac{f(\by_p|\bth,\by_p \in \mathcal{A})}{f(\by_c|\bth,\by_c \in \mathcal{A})}  
                \green{\frac{p(\by_c|\bth, \by_c \in \mathcal{A})}{p(\by_p|\bth,\by_p \in \mathcal{A})}} \\
  & = & \frac{f(\by_p | \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} \frac{\int_\mathcal{A} f(\by | \bth) d\by}{f(\by_c | \bth)} \frac{p(\by_c | \bth)}{p(\by_p | \bth)} \\
 & = & \frac{f(\by_p|\bth)}{f(\by_c|\bth)} \frac{p(\by_c|\bth)}{p(\by_p|\bth)} .  
\end{eqnarray}
\green{Note:  Above expression changed.  Check argument again.}
%In the above expression, the second line follows from the first for
%the following reason. The proposed \green{vector $\by$} is sampled from
%  $\mathcal{A}$ so that
%$T(\by_{p})=T(\by_{c})=T(\by_{obs})$. This implies 
%\green{\sout{$f(\by |\bth,
%T(\by)=T(\by_{obs}))=f(\by |\bth)\pi(\bth)/\red{f[?]}\pi(\bth, T(\by)=T(\by_{obs}))$}
%\begin{eqnarray}
%f(\by |\bth,\by \in \mathcal{A})) & = & \frac{f(\by | \bth) \pi(\bth) I(\by \in \mathcal{A})}{\int f(\by | \bth) \pi(\bth) I(\by \in \mathcal{A}) d\bth}
%\end{eqnarray}}
%where $\by$ represents either $\by_{p}$ or $\by_{c}$. %Further, the expressions $\pi(\bth)$ and $\red{f[?]}\pi(\bth, T(\by)=T(\by_{obs}))$ 
%\green{The expressions $\pi(\bth)$ and $\int f(\by | \bth) \pi(\bth) I(\by \in \mathcal{A})  d\bth$} are the same for $\by_{p}$ and $\by_{c}$ and cancel in the ratio. %Similar expansions can be made for the proposal distribution. 
%\green{Further, the indicator functions can be dropped since $\by_p$ and $\by_c$ will both fall in $\mathcal{A}$.}  
%\green{Note:  Check this argument carefully}

For the models we consider, evaluation of $f(\by | \bth)$ is straightforward.  Therefore, the difficulty in implementing this Metropolis-Hastings step manifests  itself in the ability to simulate proposals that guarantee $T(\by) = T(\by_{obs})$ and on the evaluation of the proposal density derived from the method used to simulate $\by$. We now discuss such an implementation method for the linear model in \eqref{LinearModel}.

\subsubsection{Construction of the proposal}
%\textcolor{blue}{some major revisions as indicated in the responseToReferees}
Our \green{computational} strategy is easiest to envision in a location-scale setting where 
the design matrix in model (\ref{LinearModel}) consists of a single column of ones.  Robust estimation techniques along
with model (\ref{LinearModel}) suggest a conditioning statistic $T(\by)$ which consists of
estimates of the scalars $\beta$ and $\sigma$, say $T(\by)=(b(X,\by),
s(X,\by))$.  It is not a simple matter to directly sample the required
proposal $\by$ satisfying $T(\by)=T(\by_{obs})$. However, 
  with equivariance/invariance properties of $T(\by)$, we will see in Theorem \ref{Transformation} below
    that it is possible to scale and shift any \sout{$\bz^{*}\in \mathbb R^{n}$} \green{$\bz^{*}$ which generates 
a positive scale estimate} to such a
    $\by$. Hence, to obtain $\by$ from $\mathcal A$, we proceed
  in two steps. First, a vector $\bz^*$ is sampled from a known
  distribution (examples of which are described later). This vector has summary statistic   
$T(\bz^*) = (b(X,\bz^*), s(X,\bz^*))$ which may not match the observed summary
$T(\by_{obs})$.  Second, $\bz^*$ is mapped into $\by =h(\bz^*)$
using Theorem \ref{Transformation} so that $T(\by)=T(\by_{obs})$. To
evaluate the proposal density $p(\by|\bth)$, we need to adjust
the known density of $\bz^*$, $p(\bz^*)$, with the Jacobian of
the transformation $h(\cdot)$ to $\by$. We choose the
distribution of the \green{\sout{intermediate}} data vector $\bz^*$ to have support
\green{on a subset of $\mathbb R^n$ so that}
the transformation to $\by$ is one-to-one and the Jacobian,
$\displaystyle \left|\frac{\partial h^{-1}(\by)}{\partial \by}\right|$, can be computed from first principles. It is the calculation of this Jacobian which is described in the section. We will repeatedly return to an artificial low-dimensional example in the location-scale setting to help visualize this calculation.

% To 
%obtain data $\by$ for which $T(\by) = T(\by_{obs})$, we proceed in two
%steps.  
%First, a vector $\bz^*$ is generated from a simple manifold with known
%density, for example, a uniform distribution
%on the surface of the unit sphere in ${\mathbb R}^{n-1}$ (alternatively from
%the model with current values of $\beta$ and $\sigma$).  This leads to 
%$T(\bz^*) = (b(X,\bz^*), s(X,\bz^*))$.  The vector $\bz^*$ is mapped into a vector
%$\by$ by rescaling and shifting appropriately to match the observed conditioning statistic.  For typical estimators, the appropriate scaling is 
%$s(X,\by_{obs}) / s(X,\bz^*)$ with the shift trailing along as needed to match $b(X,\by_{obs})$.  
%To evaluate the proposal density of $\by$,
%we need to adjust the density of $\bz^*$ with a Jacobian.  In the sequel, we use this artificially low-dimensional
%example to illustrate the method.

The strategy described in the previous paragraph extends to full-blown regression models.  Robust regression methods lead naturally to a conditioning statistic in the form of a classical M-estimator for $\bbeta$
and a companion estimator for $\sigma$.  We denote the resulting estimator which involves the covariates through
the design matrix and the response 
as $T(\by) = (\bb(X,\by), s(X,\by))$, with $\bb(X,\by) = (b_1(X,\by), \cdots,
b_p(X,\by))^\top$.  Simultaneous M-estimators have a number of standard properties \ref{asb}-\ref{scaleEq2Reg} which
prove useful in the sequel \citep{huber2009, maronna2006}.  
\begin{itemize}
\labitem{C3}{asb}$\bb(X,\by)$ is almost surely continuous and differentiable with respect to $\by$.  
\labitem{C4}{as} $s(X,\by)$ is almost surely positive, continuous, and differentiable with respect to $\by$.  
\labitem{C5}{regEq} $\bb(X,\by+X\bv)=\bb(X,\by)+\bv \ \ \text{for  all}\ \bv\in\mathbb{R}^p$. 
\labitem{C6}{scaleEqReg} $\bb(X,a\by)=a\bb(X,\by)\ \ \ \text{for all constants } a$.  
\labitem{C7}{regIn} $s(X,\by+X\bv)=s(X,\by) \ \ \text{for all}\ \bv\in\mathbb{R}^p$.  
\labitem{C8}{scaleEq2Reg} $s(X, a\by)=|a|s(X,\by) \ \ \text{for all constants } a$.  
\end{itemize}
Properties \ref{regEq} and \ref{scaleEqReg} of $\bb$ are called
\textit{regression} and \textit{scale equivariance},
respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
and \textit{scale equivariance}. 
Many other estimators satisfy these properties, and our subsequent results apply equally
well to them.  With more cumbersome statements, the upcoming results can be adjusted to handle 
a relaxation of \ref{as} that 
$s(X,\by_{obs}) > 0$ and $P(s(X,\by)>0)>0$.

We have stated that any vector $\bz^{*} \in \mathbb{R}^n$ can be transformed to a proposal
$\by$ satisfying $T(\by) = T(\by_{obs})$.  The properties above ensure
that this can be done through the mechanism presented in the following theorem.  The proof of this and other results appear in the appendix.
\begin{theorem}
\label{Transformation}
Assume that conditions \ref{as}-\ref{scaleEq2Reg} hold.  Then, any vector $\bz^* \in \mathbb{R}^n$ with conditioning statistic
$T(\bz^*)$ \green{for which $s(X,\bz^*) > 0$} can be transformed into $\by$ with conditioning statistic $T(\by) = T(\by_{obs})$ 
through the transformation 
\[
\by = \frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^* + X\left(\bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^*)\right) .  
\]
\end{theorem}
The mapping described in the theorem is many-to-one in general.
Its range is the collection of data sets which match
the observed summary statistic:
\begin{equation}
\label{sampleSpace}
 \mathcal{A}=\{\by\in \mathbb{R}^n | T(\by)=T(\by_{obs})\}.
\end{equation}
To see this, note that the theorem shows that any $\by$ expressed as in the theorem is an element of $\mc A$. Further, any $\by \in \mc A$ can be expressed as in the theorem by simply replacing $\bz^{*}$ with $\by$. That is, any vector already in $\mc A$ requires no shifting or scaling. The set $\mathcal{A}$ is an $n - p - 1$ dimensional space: 
there are $p$ constraints imposed by the regression coefficients and one further constraint imposed by the scale.  
The form of the set is determined by the statistic $T(\cdot)$.  Figure~\ref{fig:sampSpace} 
provides an artificial low-dimensional
visualization of such a set $\mathcal{A}$ with a location-scale
  model.  In the figure, $n = 3$, and the conditioning
statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$. The
set $\mathcal{A}$ is depicted  for $T(\by_{obs})=(0,1)$ and is a
``warped triangle'' in light blue, with each side
corresponding to a particular coordinate of $\by$ being the minimum
value \green{of} zero. The other two coordinates are restricted by the scale
statistic to lie on the quarter circle of radius one in the positive
orthant. In general, this set may be compact and given by a closed
curve, as in the figure, or it may be unbounded, depending on the
  choice of $T(\by)$.  The other sets labeled in the figure will be described shortly.

%\begin{figure}[t]
%\centering
%\includegraphics[width=4in]{minSS3dSampleSpace.jpg}
%\caption{A depiction of $\mathcal{A}$, $\Pi(\mathcal{A})$, and the
%  unit circle for the illustrative example where $b_{1}(\mathbf{1},\by)=\min(\by)=0$ and
%  $s(\mathbf{1},\by)=\sum (y_i -b_{1}(\mathbf{1},\by))^2 =1$.
%$\mathcal{A}$ is the combination of three quarter circles, one
%  on each plane defined by $y_i=0$. The projection of this manifold
%  onto the deviation space is depicted by the bowed triangular shape
%  in the plane defined by $\sum y_i=0$. The circle in this plane
%  represents the sample space for the intermediate sample \green{$\bz^*$}. Also
%  depicted is the vector $\mathbf{1}$, the design matrix for the
%  location and scale setting.}
%\label{fig:sampSpace}
%\end{figure}

The set $\mathcal{A}$ typically does not lie in a linear space of dimension $n - p - 1$, and 
so we must account for both the many-to-one nature of the mapping and
a Jacobian when deriving the proposal density.  We handle the first
point by sampling the initial $\bz^*$ from
 a reduced $n - p - 1$ dimensional space which, through the scaling and
shifting of the above theorem, maps uniquely to a point 
in $\mathcal{A}$. This reduced space is chosen so that the range of the map is the
entirety of $\mathcal{A}$.  The Jacobian does not cancel in
\eqref{MHRatio}, since the scaling depends on the initial proposal.

The reduced space from which the initial sample is taken is simply the
unit sphere \green{\sout{restricted to} in} the orthogonal complement of the column space of the design matrix (i.e., the least squares residual space). To help understand the density of the proposal derived from the transformation of this initial sample we introduce the following notation. Denote the column space of the design matrix $X$ by $\mathcal{C}(X)$ and its orthogonal complement by $\mc{C}^\perp(X)$. 
\green{\sout{This} The latter} is the least squares residual space which we will often refer to as the `deviation space'.  The projection of the set $\mathcal{A}$ onto the deviation space is 
\begin{equation}
\label{sampleSpacePerp}
\Pi(\mathcal{A})=\{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\
s.t.\ \bz=Q \by \}
\end{equation} 
where $Q$ is the projection matrix onto  $\mc{C}^\perp(X)$. Explicitly, $Q=I-H$ with $H=XX^\top$ where we assume, without
loss of generality following condition \ref{fullRank},  that the
columns of $X$ form an orthonormal basis for $\mc{C}(X)$
(i.e., $X^\top X=I$). It will also be helpful at times to write $Q=WW^{\top}$ where the columns of $W$ form an orthonormal basis for $\mc{C}^\perp(X)$. This set has been introduced because we will first transform the initial distribution on the sphere to the distribution on this set. Then we will transform to the \green{\sout{sample space} set} $\mc A$.

Returning to the artificial example, Figure~\ref{fig:sampSpace}
depicts $\Pi(\mathcal{A})$ as well as the sphere from which we obtain
the initial sample. The column vector $X=\bf{1}$ spans $\mc{C}(X)$ and
is shown as a reference. The triangle with bowed sides in dark
  blue is  $\Pi(\mathcal{A})$, the projection of $\mc A$ onto the
plane orthogonal to $\mb 1$ (i.e., $\mc{C}^\perp(X)$). The \green{unit} sphere from
which the initial sample is taken is depicted as the red circle in this plane.  In general, this is the unit sphere in the $n-p$ dimensional space $\mc{C}^\perp(X)$.

For the transformation of the initial proposal $\bz^*$ on the surface of the sphere to $\by\in \mc A$ , we first move to a point on $\Pi(\mathcal{A})$ through a 
simple scaling of $\bz^*$.  This is followed by undoing the projection with a move from 
$\Pi(\mathcal{A})$ to its (unique) preimage on $\mathcal{A}$. Together, these two steps correspond to the
transformation in Theorem~\ref{Transformation}.  The introduction of
the sphere in $\mc {C}^\perp (X)$ as the initial proposal surface
along with properties \ref{regEq}-\ref{scaleEq2Reg} ensure that the mapping is
1-1. In particular, property
\ref{scaleEq2Reg} ensures the scaling to be unique and \ref{regIn}
implies that the scale statistic is unchanged when undoing the
projection. Property \ref{regEq} ensures the uniqueness of undoing the
projection.  The general proposal strategy is summarized as follows:
\begin{enumerate}
\item Sample $\bz^*$ from a distribution with known density on the unit sphere in $\mc{C}^\perp(X)$.
\item Calculate the Jacobian of \green{the} transformation in Theorem \ref{Transformation} in two steps.
\begin{enumerate}
\item Scale from unit sphere to $\Pi(\mathcal{A})$: $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$
\item Shift  from $\Pi(\mathcal{A})$ to $\mathcal{A}$: $\by=\bz+X\left(\bb(X, \by_{obs})-\bb(X, \bz)\right)$
\end{enumerate}
\end{enumerate}

\subsubsection{Evaluation of the proposal density} 
Calculation of the appropriate Jacobian of the transformation is absolutely vital and also non-trivial. Writing the transformation from the unit sphere in deviation space to $\mathcal{A}$ in 
two steps facilitates calculation of the Jacobian in two steps as written above. % \textcolor{blue}{added the following sentence, hopefully it helps}
We now explain each step, keeping in mind that the Jacobian of a transformation is simply the ratio of infinitesimal volumes along the tangents of the domain and range of the transformation.

\vskip 0.05 in
\noindent
{\bf Scale from unit sphere to $\Pi(\mathcal{A})$} \\
The first step is constrained to $\mc{C}^\perp(X)$ where the unit sphere is transformed to $\Pi(\mathcal{A})$. We further break this \green{\sout{piece} step into \sout{in two steps} into two substeps}: first, the distribution on the unit sphere is transformed to that along a sphere of radius $r=\|\bz\|={s(X,\boldsymbol{y}_{obs})}/{s(X, \boldsymbol{z}^{*})}$. This contributes \green{a factor of} $r^{-(n-p-1)}$ to the Jacobian. Second, the new sphere is then deformed to $\Pi(\mathcal{A})$.  This deformation contributes an attenuation to the Jacobian equal to the
ratio of infinitesimal volumes in the
tangent spaces of the sphere and $\Pi(\mathcal{A})$ at $\bz$.  
Restricting ourselves to the $n-p$ dimensional space $\mc{C}^\perp(X)$, this
ratio is the cosine of the angle between the normal 
vectors of the two sets at $\bz$.  The normal to the sphere is its radius vector $\bz$. The normal to
$\Pi(\mathcal{A})$ is given in the following lemma.

\begin{lemma}
\label{gradSTheoremReg}
Assume that conditions \ref{fullRank}-\ref{supReal}, \ref{as}, and \ref{regIn} hold.  
Let $\by\in \mathcal{A}$. Let 
$\nabla s(X,\by)$ denote the
gradient of the scale statistic with respect to the data vector evaluated at
$\by$.  Then $\nabla s(X,\by)\in \mc{C}^\perp(X)$ and is 
normal to $\Pi(\mathcal{A})$ at $\bz=Q\by$  in $\mc{C}^\perp(X)$.
\end{lemma}

As a result of the lemma, the contribution to the  Jacobian of this attenuation is 
\begin{equation}
\label{cosine}
\cos(\gamma)=\frac{\nabla s(X,\by)^\top \bz}{\|\nabla
s(X,\by)\| \|\bz\|},
\end{equation}
where $\gamma$ is the angle between the two normal vectors.
This step is illustrated in Figure~\ref{fig:stretchDeform} for the toy
location-scale example.  The figure \green{\sout{only}} pictures \green{only} the deviation space
which in this case is a plane. The original unit  sphere (here, the
solid circle) is first stretched to the dashed sphere contributing
$r^{-(n-p-1)}$ to the Jacobian as seen in panel (a). In panel (b), the
dashed circle is transformed onto $\Pi(\mc A)$ contributing
$\cos(\gamma)$ to the Jacobian. The normal vectors in panel (b) are
orthogonal to the tangent vectors of $\Pi(\mc A)$ and the circle. As
stated above, the Jacobian is the ratio of infinitesimal lengths along these tangent vectors. This is the same as the ratio of the infinitesimal lengths of the normal vectors (i.e., $\cos(\gamma)$). This generalization extends to higher dimensions where the `lengths' along the tangent vectors become volumes along the tangent spaces.

%\begin{sidewaysfigure}[t]
%\centering
%\captionsetup{justification=centering}
%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace3.pdf}}\quad
%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
%\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
%  to $\bz$. The adjustment for the stretch transforms the density
%  along the unit circle to the density along the circle of radius
%  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
%  deformation from the distribution along the circle to the
%  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
%  be the cosine of the angle between the normals to each manifold.}
%\label{fig:stretchDeform}
%\end{sidewaysfigure}

\vskip 0.05 in
\noindent
{\bf Shift from $\Pi(\mathcal{A})$ to $\mathcal{A}$} \\
The final piece of the Jacobian comes from the transformation from
$\Pi(\mathcal{A})$ to $\mathcal{A}$.  %For this we return to the full $n$ dimensional space.  
This step involves a shift of
$\bz$ to $\by$ along the column space of $X$. Since the shift depends on 
$\bz$, the density on the set 
$\Pi(\mathcal{A})$ is deformed by the shift. The
contribution of this deformation to the Jacobian is, again,
the ratio of the infinitesimal volume along $\Pi(\mathcal{A})$ at $\bz$ to the
corresponding volume along $\mathcal{A}$ at $\by$. 
The ratio is calculated by considering the volume of the
projection of a unit hypercube in the tangent space of $\mathcal{A}$
at $\by$ onto $\mc{C}^\perp(X)$.
Computational details are
given in the following lemmas and subsequent theorem. Throughout, let
$\mc T_{y}(\mc A)$ and $\mc T_{y}^{\perp}(\mc A)$ denote the tangent
space to $\mc A$ at $\by$ and its orthogonal complement respectively.

\begin{lemma}
\label{lem:basis}
Assume that conditions \ref{fullRank}-\ref{regEq} and \ref{regIn}-\ref{scaleEq2Reg} hold.  Then the $p+1$ gradient vectors 
$\nabla s(X,\by), \nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$ form a
basis for $\mc T_{y}^\perp(\mc A)$ with probability one.
\end{lemma}

The lemma describes construction of a basis for $\mc T_{y}^\perp(\mc A)$.  This leads to a 
basis for $\mc T_{y}(\mc A)$.  Both of these bases can be orthonormalized.  
Let $A=[a_{1},\dots,a_{n-p-1}]$  and $B=[b_1,\dots,b_{p+1}]$ denote the 
matrices whose columns contain the orthonormal bases for  $\mc T_{y}(\mc A)$ and  $\mc T^{\perp}_{y}(\mc A)$, respectively.  
The columns in $A$ define a unit hypercube in $\mc T_{y}(\mc
  A)$ and their projections onto $\mc{C}^\perp(X)$ define a parallelepiped.
We defer construction of $A$ until later.

\begin{lemma}
\label{lem:fullrank}
Assume that conditions \ref{fullRank}-\ref{regEq} and \ref{regIn}-\ref{scaleEq2Reg} hold.  
Then the $n\times (n-p-1)$ dimensional matrix $P=QA$ is of full column rank.
\end{lemma}

As a consequence of this lemma, 
the parallelepiped spanned by the columns of $P$ is not
degenerate (it is $n-p-1$ dimensional), and its volume
is given by
\begin{equation}
\label{eq:volume}
\text{Vol} (P) := \sqrt{\text{det}(P^\top P)}=\prod_{i=1}^{r} \sigma_i
\end{equation}
where $r=\text{rank} (P)=n-p-1$ and $\sigma_1\geq
\sigma_2\geq\dots\geq\sigma_r>0$ are the singular values of $P$ (e.g.,
\cite{miao1992}). 
Combining Lemmas \ref{lem:basis} and \ref{lem:fullrank} above leaves us with the following result concerning the calculation of the desired Jacobian.  
\begin{theorem}
\label{Jacobian}
Assume that conditions \ref{fullRank}-\ref{regEq} and \ref{regIn}-\ref{scaleEq2Reg} hold.  Then the
Jacobian of the transformation from the distribution along 
$\Pi(\mc A)$ to that along $\mc A $ is equal to the volume given in \eqref{eq:volume}.
\end{theorem}

\vskip 0.05 in
\noindent
{\bf The proposal density} \\
Putting all the pieces of the Jacobian together we have the following result. Any dependence on other variables, including current states in the Markov chain, is made implicit. 
\begin{theorem} 
Assume that conditions \ref{fullRank}-\ref{scaleEq2Reg} hold.  Let $\bz^{*}$ be sampled on the unit sphere in $\mc {C}^\perp (X)$ with density $p(\bz^{*})$.  Using the transformation of $\bz^*$ to $\by\in \mc A$ described in Theorem \ref{Transformation}, the density of $\by$ is
\begin{equation}
\label{dens:ystst}
p(\by)=p(\bz^*) r^{-(n-p-1)} \cos(\gamma)\text{Vol} (P)
\end{equation}
where $r={s(X,\boldsymbol{y}_{obs})}/{s(X,  \boldsymbol{z}^{*})}$,
and $\cos(\gamma)$ and $\text{Vol} (P)$ are as in equations \eqref{cosine} and \eqref{eq:volume}, respectively. 
\end{theorem}

In practice, computing $A$ directly to find $P$ and $\text{Vol} (P)$ is computationally intensive as it involves orthogonalization of $n$ vectors in $n$-dimensional space. 
To find a matrix $A$, supplement $B$ with a set of $n$ linearly independent columns on the right, and apply Gram-Schmidt 
orthonormalization to the matrix.  This algorithm is infeasibly slow when $n$ is large because it is $\mc O(n^3)$ and must be repeated at each
iterate of the MCMC when a complete data set is drawn.  
Fortunately, we can make use of results related to \textit{principal angles} found in \cite{miao1992} to compute the volume in \eqref{eq:volume} using $B$ and an orthonormal basis for $\mc C (X)$ (The definition of principal angles can be found in the cited text). Recall, $B$ is constructed by orthogonalization of a basis for $\mc T_{y}^\perp(\mc A)$. Since this space is of dimension $p+1$, applying Gram-Schmidt to find the orthonormal basis is much faster, the algorithm is $\mc O(np^2)$, and there is a 
considerable reduction in computational burden when $n \gg p$. 
Further, the singular values of $P=QA$ are also the singular values of
$W^\top A$ (recall, $Q=WW^{\top}$), which can be easily obtained through $B$.
The following corollary formally states how computation of $A$ can be circumvented. 
\begin{corollary}
\label{theorem:sings}
Let $U$ be a matrix whose columns
form an orthonormal basis for $\mc C (X)$. Then the non-unit singular
values of $U^\top B$ are the same as the non-unit singular values of $W^\top A$.  
\end{corollary} 
\noindent Thus, we can compute $\text{Vol} (P)$ by finding the singular values of $U^\top B$, reducing the computational burden substantially.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Applications
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Applications}
\label{Applications}
We illustrate the methods developed in Sections~\ref{restrictedlikelihood} and \ref{BayesLinMod} with a pair of regression models for 
data from Nationwide Insurance Company, which concern prediction of
the performance of insurance agencies.
The data contain outliers and are subject to model misspecification.  
In particular, a group of the data do not follow the same generative process as the data of interest.  It would be 
extremely challenging to model some features of the data.  
In our analysis, we follow the standard practice when demonstrating the benefits of robust 
methods.  We work with a naive model for the data which ignores certain features of the problem.  We
do this both to create a situation where all can agree that the model for the full data $\by$ is imperfect
and to preserve the confidentiality of selected aspects of modelling done by Nationwide.  
We wish to provide inference for the `good' portion of the data.  The two models we fit either treat the analysis
as a single regression or as a collection of related regressions.  Details of the models, prior distributions, 
and conditioning statistics are given in the next two subsections.

%%%%%%%%%%%%%%%%%%%%%%%
%NW data
%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Nationwide Data}
The Nationwide Insurance Company sells many of its insurance policies through agencies which provide direct service to policy holders.  
The contractual agreements between Nationwide and these agencies vary.  Of major interest to Nationwide is the prediction of future performance of agencies where, for our purposes,  performance is measured by the total number of households an agency services (`household count'). A serviced household is one in which at least one person living at that residence has at least one policy written through the agency. We used data from previous years to build a model to forecast future household count. In particular, we use agency characteristics, as measured during a single month in $2010$, to predict household counts in the corresponding month in $2012$. The characteristics used are household count and two measurements of agency size/experience. The two measurements of agency size/experience are, roughly, the number of employed persons at the agency and the length of time the agency has been affiliated with Nationwide. The household counts (response and predictor) have been square rooted to stabilize variance. The data are 
proprietary, and to mask them all variables have been individually centered and scaled and identifiers (agency/agent names and state
labels) have been removed. 
All subsequent analysis is done on this scale.  As an exploratory view, a plot of the square root of count in 2012, against that in 2010 
is shown in Figure \ref{fig:ctVct}.  The different colors represent the varying contractual agreements as they stood in 2010. `Type 1' agencies are of special interest.  Among the open agencies, a strong linear correlation exists.  The specific linear relationship
depends on agency type. The data are characterized by a large number of agencies which were open in 2010 but closed sometime before 2012, as represented by the horizontal band at $0$. We use these data as a test bed for our techniques, fitting models that do not account for agency closures or contract type.  Our expectation is that \green{\sout{the incomplete} restricting the} likelihood will facilitate prediction for the good part of the data.

%\begin{figure}[t]
%\centering
%\includegraphics[width=4in]{countvcount.pdf}
%\caption{The square root of count in 2012 versus that in 2010 (after centering and scaling). The colors represent the varying contractual agreements as they stood in 2010.  Agencies that closed during the 2010-2012 period are represented by the zero counts for 2012. Scalings on the axes are purposely left off for proprietary reasons.}
%\label{fig:ctVct}
%\end{figure}

\subsection{Regression model}
\label{regModelNW}
The first analysis that we consider is based on a single regression.  We use 
the following standard normal theory regression model 
\begin{equation}
\label{eq:regModel}
\bbeta\sim N_p(\bmu_0, \Sigma_0);\ \ \sigma^2\sim IG(a_0,b_0);\ \  
y_{i}=\bx_{i}^\top\bbeta+\epsilon_{i},\ \ \epsilon_{i}\iid N(0, \sigma^2),\ i=1,\dots, n, 
\end{equation}
where $\bbeta$ is a four dimensional vector ($p=4$) of regression coefficients for the intercept, square root of count in 2010, and the two size/experience measures, and $y_{i}$ is the square rooted household count in 2012 for the $i^{th}$ agency with covariate vector $\bx_{i}$.  Although the mean of covariates and response have been removed, we include the intercept as fitting is done on a holdout set to evaluate predictive performance.  
The hyper-parameters $a_0, b_0, \bmu_0$ and $\Sigma_0$ are all fixed and set from a 
robust regression fit to the data from the time period two years
before. Letting $\hat\bbeta$ represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.  %corresponding to  a unit information prior for $\bbeta$. 
The hyperparameters for $\sigma^2$ are set so that the prior mean is $s^2$, the estimated variance from the robust regression, and the spread of the prior covers the range of plausible values with high probability. All values are then transformed appropriately to match the current scale of the data. In the end we take $\bmu_0=(0.18,  0.81,0.01,-0.02)^\top$ and set the mean of $\sigma^2$ to $0.014$ and standard deviation to  $0.033$.

We compare four Bayesian models: the standard Bayesian normal theory model, two restricted likelihood models, both with simultaneous M-estimators, and a heavy-tailed model.  For the restricted likelihood methods we use the same simultaneous M-estimators as in Section \ref{darwinAnalysis} adapted to linear regression.  The heavy-tailed model replaces the normal sampling density in \eqref{eq:regModel} with a $t$-distribution with $\nu = 3$ degrees of freedom. %We have used the default tuning parameter settings for the {\tt rlm} function in the R package {\tt MASS} \citep{venables2002}.  Both use Huber's scale estimator as in the {\tt rlm} implementation.  
We also fit the corresponding classical robust regressions and a least squares regression.

\subsubsection{Method of model comparison}
We wish to examine the performance of the models in a fashion that preserves the essential features of the 
problem.  Since we are concerned with outliers and model 
misspecification, we understand that our models are imperfect and so prefer to use an out-of-sample measure of fit.  
This leads us to cross-validation.  We repeatedly split the data into training
and validation sets.  We fit the model to the training data and assess its performance on the validation data.

The presence of numerous outliers in the data implies that both training and validation data will contain 
outliers.  For this reason, the evaluation must be robust to a certain fraction of bad data.  
The two main strategies are to robustify the evaluation function \citep[e.g.,][]{ronchetti1997} or 
to retain the desired evaluation function and trim cases \citep{jung2014}.  Here,
we pursue the trimming approach with log predictive density for the Bayesian models and log plug-in 
maximum likelihood for the classical fits used as the evaluation function.

The trimmed evaluation proceeds as follows in our context.  The evaluation function for case $i$ in the hold-out data
is the log predictive density, say
$\log(f(y_i))$, with the conditioning on the 
summary statistic suppressed.  The trimming 
fraction is set at $0 \leq \alpha < 1$. To score a method,
we first identify a base method. Denote the predictive density under this method by $f_{b}(y)$.  Under the base method, $\log(f_{b}(y_i))$ is computed for each case in the 
validation sample, say $i = 1, \ldots, M$.  Order the validation
sample according to the ordering of $\log(f_{b}(y_i))$ and denote this
ordering by $y_{(1)}^b, y_{(2)}^b, \dots, y_{(M)}^b$. That is, for $i<j$
$\log(f_{b}(y_{(i)}^b))<\log(f_{b}(y_{(j)}^b))$. All of the methods are then scored on the validation sample with the mean trimmed log marginal pseudo likelihood, 
\[TLM_b(A) = (M - [\alpha M])^{-1} \sum_{i=[\alpha M]+1}^{M}
    \log(f_A(y_{(i)}^b)),\]
 where $f_A$ corresponds to the predictive
 distribution under the method ``A'' being scored.  In other words, the $[\alpha M]$ observations with the smallest values of $\log(f_{b}(y))$ are 
removed from the validation sample and all of the methods are scored using only the
remaining $M - [\alpha M]$ observations. This process is advantageous to the base method.  A method
that performs poorly when it is the base method is discredited.  For a complete evaluation, we allow each method
to appear as the base method.  For brevity, we present only a selection of results in our subsequent analyses.

\subsubsection{Comparison of predictive performance}
Model performance is assessed
using the mean and standard deviation of the TLM 
across $100$ different splits into training and validation samples. First, we include all observations
in each validation sample to calculate TLM for each split. We then
repeat the evaluation using only certain subsets of the validation
sample that are of special interest. Subsets include open agencies,
open `Type 1' agencies, and `Type 1' agencies. For brevity, we include
results for the `Type 1' agencies only. As noted, assessing model
predictions on this set of agencies is of special interest to the
company.  A range of training sample sizes was used and we include
results from $n=25,100,1000,$ and $2000$ out of a total of $3180$ agencies. The trimming fraction, $\alpha$, ranges from $0$ to $0.3$. A classical robust regression to the prior data assigns zero weight to around $16\%$ of observations; in essence removing these from the analysis. This informed the range of trimming fractions chosen.  
In practice, we would set $\alpha$ slightly larger than $0.16$.

%\begin{sidewaysfigure}
%\centering
%\captionsetup{justification=centering}
%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=1]{logMargType1AgenciesBaseModelt}}\quad
%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=2]{logMargType1AgenciesBaseModelt}}\quad
%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=3]{logMargType1AgenciesBaseModelt}}
%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in, page=1]{logMargType1AgenciesBaseModelt}}\quad
%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=2]{logMargType1AgenciesBaseModelt}}\quad
%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=3]{logMargType1AgenciesBaseModelt}}
%\caption{Model evaluation for `Type 1' agencies for training sample
%  sizes of $n=25,100$, and $1000$. The $t$-model is used as the base
%  method to compute TLM. Plotted are the mean TLM for each model
%  against the trimming fraction across the $100$ cross-validation
%  samples. Error bars correspond to one standard deviation of TLM
%  above and below the mean. Models are labeled with the following
%  abbreviations: `rlm' corresponds to a classical robust fit, `restr.'
%  corresponds to our restricted likelihood method, and `t' corresponds to the
%  heavy-tailed $t$-distribution model. The letters `T' and `H'
%  appearing after `rlm' and `restr.' correspond to the use of  Tukey's
%  and Huber's $\psi$ respectively.  
%}
%\label{fig:Type1Marg}
%\end{sidewaysfigure}
%

Model evaluation for `Type 1' agencies is shown in Figure
\ref{fig:Type1Marg} for training sample sizes $n=25, 100,$ and $1000$.
The $t$-model is used as the base
  method to compute TLM.
The models pictured are: classical robust regression with Tukey's $\psi$ function (rlm-T), restricted likelihood with Tukey $\psi$ (restr.-T), classical robust regression with Huber's $\psi$ function (rlm-H), restricted likelihood  with Huber's $\psi$ (restr.-H), and the thick tailed $t$-model (t). The normal theory models perform poorly due to the numerous outliers
and are left out of the figures. Appearing in the figures are the mean TLM across
validations set for each model and each trimming fraction, $\alpha$ (along the $x$-axis). The error bars depicted are one standard deviation of the TLM above and below the mean.  The range of the vertical axis is chosen to enhance important features and as a result, some evaluation measures extend below this range. In particular, the restricted likelihood methods perform poorly if no trimming is done; reflecting that these methods are not intended to fit well to outliers. Recall that we expect about 15-16\% outliers in the validation sets, thus trimming fractions slightly larger than this amount are needed in order to assess fits to the `good' data. For $n=25$, the thick tailed model  prevails across trimming fractions, although less so for $\alpha\geq 0.15$. For sample sizes as low as $n=100$, the restricted likelihood methods outperform the heavy-tailed model with the Tukey version performing the best.   
The stronger performance of restricted likelihood based on Tukey's method and the t model is to be expected, as many of the 
residuals are so extreme that trimming is better than winsorizing (as Huber's method effectively does).  
As expected, with enough data,  the Bayesian methods and their classical counterparts perform similarly, although there
is a persistent slight edge in favor of the Bayesian restricted likelihood methods.  We attribute this advantage to the weakly informative
prior distribution which pulls the estimates slightly toward better values.  The similarity occurs as early as $n=100$.

\subsection{Hierarchical regression model}
\label{hierRegNW}
Nationwide agencies span many states and insurance regulations and the competitive environment varies between states. A natural extension to the previous analysis is a hierarchical regression model, grouping agencies within each state to reflect similar business environments. Using the same study design with the same training and validation splits, we re-analyze the data using the following hierarchical regression model:
\begin{align}
%\begin{split}
\label{eq:hierModel}
&\bbeta\sim N_p(\bmu_0, a\Sigma_0);\ \ 
\bbeta_j\iid N_p(\bbeta, b\Sigma_0); \ \  
\sigma_j^2\sim IG(a_0,b_0);  & \\ \nonumber
& \by_{ij}=\bx_{ij}^\top\bbeta_j+\epsilon_{ij},\ \ \epsilon_{ij}\iid N(0, \sigma_j^2),\ i=1,\dots, n_j,\ j=1,\dots, J &
%\end{split}
\end{align}
where $y_{ij}$  represents the $i^{th}$ observation in the $j^{th}$
state, $n_j$ is the total number of agencies in each state, and $J$ is
the number of states. $\bx_{ij}$ is a four dimensional vector
comprised of the same covariates as above. $\bbeta_j$ represents the
individual regression coefficient vector for state $j$.  We match this
model to the non-hierarchical model in several ways. First, $\bmu_0$,
$\Sigma_0$, $a_0$, and $b_0$ are fixed as before. We constrain $a+b=1$
in an attempt to partition the total variance between the individual
$\bbeta_j$'s and the overall $\bbeta$. We take $b\sim
\text{beta}(v_1,v_2)$. Using the previous data set, we assess the
variation between individual estimates of the $\beta_j$ to set $v_1$
and $v_2$ to allow for a reasonable amount of shrinkage. To allow for
dependence across the $\sigma_j^2$ we first take
$(z_1,\dots,z_J)\sim N_J(\mathbf{0}, \Sigma_\rho)$ with
$\Sigma_\rho=(1-\rho)I+\rho \mb{1}\mb{1}^{\top}$. Then we set
$\sigma^2_j=H^{-1}(\Phi(z_j))$ where $H$ is the cdf of an
$IG(a_0,b_0)$ and $\Phi$ is the cdf of a standard normal. This results in the specified marginal distribution, while
introducing correlation via $\rho$. We assume $\rho\sim
\text{beta}(a_\rho,b_\rho)$ with mean $\mu_\rho=a_\rho/(a_\rho+b_\rho)$ and precision
$\psi_\rho=a_\rho+b_\rho$. The parameters $\mu_\rho$ and
$\psi_{\rho}$  are given beta and gamma distributions, respectively. We fix the parameters of these distributions by again considering fits to individual states from the previous data set. More precise details on setting $v_{1}, v_{2}$ and the the priors on $\mu_{\rho}$ and $\psi_{\rho}$ are given in the appendix. We note that we tried a range of other fixed hyper-parameters resulting in negligible differences in the results.

Using the same techniques as in the previous section, 
we fit the normal theory hierarchical model above, a thick tailed $t$ version with $\nu = 3$ d.f., and two restricted likelihood versions (Huber's and Tukey's) of the model.  For the incomplete restricted methods, we condition on robust regression estimates fit separately within each state. We also fit classical robust regression counterparts and a least squares regression separately within each state.

We digress briefly to note that for the restricted likelihood methods no additional computational strategies outside of those discussed in Section~\ref{highDim} are needed to fit the hierarchical models described here. Since we condition on statistics which are computed within each state, the model's conditional independence between the states allows the data augmentation described earlier to be performed independently within each state.  Updates of hyperparameters follow conventional MCMC procedures.  We note that different types of statistics could be chosen for each state, if desired, allowing for a large amount of flexibility.

Selected results for the hierarchical fits appear in Figure
\ref{fig:hierType1Marg}. Hierarchical models naturally require more
data and so we consider only training sizes of $n=1000$ and
$2000$.  Again, the $t$-model is used as the base
method for computing TLM. Trimming fractions between $0.15$ and $0.3$ are displayed, as patterns for smaller trimming fractions are similar to those from the non-hierarchical fits. That is, without sufficient trimming, the Bayesian restricted likelihood fits' evaluation measure is poor. Again, the normal theory fits, both Bayesian and classical, perform poorly and are left out of the figures.  We see that the restricted likelihood with Tukey's estimator performs best in each case (assuming sufficient trimming). Huber's version also tops the thick tailed model for $n=2000$.  The Bayesian restricted likelihood fits considerably outperform their respective individual classical robust fits for training size of $n=1000$. This observation remains, though marginally so, for $n=2000$. The advantage of the hierarchical models seen here is due to the pooling of information across states, resulting in better predictive performance as compared to both the thick tailed competitor as well the respective classical fits.

%
%\begin{sidewaysfigure}[t]
%%\subcaptionbox{}{\includegraphics[width=2.75in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
%%\subcaptionbox{}{\includegraphics[width=2.75in,page=2]{hierlogMargType1AgenciesBaseModelt}}
%\subcaptionbox{}{\includegraphics[width=4in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
%\subcaptionbox{}{\includegraphics[width=4in,page=2]{hierlogMargType1AgenciesBaseModelt}}
%\caption{Model evaluation for `Type 1' agencies under the hierarchical model for $n=1000$ and $2000$. The $t$-model is used as the base method to compute TLM. Plotted are the mean TLM for each model against the trimming fraction across the $100$ cross-validation samples. Error bars correspond to one standard deviation of TLM above and below the mean. Models are labeled using the same notation as the previous figure. Only the relevant trimming fractions ($\alpha\geq .15$) are pictured.  
%}
%\label{fig:hierType1Marg}
%\end{sidewaysfigure}

\subsection{Comparison of hierarchical and non-hierarchical fits}

The performance of the methods for the hierarchical and non-hierarchical models can be contrasted through our cross validations studies.  We focus on Tukey's and Huber's conditioning statistic and concentrate our evaluation on the `Type 1' agencies. Table~\ref{tab:tlmTable} displays the mean TLM for each model and range of trimming fractions.  Our summary below focuses exclusively on realistic trimming fractions, $\alpha \geq 0.15$, and Tukey's conditioning statistic.

We first note that for the non-hierarchical model, there is little difference between mean TLM for $n=1000$ and $n=2000$, with 
the numbers differing only in the third decimal place (see rows 1 and 3 of the table).  This is due to the posterior predictive distributions having stabilized.  The
mean TLMs for the hierarchical model show a greater change with increases of about $0.05$ to $0.08$ as the training sample size changes
from $1000$ to $2000$ (see rows 2 and 4 of the table).  For calibration, the mean TLM for a normal with mean $0.5$ and variance $1$ is approximately this size
when trimming is done under a standard normal base model.  Thus, the increase in mean TLM is substantial.  
We attribute the change for the hierarchical model to the 
improvement in fits, particularly for states with fewer agencies.

Direct comparison of the hierarchical and non-hierarchical models shows that, for $n=1000$, the non-hierarchical model has uniformly 
(for $\alpha$ of interest) better mean TLM (rows 1 and 2).  The differences are substantial, and the summaries primarily reflect greater stability of fits on a state-by-state basis under the non-hierarchical model.  To a lesser extent, they reflect variation in the evaluation criterion which stems from modest validation sample size, particularly with larger trimming fractions.  The trimmed cases are not proportionally distributed across states.  The pattern changes for $n=2000$ (rows 3 and 4), with the hierarchical model showing larger mean TLMs for trimming fractions $0.15$ and $0.20$.  The improvement reflects the ability of the hierarchical model to capture differences in regressions across the states which is realized when the training sample size is large enough.  We attribute the better performance of the non-hierarchical model for the largest trimming fractions to variation in the evaluation.

\begin{table}[!tbp]
{\small
\begin{center}
\begin{tabular}{lllll}
\hline\hline
& \multicolumn{4}{c}{Trimming fraction ($\alpha$)}\\
\multicolumn{1}{l}{}&\multicolumn{1}{c}{$0.15$}&\multicolumn{1}{c}{$0.2$}&\multicolumn{1}{c}{$0.25$}&\multicolumn{1}{c}{$0.3$}\tabularnewline
\hline
{\mdseries Tukey ($n=1000$)}&&&&\tabularnewline
~~Non-Hier.&1.072 (0.014)&1.179 (0.022)&1.226 (0.029)&1.255 (0.033)\tabularnewline
~~Hier.&1.021 (0.063)&1.110 (0.070)&1.157 (0.067)&1.187 (0.065)\tabularnewline
\hline
{\mdseries Tukey ($n=2000$) }&&&&\tabularnewline
~~Non-Hier.&1.068 (0.029)&1.178 (0.007)&1.225 (0.011)&1.254 (0.014)\tabularnewline
~~Hier.&1.094 (0.041)&1.189 (0.036)&1.221 (0.033)&1.242 (0.028)\tabularnewline
\hline
{\mdseries Huber  ($n=1000$)}&&&&\tabularnewline
~~Non-Hier.&1.020 (0.020)&1.114 (0.035)&1.157 (0.041)&1.184 (0.045)\tabularnewline
~~Hier.&0.861 (0.073)&0.937 (0.079)&1.001 (0.074)&1.063 (0.064)\tabularnewline
\hline
{\mdseries Huber ($n=2000$)}&&&&\tabularnewline
~~Non-Hier.&1.015 (0.021)&1.112 (0.014)&1.154 (0.019)&1.181 (0.023)\tabularnewline
~~Hier.&0.930 (0.041)&1.014 (0.043)&1.080 (0.035)&1.148 (0.027)\tabularnewline
\hline
\end{tabular}
\end{center}
\caption{Mean (standard deviation) of TLM for `Type 1' agencies for the Bayesian restricted likelihood non-hierarchical and hierarchical models for $n=1000$ and $2000$.} \label{tab:tlmTable}
}
\end{table}

\section{Discussion}
\label{Conclusions}

%In this work, we have presented an approach which begins to reconcile Bayesian methods with the practice of data analysis.
Many routine choices in an analysis react to the gap between reality and the
statistical model, where a bit of set-up work improves inferential
performance.  Often, these choices can be recast in the framework of
restricted likelihood presented here, lending them more formality and facilitating
development of theoretical results.  But a much greater benefit of our
framework is that it leads us to blend classical estimation with
Bayesian methods.  Here, we use the likelihood from robust regression
estimators to move from prior distribution to posterior distribution.
Conditioning on the estimator, the update follows Bayes' Theorem
exactly.   Computation is driven by MCMC methods, requiring only a modest supplement to existing algorithms.  In another context, we might condition on the results of a set of estimating equations, designed to enforce lexical preferences for those features of the analysis considered most important, yet still producing inferences for secondary aspects of the problem. For example, the computational strategies we devised here allow us to apply the method to inference on quantiles of a regression model. In other settings, we envision conditioning on a mix of estimators and some of the observed data.

The framework we propose allows us to retain many benefits of Bayesian methods:  it requires a full and complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.

This same framework retains many of the benefits of classical estimation.  Great ingenuity has been used to create a wide variety of estimators in this tradition, many of which are designed to handle specific flaws in the model.  The estimators are typically accompanied by asymptotic results on consistency and distribution.  Many of these results carry over to our blend of classical and Bayesian methods, although regularity conditions differ.  We expect our procedures to have strong large sample performance, especially in settings where
pooling of information is of value.

This framework opens a number of questions, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.  Perhaps the biggest question is which summary statistic to choose.  For this, we recommend a choice based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.  \green{In our words, to provide desireable inference, we recommend use of robust and relevant summary statistics in conjunction with Bayesian models.}

\section{Appendix}
\label{sec:appendix}

\subsection{Details of Examples in Section \ref{examples}}
\subsubsection{Speed of Light}
The method is applied to estimate the speed of light using the classical data set of measurements taken by Simon Newcomb available in the {\tt R} package {\tt MASS}. Previous analyses appear in
\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}. With parameters $\bth=(\beta, \sigma)$, the full model is $\beta\sim N(23.6, 2.04^{2})$, $\sigma^{2}\sim IG(5, 10)$, $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$ where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light. $\beta$ is interpreted as the passage time of light with
$\sigma^{2}$ representing measurement error. Two outliers on the low end are a clear indication 
this model is misspecified.

The summary statistics considered for the restricted likelihood each provide an estimate of location and scale: two versions of simultaneous M-estimators (Huber's and Tukey's for location coupled with Huber's `proposal 2'  for scale \citep{Huber1964}), LMS (least median squares), and LTS (least trimmed squares) estimators. Tunning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality and for comparability, roughly $5\%$ of the residuals are trimmed for LTS. For comparison to a traditional Bayesian outlier approach a heavy-tailed model using Student's $t$ likelihood with $\nu=5$ degrees of freedom is also fit. %We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.  For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.   \citep[for details see][]{huber2009}

\subsection{Proofs}
\noindent

Proof of Theorem~\ref{Transformation}.  
\begin{proof} 
\begin{eqnarray}
 s(X,\by) & = & s\left(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)}\bz^* + X\left(\bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)}\bz^*)\right)\right) \\
& = & \frac{s(X,\by_{obs})}{s(X,\bz^*)} s(X, \bz^*)= s(X,\by_{obs}) , \qquad \mbox{and} \\
 \bb(X,\by) & = & \bb\left(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)}\bz^* + X\left(\bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)}\bz^*)\right)\right) \\
 & = & \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)}\bz^*) + \bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)}\bz^*) \\ &=& \bb(X,\by_{obs})
\end{eqnarray}
\end{proof}

\noindent
Proof of Lemma~\ref{gradSTheoremReg}.
\begin{proof}
We first show that $\nabla s(X,\by)\in \mc{C}^\perp(X)$. Recall that
$H=I-Q$. By the regression invariance property \ref{regIn} of $s$, we have
\label{perpGradReg}
\begin{equation}
\label{eq:lem3.2}
\begin{aligned}
s(X,\by)=s(X, Q\by+H\by)=s(X, Q\by).
\end{aligned}
\end{equation}
Thus, by the chain rule $\nabla s(X,\by)=Q\nabla s(X,Q\by)=Q\nabla s(X, \bz)$. Hence $X^\top \nabla s(X,\by)=0$ as desired.
From equation~\eqref{eq:lem3.2}, all vectors $\bz'\in \Pi(\mathcal{A})$ satisfy $s(X,\bz')=
s(X,\by)=s(X,\by_{obs})$, and so all directional derivatives of $s$ along each tangent $\bv$ to
  $\Pi(\mathcal{A})$ in $\mc C^\perp(X)$ at $\bz$ are equal to 0 (i.e., $\nabla s(X,\bz) \cdot \bv=0$).  Thus $\nabla s(X,\bz)$ is orthogonal to  $\Pi(\mathcal{A})$ at $\bz$.  
Since $\Pi(\mathcal{A})$ has dimension $n-p-1$, $\nabla s(X,\bz)$ gives the unique (up to scaling and reversing direction) normal in the $n-p$ dimensional $\mc C^\perp(X)$.  
\end{proof}

\noindent
Proof of Lemma~\ref{lem:basis}

\begin{proof}
Without loss of generality, assume the columns of $X$ form an
orthonormal basis for $\mc C (X)$ and likewise the columns of $W$ form
and orthonormal basis for $\mc C^\perp(X)$. With earlier notation,
$H=XX^{\top}$ and $Q=WW^{\top}$. The set $\mc A$ is defined by the
$p+1$ equations  $s(X,\by)=s(X,\by_{obs})$, 
$b_1(X,\by)=b_1(X,\by_{obs}),\dots,  b_p(X,\by)=b_p(X,\by_{obs})$. Consequently, the gradients are orthogonal to $\mc A$. Let  $\nabla\bb(X,\by)$ denote the $n\times p$ matrix with columns $\nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$. We seek to show the $n \times (p+1)$ matrix $[\nabla\boldsymbol\bb(X,\by),\nabla s(X,\by)]$ has rank $p+1$. Using property \ref{regEq}, we have that 
\[
\bb(X, \by)=\bb(X,Q\by+H\by)=\bb(X, Q\by)+X^\top \by
\] 
Then $\nabla \bb(X,\by)=Q\nabla\boldsymbol\bb(X, Q\by)+ X$ and 
\begin{eqnarray}
\label{BigMatrix}
[XX^\top, WW^\top]^\top[\nabla\boldsymbol\bb(X,\by),\nabla s(X,\by)]=
 \left( \begin{array}{cc}
X & \mathbf{0} \\
WW^\top\nabla b(X,\by)  &\nabla s(X,\by)  \\ \end{array} \right)
\end{eqnarray}
The last column comes from Lemma \ref{gradSTheoremReg}. The matrix $[XX^\top, WW^\top]^\top$ is of full
column rank (rank $n$), and so the rank of $[\nabla\boldsymbol\bb(X,\by),\nabla s(X,\by)]$ is the same as the rank
of the matrix on the right hand side of (\ref{BigMatrix}).  This last
matrix has rank $p+1$ since $\nabla s(X,\by) \ne \bzero$ by \ref{scaleEq2Reg}, and so does 
$[\nabla b(X,\by),\nabla s(X,\by)]$.
\end{proof}

\noindent
Proof of Lemma~\ref{lem:fullrank}

\begin{proof}
$P$ is the projection of the columns of $A$ onto $\mc
C^{\perp}(X)$. For this to result in a loss of rank, a subspace of
$\mc T_{y}(\mc A)$ must belong to $\mc C(X)$.  Following property
\ref{regEq}, for an arbitrary vector $X \bv \in \mc C(X)$, $\bb(X,\by
+ X \bv) = \bb(X,\by) + \bv$.  From the property, we can show that the directional derivative
  of $\bb$ along $X \bv$ with $\bv \ne \bzero$ is $\bv$, which is a
  nonzero vector. Hence $X\bv \notin \mc T_{y}(\mc A)$.  
\end{proof}

\noindent
Proof of Corollary~\ref{theorem:sings}

\begin{proof}
The corollary relies on a lemma and theorem from \cite{miao1992} which we restate 
slightly for brevity of presentation.  The principal angles between subspaces pluck off a
set of angles between subspaces, from smallest to largest.  The number of such angles 
is the minimum of the dimensions of the two subspaces.  Miao and Ben-Israel's first result
(their Lemma 1) connects these principal angles to a set of singular values, and hence to 
volumes.   
\begin{lemma}{(Miao, Ben-Israel)}
\label{MBI:lemma}
Let the columns of $Q_L\in \mathbb{R}^{n\times l}$ and $Q_M\in
\mathbb{R}^{n\times m}$ form orthonormal bases for linear subspaces
$L$ and $M$ respectively, with $l \leq m$. Let $\sigma_1\geq\cdots\geq
\sigma_l\geq0$ be the singular values of $Q_M^\top Q_L$. Then $\cos
\theta_i=\sigma_i, i=1,\dots,l$ where $0\leq\theta_1\leq\theta_2\leq
\cdots \leq\theta_l\leq\frac{\pi}{2}$ are the principal angles between $L$ and $M$.  
\end{lemma}

Miao and Ben-Israel's second result (their Theorem 3) makes a match between the principal
angles between a pair of subspaces and the principal angles between their orthogonal complements.  
\begin{theorem}{(Miao, Ben-Israel)}
\label{MBI:thm}
The nonzero principal angles between subspace $L$ and $M$ are equal to the 
nonzero principal angles between $L^\perp$ and $M^\perp$.
\end{theorem}

To establish the corollary, we appeal to Lemma~\ref{MBI:lemma} and Theorem~\ref{MBI:thm}.  Translating Miao and Ben Israel's
notation, we have $M=\mc C^\perp (X)$, $Q_M=W$, $L=\mc
T_{\boldsymbol{y}}(\mc{A})$, and $Q_L= A$. By Theorem~\ref{MBI:thm}, the
nonzero principal angles between $\mc{T}_{\boldsymbol{y}}(\mc{A})$ and
$\mc C^\perp(X)$ are the same as the nonzero principal angles between
$\mathcal{T}_{\boldsymbol{y}}^\perp(\mathcal{A})$ and $\mc C(X)$. By
\ref{MBI:lemma}, the non-unit singular values of $W^\top A$ are the
same as the non-unit singular values of $U^\top B$.  
\end{proof}

\subsection{Setting the hierarchical prior values}
In setting the priors we use the same previous data set used to set the priors for the non-hierarchical model (Section \ref{regModelNW}) and several heuristic arguments. While the analyses in Section \ref{hierRegNW} set the hyper-parameters using what is described here, the results were not sensitive to these choices.  This section describes the heuristics used in setting these prior parameters and is given for completeness. Using the previous data set we fit separate (robust) regressions to each state and a  regression to the \green{\sout{entire} entirety of the} data at once. Let the estimates for the fits to each state be $\hat{\beta_{1}}, \dots, \hat \beta_{J}, \hat \sigma_{1}, \dots, \hat \sigma_{J}$ and the estimates from the single regression be $\hat \beta$ and $\hat \sigma$. These are classical robust estimates using Tukey's regression and Huber's scale. Let $n_{j}$ denote the number of observations in the $j^{th}$ state and set $n=\sum n_{j}$.

First, consider $v_{1}$ and $v_{2}$ in the prior $b\sim\text{beta}(v_{1},v_{2})$.  In the hierarchical model \eqref{eq:hierModel}, $b=0$ implies all the $\bbeta_{j}'s$ are equal (no variation between states) and $b=1$ implies the $\bbeta_{j}'s$ vary about $\mu_{0}$ according to $\Sigma_{0}=n\cdot \mbox{var}(\hat\beta)$ (see Section \ref{regModelNW}). We seek a prior measure for what we think $b$ should be. In other words, how much prior uncertainty should we allow in $\bbeta$ as opposed to the uncertainty amongst the $\bbeta_{j}'s$? Using the prior fit, a measure for  uncertainty for $\bbeta$ is $\Sigma_{\hat\beta}=\mbox{var}(\hat\beta)$, the estimate of the covariance from the single regression. For the $\bbeta_{j}'s$, take $\delta_{j}=\hat\beta_{j}-\hat\beta$ and set the prior uncertainty to $\Sigma_{\delta}=n^{-1}\sum n_{j}\delta_{j}\delta_{j}^{\top}$. Consider the value $g= \left(|\Sigma_{\delta}|/|\Sigma_{\hat\beta}|\right)^{1/p}$. Heuristically, $g$ is measure of the amount of uncertainty between the $\bbeta_{j}'s$ to the amount of uncertainty in $\bbeta$. Now in the prior, we heuristically set the uncertainty in the $\bbeta_{j}'s$ ($b\Sigma_{0}$) to be approximately equal to $g\cdot\mbox{var}(\hat\beta)$. That is, $b\Sigma_{0}\approx g\cdot\mbox{var}(\hat\beta)= \frac{g}{n} \Sigma_{0}$, suggesting $b\approx  \frac{g}{n}$.  Hence we set $E[b]=\frac{g}{n}$. The precision, $v_{1}+v_{2}$, is set to be relatively high at $20$, completing the specification for the prior on $b$.

In setting the parameters for the beta prior on $\mu_{\rho}$ and gamma prior on  $\psi_\rho$ we first take $\hat z_{j}= \Phi^{-1} (H(\hat\sigma_{j}^{2}))$. As in the prior we assume $(\hat z_1,\dots,\hat z_J)\sim N_J(\mathbf{0}, \Sigma_\rho)$ with
$\Sigma_\rho=(1-\rho)I+\rho \mb{1}\mb{1}^{\top}$ and find the MLE, $\hat\rho_{mle}$, and observed inverse Fisher information, $I^{-1}(\rho_{mle})$. The mean of the beta prior on $\mu_{\rho}$ is set to $\hat\rho_{mle}$. Its variance is inflated somewhat and set to $2I^{-1}(\hat\rho_{mle})$. Since $\text{var}(\rho|\mu_{\rho}, \psi_{\rho})=\mu_{\rho} (1-\mu_{p})/(\psi_{\rho}+1)$ we replace $\mu_{\rho}$ with $\hat\rho_{mle}$, $\text{var}(\rho|\mu_{\rho}, \psi_{\rho})$ with $2I^{-1}(\hat\rho_{mle})$, and set the mean of the gamma prior on $\psi_{\rho}$ equal to $\hat\rho_{mle} (1-\hat\rho_{mle})/(2I^{-1}(\hat\rho_{mle}))-1$. Finally, we arbitrarily set the variance of the gamma prior to be approximately the same as the mean.
%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$

%
%Plugging the estimates of $z_j$ into the multivariate normal, the mean of $\mu_\rho$ is set to the MLE of $\rho$ and the variance is set to the observed inverse Fisher information matrix, inflated by a factor of $2$ to weaken the prior for this parameter.  We use the same MLE and inflated information matrix to set the mean for $\psi_{\rho}$. Its variance is chosen to cover a range of plausible values. A range of other values for the fixed hyper-parameters was also studied.  The differences in results were negligible.

\bibliographystyle{apalike}
\bibliography{refs}

\end{document}

### 2018-02-02 code/calls/calls.R

@@ -1,0 +1,103 @@
+# Analyze the Belgium Calls Data
+
+library(tidyverse)
+library(brlm)
+library(MASS)
+library(mvtnorm)
+library(coda)
+library(MCMCpack)
+
+log_scale  <- 1
+
+phones$year<- phones$year - mean(phones$year)
+phones <- bind_cols(phones)
+if(log_scale) phones$calls <- log(phones$calls)
+plot(phones$year, phones$calls)
+
+# mn_sd <- summarise_all(phones, funs(mean, sd))
+# phones <- as_tibble(scale(phones))
+
+
+# Restricted fit with Tukey locataion and MAD for scale-----
+
+n_prior <- 3
+(fit <- lm(calls ~ year, data = phones[1:n_prior,]))
+
+
+(lm_fit <- lm(calls ~ year, data = phones))
+# prior parameters -----
+g <- nrow(phones) - n_prior
+mu0 <- fit$coefficients
+X <- model.matrix(fit)
+Sigma0 <- g*sigma(fit)^2*solve(t(X)%*%X)
+a0 <- 2
+b0 <- 1 
+
+
+y <- phones$calls[-c(1:n_prior)]
+X_fit <- cbind(1, phones$year[-c(1:n_prior)])
+
+# Importance Sampling 
+# define statistic
+rlm_tukey <- function(y, X){
+  fit <- rlm(X, y, psi = psi.bisquare,  scale.est = 'MAD', maxit=1e4)
+  c(fit$coefficients, fit$s)
+}
+# importance distribution parameters 
+rlm_tukey(y, X_fit)
+
+rlm_fit <- rlm(calls ~ year, data = phones[-c(1:n_prior),], psi = psi.bisquare, scale.est = 'MAD')
+c(rlm_fit$coefficients, rlm_fit$s)
+plot(phones$year, phones$calls)
+lines(phones$year[-c(1:n_prior)], fitted(rlm_fit))
+
+
+i <- 2
+par(mfrow = c(2,1))
+smp1 <- rnorm(1000, mu0[i], sqrt(Sigma0[i,i]))
+smp2 <- rnorm(1000, rlm_fit$coefficients[i], sqrt(vcov(rlm_fit)[i,i]))
+hist(smp1, xlim = range(smp1, smp2))
+hist(smp2, xlim = range(smp1, smp2))
+par(mfrow = c(1,1))
+
+
+
[…]

### 2018-02-02 code/speed_of_light/summarize_speed_of_light.R

@@ -1,0 +1,166 @@
+# summarize the speed of light fits
+library(tidyverse)
+fig_path <- file.path('..', '..', 'figs')
+nu <- 5
+
+# read results ---- 
+fit_tukey <- readRDS('out/fit_tukey.rds')
+fit_huber <- readRDS('out/fit_huber.rds')
+fit_lms <- readRDS('out/fit_lms.rds')
+fit_lts <- readRDS('out/fit_lts.rds')
+fit_normal <- readRDS('out/fit_normal.rds')
+fit_t <- readRDS('out/fit_t.rds')
+
+
+extract_pdf <- function(fit, model){
+beta <- tibble(beta = fit$muPost[,1], posterior = fit$muPost[,2], Model = model)
+sigma2 <- tibble(sigma2 = fit$sigma2Post[,1], posterior = fit$sigma2Post[,2], Model = model)
+list(beta = beta, sigma2 = sigma2)
+}
+
+pdf_tukey <- extract_pdf(fit_tukey, 'Tukey')
+pdf_huber <- extract_pdf(fit_huber, 'Huber')
+pdf_lms <- extract_pdf(fit_lms, 'LMS')
+pdf_lts <- extract_pdf(fit_lts, 'LTS')
+
+compute_pdf <- function(samples, model){
+  pdf_beta <- density(samples[,1])
+  pdf_sigma2 <- density(samples[,2])
+  beta <- tibble(beta = pdf_beta$x, posterior = pdf_beta$y, Model = model)
+  sigma2 <- tibble(sigma2 = pdf_sigma2$x, posterior = pdf_sigma2$y, Model = model)
+  list(beta = beta, sigma2 = sigma2)
+}
+
+pdf_normal <- compute_pdf(fit_normal, 'Normal')
+pdf_t <- compute_pdf(fit_t, 't')
+
+
+model_order <- c('Normal', 't', 'Tukey', 'Huber', 'LMS', 'LTS')
+beta_pdfs <- bind_rows(pdf_normal$beta, pdf_t$beta, pdf_tukey$beta, pdf_huber$beta, pdf_lms$beta, pdf_lts$beta)
+beta_pdfs$Model <- factor(beta_pdfs$Model, levels = model_order)
+
+
+sigma2_pdfs <- bind_rows(pdf_normal$sigma2, pdf_t$sigma2, pdf_tukey$sigma2, pdf_huber$sigma2, pdf_lms$sigma2, pdf_lts$sigma2)
[…]

### 2018-02-02 paper.tex
edits to paper, looking to make some major formatting changes

@@
 \newcommand{\bx}{\mbox{\boldmath $x$}}
+\newcommand{\bX}{\mbox{\boldmath $X$}}
 \newcommand{\bu}{\mbox{\boldmath $u$}}
@@
 \label{examples}
-Before discussing computational details, the method is applied in a series of simple examples on well known datasets to demonstrate its effectiveness in situations where outliers are a major concern.
+Before discussing computational details, the method is applied to two simple examples on well known datasets to demonstrate its effectiveness in situations where outliers are a major concern.
 The full model in each case fits into the Bayesian linear regression framework discussed in \ref{}.
@@
 The full model is a standard location-scale Bayesian model assuming normally distributed errors.
-Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)   Tukey's M-estimator for location with Huber's 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
+Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)   Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
 Additionally, the common approach of assuming a t-distribution for the errors is also fit.
-The posteriors of $\beta$ under each model appear in \ref{fig:newcomb_beta}.
+The posteriors of $\beta$ under each model appear in Figure \ref{fig:newcomb_beta}.
 As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy tailed model provides robustness against them.
@@
 They also provide more precise predictions than the heavy-tailed model as illustrated by the predictive distributions displayed in \ref{fig:newcomb_predictive} which are also dependent on the posterior for the scale parameter.
+
 \begin{figure}
 \centering
-{\includegraphics[width=\textwidth]{figs/speed_of_light_beta.png}}
+\begin{subfigure}{.45\textwidth}
+{\includegraphics[width = 3.1in]{figs/speed_of_light_beta.png}}
+\caption{Posteriors of the location parameter $\beta$ under the normal theory model, the t-model, and four restricted likelihood models for Newcomb's speed of light measurements.}
 \label{fig:newcomb_beta}
-\caption{Posteriors of the location parameter $\beta$ under each model for Newcomb's speed-of-light measurements.}
+\end{subfigure}
+\begin{subfigure}{.45\textwidth}
+\centering
+{\includegraphics[width = 3.1in]{figs/speed_of_light_predictive.png}}
+\caption{Posterior predictive distribution of the speed of light under the normal theory model, the t-model, and four restricted likelihood models.}
+\label{fig:newcomb_predictive}
+\end{subfigure}
+\caption{}
 \end{figure}
+
+As a second example, the phones dataset measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
+The outliers in this case were due simply to a change in units on which calls were recorded for part of the dataset.
+The full model is a standard normal Bayesian linear regression with year as the only covariate and response the logarithm of the number of calls.
+The restricted likelihood method uses Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
+Likewise, the heavy-tailed t-distribution model is fit.
+The data along with  $95\%$ credible bands of the posterior predictive distribution under each model are displayed in Figure \ref{}.
+The normal theory model is only fit to the obvious non-outlying points.
+Since the t-model assumes the data are heavy-tailed, the posterior predictive distribution is much wider.
+Further, the outliers are not symmetric as assumed by this model, resulting in the posterior being pulled toward the outliers.
+On the other hand, the predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit that discards the outliers.
+Alternatively, a two component mixture distribution could also be used with one component for the `good' data and another for the outliers.
+The predictive distribution would then just use the component for the good data.
+This would work in this case, but involves explicitly modeling the outlier generating mechanism.
+In more more complex situations where the outlier generating mechanism is transient (i.e.
+ever changing and more complex than just a unit error in the recording), modeling the outliers becomes more difficult.
+Like classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
 
@@
 \centering
-{\includegraphics[width=\textwidth]{figs/speed_of_light_predictive.png}}
-\label{fig:newcomb_predictive}
-\caption{predit}
+{\includegraphics[width = 4in]{figs/calls_predictive.png}}
+\label{fig:calls_predictive}
+\caption{Predictive distribution of log(calls) under the Normal theory model fit to the non-outliers, the restricted likelihood model with  Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
+The first three data points were used to specify the prior with the remaining points used in the posterior fits.
+See details in the Appendix.
+}
 \end{figure}
-
-%\begin{sidewaysfigure}
-%\begin{subfigure}[b]{.5\linewidth}
-%\captionsetup{justification=centering}
-%\centering 
-%\caption{}\label{fig:newcombBeta}
-%\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}
-%\end{subfigure}
-%\quad
-%\begin{subfigure}[b]{.5\linewidth}
-%\captionsetup{justification=centering}
-%\centering
-%\caption{}\label{fig:newcombSig2}
-%\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}
-%\end{subfigure}
-%\quad
-%\begin{subfigure}[b]{.5\linewidth}
-%\captionsetup{justification=centering}
-%\centering
-%\caption{}\label{fig:newcombPred}
-%\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}
-%\end{subfigure}
-
-%\caption{Clockwise from top left: (a) marginal posteriors of $\beta$. (b) marginal posteriors for $\sigma^{2}$. (c) log predictive distributions.}
-%\label{fig:newcomb}
-%\end{sidewaysfigure}
-
-%\textcolor{blue}{if we add the Newcomb and Belgium Calls data examples, this might be a good place to add them because they are low dimensional.
-I think it would be a good lead into the high dimensional computational strategies}
 
@@
 We focus on the use of restricted likelihood for the Bayesian linear
-model with a standard formulation: 
-%\begin{eqnarray}
-%\label{LinearModel}
-%\bbeta & \sim & \pi_1(\bbeta); \qquad \sigma^2  \sim  \pi_2(\sigma^2)
-%\nonumber\\
-%y_i  & =  & x_i^\top \bbeta + \epsilon_i , \mbox{ for } i = 1, \ldots, n 
-%\end{eqnarray}
+model: 
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $x_i$ and $\bbeta \in \mathbb{R}^p$, \green{$\sigma^2 \in \mathbb{R}^+$}, 
+where $x_i$ and $\bbeta \in \mathbb{R}^p$, $\sigma^2 \in \mathbb{R}^+$, 
 and the $\epsilon_i$ are independent 
@@
 As summary statistics for the data, we concentrate on robust estimators for the 
-\green{regression} coefficients in the linear model and an associated 
+regression coefficients in the linear model and an associated 
 estimator of the scale.
-In particular, we demonstrate the method using simultaneous M-estimators defined by \eqref{Mest} for the one-sample setting and easily extended to the linear model in \eqref{LinearModel}.
-The estimator of the \green{regression} coefficients is denoted by $\bb(X, \by)\in \mathbb R^{p}$ and that of the scale by \green{\sout{$s(X, \by)\in \mathbb R$} $s(X, \by)\in \{0\} \cup {\mathbb R}^+$} .
+In particular, we demonstrate the method using simultaneous M-estimators \cite{} or add equations.
+The estimator of the regression coefficients is denoted by $\bb(X, \by)\in \mathbb R^{p}$ and that of the scale by $s(X, \by)\in \{0\} \cup {\mathbb R}^+$ .
 Thus, $T(\by)=(\bb(X, \by), s(X, \by))$.
@@
 
-As mentioned above, direct computational strategies designed to approximate the restricted posterior break down for high-dimensional statistics $T(\by)$ or high-dimensional parameters $\bth$.
-%, direct computational strategies break down.
-When the conditioning statistic is of high-dimension, density estimation becomes difficult and the associated approximate update in (\ref{RestrictedPosterior}) is unstable; when $\bth$is high dimensional, grid-based calculation and other numerical integration strategies fail.
-However, Markov chain Monte Carlo (MCMC) methods were developed for exactly these situations.  We turn to MCMC to 
-fit the model in these circumstances.
-
-%The general style of algorithm that we present relies on the decomposition of the sampling density in (\ref{FullLikelihood})
-%into one piece involving only $T(\by)$ and a second piece for the
-%complete data $\by$ given $T(\by)$. 
-%Relying on the modularity of MCMC algorithms, we construct a data augmented Gibbs sampler targeting $\pi(\bth, \by | T(\by)=T(\by_{obs}))$, the joint posterior of $\bth$ and $\by$ conditioned on the summary statistic $T(\by_{obs})$ for observed data vector $\by_{obs}$.
-The Gibbs sampler iteratively samples from the full conditionals written as $\pi(\bth|\by T(\by)=T(\by_{obs})$ and $f(\by|\bth, T(\by)=T(\by_{obs})$
-% \textcolor{blue}{some major changes from here to the end of the section}
-The general style of algorithm that we present is a data augmented
+Computational strategies to approximate the restricted posterior involving kernel density estimation and numerical integration are discussed in \cite{}.
+Such methods break down for high-dimensional statistics $T(\by)$ or high-dimensional parameters $\bth$.
+This section describes a Markov chain Monte Carlo (MCMC) algorithm which overcomes these limitations for a wide class of conditioning statistics  $T(\by)$.
+
+The general approach is a data augmented
 MCMC algorithm targeting $f(\bth, \by |
 T(\by)=T(\by_{obs}))$, the joint distribution of $\bth$ and the full
-data given the summary statistic $T(\by_{obs})$.  % with $\by_{obs}$  representing the observed complete data. 
- The Gibbs sampler \citep{gelfand1990} iteratively samples from the
- full conditionals $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ and
- $f(\by|\bth, T(\by)=T(\by_{obs}))$.  
-\green{Alternative algorithms substitute other generations for the full conditionals, such as the Metropolis-Hastings propose and accept/reject framework.
+data given the summary statistic $T(\by_{obs})$. 
+The Gibbs sampler \citep{gelfand1990} iteratively samples from the full conditionals $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ and $f(\by|\bth, T(\by)=T(\by_{obs}))$.
+Alternative algorithms substitute other generations for the full conditionals, such as the Metropolis-Hastings propose and accept/reject framework.
 Our algorithms are based on the decomposition of the MCMC algorithm into conventional full data sampling steps where $\bth$ is generated given $\by$, and steps that allow us to complete the data set where $\by$ is generated given $\bth$ and $T(\by)$.
 The latter generation relies on the conditioning set $\mathcal{A}=\{\by\in \mathbb{R}^n|T(\by)=T(\by_{obs})\}$.
-The set $\mathcal{A}$ may contain more than one element (i.e., it is not degenerate) when $T(\by) : \by \rightarrow T(\by)$ is not a $1-1$ function.}
-%\red{\sout{, where the two
-%     conditioning sets are not degenerate (that is, $\by$ is such that
-%     $T(\by)=T(\by_{obs})$).}}  \red{Unless $T(\by)=\by$, the set
-%   $\mathcal{A}=\{\by\in \mathbb{R}^n|T(\by)=T(\by_{obs})\}$
-%   is not degenerate, containing more elements than $\by_{obs}$ only.}
-
-When $\by$ has the summary statistic \sout{$T(\by)$ matching $T(\by_{obs})$,} \green{$T(\by) = T(\by_{obs})$,}
+The set $\mathcal{A}$ may contain more than one element (i.e., it is not degenerate) when $T(\by) : \by \rightarrow T(\by)$ is not a $1-1$ function.
+
+When $\by$ has the summary statistic matching $T(\by_{obs})$, $T(\by) = T(\by_{obs})$,
 the first full conditional, $\pi(\bth|\by, T(\by)=T(\by_{obs}))$, is
-\red{the same as} the full data posterior
+the same as the full data posterior
 $\pi(\bth|\by)$.
-\green{In this case, the condition $T(\by) = T(\by_{obs})$ is redundant.  This allows us to make use of conventional MCMC steps for this generation.  For} 
-\sout{In the case of} typical regression models, algorithms abound.  Details of the \green{recommended} algorithms depend on details of
-the prior distribution and sampling density.  As examples, a normal
-prior distribution and normal likelihood in the regression setting
-allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
-leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
-in the style of the 
-hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
-$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
-a scale parameter for each case and an extra stage where these scale parameters are generated.
-
-%The other stage in the Gibbs sampler is the generation of complete data from the full conditional  $f(\by|\bth, T(\by)=T(\by_{obs}))$.
-%Condition \ref{supReal} above facilitates the extension of convergence proofs for the complete data algorithm to those for the incomplete data algorithm.
-%In this subsection, we focus exclusively this stage. 
-%we begin with any conventional complete data algorithm.  In the case of typical regression models, these algorithms abound.  Details of the algorithm depend on details of
-%the prior distribution and sampling density.  As examples, a normal
-%prior distribution and normal likelihood in the regression setting
-%allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
-%leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
-%in the style of the 
-%hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
-%$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
-%a scale parameter for each case and an extra stage where these scale parameters are generated.  
-%The additional stage needed to implement the incomplete likelihood analysis via MCMC 
-%is a generation of the complete data given statistic ($T(\by_{obs})$) and parameter ($\bth$).
-Condition \ref{supReal} facilitates the extension of convergence proofs for the complete data algorithm to those for the incomplete data algorithm.
-%In this subsection, we focus exclusively on the additional stage
-%where we generate $\by | \bth, T(\by)$.  
-For a typical model and conditioning statistic, the second full conditional $f(\by|\bth, T(\by)=T(\by_{obs}))\blue{ =f(\by|\bth, \by\in\mc A)}$ is not available in closed form.  
+In this case, the condition $T(\by) = T(\by_{obs})$ is redundant.
+This allows us to make use of conventional MCMC steps for this generation.
+For typical regression models, algorithms for this step are readily available.
+%Recommended algorithms depend on details of the prior distribution and sampling density.
+As examples, a normal prior distribution and normal likelihood in the regression setting allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions in the style of the hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale  $g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of a scale parameter for each case and an extra stage where these scale parameters are generated.
+
+For a typical model and conditioning statistic, the second full conditional $f(\by|\bth, T(\by)=T(\by_{obs})) =f(\by|\bth, \by\in\mc A)$ is not available in closed form.
 As a consequence, we turn to Metropolis-Hastings \citep{hastings1970},
-using the strategy of proposing full data $\by$ \green{\sout{in the sample
-space of the distribution} for which $T(\by) = T(\by_{obs})$} and either accepting or rejecting the
+using the strategy of proposing full data $\by$ such that $T(\by) = T(\by_{obs})$ and either accepting or rejecting the
 proposal. Let $\by_p$ and  $\by_c$ represent the proposed and current
-full data, respectively.
-\green{In subsequent algorithms, we propose only from the set $\mathcal{A}$}.
-Denote the proposal distribution for $\by_{p}$ by $p(\by_p|\bth,T(\by_p) = T(\by_{obs})) \green{ = p(\by_p|\bth,\by_p \in \mathcal{A}) = p(\by_p | \bth)}$.
-\green{The last equality follows from the fact that our $p(\cdot | \bth)$ assigns probability one to the event $\{ \by_p \in \mathcal{A} \}$.
+full data, respectively, both belonging to the set $\mathcal{A}$.
+Denote the proposal distribution for $\by_{p}$ by $p(\by_p|\bth,T(\by_p) = T(\by_{obs}))  = p(\by_p|\bth,\by_p \in \mathcal{A}) = p(\by_p | \bth)$.
+The last equality follows from the fact that our $p(\cdot | \bth)$ assigns probability one to the event $\{ \by_p \in \mathcal{A} \}$.
 These equalities still hold if the dummy argument $\by_p$ is replaced with $\by_c$.
@@
 \end{eqnarray*}
-for $\by \in \mathcal{A}$.  This includes both $\by_p$ and $\by_c$.  
-}
+for $\by \in \mathcal{A}$.
 
@@
 %\textcolor{blue}{some major revisions as indicated in the responseToReferees}
-Our \green{computational} strategy is easiest to envision in a location-scale setting where 
+Our computational strategy is easiest to envision in a location-scale setting where 
 the design matrix in model (\ref{LinearModel}) consists of a single column of ones.  Robust estimation techniques along
@@
   distribution (examples of which are described later). This vector has summary statistic   
-$T(\bz^*) = (b(X,\bz^*), s(X,\bz^*))$ which may not match the observed summary
-$T(\by_{obs})$.  Second, $\bz^*$ is mapped into $\by =h(\bz^*)$
+$T(\bz^*) = (b(X,\bz^*), s(X,\bz^*))$.  Second, $\bz^*$ is mapped into $\by =h(\bz^*)$
 using Theorem \ref{Transformation} so that $T(\by)=T(\by_{obs})$. To
@@
 \subsubsection{Speed of Light}
-The method is applied to estimate the speed of light using the classical data set of measurements taken by Simon Newcomb available in the {\tt R} package {\tt MASS}. Previous analyses appear in
-\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}.
-With parameters $\bth=(\beta, \sigma)$, the full model is $\beta\sim N(23.6, 2.04^{2})$, $\sigma^{2}\sim IG(5, 10)$, $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$ where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light.
+With parameters $\beta$ and $\sigma$, the full model is $\beta\sim N(23.6, 2.04^{2})$, $\sigma^{2}\sim IG(5, 10)$, $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$ where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light.
 $\beta$ is interpreted as the passage time of light with
-$\sigma^{2}$ representing measurement error. Two outliers on the low end are a clear indication 
-this model is misspecified.
-
-The summary statistics considered for the restricted likelihood each provide an estimate of location and scale: two versions of simultaneous M-estimators (Huber's and Tukey's for location coupled with Huber's `proposal 2'  for scale \citep{Huber1964}), LMS (least median squares), and LTS (least trimmed squares) estimators.
-Tunning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
-For comparison to a traditional Bayesian outlier approach a heavy-tailed model using Student's $t$ likelihood with $\nu=5$ degrees of freedom is also fit.
+$\sigma^{2}$ representing measurement error.
+Tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$.
+The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models.
 %We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.
@@
 \citep[for details see][]{huber2009}
+
+\subsubsection{Belgium Calls}
+With $\bbeta = (\beta_{0}, \beta_{1})^{\top}$ and $\sigma$ the full model is $\bbeta\sim N(\boldmath{\mu}_{0}, \boldmath{\Sigma}_{0})$, $\sigma^{2} \sim IG(a, b)$, $\by \sim N(X\bbeta, \sigma^{2} I)$.
+Where $\mb y$ is the vector of the logarithm of the number of calls.
+Maximum likelihood estimators fit to the first three data points is used to set the prior parameters.
+In particular, $\Sigma_{0} = g\sigma_{0}^2 (X^{\top}X)^{-1}$ and $\mu_{0} = (1.87,  0.03)^{\top}$, $\sigma_{0} = 0.03$ the MLEs fit to the first three data points.
+The models are fit to the remaining 21 data points and the parameter $g$ is set to $21$ reflecting a unit information prior \cite{}.
+Finally $a = 2$ and $b =1$ for the normal theory and restricted likelihood models.
+For the t-model,  $\by \sim t_{\nu}(X\bbeta, \sigma^{2} I)$ with degrees of freedom set to $\nu = 5$ and the scale of the inverse gamma prior on the $\sigma^{2}$ adjusted to $\frac{\nu-2}{\nu}$ so the prior on the variance is the same as the other models.
 

### 2018-02-02 code/calls/calls_summarize.R

@@ -1,18 +1,23 @@
+# summarize calls data and make plots
 library(tidyverse)
 library(MASS)
-log_scale  <- 1
+fig_path <- file.path('..', '..', 'figs')
+log_scale  <- read_rds(path = file.path(here::here(), 'out', 'log_scale.rds'))
+n_prior  <- read_rds(path = file.path(here::here(), 'out', 'n_prior.rds'))
 phones
 #phones$year<- phones$year - mean(phones$year)
 phones <- bind_cols(phones)
 if(log_scale) phones$calls <- log(phones$calls)
-plot(phones$year, log(phones$calls))
+plot(phones$year, phones$calls, ylab = if_else(as.logical(log_scale), 'log calls', 'calls'))
 
 x <- phones$year- mean(phones$year)
 y <- phones$calls
-rl_fit <- read_rds(file.path(here::here(), 'rl_fit.rds'))
-t_fit <- read_rds(file.path(here::here(), 't_fit.rds'))
+rl_fit <- read_rds(file.path(here::here(), 'out', 'rl_fit.rds'))
+t_fit <- read_rds(file.path(here::here(), 'out', 't_fit.rds'))
 nu <- 5
-normal_fit <- read_rds(file.path(here::here(), 'normal_fit.rds'))
+normal_fit <- read_rds(file.path(here::here(), 'out', 'normal_fit.rds'))
+
+#plot(log(rl_fit$w + 1e-20), cex = .2)
 
 
 #functions needed posteriors ----
@@ -88,12 +93,13 @@ ppd_rl <- sapply(x_grid, function(x){
 ppd_rl <- as_tibble(as.data.frame(cbind(t(ppd_rl), x_grid)))
 
 ppd_rl_gather <- gather(ppd_rl, key = 'sample', value = 'value', -x_grid)
+length(unique(ppd_rl_gather$sample))
 
 rl_cred_bounds <- ppd_rl_gather %>% 
   group_by(x_grid) %>% 
-  summarize(lower = quantile(value, probs = .05), upper = quantile(value, probs = .95), model = 'rl')
+  summarize(lower = quantile(value, probs = .05), upper = quantile(value, probs = .95), Model = 'restricted likelihood')
 
-# t model -----
+# t Model -----
 ppd_t <- sapply(x_grid, function(x){
   rpd_t(t_fit,x, n = n_samps)
 })
[…]

### 2018-07-09 revision_1/responseToReferees.tex
gathering all revision in order to work on paper again

\documentclass[12pt]{article}
\usepackage{fullpage,amsmath}% mathtools}
\usepackage{setspace}
\usepackage{graphicx, psfrag, amsfonts}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{hhline}
%\usepackage{color}
\usepackage{caption, setspace}
%\usepackage{subcaption}

\def\bgam{\mbox{\boldmath $\gamma$}}
\def\bth{\mbox{\boldmath $\theta$}}
\def\bbeta{\mbox{\boldmath $\beta$}}
\def\blam{\mbox{\boldmath $\lambda$}}
\def\bmu{\mbox{\boldmath $\mu$}}

\newcommand{\bx}{\mbox{\boldmath $x$}}
\newcommand{\bu}{\mbox{\boldmath $u$}}
\newcommand{\bc}{\mbox{\boldmath $c$}}
\newcommand{\bs}{\mbox{\boldmath $s$}}
\newcommand{\by}{\mbox{\boldmath $y$}}
\newcommand{\bz}{\mbox{\boldmath $z$}}
\newcommand{\bv}{\mbox{\boldmath $v$}}
\newcommand{\bb}{\mbox{\boldmath $b$}}
\newcommand{\thstarj}{\mbox{$\bth^\star_j$}}
\newcommand{\bths}{\mbox{$\bth^\star$}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\uI}{\mathrm{I}}
\newcommand{\uP}{\mathrm{P}}
\newcommand{\up}{\mathrm{p}}
\newcommand{\mb}{\mathbf}
\newcommand{\mc}{\mathcal}

\newcommand{\Bern}{\mbox{Bern}}
\newcommand{\Nor}{\mbox{N}}
\newcommand{\Ga}{\mbox{Gamma}}
\newcommand{\Dir}{\mbox{Dir}}
\newcommand{\Ber}{\mbox{Ber}}
\newcommand{\Be}{\mbox{Be}}
\newcommand{\Unif}{\mbox{Unif}}
\newcommand{\Binom}{\mbox{Bin}}
\newcommand{\IG}{\mbox{IG}}

\newcommand{\Xs}{X^\star}
\newcommand{\Lc}{{\cal L}}

\usepackage[dvipsnames,usenames]{color}
\newcommand{\yy}{\color{magenta}\it}
\newcommand{\jj}{\color{Black}\rm}
\newcommand{\yjnote}[1]{\footnote{\color{Brown}\rm #1 \color{Black}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{\bf Definition}
\newtheorem{lemma}[theorem]{\bf Lemma}
\newtheorem{corollary}[theorem]{\bf Corollary}
\newtheorem{proposition}[theorem]{\bf Proposition}
\newtheorem{assumption}[theorem]{\bf Assumption}
\newtheorem{example}[theorem]{\bf Example}
\newtheorem{remark}[theorem]{\bf Remark}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\stackrel{indep}{\sim}}

\doublespacing
\setlength{\textwidth}{6 in}

\title{Response to Referees' Comments on ``Bayesian Restricted Likelihood Methods'' by John Lewis, Steven M. MacEachern, and Yoonkyung Lee.} 
\date{}
\begin{document}
\maketitle

%The authors thank the AE and the two referees for their thoughtful comments and suggestions. We start by addressing the concerns listed by the AE which are shared by the referees. We then address the remaining concerns discussed in the referees' reports not listed by the AE

The comments from the referees/AE are paraphrased in \textit{italics}

\section*{Comments from the AE}

\begin{enumerate}

\item \textit{The exposition of the material in the paper needs to be improved considerably and reading of the paper has to be made easier. One of the reviewers made very detailed suggestions how this could be achieved. Like this reviewer, I found the exposition of the MH algorithm on p. 12 particularly obscure, see also Comment 7 below.}

See response to all the major points from Referee 1 as well as to comment 7.

\item \textit{I agree that the term ``restricted'' is misleading. How about a term such as “Bayesian inference for data with incompletely specified likeilihood”, or something similar?}

See response to Referee 1 Minor point number 2.

\item \textit{I found the discussion how the suggested approach is related to ABC methods very vague and would appreciate more details.}

We can add more detail here. Including what ABC actually does and how it `looks' like our method but with different motivation \dots as well as it's use of an observed data dependent `statistic' which does not partition the sample space.

\item \textit{ There are several references to unpublished material such as Jung et al. (2014) which makes it hard to evaluate the value added by the corresponding material in the present paper.}

Jung et al. 2014, Lee J. and MacEachern 2014, and my thesis were unpublished when we wrote this. My thesis is openly available now on OhioLink. Should we add the website https://etd.ohiolink.edu/  to the citation? Also, are the other manuscripts available somewhere? I couldn't find them with a google search.

\item \textit{As for ABC methods, the suggested approach heavily relies on choosing appropriate statistics of the data. Since robustness to ``bad'' data is the major concern of the authors, they should pursue one reviewer’s advice go beyond M-estimators and consider high-break down estimators such as LMS and LTS. Also the choice of a suitable statistic for the scale is an important issue that should be discussed in more detail.}

Yes, robustness to ``bad'' is the major concern. Going beyond M-estimators is something I always thought of as a possible route to take next with this research.  It would involve a detailed study of conditions C1-C8 to see if such estimators satisfy these assumptions as the validity of the sampling strategy depends on them. Otherwise a potentially new sampling strategy would need to be developed.  Beyond this, my personal concern with pursuing this for this paper is that my code is only robust enough to handle the standard M-estimators (Huber's and Tukey's at this point). A great deal more work on the coding side would be needed to attempt other estimators even if they satisfy C1-C8.

As a seminal paper I don't think our goal is really to have a comprehensive study of different conditioning statistics. I think the main goal is to present the idea and give a few examples. In my mind, a comprehensive comparison of different conditioning statistics could be its own stand alone paper. Also, Huber himself has a little discussion in the newest version of his book arguing that researchers have spent far too much time trying to achieve high-breakdown estimators (e.g. a breakdown of $.5$) when in reality datasets will not have that much contamination. I think this gives some merit to our choice of statistics we present here.

A suitable scale statistic is definitely important. Again, I think a comprehensive study of this could be part of another stand alone paper. With all that said, I think we could at least add a discussion on the possibility of going beyond M-estimators as Reviewer 2 suggests.

\item \textit{ As noted by one referee, the gain in performance of the suggested approach for the two models discussed in the paper is not terribly convincing. Hence, I strongly encourage the authors to include an additional example that shows a significant edge of their method over classical ones, or at least to provide artificial data, where this is the case.}

These comments on the results not being terribly convincing are echoed by referee 2. There is definitely merit to these comments. 
It would be nice to have another example. Though not too terribly interesting, the analysis of Newcomb's data and the Belgium calls data I have in my dissertation are two potential examples that show substantial differences in posterior distributions between the heavy-tailed model and the restricted models. It doesn't address the comparison between the classical fits and the restricted fits though.

However, my take is this: For the standard regression model,  we expect the classical and Bayesian methods to perform similarly for large sample sizes. The priors should only make a difference for small sample sizes. Indeed, for n=25 the improvement is marginal as long as the trimming fraction is large enough. For smaller trimming fractions (less than .15) the differences are more substantial. This demonstrates some robustness to the trimming fraction. Also, for n=25, our methods are outperformed by the heavy-tailed model, but our method still performs well. Perhaps this is an area where another choice of statistic (or tuning parameters) could improve the fits.

For the hierarchical regression model, we see a substantial reduction in variance of the TLM for n=1000 which I think justifies the extra effort. For n=2000, The similar performance between the classical fits to each group separately and our method reflects the substantial differences between the groups. The hierarchical model is able to capture this as well and is a demonstration of the flexibility of modeling hierarchically --- even with our new method. This is a worthy observation and I think computational complexity is a secondary issue (at least from a philosophical point of view)

Steve: I know you had the idea to try a few applications. Did anything fruitful ever come out of that?

\item \textit{ One reason for this performance could be that, strictly speaking, the model is not only misspecified for the “bad” part of the data, but also for the “good” part of the data which are count data, rather than genuinely Gaussian. In particular, if these outcomes are small counts (there is not scale on Figure 3, so it is difficult to say), the square root transformation might not be enough to ensure normality of the outcomes in regression (14) and its generalization in Section 4.3. Apart from non-Gaussianity, also the assumption of homoscedasticity of the error term might be misspecified. I wonder, how robust the whole approach is to model misspecification also for the “good” part of the data, since the acceptance rate of the MH algorithm in (7) and (8) seems to be based on the (potentially misspecified) outcome regression.}

The observations we centered and scaled before taking square roots. The center and scaling was done to mask the data (the reason why there are no scales on the axes) but also helps to `normalize' the data after taking the square roots. The homoscedasticity assumption may not be justified for the simple regression model. This is not something I even considered and it is a noteworthy point. For the hierarchical model, a separate variance was assumed for each group. I am assuming this helps in terms of the assumptions, but again I did not do any diagnostics within a each group to check the assumption that a homoscedasticity held within each group.

With robust regression, observations with large residuals (large variances) are trimmed (either fully or partially). Hence assuming homoscedasticity when it is not valid could cause the method to trim `good' data. The estimate of the mean regression line, which is the major concern here, should not be effected much by assuming homoscedasticity. This is heuristic and deserves research.

\vspace{.1in}

\end{enumerate}

\newpage

\section*{Comments from Referee 1}

\begin{enumerate}

\item %Referee 1 Major Point 1: 
\textit{The Introduction and Sec. 2 are too long and detract from the focus of the paper}.

\vspace{.1in}

I am still wondering how to address this comment in ways other than trying to cut down some of the wording. I believe the introduction should address the following points (which are already in the paper):
\begin{enumerate}
\item The difficulty in eliciting a really good data model for certain situations 
\item The usual approaches using mixture/heavy-tailed models and their drawbacks. This will lead to pointing to the `restricted likelihood' as an alternative
\item A high level description of the new method.
\end{enumerate} 
With that said, it may be appropriate to move the discussion on model misspecification (2nd to last paragraph of intro) to the concluding section. I say this because the paper indeed focuses on handling outliers and stating that the method also addresses model misspecification at the end might be a nice `take-away' that isn't forgotten.

\vspace{.1in}

I believe Section 2 should address the following points (which are already in the paper):
\begin{enumerate}
\item Give the two data analysis examples (subset of known bad data and censored data) to introduce equation (3) and the fact that our method is often used informally in practical ways. 
\item Explicit form of $\pi(\bth|T(y))$ as well as $f(y_{n+1}|T(\by))$ should be given 
\item lit review on the previous uses of this method
\end{enumerate}

\vspace{.1in}

I am unsure what the referee means by `model-uncertainty outside the across-model prior setting.' However, I am familiar with some of the references given. Perhaps a discussion in the concluding section on the possible extensions to model averaging and it's relationship to the M-closed/complete/open concepts of Bernardo and Smith 2000 is in order\dots though I am not sure what this relationship is exactly at this point. I'd have to sit down with several of these papers to be see how they can be related to our situation.

\item % Referee 1 comment 2 
 \textit{The paper should be more self-contained}

I can definitely see how the disposition on page 12 is confusion. Before discussing the MH step for proposing data, I think it would help the casual reader to explicitly state that we are using a data-augmented algorithm sampling from $[\bth, \by|T(\by)]$ and using Gibbs sampling to iteratively sample from $[\bth|\by, T(\by)]=[\bth|\by]$ and $[\by|\bth, T(\by)]$. The second step, sampling from $[\by|\bth, T(\by)]$, is the difficult part and requires the MH algorithm.

Before the expression for $R$ (or perhaps after) I think something along the lines of the following may help:

The proposed data is sampled in such a way that $T(\by_{p})=T(\by_{c})=T(\by_{obs})$. Further, $f(\by_{p}|\bth, T(\by_{p})=T(\by_{obs}))=[T(\by_{p})=T(\by_{obs})|\bth, \by_{obs}]f(\by_{p}|\bth)\pi(\bth)/[\bth, T(\by_{p})=T(\by_{obs})]$. The first expression in brackets is one since $\by_{p}$ was sampled such that $T(\by_{p})=T(\by_{obs})$. Further, the expressions $\pi(\bth)$ and $[\bth, T(\by_{p})=T(\by_{obs})]$ are fixed in this step of the Gibbs sampler. Similar expansions can be made of the the proposal distribution. These fixed quantities cancel in the Metropolis-Hastings acceptance ratio, and consequently, the ratio reduces to (8).

After the above explanation, an additional line of algebra between (7) and (8) may not be necessary.  Also, the notation $p(\cdot)$ was confusing to referee 1. Perhaps a better notation is $p(\cdot|\bth, T(\cdot)=T(\by_{obs}))$.

The additional comments of the referee here indicate confusion (and perhaps this is our fault?). However, we did state clearly that $[\by|\bth, T(\by)]$ is NOT available in closed form. Perhaps adding explicitly that we are sampling from $[\by|\bth, T(\by)]$, as a suggested above, will alleviate this confusion.

Referee 1 also comments that too many details are left out of section 3.2.1:

I think what is missing here is an explicit statement that it is not trivial to directly sample a new data vector satisfying $T(\by_{obs})$.  This is the motivation for first proposing an intermediate data vector and then mapping it a vector satisfying the summary statistics. After the sentence ending in ``say, $(b(X, \by), s(X, \by))$'' I suggest adding something to clarify this \dots perhaps:

`It is not a simple matter to directly sample a data vector satisfying $T(\by_{obs})$. However, given any data vector $\by^{*}\in R^{n}$ and our assumptions, we will see in Theorem 3.1 below that it is possible to scale and shift $\by^{*}$ in a particular way resulting in a vector $\by$ satisfying $T(\by)=T(\by_{obs})$. Hence, to obtain such data $\by$, we proceed in two steps.'

From here we pick up with ``First a vector, $\bz^{*}$ is generated\dots'' However, we might change $\bz^{*}$ to $\by^{*}$ here and also leave out any detail about proposing from a reduced space until after Theorem 3.1. In particular\dots here is how I think the rest of this paragraph should read:

`First, a vector $\by^*$ is sampled from a known distribution (to be described later). This vector has summary statistic   
$T(\by^*) = (b(X,\by^*), s(X,\by^*))$ which (with probability one) will not match the observed summary $T(\by_{obs})$.  The vector $\by^*$ is mapped into a vector
$\by$ by rescaling and shifting appropriately using Theorem 3.1 below to match the observed conditioning statistic. To evaluate the proposal density, we need to adjust the known density of $\by^*$ with a Jacobian. We choose the distribution of the intermediate data vector $\by^*$ to have support so the transformation to $\by$ is one-to-one and the Jacobian can be computed using first principles. In the sequel, we use this artificially low-dimensional example to illustrate the method.'

The other option I think would be to change the $\by^{*}$ in theorem 3.1 to $\bz^{*}$. I know we have discussed this notional issue before \dots but I think we may be able to cut down a little on the number of `stars' we introduce.

Referee 1 one asks, `How does the expression in the Theorem lead to the set in $(9)$. After set (9) we should state that an examination of the proof of Theorem 3.1 in the appendix shows that any $\by$ expressed as in the Theorem will have $\bb(X, \by)=\bb(X, \by_{obs})$ and $ s(X, \by)=s(X, \by_{obs})$ (i.e. $T(\by)=T(\by_{obs}))$. Further any $\by$ in $\mc A$ can be expressed as in the theorem by simply replacing $\by^{*}$ with $\by$. This should make clear that the range of the transformation is indeed $\mc A$.

\item % Referee 1 comment 3 
\textit{The intuition should be better explicated}

Well\dots I am a little bummed after reading, `the authors have not yet found a good way to express their ideas so that they can be readily assimilated by some one who does not already understand' given the amount of time I have thought about this sampling process and how to explain the reasoning. However, maybe there should be a little more explanation as to why the Jacobian is what it is. For example, we say on page 17 that `This deformation contributes an attenuation to the Jacobian equal to the ratio of infinitesimal volumes in the tangent spaces of the sphere and $\Pi(\mc A)$ at $\bz$.' Maybe at the beginning of Section 3.2.2 we can state that from first principles Jacobians are simply ratios of infinitesimal volumes and that in the construction of the proposal we must  understand what these ratios are and efficiently compute them.

\item % Referee 1 comment 4 
\textit{The results of the application need better labeling/expostion}

\textit{It would be helpful if the authors could write out exactly and explicitly what cross-validation type of evaluation is being calculated. This is described at the bottom of p. 24, top of p. 25 in words, but the mathematical expressions should be given fully as well. This would clarify the role of the base method and the comment on p. 27, l. 3-4.}

Sure. We give the expression for TLM and we could also add more explicit notation for which observations are kept.

\textit{The same sort of comment applies to p. 27-28: Please give the mathematical expressions rather than just the words.}

This involves giving detailed expressions for how the priors were constructed. I didn't think this we was worth doing when writing the original draft but if the reviewers want it then I don't see why we couldn't do it. Perhaps adding this to the appendix would be better. It would involve some detail.

\textit{Maybe it’s just the way that my copy printed, but in Figs. 3, 4, and 5 the ranges/dots are hard to distinguish from each other so it’s hard to tell which is what. Could the different cases have different symbols that would be easier to tell apart? Even making the figures larger would help.}

Yes, the symbols are already different (but could be made more different) and the figures should be made larger.

\textit{To make it easier for the reader could the discussion of Table 1 p. 31 refer to the rows in the table? }

Yes. We can add this.

\textit{A related question: What does Fig. 1 show that is essential to the discussion?}

Figure 1 is notional and used in an attempt to explain the sampling process.

\item % Refee 1 comment 5 
\textit{Gather and organize your thoughts on model mis-specification in Sec. 5} Listed in order with my comments are:

\textit{For instance, the paragraph beginning In addition to... on p. 4}  Addressed as in comment 1 by moving the discussion of model misspecification to the discussion.

\textit{the first part of the paragraph beginning Further examples…\dots on p. 6} I am okay with moving this directly to the discussion.

\textit{middle paragraph on p.8, } I think this is an important part of the lit review is should probably remain where it is.

\textit{the discussion of instability in the first two paragraphs of Sec. 3.2,} These two paragraphs motivate the need for the sampling method. I don't think we can wait until the discussion for this. However, the sentence starting with 'A variety of variance techniques\dots' in the first paragraph is is vague and we may think about removing it.

\textit{We digress...on p. 28} This paragraph explains that no new computational strategies are needed for the hierarchical model. I think this is an important point to make since we describe our method for standard regression. It could potentially wait until the discussion.

\item %Referee 1 
Minor comments

\textit{1) p. 3, para. beginning The focus of this work...: State this more formally with mathematical notation.} Not sure how to do this?

\textit{2) p. 3, l. -2: The word restricted likelihood is OK, but if the authors could use some other word it would be better. The term restricted is already used in the sense of restricted MLE and that’s not the same as the authors mean here. This would help avoid possible confusion.}

This point is well taken and also addressed by the AE's comment number 2 who gives the suggestion ``Bayesian inference for data with incompletely specified likelihood.' I am certainly okay with giving a more descriptive name or perhaps going back to 'the blended paradigm.' I am not really sure what made me stick with the `restricted likelihood'\dots it just propagated through my dissertation and at some point just became too difficult to change with deadlines looming :).

\textit{3) p. 4, l. 11: Wong and Clarke CJS 2004 shows a case where using less but well chosen data gives better prediction.} We can mention this in the list review

\textit{4) p. 4, l. -8: The authors might want to have a look at Bernardo and Smith 2000 for their discussion on M-closed, -complete, -open problems. Maybe mention variance-bias decompositions for MSE?} Already addressed this a bit above

\textit{5) p. 4, l. -4,-5: Yes, mis-specification and outliers somehow represent the same problem...Could this point be made with more clarity?} More clarification may be warranted. The discussion of model misspecification may be moved to the Discussion as noted above.

\textit{6) p. 5, l. -4: term should be factor.} Okay. Can change here as well as if `term' it is used elsewhere in similar context

\textit{7) p. 6, l. 7: Alternatively should be Hence (for instance).} Okay.

\textit{8) Keep the ordering of conditioning variables the same e.g., (3) p. 6 uses
(y|T (y), ?) while p. 1, l. -2 uses (y|?, T (y)).} Yes, we should be careful about this.

\textit{9) p. 23, l. -1: ``tunning'' should be ``tuning''} Yes, yes it should.

\end{enumerate}

\newpage
\section*{Comments from Referee 2}

\begin{enumerate}
\item \textit{in the example chosen by the authors the gain in performance as
compared to classical methods is marginal at best, at the price of a presum-
ably much larger computational complexity. In the simple regression model
the restricted likelihood is outperformed by the heavy-tailed model for the
small sample size, whereas for larger sample sizes its performance is virtually
identical to the classical robust estimators. In the hierarchical model, it is
indeed slightly better than the classical estimators, but I wonder whether this
slight gain justifies the additional effort of finding reasonable priors for the
hyperparameters and the much more involved computation of the estimates.
If the priors are not chosen carefully, the results could even be worse than
the ones from the classical estimators. The authors should therefore provide
an additional example where the superiority of their approach shows more
clearly. It would also be useful to tell the reader whether the code used in the
example is already publicly available, and how it compares in terms of computational load with the classical M-estimators and also with other robust
estimators such as LMS (least median of squares) and LTS (least trimmed
squares).}

Comments in the second paragraph: These refer to the marginal gain in performance of our method and the suggestion to explore other conditioning statistics. These comments were addressed above in the AE's comments.

Code for implementing the method can be made available.

\item \textit{In addition to the usual concerns about the sensitivity
    of the results on the prior in the Bayesian context, the method as
    presented here raises the problem of choosing the type of the
    M-estimator, to which the example data seem to be quite
    sensitive. It is not difficult to understand why Tukey's
    redescending M-estimator performs better than the Huber-type
    M-estimator, but maybe not so easy why the difference is much more pronounced in the
hierarchical model as compared to the simple model. If the authors have an
explanation for this effect it should be given in the paper. For other data
sets, however, a good choice of the M-estimator could well be different, so
some guidelines would be welcome to the practitioner.
}

Comments in the third paragraph: The referee wonders if we have intuition as to why the difference between Tukey's and Huber's estimator is much more pronounced in the hierarchical model. I believe this is due to the fact that the conditioning statistics are estimated separately within each group, and some groups have small sample sizes and/or a large number of outliers. Huber's method doesn't completely trim outliers and can be more affected by them especially with small sample sizes. Thus, the conditioning statistic may not be as good in these groups.

As far as guidelines go, I don't think these would be much different from the guidelines users of classical robust estimators use, but it is something to think about.

\item \textit{The authors should also discuss in more detail whether
    it is possible to go beyond M-estimators and to use high
    breakdown-point estimators such as LMS and LTS as the conditioning
    statistic, and which scale estimators could or should be used as
    companions. As the LMS regression has no tunable parameters, and
    the LTS regression has only a single one, the user would be
    relieved from studying the sensitivity to the choice of the
    M-estimator from an infinite number of possibilities.}

Comments in the fourth paragraph: These comment was addressed in the AE section.

\item \textit{Finally, I have to remark that the first sentence of the
    Discussion is dangerously close to an insult to the numerous
    researchers and practitioners who have applied Bayesian methods in
    data analysis for years, even decades. The approach chosen by the
    authors is certainly innovative and in my opinion potentially
    fruitful, but it can hardly claim to begin to reconcile the two
    fields. I think it is fair to ask that the authors find a slightly
    more modest expression of their enthusiasm.}

Comments in the fifth paragraph: Yes, we could tone down this first sentence a bit.

\item \textit{It should contain an additional example that shows a significant
edge of their method over the classical ones. In this new example robust
estimators with high breakdown point (LMS and LTS) should be studied
along with suitable M-estimators. As is well known, the LMS-estimator
has worse asymptotic properties than M-estimators and LTS, and it will be
interesting to see whether this is visible in the results.}

Comments in the sixth paragraph: We should have an additional
  example even if it is simple, and it could potentially study other estimators.

\item Minor Comment: Figures will be made larger.

\end{enumerate}

\end{document}

### 2018-07-09 revision_1/code/calls/calls.Rmd
gathering all revision in order to work on paper again

--- 2018-02-02 code/calls/calls.Rmd
@@
 log_scale  <- 1
+write_rds(log_scale, path = file.path(here::here(), 'out', 'log_scale.rds'))
 ```
@@
 n_prior <- 3
+write_rds(n_prior, path = file.path(here::here(), 'out', 'n_prior.rds'))
 (fit <- lm(calls ~ year, data = phones[1:n_prior,]))
@@
 ## Restricted Likelihood Fit
-```{r rl fit tukey with MAD, cache = TRUE}
+```{r rl fit tukey with MAD setup, cache = TRUE}
 y <- phones$calls[-c(1:n_prior)]
@@
 
-i <- 2
-par(mfrow = c(2,1))
-smp1 <- rnorm(1000, mu0[i], sqrt(Sigma0[i,i]))
-smp2 <- rnorm(1000, rlm_fit$coefficients[i], sqrt(vcov(rlm_fit)[i,i]))
-hist(smp1, xlim = range(smp1, smp2))
-hist(smp2, xlim = range(smp1, smp2))
-par(mfrow = c(1,1))
-
 cov_b <- vcov(rlm_fit)
@@
 set.seed(125)
+```
+
+```{r rl fit  , cache = TRUE}
 rl_fit <- rl_importance(y, X_fit, statistic = rlm_tukey, mu0 = mu0, Sigma0 = Sigma0, alpha = a0, beta = b0, cov_b = cov_b, scale = scale, smooth = 1, N = N,Nins = Nins)
@@
 # check weights -----
-# plot(log(rl_fit$w + 1e-20), cex = .2)
-plot(rl_fit$w, cex = .2)
+plot(log(rl_fit$w + 1e-20), cex = .2)
+#plot(rl_fit$w, cex = .2)
 
-write_rds(rl_fit, path = file.path(here::here(), 'rl_fit.rds'))
+write_rds(rl_fit, path = file.path(here::here(), 'out', 'rl_fit.rds'))
 
@@
 
-write_rds(t_fit, path = file.path(here::here(), 't_fit.rds'))
-
+write_rds(t_fit, path = file.path(here::here(), 'out','t_fit.rds'))
+```
+## Normal Distribution Fit
+```{r Normal distribution fit, cache = TRUE}
 # fit normal model on subset of the data.
@@
 nburn <- 2e3
-normal_ind <- c(4:13,21:24)
+normal_ind <- c(4:14,22:24)
 y_normal <- phones$calls[normal_ind]
@@
 coda::traceplot(normal_fit$mcmc,smooth = TRUE)
-write_rds(normal_fit, path = file.path(here::here(), 'normal_fit.rds'))
+write_rds(normal_fit, path = file.path(here::here(),'out', 'normal_fit.rds'))
 ```

### 2018-07-09 revision_1/paper.tex
gathering all revision in order to work on paper again

--- 2018-02-02 paper.tex
@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 %\documentclass[ba]{imsart}
@@
 
+%  Points to handle in preparing the manuscript
+%
+%  1.  Out of sample evaluation of the model.  We should go with trimmed mean log-likelihood (trimming the cases
+%       that contribute least to log-likelihood).  Justification for the trimming mentioned in a sentence
+%       here, to be more carefully and completely done in separate work (with Yoonsuh).  
+%
+%  3.  Add quite a number of references to Section 2.  This is where we should catch the old work
+%      that conditions on the sample mean and proceeds through asymptotic approximation, Peter 
+%      Hoff's work on ranks, Holmes and Walker's work, and ABC.  New text needs to accompany the
+%      references, making clear what the other work does and how ours differs.  The new text should
+%      be quite brief.  
+%
+%  4.  A big question.  Should we try to add any asymptotic theory?  A Section 3.4?  See next comment.  
+%      My vote is "no".  
+%
+%  5.  Page limitations.  A goal for the entire manuscript is 30 pages.  Current length is 34+, spilling
+%      onto page 35.  But, additions will include the abstract (1/2 page or so), conclusions (1 page or 
+%      so), more references (another half page?), and more writing scattered throughout.  Redoing
+%      figures (two to drop) and tables will save a modest amount of space.   I propose that we 
+%      hold off on adding new content until we see how long the paper is.  Also, new content along
+%      the lines of point 4 would mean that we have to prove/use existing results to show the truth
+%      of whatever we claim!  
+%
+%  6.  Confirm with Nationwide that they are okay with our using their data and that they are comfortable
+%       with the descriptions we have in the paper.  
+%
+%  7.  Fit the hierarchical model, conditioning on the robust summaries at each leaf in the model.  
+%
+%  9.  A hedge on computations?  There are examples (pathological in some senses) for which a basic
+%      MCMC based on the complete data works, but where conditioning on a poorly chosen T(y) leads
+%      to a reducible Markov chain.  I don't think this happens when the support of y is the same for all
+%      \theta (it may be that mutual absolute continuity of all distributions for y|\theta is needed, though
+%      definitions of "support" vary somewhat).  I think we can ignore this here, but an example could go
+%      into the dissertation.  (one sentence now included to hint at this).
+
+%  To be added
+%
+%  1.  Abstract.  
+%
+%  2.  Conclusions.  To be written later.  I will take a pass at them once a few results are filled in for
+%       the data analysis.  
+%
+
+%  John.  
+%  See notes in red throughout.  The overarching goal is to move the manuscript toward completion.  
+%  To do so means filling in details to get them taken care of.  Big batches are (i) references, (ii) 
+%  deciding on notation for the estimator (b to replace beta?), (iii) verifying that the theorems have the
+%  right conditions, (iv) patching figures, (v) adding material for the examples, and (vi) deciding whether
+%  the figure and text on the last two pages is needed.  
+%  If you want to add comments for us, pick a color other than red and add them in that color.
+
+%  Yoon.  
+%  A check on the theorems would be great.  No need, I think, to dig out the paper by Miao and Ben Israel
+%  as that part of the math is fine (I'll check to make sure that all conditions for our use of the theorems have
+%  been stated in the Corollary).  Once more details are in place, proof reading and adjustment.
+
+%\newpage
 \title{Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression}
@@
 \begin{abstract}
-The \textit{restricted likelihood} is introduced as a method to address concerns about the miss-specification of the likelihood in Bayesian models.
-To apply, the data is summarized through a set of insufficient statistics,
-targeting inferential quantities of interest, and the prior is updated with only the summary statistics.
-By a careful choice of the summary, we retain the main benefits of Bayesian methods while reducing the
+Bayesian methods have proven themselves to be successful across a wide
+range of scientific problems and have many well-documented advantages
+over competing methods. However, these methods run into difficulties
+for two major and prevalent classes of problems: handling data sets
+with outliers and dealing with model misspecification. We outline the
+drawbacks of previous solutions to both of these problems (e.g., use of
+heavy-tailed likelihoods) and propose a new method as an
+alternative.  When working with the new method, we summarize
+the data through a set of insufficient statistics,
+targeting inferential quantities of interest, and update the prior
+distribution with the summary statistics rather than the complete
+data.  By careful choice of conditioning statistics, we
+retain the main benefits of Bayesian methods while reducing the
 sensitivity of the analysis to features of the data not captured by
-the conditioning statistics. Examples specifically address reducing sensitivity to outliers,
-where classical robust estimators (e.g., M-estimators) are natural choices
-for conditioning statistics. With these choices, the method can be thought of as a blend of classical robust estimation and Bayesian methods.
-
-A Markov chain Monte Carlo (MCMC) algorithm, applicable for the linear model and a wide range of choices for
-summary statistics, is developed to overcome implementation challenges.
-The method is demonstrated with several examples including simulations and messy insurance agency data with many outliers.
-Success is manifested in better predictive
-performance for data points of interest as compared to competing methods.
+the conditioning statistics. For reducing sensitivity to outliers,
+classical robust estimators (e.g., M-estimators) are natural choices
+for conditioning statistics. With these choicees, the method can be thought of as a
+blend of classical robust estimation and Bayesian methods.
+
+A major contribution of this work is the development of a data 
+augmented Markov chain Monte Carlo (MCMC) algorithm
+for the linear model and a wide range of choices for
+summary statistics. We demonstrate the method on an
+insurance agency data set containing many outliers and subject to model
+misspecification. Success is manifested in better predictive
+performance for data points of interest as compared to competing
+methods.
 
@@
 \section{Introduction}
-Bayesian methods are useful to a wide range of scientific problems, with their value
-having been demonstrated both empirically and theoretically. However, these methods run into difficulties
-for two major and prevalent classes of problems: handling data sets
-with outliers and dealing with model misspecification.
-From Bayesian perspective the model refers to the prior, the likelihood, as well as the loss function when formal inference is required.
-While optimality of Bayesian methods is unquestioned if one accepts the validity of all three of these elements, healthy skepticism encourages us to question each.
-Concern about the prior distribution has
-been addressed through objective Bayesian methods \citep{berger2006} prior elicitation methods \citep{garthwaite2005, ohagan2006}.
-Concern about the loss function is reflected in the extensive literature on Bayesian hypothesis tests \citep{kass1995}.
-Despite the common use of flat-tailed distributions \citep{berger1994} or nonparametric techniques \red{References?}, the sampling density has been given less attention from a specifically Bayesian view.
-The work on predictive diagnostics \citep{box1980} departs from classical
+Bayesian methods have provided successful solutions to a wide range of scientific problems, with their value
+having been demonstrated both empirically and theoretically.  
+In simple settings, the success of the methods is often attributed to formal optimality properties, sometimes derived
+through the laws of subjective probability 
+and sometimes through admissibility and the complete class
+theorems of decision theory.  In complex settings, the hierarchical model allows one to create 
+and fit sophisticated models that may, for example, pool information across similar problems.
+
+The development of Bayesian inference relies on a complete Bayesian model consisting of 
+three elements:  the prior distribution, the loss function, and the likelihood or sampling density.  While formal
+optimality of Bayesian methods is unquestioned if one accepts the validity of all three of these elements, 
+ a healthy skepticism encourages us to question each of them.  Concern about the prior distribution has
+been addressed through the development of techniques for subjective elicitation \citep{garthwaite2005, ohagan2006} \blue{(added the O'Hagan text here)} and
+the rise of objective Bayesian methods \citep{berger2006}.  
+Concern about the loss function is reflected in, for example, the
+extensive literature on Bayesian hypothesis tests \citep{kass1995}.  
+The sampling density has been given less attention from a specifically
+Bayesian view, although the work on predictive diagnostics \citep{box1980} departs from classical
 traditions.
 
+%The focus of this work is the intersection of Bayesian methodology and data analysis. In particular, we develop techniques to handle imperfections in the sampling density
 The focus of this work is the development of techniques to handle imperfections in the sampling density.  These imperfections often show
-themselves through the presence of outliers--cases not reflecting the phenomenon under
-study. There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling
+themselves through the presence of outliers--cases %--here taken to be 
+not reflecting the phenomenon under
+study. %--in the data set. 
+%A traditional solution to Bayesian outlier-handling involves replacing the original sampling density with a mixture or heavy-tailed density.
+A mixture model  includes one component for the ``good'' data and a second component for the ``bad'' data in an attempt to compartmentalize the outliers.
+The heavy-tailed approach simply attempts to discount the outliers directly.
+Another traditional approach fits a flexible (typically nonparametric) model to the data, producing a Bayesian version of a density estimate for both good and bad data.
+In recent development, inference is made through the use of robust inference functions \citep[][in press]{lee2013}.
+%\red{Q: Is the above sentence still about modifying the sampling density to
+%  handle outliers?}
+There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling
 density with a mixture model which includes one component for the ``good'' data and a second 
-component for the ``bad'' data.  The second approach replaces the
-basic sampling density with a thick-tailed density in an attempt to discount outliers.
-The third approach fits a flexible (typically nonparametric) model to the data, producing a Bayesian version of a density estimate for both good and bad data.
-In recent
-development, inference is made through the use of robust inference functions \citep[][in press]{lee2013}.
+component for the ``bad'' data.  With this approach, the prior distribution is updated with the likelihood
+from the mixture model to obtain the complete-data posterior distribution.  The good component of
+the sampling density is used for prediction of future good data.  The second approach replaces the
+basic sampling density with a thick-tailed density in an attempt to discount outliers, yielding techniques that 
+often provide solid estimates of the center of the distribution but 
+do not easily translate to predictive
+densities for further good data.  The third approach fits a flexible (typically nonparametric) model to 
+the data, producing a Bayesian version of a density estimate for both good and bad data.  In recent 
+development, inference 
+is made through the use of robust inference functions \citep[][in press]{lee2013}.
 
@@
 model for both good and bad data combined.  Instead of attempting to model both good and bad
-data, we propose a new strategy. In a nutshell, we begin with a complete model   
-as if all of the data are good. But rather than driving the move from prior distribution to posterior
-distribution by the entire likelihood, we use only the likelihood driven by a
-few summary statistics that target inferential quantities
-of interest.  We call this the \textit{restricted likelihood}. The update is a formal update from prior distribution to posterior distribution, based on the sampling density of the summary statistics.
-
-While the focus of this work is handling outliers, model miss-specification is more general.
-By focusing on robustly estimating quantities of interest and conditioning on these estimates, the restricted likelihood offers promiss in handling more general miss-specification issues in model building.
-The remainder of the paper.....develops Bayesian restricted likelihood (Section~\ref{restrictedlikelihood}), shows
+data, we propose a novel strategy for handling outliers. %:  the use of restricted likelihood.  
+In a nutshell, we begin with a complete model   
+as if all of the data are good.
+But rather than driving the move from prior distribution to posterior
+distribution by the entire likelihood, we use only the likelihood
+driven by a
+few summary statistics which typically target inferential quantities
+of interest.  We call this reduced likelihood a restricted % an incomplete
+likelihood. 
+%\red{[better to call a restricted likelihood? if we change, make sure to change consistently throughout the paper]} 
+%\green{[I agree with Yoon.  Better to call this a restricted likelihood.]}
+The 
+update is a formal update from prior distribution to posterior distribution, based on the sampling density
+of the summary statistics. 
+ %In our approach, the reader will identify a stream of reasoning which is manifested in classical M-estimation, generalized estimating equations, approximate Bayesian computation, and elsewhere.  
+The novelty of the work is twofold.  We make use of
+classical robust estimators as  summary statistics in a formal
+Bayesian framework, using the sampling density of the estimators as a replacement for the 
+sampling density of the data.  Second, we advance the argument that conditioning on an insufficient
+summary of the data is sound practice, rather than merely being done for computational and 
+modelling convenience.
+
+% \red{[Steve, just a reminder that a paragraph about model misspecification was here orginally but commented out by John following a referee's suggestion.
+I also agree with the referee in that model misspecification could be a much broader issue than having a fraction of bad data while the model for good data is correctly specified.]}
+%In addition to outlier-prone data, the 
+\green{ The sampling density can err due to other forms of model misspecification.  
+The traditional view is that, if the model is inadequate, one should build a better model.  In our
+empirical work, as data sets have become larger and more complex, we have bumped into 
+settings where we cannot realistically build the perfect model.  We ask the question ``by attempting
+to improve our model through elaboration, will the overall performance of the model suffer?''  If yes,
+we avoid the elaboration, retaining a model with some level of misspecification.  Acknowledging that
+the model is misspecified implies acknowledging that the sampling density is incorrect, as
+we do when outliers are present.  Thus, outliers are but one form of misspecified model.  
+We recommend a common solution for dealing with outliers and more general forms of model misspecification.}
+
+The remainder of the paper develops Bayesian restricted likelihood (Section~\ref{restrictedlikelihood}), shows
 how it can be applied to a Bayesian linear model (Section~\ref{BayesLinMod}), illustrates its use
@@
 
-\section{The Restricted Likelihood}
+\section{Restricted Likelihood}
 \label{restrictedlikelihood}
-
-This sections describes the restricted likelihood using a pair of simple examples and the relates the method to the current literature.
-For the examples assume $\by=(y_1,\ldots,y_n)$ is a random sample
+%\textcolor{blue}{Tried to make more concise. Commented out section describing the further examples related to randomized experiments, contingency tables, and meta-analysis. }
+
+\subsection{Examples}
+To describe the use of the restricted likelihood in a Bayesian framework, 
+we begin with a pair of simple examples
+for the one-sample problem. Several more examples are detailed in \cite{lewis2014}.  For those discussed here, the model takes the
+data $\by=(y_1,\ldots,y_n)$
+to be a random sample
 of size $n$ from a continuous distribution indexed by a parameter
-vector $\bth$, with pdf $f(y| \bth)$.  The full-data, likelihood is $L(\bth | \by) = \prod_{i=1}^n f(y_i | \bth)$.
-
-For the first example, consider that a known subset of the data is not informative about $\bth$.
-This case mimics the setting where outlying observations  are identified and discarded before formal analysis.
-Labeling the good cases $1$ through $n-k$ and the bad cases $n-k+1$ through $n$.  
-The relevant likelihood to be used to move from prior distribution to posterior distribution is 
+vector $\bth$, with pdf $f(y| \bth)$.  The standard, or full-data,
+likelihood would be $L(\bth | \by) = \prod_{i=1}^n f(y_i | \bth)$.
+
+As a first example, we consider the case where a subset of the data are known to be 
+bad in the sense of not informing us about $\bth$--and where the subset is known.  This case mimics the setting where outliers in
+a data set are identified and discarded before a formal analysis is done.  
+Without loss of generality, we label the good 
+cases $1$ through $n-k$ and the bad 
+cases $n-k+1$ through $n$.  
+The relevant likelihood to be used to move from prior distribution to posterior distribution is clearly 
 $L(\bth | y_1, \ldots, y_{n-k}) = \prod_{i=1}^{n-k} f(y_i | \bth)$.  
-Equivalently,  the full 
-likelihood is rewritten as 
+For an equivalent analysis, we rewrite the full %entire
+likelihood as the product of two pieces,
 \begin{eqnarray}
@@
 \end{eqnarray}
-The second piece, which is independent of $\theta$,  is dropped to provide better inference on $\bth$.
+% where the second factor may not actually involve $\bth$.
+We wish to keep the first piece and drop the second for better inference on $\bth$.
 
@@
 sometimes done as a precursor to the analysis of reaction time
-experiments  \citep[e.g.,][]{ratcliff1993} where very short and long reaction times are usually explained as anticipation and inattention, respectively, and do not reflect the process being studied.
-With lower and upper censoring times at $t_1$ and $t_2$, the post-censoring sampling distribution
+experiments  \citep[e.g.,][]{ratcliff1993}
+\green{where very small reaction times are physiologically too quick to be true reaction times
+are usually explained as anticipation, and where implausibly long reaction times are believed due to inattention. }  
+%\red{Q: provide a reason why this deliberate censoring is done?}
+With lower
+and upper censoring times at $t_1$ and $t_2$, the post-censoring sampling distribution
 is of mixed form, with masses $F(t_1|\bth)$ at $t_1$ and $1-F(t_2|\bth)$ at $t_2$,
-and density $f(y | \bth)$ for $y \in (t_1, t_2)$.  Adjusting $y_i$,
-with $c(y_i)$ where $c(y_i)= t_1$ if $y_i \leq t_1$, $c(y_i)=t_2$ 
+and density $f(y | \bth)$ for $y \in (t_1, t_2)$.  We adjust the original data $y_i$,
+producing $c(y_i)$ by defining $c(y_i)= t_1$ if $y_i \leq t_1$, $c(y_i)=t_2$ 
 if $y_i \geq t_2$, and $c(y_i)=y_i$ otherwise.  
@@
 $g(t_2 | \bth) = 1 - F(t_2|\bth)$, and $g(y|\bth)=f(y|\bth)$ for
-$y \in (t_1, t_2)$. The full likelihood as the product of two pieces, 
+$y \in (t_1, t_2)$.
+Hence, we may rewrite the full %complete %entire 
+likelihood as the product of
+two pieces, 
 \begin{eqnarray}
 \label{Censoring}
-L(\bth | \by) =  \left( \prod_{i=1}^n g(c(y_i)  | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth,c(y_i) ) \right) ,  
+%L(\bth | \by) =  \left( \prod_{i=1}^n g(x_i | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth, x_i) \right) ,
+L(\bth | \by) =  
+\left( \prod_{i=1}^n g(c(y_i)  | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth,c(y_i) ) \right) ,  
 \end{eqnarray}
-and only the first for the formal update.
-
-Further example abound with more given in \cite{lewis2014}. To generalize, we write the full likelihood in two pieces
+and retain only the first for the formal update.
+
+%Further examples abound. In a completely randomized experimental design, we randomize %our 
+%experimental units to treatment conditions and then ignore the details of the observed randomization \citep{dean1999}; 
+%in work with contingency tables,  
+%we collapse categories with small counts, coarsening the scale of %our 
+%data \citep{agresti2002}; in meta-analysis, we ignore the individual patient-level data and instead
+%work with estimated effects from the studies \citep{orourke2007}.  
+%Further examples are described in \cite{lewis2014}. 
+\subsection{Generalization}
+
+To generalize the approach in \eqref{OutlyingCases} and
+\eqref{Censoring}, %, and these other settings,
+we write the full likelihood in two pieces with a conditioning statistic $T(\by)$, as indicated below:
 \begin{eqnarray}
 \label{FullLikelihood}
-L(\bth | \by)  & = & f(T(\by) | \bth) \,\, f(\by |\bth, T(\by)) .  
+L(\bth | \by)  
+& = & f(T(\by) | \bth) \,\, f(\by |\bth, T(\by)) .  
 \end{eqnarray}
-where $T(\by)$ is any statistic.
+%Throughout the paper, we use the convention that a function is defined by its inputs. 
 Here,  $f(T(\by) | \bth)$ is the conditional pdf of $T(\by)$ given $\bth$ and $f(\by |\bth, T(\by))$ is the conditional pdf of $\by$ given $\bth$ and $T(\by)$.
-In \eqref{OutlyingCases}, the conditioning statistic is $T(\by) = (y_1, \ldots, y_{n-k})$ and in \eqref{Censoring}, the conditioning statistic is $T(\by) = (c(y_1),\ldots,c(y_n))$.
-We refer to
+In the dropped case example, the conditioning statistic is $T(\by) = (y_1, \ldots, y_{n-k})$.
+In
+the censoring example, the conditioning statistic is $T(\by) = (c(y_1),\ldots,c(y_n))$.  We refer to 
 $f(T(\by) | \bth)$ as the restricted likelihood and $L(\bth | \by)=f(\by|\bth)$ as the full likelihood.
 
-$T(\by)$ is a well-defined random variable with a probability distribution indexed by $\bth$ and the update from prior  to posterior can be made using $f(T(\by)|\bth)$ rather than $f(\by|\bth)$.
-This leads to the \textit{restricted likelihood posterior}
+Bayesian methods can make use of a restricted likelihood %in place of a complete likelihood
+since $T(\by)$ is a well-defined random variable with a probability distribution indexed by $\bth$.  
+The update from prior distribution to posterior distribution can be 
+made on the basis of $f(T(\by)|\bth)$ rather than $f(\by|\bth)$.  This leads to the restricted likelihood posterior 
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $\pi(\bth)$ is the prior distribution and $m(T(\by))$ is the marginal distribution of $T(\by)$ under prior. The associated predictive distribution for a single observation $\tilde y$ is
+where $m(T(\by))$ is the marginal distribution of $T(\by)$ under the prior distribution.  
+Predictive statements for further (good) data rely on the model.  For another observation,
+say $y_{n+1}$, we would have the predictive density 
 \begin{eqnarray}
 \label{RestrictedpredDist}
-f(\tilde y | T(\by)) = \int f(\tilde y | \bth) \pi(\bth | T(\by))\ d\bth .  
+f(y_{n+1} | T(\by)) = \int f(y_{n+1} | \bth) \pi(\bth | T(\by))\ d\bth .  
 \end{eqnarray}
 
+\subsection{Literature review}
 Direct use of restricted likelihood appears in many areas of the literature.  The motivation is often similar to ours:   
 concern about outliers or, more generally, model misspecification.
-The use of rank likelihoods is discussed by \cite{savage1969}, \cite{pettitt1983, pettitt1982}, and more recently by \cite{hoff2013}.
-\cite{lewis2012} make use of robust regression estimators for $T(\by)$.
-Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}.
-These asymptotic results asserts that under certain assumptions, posterior distribution resembles the asymptotic sampling distribution of the conditioning statistic.
-
-Restricted likelihoods have been used as practical approximations to a full likelihood.
+For example, the use of rank likelihoods is discussed by \cite{savage1969}, \cite{pettitt1983, pettitt1982}, and more recently by \cite{hoff2013}.
+\green{Lewis et al. (2012 xxxx) make use of robust regression estimators for $T(\by)$.}  
+Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}. The tenor of these asymptotic 
+results is that, for a variety of conditioning statistics with non-trivial regularity conditions on prior, model, and likelihood, the
+posterior distribution resembles the asymptotic sampling distribution of the conditioning statistic.
+
+%edited to include more detail on ABC:
+%\textcolor{blue}{Part on the use of incomplete likelihoods being used as approximations to complete likelihoods was commented out.
+However, I added more detail on ABC.
+Thought is that we could move this to the discussion.}
+%\red{This additional discussion on ABC
+%  (next two paragraphs) looks a bit too long.}
+Restricted likelihoods have also been used as practical approximations to a full likelihood.
 For example, \cite{pratt1965} appeals to heuristic arguments regarding approximate sufficiency to justify the use of the restricted likelihood of the sample mean and standard deviation.
-Approximate sufficiency is also used in Approximate Bayesian Computation (ABC), which is related to our method.
-ABC has recently experienced success in applications to epidemiology, genetics, and quality control \citep[see, for example,][]{tavare1997, pritchard1999,  marjoram2003, fearnhead2012}.
-Interest typically lies in the full data posterior and ABC is used for computational convenience.
+Approximate sufficiency is also appealed to in the use of Approximate Bayesian Computation (ABC), which is related to our method.
+ABC is a collection of posterior approximation methods which has recently experienced success in applications to epidemiology, genetics, and quality control \citep[see, for example,][]{tavare1997, pritchard1999,  marjoram2003, fearnhead2012}.
+Interest typically lies in the full data posterior and ABC is used for computational convenience as an approximation.
 Consequently, effort is made to choose an approximately sufficient $T(\by)$ and update to the ABC posterior by using the likelihood $L(\bth| \mathcal{B}(\by))$, where $\mathcal{B}(\by)=\{\by^{*}|\rho(T(\by),T(\by^{*}))<\epsilon\}$, $\rho$ is a metric, and $\epsilon$ is a tolerance level.
-This is the likelihood conditioned on the collection of data sets close to $\by$ as measured by the summary statistic.
-By choosing an approximately sufficient $T(\cdot)$ and a small enough $\epsilon$ the claim $L(\bth|\mathcal{B}(\by))\approx L(\bth|T(\by))\approx L(\bth|\by)$.
+This is the likelihood ``conditioned'' on the collection of data sets which result in a $T(\cdot)$ within $\epsilon$ of the observed $T(\by)$.
+%Hence, we can see that, as in our method, conditioning is done on a summary of the complete data.
+By choosing an approximately sufficient $T(\cdot)$ and a small enough $\epsilon$ the claim is made that $L(\bth|\mathcal{B}(\by))\approx L(\bth|T(\by))\approx L(\bth|\by)$.
 Consequently, the ABC posterior approximates the full data posterior.
-Efforts have been made to formalize what is meant by  approximate sufficiency \citep[e.g.,][]{joyce2008}.
-
-ABC is related to our method in that conditioning is on something other than the full data.
-For technical reasons, the calculation proceeding from $\pi(\bth)$ to $\pi(\bth | \mathcal{B}(\by))$ is not a formal conditional update.
+We note that efforts have been made to formalize what is meant by  approximate sufficiency \citep[e.g.,][]{joyce2008}.
+
+%ABC is related to our method in that conditioning is on something other than the complete data.
+Even if $T(\by)$ were exactly  sufficient in the traditional sense, a positive $\epsilon$ would result in something theoretically different from the complete data posterior (even if they are indeed approximately the same).
+We also mention that in ABC, $\mathcal{B}(\by)$ is not a statistic in the strict sense because it does not partition the sample space before observing data.
+That is, a feasible data set $\bz^{*}$ can belong to more than one `ball'  $\mathcal{B}(\cdot)$.
+The method relies on conditioning on this set because in most ABC applications, approximating the complete data posterior directly is hard (or impossible) and sampling data matching the observed summary exactly is also hard (or impossible).
+ABC methods are a practical and useful solution in these settings.
+For the regression models we present, sampling new data matching the observed summary exactly is indeed possible and so we can condition exactly on the observed summary.
+Further, we reiterate that our motivation is different from ABC in that we do not want to condition on the complete data because we assume it contains inherent flaws which can be detrimental to inference.
+
+\green{ABC is related to our method in that the ``conditioning'' is on something other than the data $\by$.
+However, the conditioning in ABC is heuristic.
+For technical reasons, the calculation proceeding from $\pi(\bth)$ to $\pi(\bth)L(\bth| \mathcal{B}(\by))/\int \pi(\bth)L(\bth| \mathcal{B}(\by)) d\bth$ is not a formal conditional update.
 Simply put, if an external observer told $\mathcal{B}(\by)$ can supply $T(\by)$ and vice-versa, the information contained in $\mathcal{B}(\by)$ is exactly that contained in $T(\by)$ and proper conditioning will lead to identical posterior distributions.
-This is not the case with a typical implementation of ABC.
+This is not the case with a typical implementation of ABC.}
 
@@
 
-This work extends the development of Bayesian restricted likelihood by arguing that deliberate choice of $T(\by)$ is sound practice and also by expanding the class of conditioning statistics in which exact conditioning can be achieved.
-Our methods do not rely on asymptotic properties, approximate conditioning, nor do they need to correspond to artificial censoring to create incomplete or missing data \citep[e.g.,][]{albert1988, hoffwakefield2013}.
-\green{Note - fix references here hoffwakefield for asymptotic; albert for ?
-.}
-
-\red{ MOVE THIS PIECE OR REMOVE ---
+This work extends the development of Bayesian restricted likelihood by arguing \green{that deliberate choice of $T(\by)$} is sound practice and also by expanding the class of conditioning statistics in which exact conditioning can be achieved.
+%well beyond ranks.
+Our methods do not rely on asymptotic properties, \green{nor do they rely on} approximate conditioning, \green{nor do they need to correspond to artificial censoring to create incomplete or missing data}  \citep[e.g.,][]{albert1988, hoffwakefield2013}.
+\green{Note - fix references here hoffwakefield for asymptotic; albert for ? .}
+
 The key to productive use of the restricted likelihood is the choice of $T(\by)$ and the development
@@
 %The next section develops the necessary computational strategies.
-}
-
-\section{Examples}
-\label{examples}
-Before discussing computational details, the method is applied in a series of simple examples on well known datasets to demonstrate its effectiveness in situations where outliers are a major concern.
-The full model in each case fits into the Bayesian linear regression framework discussed in \ref{}.
-Specific details are left to the Appendix.
-
-The first example is an analysis of Simon Necomb's 66 measurements of the speed of light; two of which are significant outliers in the lower tail.
-The full model is a standard location-scale Bayesian model assuming normally distributed errors.
-Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)   Tukey's M-estimator for location with Huber's 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
-Additionally, the common approach of assuming a t-distribution for the errors is also fit.
-The posteriors of $\beta$ under each model appear in \ref{fig:newcomb_beta}.
-As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy tailed model provides robustness against them.
-The restricted likelihood methods using the M-estimators and LTS statistics also achieve robustness against the outliers.
-Conditioning on LMS however, results in a posterior similar to the one under the normal model.
-The M-estimators provide the tightest posteriors in this case.
-They also provide more precise predictions than the heavy-tailed model as illustrated by the predictive distributions displayed in \ref{fig:newcomb_predictive} which are also dependent on the posterior for the scale parameter.
-\begin{figure}
+
+\subsection{A first data analysis example} %\textcolor{blue}{ADDED}
+\label{darwinAnalysis}
+Before discussing computational details of finding restricted 
+posteriors, we begin by analyzing a simple example involving
+outliers. The data consists of well known measurements of the \green{passage time} of
+light taken by Simon Newcomb in the late nineteenth century and
+contain two clear outliers on the low end. Details and data are
+available in the R package {\tt MASS} and previous analyses appear in
+\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}. Letting
+$y_{i}$ denote the $i^{th}$ coded measurement of the passage time of light, we
+assume $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$. The
+parameter $\beta$ can be interpreted as the passage time of light with
+$\sigma^{2}$ representing measurement error. The outliers \green{are a clear indication} %make clear
+that this normal model is misspecified.  \green{Also,} %Another reason for model misspecification is that 
+the measurements are coarse, taking on only
+integer values.  For a Bayesian analysis, we must specify prior
+distributions on the parameters $\bth=(\beta, \sigma)$. For this we
+assume an independent normal -- inverse gamma model. That is,
+$\beta\sim N(\eta, \tau^{2})$ and $\sigma^{2}\sim IG(a, b)$. The
+hyperparameters  are fixed for simplicity and taken to be $\eta=23.6$,
+$\tau=2.04$, $a=5$,  and $b=10$. We note that our computational
+strategy described in Section \ref{highDim} makes it feasible to fit
+more complex model structures. The Bayesian model presented here is a
+special case of the linear model in \eqref{LinearModel} presented below.
+
+As summary statistics for the restricted likelihood methods, we
+consider robust simultaneous M-estimators of location and scale as
+well as LMS (least median squares) and LTS (least trimmed squares) estimators.
+The simultaneous M-estimators $b(\by)$ and $s(\by)$ of $\beta$ and $\sigma$, respectively, are the solutions to the equations
+\begin{eqnarray}
+\label{Mest}
+ \sum_{i=1}^n \psi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 \\
+ \sum_{i=1}^n \chi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 . \nonumber 
+\end{eqnarray} 
+For the first equation we consider two $\psi$ functions: Huber's and Tukey's.
+These are both coupled with Huber's `proposal 2'  for the $\chi$ function in the second equation \citep[for details see][]{huber2009}.
+Tuning parameters for these functions are set to achieve $95\%$ efficiency under normally distributed data.
+
+LMS minimizes the median squared residual and LTS minimizes the sum of the $k$ smallest squared residuals where $k$ is chosen by the user.
+These estimators are considered because, unlike the M-estimators above, they can achieve high breakdown.
+%These estimators are easily implemented by the {\tt rlm} function of the {\tt MASS} package in R. 
+It is well known that LMS has highest possible breakdown but is inefficient.
+LTS is more efficient and its breakdown properties are determined by $k$, with highest possible breakdown occurring for $\left \lfloor{\frac{n+1}{2}}\right \rfloor\leq k\leq\left \lfloor{\frac{n+2}{2}}\right \rfloor$.
+%For the current data set $n=66$ and we take $k=34$ to achieve highest possible breakdown.
+For the current analysis we do not choose $k$ to achieve highest possible breakdown. Instead, with $n=66$ and we choose $k=62$ (roughly $95\%$ of $n$) to be \green{more} %somewhat
+comparable to the tuning parameters chosen for the M-estimators.
+The LMS and LTS \green{estimators} are also coupled with an estimator of scale for the conditioning.
+We set the scale estimator to the minimum of the corresponding objective function, appropriately scaled for consistency.
+%we use the scale estimator corresponding to the respective objective function.
+These are the median squared residual for LMS and sum of the smallest squared residuals for LTS multiplied by an appropriate correction factor chosen for consistency.
+%Computation of these estimators are also implemented in the {\tt MASS} package by the function {\tt lqs}.
+
+For comparison to a traditional Bayesian outlier approach we also fit a heavy-tailed model by changing the data distribution from a normal to a Student's $t$ with $\nu=5$ degrees of freedom.
+We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.
+For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.
+
+The marginal posteriors for $\beta$ and $\sigma^{2}$ as well as the
+predictive distribution \eqref{RestrictedpredDist} under each model
+are displayed in Figures
+\ref{fig:newcombBeta}-\ref{fig:newcombPred}. Both of the two small
+outliers and the normal prior on $\beta$ centered at $23.6$ are
+influential in the results. The normal theory model is most
+drastically affected with the posterior of $\beta$ being pulled
+towards the prior and outliers. Inference on $\sigma^{2}$ under this
+model is impacted by the outliers (see Figure
+\ref{fig:newcombSig2}) \green{resulting in overestimation of $\sigma^{2}$}. 
+The heavy-tailed model as well as the
+restricted likelihood methods with LTS, Huber's, and Tukey's summary
+statistics are less influenced by the outliers and priors. The
+marginal posteriors for $\beta$ are closer to the center of the
+non-outlying data. Inference on the variance parameter also more
+closely reflects the variance information in this part of the data
+(the mean and variance of the data without the two outliers are $27.8$
+and $25.8$, respectively). The posterior of $\beta$ under LTS is
+slightly more dispersed than under the two M-estimator methods. This is
+also reflected in the variance parameter in that under LTS the posterior distribution \green{concentrates on 
+slightly larger values of $\sigma^2$} % is slightly higher. 
+While LMS has high breakdown, it has been more drastically affected by the normal prior centered at $23.6$ than the others. This is % likely 
+because LMS achieves high breakdown by discounting much of the information in the data.
+
+Though inference for the main parameter of interest ($\beta$) is
+similar between the traditional heavy-tailed approach and the new
+method with LTS, Huber's, and Tukey's summary statistics,  the
+traditional heavy-tailed method has the disadvantage of less precise
+predictive capability. This is reflected in the heavier tails of its
+predictive distribution  \eqref{RestrictedpredDist} seen in Figure
+\ref{fig:newcombPred} (plotted are the log predictive \green{densities} %distributions
+under each method). The predictive distributions under each of the
+restricted likelihood methods are comparable. Surprisingly, despite the poor
+inference on $\beta$ under LMS, the predictive distribution is
+\green{concentrated more sharply} than \green{under} the other restricted likelihood methods. This is
+related to its posterior of $\sigma^{2}$ seen in
+Figure \ref{fig:newcombSig2}  which is the tightest
+distribution and shifted the most to the left. 
+% However, this is likely a consequence of the scale estimator chosen for the conditioning.
+Recall it involves a correction factor which is chosen asymptotically.
+Even for $n=66$, this correction factor can contribute to underestimation (\textcolor{blue}{REFERENCE: I know I read something like this somewhere}).
+\red{[I don't know what exactly this correction factor is.
+Is it similar to the bending constant for $\psi$?]}
+
+%\red{[I suggest to omit the following paragraphs given that the second last paragraph in the previous section (``the key to the productive ...'') has similar discussions already.]} This simple example raises many questions regarding the proposed method.
+The first of which is how to choose the summary statistic.
+In principle, we may choose any summary and it doesn't have to be an estimator of location and scale.
+However, for outlier problems this choice seems logical and we use it for this paper.
+Further, estimator specific tuning parameters clearly effect the results.
+For example, we also looked at LTS with $k=34$ to achieve high breakdown.
+This resulted in a posterior for $\beta$ which closely resembled that of LMS.
+
+%Other questions may be posed by the reader and addressing each of these is beyond the scope of this paper.
+Instead we focus on introducing the method and deriving a computational strategy that will allow such models to be fit to higher dimensional problems with a large class of summary statistics.
+It is our hope that this computational strategy will facilitate the study of further questions regarding the method.
+
+\begin{sidewaysfigure}
 \centering
-{\includegraphics[width=\textwidth]{figs/speed_of_light_beta.png}}
-\label{fig:newcomb_beta}
-\caption{Posteriors of the location parameter $\beta$ under each model for Newcomb's speed-of-light measurements.}
-\end{figure}
-
-\begin{figure}
-\centering
-{\includegraphics[width=\textwidth]{figs/speed_of_light_predictive.png}}
-\label{fig:newcomb_predictive}
-\caption{predit}
-\end{figure}
+\captionsetup{justification=centering}
+\subcaptionbox{\label{fig:newcombBeta}}{\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}}\quad
+\subcaptionbox{\label{fig:newcombSig2}}{\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}}\quad
+\subcaptionbox{\label{fig:newcombPred}}{\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}}
+\caption{Clockwise from top left: (a) marginal posteriors of $\beta$ (b) marginal posteriors for $\sigma^{2}$ (c) log predictive distributions.}
+\label{fig:newcomb}
+\end{sidewaysfigure}
 
@@
 
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=4in]{minSS3dSampleSpace.jpg}
-%\caption{A depiction of $\mathcal{A}$, $\Pi(\mathcal{A})$, and the
-%  unit circle for the illustrative example where $b_{1}(\mathbf{1},\by)=\min(\by)=0$ and
-%  $s(\mathbf{1},\by)=\sum (y_i -b_{1}(\mathbf{1},\by))^2 =1$.
-%$\mathcal{A}$ is the combination of three quarter circles, one
-%  on each plane defined by $y_i=0$. The projection of this manifold
-%  onto the deviation space is depicted by the bowed triangular shape
-%  in the plane defined by $\sum y_i=0$. The circle in this plane
-%  represents the sample space for the intermediate sample \green{$\bz^*$}. Also
-%  depicted is the vector $\mathbf{1}$, the design matrix for the
-%  location and scale setting.}
-%\label{fig:sampSpace}
-%\end{figure}
+\begin{figure}[t]
+\centering
+\includegraphics[width=4in]{minSS3dSampleSpace.jpg}
+\caption{A depiction of $\mathcal{A}$, $\Pi(\mathcal{A})$, and the
+  unit circle for the illustrative example where $b_{1}(\mathbf{1},\by)=\min(\by)=0$ and
+  $s(\mathbf{1},\by)=\sum (y_i -b_{1}(\mathbf{1},\by))^2 =1$.
+$\mathcal{A}$ is the combination of three quarter circles, one
+  on each plane defined by $y_i=0$. The projection of this manifold
+  onto the deviation space is depicted by the bowed triangular shape
+  in the plane defined by $\sum y_i=0$. The circle in this plane
+  represents the sample space for the intermediate sample \green{$\bz^*$}. Also
+  depicted is the vector $\mathbf{1}$, the design matrix for the
+  location and scale setting.}
+\label{fig:sampSpace}
+\end{figure}
 
@@
 
-%\begin{sidewaysfigure}[t]
-%\centering
-%\captionsetup{justification=centering}
-%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace3.pdf}}\quad
-%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
-%\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
-%  to $\bz$. The adjustment for the stretch transforms the density
-%  along the unit circle to the density along the circle of radius
-%  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
-%  deformation from the distribution along the circle to the
-%  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
-%  be the cosine of the angle between the normals to each manifold.}
-%\label{fig:stretchDeform}
-%\end{sidewaysfigure}
+\begin{sidewaysfigure}[t]
+\centering
+\captionsetup{justification=centering}
+\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace3.pdf}}\quad
+\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
+\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
+  to $\bz$. The adjustment for the stretch transforms the density
+  along the unit circle to the density along the circle of radius
+  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
+  deformation from the distribution along the circle to the
+  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
+  be the cosine of the angle between the normals to each manifold.}
+\label{fig:stretchDeform}
+\end{sidewaysfigure}
 
@@
 
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=4in]{countvcount.pdf}
-%\caption{The square root of count in 2012 versus that in 2010 (after centering and scaling).
+\begin{figure}[t]
+\centering
+\includegraphics[width=4in]{countvcount.pdf}
+\caption{The square root of count in 2012 versus that in 2010 (after centering and scaling).
 The colors represent the varying contractual agreements as they stood in 2010.
@@
 Scalings on the axes are purposely left off for proprietary reasons.}
-%\label{fig:ctVct}
-%\end{figure}
+\label{fig:ctVct}
+\end{figure}
 
@@
 
-%\begin{sidewaysfigure}
-%\centering
-%\captionsetup{justification=centering}
-%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=1]{logMargType1AgenciesBaseModelt}}\quad
-%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=2]{logMargType1AgenciesBaseModelt}}\quad
-%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=3]{logMargType1AgenciesBaseModelt}}
-%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in, page=1]{logMargType1AgenciesBaseModelt}}\quad
-%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=2]{logMargType1AgenciesBaseModelt}}\quad
-%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=3]{logMargType1AgenciesBaseModelt}}
-%\caption{Model evaluation for `Type 1' agencies for training sample
-%  sizes of $n=25,100$, and $1000$. The $t$-model is used as the base
-%  method to compute TLM. Plotted are the mean TLM for each model
-%  against the trimming fraction across the $100$ cross-validation
-%  samples. Error bars correspond to one standard deviation of TLM
-%  above and below the mean. Models are labeled with the following
-%  abbreviations: `rlm' corresponds to a classical robust fit, `restr.'
-%  corresponds to our restricted likelihood method, and `t' corresponds to the
-%  heavy-tailed $t$-distribution model. The letters `T' and `H'
-%  appearing after `rlm' and `restr.' correspond to the use of  Tukey's
-%  and Huber's $\psi$ respectively.  
-%}
-%\label{fig:Type1Marg}
-%\end{sidewaysfigure}
-%
+\begin{sidewaysfigure}
+\centering
+\captionsetup{justification=centering}
+%\subcaptionbox{}{\includegraphics[width=\textwidth,page=1]{logMargType1AgenciesBaseModelt}}\quad
+%\subcaptionbox{}{\includegraphics[width=\textwidth,page=2]{logMargType1AgenciesBaseModelt}}\quad
+%\subcaptionbox{}{\includegraphics[width=\textwidth,page=3]{logMargType1AgenciesBaseModelt}}
+\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in, page=1]{logMargType1AgenciesBaseModelt}}\quad
+\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=2]{logMargType1AgenciesBaseModelt}}\quad
+\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=3]{logMargType1AgenciesBaseModelt}}
+\caption{Model evaluation for `Type 1' agencies for training sample
+  sizes of $n=25,100$, and $1000$. The $t$-model is used as the base
+  method to compute TLM. Plotted are the mean TLM for each model
+  against the trimming fraction across the $100$ cross-validation
+  samples. Error bars correspond to one standard deviation of TLM
+  above and below the mean. Models are labeled with the following
+  abbreviations: `rlm' corresponds to a classical robust fit, `restr.'
+  corresponds to our restricted likelihood method, and `t' corresponds to the
+  heavy-tailed $t$-distribution model. The letters `T' and `H'
+  appearing after `rlm' and `restr.' correspond to the use of  Tukey's
+  and Huber's $\psi$ respectively.  
+}
+\label{fig:Type1Marg}
+\end{sidewaysfigure}
 
@@
 
-%
-%\begin{sidewaysfigure}[t]
-%%\subcaptionbox{}{\includegraphics[width=2.75in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
-%%\subcaptionbox{}{\includegraphics[width=2.75in,page=2]{hierlogMargType1AgenciesBaseModelt}}
-%\subcaptionbox{}{\includegraphics[width=4in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
-%\subcaptionbox{}{\includegraphics[width=4in,page=2]{hierlogMargType1AgenciesBaseModelt}}
-%\caption{Model evaluation for `Type 1' agencies under the hierarchical model for $n=1000$ and $2000$.
+\begin{sidewaysfigure}[t]
+%\subcaptionbox{}{\includegraphics[width=2.75in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
+%\subcaptionbox{}{\includegraphics[width=2.75in,page=2]{hierlogMargType1AgenciesBaseModelt}}
+\subcaptionbox{}{\includegraphics[width=4in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
+\subcaptionbox{}{\includegraphics[width=4in,page=2]{hierlogMargType1AgenciesBaseModelt}}
+\caption{Model evaluation for `Type 1' agencies under the hierarchical model for $n=1000$ and $2000$.
 The $t$-model is used as the base method to compute TLM.
@@
 Only the relevant trimming fractions ($\alpha\geq .15$) are pictured.
-%}
-%\label{fig:hierType1Marg}
-%\end{sidewaysfigure}
+}
+\label{fig:hierType1Marg}
+\end{sidewaysfigure}
 
@@
 \label{sec:appendix}
-
-\subsection{Details of Examples in Section \ref{examples}}
-\subsubsection{Speed of Light}
-The method is applied to estimate the speed of light using the classical data set of measurements taken by Simon Newcomb available in the {\tt R} package {\tt MASS}. Previous analyses appear in
-\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}.
-With parameters $\bth=(\beta, \sigma)$, the full model is $\beta\sim N(23.6, 2.04^{2})$, $\sigma^{2}\sim IG(5, 10)$, $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$ where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light.
-$\beta$ is interpreted as the passage time of light with
-$\sigma^{2}$ representing measurement error. Two outliers on the low end are a clear indication 
-this model is misspecified.
-
-The summary statistics considered for the restricted likelihood each provide an estimate of location and scale: two versions of simultaneous M-estimators (Huber's and Tukey's for location coupled with Huber's `proposal 2'  for scale \citep{Huber1964}), LMS (least median squares), and LTS (least trimmed squares) estimators.
-Tunning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
-For comparison to a traditional Bayesian outlier approach a heavy-tailed model using Student's $t$ likelihood with $\nu=5$ degrees of freedom is also fit.
-%We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.
-For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.
-\citep[for details see][]{huber2009}
-
 \subsection{Proofs}
@@
 \bibliographystyle{apalike}
-\bibliography{refs}
+\bibliography{refPaper1}
 

### 2018-07-09 revision_temp/Blended Paradigm 4 25.tex
gathering all revision in order to work on paper again

--- 2018-07-09 revision_1/paper.tex
@@
 \end{eqnarray}
-where $m(T(\by))$ is the marginal distribution of $T(\by)$ under the prior distribution.  
+where \blue{$\pi(\bth)$ is the prior distribution and} $m(T(\by))$ is the marginal distribution of $T(\by)$ under \blue{this prior \sout{the prior distribution}}.  
 Predictive statements for further (good) data rely on the model.  For another observation,
@@
 For example, the use of rank likelihoods is discussed by \cite{savage1969}, \cite{pettitt1983, pettitt1982}, and more recently by \cite{hoff2013}.
-\green{Lewis et al. (2012 xxxx) make use of robust regression estimators for $T(\by)$.}  
+\green{\cite{lewis2012} make use of robust regression estimators for $T(\by)$.}  
 Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}. The tenor of these asymptotic 

### 2018-07-09 revision_temp/paper.tex
gathering all revision in order to work on paper again

--- 2018-02-02 paper.tex
@@
 
+Outline:
+\begin{enumerate}
+\item Intro - in good shape
+\item Restricted likelihood - in good shape
+\item Illustrations - In good shape
+\item Computation - in good shape - need to review again and make sure figures appear
+\item Examples
+\begin{enumerate}
+\item Simulation 1 - done with computation, need to add to paper
+\item Simulation 2 - involves hierarchical model example - need to redo completely.
+\item Real Data Analysis - Thoughts on keeping the NW data or using something else.
+\end{enumerate}
+
+\end{enumerate}
+
 \section{Introduction}
@@
 
-\section{Examples}
-\label{examples}
+\section{Simple Illustrations}
+\label{illustrations}
 Before discussing computational details, the method is applied to two simple examples on well known datasets to demonstrate its effectiveness in situations where outliers are a major concern.
@@
 data given the summary statistic $T(\by_{obs})$. 
-The Gibbs sampler \citep{gelfand1990} iteratively samples from the full conditionals $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ and $f(\by|\bth, T(\by)=T(\by_{obs}))$.
+The Gibbs sampler \citep{geman1984} iteratively samples from the full conditionals $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ and $f(\by|\bth, T(\by)=T(\by_{obs}))$.
 Alternative algorithms substitute other generations for the full conditionals, such as the Metropolis-Hastings propose and accept/reject framework.
@@
 
-\subsection{Details of Examples in Section \ref{examples}}
+\subsection{Details of Examples in Section \ref{illustrations}}
 \subsubsection{Speed of Light}

### 2018-07-09 code/simulation_1/simulation_1.R

@@ -1,138 +1,0 @@
-# Simulation
-  # simulate data from a 'true model'
-  # fit various models. 
-  # estimate mean
-  # repeat
-
-
-
-#Note - when re-run, previous results are deleted
-
-library(brlm)
-library(rstan)
-library(tidyverse)
-library(MASS)
-library(MCMCpack)
-
-set.seed(123)
-
-# choose true model ----
-#either normal, mixture 1, mixture 2, or t
-true_model <- 't'
-
-#simulation parameters ----
-n_sim <- 50
-samp_sizes <- c(25, 50, 100)
-
-
-# create data_gen function----
-#generates true data
-if(true_model == 'normal'){
-data_gen <- function(n){
-  rnorm(n)
-}
-} else if(true_model == 'mixture 1'){
-  data_gen <- function(n){
-    x <- rbinom(n, 1, .9)
-    sapply(x, function(a) ifelse(a, rnorm(1), rnorm(1, sd = 3)))
-  }
-} else if(true_model == 'mixture 2'){
-  data_gen <- function(n){
-  x <- rbinom(n, 1, .9)
-  sapply(x, function(a) ifelse(a, rnorm(1), rnorm(1, mean = 3,  sd = 3)))
-  }
-} else if(true_model == 't'){
-  data_gen <- function(n){
-  rt(n,df = 3)/sqrt(3)
-  }
-}
-
-
-
-
-# prior parameters ----
-eta <- 0
-tau <- 3
-a <- 7
-b <- 10
-
-
-# set up empty tibbles to store results----
-empty_mat <- matrix(NA, n_sim, length(samp_sizes))
-colnames(empty_mat) <- samp_sizes
-empty_mat <- as_tibble(empty_mat)
-
-normal_post_means <- mixture_1_post_means <- mixture_2_post_means <- t_post_means <- tukey_post_means <- huber_post_means <- empty_mat 
-
-# initiate log file ----
-out <- here::here(paste0('results_','true_model_', true_model))
-
-if(dir.exists(out)){
- unlink(file.path(out, '*')) #removes previous results
-} else {
-  dir.create(out)
-}
-
-writeLines(paste('n  sim' , 'at', Sys.time(), '\n'),file.path(out, 'log.txt'))
-
-
-# begin for loop ----
-for(i in seq_along(samp_sizes)){
-n <- samp_sizes[i]
[…]

### 2018-07-09 code/simulation_1/summarize_simulation_1.R

@@ -1,45 +1,0 @@
-# summarize simulation 1
-library(tidyverse)
-library(stringr)
-
-results_dir <- str_subset(dir(getwd()), 'results_true_model')
-
-results_all <- map(results_dir, function(dir){
-  tib <- read_rds(file.path(dir, "means_all_long.rds"))
-  tib$true_model <- str_sub(dir, 20)
-  tib
-})
-
-results_all <- bind_rows(results_all)
-
-mse_all <- results_all %>% 
-  group_by(true_model, n, `Fitted Model`) %>% 
-  summarise(MSE = mean((mean-0)^2), sd_mean = sd(mean), bias = mean(mean), `# simulations` = n())
-mse_all$n <- factor(mse_all$n, levels = c("25", "50", "100"))
-
-ggplot(mse_all, aes(x = n, y = MSE, shape = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
-
-ggplot(mse_all, aes(x = n, y = sd_mean, col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
-
-
-ggplot(mse_all, aes(x = n, y = bias^2 , col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
-
-#plot relative MSE's
-
-# make the levels of true_model match those of `Fitted Model`
-mse_all$true_model <- factor(sapply(mse_all$true_model, function(x){
-  if(x == 'mixture 1') {a <- 'Mixture 1'}
-  if(x == 'mixture 2') {a <- 'Mixture 2'}
-  if(x == 'normal') {a <- 'Normal'}
-  if(x == 't') {a <- 'Student-t'}
-  a
-}), levels = c('Normal', 'Student-t', 'Mixture 1', 'Mixture 2'))
-
-
-relative_mse <- mse_all %>% 
-  group_by(true_model, n) %>% 
-  mutate(indicator = true_model == `Fitted Model`, base_mse = MSE[indicator], relative_mse = MSE/base_mse)
-
[…]

### 2018-07-09 revision_1/code/simulation_2/steves_sims/StevesimulationSourceCode.R

@@ -1,0 +1,432 @@
+#
+# Simulation ------- 
+#
+
+#requires sourcing linearRegressionHuberAndProposal2.R #path may need to be changed
+# Adjust source for Steve's directories at work
+# source('../linearRegressionHuberAndProposal2.R')
+source('//trad/profs$/maceachern.1/Desktop/LEWIS.LEE/codeForPaper/codeForPaper/linearRegressionHuberAndProposal2.R')
+
+
+#
+# Complete Model ----
+# theta_i \sim N(mu, tau^2)
+# Y_ij | \theta_i \sim N(\theta_i, sigma_i^2)  
+# with a fairly flat distribution on mu, tau^2 and sigma_i^2.
+# mu \propto 1, \tau^2 \propto 1/\tau^2, sigma_i^2 \propto \sigma_2^2
+# i runs from 1 to 90
+#
+
+#
+# Data Generation ----
+# see fn.gen.data
+# theta_i~N(0,1) i=1,...,90
+# Y_ij | \theta_i \sim (1-p) N(theta_i, sigma2)+ p N(theta_i,m*sigma2), j=1,...,n_i
+
+#90 groups formed by factorial stucture of the 3 factors
+# n_i=25, 50, 100
+# p= .1,.2,.3
+# m= 9, 25
+# each combination observed in five groups
+# sigma2 also will vary: .5, 1, 4, 10
+
+#
+# 
+# Sampling functions---
+#
+#
+
+# [tau^2 | rest ] ----
+
+# tau^2 \sim IG(a,b) in functional form with a=b=0
+fn.sample.tau2<-function(theta, mu, a=0, b=0){
+  #theta is the vector of theta_i
+  K<-length(theta)
+  anew<-0.5*K+a
+  bnew<-0.5*sum((theta-mu)^2)+b
+  1/rgamma(1, shape=anew, rate=bnew)
+}
+
+# [mu | rest ] ----
+
+fn.sample.mu<-function(theta, tau2){
+  K<-length(theta)
+  rnorm(1, mean(theta),sqrt(tau2/K))
+}
+
+# [sigma2_i| rest ] ----
+# sigma2_i \sim IG(a,b) in functional form with a=b=0
+
+# fn.sample.sigma2.i<-function(Yi, thetai, a=0,b=0){
+fn.sample.sigma2.i<-function(Yi, thetai, ass , bss){  # SteveMod
[…]

### 2018-07-09 revision_1/code/simulation_2/steves_sims/simulation.R

@@ -1,0 +1,181 @@
+#
+# Simulation for paper ----
+#
+
+# 'Complete' represents full data posteriors
+# 'Incomplete' represents our restricted versions
+
+date() # SteveMod
+
+rm(list=ls())
+source('//trad/profs$/maceachern.1/Desktop/LEWIS.LEE/codeForPaper/codeForPaper/simulation/StevesimulationSourceCode.R')
+st<-Sys.time()
+set.seed(123) # for reproducible results
+
+concTau2Near1<-0 #1: then concentrate tau^2 prior near 1. 0: then don't and a=b=0
+
+if(concTau2Near1){
+  mu<-1
+  v<-.00001
+  a<-mu^2/v-2 #most prob between .99 and 1.01
+  b<-mu*(a-1)
+} else {
+  a<-0; b<-0
+}
+
+
+# sigma2True<-c(.5,1,4,10) #true values of sigma2 to try for the generation of data
+sigma2True <- 4  # SteveMod
+ass <- 1.25 # SteveMod
+
+#size of MCMC chain
+nburn<-1e4
+nkeep<-1e4
+  
+#print progess after printEach interations
+printEach<-floor(nkeep/10)
+#max number of iterations for the rlm fit
+maxit<-400
+
+for (sig2True in sigma2True){
+#sigma2True <- 4  # SteveMod
+#sig2True <- 4    # SteveMod
+#ass.vec <- c(2.5,5,10,20)
+#for (ass in ass.vec){    # SteveMod
+
+
+#
+# Generate the data ----
+#
+
+YList<-fn.gen.data(sig2True)
+factorsList<-YList$factorsList
+factorsMat<-matrix(unlist(factorsList), nrow=90, ncol=3, byrow = TRUE)
+p<-factorsMat[,1]
+n<-factorsMat[,2]
+m<-factorsMat[,3]
+thetaTrue<-YList$theta
+
+YList<-YList$yList
+
+assign(paste0('YList', 'Sig2_', sig2True), YList)
+assign(paste0('thetaTrue', 'Sig2_', sig2True), thetaTrue)
+
+# SteveMod 
+#
+bss <- ass * sig2True / 2
+#
+# End SteveMod
+
+#
+# Fit the complete normal theory model---
+#
+
+
+#intitial values
+
+thetaInt<-rnorm(90, sapply(YList, mean))
+
+muInt<-rnorm(1, mean(thetaInt))
+
[…]

### 2018-07-09 revision_temp/code/calls/calls_mixture.R

@@ -1,0 +1,72 @@
+# Analyze the Belgium Calls Data
+
+library(tidyverse)
+library(MASS)
+library(rstan)
+
+log_scale  <- 1
+
+phones$year<- phones$year - mean(phones$year)
+phones <- bind_cols(phones)
+if(log_scale) phones$calls <- log(phones$calls)
+plot(phones$year, phones$calls)
+
+# mn_sd <- summarise_all(phones, funs(mean, sd))
+# phones <- as_tibble(scale(phones))
+
+
+# Restricted fit with Tukey locataion and MAD for scale-----
+
+n_prior <- 3
+(fit <- lm(calls ~ year, data = phones[1:n_prior,]))
+
+
+(lm_fit <- lm(calls ~ year, data = phones))
+# prior parameters -----
+g <- nrow(phones) - n_prior
+mu0 <- fit$coefficients
+X <- model.matrix(fit)
+Sigma0 <- g*sigma(fit)^2*solve(t(X)%*%X)
+a0 <- 2
+b0 <- 1 
+
+mu0 + 3*sqrt(diag(Sigma0))
+mu0 - 3*sqrt(diag(Sigma0))
+mu0 + 3*(diag(Sigma0))
+mu0 - 3*(diag(Sigma0))
+
+
+y <- phones$calls[-c(1:n_prior)]
+X_fit <- cbind(1, phones$year[-c(1:n_prior)])
+x <- X_fit[,2]
+N <- length(y)
+stan_rdump(c("N", "y", 'x', 'mu0', 'Sigma0', 'a0', 'b0'), file="mix.data.R")
+library(MASS)
+summary(rlm(y~x,  psi = 'psi.bisquare'))
+summary(lm(y~x))
+input_data <- read_rdump("mix.data.R")
+
+fit_mix <- stan(file='calls_mixture.stan', data=input_data,
+            chains=4, seed=123, iter = 1e4, refresh=2000)
+
+saveRDS(fit_mix, 'out/mixture_stan.rds')
+fit_mix <- readRDS('out/mixture_stan.rds')
+rstan::get_posterior_mean(fit_mix)
+
+plot(fit_mix)
+stan_trace(fit_mix, window = c(9000,10000))
+# stan_scat(fit_mix, pars = c("beta0[1]", "beta0[2]"))
+# stan_scat(fit_mix, pars = c("beta1[1]", "beta1[2]"))
[…]

### 2018-07-09 revision_temp/code/simulation_1/summarize_simulation_1.R

@@ -1,0 +1,45 @@
+# summarize simulation 1
+library(tidyverse)
+library(stringr)
+
+results_dir <- str_subset(dir(getwd()), 'results_true_model')
+
+results_all <- map(results_dir, function(dir){
+  tib <- read_rds(file.path(dir, "means_all_long.rds"))
+  tib$true_model <- str_sub(dir, 20)
+  tib
+})
+
+results_all <- bind_rows(results_all)
+
+mse_all <- results_all %>% 
+  group_by(true_model, n, `Fitted Model`) %>% 
+  summarise(MSE = mean((mean-0)^2), sd_mean = sd(mean), bias = mean(mean), `# simulations` = n())
+mse_all$n <- factor(mse_all$n, levels = c("25", "50", "100"))
+
+ggplot(mse_all, aes(x = n, y = MSE, shape = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
+
+ggplot(mse_all, aes(x = n, y = sd_mean, col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
+
+
+ggplot(mse_all, aes(x = n, y = bias^2 , col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
+
+#plot relative MSE's
+
+# make the levels of true_model match those of `Fitted Model`
+mse_all$true_model <- factor(sapply(mse_all$true_model, function(x){
+  if(x == 'mixture 1') {a <- 'Mixture 1'}
+  if(x == 'mixture 2') {a <- 'Mixture 2'}
+  if(x == 'normal') {a <- 'Normal'}
+  if(x == 'Student-t') {a <- 'Student-t'}
+  a
+}), levels = c('Normal', 'Student-t', 'Mixture 1', 'Mixture 2'))
+
+
+relative_mse <- mse_all %>% 
+  group_by(true_model, n) %>% 
+  mutate(indicator = true_model == `Fitted Model`, base_mse = MSE[indicator], relative_mse = MSE/base_mse)
+
[…]

### 2018-07-09 revision_temp/code/speed_of_light/mix.data.R

@@ -1,0 +1,11 @@
+N <- 66
+y <- 
+c(28, -44, 29, 30, 24, 28, 37, 32, 36, 27, 26, 28,
+29, 26, 27, 22, 23, 20, 25, 25, 36, 23, 31, 32, 24, 27,
+33, 16, 24, 29, 36, 21, 28, 26, 27, 27, 32, 25, 28, 24,
+40, 21, 31, 32, 28, 26, 30, 27, 26, 24, 32, 29, 34, -2,
+25, 19, 36, 29, 30, 22, 28, 33, 39, 25, 16, 23)
+eta <- 0
+tau <- 50
+a <- 5
+b <- 10

### 2018-07-11 revision_1/code/simulation_2/steves_sims/1_simulation.R
ran first pass at simulation

@@ -1,0 +1,180 @@
+#
+# Simulation for paper ----
+#
+
+# 'Complete' represents full data posteriors
+# 'Incomplete' represents our restricted versions
+
+date() # SteveMod
+
+# rm(list=ls())
+# source('//trad/profs$/maceachern.1/Desktop/LEWIS.LEE/codeForPaper/codeForPaper/simulation/StevesimulationSourceCode.R')
+source('StevesimulationSourceCode.R')
+st<-Sys.time()
+set.seed(123) # for reproducible results
+
+#concTau2Near1<-0 #1: then concentrate tau^2 prior near 1. 0: then don't and a=b=0
+
+# if(concTau2Near1){
+#   mu<-1
+#   v<-.00001
+#   a<-mu^2/v-2 #most prob between .99 and 1.01
+#   b<-mu*(a-1)
+# } else {
+  a<-0; b<-0
+# }
+
+
+sigma2True<- 4 #true values of sigma2 to try for #the generation of data
+#sigma2True <- 4  # SteveMod
+#ass <- 1.25 # SteveMod
+ass.vec <- c(1.25, 2.5,5,10,20) #values of shape parameter (alpha) on sigma_i^2 to use.
+scale_vec <- c(0.5, 1/sqrt(2),1, sqrt(2), 2) #values of scale to use to define the scale parameter on sigma_i^2 where  beta_ss = alpha_ss * sig2True * scale. A value of 1 shrinks to the correct value of sigma2.  
+
+#size of MCMC chain
+nburn <- 1000
+nkeep <- 1000
+  
+#print progess after printEach interations
+printEach <- floor(nkeep/2)
+#max number of iterations for the rlm fit
+maxit <- 400
+
+results_dir <- file.path(getwd(), 'results')
+dir.create(results_dir, showWarnings = FALSE)
+
+for(sig2True in sigma2True){
+#sigma2True <- 4  # SteveMod
+#sig2True <- 4    # SteveMod
+
+# Generate the data ----
+dir_to_save_data <- file.path(getwd(), paste0('data_', "sig2_", sig2True))
+dir.create(dir_to_save_data, showWarnings = FALSE)
+  
+YList<-fn.gen.data(sig2True)
+saveRDS(YList, file.path(dir_to_save_data,  'data.rds'))
+  factorsList<-YList$factorsList
[…]

### 2018-07-11 revision_1/code/simulation_2/steves_sims/linearRegressionHuberAndProposal2.R

@@ -70,7 +70,7 @@ fn.chi.prop2<-function(u, k=1.345, deriv=0, b=.71016){
 #---------------
 
 #the linear equation to solve is of the form A*deriv=b
-#function should only input y's that satisfy l1obs and s1obs
+#function should only input y's that satisfy the conditioning statistic values (l1obs and s1obs)
 
 
 #for simplicity this is set up only to handle the default tunning constants given by fn.psi.huber, fn.psi.bisquare  and fn.psi.prop2

### 2018-07-11 revision_1/code/simulation_2/steves_sims/simulation.R

@@ -1,181 +1,0 @@
-#
-# Simulation for paper ----
-#
-
-# 'Complete' represents full data posteriors
-# 'Incomplete' represents our restricted versions
-
-date() # SteveMod
-
-rm(list=ls())
-source('//trad/profs$/maceachern.1/Desktop/LEWIS.LEE/codeForPaper/codeForPaper/simulation/StevesimulationSourceCode.R')
-st<-Sys.time()
-set.seed(123) # for reproducible results
-
-concTau2Near1<-0 #1: then concentrate tau^2 prior near 1. 0: then don't and a=b=0
-
-if(concTau2Near1){
-  mu<-1
-  v<-.00001
-  a<-mu^2/v-2 #most prob between .99 and 1.01
-  b<-mu*(a-1)
-} else {
-  a<-0; b<-0
-}
-
-
-# sigma2True<-c(.5,1,4,10) #true values of sigma2 to try for the generation of data
-sigma2True <- 4  # SteveMod
-ass <- 1.25 # SteveMod
-
-#size of MCMC chain
-nburn<-1e4
-nkeep<-1e4
-  
-#print progess after printEach interations
-printEach<-floor(nkeep/10)
-#max number of iterations for the rlm fit
-maxit<-400
-
-for (sig2True in sigma2True){
-#sigma2True <- 4  # SteveMod
-#sig2True <- 4    # SteveMod
-#ass.vec <- c(2.5,5,10,20)
-#for (ass in ass.vec){    # SteveMod
-
-
-#
-# Generate the data ----
-#
-
-YList<-fn.gen.data(sig2True)
-factorsList<-YList$factorsList
-factorsMat<-matrix(unlist(factorsList), nrow=90, ncol=3, byrow = TRUE)
-p<-factorsMat[,1]
-n<-factorsMat[,2]
-m<-factorsMat[,3]
-thetaTrue<-YList$theta
-
-YList<-YList$yList
-
-assign(paste0('YList', 'Sig2_', sig2True), YList)
-assign(paste0('thetaTrue', 'Sig2_', sig2True), thetaTrue)
-
-# SteveMod 
-#
-bss <- ass * sig2True / 2
-#
-# End SteveMod
-
-#
-# Fit the complete normal theory model---
-#
-
-
-#intitial values
-
-thetaInt<-rnorm(90, sapply(YList, mean))
-
-muInt<-rnorm(1, mean(thetaInt))
-
[…]

### 2018-07-20 revision_1/paper.tex
ran first pass at simulation
done for now on sim 2, editing evaluation of sim 1

@@
 \DeclareMathOperator*{\argmin}{\arg\!\min}
-\graphicspath{{figures/}}
+\graphicspath{{figures/}{figs/}}
 
@@
 \noindent Thus, we can compute $\text{Vol} (P)$ by finding the singular values of $U^\top B$, reducing the computational burden substantially.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Simulations
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Simulations}
+\subsection{Simulation 1}
+
+\subsection{Simulation 2}
+Data generating model:
+\begin{equation}
+\label{gensim2}
+\begin{split}
+\theta_{i}  \sim &  N(\mu, \tau^{2}),  \ i = 1, 2, \dots, 90  \\ 
+y_{ij} \sim & (1-p_{i})N(\theta_{i}, \sigma^{2}) + p_{i}N(\theta_{i}, m_{i}\sigma^{2}), j = 1, 2,..., n_{i}
+\end{split}
+\end{equation}
+with $\mu = 0, \tau^{2} = 1, \sigma^{2} = 4$.
+The values of $p_{i}, m_{i}$, and $n_{i}$ depend on the group and are formed using 5 replicates of the full factorial design over factors $p_{i},m_{i},n_{i}$ with levels $p_{i} = .1, .2, .3$, $m_{i} = 9, 25$, and $n_{i} = 25, 50, 100$.
+The full model for fitting is a corresponding normal model without contamination:
+\begin{equation}
+\label{fullsim2}
+\begin{split}
+\mu \propto 1, \ & \tau^{2} \propto \tau^{-2}, \\
+\theta_{i}\sim N(\mu, \tau^{2}), \ & \sigma^{2}_{i} \sim IG(a_{s}, b_{s}),  \ i = 1, 2, \dots, 90, \\ 
+y_{ij}\sim  N(\theta_{i},\sigma^{2}_{i}), \ j = 1, 2, \dots, n_{i}
+\end{split}
+\end{equation}
+For the restricted likelihood versions we condition on robust M-estimators of location and scale in each group: $T_{i}(\by_{i}) = (\hat\theta_{i}, \hat\sigma^{2}_{i}), i = 1, 2, ..., 90$.
+The two versions used are Huber's and Tukey's location estimator both coupled with Huber's scale estimator.
+The estimates from the Bayesian models are compared to these estimates.
+To complete the specification of model \eqref{fullsim2} we must specify $a_{s}$ and $b_{s}$.
+For this we use a variety of values representing different levels of prior knowledge.
+For each we set $b_{s} = 4a_{s}c_{s}$ resulting in a prior mean for each $\sigma^{2}_{i}$ of $\frac{4c_{s}a_{s}}{a_{s}-1}, \ a_{s} >1$.
+The larger $a_{s}$, the more informative the prior.
+With $c_{s} = 1$ the shrinkage (for large $a_{s}$) is to the true value of $\sigma^{2} = 4$ of the variance of the good component of data in the data generating model.
+We consider $a_{s} = 1.25, 2.5, 5, 10, 20 $ and $c_{s} = 1/2, 1/\sqrt{2}, 1, \sqrt{2}, 2$.
+Values of $c_{s} \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$ with strength growing with $a_{s}$.
+
+A single (\red{maybe need to do more...each run through takes about 3 hours on my laptop and current code, maybe 10 different sets would suffice}) set of data is generated from \eqref{gensim2}.
+The models compared are: the full model \eqref{fullsim2}, the two restricted likelihood versions of this full model, classical robust linear models fit individually to each group.
+
+We compare fits of each model using $MSE = \frac{1}{90}\sum_{i = 1}^{90} (\hat\theta_{i} -\theta_{i})^{2}$ with $\hat\theta_{i}$ the estimate of $\theta_{i}$ from the corresponding model.
+
+Results for MSE
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale = .3]{mse_sim2_facet_scale.png}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale = .3]{mse_sim2_facet_as.png}
+\end{figure}
+
+Big picture - restricted methods beating corresponding robust regressions (labeled rlm). MSE robustness to prior on $\sigma_{i}^{2}$
+
+Results for KL (plots are average of the KLs computed for each group):
+\begin{figure}[H]
+\centering
+\includegraphics[scale = .3]{kl_sim2_facet_scale.png}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale = .3]{kl_sim2_facet_as.png}
+\end{figure}
+
+One explaination for the idea that 'shrinking towards smaller values' may do slightly better than shrinking toward the true value is the fact that we used default tuning parameters to define M-Estimators.
+For the amount of contaimination in each group, the expected value of the variance estimate (Huber's proposal 2) is larger that $\sigma^{2} = 4$.
+The histogram below demonstrates a sample of variaince estimates for data generated from one of the contamination groups....the estimates are consitently above 4.
+Thus it appears the prior mean must be smaller than the true value to get the `correct' amount of shrinkage.
+There is a suggestion that if the prior is too strong (large $a_{s}$), at some point, shrinking to too small a value degrades performance....which would be expected.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale = .3]{hist_sig2_ests.png}
+\end{figure}
 

### 2018-07-20 revision_1/code/simulation_1/1_simulation1.R

@@ -21,8 +21,8 @@ set.seed(123)
 # true_model <- 't'
 
 #simulation parameters ----
-n_sim <- 100
-samp_sizes <- c(25, 50, 100)
+n_sim <- 2
+samp_sizes <- c(25, 50) #, 100)
 
 for(true_model in c("Normal", "Mixture 1", "Mixture 2", "Student-t")){
 
@@ -53,9 +53,9 @@ data_gen <- function(n){
 
 # prior parameters ----
 eta <- 0
-tau <- 10
-a <- 2.1
-b <- 1
+tau <- 2
+a <- 10
+b <- 9
 
 
 # set up empty tibbles to store results----

### 2018-07-20 revision_1/code/simulation_1/2_summarize_simulation1.R

@@ -17,9 +17,11 @@ mse_all <- results_all %>%
   summarise(MSE = mean((mean-0)^2), sd_mean = sd(mean), bias = mean(mean), `# simulations` = n())
 mse_all$n <- factor(mse_all$n, levels = c("25", "50", "100"))
 
-ggplot(mse_all, aes(x = n, y = MSE, shape = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
+# plot(sqrt(mse_all$MSE), mse_all$sd_mean)
 
-ggplot(mse_all, aes(x = n, y = sd_mean, col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
+ggplot(mse_all, aes(x = n, y = MSE, col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
+
+ggplot(filter(mse_all, `Fitted Model`!= 'Normal'), aes(x = n, y = sd_mean, col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
 
 
 ggplot(mse_all, aes(x = n, y = bias^2 , col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
@@ -33,7 +35,7 @@ mse_all$true_model <- factor(sapply(mse_all$true_model, function(x){
   if(x == 'normal') {a <- 'Normal'}
   if(x == 'Student-t') {a <- 'Student-t'}
   a
-}), levels = c('Normal', 'Student-t', 'Mixture 1', 'Mixture 2'))
+}))
 
 
 relative_mse <- mse_all %>% 
@@ -42,4 +44,4 @@ relative_mse <- mse_all %>%
 
 relative_mse$`Fitted Model` <- factor(relative_mse$`Fitted Model`, levels = c("Normal", "Student-t", "Mixture 1", "Mixture 2",  "Huber","Tukey"))
 
[…]

### 2018-07-20 revision_1/code/simulation_2/hierarchical_sim/2_summarizeSimulations.R

@@ -14,6 +14,9 @@ scale_vec <- round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
 
 sig2 <- 4
 
+
+# MSE evaluation metric -----
+
 dfs <- vector('list', length(ass.vec)*length(scale_vec)*length(sig2))
 i <- 1
 for(ss in sig2){
@@ -22,6 +25,8 @@ for(ss in sig2){
       rds_name <- paste0("__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
     
     huber <- read_rds(file.path(results_df, paste0("huber", rds_name)))
+    
+    #computes the estimates --- 
     theta_huber_rest <- apply(huber$theta, 2, mean)
     theta_huber_rlm  <- sapply(huber$robustFits, function(x) x$coefficients)
     huber_df <- tibble(theta = rep(data$theta,2), 
@@ -35,6 +40,8 @@ for(ss in sig2){
     
     
     tukey <- read_rds(file.path(results_df, paste0("tukey", rds_name)))
+    
+    #computes the estimates --- 
     theta_tukey_rest <- apply(tukey$theta, 2, mean)
     theta_tukey_rlm  <- sapply(tukey$robustFits, function(x) x$coefficients)
     
@@ -51,11 +58,10 @@ for(ss in sig2){
     
     
     normal <- read_rds(file.path(results_df, paste0("normal", rds_name)))
+    #computes the estimates --- 
     theta_normal <- apply(normal$theta, 2, mean)
 
-    
-    
-    normal_df <- tibble(theta = rep(data$theta), 
+    normal_df <- tibble(theta = data$theta, 
                        theta_hat = c(theta_normal), 
                        statistic = rep('Normal', n_groups), 
                        method =  rep('Normal', n_groups),
@@ -63,7 +69,6 @@ for(ss in sig2){
                        scale_as = rep(sc, n_groups),
                        sigma2 = rep(ss, n_groups)
     )
-    
     
     df <- bind_rows(huber_df, tukey_df, normal_df)
     dfs[[i]] <- df
@@ -84,12 +89,199 @@ df_mse <- df_estimates %>%
 
 ggplot(df_mse, aes(x = as.factor(a_s), y = MSE, col = interaction(method,statistic), group = interaction(method,statistic))) +
   geom_line() + geom_point() +
-  facet_wrap(~scale_as)
-  
+  facet_wrap(~scale_as) + theme_bw()
[…]

### 2018-08-12 revision_1/paper.tex
paper revisions up to section on computational strategy

@@
 classical robust estimators (e.g., M-estimators) are natural choices
-for conditioning statistics. With these choicees, the method can be thought of as a
+for conditioning statistics. With these choices, the method can be thought of as a
 blend of classical robust estimation and Bayesian methods.
@@
 The development of Bayesian inference relies on a complete Bayesian model consisting of 
-three elements:  the prior distribution, the loss function, and the likelihood or sampling density.  While formal
-optimality of Bayesian methods is unquestioned if one accepts the validity of all three of these elements, 
- a healthy skepticism encourages us to question each of them.  Concern about the prior distribution has
-been addressed through the development of techniques for subjective elicitation \citep{garthwaite2005, ohagan2006} \blue{(added the O'Hagan text here)} and
-the rise of objective Bayesian methods \citep{berger2006}.  
+three elements:  the prior distribution, the loss function, and the likelihood or sampling density.
+While formal optimality of Bayesian methods is unquestioned if one accepts the validity of all three of these elements, a healthy skepticism encourages us to question each of them.
+Concern about the prior distribution has been addressed through the development of techniques for subjective elicitation \citep{garthwaite2005, ohagan2006} and objective Bayesian methods \citep{berger2006}.
 Concern about the loss function is reflected in, for example, the
 extensive literature on Bayesian hypothesis tests \citep{kass1995}.  
-The sampling density has been given less attention from a specifically
-Bayesian view, although the work on predictive diagnostics \citep{box1980} departs from classical
-traditions.
-
-%The focus of this work is the intersection of Bayesian methodology and data analysis. In particular, we develop techniques to handle imperfections in the sampling density
-The focus of this work is the development of techniques to handle imperfections in the sampling density.  These imperfections often show
-themselves through the presence of outliers--cases %--here taken to be 
-not reflecting the phenomenon under
-study. %--in the data set. 
-%A traditional solution to Bayesian outlier-handling involves replacing the original sampling density with a mixture or heavy-tailed density.
-A mixture model  includes one component for the ``good'' data and a second component for the ``bad'' data in an attempt to compartmentalize the outliers.
-The heavy-tailed approach simply attempts to discount the outliers directly.
-Another traditional approach fits a flexible (typically nonparametric) model to the data, producing a Bayesian version of a density estimate for both good and bad data.
-In recent development, inference is made through the use of robust inference functions \citep[][in press]{lee2013}.
-%\red{Q: Is the above sentence still about modifying the sampling density to
-%  handle outliers?}
-There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling
+%This work focus on the likelihood.
+% sampling density has been given less attention from a specificallyBayesian view, although the work on predictive diagnostics \citep{box1980} departs from classical traditions.
+
+The focus of this work is the development of techniques to handle imperfections in the likelihood.  These imperfections often show themselves through the presence of outliers--cases 
+not reflecting the phenomenon under study. There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling
 density with a mixture model which includes one component for the ``good'' data and a second 
-component for the ``bad'' data.  With this approach, the prior distribution is updated with the likelihood
-from the mixture model to obtain the complete-data posterior distribution.  The good component of
-the sampling density is used for prediction of future good data.  The second approach replaces the
+component for the ``bad'' data.
+With this approach, the prior distribution is updated with the  mixture model likelihood to obtain the complete-data posterior distribution and  the good component of the sampling density is used for prediction of future good data.
+The second approach replaces the
 basic sampling density with a thick-tailed density in an attempt to discount outliers, yielding techniques that 
 often provide solid estimates of the center of the distribution but 
-do not easily translate to predictive
-densities for further good data.  The third approach fits a flexible (typically nonparametric) model to 
-the data, producing a Bayesian version of a density estimate for both good and bad data.  In recent 
-development, inference 
-is made through the use of robust inference functions \citep[][in press]{lee2013}.
-
-The traditional strategies for handling outliers all have their drawbacks.  While we view the sampling 
-density for the good data as stable, the outlier-generating processes 
-may be transitory in nature, constantly shifting as the source of bad data changes.  This prevents
-us from appealing to large-sample arguments to claim that, with enough data, we can nail down a
-model for both good and bad data combined.  Instead of attempting to model both good and bad
-data, we propose a novel strategy for handling outliers. %:  the use of restricted likelihood.  
-In a nutshell, we begin with a complete model   
-as if all of the data are good.
-But rather than driving the move from prior distribution to posterior
-distribution by the entire likelihood, we use only the likelihood
-driven by a
-few summary statistics which typically target inferential quantities
-of interest.  We call this reduced likelihood a restricted % an incomplete
-likelihood. 
-%\red{[better to call a restricted likelihood? if we change, make sure to change consistently throughout the paper]} 
-%\green{[I agree with Yoon.  Better to call this a restricted likelihood.]}
-The 
-update is a formal update from prior distribution to posterior distribution, based on the sampling density
-of the summary statistics. 
- %In our approach, the reader will identify a stream of reasoning which is manifested in classical M-estimation, generalized estimating equations, approximate Bayesian computation, and elsewhere.  
-The novelty of the work is twofold.  We make use of
-classical robust estimators as  summary statistics in a formal
+do not easily translate to predictive densities for further good data.
+The third approach fits a flexible (typically nonparametric) model to  the data, producing a Bayesian version of a density estimate for both good and bad data.
+In recent development, inference
+is made through the use of robust inference functions \citep{lee2014}.
+
+The traditional strategies for handling outliers all have their drawbacks.  While we view the sampling density for the good data as stable, the outlier-generating processes 
+may be transitory in nature, constantly shifting as the source of bad data changes.
+This prevents us from appealing to large-sample arguments to claim that, with enough data, we can nail down a model for both good and bad data combined.
+Instead of attempting to model both good and bad data, we propose a novel strategy for handling outliers.
+In a nutshell, we begin with a complete model  as if all of the data are good.
+Rather than driving the move from prior to posterior  by the full likelihood, we use only the likelihood
+driven by a few summary statistics which typically target inferential quantities
+of interest.
+We call this likelihood a restricted because conditioning is done on a restricted set of data; the set which satisfies the observed summary statistics.
+This is a formal update of the prior distribution based on the sampling density of the summary statistics.
+The novelty of the work is twofold.
+We make use of classical robust estimators as  summary statistics in a formal
 Bayesian framework, using the sampling density of the estimators as a replacement for the 
-sampling density of the data.  Second, we advance the argument that conditioning on an insufficient
-summary of the data is sound practice, rather than merely being done for computational and 
-modelling convenience.
+sampling density of the data.
+Second, we advance the argument that conditioning on an insufficient summary of the data is sound practice, rather than merely being done for computational and modelling convenience.
 
@@
 %In addition to outlier-prone data, the 
-\green{ The sampling density can err due to other forms of model misspecification.  
-The traditional view is that, if the model is inadequate, one should build a better model.  In our
-empirical work, as data sets have become larger and more complex, we have bumped into 
-settings where we cannot realistically build the perfect model.  We ask the question ``by attempting
-to improve our model through elaboration, will the overall performance of the model suffer?''  If yes,
-we avoid the elaboration, retaining a model with some level of misspecification.  Acknowledging that
-the model is misspecified implies acknowledging that the sampling density is incorrect, as
-we do when outliers are present.  Thus, outliers are but one form of misspecified model.  
-We recommend a common solution for dealing with outliers and more general forms of model misspecification.}
-
-The remainder of the paper develops Bayesian restricted likelihood (Section~\ref{restrictedlikelihood}), shows
-how it can be applied to a Bayesian linear model (Section~\ref{BayesLinMod}), illustrates its use
-on an insurance agencies data set with a novel twist on model evaluation (Section~\ref{Applications}), 
-and wraps up with a discussion (Section~\ref{Conclusions}).  
-A major contribution of this work is the computational strategy whose legitimacy is established 
-in Section~\ref{BayesLinMod}.  The technical proofs are in the appendix.
+%\green{ The sampling density can err due to other forms of model misspecification.  
+%The traditional view is that, if the model is inadequate, one should build a better model.  In our
+%empirical work, as data sets have become larger and more complex, we have bumped into 
+%settings where we cannot realistically build the perfect model.  We ask the question ``by attempting
+%to improve our model through elaboration, will the overall performance of the model suffer?''  If yes,
+%we avoid the elaboration, retaining a model with some level of misspecification.  Acknowledging that
+%the model is misspecified implies acknowledging that the sampling density is incorrect, as
+%we do when outliers are present.  Thus, outliers are but one form of misspecified model.  
+%We recommend a common solution for dealing with outliers and more general forms of model misspecification.}
+
+The remainder of the paper develops....
+%Bayesian restricted likelihood (Section~\ref{restrictedlikelihood}), shows how it can be applied to a Bayesian linear model (Section~\ref{BayesLinMod}), illustrates its use on an insurance agencies data set with a novel twist on model evaluation (Section~\ref{Applications}), and wraps up with a discussion (Section~\ref{Conclusions}).
+A major contribution of this work is the computational strategy whose legitimacy is established in Section~\ref{BayesLinMod}.
+The technical proofs are in the appendix.
 
@@
 \subsection{Examples}
-To describe the use of the restricted likelihood in a Bayesian framework, 
-we begin with a pair of simple examples
-for the one-sample problem. Several more examples are detailed in \cite{lewis2014}.  For those discussed here, the model takes the
-data $\by=(y_1,\ldots,y_n)$
-to be a random sample
+To describe the use of the restricted likelihood, 
+we begin with a pair of simple examples for the one-sample problem.  For both, the model takes the data $\by=(y_1,\ldots,y_n)$ to be a random sample
 of size $n$ from a continuous distribution indexed by a parameter
-vector $\bth$, with pdf $f(y| \bth)$.  The standard, or full-data,
-likelihood would be $L(\bth | \by) = \prod_{i=1}^n f(y_i | \bth)$.
-
-As a first example, we consider the case where a subset of the data are known to be 
-bad in the sense of not informing us about $\bth$--and where the subset is known.  This case mimics the setting where outliers in
-a data set are identified and discarded before a formal analysis is done.  
-Without loss of generality, we label the good 
-cases $1$ through $n-k$ and the bad 
-cases $n-k+1$ through $n$.  
-The relevant likelihood to be used to move from prior distribution to posterior distribution is clearly 
-$L(\bth | y_1, \ldots, y_{n-k}) = \prod_{i=1}^{n-k} f(y_i | \bth)$.  
-For an equivalent analysis, we rewrite the full %entire
-likelihood as the product of two pieces,
+vector $\bth$, with pdf $f(y| \bth)$.  The standard, or full,
+likelihood is $L(\bth | \by) = \prod_{i=1}^n f(y_i | \bth)$.
+
+The first example considers the case where a known subset of the data are known to be 
+bad in the sense of not informing us about $\bth$.
+This case mimics the setting where outliers are identified and discarded before doing a formal analysis.
+Without loss of generality, we label the good cases $1$ through $n-k$ and the bad cases $n-k+1$ through $n$.
+The relevant likelihood to be used to move from prior distribution to posterior distribution is clearly $L(\bth | y_1, \ldots, y_{n-k}) = \prod_{i=1}^{n-k} f(y_i | \bth)$.
+For an equivalent analysis, we rewrite the full likelihood as the product of two pieces:
 \begin{eqnarray}
@@
 \end{eqnarray}
-% where the second factor may not actually involve $\bth$.
 We wish to keep the first piece and drop the second for better inference on $\bth$.
 
-A second example involves deliberate censoring of small and large observations.  This is
-sometimes done as a precursor to the analysis of reaction time
-experiments  \citep[e.g.,][]{ratcliff1993}
-\green{where very small reaction times are physiologically too quick to be true reaction times
-are usually explained as anticipation, and where implausibly long reaction times are believed due to inattention. }  
-%\red{Q: provide a reason why this deliberate censoring is done?}
-With lower
-and upper censoring times at $t_1$ and $t_2$, the post-censoring sampling distribution
-is of mixed form, with masses $F(t_1|\bth)$ at $t_1$ and $1-F(t_2|\bth)$ at $t_2$,
+The second example involves deliberate censoring of small and large observations. This is
+sometimes done as a precursor to the analysis of reaction time experiments  \citep[e.g.,][]{ratcliff1993} where very small and large reaction times are physiologically implausible;  explained by either anticipation or lack of attention of the subject.
+With lower and upper censoring times at $t_1$ and $t_2$, the post-censoring sampling distribution is of mixed form, with masses $F(t_1|\bth)$ at $t_1$ and $1-F(t_2|\bth)$ at $t_2$,
 and density $f(y | \bth)$ for $y \in (t_1, t_2)$.  We adjust the original data $y_i$,
@@
 The adjusted update is performed with $L(\bth |c(\by))$.  
-With slightly non-standard notation, we let $g(t_1|\bth) = F(t_1|\bth)$,
+Letting $g(t_1|\bth) = F(t_1|\bth)$,
 $g(t_2 | \bth) = 1 - F(t_2|\bth)$, and $g(y|\bth)=f(y|\bth)$ for
-$y \in (t_1, t_2)$.
-Hence, we may rewrite the full %complete %entire 
-likelihood as the product of
-two pieces, 
+$y \in (t_1, t_2)$, we may rewrite the full 
+likelihood as the product of two pieces
 \begin{eqnarray}
 \label{Censoring} 
-%L(\bth | \by) =  \left( \prod_{i=1}^n g(x_i | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth, x_i) \right) ,
-L(\bth | \by) =  
-\left( \prod_{i=1}^n g(c(y_i)  | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth,c(y_i) ) \right) ,  
+L(\bth | \by) =  \left( \prod_{i=1}^n g(c(y_i)  | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth,c(y_i)). \right) ,  
 \end{eqnarray}
-and retain only the first for the formal update.
+Only the first part is retained the analysis. Several more examples are detailed in \cite{lewis2014}.
 
@@
 since $T(\by)$ is a well-defined random variable with a probability distribution indexed by $\bth$.  
-The update from prior distribution to posterior distribution can be 
-made on the basis of $f(T(\by)|\bth)$ rather than $f(\by|\bth)$.  This leads to the restricted likelihood posterior 
+This leads to the restricted likelihood posterior 
 \begin{eqnarray}
@@
 For example, the use of rank likelihoods is discussed by \cite{savage1969}, \cite{pettitt1983, pettitt1982}, and more recently by \cite{hoff2013}.
-\green{Lewis et al. (2012 xxxx) make use of robust regression estimators for $T(\by)$.}  
+\cite{lewis2012} make use order statistics and robust estimators for $T(\by)$ in the location-scale setting. 
 Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}. The tenor of these asymptotic 
@@
 
-%edited to include more detail on ABC:
-%\textcolor{blue}{Part on the use of incomplete likelihoods being used as approximations to complete likelihoods was commented out.
-However, I added more detail on ABC.
-Thought is that we could move this to the discussion.}
-%\red{This additional discussion on ABC
-%  (next two paragraphs) looks a bit too long.}
 Restricted likelihoods have also been used as practical approximations to a full likelihood.
@@
 %Hence, we can see that, as in our method, conditioning is done on a summary of the complete data.
-By choosing an approximately sufficient $T(\cdot)$ and a small enough $\epsilon$ the claim is made that $L(\bth|\mathcal{B}(\by))\approx L(\bth|T(\by))\approx L(\bth|\by)$.
-Consequently, the ABC posterior approximates the full data posterior.
-We note that efforts have been made to formalize what is meant by  approximate sufficiency \citep[e.g.,][]{joyce2008}.
+With an approximately sufficient $T(\cdot)$ and a small enough $\epsilon$, heuristically  $L(\bth|\mathcal{B}(\by))\approx L(\bth|T(\by))\approx L(\bth|\by)$.
+Consequently, the ABC posterior approximates the full data posterior and efforts have been made to formalize what is meant by  approximate sufficiency \citep[e.g.,][]{joyce2008}.
+ABC is related to our method in that the ``conditioning'' is on something other than the data $\by$.
+However, we specifically seek to condition on an insufficient statistic to guard against misspecification in parts of the likelihood.
+Additionally, we develop methods where the conditioning is exact (i.e.
+$\epsilon = 0$).
 
@@
 
-\green{ABC is related to our method in that the ``conditioning'' is on something other than the data $\by$.
-However, the conditioning in ABC is heuristic.
+%However, the conditioning in ABC is heuristic.
 For technical reasons, the calculation proceeding from $\pi(\bth)$ to $\pi(\bth)L(\bth| \mathcal{B}(\by))/\int \pi(\bth)L(\bth| \mathcal{B}(\by)) d\bth$ is not a formal conditional update.
 Simply put, if an external observer told $\mathcal{B}(\by)$ can supply $T(\by)$ and vice-versa, the information contained in $\mathcal{B}(\by)$ is exactly that contained in $T(\by)$ and proper conditioning will lead to identical posterior distributions.
-This is not the case with a typical implementation of ABC.}
+This is not the case with a typical implementation of ABC.
 
@@
 
-This work extends the development of Bayesian restricted likelihood by arguing \green{that deliberate choice of $T(\by)$} is sound practice and also by expanding the class of conditioning statistics in which exact conditioning can be achieved.
-%well beyond ranks.
-Our methods do not rely on asymptotic properties, \green{nor do they rely on} approximate conditioning, \green{nor do they need to correspond to artificial censoring to create incomplete or missing data}  \citep[e.g.,][]{albert1988, hoffwakefield2013}.
-\green{Note - fix references here hoffwakefield for asymptotic; albert for ? .}
-
-The key to productive use of the restricted likelihood is the choice of $T(\by)$ and the development
-of computational strategies that allow us to truly condition on the observed $T(\by)$ and 
-fit the model in formal Bayesian fashion.  In this work, we focus
-on robustness, and natural choices of $T(\by)$ for the one-sample problem include a set of middling order statistics, a trimmed
-mean, or a classical robust estimator of location and/or scale.  
-We have previously implemented several of these methods and have found them to perform well \citep[][]{lewis2012}.
+This work extends the development of Bayesian restricted likelihood by arguing that deliberate choice of $T(\by)$ is sound practice and also by expanding the class of conditioning statistics in which exact conditioning can be achieved.
+Our methods do not rely on asymptotic properties, nor do they rely on approximate conditioning.%, \green{nor do they need to correspond to artificial censoring to create incomplete or missing data}  \citep[e.g.,][]{albert1988, hoffwakefield2013}.
+%\green{Note - fix references here hoffwakefield for asymptotic; albert for ? .}
+
+%The key to productive use of the restricted likelihood is the choice of $T(\by)$ and the development
+%of computational strategies that allow us to truly condition on the observed $T(\by)$ and 
+%fit the model in formal Bayesian fashion.  In this work, we focus
+%on robustness, and natural choices of $T(\by)$ for the one-sample problem include a set of middling order statistics, a trimmed
+%mean, or a classical robust estimator of location and/or scale.  
+%We have previously implemented several of these methods and have found them to perform well \citep[][]{lewis2012}.
 Versions most extensible to the linear model include the M-estimators in the tradition of \cite{huber1964}, least median squares (LMS), and least trimmed squares (LTS).
@@
 These strategies rely on generation of complete data sets from different values of $\bth$.
-Each complete data set leads to a statistic $T(\by)$ under $\bth$, and these generated statistics are used to estimate the density at $T(\by_{obs})$, where $\by_{obs}$ is the observed complete data.
+%Each complete data set leads to a statistic $T(\by)$ under $\bth$, and these generated statistics are used to estimate the density at $T(\by_{obs})$, where $\by_{obs}$ is the observed complete data.
 This estimate is fed into Bayes' theorem for the update from prior distribution to posterior distribution.
+
 %For the example in the previous section, these strategies work well.
@@
 
-These direct sampling techniques rely on density estimation and numerical integration.
+%These direct sampling techniques rely on density estimation and numerical integration.
 Density estimation becomes difficult for high dimensional $T(\by)$ and numerical integration breaks down for high dimensional $\bth$.
@@
 
-\subsection{A first data analysis example} %\textcolor{blue}{ADDED}
-\label{darwinAnalysis}
-Before discussing computational details of finding restricted 
-posteriors, we begin by analyzing a simple example involving
-outliers. The data consists of well known measurements of the \green{passage time} of
-light taken by Simon Newcomb in the late nineteenth century and
-contain two clear outliers on the low end. Details and data are
-available in the R package {\tt MASS} and previous analyses appear in
-\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}. Letting
-$y_{i}$ denote the $i^{th}$ coded measurement of the passage time of light, we
-assume $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$. The
-parameter $\beta$ can be interpreted as the passage time of light with
-$\sigma^{2}$ representing measurement error. The outliers \green{are a clear indication} %make clear
-that this normal model is misspecified.  \green{Also,} %Another reason for model misspecification is that 
-the measurements are coarse, taking on only
-integer values.  For a Bayesian analysis, we must specify prior
-distributions on the parameters $\bth=(\beta, \sigma)$. For this we
-assume an independent normal -- inverse gamma model. That is,
-$\beta\sim N(\eta, \tau^{2})$ and $\sigma^{2}\sim IG(a, b)$. The
-hyperparameters  are fixed for simplicity and taken to be $\eta=23.6$,
-$\tau=2.04$, $a=5$,  and $b=10$. We note that our computational
-strategy described in Section \ref{highDim} makes it feasible to fit
-more complex model structures. The Bayesian model presented here is a
-special case of the linear model in \eqref{LinearModel} presented below.
-
-As summary statistics for the restricted likelihood methods, we
-consider robust simultaneous M-estimators of location and scale as
-well as LMS (least median squares) and LTS (least trimmed squares) estimators.
+%\subsection{Details of Examples in Section \ref{illustrations}}
+%\subsubsection{Speed of Light}
+%With parameters $\beta$ and $\sigma$, the full model is $\beta\sim N(23.6, 2.04^{2})$, $\sigma^{2}\sim IG(5, 10)$, $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$ where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light.
+$\beta$ is interpreted as the passage time of light with
+%$\sigma^{2}$ representing measurement error.
+Tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$.
+The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models.
+%We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.
+For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.
+\citep[for details see][]{huber2009}
+
+\section{Illustrative Examples}
+\label{illustrations}
+Before discussing computational details, the method is applied to two simple examples on well known data sets to demonstrate its effectiveness in situations where outliers are a major concern.
+The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}.
+%Specific details are left to the Appendix.
+
+The first example is an analysis of Simon Necomb's 66 measurements of the speed of light; two of which are significant outliers in the lower tail.
+The full model is a standard location-scale Bayesian model:
+\begin{equation}
+\beta\sim N(23.6, 2.04^{2}),\  \sigma^{2}\sim IG(5, 10), \ y_{i}\iid N (\beta, \sigma^{2}), i=1,2,\dots, n=66,
+\end{equation}
+where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light. $\beta$ is interpreted as the passage time of light with $\sigma^{2}$ representing measurement error.
+Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)  Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
+Associated tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \cite{huber1964} and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+Additionally, two other common approaches to outlier handling are fit: 1) replacing the normal distribution with a t-distribution and, 2) replacing the normal distribution with a mixture of two normals.
+The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$.
+The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models.
+The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ assuming the prior $p \sim beta(20,1)$ on the probability of belonging to the `good' component.
+
+The posteriors of $\beta$ under each model appear in top of Figure \ref{fig:newcomb_post}.
+As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy tailed model provides robustness against them.
+The restricted likelihood methods using the M-estimators and LTS statistics also achieve robustness against the outliers.
+Conditioning on LMS however, results in a posterior similar to the one under the normal model.
+The M-estimators provide the most precise posteriors in this case.
+This is reflected in more precise predictions than the heavy-tailed and mixture model as illustrated by the predictive distributions displayed in the bottom of Figure \ref{fig:newcomb_post}.
+
+\begin{figure}
+\centering
+\begin{subfigure}{\textwidth}
+{\includegraphics[width = 6in]{figs/speed_of_light_beta.png}}
+%\caption{}
+%\label{fig:newcomb_beta}
+\end{subfigure}
+\centering
+\begin{subfigure}{\textwidth}
+{\includegraphics[width = 6in]{figs/speed_of_light_predictive.png}}
+%\caption{}
+%\label{fig:newcomb_predictive}
+\end{subfigure}
+\caption{Top: Posteriors of the location parameter $\beta$ under the normal theory model, the t-model, and four restricted likelihood models for Newcomb's speed of light measurements.
+Bottom: Posterior predictive distribution of the speed of light under the normal theory model, the t-model, and four restricted likelihood models.}
+\label{fig:newcomb_post}
+\end{figure}
+
+As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
+The outliers in this case are due to a change in units on which calls were recorded for part of the dataset.
+The full model is a standard normal Bayesian linear regression:
+
+\begin{equation}
+{\boldsymbol{\beta}}\sim N_{2}(\boldsymbol{\mu}_{0}, \boldsymbol{\Sigma}_{0}),\  \sigma^{2} \sim IG(a, b), \by \sim N(X\boldsymbol{\beta}, \sigma^{2} I),
+\end{equation}
+where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and X is the $n\times 2$ design matrix.
+Prior parameters are fixed via a fit to the first 3 data points.
+In particular, $\Sigma_{0} = g\sigma_{0}^2 (X^{\top}X)^{-1}$, with $\sigma_{0} = 0.03$ and $\mu_{0} = (1.87,  0.03)^{\top}$; the MLEs fit to the first three data points.
+There are $n=21$ remaining data points and the parameter $g$ is set to $21$ reflecting a unit information prior \cite{}.
+Finally $a = 2$ and $b =1$ for the normal theory and restricted likelihood models.
+
+Four models are compared: 1) the normal theory base model 2) A two component normal mixture model, 3) a t-model, and 4) a restricted likelihood model conditioning on Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
+The mixture model assumes different mean regression functions and variances for each component, but keeps the same, relatively non-informative priors.
+The probability of belonging to the first component is given a $beta(5,1)$ prior.
+The heavy-tailed model fixes the degrees of freedom to 5 with the same adjustment to the prior on $\sigma^{2}$ as above.
+
+The data and  $95\%$ credible bands of the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}.
+The normal theory model is only fit to the obvious non-outlying points.
+Since the t-model assumes the data are heavy-tailed, the posterior predictive distribution is much wider.
+On the other hand, the predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit that discards the outliers.
+It is also close to the two component mixture results where the predictive distribution is formulated using only the good component.
+The mixture model involves explicitly modeling the outlier generating mechanism.
+In more more complex situations where the outlier generating mechanism is transient (i.e.
+ever changing and more complex than just a unit error in the recording), modeling the outliers becomes more difficult.
+Like classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
+
+\begin{figure}
+\centering
+{\includegraphics[width = 4in]{figs/calls_predictive.png}}
+\caption{Predictive distribution of log(calls) under the Normal theory model fit to the non-outliers, the restricted likelihood model with  Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
+The first three data points were used to specify the prior with the remaining points used in the posterior fits.
+See details in the Appendix.}
+\label{fig:calls_predictive}
+\end{figure}
+
+%
+% and the development
+%of computational strategies that allow us to truly condition on the observed $T(\by)$ and 
+%fit the model in formal Bayesian fashion.  In this work, we focus
+%on robustness, and natural choices of $T(\by)$ for the one-sample problem include a set of middling order statistics, a trimmed
+%mean, or a classical robust estimator of location and/or scale.  
+%We have previously implemented several of these methods and have found them to perform well \citep[][]{lewis2012}.
+Versions most extensible to the linear model include the M-estimators in the tradition of \cite{huber1964}, least median squares (LMS), and least trimmed squares (LTS).
+For these choices the restricted likelihood is not available in closed form, making computation of the restricted posterior a challenge.
+For low-dimensional statistics $T(\by)$ and parameters $\bth$, the direct computational strategies described in \cite{lewis2014} can be used to estimate the incomplete posterior conditioned on essentially any statistic.
+These strategies rely on generation of complete data sets from different values of $\bth$.
+%Each complete data set leads to a statistic $T(\by)$ under $\bth$, and these generated statistics are used to estimate the density at $T(\by_{obs})$, where $\by_{obs}$ is the observed complete data.
+This estimate is fed into Bayes' theorem for the update from prior distribution to posterior distribution.
+%
+
+%\subsection{A first data analysis example} %\textcolor{blue}{ADDED}
+%\label{darwinAnalysis}
+%Before discussing computational details of finding restricted 
+%posteriors, we begin by analyzing a simple example involving
+%outliers. The data consists of well known measurements of the \green{passage time} of
+%light taken by Simon Newcomb in the late nineteenth century and
+%contain two clear outliers on the low end. Details and data are
+%available in the R package {\tt MASS} and previous analyses appear in
+%\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}. Letting
+%$y_{i}$ denote the $i^{th}$ coded measurement of the passage time of light, we
+%assume $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$. The
+%parameter $\beta$ can be interpreted as the passage time of light with
+%$\sigma^{2}$ representing measurement error. The outliers \green{are a clear indication} %make clear
+%that this normal model is misspecified.  \green{Also,} %Another reason for model misspecification is that 
+%the measurements are coarse, taking on only
+%integer values.  For a Bayesian analysis, we must specify prior
+%distributions on the parameters $\bth=(\beta, \sigma)$. For this we
+%assume an independent normal -- inverse gamma model. That is,
+%$\beta\sim N(\eta, \tau^{2})$ and $\sigma^{2}\sim IG(a, b)$. The
+%hyperparameters  are fixed for simplicity and taken to be $\eta=23.6$,
+%$\tau=2.04$, $a=5$,  and $b=10$. We note that our computational
+%strategy described in Section \ref{highDim} makes it feasible to fit
+%more complex model structures. The Bayesian model presented here is a
+%special case of the linear model in \eqref{LinearModel} presented below.
+%
+%As summary statistics for the restricted likelihood methods, we
+%consider robust simultaneous M-estimators of location and scale as
+%well as LMS (least median squares) and LTS (least trimmed squares) estimators.
 The simultaneous M-estimators $b(\by)$ and $s(\by)$ of $\beta$ and $\sigma$, respectively, are the solutions to the equations
-\begin{eqnarray}
-\label{Mest}
- \sum_{i=1}^n \psi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 \\
- \sum_{i=1}^n \chi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 . \nonumber 
-\end{eqnarray} 
-For the first equation we consider two $\psi$ functions: Huber's and Tukey's.
+%\begin{eqnarray}
+%\label{Mest}
+% \sum_{i=1}^n \psi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 \\
+% \sum_{i=1}^n \chi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 . \nonumber 
+%\end{eqnarray} 
+%For the first equation we consider two $\psi$ functions: Huber's and Tukey's.
 These are both coupled with Huber's `proposal 2'  for the $\chi$ function in the second equation \citep[for details see][]{huber2009}.
 Tuning parameters for these functions are set to achieve $95\%$ efficiency under normally distributed data.
-
-LMS minimizes the median squared residual and LTS minimizes the sum of the $k$ smallest squared residuals where $k$ is chosen by the user.
+%
+%LMS minimizes the median squared residual and LTS minimizes the sum of the $k$ smallest squared residuals where $k$ is chosen by the user.
 These estimators are considered because, unlike the M-estimators above, they can achieve high breakdown.
-%These estimators are easily implemented by the {\tt rlm} function of the {\tt MASS} package in R. 
-It is well known that LMS has highest possible breakdown but is inefficient.
+%%These estimators are easily implemented by the {\tt rlm} function of the {\tt MASS} package in R. 
+%It is well known that LMS has highest possible breakdown but is inefficient.
 LTS is more efficient and its breakdown properties are determined by $k$, with highest possible breakdown occurring for $\left \lfloor{\frac{n+1}{2}}\right \rfloor\leq k\leq\left \lfloor{\frac{n+2}{2}}\right \rfloor$.
 %For the current data set $n=66$ and we take $k=34$ to achieve highest possible breakdown.
-For the current analysis we do not choose $k$ to achieve highest possible breakdown. Instead, with $n=66$ and we choose $k=62$ (roughly $95\%$ of $n$) to be \green{more} %somewhat
-comparable to the tuning parameters chosen for the M-estimators.
+%For the current analysis we do not choose $k$ to achieve highest possible breakdown. Instead, with $n=66$ and we choose $k=62$ (roughly $95\%$ of $n$) to be \green{more} %somewhat
+%comparable to the tuning parameters chosen for the M-estimators.
 The LMS and LTS \green{estimators} are also coupled with an estimator of scale for the conditioning.
@@
 %Computation of these estimators are also implemented in the {\tt MASS} package by the function {\tt lqs}.
-
-For comparison to a traditional Bayesian outlier approach we also fit a heavy-tailed model by changing the data distribution from a normal to a Student's $t$ with $\nu=5$ degrees of freedom.
+%
+%For comparison to a traditional Bayesian outlier approach we also fit a heavy-tailed model by changing the data distribution from a normal to a Student's $t$ with $\nu=5$ degrees of freedom.
 We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.
 For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.
-
-The marginal posteriors for $\beta$ and $\sigma^{2}$ as well as the
-predictive distribution \eqref{RestrictedpredDist} under each model
-are displayed in Figures
-\ref{fig:newcombBeta}-\ref{fig:newcombPred}. Both of the two small
-outliers and the normal prior on $\beta$ centered at $23.6$ are
-influential in the results. The normal theory model is most
-drastically affected with the posterior of $\beta$ being pulled
-towards the prior and outliers. Inference on $\sigma^{2}$ under this
-model is impacted by the outliers (see Figure
-\ref{fig:newcombSig2}) \green{resulting in overestimation of $\sigma^{2}$}. 
-The heavy-tailed model as well as the
-restricted likelihood methods with LTS, Huber's, and Tukey's summary
-statistics are less influenced by the outliers and priors. The
-marginal posteriors for $\beta$ are closer to the center of the
-non-outlying data. Inference on the variance parameter also more
-closely reflects the variance information in this part of the data
-(the mean and variance of the data without the two outliers are $27.8$
-and $25.8$, respectively). The posterior of $\beta$ under LTS is
-slightly more dispersed than under the two M-estimator methods. This is
-also reflected in the variance parameter in that under LTS the posterior distribution \green{concentrates on 
-slightly larger values of $\sigma^2$} % is slightly higher. 
-While LMS has high breakdown, it has been more drastically affected by the normal prior centered at $23.6$ than the others. This is % likely 
-because LMS achieves high breakdown by discounting much of the information in the data.
-
-Though inference for the main parameter of interest ($\beta$) is
-similar between the traditional heavy-tailed approach and the new
-method with LTS, Huber's, and Tukey's summary statistics,  the
-traditional heavy-tailed method has the disadvantage of less precise
-predictive capability. This is reflected in the heavier tails of its
-predictive distribution  \eqref{RestrictedpredDist} seen in Figure
-\ref{fig:newcombPred} (plotted are the log predictive \green{densities} %distributions
-under each method). The predictive distributions under each of the
-restricted likelihood methods are comparable. Surprisingly, despite the poor
-inference on $\beta$ under LMS, the predictive distribution is
-\green{concentrated more sharply} than \green{under} the other restricted likelihood methods. This is
-related to its posterior of $\sigma^{2}$ seen in
-Figure \ref{fig:newcombSig2}  which is the tightest
-distribution and shifted the most to the left. 
-% However, this is likely a consequence of the scale estimator chosen for the conditioning.
+%
+%The marginal posteriors for $\beta$ and $\sigma^{2}$ as well as the
+%predictive distribution \eqref{RestrictedpredDist} under each model
+%are displayed in Figures
+%\ref{fig:newcombBeta}-\ref{fig:newcombPred}. Both of the two small
+%outliers and the normal prior on $\beta$ centered at $23.6$ are
+%influential in the results. The normal theory model is most
+%drastically affected with the posterior of $\beta$ being pulled
+%towards the prior and outliers. Inference on $\sigma^{2}$ under this
+%model is impacted by the outliers (see Figure
+%\ref{fig:newcombSig2}) \green{resulting in overestimation of $\sigma^{2}$}. 
+%The heavy-tailed model as well as the
+%restricted likelihood methods with LTS, Huber's, and Tukey's summary
+%statistics are less influenced by the outliers and priors. The
+%marginal posteriors for $\beta$ are closer to the center of the
+%non-outlying data. Inference on the variance parameter also more
+%closely reflects the variance information in this part of the data
+%(the mean and variance of the data without the two outliers are $27.8$
+%and $25.8$, respectively). The posterior of $\beta$ under LTS is
+%slightly more dispersed than under the two M-estimator methods. This is
+%also reflected in the variance parameter in that under LTS the posterior distribution \green{concentrates on 
+%slightly larger values of $\sigma^2$} % is slightly higher. 
+%While LMS has high breakdown, it has been more drastically affected by the normal prior centered at $23.6$ than the others. This is % likely 
+%because LMS achieves high breakdown by discounting much of the information in the data. 
+%
+%Though inference for the main parameter of interest ($\beta$) is
+%similar between the traditional heavy-tailed approach and the new
+%method with LTS, Huber's, and Tukey's summary statistics,  the
+%traditional heavy-tailed method has the disadvantage of less precise
+%predictive capability. This is reflected in the heavier tails of its
+%predictive distribution  \eqref{RestrictedpredDist} seen in Figure
+%\ref{fig:newcombPred} (plotted are the log predictive \green{densities} %distributions
+%under each method). The predictive distributions under each of the
+%restricted likelihood methods are comparable. Surprisingly, despite the poor
+%inference on $\beta$ under LMS, the predictive distribution is
+%\green{concentrated more sharply} than \green{under} the other restricted likelihood methods. This is
+%related to its posterior of $\sigma^{2}$ seen in
+%Figure \ref{fig:newcombSig2}  which is the tightest
+%distribution and shifted the most to the left. 
+%% However, this is likely a consequence of the scale estimator chosen for the conditioning.
 Recall it involves a correction factor which is chosen asymptotically.
@@
 Is it similar to the bending constant for $\psi$?]}
-
-%\red{[I suggest to omit the following paragraphs given that the second last paragraph in the previous section (``the key to the productive ...'') has similar discussions already.]} This simple example raises many questions regarding the proposed method.
+%
+%%\red{[I suggest to omit the following paragraphs given that the second last paragraph in the previous section (``the key to the productive ...'') has similar discussions already.]} This simple example raises many questions regarding the proposed method.
 The first of which is how to choose the summary statistic.
@@
 This resulted in a posterior for $\beta$ which closely resembled that of LMS.
-
-%Other questions may be posed by the reader and addressing each of these is beyond the scope of this paper.
+%
+%%Other questions may be posed by the reader and addressing each of these is beyond the scope of this paper.
 Instead we focus on introducing the method and deriving a computational strategy that will allow such models to be fit to higher dimensional problems with a large class of summary statistics.
 It is our hope that this computational strategy will facilitate the study of further questions regarding the method.
-
-\begin{sidewaysfigure}
-\centering
-\captionsetup{justification=centering}
-\subcaptionbox{\label{fig:newcombBeta}}{\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}}\quad
-\subcaptionbox{\label{fig:newcombSig2}}{\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}}\quad
-\subcaptionbox{\label{fig:newcombPred}}{\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}}
-\caption{Clockwise from top left: (a) marginal posteriors of $\beta$ (b) marginal posteriors for $\sigma^{2}$ (c) log predictive distributions.}
-\label{fig:newcomb}
-\end{sidewaysfigure}
-
+%
 %\begin{sidewaysfigure}
-%\begin{subfigure}[b]{.5\linewidth}
+%\centering
 %\captionsetup{justification=centering}
-%\centering 
-%\caption{}\label{fig:newcombBeta}
-%\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}
-%\end{subfigure}
-%\quad
-%\begin{subfigure}[b]{.5\linewidth}
-%\captionsetup{justification=centering}
-%\centering
-%\caption{}\label{fig:newcombSig2}
-%\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}
-%\end{subfigure}
-%\quad
-%\begin{subfigure}[b]{.5\linewidth}
-%\captionsetup{justification=centering}
-%\centering
-%\caption{}\label{fig:newcombPred}
-%\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}
-%\end{subfigure}
-
-%\caption{Clockwise from top left: (a) marginal posteriors of $\beta$. (b) marginal posteriors for $\sigma^{2}$. (c) log predictive distributions.}
+%\subcaptionbox{\label{fig:newcombBeta}}{\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}}\quad
+%\subcaptionbox{\label{fig:newcombSig2}}{\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}}\quad
+%\subcaptionbox{\label{fig:newcombPred}}{\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}}
+%\caption{Clockwise from top left: (a) marginal posteriors of $\beta$ (b) marginal posteriors for $\sigma^{2}$ (c) log predictive distributions.}
 %\label{fig:newcomb}
 %\end{sidewaysfigure}
-
-%\textcolor{blue}{if we add the Newcomb and Belgium Calls data examples, this might be a good place to add them because they are low dimensional.
+%
+%
+%%\begin{sidewaysfigure}
+%%\begin{subfigure}[b]{.5\linewidth}
+%%\captionsetup{justification=centering}
+%%\centering 
+%%\caption{}\label{fig:newcombBeta}
+%%\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}
+%%\end{subfigure}
+%%\quad
+%%\begin{subfigure}[b]{.5\linewidth}
+%%\captionsetup{justification=centering}
+%%\centering
+%%\caption{}\label{fig:newcombSig2}
+%%\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}
+%%\end{subfigure}
+%%\quad
+%%\begin{subfigure}[b]{.5\linewidth}
+%%\captionsetup{justification=centering}
+%%\centering
+%%\caption{}\label{fig:newcombPred}
+%%\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}
+%%\end{subfigure}
+%
+%%\caption{Clockwise from top left: (a) marginal posteriors of $\beta$. (b) marginal posteriors for $\sigma^{2}$. (c) log predictive distributions.}
+%%\label{fig:newcomb}
+%%\end{sidewaysfigure}
+%
+%
+%
+%%\textcolor{blue}{if we add the Newcomb and Belgium Calls data examples, this might be a good place to add them because they are low dimensional.
 I think it would be a good lead into the high dimensional computational strategies}
+%
+%
 
@@
 \label{BayesLinMod}
+
+The simple examples in the previous section highlight that productive use of the restricted likelihood relies on a good choice of $T(\by)$.
+This work focuses on robustness in linear models where natural choices include many used above:  M-estimators in the tradition of \cite{huber1964}, least median squares (LMS), and least trimmed squares (LTS).
+For these choices the restricted likelihood is not available in closed form, making computation of the restricted posterior a challenge.
+For low-dimensional statistics $T(\by)$ and parameters $\bth$, direct computational strategies described in \cite{lewis2014} can be used to estimate the restricted posterior conditioned on essentially any statistic.
+These strategies rely on density estimation $f(T(\by)|\theta)$ using samples of $T(\by)$ for many values of $\theta$; a strategy which breaks down in higher dimensions.
+This section outlines a data-augmented MCMC algorithm that can be applied to the Bayesian linear model when $T(\by)$ consists of estimates of the regression coefficients and scale parameter.
 
@@
 \end{eqnarray}
-where $x_i$ and $\bbeta \in \mathbb{R}^p$, \green{$\sigma^2 \in \mathbb{R}^+$}, 
-and the $\epsilon_i$ are independent 
-draws from a distribution with center $0$ and scale $\sigma$.
-Two conditions are imposed on the model:
+where $x_i$ and $\bbeta \in \mathbb{R}^p$, $\sigma^2 \in \mathbb{R}^+$, 
+and the $\epsilon_i$ are independent draws from a distribution with center $0$ and scale $\sigma$. $X$ denotes the design matrix whose rows are  $x_i^\top$.
+
+For the MCMC algorithm,  conditioning statistics are assumed to be of the form $T(\by) = (\bb(X, \by), s(X, \by)$ where $\bb(X, \by)\in \mathbb R^{p}$ is an estimator for the regression coefficients and $s(X, \by)\in \{0\} \cup {\mathbb R}^+$ is an estimator of the scale.
+Throughout, observed data and summary statistic is denoted by $\by_{obs}$ and $T(\by_{obs})=(\bb(X, \by_{obs}), s(X, \by_{obs}))$, respectively.
+
+% In particular, we demonstrate the method using simultaneous M-estimators defined by \eqref{Mest} for the one-sample setting and easily extended to the linear model in \eqref{LinearModel}.
+The estimator of the \green{regression} coefficients is denoted by $\bb(X, \by)\in \mathbb R^{p}$ and that of the scale by \green{\sout{$s(X, \by)\in \mathbb R$} $s(X, \by)\in \{0\} \cup {\mathbb R}^+$} .
+Thus, $T(\by)=(\bb(X, \by), s(X, \by))$.
+
+Several conditions are imposed on the model and statistic to ensure validity of the MCMC algorithm:
 \begin{itemize}
@@
 respect to Lebesgue measure on the real line and for which the support is the real line.  
+\labitem{C3}{asb}$\bb(X,\by)$ is almost surely continuous and differentiable with respect to $\by$.  
+\labitem{C4}{as} $s(X,\by)$ is almost surely positive, continuous, and differentiable with respect to $\by$.  
+\labitem{C5}{regEq} $\bb(X,\by+X\bv)=\bb(X,\by)+\bv \ \ \text{for  all}\ \bv\in\mathbb{R}^p$. 
+\labitem{C6}{scaleEqReg} $\bb(X,a\by)=a\bb(X,\by)\ \ \ \text{for all constants } a$.  
+\labitem{C7}{regIn} $s(X,\by+X\bv)=s(X,\by) \ \ \text{for all}\ \bv\in\mathbb{R}^p$.  
+\labitem{C8}{scaleEq2Reg} $s(X, a\by)=|a|s(X,\by) \ \ \text{for all constants } a$.  
 \end{itemize}
+Properties \ref{regEq} and \ref{scaleEqReg} of $\bb$ are called
+\textit{regression} and \textit{scale equivariance},
+respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
+and \textit{scale equivariance}. 
+Many estimators satisfy the above properties, including simultaneous M-estimators \citep{huber2009, maronna2006} for which the R package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC.
+Further software development is required to extend the MCMC implementation beyond these M-estimators.
+The package also implements the direct computational methods described in \cite{lewis2014}.
+These methods are effective in lower dimensional problems and were used in several of the examples in Section \ref{illustrations}.
+
+%The strategy described in the previous paragraph extends to full-blown regression models.
+Robust regression methods lead naturally to a conditioning statistic in the form of a classical M-estimator for $\bbeta$
+%and a companion estimator for $\sigma$.  We denote the resulting estimator which involves the covariates through
+%the design matrix and the response 
+%as $T(\by) = (\bb(X,\by), s(X,\by))$, with $\bb(X,\by) = (b_1(X,\by), \cdots,
+%b_p(X,\by))^\top$.  Simultaneous M-estimators have a number of standard properties \ref{asb}-\ref{scaleEq2Reg} which
+%prove useful in the sequel \citep{huber2009, maronna2006}.  
+%\begin{itemize}
+%\labitem{C3}{asb}$\bb(X,\by)$ is almost surely continuous and differentiable with respect to $\by$.  
+%\labitem{C4}{as} $s(X,\by)$ is almost surely positive, continuous, and differentiable with respect to $\by$.  
+%\labitem{C5}{regEq} $\bb(X,\by+X\bv)=\bb(X,\by)+\bv \ \ \text{for  all}\ \bv\in\mathbb{R}^p$. 
+%\labitem{C6}{scaleEqReg} $\bb(X,a\by)=a\bb(X,\by)\ \ \ \text{for all constants } a$.  
+%\labitem{C7}{regIn} $s(X,\by+X\bv)=s(X,\by) \ \ \text{for all}\ \bv\in\mathbb{R}^p$.  
+%\labitem{C8}{scaleEq2Reg} $s(X, a\by)=|a|s(X,\by) \ \ \text{for all constants } a$.  
+%\end{itemize}
+
+%Properties \ref{regEq} and \ref{scaleEqReg} of $\bb$ are called
+%\textit{regression} and \textit{scale equivariance},
+%respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
+%and \textit{scale equivariance}. 
+%Many other estimators satisfy these properties, and our subsequent results apply equally
+%well to them.  With more cumbersome statements, the upcoming results can be adjusted to handle 
+%a relaxation of \ref{as} that 
+%$s(X,\by_{obs}) > 0$ and $P(s(X,\by)>0)>0$.  
+%
 
@@
 %and $\sigma^2$. 
-As summary statistics for the data, we concentrate on robust estimators for the 
-\green{regression} coefficients in the linear model and an associated 
-estimator of the scale.
+%
+%
+%As summary statistics for the data, we concentrate on robust estimators for the 
+%\green{regression} coefficients in the linear model and an associated 
+%estimator of the scale.
 In particular, we demonstrate the method using simultaneous M-estimators defined by \eqref{Mest} for the one-sample setting and easily extended to the linear model in \eqref{LinearModel}.
@@
 The observed complete data is denoted by $\by_{obs}$ with observed statistic  denoted by $T(\by_{obs})=(\bb(X, \by_{obs}), s(X, \by_{obs}))$.
+
 %Assumption \ref{supReal} is important as it translates into a continuous distribution for $\bb(X, \by)$ and $s(X, \by)$ (with respect to $\by$), which is presumed for our computational strategy described below.
@@
 
-As mentioned above, direct computational strategies designed to approximate the restricted posterior break down for high-dimensional statistics $T(\by)$ or high-dimensional parameters $\bth$.
+%As mentioned above, direct computational strategies designed to approximate the restricted posterior break down for high-dimensional statistics $T(\by)$ or high-dimensional parameters $\bth$.
 %, direct computational strategies break down.
 When the conditioning statistic is of high-dimension, density estimation becomes difficult and the associated approximate update in (\ref{RestrictedPosterior}) is unstable; when $\bth$is high dimensional, grid-based calculation and other numerical integration strategies fail.
-However, Markov chain Monte Carlo (MCMC) methods were developed for exactly these situations.  We turn to MCMC to 
-fit the model in these circumstances.
+%However, Markov chain Monte Carlo (MCMC) methods were developed for exactly these situations.  We turn to MCMC to 
+%fit the model in these circumstances.
 

### 2018-08-12 revision_1/code/speed_of_light/mix.data.R

@@ -1,11 +1,12 @@
 N <- 66
 y <- 
-c(28, -44, 29, 30, 24, 28, 37, 32, 36, 27, 26, 28,
-29, 26, 27, 22, 23, 20, 25, 25, 36, 23, 31, 32, 24, 27,
-33, 16, 24, 29, 36, 21, 28, 26, 27, 27, 32, 25, 28, 24,
-40, 21, 31, 32, 28, 26, 30, 27, 26, 24, 32, 29, 34, -2,
-25, 19, 36, 29, 30, 22, 28, 33, 39, 25, 16, 23)
-eta <- 0
-tau <- 50
+c(28, -44, 29, 30, 24, 28, 37, 32, 36, 27, 26,
+28, 29, 26, 27, 22, 23, 20, 25, 25, 36, 23, 31, 32,
+24, 27, 33, 16, 24, 29, 36, 21, 28, 26, 27, 27, 32,
+25, 28, 24, 40, 21, 31, 32, 28, 26, 30, 27, 26, 24,
+32, 29, 34, -2, 25, 19, 36, 29, 30, 22, 28, 33, 39,
+25, 16, 23)
+eta <- 23.6
+tau <- 2.04
 a <- 5
 b <- 10

### 2018-08-15 revision_1/paper.tex
revisions to the proposal density derivation sections

@@
 
-For the MCMC algorithm,  conditioning statistics are assumed to be of the form $T(\by) = (\bb(X, \by), s(X, \by)$ where $\bb(X, \by)\in \mathbb R^{p}$ is an estimator for the regression coefficients and $s(X, \by)\in \{0\} \cup {\mathbb R}^+$ is an estimator of the scale.
+For the restricted likelihood model,  conditioning statistics are assumed to be of the form $T(\by) = (\bb(X, \by), s(X, \by))$ where $\bb(X, \by)= (b_1(X,\by), \dots,b_p(X,\by))^\top\in \mathbb R^{p}$ is an estimator for the regression coefficients and $s(X, \by)\in \{0\} \cup {\mathbb R}^+$ is an estimator of the scale.
 Throughout, observed data and summary statistic is denoted by $\by_{obs}$ and $T(\by_{obs})=(\bb(X, \by_{obs}), s(X, \by_{obs}))$, respectively.
-
 % In particular, we demonstrate the method using simultaneous M-estimators defined by \eqref{Mest} for the one-sample setting and easily extended to the linear model in \eqref{LinearModel}.
@@
 Thus, $T(\by)=(\bb(X, \by), s(X, \by))$.
-
 Several conditions are imposed on the model and statistic to ensure validity of the MCMC algorithm:
@@
 and \textit{scale equivariance}. 
-Many estimators satisfy the above properties, including simultaneous M-estimators \citep{huber2009, maronna2006} for which the R package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC.
+Many estimators satisfy the above properties, including simultaneous M-estimators \citep{huber2009, maronna2006} for which the R package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC described here.
 Further software development is required to extend the MCMC implementation beyond these M-estimators.
@@
 % \textcolor{blue}{some major changes from here to the end of the section}
-The general style of algorithm that we present is a data augmented
-MCMC algorithm targeting $f(\bth, \by |
+The general style of algorithm we present is a data augmented
+MCMC targeting $f(\bth, \by |
 T(\by)=T(\by_{obs}))$, the joint distribution of $\bth$ and the full
-data given the summary statistic $T(\by_{obs})$.  % with $\by_{obs}$  representing the observed complete data. 
+data given the summary statistic $T(\by_{obs})$. 
  The Gibbs sampler \citep{gelfand1990} iteratively samples from the
- full conditionals $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ and
- $f(\by|\bth, T(\by)=T(\by_{obs}))$.  
-\green{Alternative algorithms substitute other generations for the full conditionals, such as the Metropolis-Hastings propose and accept/reject framework.
+ full conditionals 
+ \begin{enumerate}
+ \item $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ 
+ \item $f(\by|\bth, T(\by)=T(\by_{obs}))$.  
+ \end{enumerate}
+When $\by$ has the summary statistic $T(\by) = T(\by_{obs})$,
+the first full conditional is the same as the full data posterior $\pi(\bth|\by)$.
+In this case, the condition $T(\by) = T(\by_{obs})$ is redundant.
+This allows us to make use of conventional MCMC steps for this generation.
+For typical regression models, algorithms abound.
+Details of the recommended algorithms depend on details of
+the prior distribution and sampling density and we assume this can be done \citep[see e.g.,][]{liu1994, liang2008}.
+
+%As examples, a normal
+%prior distribution and normal likelihood in the regression setting
+%allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
+%leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
+%in the style of the hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
+%$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
+%a scale parameter for each case and an extra stage where these scale parameters are generated.
+
+%\green{Alternative algorithms substitute other generations for the full conditionals, such as the Metropolis-Hastings propose and accept/reject framework.
 Our algorithms are based on the decomposition of the MCMC algorithm into conventional full data sampling steps where $\bth$ is generated given $\by$, and steps that allow us to complete the data set where $\by$ is generated given $\bth$ and $T(\by)$.
@@
 The set $\mathcal{A}$ may contain more than one element (i.e., it is not degenerate) when $T(\by) : \by \rightarrow T(\by)$ is not a $1-1$ function.}
-%\red{\sout{, where the two
-%     conditioning sets are not degenerate (that is, $\by$ is such that
-%     $T(\by)=T(\by_{obs})$).}}  \red{Unless $T(\by)=\by$, the set
-%   $\mathcal{A}=\{\by\in \mathbb{R}^n|T(\by)=T(\by_{obs})\}$
-%   is not degenerate, containing more elements than $\by_{obs}$ only.}
-
-When $\by$ has the summary statistic \sout{$T(\by)$ matching $T(\by_{obs})$,} \green{$T(\by) = T(\by_{obs})$,}
-the first full conditional, $\pi(\bth|\by, T(\by)=T(\by_{obs}))$, is
-\red{the same as} the full data posterior
-$\pi(\bth|\by)$. 
-\green{In this case, the condition $T(\by) = T(\by_{obs})$ is redundant.  This allows us to make use of conventional MCMC steps for this generation.  For} 
-\sout{In the case of} typical regression models, algorithms abound.  Details of the \green{recommended} algorithms depend on details of
-the prior distribution and sampling density.  As examples, a normal
-prior distribution and normal likelihood in the regression setting
-allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
-leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
-in the style of the 
-hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
-$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
-a scale parameter for each case and an extra stage where these scale parameters are generated.
 
@@
 %where we generate $\by | \bth, T(\by)$.  
-For a typical model and conditioning statistic, the second full conditional $f(\by|\bth, T(\by)=T(\by_{obs}))\blue{ =f(\by|\bth, \by\in\mc A)}$ is not available in closed form.  
-As a consequence, we turn to Metropolis-Hastings \citep{hastings1970},
-using the strategy of proposing full data $\by$ \green{\sout{in the sample
-space of the distribution} for which $T(\by) = T(\by_{obs})$} and either accepting or rejecting the
-proposal. Let $\by_p$ and  $\by_c$ represent the proposed and current
+For a typical model and conditioning statistic, the second full conditional $f(\by|\bth, T(\by)=T(\by_{obs}))$ %\blue{ =f(\by|\bth, \by\in\mc A)}$ 
+is not available in closed form.  We turn to Metropolis-Hastings \citep{hastings1970},
+using the strategy of proposing full data $\by \in \mathcal{A}:=\{\by \in \mathbb{R}^n | T(\by)=T(\by_{obs})\}$ from a well defined distribution with support $\mathcal{A}$ and either accepting or rejecting the
+proposal. Let $\by_p, \by_c \in \mathcal{A}$ represent the proposed and current
 full data, respectively.
-\green{In subsequent algorithms, we propose only from the set $\mathcal{A}$}.
-Denote the proposal distribution for $\by_{p}$ by $p(\by_p|\bth,T(\by_p) = T(\by_{obs})) \green{ = p(\by_p|\bth,\by_p \in \mathcal{A}) = p(\by_p | \bth)}$.
-\green{The last equality follows from the fact that our $p(\cdot | \bth)$ assigns probability one to the event $\{ \by_p \in \mathcal{A} \}$.
+Denote the proposal distribution for $\by_{p}$ by $p(\by_p|\bth,T(\by_p) = T(\by_{obs})) = p(\by_p|\bth,\by_p \in \mathcal{A}) = p(\by_p | \bth)$.
+The last equality follows from the fact that our $p(\cdot | \bth)$ assigns probability one to the event $\{ \by_p \in \mathcal{A} \}$.
 These equalities still hold if the dummy argument $\by_p$ is replaced with $\by_c$.
@@
 \end{eqnarray*}
-for $\by \in \mathcal{A}$.  This includes both $\by_p$ and $\by_c$.  
-}
-
-The Metropolis-Hastings acceptance probability  is the minimum of 1 and $R$ where,
+for $\by \in \mathcal{A}$.  This includes both $\by_p$ and $\by_c$.  The Metropolis-Hastings acceptance probability  is the minimum of 1 and $R$ where,
 \begin{eqnarray}
@@
 R & = & \frac{f(\by_p|\bth,\by_p \in \mathcal{A})}{f(\by_c|\bth,\by_c \in \mathcal{A})}  
-                \green{\frac{p(\by_c|\bth, \by_c \in \mathcal{A})}{p(\by_p|\bth,\by_p \in \mathcal{A})}} \\
+                \frac{p(\by_c|\bth, \by_c \in \mathcal{A})}{p(\by_p|\bth,\by_p \in \mathcal{A})} \\
   & = & \frac{f(\by_p | \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} \frac{\int_\mathcal{A} f(\by | \bth) d\by}{f(\by_c | \bth)} \frac{p(\by_c | \bth)}{p(\by_p | \bth)} \\
@@
 \end{eqnarray}
-\green{Note:  Above expression changed.  Check argument again.}
 %In the above expression, the second line follows from the first for
@@
 %\green{Note:  Check this argument carefully}
-
 For the models we consider, evaluation of $f(\by | \bth)$ is straightforward.
-Therefore, the difficulty in implementing this Metropolis-Hastings step manifests  itself in the ability to simulate proposals that guarantee $T(\by) = T(\by_{obs})$ and on the evaluation of the proposal density derived from the method used to simulate $\by$.
+Therefore, the difficulty in implementing this Metropolis-Hastings step manifests  itself in the ability to both simulate from and evaluate $p(\by_p | \bth)$; the well defined distribution with support $\mathcal{A}$.
 We now discuss such an implementation method for the linear model in \eqref{LinearModel}.
@@
 %\textcolor{blue}{some major revisions as indicated in the responseToReferees}
-Our \green{computational} strategy is easiest to envision in a location-scale setting where 
-the design matrix in model (\ref{LinearModel}) consists of a single column of ones.  Robust estimation techniques along
-with model (\ref{LinearModel}) suggest a conditioning statistic $T(\by)$ which consists of
-estimates of the scalars $\beta$ and $\sigma$, say $T(\by)=(b(X,\by),
-s(X,\by))$.  It is not a simple matter to directly sample the required
-proposal $\by$ satisfying $T(\by)=T(\by_{obs})$. However, 
-  with equivariance/invariance properties of $T(\by)$, we will see in Theorem \ref{Transformation} below
-    that it is possible to scale and shift any \sout{$\bz^{*}\in \mathbb R^{n}$} \green{$\bz^{*}$ which generates 
-a positive scale estimate} to such a
-    $\by$. Hence, to obtain $\by$ from $\mathcal A$, we proceed
-  in two steps. First, a vector $\bz^*$ is sampled from a known
-  distribution (examples of which are described later). This vector has summary statistic   
-$T(\bz^*) = (b(X,\bz^*), s(X,\bz^*))$ which may not match the observed summary
-$T(\by_{obs})$.  Second, $\bz^*$ is mapped into $\by =h(\bz^*)$
-using Theorem \ref{Transformation} so that $T(\by)=T(\by_{obs})$. To
-evaluate the proposal density $p(\by|\bth)$, we need to adjust
-the known density of $\bz^*$, $p(\bz^*)$, with the Jacobian of
-the transformation $h(\cdot)$ to $\by$. We choose the
-distribution of the \green{\sout{intermediate}} data vector $\bz^*$ to have support
-\green{on a subset of $\mathbb R^n$ so that}
-the transformation to $\by$ is one-to-one and the Jacobian,
-$\displaystyle \left|\frac{\partial h^{-1}(\by)}{\partial \by}\right|$, can be computed from first principles.
-It is the calculation of this Jacobian which is described in the section.
-We will repeatedly return to an artificial low-dimensional example in the location-scale setting to help visualize this calculation.
-
+Our computational strategy relies on proposing $\by$ such that $T(\by) = T(\by_{obs})$ where $T(\cdot) = (\bb(X, \cdot), s(X, \cdot))$ satisfies the conditions \ref{asb}-\ref{scaleEq2Reg}.
+It is not a simple matter to do this directly, but with the specified conditions, it is possible to scale and shift any $\bz^{*}$ which generates
+a positive scale estimate to such a $\by$ via the following Theorem whose proof is in the appendix. 
+\begin{theorem}
+\label{Transformation}
+Assume that conditions \ref{as}-\ref{scaleEq2Reg} hold.  Then, any vector $\bz^* \in \mathbb{R}^n$ with conditioning statistic
+$T(\bz^*)$ for which $s(X,\bz^*) > 0$ can be transformed into $\by$ with conditioning statistic $T(\by) = T(\by_{obs})$ 
+through the transformation 
+\[
+\by = h(\bz^*) := \frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^* + X\left(\bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^*)\right) .  
+\]
+\end{theorem}
+% (details are given in Theorem \ref{Transformation} below). Hence, to obtain $\by \in\mathcal A$, we proceed in two steps:
+%\begin{enumerate}
+%\item Sample $\bz^*\in \mathbb{R}^{n}$ from a known distribution (examples of which are described later).
+%\item Transform $\bz^*$ to $\by =h(\bz^*)$ using Theorem \ref{Transformation} so that $T(\by)=T(\by_{obs})$. 
+%\end{enumerate}
 % To 
@@
 %example to illustrate the method.  
-
-The strategy described in the previous paragraph extends to full-blown regression models.
+%The strategy described in the previous paragraph extends to full-blown regression models.
 Robust regression methods lead naturally to a conditioning statistic in the form of a classical M-estimator for $\bbeta$
-and a companion estimator for $\sigma$.  We denote the resulting estimator which involves the covariates through
-the design matrix and the response 
-as $T(\by) = (\bb(X,\by), s(X,\by))$, with $\bb(X,\by) = (b_1(X,\by), \cdots,
-b_p(X,\by))^\top$.  Simultaneous M-estimators have a number of standard properties \ref{asb}-\ref{scaleEq2Reg} which
-prove useful in the sequel \citep{huber2009, maronna2006}.  
-\begin{itemize}
-\labitem{C3}{asb}$\bb(X,\by)$ is almost surely continuous and differentiable with respect to $\by$.  
-\labitem{C4}{as} $s(X,\by)$ is almost surely positive, continuous, and differentiable with respect to $\by$.  
-\labitem{C5}{regEq} $\bb(X,\by+X\bv)=\bb(X,\by)+\bv \ \ \text{for  all}\ \bv\in\mathbb{R}^p$. 
-\labitem{C6}{scaleEqReg} $\bb(X,a\by)=a\bb(X,\by)\ \ \ \text{for all constants } a$.  
-\labitem{C7}{regIn} $s(X,\by+X\bv)=s(X,\by) \ \ \text{for all}\ \bv\in\mathbb{R}^p$.  
-\labitem{C8}{scaleEq2Reg} $s(X, a\by)=|a|s(X,\by) \ \ \text{for all constants } a$.  
-\end{itemize}
-Properties \ref{regEq} and \ref{scaleEqReg} of $\bb$ are called
-\textit{regression} and \textit{scale equivariance},
-respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
-and \textit{scale equivariance}. 
-Many other estimators satisfy these properties, and our subsequent results apply equally
-well to them.  With more cumbersome statements, the upcoming results can be adjusted to handle 
-a relaxation of \ref{as} that 
-$s(X,\by_{obs}) > 0$ and $P(s(X,\by)>0)>0$.
-
-We have stated that any vector $\bz^{*} \in \mathbb{R}^n$ can be transformed to a proposal
-$\by$ satisfying $T(\by) = T(\by_{obs})$.  The properties above ensure
-that this can be done through the mechanism presented in the following theorem.  The proof of this and other results appear in the appendix.
-\begin{theorem}
-\label{Transformation}
-Assume that conditions \ref{as}-\ref{scaleEq2Reg} hold.  Then, any vector $\bz^* \in \mathbb{R}^n$ with conditioning statistic
-$T(\bz^*)$ \green{for which $s(X,\bz^*) > 0$} can be transformed into $\by$ with conditioning statistic $T(\by) = T(\by_{obs})$ 
-through the transformation 
-\[
-\by = \frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^* + X\left(\bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^*)\right) .  
-\]
-\end{theorem}
-The mapping described in the theorem is many-to-one in general.
-Its range is the collection of data sets which match
-the observed summary statistic:
-\begin{equation}
-\label{sampleSpace}
- \mathcal{A}=\{\by\in \mathbb{R}^n | T(\by)=T(\by_{obs})\}.
-\end{equation}
-To see this, note that the theorem shows that any $\by$ expressed as in the theorem is an element of $\mc A$.
-Further, any $\by \in \mc A$ can be expressed as in the theorem by simply replacing $\bz^{*}$ with $\by$.
-That is, any vector already in $\mc A$ requires no shifting or scaling.
-The set $\mathcal{A}$ is an $n - p - 1$ dimensional space:
-there are $p$ constraints imposed by the regression coefficients and one further constraint imposed by the scale.  
-The form of the set is determined by the statistic $T(\cdot)$.  Figure~\ref{fig:sampSpace} 
-provides an artificial low-dimensional
-visualization of such a set $\mathcal{A}$ with a location-scale
-  model.  In the figure, $n = 3$, and the conditioning
-statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$. The
-set $\mathcal{A}$ is depicted  for $T(\by_{obs})=(0,1)$ and is a
-``warped triangle'' in light blue, with each side
-corresponding to a particular coordinate of $\by$ being the minimum
-value \green{of} zero. The other two coordinates are restricted by the scale
-statistic to lie on the quarter circle of radius one in the positive
-orthant. In general, this set may be compact and given by a closed
-curve, as in the figure, or it may be unbounded, depending on the
-  choice of $T(\by)$.  The other sets labeled in the figure will be described shortly.
+%and a companion estimator for $\sigma$.  We denote the resulting estimator which involves the covariates through
+%the design matrix and the response 
+%as $T(\by) = (\bb(X,\by), s(X,\by))$, with $\bb(X,\by) = (b_1(X,\by), \cdots,
+%b_p(X,\by))^\top$.  Simultaneous M-estimators have a number of standard properties \ref{asb}-\ref{scaleEq2Reg} which
+%prove useful in the sequel \citep{huber2009, maronna2006}.  
+%\begin{itemize}
+%\labitem{C3}{asb}$\bb(X,\by)$ is almost surely continuous and differentiable with respect to $\by$.  
+%\labitem{C4}{as} $s(X,\by)$ is almost surely positive, continuous, and differentiable with respect to $\by$.  
+%\labitem{C5}{regEq} $\bb(X,\by+X\bv)=\bb(X,\by)+\bv \ \ \text{for  all}\ \bv\in\mathbb{R}^p$. 
+%\labitem{C6}{scaleEqReg} $\bb(X,a\by)=a\bb(X,\by)\ \ \ \text{for all constants } a$.  
+%\labitem{C7}{regIn} $s(X,\by+X\bv)=s(X,\by) \ \ \text{for all}\ \bv\in\mathbb{R}^p$.  
+%\labitem{C8}{scaleEq2Reg} $s(X, a\by)=|a|s(X,\by) \ \ \text{for all constants } a$.  
+%\end{itemize}
+%Properties \ref{regEq} and \ref{scaleEqReg} of $\bb$ are called
+%\textit{regression} and \textit{scale equivariance},
+%respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
+%and \textit{scale equivariance}. 
+%Many other estimators satisfy these properties, and our subsequent results apply equally
+%well to them.  With more cumbersome statements, the upcoming results can be adjusted to handle 
+%a relaxation of \ref{as} that 
+%%$s(X,\by_{obs}) > 0$ and $P(s(X,\by)>0)>0$.  
+%To understand the Jacobian calculation, we start with the following Theorem whose proof is in the appendix. 
+%%We have stated that any vector $\bz^{*} \in \mathbb{R}^n$ can be transformed to a proposal
+%%$\by$ satisfying $T(\by) = T(\by_{obs})$.  The properties above ensure
+%%that this can be done through the mechanism presented in the following theorem.  The proof of this and other results appear in the appendix.
+%\begin{theorem}
+%\label{Transformation}
+%Assume that conditions \ref{as}-\ref{scaleEq2Reg} hold.  Then, any vector $\bz^* \in \mathbb{R}^n$ with conditioning statistic
+%$T(\bz^*)$ for which $s(X,\bz^*) > 0$ can be transformed into $\by$ with conditioning statistic $T(\by) = T(\by_{obs})$ 
+%through the transformation 
+%\[
+%\by = h(\bz^*) := \frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^* + X\left(\bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^*)\right) .  
+%\]
+%\end{theorem}
+Using the theorem, the general idea is to first start with a sample $\bz^*$ from a known distribution, say $p(\bz^*)$, and transform via $h(\cdot)$ to $\by \in \mathcal{A}$.
+The proposal density $p(\by|\bth)$ is then a change-of-variables adjustment on $p(\bz^*)$ derived from $h(\cdot)$.
+%To evaluate the proposal density $p(\by|\bth)$, we need to adjust the known density of $\bz^*$, $p(\bz^*)$, with the Jacobian of the transformation $h(\cdot)$ to $\by$. We choose the
+%distribution of $\bz^*$ to have support on a subset of $\mathbb R^n$ so that
+%the transformation to $\by$ is one-to-one and the Jacobian, $\displaystyle \left|\frac{\partial h^{-1}(\by)}{\partial \by}\right|$, can be computed directly.  
+In general however, the mapping $h()$ is many-to-one: for any $\bv\in \mathbb{R}^{n}$ and any $c\in \mathbb{R}^{+}$, $c\bz^{*} + X\bv$ map to the same $\by$.
+This makes the change-of-variables adjustment difficult.
+%The set $\mathcal{A}$ typically does not lie in a linear space of dimension $n - p - 1$, and 
+%so we must account for both the many-to-one nature of the mapping $h(\dot)$ and
+%a Jacobian when deriving the proposal density.  
+We handle this point by first noticing that the set $\mathcal{A}$ is an $n - p - 1$ dimensional space:  there are $p$ constraints imposed by the regression coefficients and one further constraint imposed by the scale.
+Hence, we restrict the initial $\bz^*$ to an easily understood $n - p - 1$ dimensional space.
+Specifically, this space is  the unit sphere in the orthogonal complement of the column space of the design matrix.
+Denote the column space and its orthogonal complement with $\mathcal{C}(X)$ and  $\mathcal{C}^{\perp}(X)$, respectively.
+With $\bz^{*}$ on this sphere, $c\bz^{*} + X\bv$ is clearly not (unless $c=1$ and $\bv = \mathbf{0})$ since every point on the sphere is both in  $\mathcal{C}^{\perp}(X)$ and has $||\bz^{*}|| = 1$.
+Thus the mapping has become one-to-one making the change of variables more feasible.
+
+With the domain of $h(\dot)$ restricted to the unit sphere in $\mathcal{C}^{\perp}(X)$, the range is still the entirety of $\mathcal{A}$.
+This is important so that the support of the proposal distribution (i.e.
+the $h(\dot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
+To see that the range of $h(\dot)$ is $\mathcal{A}$, consider any $\by \in \mathcal{A}$ and its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$ \footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).}.
+It is easy to show that $\bz^{*} = Q\by/||Q\by||$ is on the unit sphere and $h(\bz^{*}) = \by$.
+
+Given the one-to-one and onto mapping from the sphere to $\mathcal{A}$, the general proposal strategy is summarized as follows:
+\begin{enumerate}
+\item Sample $\bz^*$ from a distribution with known density on the unit sphere in $\mc{C}^\perp(X)$.
+\item Set $\by = h(\bz^*)$ and calculate the Jacobian of this transformation in two steps.
+\begin{enumerate}
+\item Scale from unit sphere to the set $\Pi(\mathcal{A}):= \{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\ s.t.\ \bz=Q \by \}$.
+This is the projection of $\mathcal{A}$ onto $\mathcal{C}^{\perp}(X)$ and, by condition \ref{regIn}, every element of this set has $s(X, \bz) = s(X, \by_{obs})$.
+Specifically, set $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$.
+There are two pieces of this Jacobian: one for the scaling and one for the mapping of the sphere onto $\Pi(\mathcal{A})$.
+The latter piece is given in equation \eqref{cosine}.
+\item Shift  from $\Pi(\mathcal{A})$ to $\mathcal{A}$: $\by=\bz+X\left(\bb(X, \by_{obs})-\bb(X, \bz)\right)$.
+This shift is along the column space of $X$ to the unique element in $\mathcal{A}$.
+The Jacobian of this transformation is given by equation \eqref{eq:volume}.
+\end{enumerate}
+\end{enumerate}
+The final proposal distribution including the complete Jacobian is given in equation \eqref{dens:ystst} with details in the next section.
+Before giving these details we provide a visualization of each of the sets described above to aid in the understanding of the strategy we are taking.
+Figure~\ref{fig:sampSpace} depicts an artificial low-dimensional location-scale example.
+In the figure, $n = 3$, $p=1$, and the conditioning statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$.
+The set $\mathcal{A}$ is depicted for $T(\by_{obs})=(0,1)$ which we describe as a ``warped triangle'' in light blue, with each side corresponding to a particular coordinate of $\by$ being the minimum value of zero.
+The other two coordinates are restricted by the scale statistic to lie on the quarter circle of radius one in the positive orthant.
+In this example, the column vector $X=\bf{1}$ (shown as a reference) spans $\mc{C}(X)$  and the unit sphere in $\mathcal{C}^{\perp}(X)$ is a unit circle on the orthogonal plane (shown in red).
+This is the sphere from which the initial sample $\bz^{*}$ is taken.
+$\Pi(\mathcal{A})$, the projection of $\mc A$ onto the orthogonal plane is depicted as the bowed triangle in dark blue.
+We will come back to this artificial example in the next section in an attempt to visualize the Jacobian calculations
 
@@
   in the plane defined by $\sum y_i=0$. The circle in this plane
-  represents the sample space for the intermediate sample \green{$\bz^*$}. Also
+  represents the sample space for the intermediate sample $\bz^*$. Also
   depicted is the vector $\mathbf{1}$, the design matrix for the
@@
 
-The set $\mathcal{A}$ typically does not lie in a linear space of dimension $n - p - 1$, and 
-so we must account for both the many-to-one nature of the mapping and
-a Jacobian when deriving the proposal density.  We handle the first
-point by sampling the initial $\bz^*$ from
- a reduced $n - p - 1$ dimensional space which, through the scaling and
-shifting of the above theorem, maps uniquely to a point 
-in $\mathcal{A}$. This reduced space is chosen so that the range of the map is the
-entirety of $\mathcal{A}$.  The Jacobian does not cancel in
-\eqref{MHRatio}, since the scaling depends on the initial proposal.
-
-The reduced space from which the initial sample is taken is simply the
-unit sphere \green{\sout{restricted to} in} the orthogonal complement of the column space of the design matrix (i.e., the least squares residual space).
+%The \green{unit} sphere from
+%which the initial sample is taken is depicted as the red circle in this plane.  In general, this is the unit sphere in the $n-p$ dimensional space $\mc{C}^\perp(X)$.  
+%With the domain of $h(\dot)$ restricted to the unit sphere in $\mathcal{C}^{\perp}(X)$, the range is still the entirety of $\mathcal{A}$.
+This is important so that the support of the proposal distribution (i.e.
+the $h(\dot)$) is at least as large as the support of the target  $f(\by | \theta, y\in \mathcal{A})$, which is  $\mathcal{A}$; a necessary condition for convergence of the Metroplis-Hastings algorithm.
+To see that the range of $h(\dot)$ is $\mathcal{A}$, consider the any $\by \in \mathcal{A}$ and its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$ \footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).}.
+It is easy to show that $\bz^{*} = Q\by/||Q\by||$ is on the unit sphere and $h(\bz^{*}) = \by$.
+%
+%
+%
+%To see this, note that the theorem shows that any $\by$ expressed as in the theorem is an element of $\mc A$.
+Further, any $\by \in \mc A$ can be expressed as in the theorem by simply replacing $\bz^{*}$ with $\by$.
+The set $\mathcal{A}$ is an $n - p - 1$ dimensional space:  there are $p$ constraints imposed by the regression coefficients and one further constraint imposed by the scale.
+The form of the set is determined by the statistic $T(\cdot)$.
+
+%As an example, Figure~\ref{fig:sampSpace} provides an artificial low-dimensional visualization of such a set for a location-scale model.
+In the figure, $n = 3$, and the conditioning statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$.
+The set $\mathcal{A}$ is depicted for $T(\by_{obs})=(0,1)$ which we describe as a ``warped triangle'' in light blue, with each side corresponding to a particular coordinate of $\by$ being the minimum
+%value of zero.
+The other two coordinates are restricted by the scale statistic to lie on the quarter circle of radius one in the positive orthant.
+In general, this set may be compact and given by a closed
+%curve, as in the figure, or it may be unbounded, depending on the choice of $T(\by)$.  The other sets labeled in the figure will be described shortly.
+%
+
+%Further, this reduced space is chosen so that the range of the map is the entirety of $\mathcal{A}$.
+%The Jacobian does not cancel in \eqref{MHRatio}, since the scaling depends on the initial proposal.
+
+%The reduced space from which the initial sample is taken is simply the
+%unit sphere \green{\sout{restricted to} in} the orthogonal complement of the column space of the design matrix (i.e., the least squares residual space).
 To help understand the density of the proposal derived from the transformation of this initial sample we introduce the following notation.
 Denote the column space of the design matrix $X$ by $\mathcal{C}(X)$ and its orthogonal complement by $\mc{C}^\perp(X)$.
-\green{\sout{This} The latter} is the least squares residual space which we will often refer to as the `deviation space'.  The projection of the set $\mathcal{A}$ onto the deviation space is 
-\begin{equation}
-\label{sampleSpacePerp}
-\Pi(\mathcal{A})=\{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\
-s.t.\ \bz=Q \by \}
-\end{equation} 
-where $Q$ is the projection matrix onto  $\mc{C}^\perp(X)$. Explicitly, $Q=I-H$ with $H=XX^\top$ where we assume, without
-loss of generality following condition \ref{fullRank},  that the
-columns of $X$ form an orthonormal basis for $\mc{C}(X)$
-(i.e., $X^\top X=I$).
+%\green{\sout{This} The latter} is the least squares residual space which we will often refer to as the `deviation space'.  The projection of the set $\mathcal{A}$ onto the deviation space is 
+%\begin{equation}
+%\label{sampleSpacePerp}
+%\Pi(\mathcal{A})=\{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\
+%s.t.\ \bz=Q \by \}
+%\end{equation} 
+%where $Q$ is the projection matrix onto  $\mc{C}^\perp(X)$. Explicitly, $Q=I-H$ with $H=XX^\top$ where we assume, without
+%loss of generality following condition \ref{fullRank},  that the
+%columns of $X$ form an orthonormal basis for $\mc{C}(X)$
+%(i.e., $X^\top X=I$).
 It will also be helpful at times to write $Q=WW^{\top}$ where the columns of $W$ form an orthonormal basis for $\mc{C}^\perp(X)$.
@@
 
-Returning to the artificial example, Figure~\ref{fig:sampSpace}
-depicts $\Pi(\mathcal{A})$ as well as the sphere from which we obtain
-the initial sample. The column vector $X=\bf{1}$ spans $\mc{C}(X)$ and
-is shown as a reference. The triangle with bowed sides in dark
-  blue is  $\Pi(\mathcal{A})$, the projection of $\mc A$ onto the
-plane orthogonal to $\mb 1$ (i.e., $\mc{C}^\perp(X)$). The \green{unit} sphere from
-which the initial sample is taken is depicted as the red circle in this plane.  In general, this is the unit sphere in the $n-p$ dimensional space $\mc{C}^\perp(X)$.
-
-For the transformation of the initial proposal $\bz^*$ on the surface of the sphere to $\by\in \mc A$ , we first move to a point on $\Pi(\mathcal{A})$ through a 
-simple scaling of $\bz^*$.  This is followed by undoing the projection with a move from 
-$\Pi(\mathcal{A})$ to its (unique) preimage on $\mathcal{A}$. Together, these two steps correspond to the
-transformation in Theorem~\ref{Transformation}.  The introduction of
-the sphere in $\mc {C}^\perp (X)$ as the initial proposal surface
-along with properties \ref{regEq}-\ref{scaleEq2Reg} ensure that the mapping is
-1-1. In particular, property
-\ref{scaleEq2Reg} ensures the scaling to be unique and \ref{regIn}
-implies that the scale statistic is unchanged when undoing the
-projection. Property \ref{regEq} ensures the uniqueness of undoing the
-projection.  The general proposal strategy is summarized as follows:
-\begin{enumerate}
-\item Sample $\bz^*$ from a distribution with known density on the unit sphere in $\mc{C}^\perp(X)$.
-\item Calculate the Jacobian of \green{the} transformation in Theorem \ref{Transformation} in two steps.
-\begin{enumerate}
-\item Scale from unit sphere to $\Pi(\mathcal{A})$: $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$
-\item Shift  from $\Pi(\mathcal{A})$ to $\mathcal{A}$: $\by=\bz+X\left(\bb(X, \by_{obs})-\bb(X, \bz)\right)$
-\end{enumerate}
-\end{enumerate}
-
+%Returning to the artificial example, Figure~\ref{fig:sampSpace}
+%depicts $\Pi(\mathcal{A})$ as well as the sphere from which we obtain
+%the initial sample. The column vector $X=\bf{1}$ spans $\mc{C}(X)$ and
+%is shown as a reference. The triangle with bowed sides in dark
+%  blue is  $\Pi(\mathcal{A})$, the projection of $\mc A$ onto the
+%plane orthogonal to $\mb 1$ (i.e., $\mc{C}^\perp(X)$). The \green{unit} sphere from
+%which the initial sample is taken is depicted as the red circle in this plane.  In general, this is the unit sphere in the $n-p$ dimensional space $\mc{C}^\perp(X)$.  
+%
+%For the transformation of the initial proposal $\bz^*$ on the surface of the sphere to $\by\in \mc A$ , we first move to a point on $\Pi(\mathcal{A})$ through a 
+%simple scaling of $\bz^*$.  This is followed by undoing the projection with a move from 
+%$\Pi(\mathcal{A})$ to its (unique) preimage on $\mathcal{A}$. Together, these two steps correspond to the
+%transformation in Theorem~\ref{Transformation}.  The introduction of
+%the sphere in $\mc {C}^\perp (X)$ as the initial proposal surface
+%along with properties \ref{regEq}-\ref{scaleEq2Reg} ensure that the mapping is
+%1-1. In particular, property
+%\ref{scaleEq2Reg} ensures the scaling to be unique and \ref{regIn}
+%implies that the scale statistic is unchanged when undoing the
+%projection. Property \ref{regEq} ensures the uniqueness of undoing the
+%projection.  The general proposal strategy is summarized as follows:
+%\begin{enumerate}
+%\item Sample $\bz^*$ from a distribution with known density on the unit sphere in $\mc{C}^\perp(X)$.
+%\item Calculate the Jacobian of \green{the} transformation in Theorem \ref{Transformation} in two steps.
+%\begin{enumerate}
+%\item Scale from unit sphere to $\Pi(\mathcal{A})$: $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$
+%\item Shift  from $\Pi(\mathcal{A})$ to $\mathcal{A}$: $\by=\bz+X\left(\bb(X, \by_{obs})-\bb(X, \bz)\right)$
+%\end{enumerate}
+%\end{enumerate}
+%
 \subsubsection{Evaluation of the proposal density} 
-Calculation of the appropriate Jacobian of the transformation is absolutely vital and also non-trivial. Writing the transformation from the unit sphere in deviation space to $\mathcal{A}$ in 
-two steps facilitates calculation of the Jacobian in two steps as written above. % \textcolor{blue}{added the following sentence, hopefully it helps}
-We now explain each step, keeping in mind that the Jacobian of a transformation is simply the ratio of infinitesimal volumes along the tangents of the domain and range of the transformation.
-
+%Calculation of the appropriate Jacobian of the transformation is absolutely vital and also non-trivial. Writing the transformation from the unit sphere in deviation space to $\mathcal{A}$ in 
+%two steps facilitates calculation of the Jacobian in two steps as written above. % \textcolor{blue}{added the following sentence, hopefully it helps}
+We now explain each step in computing the Jacobian described above.
+%the scale transformation from the unit sphere to $\Pi(\mathcal{A})$, {keeping in mind that the Jacobian of a transformation is simply the ratio of infinitesimal volumes along the tangents of the domain and range of the transformation.
 \vskip 0.05 in
@@
 The first step is constrained to $\mc{C}^\perp(X)$ where the unit sphere is transformed to $\Pi(\mathcal{A})$.
-We further break this \green{\sout{piece} step into \sout{in two steps} into two substeps}: first, the distribution on the unit sphere is transformed to that along a sphere of radius $r=\|\bz\|={s(X,\boldsymbol{y}_{obs})}/{s(X, \boldsymbol{z}^{*})}$.
-This contributes \green{a factor of} $r^{-(n-p-1)}$ to the Jacobian.
+We further break this step into into two substeps: first, the distribution on the unit sphere is transformed to that along a sphere of radius $r=\|\bz\|={s(X,\boldsymbol{y}_{obs})}/{s(X, \boldsymbol{z}^{*})}$.
+This contributes a factor of $r^{-(n-p-1)}$ to the Jacobian.
 Second, the new sphere is then deformed to $\Pi(\mathcal{A})$.
-This deformation contributes an attenuation to the Jacobian equal to the
-ratio of infinitesimal volumes in the
+This deformation contributes an attenuation to the Jacobian equal to the ratio of infinitesimal volumes in the
 tangent spaces of the sphere and $\Pi(\mathcal{A})$ at $\bz$.  
@@
 where $\gamma$ is the angle between the two normal vectors.
-This step is illustrated in Figure~\ref{fig:stretchDeform} for the toy
-location-scale example.  The figure \green{\sout{only}} pictures \green{only} the deviation space
+This step is visualized in Figure~\ref{fig:stretchDeform} for the artificial
+location-scale example.  The figure pictures only the $\mathcal{C}^{\perp}(X)$,
 which in this case is a plane. The original unit  sphere (here, the

### 2018-08-17 revision_1/paper.tex
paper edits and reorginization of code

@@
 It is not a simple matter to do this directly, but with the specified conditions, it is possible to scale and shift any $\bz^{*}$ which generates
-a positive scale estimate to such a $\by$ via the following Theorem whose proof is in the appendix. 
+a positive scale estimate to such a $\by$ via the following Theorem, whose proof is in the appendix. 
 \begin{theorem}
@@
 \]
-\end{theorem}
-% (details are given in Theorem \ref{Transformation} below). Hence, to obtain $\by \in\mathcal A$, we proceed in two steps:
+\end{theorem}% (details are given in Theorem \ref{Transformation} below). Hence, to obtain $\by \in\mathcal A$, we proceed in two steps:
 %\begin{enumerate}
@@
 %\end{theorem}
-Using the theorem, the general idea is to first start with a sample $\bz^*$ from a known distribution, say $p(\bz^*)$, and transform via $h(\cdot)$ to $\by \in \mathcal{A}$.
+Using the theorem, the general idea is to first start with an initial vector $\bz^*$ drawn from a known distribution, say $p(\bz^*)$, and transform via $h(\cdot)$ to $\by \in \mathcal{A}$.
 The proposal density $p(\by|\bth)$ is then a change-of-variables adjustment on $p(\bz^*)$ derived from $h(\cdot)$.
@@
 %the transformation to $\by$ is one-to-one and the Jacobian, $\displaystyle \left|\frac{\partial h^{-1}(\by)}{\partial \by}\right|$, can be computed directly.  
-In general however, the mapping $h()$ is many-to-one: for any $\bv\in \mathbb{R}^{n}$ and any $c\in \mathbb{R}^{+}$, $c\bz^{*} + X\bv$ map to the same $\by$.
+In general however, the mapping $h(\cdot)$ is many-to-one: for any $\bv\in \mathbb{R}^{n}$ and any $c\in \mathbb{R}^{+}$, $c\bz^{*} + X\bv$ map to the same $\by$.
 This makes the change-of-variables adjustment difficult.
@@
 Hence, we restrict the initial $\bz^*$ to an easily understood $n - p - 1$ dimensional space.
-Specifically, this space is  the unit sphere in the orthogonal complement of the column space of the design matrix.
-Denote the column space and its orthogonal complement with $\mathcal{C}(X)$ and  $\mathcal{C}^{\perp}(X)$, respectively.
-With $\bz^{*}$ on this sphere, $c\bz^{*} + X\bv$ is clearly not (unless $c=1$ and $\bv = \mathbf{0})$ since every point on the sphere is both in  $\mathcal{C}^{\perp}(X)$ and has $||\bz^{*}|| = 1$.
-Thus the mapping has become one-to-one making the change of variables more feasible.
-
-With the domain of $h(\dot)$ restricted to the unit sphere in $\mathcal{C}^{\perp}(X)$, the range is still the entirety of $\mathcal{A}$.
-This is important so that the support of the proposal distribution (i.e.
-the $h(\dot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
-To see that the range of $h(\dot)$ is $\mathcal{A}$, consider any $\by \in \mathcal{A}$ and its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$ \footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).}.
-It is easy to show that $\bz^{*} = Q\by/||Q\by||$ is on the unit sphere and $h(\bz^{*}) = \by$.
-
-Given the one-to-one and onto mapping from the sphere to $\mathcal{A}$, the general proposal strategy is summarized as follows:
+Specifically, this space is  the unit sphere in the orthogonal complement of the column space of the design matrix: $\mathbb{S} := \{\bz^* \in \mathcal{C}^{\perp}(X)\  |\  ||\bz^*|| = 1\}$, where $\mathcal{C}(X)$ and  $\mathcal{C}^{\perp}(X)$ are the column space of $X$ and its orthogonal complement, respectively.
+With $\bz^{*}\in \mathbb{S}$, $c\bz^{*} + X\bv$ is not (unless $c=1$ and $\bv = \mathbf{0})$; the scaling by $c$ and/or the affine transformation in the direction of $\mathcal{C}(X)$ takes the point off $\mathbb{S}$.
+The mapping $h: \mathbb{S} \rightarrow \mathcal{A}$ is one-to-one making the change of variables more feasible.
+
+With the domain of $h(\cdot)$ restricted to  $\mathbb{S}$, the range is still the entirety of $\mathcal{A}$.
+This is important so that the support of the proposal distribution (which is the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
+To see that the range of $h(\cdot)$ is $\mathcal{A}$, consider any $\by \in \mathcal{A}$ and its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$.
+\footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).} It is easy to show that $\bz^{*} = Q\by/||Q\by|| \in \mathbb{S}$ and $h(\bz^{*}) = \by$.
+
+Given the one-to-one and onto mapping $h: \mathbb{S} \rightarrow \mathcal{A}$, the general proposal strategy is summarized as follows:
 \begin{enumerate}
-\item Sample $\bz^*$ from a distribution with known density on the unit sphere in $\mc{C}^\perp(X)$.
+\item Sample $\bz^*$ from a distribution with known density on $\mathbb{S}$.
 \item Set $\by = h(\bz^*)$ and calculate the Jacobian of this transformation in two steps.
 \begin{enumerate}
-\item Scale from unit sphere to the set $\Pi(\mathcal{A}):= \{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\ s.t.\ \bz=Q \by \}$.
-This is the projection of $\mathcal{A}$ onto $\mathcal{C}^{\perp}(X)$ and, by condition \ref{regIn}, every element of this set has $s(X, \bz) = s(X, \by_{obs})$.
+\item Scale from $\mathbb{S}$ to the set $\Pi(\mathcal{A}):= \{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\ s.t.\ \bz=Q \by \}$.
+$\Pi(\mathcal{A})$ is the projection of $\mathcal{A}$ onto $\mathcal{C}^{\perp}(X)$ and, by condition \ref{regIn}, every element of this set has $s(X, \bz) = s(X, \by_{obs})$.
 Specifically, set $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$.
@@
 The final proposal distribution including the complete Jacobian is given in equation \eqref{dens:ystst} with details in the next section.
-Before giving these details we provide a visualization of each of the sets described above to aid in the understanding of the strategy we are taking.
-Figure~\ref{fig:sampSpace} depicts an artificial low-dimensional location-scale example.
+Before giving these details we provide a visualization  in Figure~\ref{fig:sampSpace} of each of the sets described above to aid in the understanding of the strategy we are taking.
 In the figure, $n = 3$, $p=1$, and the conditioning statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$.
@@
 The other two coordinates are restricted by the scale statistic to lie on the quarter circle of radius one in the positive orthant.
-In this example, the column vector $X=\bf{1}$ (shown as a reference) spans $\mc{C}(X)$  and the unit sphere in $\mathcal{C}^{\perp}(X)$ is a unit circle on the orthogonal plane (shown in red).
-This is the sphere from which the initial sample $\bz^{*}$ is taken.
-$\Pi(\mathcal{A})$, the projection of $\mc A$ onto the orthogonal plane is depicted as the bowed triangle in dark blue.
-We will come back to this artificial example in the next section in an attempt to visualize the Jacobian calculations
+In this example, the column vector $X=\bf{1}$ (shown as a reference) spans $\mc{C}(X)$  and $\mathbb{S}$ is a unit circle on the orthogonal plane (shown in red).
+$\Pi(\mathcal{A})$ is depicted as the bowed triangle in dark blue.
+We will come back to this artificial example in the next section in an attempt to visualize the Jacobian calculations.
 
@@
 \noindent
-{\bf Scale from unit sphere to $\Pi(\mathcal{A})$} \\
-The first step is constrained to $\mc{C}^\perp(X)$ where the unit sphere is transformed to $\Pi(\mathcal{A})$.
-We further break this step into into two substeps: first, the distribution on the unit sphere is transformed to that along a sphere of radius $r=\|\bz\|={s(X,\boldsymbol{y}_{obs})}/{s(X, \boldsymbol{z}^{*})}$.
-This contributes a factor of $r^{-(n-p-1)}$ to the Jacobian.
-Second, the new sphere is then deformed to $\Pi(\mathcal{A})$.
-This deformation contributes an attenuation to the Jacobian equal to the ratio of infinitesimal volumes in the
-tangent spaces of the sphere and $\Pi(\mathcal{A})$ at $\bz$.  
-Restricting ourselves to the $n-p$ dimensional space $\mc{C}^\perp(X)$, this
-ratio is the cosine of the angle between the normal 
+{\bf Scale from $\mathbb{S}$ to $\Pi(\mathcal{A})$} \\
+The first step is constrained to $\mc{C}^\perp(X)$  and scales the initial $\bz^{*}$ to $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$.
+For the Jacobian, we consider two substeps: first, the distribution on  $\mathbb{S}$ is transformed to that along a sphere of radius $r=\|\bz\|={s(X,\boldsymbol{y}_{obs})}/{s(X, \boldsymbol{z}^{*})}$.
+By comparison of the volumes of these spheres, this transformation contributes a factor of $r^{-(n-p-1)}$ to the Jacobian.
+For the second substep, the sphere of radius $r$ is deformed onto $\Pi(\mathcal{A})$.
+This deformation contributes an attenuation to the Jacobian equal to the ratio of infinitesimal volumes in the tangent spaces of the sphere and $\Pi(\mathcal{A})$ at $\bz$.
+Restricting to $\mc{C}^\perp(X)$, this ratio is the cosine of the angle between the normal 
 vectors of the two sets at $\bz$.  The normal to the sphere is its radius vector $\bz$. The normal to
 $\Pi(\mathcal{A})$ is given in the following lemma.  
-
 \begin{lemma}
 \label{gradSTheoremReg}
-Assume that conditions \ref{fullRank}-\ref{supReal}, \ref{as}, and \ref{regIn} hold.  
-Let $\by\in \mathcal{A}$. Let 
+Assume that conditions \ref{fullRank}-\ref{supReal}, \ref{as}, and \ref{regIn} hold and $\by\in \mathcal{A}$. Let 
 $\nabla s(X,\by)$ denote the
@@
 \end{lemma}
-
 As a result of the lemma, the contribution to the  Jacobian of this attenuation is 
@@
 location-scale example.  The figure pictures only the $\mathcal{C}^{\perp}(X)$,
-which in this case is a plane. The original unit  sphere (here, the
-solid circle) is first stretched to the dashed sphere contributing
+which in this case is a plane. The unit sphere (here, the
+solid circle) is stretched to the dashed sphere contributing
 $r^{-(n-p-1)}$ to the Jacobian as seen in panel (a). In panel (b), the
@@
 $\cos(\gamma)$ to the Jacobian. The normal vectors in panel (b) are
-orthogonal to the tangent vectors of $\Pi(\mc A)$ and the circle. As
-stated above, the Jacobian is the ratio of infinitesimal lengths along these tangent vectors.
+orthogonal to the tangent vectors of $\Pi(\mc A)$ and the circle.
+%As stated above, the Jacobian is the ratio of infinitesimal lengths along these tangent vectors.
 This is the same as the ratio of the infinitesimal lengths of the normal vectors (i.e., $\cos(\gamma)$).
@@
 contribution of this deformation to the Jacobian is, again,
-the ratio of the infinitesimal volume along $\Pi(\mathcal{A})$ at $\bz$ to the
+the ratio of the infinitesimal volumes along $\Pi(\mathcal{A})$ at $\bz$ to the
 corresponding volume along $\mathcal{A}$ at $\by$. 
@@
 $\mc T_{y}(\mc A)$ and $\mc T_{y}^{\perp}(\mc A)$ denote the tangent
-space to $\mc A$ at $\by$ and its orthogonal complement respectively.
-
+space to $\mc A$ at $\by$ and its orthogonal complement respectively. All gradients denote with $\nabla$ are with respect to the data vector.
 \begin{lemma}
@@
 
-The lemma describes construction of a basis for $\mc T_{y}^\perp(\mc A)$.  This leads to a 
+The lemma describes construction of a basis for $\mc T_{y}^\perp(\mc A)$, leading to a 
 basis for $\mc T_{y}(\mc A)$.  Both of these bases can be orthonormalized.  
@@
 
-In practice, computing $A$ directly to find $P$ and $\text{Vol} (P)$ is computationally intensive as it involves orthogonalization of $n$ vectors in $n$-dimensional space. 
-To find a matrix $A$, supplement $B$ with a set of $n$ linearly independent columns on the right, and apply Gram-Schmidt 
-orthonormalization to the matrix.  This algorithm is infeasibly slow when $n$ is large because it is $\mc O(n^3)$ and must be repeated at each
-iterate of the MCMC when a complete data set is drawn.  
-Fortunately, we can make use of results related to \textit{principal angles} found in \cite{miao1992} to compute the volume in \eqref{eq:volume} using $B$ and an orthonormal basis for $\mc C (X)$ (The definition of principal angles can be found in the cited text).
-Recall, $B$ is constructed by orthogonalization of a basis for $\mc T_{y}^\perp(\mc A)$.
-Since this space is of dimension $p+1$, applying Gram-Schmidt to find the orthonormal basis is much faster, the algorithm is $\mc O(np^2)$, and there is a
+%In practice, computing $A$ directly to find $P$ and $\text{Vol} (P)$ is computationally intensive as it involves orthogonalization of $n$ vectors in $n$-dimensional space. 
+A few details for computingthe needed quantities are worth further explanation.
+Computing $\text{Vol} (P)$ involves finding an orthornormal matrix $A$ whose columns span $\mc T_{y}(\mc A)$.
+This matrix can be found by supplementing $B$ with a set of $n$ linearly independent columns on the right, and apply Gram-Schmidt orthonormalization.
+This is $\mc O(n^3)$ and is infeasibly slow when $n$ is large because it must be repeated at each iterate of the MCMC when a complete data set is drawn.
+However, using results related to \textit{principal angles} found in \cite{miao1992} the volume \eqref{eq:volume} can be computed using only $B$.
+$B$ is constructed by Gram-Schmidt orthogonalization of $\nabla s(X,\by), \nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$, which is  $\mc O(np^2)$;  a
 considerable reduction in computational burden when $n \gg p$. 
-Further, the singular values of $P=QA$ are also the singular values of
-$W^\top A$ (recall, $Q=WW^{\top}$), which can be easily obtained through $B$.
+%Further, the singular values of $P=QA$ are also the singular values of
+%$W^\top A$ where $Q=WW^{\top}$, which can be easily obtained through $B$.
 The following corollary formally states how computation of $A$ can be circumvented. 
@@
 \label{theorem:sings}
-Let $U$ be a matrix whose columns
-form an orthonormal basis for $\mc C (X)$. Then the non-unit singular
-values of $U^\top B$ are the same as the non-unit singular values of $W^\top A$.  
+Let $U$ be a matrix whose columns form an orthonormal basis for $\mc C (X)$ and set $Q=WW^{\top}$ where the columns of $W$ form an orthonormal basis for $\mc{C}^\perp(X)$.
+Then the non-unit singular values of $U^\top B$ are the same as the non-unit singular values of $W^\top A$.
 \end{corollary} 
-\noindent Thus, we can compute $\text{Vol} (P)$ by finding the singular values of $U^\top B$, reducing the computational burden substantially.
+\noindent The lemma implies the $\text{Vol} (P)$ is the product of the singular values of $U^\top B$.
+
+Second, the gradients of $\nabla s(X,\by), \nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$ are easily computed. For example, below we consider M-estimators defined by the estimating equations:
+\begin{eqnarray}
+\label{Mest}
+ \sum_{i=1}^n \psi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)= & 0 \\
+ \sum_{i=1}^n \chi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)= & 0, \nonumber 
+\end{eqnarray} 
+where $\psi$ and $\chi$ are almost surely differentiable.
+Differentiating this system of equations with respect to each $y_{i}$ can be used to find the gradients.
+In theory, finite differences could also be used.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Simulations}
-\subsection{Simulation 1}
-
-\subsection{Simulation 2}
+\section{Simulation}
 Data generating model:

### 2018-08-17 submission_1/codeForPaper/newcomb/directSampling/readMeDirectSampling.tex
added code for first draft submission to the repo.

readMe: DirectSampling

Direct Sampling methods for evaluated the restricted posterior [theta, sigma^{2}| T(X)] for T(X) = Huber/Huber Proposal 2, LTS, and LMS estimators

##
speedOfLightAnalysisHuberDirectSampling
description: Posterior evaluation using Huber's estimators. Saves results to a workspace  wsNewcombDirectSamplingHuber2.RData

##
speedOfLightLMSDirectSampling
description: Posterior evaluation using LMS. Saves results to a workspace  wsNewcombDirectSamplingLMS2.RData

##
speedOfLightLTSDirectSampling
description: Posterior evaluation using LTS. Saves results to a workspace  wsNewcombDirectSamplingLMS2trim_2.RData
*Note: trim_2 refers to k=62, the value ultimately used in the paper. This can be changed in the code to use k=34. If done, the ws is saved as wsNewcombDirectSamplingLMS2.RData

### 2018-08-17 submission_1/codeForPaper/newcomb/mcmc/readMeMCMC.tex
added code for first draft submission to the repo.

ReadMe: newcomb/mcmc

##
locAndScaleHuberAndProposal2 and locAndScaleTukeyAndProposal2

These are source files containing functions used to sample from the restricted posterior using the M-estimators used in the paper. They are sourced by newcombHuberAndProposal2Analysis.R and  newcombTukeyAndProposal2Analysis.R, respectively

*Note: These are specific to the location and scale setting. Functions have since been updated to allow for covariates and provided in linearRegressionHuberAndProposal2.

##
newcombFullNormalModel.R
Fits the full normal theory model. Saves results in workspace WorkSpaceNewcombFullNormalModel2.RData

##
newcombHuberAndProposal2Analysis.R and  newcombTukeyAndProposal2Analysis.R

Uses mcmc to fit the restricted models. Also includes analysis done where the outliers are deleted (not discussed in the paper). Workspaces are saved in WorkSpaceNewcombHuberAndProposal2AnalysisWithDelAnalysis2.RData and WorkSpaceNewcombTukeyAndProposal2AnalysisWithDelAnalysis2.RData.

### 2018-08-17 submission_1/codeForPaper/newcomb/readMeNewcomb.tex
added code for first draft submission to the repo.

ReadMe: Newcomb

Code to analyze the speed of light data in several ways

##

newcombAnalyzeOutput.R
description: Creates plots used in paper. Must have access to the workspaces created by code in the directSampling and mcmc folders.

##

newcombFixedParameters1.R and newcombFixedParameters2.R
description: defines hyper parameters. Two different versions. Values in newcombFixedParameters2.R were ultimately used in the paper.

##
Folders

##
directSampling: 
Uses 'direct sampling' techniques to sample from the restricted posterior under Huber, LTS, and LMS. See read me file in the folder

##
fittingTdist
uses MCMC and grid techniques to fit the t-distribution model.  See read me file in the folder

##
mcmc
uses MCMC techniques to sample from the full posterior and restricted posterior under Huber/huber prop2 and Tukey/Huber prop2 estimators. See read me file in the folder

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/readMeHierLinearReg.tex
added code for first draft submission to the repo.

Read me
nwHierLinearReg Folder

#Description of how to reproduce results from paper.
#setwd to the code folder#

To reproduce the paper results from scratch run the 'ÉAnalysis.R' files in the code folder after running code in nwLinearReg. For n=1000, 2000, run each of the three '...Analysis.R'  files 4 times with run=1,2,3,4 and reps=25. For the new method  do this for both regEst<-'Huber' and regEst<-'Tukey' which is defined at the top of the  nwRestrictedHierAnalysis.R file. Each run fits the model to 25 splits of training/holdout. These runs should preferably be done as background jobs as they take some time to run.

After running, the results are saved in workspaces with names 
wsNwNormalHierarchAnalysis_n#run#.RData
wsNwRestrictedHierarchAnalysisHuber_n#run#.RData
wsNwRestrictedHierarchAnalysisTukey_n#run#.RData
wsNwTModelHierarchAnalysis_n#run#.RData

where n# is either n1000 or n2000 for training sets of size 1000 and 2000
run# is run1, run2, run3, run4, to identify which 'run'. This results is a total 32 workspaces.

Then run consolidateOutputFromHierAnalyses.R to consolidate the results from all workspaces to one workspace consolidateOutputFromHierAnalysesFIX.RData

Finally, nwAnalyzeHierOutputWithin.R summarizes results, creates plots. Comparing the hierarchical and nonhierarchical models is done in compareHierVNonHier.R

#--------------
## Code Folder
#-------------

compareHierVNonHier.R
	compares hierarchical and nonhierarchical models using consolidated results from nonhier fits (consolidatedOutputForPlots.RData) and hierarchical fits (consolidateOutputFromHierAnalysesFIX.RData).

consolidateOutputFromHierAnalyses.R
	consolidates the workspaces 
		wsNwNormalHierarchAnalysis_n#run#.RData
		wsNwRestrictedHierarchAnalysisHuber_n#run#.RData
		wsNwRestrictedHierarchAnalysisTukey_n#run#.RData
		wsNwTModelHierarchAnalysis_n#run#.RData 
	created by each anlaysis.R file run into one workspace consolidateOutputFromHierAnalysesFIX.RData

nwAnalyzeHierOutputWithin.R
	Summarizes results and creates plots using the consolidated results created by consolidateOutputFromHierAnalyses.R contained in consolidateOutputFromHierAnalysesFIX.RData

nwHierNormalModelFittingFunction.R
	loads nwHierNormalModelSamplingFunctions.R for the sample functions. Defines 
	fn.hier.one.rep: one rep of MH algorithm for the hier. model
	heirNormTheoryLm: full MCMC function

nwHierNormalModelSamplingFunctions.R
	sampling functions for the normal theory hierarchical model.

nwHierRestrictedModelFittingFunction.R
	fits the hierarchical model conditioning on separate robust estimators in each group
	same sampling functions for the parameters from normal theory model are used.
	within each group, the update of the data vector is the same as before. (from linearRegressionHuberAndProposal2.R) 
	hierNormTheoryRestLm2: Full MCMC for hier. model.

nwNormalHierAnalysis.R:
	Analysis using the normal theory model, creates the wsNwNormalHierarchAnalysis_n#run#.RData workspaces with the results for each t	raining set size and run (runs 1-4 each 	containing 25 reps set by sourceCodeForAnalysis.R)

nwRestrictedHierAnalysis.R
	Analysis using the normal theory model but conditioning on robust regressions in each group, creates the 	wsNwRestrictedHierarchAnalysisRegEst_n#run#.RData workspaces with the results for each training set size and run (runs 1-4 each 	containing 25 reps set by 	sourceCodeForAnalysis.R). The RegEst is either Huber or Tukey.

nwTdistHierModelFittingFunction.R 
	sampling functions for the hierarchical model using t-distribution. Note only a couple of the sampling functions defined in 	nwHierNormalModelSamplingFunctions.R need to be adjusted. 
	Full MCMC function is heirTTheoryLm.

nwTHierAnalysis:
	Analysis using the t-model. Creates the wsNwTModelHierarchAnalysis_n#run#.RData workspaces with the results for each training set 	size and run (runs 1-4 each containing 25 reps set by sourceCodeForAnalysis.R)

settingHyperParameters.R
	use prior data set to set reasonable values for the fixed hyperparameters. Creates the wsnwdataHierPriorConstruction.RData 	workspace which has the values of the resulting hyperparemters. Unfortunately it cannot be run without access the proprietary dataset in 	nwdataPrepPaper1DataCleanWorkspace.RData (this cannot be provided unfortunately)

sourceCodeForAnalysis.R
	loaded by each '...Analysis.R' function. It loads the workspaces created by the standard linear regression fits. This is done to get the same 	training/holdout splits as used for the standard linear regression model. It also loads the functions needed to fit each model and defines 	some other functions such as fn.compute.marginals.hierModelNormal and fn.compute.marginals.hierModelTmodel to compute marginal 	distributions.

#--------------
## Workspaces Folder
#-------------
wsnwdataHierPriorConstruction.RData: Contains the values of the hyper parameters. created by running settingHyperParameters.R

consolidateOutputFromHierAnalysesFIX.RData --- This must be produced using the steps above. Not included because of its size. 
Consolidated results for summarizing results.

### 2018-08-17 submission_1/codeForPaper/nwLinearReg/readMeLinearReg.tex
added code for first draft submission to the repo.

Read me
nwLinearReg Folder

NOTE: Some workspaces referenced contain proprietary data which is not masked. Hence they cannot be shared. However the masked data is available in workSpaces/nwdataPaper1PriorConstructionWorkSpace.RData.

#Description of how to reproduce results from paper.
#Code should run if wd is set to the code folder#

To reproduce the paper results from scratch, run the nwAnalysisSimulation.R file in the code folder. This file splits the data into training and holdoutset and runs each model. For n  (training set size) of less than 1000, I ran the code once with reps set to 100. For n greater than or equal to 1000, we ran the file four times (run=1,2,3,4) with reps set to 25, to save on computation time by running each in parallel. We used n=25,50,100,200,500,1000, 2000, but only a subset of these are in the paper. Runs should preferably be done as background jobs as they take some time to run.

After running, the results are saved in workspaces with names 
wsNwAnalysis_n# (if just one run)
wsNwAnalysis_n#run# (if multiple runs)

where the # in n# is the training set size
the # run# is the run number (1,2,3,4)

Then run nwConsolidateAndSummarizeSims.R to consolidate the results from all workspaces to one workspace consolidatedOutputForPlots.RData

Finally, nwAnalyzeOutput.R loads nwdataPaper1PriorConstructionWorkSpace.RData and consolidatedOutputForPlots.RData and summarizes results and creates plots.

Note: nwdataPrepPaper1DataClean.R, nwdataPaper1PriorConstruction.R do data cleaning and set prior parameters from proprietary data. Code provided for documentation, but proprietary data can't be shared.

#--------
#Code Folder: 
#---------
%Not included
%nwdataPrepPaper1DataClean.R: 
%	Loads original data from nwdataPrepPaper1Workspace.RData, strips identifiers, renames variables. Does this for both the prior data and fitting data. Data in nwdataPrepPaper1Workspace.RData is proprietary. Data saved to nwdataPrepPaper1DataCleanWorkspace.RData is also proprietary. These .RData files unfortunately cannot be provided.

## 
nwdataPaper1PriorConstruction.R
	Centers and scales original (cleaned) data from nwdataPrepPaper1DataCleanWorkspace.RData (contains unsharable data). Also uses the prior data to choose the prior parameters of the model. Creates nwdataPaper1PriorConstructionWorkSpace.RData (sharable) in workspaces folder.

## 
nwAnalysisSimulation.R:   
	Contains the code to repeatedly split the data into a training and holdout set, fit each model, and record the needed results. Loads data from nwdataPaper1PriorConstructionWorkSpace.RData. For each run, it creates the 'wsNwAnalysis' workspaces used by nwConsolidateAndSummarizeSims.R.

## 
nwConsolidateAndSummarizeSims.R: 
	Combines results from training/holdout fits for multiple training sample sizes and saves to consolidatedOutputForPlots.RData.
	The 'wsNwAnalysis' workspaces created by each run of nwAnalysisSimulation.R must be available. These have names of the form wsNwAnalysis_n#run#.RData where 	the # after n is the training set size and the # after run is the run number (I used 4 runs for larger values of n to cut down on computation time)
## 
nwAnalyzeOutput.R: 
	Loads nwdataPaper1PriorConstructionWorkSpace.RData and consolidatedOutputForPlots.RData, analyzes the results, and creates plots.
##

#--------
#Workspace Folder: 
#---------

##
consolidatedOutputForPlots.RData ---- This must be produced by following the steps above. It is not included because of its size. 
	results consolidated and ready for plotting (see nwConsolidateAndSummarizeSims.R above)

##
nwdataPaper1PriorConstructionWorkSpace.RData
	Has the sharable dataset along with the prior parameters.  (see nwdataPaper1PriorConstruction.R above)

### 2018-08-17 submission_1/codeForPaper/readMeCodeForPaper.tex
added code for first draft submission to the repo.

ReadMe: codeForPaper

##
linearRegressionHuberAndProposal2.R
  description: contains functions for the MH algorithm for sampling from the full conditional [Y|T(Y)=T(y_obs), theta] for the Bayesian linear model. This is perhaps the most important piece of code.

NOTE: the original file was named as such because it was originally written to only handle Huber's estimators. It has morphed into slightly more than that since.

##
bayesLM.R
	description: contains functions for MCMC algorithms for various linear models
	bayesLm: standard normal theory regression. See file for full description of model. 
	restrictedBayesLm: linear model conditioning on summary statistics.
	bayesTdistLm: linear model using Student's t-distribution. 
	bayesTdistLm2: second version of MCMC for the t model. Same stationary distribution just different sampling method.

##Folders##

##	
nwLinearReg
	See readMeLinearReg in folder
##	
nwHierLinearReg
	See readMeHierLinearReg in folder

## 
newcomb
	See readMeNewcomb in folder

##
simulation
  See readMeNewcomb in folder

### 2018-08-17 submission_1/codeForPaper/simulation/readMeSimulation.tex
added code for first draft submission to the repo.

readMe: Simulation

##
simulation.R: code for simulation described in paper. Saves results in simulationWorkspace.RData or simulationWorkSpace_concTau2Near1.RData. The latter uses a prior that concentrates around the true value for tau^{2} of 1. These are not provided as they are large workspaces.

##
simulationSourceCode.R: code sourced by simulation.R. This defines functions necessary to fit each model. Also defines a function to simulation data (fn.gen.data)

##
postProcessingSimulation.R
post-processes simulation results and computes evaluation metrics. Saves results in simPostProcessed.RData or simPostProcessed_concTau2Near1.RData.

##
summarizeSimulations.R
summarizes the evaluation metrics computed in postProcessingSimulation.R and creates some plots

##
testSimulationSourceCode.R
some code to informally check that the functions in simulationSourceCode.R are giving reasonable results.

### 2018-08-17 submission_1/codeForPaper/newcomb/directSampling/speedOfLightAnalysisHuberDirectSampling.R

@@ -1,0 +1,193 @@
+#################
+#John Lewis
+#Robust inference via the Blended Paradigm
+# Speed of Light Data Analysis
+#
+#Using Direct Sampling to evaluate the posterior distribution
+# [theta,sigma^2|T(X),S(X)]
+#  Focus Here is T(X) as Huber's location estimator and S(X) as Huber's proposal 2
+#############################################
+
+
+#################
+#Libraries
+#################
+library(MASS)
+library(ks)
+library(MCMCpack)
+################
+
+data(newcomb)
+n<-length(newcomb)
+paramSet<-2  #set this to 1 or 2: 1 is the original set of hyper-parameters I came up with, 2 is from MacEachern's paper
+source(do.call(paste, list('../',"newcombFixedParameters", paramSet, '.R', sep='')))
+#source('../newcombFixedParameters1.R')
+
+eta
+tau
+alpha
+beta
+
+
+#X_1,...,X_n iid N(theta, sigma^2)
+#let T(X), S(X) be Huber estimators of location and scale
+
+#Prior Distributions for theta and sigma^2 are specified as follows:
+#theta~N(eta, tau^2)
+#sigma^2~IG(alpha, beta)
+#Analysis is based on the posterior [theta, sigma^2|T(X),S(X)]
+
+
+
+#View the data 
+
+# dev.new()
+# pdf('newcomb.pdf')
+# plot(density(newcomb), main='Observed Speed of Light Data', xlab='')
+# dev.off()
+
+
+#Specify the prior Parameters
+#prior parameters #prior parameters for the mean are chosen by looking a
+#estimates of the speed of light from before the experiment.
+#these were determined in speedOflightAnalysisClean2 in the orderstatistics folder
+# ##############################################################
+# eta<--222.32 #value of the mean from previous estimates
+# tau<-540.4248  #value of the standard deviations from previous estimates
+# #the prior for sigma^2 is  an inverse gamma
+# #inverse gamma parameters (Note R's parameterization)
+# alpha<-5   #shape parameter
+# beta<-50*(alpha-1)   #this gives a mean of 50
+#####################################################
+#beta^2/((alpha-1)^2*(alpha-2))
+
+start<-Sys.time()
+
+
+
+####################
+#Summarize the Data with the observed value of the robust summary statistics
+#####################
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/directSampling/speedOfLightLMSDirectSampling.R

@@ -1,0 +1,171 @@
+#######################
+#John Lewis
+# Speed of Light Data Analysis
+#
+#Using Direct Sampling to sample from the posterior distribution
+# [theta,sigma^2|T(X),S(X)]
+#  T(X) is LMS and S(X) 
+#############################################
+rm(list=ls())
+#################
+#Libraries
+#################
+library(MASS)
+library(ks)
+library(MCMCpack)
+################
+
+data(newcomb)
+n<-length(newcomb)
+paramSet<-2  #set this to 1 or 2: 1 is the original set of hyper-parameters I came up with, 2 is from MacEachern's paper
+
+setwd("~/Box Sync/research/snm/BlendedParadigmWriting/codeForPaper/newcomb/directSampling")
+
+source(do.call(paste, list('../',"newcombFixedParameters", paramSet, '.R', sep='')))
+#source('../newcombFixedParameters1.R')
+
+eta
+tau
+alpha
+beta
+
+
+#X_1,...,X_n iid N(theta, sigma^2)
+# T(X), S(X)  LMS location and scale estimators
+
+#Prior Distributions for theta and sigma^2 are specified as follows:
+#theta~N(eta, tau^2)
+#sigma^2~IG(alpha, beta)
+#Analysis is based on the posterior [theta, sigma^2|T(X),S(X)]
+
+
+start<-Sys.time()
+
+####################
+#Summarize the Data with the observed value of the robust summary statistics
+#####################
+lms.obs<-lqs(newcomb~1, method='lms')
+t.obs<-lms.obs$coefficients  #observed location estimate
+s.obs<-lms.obs$scale[1]             #observed scale estimate, based on fit criterion
+log.s.obs<-log(s.obs)
+##############################################################
+
+
+
+#################
+#Step 1: 
+#Generation of N samples from the 'standard' distribution (in this case the standard normal)
+#Summarize each by (T,S)_i i in 1,...,N. (These are the 'robust' summary statistics in this case)
+##################
+set.seed(1)
+N<-5e4 #number of samples of size n to draw and summarize with T and S
+
+
+########################
+#define a function to output the estimators 
+#scale estimates on the log scale
+#########################
+lms.estimators<-function(X){
+  lms.out<-lqs(X~1, method='lms')
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/fittingTdist/fittingTdistribution.R

@@ -1,0 +1,200 @@
+########################################
+#John Lewis
+#using a t-distribution in the analysis of the newcomb data
+#using my own code
+#########################################
+set.seed(3)
+library(MCMCpack)
+library(msm)
+library(MCMCpack)
+
+
+#number of samples
+nkeep<-1e6
+nburn<-1e5
+
+
+paramSet<-2  #set this to 1 or 2: 1 is the original set of hyper-parameters I came up with, 2 is from MacEachern's paper
+source(do.call(paste, list('../',"newcombFixedParameters", paramSet, '.R', sep='')))
+#source('../newcombFixedParameters1.R')
+eta
+tau
+alpha
+beta
+data(newcomb)
+n<-length(newcomb)
+y<-newcomb
+
+#Y_1,...,Y_n iid t_nu(mu, sigma^2)
+
+#Prior Distributions for mu and sigma^2 are specified as follows:
+#mu~N(eta, tau^2)
+#sigma^2~IG(alpha, beta)
+#Analysis is based on the posterior [mu, sigma^2|Y]
+#set up with auxillary parameters v_i: y_i~N(mu,V_i)
+#V_i~inv-chi(nu,sigma^2)
+
+
+#Specify the prior Parameters
+#prior parameters #prior parameters for the mean are chosen by looking a
+#estimates of the speed of light from before the experiment.
+#these were determined in speedOflightAnalysisClean2 in the orderstatistics folder
+##############################################################
+
+
+#special fo t-distribution; keep
+nu<-5 # degrees of freedom for the t
+#should the prior on sigma2 change??
+#yes
+#want the prior on the var(Y)=(nu/(n-2))sigma2 ~IG(alpha, beta)
+#so sigma2=((n-2)/nu)Var(Y)~IG(alpha,((n-2)/nu) beta)
+beta<-beta*(nu-2)/nu 
+#####################################################
+
+
+#setwd("~/My Box Files/research/snm/locationAndScale/dataAnalysis/newcomb/fittingTdist")
+
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/fittingTdist/fittingTdistributionOnGrid.R

@@ -1,0 +1,85 @@
+########################################
+#John Lewis
+#using a t-distribution in the analysis of the newcomb data
+#using Grid estimation
+#########################################
+set.seed(3)
+library(MCMCpack)
+library(msm)
+library(MCMCpack)
+
+#load this workspace along with fixed hyperparameters
+load("~/Box Sync/research/snm/locationAndScale/dataAnalysis/newcomb/fittingTdist/workSpaceFittingT5dfParamset2.RData")
+nu
+eta
+tau
+alpha
+beta #has already been adjusted for t-model
+y
+
+#Y_1,...,Y_n iid t_nu(mu, sigma^2)
+#Prior Distributions for mu and sigma^2 are specified as follows:
+#mu~N(eta, tau^2)
+#sigma^2~IG(alpha, beta)
+#Analysis is based on the posterior [mu, sigma^2|Y]
+#set up with auxillary parameters v_i: y_i~N(mu,V_i)
+#V_i~inv-chi(nu,sigma^2)
+
+#define the grid
+#delta.theta<-.02  #distance between points on theta grid 
+ticks.theta<-200
+theta.grid<-seq(20,35,length.out=ticks.theta)
+delta.theta<-diff(theta.grid[1:2])
+#ticks.theta<-length(theta.grid) #number of tick marks for theta
+
+#delta.sigma2<-.02 #distance between points on sigma2 grid
+ticks.sigma2<-200 #number of tick marks for sigma2
+sigma2.grid<-seq(1,70,length.out=ticks.sigma2)
+delta.sigma2<-diff(sigma2.grid[1:2])
+#ticks.sigma2<-length(sigma2.grid) #number of tick marks for sigma2
+
+
+#expand theta.grid and sigma.grid so that there are two vectors. Every possible pair of (theta,sigma2) is a single Row
+#use expand.grid
+expandGrid<-expand.grid(theta.grid,sigma2.grid)
+#first column is the expanded theta vector, second column is the expanded sigma2 column
+
+
+
+#unormalized posterior estimate function: estimates the posterior (unormalized) on the log scale
+posterior.estimate<-function(theta,sigma2){
+  #unormalized kernel density estimate of the postorior [theta, sigma2|t.obs,s.obs] on the log scale
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/mcmc/locAndScaleHuberAndProposal2.R

@@ -1,0 +1,357 @@
+####################################
+#John Lewis August 1st 2013
+#Beginings of code to run correct mcmc algorithm when conditing on robust statistics
+#Focus here is on Huber's loss and Huber's proposal 2 to form the estimating equations for the location and scale in the location and scale setting
+#will compare results to grid point estimation to verify the match
+######################################
+
+#The code will develop the sampling function to sample from the following full conditional in the gibbs step
+
+#[Y|T(y), theta]
+#where the model is
+
+#y_i~iid N(mu, sigma^2) i=1,2,3,...,n
+#priors
+#mu~
+#sigma^2~
+#note that since conditional on mu and sigma^2, Y is independent of any other hyperparameters, sampling from [Y|T(y), theta] should be independent of any other hyperparameters set in the model
+
+##################################
+#As laid out, calculations are done in two steps
+
+#1) occurs in the deviation space: a stretch and an attenuation
+#2) is the attenuation from the deviation space to the original space
+
+#calculations involve the gradients of the location and scale statistics wrt the each data value
+
+
+#####################################
+#Functions needed for the calculations of the gradients of the location and scale statistics
+######################################
+
+library(MASS)
+
+#note: psi.huber is available in the mass library: I write my own.
+fn.psi.huber<-function(u,k=1.345){
+  pmax(-k, pmin(k,u))
+}
+
+# x<-seq(-4,4, by=.001)
+# plot(x,fn.psi.huber(x), type='l', lwd=2)
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/mcmc/locAndScaleTukeyAndProposal2.R

@@ -1,0 +1,240 @@
+####################################
+#John Lewis October 2013
+#Beginings of code to run correct mcmc algorithm when conditing on robust statistics
+#Focus here is on Tukey's loss and Huber's proposal 2 to form the estimating equations for the location and scale in the location and scale setting
+#will compare results to grid point estimation to verify the match
+######################################
+
+
+##########################
+#All i did was change the psi functions used in locAndScaleHuberAndProposal2.R
+#Should be able to unify this all into one.
+#####################################
+
+
+
+
+#The code will develop the sampling function to sample from the following full conditional in the gibbs step
+
+#[Y|T(y), theta]
+#where the model is
+
+#y_i~iid N(mu, sigma^2) i=1,2,3,...,n
+#priors
+#mu~
+#sigma^2~
+#note that since conditional on mu and sigma^2, Y is independent of any other hyperparameters, sampling from [Y|T(y), theta] should be independent of any other hyperparameters set in the model
+
+##################################
+#As laid out, calculations are done in two steps
+
+#1) occurs in the deviation space: a stretch and an attenuation
+#2) is the attenuation from the deviation space to the original space
+
+#calculations involve the gradients of the location and scale statistics wrt the each data value
+
+
+#####################################
+#Functions needed for the calculations of the gradients of the location and scale statistics
+######################################
+
+library(MASS)
+
+
+
+
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/mcmc/newcombFullNormalModel.R

@@ -1,0 +1,121 @@
+########################################
+#John Lewis
+#Fitting the full normal to newcombs data
+#Custom Code
+#########################################
+
+strt<-Sys.time()
+
+set.seed(2)
+
+library(MCMCpack)
+
+
+#number of samples
+nkeep<-1e6
+nburn<-1e5
+
+paramSet<-2  #set this to 1 or 2: 1 is the original set of hyper-parameters I came up with, 2 is from MacEachern's paper
+source(do.call(paste, list('../',"newcombFixedParameters", paramSet, '.R', sep='')))
+
+alpha
+beta
+eta
+tau
+
+#Y_1,...,Y_n iid N(mu, sigma^2)
+#let T(Y), S(Y) be Huber estimators of location and scale
+
+#Prior Distributions for mu and sigma^2 are specified as follows:
+#mu~N(eta, tau^2)
+#sigma^2~IG(alpha, beta)
+#Analysis is based on the posterior [mu, sigma^2|T(Y),S(Y)]
+
+
+# #Specify the prior Parameters
+# #prior parameters #prior parameters for the mean are chosen by looking a
+# #estimates of the speed of light from before the experiment.
+# #these were determined in speedOflightAnalysisClean2 in the orderstatistics folder
+
+
+#sampling functions
+
+sample.mu<-function(y,sigma.sq,eta, tau, n=length(y))
+{
+  condMean<-((n*mean(y)*tau^2+eta*sigma.sq)/(n*tau^2+sigma.sq))
+  condVar<-(sigma.sq*tau^2)/(n*tau^2+sigma.sq)
+  return(rnorm(1,mean=condMean, sd=sqrt(condVar)))
+}
+
+
+sample.sigma.sq<-function(y, mu, alpha, beta, n=length(y))
+{
+  alphaNew<-(0.5*n+alpha)
+  betaNew<-(0.5*sum((y-mu)^2)+beta)
+  return(rinvgamma(1,shape= alphaNew,scale=betaNew))
+}
+
+
+
+total<-nkeep+nburn
+muSamplesFull<-numeric(total)
+sigma2SamplesFull<-numeric(total)
+sigma2Cur<-100
+n<-length(newcomb)
+
+###############################
+system.time(for(i in 1:total){
+  muCur<-sample.mu(newcomb,sigma2Cur,eta, tau)
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/mcmc/newcombTukeyAndProposal2Analysis.R

@@ -1,0 +1,166 @@
+########################################
+#John Lewis
+#Analysis newcomb's data using restricted likelihood of Tukey's location and Tukey's proposal 2
+#########################################
+
+strt<-Sys.time()
+
+set.seed(2)
+
+library(MCMCpack)
+
+
+#number of samples
+nkeep<-1e4
+nburn<-1e4
+
+
+paramSet<-2  #set this to 1 or 2: 1 is the original set of hyper-parameters I came up with, 2 is from MacEachern's paper
+source(do.call(paste, list('../',"newcombFixedParameters", paramSet, '.R', sep='')))
+
+eta
+tau
+alpha
+beta
+data(newcomb)
+n<-length(newcomb)
+y<-newcomb
+
+
+# data(newcomb)
+# n<-length(newcomb)
+
+#Y_1,...,Y_n iid N(mu, sigma^2)
+#let T(Y), S(Y) be Tukey estimators of location and scale
+
+#Prior Distributions for mu and sigma^2 are specified as follows:
+#mu~N(eta, tau^2)
+#sigma^2~IG(alpha, beta)
+#Analysis is based on the posterior [mu, sigma^2|T(Y),S(Y)]
+
+
+#sampling functions
+
+sample.mu<-function(y,sigma.sq,eta, tau)
+{
+  condMean<-((n*mean(y)*tau^2+eta*sigma.sq)/(n*tau^2+sigma.sq))
+  condVar<-(sigma.sq*tau^2)/(n*tau^2+sigma.sq)
+  return(rnorm(1,mean=condMean, sd=sqrt(condVar)))
+}
+
+
+sample.sigma.sq<-function(y, mu, alpha, beta, n=length(y))
+{
+  alphaNew<-(0.5*n+alpha)
+  betaNew<-(0.5*sum((y-mu)^2)+beta)
+  return(rinvgamma(1,shape= alphaNew,scale=betaNew))
+}
+
+#setwd("~/My Box Files/research/snm/locationAndScale/mcmcCodes")
+# setwd("../../../mcmcCodes")
+source('locAndScaleTukeyAndProposal2.R')
+
+
+
+total<-nkeep+nburn
+muSamplesTukey<-numeric(total)
+sigma2SamplesTukey<-numeric(total)
+
+fit1<-rlm(newcomb~1,psi=psi.bisquare, scale.est='Huber')
[…]

### 2018-08-17 submission_1/codeForPaper/newcomb/newcombAnalyzeOutput.R

@@ -1,0 +1,446 @@
+#######
+#Running from start to finish generates plots for the newcomb application section in the paper
+#paramSet controls which set of hyper-parameters to use
+#plots saved in figures folder (user degined), table for predictive distributions saved in the paper_version2 folder
+
+library(tables) #for easy importing to latex
+rm(list=ls())
+paramSet<-2 #set this to 1 or 2: 1 is the original set of hyper-parameters I came up with, 2 is from MacEachern's paper; this number is appended on the end of each workspace
+trim=2 #For LTS: what is k? trim=1: k=34, trim=2: k=62
+
+#################################################
+library(MASS)
+data(newcomb)
+#May need to change working directories
+
+setwd("~/Box Sync/research/snm/BlendedParadigmWriting/codeForPaper/newcomb")
+
+
+dirSampDirectory<-paste0(getwd(), "/directSampling/")
+
+
+mcmcDirectory<-paste0(getwd(), "/mcmc/")
+
+#tDistDirectory<-"~/Box Sync/research/snm/locationAndScale/dataAnalysis/newcomb/fittingTdist/"
+
+tDistDirectory<-paste0(getwd(), "/fittingTdist/")
+
+
+path.to.figures<-"~/Box Sync/research/snm/BlendedParadigmWriting/paper_version2/figures/"
+
+nu<-5
+
+######################################################
+#read in the posterior marginal pdfs from Huber statistics from the direct sampling
+#########################################################
+
+load(paste(dirSampDirectory,"wsNewcombDirectSamplingHuber", paramSet, ".RData", sep=''))
+eta
+tau
+alpha
+beta
+
+joint.post.Huber<-log.post.density.final
+pdfThetaRestricted<-cbind(theta.grid,post.theta.pdf)
+pdfSigma2Restricted<-cbind(sigma2.grid,post.sigma2.pdf)
+theta.gridHuber<-theta.grid
+sigma2.gridHuber<-sigma2.grid
+delta.thetaHuber<-delta.theta
+delta.sigma2Huber<-delta.sigma2
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/consolidateOutputFromHierAnalyses.R

@@ -1,0 +1,269 @@
+#Consolidate output from Hierarchical models; combining multiple workspaces from each model into one workspace
+
+#analyses for n=1000,2000
+
+#For n=1000, and 2000 I have  multiple (4) runs for each model, saved in aptley named workspaces
+#--
+#Load all of the results
+#--
+path.to.workspaces<-"../workSpaces/"
+path.to.nonHierWorkSpaces<-"../../nwLinearReg/workSpaces/"
+setwd(path.to.workspaces)
+
+#load prior info; this also loads the analysis set called analysisSetCs
+load(paste0(path.to.nonHierWorkSpaces,"nwdataPaper1PriorConstructionWorkSpace.RData"))
+load("wsnwdataHierPriorConstruction.RData")
+
+N<-nrow(analysisSetCs)
+
+# n<-1000
+# rest<-'Huber'
+
+for(rest in c('Huber', 'Tukey')){
+  for(run in 1:4){
+    for(n in c(1000, 2000)){
+  load(paste0('wsNwRestrictedHierarchAnalysis', rest, '_n', n, 'run', run, '.RData'))
+  
+}
+}
+}
+
+for(run in 1:4){
+   for(n in c(1000, 2000)){
+  load(paste0('wsNwNormalHierarchAnalysis', '_n', n, 'run', run, '.RData'))
+  load(paste0('wsNwTModelHierarchAnalysis', '_n', n, 'run', run, '.RData'))
+}
+}
+
+
+
+for(n in c(1000,2000)){
+
+ #huber restricted
+  hubMarg<-c(get(paste0("HuberrestrictedMarginalsListofLists",n,"_run1")),
+             get(paste0("HuberrestrictedMarginalsListofLists",n,"_run2")),
+             get(paste0("HuberrestrictedMarginalsListofLists",n,"_run3")),
+             get(paste0("HuberrestrictedMarginalsListofLists",n,"_run4"))
+                 )
+  
+  #unlisting
+  hubMarMat<-matrix(unlist(hubMarg), length(hubMarg),byrow=TRUE)
+  
+assign(paste0('All_HuberrestrictedMarginalsMat',n), hubMarMat)
+
+  hubPred<-c(get(paste0("HuberrestrictedPredListofLists",n,"_run1")),
+             get(paste0("HuberrestrictedPredListofLists",n,"_run2")),
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/nwAnalyzeHierOutputWithin.R

@@ -1,0 +1,238 @@
+#Analyze output from Hierarchical models
+#Within: average the trimmed marginals within each rep
+#John Lewis
+#Summarize the output from nwNormalHierAnalysis.R, nwRestrictedHierAnalysis.R (Huber and Tukey), nwTHierAnalysis.R.
+
+#analyses for n=1000,2000
+
+#For n=1000, and 2000 I have  multiple (4) runs for each model, saved in aptley named workspaces
+rm(list=ls())
+
+#add your own path to figures here
+path.to.figures<-"~/Box Sync/research/snm/linearRegression/nwPaperHierUpdated/figures"
+path.to.figures<-"~/Box Sync/research/snm/BlendedParadigmWriting/paper_version2/figures" 
+#--
+#Load all of the results
+#--
+path.to.workspaces<-"../workSpaces/"
+path.to.nonHierWorkSpaces<-"../../nwLinearReg/workSpaces/"
+setwd(path.to.workspaces)
+
+
+#load prior info; this also loads the analysis set called analysisSetCs
+
+load(paste0(path.to.nonHierWorkSpaces,"nwdataPaper1PriorConstructionWorkSpace.RData"))
+load("wsnwdataHierPriorConstruction.RData")
+
+
+#load consolidated WS results
+load('consolidateOutputFromHierAnalysesFIX.RData') #FIX: had the wrong hyper-params for restricted fits-didn't make any difference
+
+range(get(paste0('HuberyAccept1000_run', 1:4)))
+range(get(paste0('HuberyAccept2000_run', 1:4)))
+range(get(paste0('TukeyyAccept1000_run', 1:4)))
+range(get(paste0('TukeyyAccept2000_run', 1:4)))
+
+
+rounding<-5 #number of decimal places to round
+multiply<-100 #multiply mse's by this number
+model.names<-c('rlm-T','rlm-H','ols', 'normal', 'incomp.-T','incomp.-H', 't') #names in the original order
+ord<-c(1,5,2,6,7,3,4) #the order to display the results in latex
+#put in the order I want
+model.names<-model.names[ord]
+sampsizes<-c('1000','2000')
+
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/nwHierNormalModelSamplingFunctions.R

@@ -1,0 +1,640 @@
+#############################
+#Fitting Hierarchical Bayes Basic Normal Theory Linear Model
+#To the Nationwide data set
+#############################
+library(MCMCpack)
+library(msm) #for truncated normal
+library(Matrix)
+library(MASS)
+library(plyr)
+#######
+#Model
+#######
+
+#------------------------------
+#Code to fit the following Hierarchical linear model to the 
+#NW data set
+#------------------------------
+
+#[beta| mu0, Sigma0, b^*]~N(mu0, a*Sigma0) #mu0, Sigma0- fixed
+#[b_i|beta, Sigma0, b^*]~iid N(beta,b^*Sigma0) 
+
+#b=b^*swSq, where swSq is fixed (swSq=sum w_i^2, from previous data set)
+
+#Variance is partitioned between beta and (b_i, i=1,..,K) to connect to the non-hierarchical version of this model
+# this reasoning implies a+b^*=1
+
+#[b^*|v1, v2]~beta(v1, v2) 
+
+#priors are placed on mu_b*=v1/(v1+v2) and psi_b*=v1+v2 in the following way
+#mu_b*~beta(alpha_mu*, beta_mu*) with parameters fixed so the mean is small....see notes and setting of prior parameters
+#psi_b*~gamma(a_psib, b_psi_b) 
+#that is, the mean of b^*|v1,v2 is mu_b* and the variance is mu_b*(1-mu_b*)/(psi_b*+1)
+
+
+#[sigma^2_i |mu_rho, K_rho, rho]~InG(a0,b0) a0, b0 fixed from previous data set (use the same values as the non-hiearchical fit). But sigma^2_i's not independent
+
+# connect the sigma^2_i's via the formulation
+# Z~N_K(0, Sigma_rho) with sigma^2_i=H^-1(phi(z_i)) where H is the cdf of IG(a0, b0) and Sigma_rho=rho*J+(1-rho)I
+
+#to allow for data dependence in the correlation of the sigma^2_i
+
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/nwHierRestrictedModelFittingFunction.R

@@ -1,0 +1,461 @@
+ ##################
+#Restricted posterior Code
+# condition on individual statistics from each group
+#base model is in HierNormTheoryLm.R
+
+
+#T() is a robust summary of the data; Here T(X) represents the regression and scale estimates from each group individually
+
+
+
+source("nwHierNormalModelSamplingFunctions.R")
+source("nwHierNormalModelFittingFunction.R")
+source("../../linearRegressionHuberAndProposal2.R")
+
+
+
+####################################################
+#new: a bit faster; uses fn.one.rep.y2 which uses fn.attenuation2-a slightly faster version of fn.attenuation
+hierNormTheoryRestLm2<-function(y,
+                                X,
+                                regEst='Huber',
+                                scaleEst='Huber',
+                                nkeep=1e4, nburn=1e3,
+                                mu0,
+                                Sigma0,
+                                a0, 
+                                b0,
+                                mu_bstr,
+                                psi_bstr,
+                                swSq=1,
+                                w1,
+                                w2, 
+                                a_psir,
+                                b_psir,
+                                maxit=400)
+{
+  #y is a list of the responses for each group
+  #X is the design Matrix-a list of the design matrices Xi for each group
+  #X[[i]] is the design matrix for each group
+  
+  mu0<<-mu0
+  Sigma0<<-Sigma0
+  a0<<-a0
+  b0<<-b0
+  #alpha_mustr<<-alpha_mustr
+  #beta_mustr<<-beta_mustr
+  #a_psib<<-a_psib
+  #b_psib<<-b_psib
+  swSq<<-swSq
+  w1<<-w1; w2<<-w2
+  a_psir<<-a_psir
+  b_psir<<-b_psir
+  v12<<-fn.compute.ab(mu_bstr,psi_bstr)
+  v1<<-v12[1]
+  v2<<-v12[2]
+  ############
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/nwNormalHierAnalysis.R

@@ -1,0 +1,257 @@
+###########################
+#Normal Hierarchical Model Analysis
+###########################
+rm(list=ls())
+#setwd(code folder)
+source("sourceCodeForAnalysis.R")
+#n's from here (25,100,1000,2000)
+n
+run
+reps
+nburn
+nkeep
+
+
+Sys.info()
+
+
+#run multiple runs
+seeds<-c(3,4,5,6,7)
+#set seed after this load it brings in a seed already
+set.seed(seeds[run])
+
+
+p<-length(mu0Star)
+#for run in run....
+
+
+#-------------------
+#outputs to save
+#--------------------
+nTheoryGroupBetaMeans<-array(NA, c(p,nGroups, reps))
+nTheoryGroupBetaSDs<-array(NA, c(p,nGroups, reps))
+nTheorybetalConverge<-array(NA, c(p,nGroups, reps))
+
+nTheoryBetaMeans<-array(NA, c(p, reps))
+nTheoryBetaSDs<-array(NA, c(p, reps))
+nTheoryBETAconverge<-array(NA, c(p, reps))
+
+nTheorySigma2Means<-array(NA, c(nGroups, reps))
+nTheorySigma2SDs<-array(NA, c(nGroups, reps))
+nTheorySigma2Converge<-array(NA, c(nGroups, reps))
+
+nTheorybstarConverge<-numeric(reps)
+nTheoryMuRhoConverge<-numeric(reps)
+nTheoryPsiRhoConverge<-numeric(reps)
+nTheoryRhoConverge<-numeric(reps)
+
+#predictions: This is a list of lists: For each rep there is a list of the predictions for each state (list length ==22) split by state
+nTheoryPredListofLists<-replicate(reps, list()) 
+
+#marginals
+nTheoryMarginalsListofLists<-replicate(reps, list())
+
+
+
+olsPredListofLists<-replicate(reps, list()) 
+
+#marginals
+olsMarginalsListofLists<-replicate(reps, list())
+
+
+stateCountsList<-list();length(stateCountsList)<-reps
+
+#------------------------------------
+
+
+
+
+system.time(  
+for(i in 1:reps){
+
+
+hold<-get(paste0("holdIndicesMatrix",n))[i,]
+holdoutSet<-analysisSetCs[hold,]
+
+trainingSet<-analysisSetCs[-hold,]
+stateCounts<-table(trainingSet$Primary_Agency_State)
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/nwTHierAnalysis.R

@@ -1,0 +1,269 @@
+###########################
+#Normal Hierarchical Model Analysis
+###########################
+rm(list=ls())
+#setwd to code folder
+source("sourceCodeForAnalysis.R")
+
+#n's from here (25,100,1000,2000)
+n
+run
+reps
+nburn
+nkeep
+
+Sys.info()
+
+
+
+#run multiple runs
+seeds<-c(3,4,5,6,7)
+#set seed after this load it brings in a seed already
+set.seed(seeds[run])
+
+
+p<-length(mu0Star)
+#for run in run....
+
+
+#-------------------
+#outputs to save
+#--------------------
+tModelGroupBetaMeans<-array(NA, c(p,nGroups, reps))
+tModelGroupBetaSDs<-array(NA, c(p,nGroups, reps))
+tModelbetalConverge<-array(NA, c(p,nGroups, reps))
+
+tModelBetaMeans<-array(NA, c(p, reps))
+tModelBetaSDs<-array(NA, c(p, reps))
+tModelBETAconverge<-array(NA, c(p, reps))
+
+tModelSigma2Means<-array(NA, c(nGroups, reps))
+tModelSigma2SDs<-array(NA, c(nGroups, reps))
+tModelSigma2Converge<-array(NA, c(nGroups, reps))
+
+tModelbstarConverge<-numeric(reps)
+tModelMuRhoConverge<-numeric(reps)
+tModelPsiRhoConverge<-numeric(reps)
+tModelRhoConverge<-numeric(reps)
+
+#predictions: This is a list of lists: For each rep there is a list of the predictions for each state (list length ==22) split by state
+tModelPredListofLists<-replicate(reps, list()) 
+
+#marginals
+tModelMarginalsListofLists<-replicate(reps, list())
+
+
+# 
+# olsPredListofLists<-replicate(reps, list()) 
+# 
+# #marginals
+# olsMarginalsListofLists<-replicate(reps, list())
+
+
+stateCountsList<-list();length(stateCountsList)<-reps
+
+#------------------------------------
+
+
+
+
+system.time(  
+  for(i in 1:reps){
+    
+    
+    hold<-get(paste0("holdIndicesMatrix",n))[i,]
+    holdoutSet<-analysisSetCs[hold,]
+    
+    trainingSet<-analysisSetCs[-hold,]
+    stateCounts<-table(trainingSet$Primary_Agency_State)
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/nwTdistHierModelFittingFunction.R

@@ -1,0 +1,318 @@
+#--------------------
+#Sampling and fitting function for T-model
+#-------------------
+
+#reformulation of the data model: See BDA book
+#y_ij~N(t(x_ij)beta_j, V_ij)
+#V_ij~Inv-Chisq(nu, sigma_j^2)
+
+
+#steps changing in the Gibbs sampler are [beta_j|-] and [Z|-]
+
+#-----------
+#Sampling functions New to t-model
+#-----------
+
+
+#loop through for each group
+#5. [beta_l|-] l=1,..,nGroups
+#leave yl and Xl as inputs for easy transition to restricted model.
+# these are the responses and design matrix for the lth group
+#SigmaVlInv: diagonal matrix with v^-1_ij
+#sigma2l: the sigma^2_l for the l group
+#b=b^*/swSq
+#Sigma0Inv: fixed
+fn.sample.beta.lTmodel<-function(yl, Xl,SigmaVlInv,Beta,bstar){
+  b<-bstar/swSq
+  Sigma.betal<-solve(t(Xl)%*%SigmaVlInv%*%Xl+Sigma0Inv/b)
+  mu.l<-Sigma.betal%*%(t(Xl)%*%SigmaVlInv%*%yl+Sigma0Inv%*%Beta/b)
+  mvrnorm(1, mu.l, Sigma.betal)
+}
+
+fn.sample.v.lTmodel<-function(yl, Xl,betal,sigma2l){
+    nl<-length(yl)
+    as.vector(((yl-Xl%*%betal)^2+nu*sigma2l)/rchisq(nl,nu+1))
+  }
+#vlList: list of the vij's for each group
+fn.one.rep.betasAndVs<-function(y, X,Beta,sigma2,betalMat, vlList,bstar){
+  for(l in 1:ncol(betalMat)){
+    yl<-y[[l]]
+    Xl<-X[[l]]
+    vis<-vlList[[l]]
+    SigmaVlInv<-diag(1/vis)
+    sigma2l<-sigma2[l]
+    beta.l<-fn.sample.beta.lTmodel(yl, Xl,SigmaVlInv,Beta,bstar)
+    betalMat[,l]<-beta.l
+    vsl<-fn.sample.v.lTmodel(yl, Xl,beta.l,sigma2l)
+    vlList[[l]]<-vsl
+  }
+out<-list()
+out$betalMat<-betalMat
+out$vlList<-vlList
+out
+}
+
+#--------------------
+#[Z|-]
[…]

### 2018-08-17 submission_1/codeForPaper/nwHierLinearReg/code/settingHyperParameters.R

@@ -1,0 +1,355 @@
+#----------------------
+#Setting priors for hierarchical model on NW data
+#----------------------
+
+library(MASS)
+library(MCMCpack)
+#-fit robust regressions to each state seperately
+rm(list=ls())
+path.to.NonHierworkspaces<-'../../nwLinearReg/workSpaces'
+setwd(path.to.NonHierworkspaces)
+load("nwdataPaper1PriorConstructionWorkSpace.RData")
+load("nwdataPrepPaper1DataCleanWorkspace.RData") #not provided 
+path.to.workspaces<-'../../nwHierLinearReg/workSpaces'
+setwd(path.to.workspaces)
+#View(priorDataSet)
+X<-model.matrix(priorRlm)
+sd(analysisSet$sqrt_Count2012)
+dim(X)
+# rm(c)
+p<-4
+states<-unique(priorDataSet$Primary_Agency_State)
+nStates<-length(states)
+stateFits<-list(); length(stateFits)<-nStates
+n_is<-rep(NA, length(states))
+#make sure there are enough cases for good estimate of sigma2??
+for(i in 1:nStates){
+  dataset<-subset(priorDataSet, priorDataSet$Primary_Agency_State==states[i])
+  if(nrow(dataset)>40){
+  stateFits[[i]]<-rlm(sqrt_Count2010~sqrt_Count2008+Associate_Count+ageMeasure,psi=psi.bisquare,scale.est="Huber",data=dataset, maxit=400)
+  n_is[i]<-nrow(dataset)
+  }
+}
+
+
+whichFit<-unlist(lapply(stateFits, FUN=function(x) class(x)[1]=='rlm'))
+sum(whichFit)
+
+
+which(is.na(n_is))
+betaHats<-matrix(NA, nStates, 4)
+sigma2Hats<-rep(NA,nStates)
+for(i in c(1:nStates)[whichFit]){
+  {
+    betaHats[i,]<-coef(stateFits[[i]])
+    sigma2Hats[i]<-stateFits[[i]]$s^2
+  }
+}
+sum(is.na(betaHats[,1]))
+
+cbind(sigma2Hats,n_is)
+sum(is.na(n_is))
[…]

### 2018-08-17 submission_1/codeForPaper/nwLinearReg/code/nwAnalysisSimulation.R

@@ -1,0 +1,383 @@
+#########################################
+#John Lewis
+#Simulation
+#data was prepared on NW laptop: 2008-2010 for prior constuction and 2010-2012 for data analysis
+
+#Models described by bayesLM.R (requires linearRegressionHuberAndProposal2.R for the restricted methods)
+
+#Priors constructed using nwdataPaper1PriorContruction.R and results saved in nwdataPaper1PriorConstructionWorkSpace.RData
+#rlm model on 2008-2010 data used to set prior parameters for beta and sigma2
+#relavent transformation of these parameters made when centering and scaling: see nwdataPaper1PriorContruction.R
+#prior parameters suffixed by 'star' to indicate these are after transformation
+
+
+
+
+#Task: one simulation consists of taking a sample of size n for the training set 
+#Fit the rlm,ols, normal theory Bayes, restricted Bayes (with Tukeys and another with Hubers location), and t-distribution Bayes model: 6 models in total
+
+#suffixes: Rest uses Tukey's regression estimates, RestHuber uses Huber's regression estimates
+
+#prior parameters mu0Star, Sigma0StarUnscaled, a0Star, b0Star construction in nwdataPaper1PriorConstuction
+
+#########################################
+#n's from here (25,50,100,200,500,1000,2000)
+n<-1000 #sample size for the training data
+run<-4 #for large n; run multiple runs in parallel. Set the seed using the index number of seeds
+seeds<-c(3,4,5,6)
+reps<-25 #number of repetitions of the simulation. If simulations are split into 4 runs and we want a total on 100 reps, use reps=25
+nburn<-2000 #set length of mcmc chains
+nkeep<-20000
+nkeept<-40000 #for the t-model.
+
+
+#number of samples for the t-model a bit different to allow for longer chain
+#load the MCMC algorithm functions
+
[…]

### 2018-08-17 submission_1/codeForPaper/nwLinearReg/code/nwdataPaper1PriorConstruction.R

@@ -1,0 +1,161 @@
+#########################################
+#John Lewis
+#Prior Construction: Using the data from 2008-2010
+#data was prepared on NW laptop: 2008-2010 for prior constuction and 2010-2012 for data
+#########################################
+
+load("../workSpaces/nwdataPrepPaper1DataCleanWorkspace.RData") #not included
+library(plyr)
+library(MASS)
+library(MCMCpack)
+
+#######################################
+#For paper; remove states with fewer than 25 agencies
+stCounts<-table(analysisSet$Primary_Agency_State)
+
+
+
+pairs(~sqrt_Count2010+sqrt_Count2008+Associate_Count+ageMeasure, data=priorDataSet, pch=19, cex=.3)
+
+
+# rlmfit<-rlm(sqrt_Count2012~sqrt_Count2010+Associate_Count+ageMeasure, psi=psi.bisquare, scale.est='Huber',data=analysisSet, maxit=1000)
+# rlmfit$s^2
+# curve(dinvgamma(x,(4+priorRlm$s^2)/priorRlm$s^2,4), from=0, to=10)
+# 
+#regression to for prior information
+
+priorRlm<-rlm(sqrt_Count2010~sqrt_Count2008+Associate_Count+ageMeasure, psi=psi.bisquare, scale.est='Huber',data=priorDataSet, maxit=400)
+priorRlm$s^2
+priorOls<-lm(sqrt_Count2010~sqrt_Count2008+Associate_Count+ageMeasure, data=priorDataSet)
+summary(priorOls)$sigma^2
+
+head(priorDataSet)
+nPrior<-nrow(priorDataSet)
+#plot(priorRlm$residuals)
+summary(priorRlm)
+###############
+#prior mean and variance for beta
+###############
+mu0<-as.numeric(coef(priorRlm))
+#construction of covariance matrix estimate; refer to page 108 maronna
+X<-model.matrix(priorRlm)
+resids<-priorRlm$residuals
+# resids2<-priorDataSet$sqrt_Count2010-fitted(priorRlm)
+# plot(resids,resids)
+n<-nrow(X)
+p<-ncol(X)
+
+sigmahat<-priorRlm$s
+meanPsiSq<-mean(((resids/sigmahat)*psi.bisquare(resids/sigmahat))^2)
+meanPsiPrime<-mean(psi.bisquare(resids/sigmahat, deriv=1))
[…]

### 2018-08-17 submission_1/codeForPaper/simulation/simulation.R

@@ -1,0 +1,159 @@
+#
+# Simulation for paper ----
+#
+
+# 'Complete' represents full data posteriors
+# 'Incomplete' represents our restricted versions
+
+
+rm(list=ls())
+source('simulationSourceCode.R')
+st<-Sys.time()
+set.seed(123) # for reproducible results
+
+concTau2Near1<-0 #1: then concentrate tau^2 prior near 1. 0: then don't and a=b=0
+
+if(concTau2Near1){
+  mu<-1
+  v<-.00001
+  a<-mu^2/v-2 #most prob between .99 and 1.01
+  b<-mu*(a-1)
+} else {
+  a<-0; b<-0
+}
+
+
+sigma2True<-c(.5,1,4,10) #true values of sigma2 to try for the generation of data
+
+#size of MCMC chain
+nburn<-1e4
+nkeep<-1e4
+  
+#print progess after printEach interations
+printEach<-floor(nkeep/10)
+#max number of iterations for the rlm fit
+maxit<-400
+
+for (sig2True in sigma2True){
+
+#
+# Generate the data ----
+#
+
+YList<-fn.gen.data(sig2True)
+factorsList<-YList$factorsList
+factorsMat<-matrix(unlist(factorsList), nrow=90, ncol=3, byrow = TRUE)
+p<-factorsMat[,1]
+n<-factorsMat[,2]
+m<-factorsMat[,3]
+thetaTrue<-YList$theta
+
+YList<-YList$yList
+
+assign(paste0('YList', 'Sig2_', sig2True), YList)
+assign(paste0('thetaTrue', 'Sig2_', sig2True), thetaTrue)
+
+#
+# Fit the complete normal theory model---
+#
+
+
+#intitial values
+
+thetaInt<-rnorm(90, sapply(YList, mean))
+
+muInt<-rnorm(1, mean(thetaInt))
+
+print(paste('begin normal theory fit- sigma2', sig2True))
+
+completeFit<-fn.complete.MCMC(YList, 
+                              nkeep=nkeep, 
+                              nburn=nburn, 
+                              theta=thetaInt, 
+                              sigma2=NULL, 
+                              mu=muInt, 
+                              tau2=NULL,
+                              printEach=printEach, 
+                              a=a, 
+                              b=b)
+
+print(paste('end normal theory fit- sigma2', sig2True))
+
+
+assign(paste0('normalTheoryFit', 'Sig2_', sig2True), completeFit)
[…]

### 2018-08-17 submission_1/codeForPaper/simulation/simulationSourceCode.R

@@ -1,0 +1,421 @@
+#
+# Simulation ------- 
+#
+
+#requires sourcing linearRegressionHuberAndProposal2.R #path may need to be changed
+source('../linearRegressionHuberAndProposal2.R')
+
+
+#
+# Complete Model ----
+# theta_i \sim N(mu, tau^2)
+# Y_ij | \theta_i \sim N(\theta_i, sigma_i^2)  
+# with a fairly flat distribution on mu, tau^2 and sigma_i^2.
+# mu \propto 1, \tau^2 \propto 1/\tau^2, sigma_i^2 \propto \sigma_2^2
+# i runs from 1 to 90
+#
+
+#
+# Data Generation ----
+# see fn.gen.data
+# theta_i~N(0,1) i=1,...,90
+# Y_ij | \theta_i \sim (1-p) N(theta_i, sigma2)+ p N(theta_i,m*sigma2), j=1,...,n_i
+
+#90 groups formed by factorial stucture of the 3 factors
+# n_i=25, 50, 100
+# p= .1,.2,.3
+# m= 9, 25
+# each combination observed in five groups
+# sigma2 also will vary: .5, 1, 4, 10
+
+#
+# 
+# Sampling functions---
+#
+#
+
+# [tau^2 | rest ] ----
+
+# tau^2 \sim IG(a,b) in functional form with a=b=0
+fn.sample.tau2<-function(theta, mu, a=0, b=0){
+  #theta is the vector of theta_i
+  K<-length(theta)
+  anew<-0.5*K+a
+  bnew<-0.5*sum((theta-mu)^2)+b
+  1/rgamma(1, shape=anew, rate=bnew)
+}
+
+# [mu | rest ] ----
+
+fn.sample.mu<-function(theta, tau2){
+  K<-length(theta)
+  rnorm(1, mean(theta),sqrt(tau2/K))
+}
+
+# [sigma2_i| rest ] ----
+# sigma2_i \sim IG(a,b) in functional form with a=b=0
+
+fn.sample.sigma2.i<-function(Yi, thetai, a=0,b=0){
+  # Yi: data vector from ith group
+  # thetai: ith theta
+  n<-length(Yi)
+  anew<-0.5*n+a
+  bnew<-0.5*sum((Yi-thetai)^2)+b
+  1/rgamma(1, shape=anew, rate=bnew)
+}
+
+
+# [theta_i| rest ]
[…]

### 2018-08-17 submission_1/codeForPaper/simulation/summarizeSimulations.R

@@ -1,0 +1,409 @@
+#
+# Summaries of Evaluation Metrics ---
+#
+library('plyr')
+library('reshape2')
+rm(list=ls())
+concTau2Near1<-0
+
+if(concTau2Near1){
+  load('simPostProcessed_concTau2Near1.RData')
+  #load('simPostProcessed2_concTau2Near1.RData')
+} else {
+  load('simPostProcessed.RData')
+  #load('simPostProcessed2.RData')
+}
+
+
+#load('simPostProcessed2_sampleVersion.RData')
+sumNames<-c('Full', 'RestHuber', 'RestTukey', 'RlmHuber','RlmTukey')
+#get(paste0('mse', sumNames[1],'Sig2_', sigma2True[1]))
+
+
+#combine the results into data.frame
+mseDf<-matrix(NA, ncol=9)
+klDf<-matrix(NA, ncol=9)
+#trimMspeDf<-matrix(NA, ncol=9)
+#tlmDf<-matrix(NA, ncol=9)
+
+for(i in 1:length(sigma2True)){
+mseDfTemp<-cbind(factorsMat, sigma2True[i])
+klDfTemp<-cbind(factorsMat, sigma2True[i])
+#trimMspeDfTemp<-cbind(factorsMat, sigma2True[i])
+#tlmDfTemp<-cbind(factorsMat, sigma2True[i])
+
+#meanTlmDfTemp<-cbind(factorsMat, sigma2True[i])
+ for(j in 1:5){
+   mseDfTemp<-cbind(mseDfTemp, get(paste0('mse', sumNames[j],'Sig2_', sigma2True[i])))
+   klDfTemp<-cbind(klDfTemp, get(paste0('kl', sumNames[j],'Sig2_', sigma2True[i])))
+ #  trimMspeDfTemp<-cbind(trimMspeDfTemp, get(paste0('trimMspe', sumNames[j],'Sig2_', sigma2True[i]))/sigma2True[i]) 
+  # tlmDfTemp<-cbind(tlmDfTemp, get(paste0('tlm', sumNames[j],'Sig2_', sigma2True[i]))) 
+#   meanTlmDfTemp<-cbind(meanTlmDfTemp, get(paste0('meanTlm', sumNames[j],'Sig2_', sigma2True[i])))
+ }
+mseDf<-rbind(mseDf, mseDfTemp)
+klDf<-rbind(klDf, klDfTemp)
[…]

### 2018-08-18 revision_1/paper.tex
edits to simulation section and corresponding code

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Simulation}
-Data generating model:
-\begin{equation}
+\section{Applications}
+In this section we apply the restricted likelihood to both simulated and real data.
+
+\subsection{Simulation}
+For this simulation, the true data comes from the following hierarchical data generating model:
+\begin{align}
 \label{gensim2}
 \begin{split}
-\theta_{i}  \sim &  N(\mu, \tau^{2}),  \ i = 1, 2, \dots, 90  \\ 
-y_{ij} \sim & (1-p_{i})N(\theta_{i}, \sigma^{2}) + p_{i}N(\theta_{i}, m_{i}\sigma^{2}), j = 1, 2,..., n_{i}
+& \theta_{i}  \sim   N(\mu, \tau^{2}),  \ i = 1, 2, \dots, 90  \\ 
+& y_{ij} \sim (1-p_{i})N(\theta_{i}, \sigma^{2}) + p_{i}N(\theta_{i}, m_{i}\sigma^{2}), j = 1, 2,..., n_{i}
 \end{split}
-\end{equation}
+\end{align}
 with $\mu = 0, \tau^{2} = 1, \sigma^{2} = 4$.
 The values of $p_{i}, m_{i}$, and $n_{i}$ depend on the group and are formed using 5 replicates of the full factorial design over factors $p_{i},m_{i},n_{i}$ with levels $p_{i} = .1, .2, .3$, $m_{i} = 9, 25$, and $n_{i} = 25, 50, 100$.
+Thus, the 90 groups have a varying level of outlier contamination and sample size.
+We wish to build models that offer good prediction for the good portion of data within each group.
 The full model for fitting is a corresponding normal model without contamination:
@@
 \begin{split}
-\mu \propto 1, \ & \tau^{2} \propto \tau^{-2}, \\
-\theta_{i}\sim N(\mu, \tau^{2}), \ & \sigma^{2}_{i} \sim IG(a_{s}, b_{s}),  \ i = 1, 2, \dots, 90, \\ 
-y_{ij}\sim  N(\theta_{i},\sigma^{2}_{i}), \ j = 1, 2, \dots, n_{i}
+& \mu \propto 1, \  \tau^{2} \propto \tau^{-2}, \\
+& \theta_{i}\sim N(\mu, \tau^{2}), \  \sigma^{2}_{i} \sim IG(a_{s}, b_{s}),  \ i = 1, 2, \dots, 90, \\ 
+& y_{ij}\sim  N(\theta_{i},\sigma^{2}_{i}), \ j = 1, 2, \dots, n_{i}
 \end{split}
@@
 For the restricted likelihood versions we condition on robust M-estimators of location and scale in each group: $T_{i}(\by_{i}) = (\hat\theta_{i}, \hat\sigma^{2}_{i}), i = 1, 2, ..., 90$.
-The two versions used are Huber's and Tukey's location estimator both coupled with Huber's scale estimator.
-The estimates from the Bayesian models are compared to these estimates.
+The two versions use Huber's and Tukey's $\psi$ function, while both versions use Huber's $\chi$ function in $\eqref{Mest}$.
+
 To complete the specification of model \eqref{fullsim2} we must specify $a_{s}$ and $b_{s}$.
@@
 With $c_{s} = 1$ the shrinkage (for large $a_{s}$) is to the true value of $\sigma^{2} = 4$ of the variance of the good component of data in the data generating model.
-We consider $a_{s} = 1.25, 2.5, 5, 10, 20 $ and $c_{s} = 1/2, 1/\sqrt{2}, 1, \sqrt{2}, 2$.
-Values of $c_{s} \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$ with strength growing with $a_{s}$.
-
-A single (\red{maybe need to do more...each run through takes about 3 hours on my laptop and current code, maybe 10 different sets would suffice}) set of data is generated from \eqref{gensim2}.
-The models compared are: the full model \eqref{fullsim2}, the two restricted likelihood versions of this full model, classical robust linear models fit individually to each group.
-
-We compare fits of each model using $MSE = \frac{1}{90}\sum_{i = 1}^{90} (\hat\theta_{i} -\theta_{i})^{2}$ with $\hat\theta_{i}$ the estimate of $\theta_{i}$ from the corresponding model.
-
-Results for MSE
+We consider $a_{s} = 1.25,  5, 10,$ and $c_{s} = 1/2, 1, 2$.
+Values of $c_{s} \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$.
+
+For each simulated data set, the Bayesian models are fit using MCMC.
+The MCMC for the restricted likelihood version requires no further computational details other than those described for the traditional Bayesian model in Section \ref{BayesLinMod}.
+This is because there are conditioning statistics for each group and the model's conditional independence between the groups allows the data augmentation described earlier to be performed independently within each group.
+That is, there is a separate Gibbs step for each group  generating group level data matching the statistics for that group.
+
+The models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution in order to assess the predictive capability of the models for the good part of the data.
+Specifically, the $i^{th}$ group of the $k^{th}$ simulated data set $\by_{k}$ compute:
+\begin{equation}
+\label{kl}
+KL^{(M)}_{ik} = \int \log \frac{f(\tilde y | \theta_{i}, \sigma^{2})}{f_{i}(\tilde y | M, \by_{k})}  f(\tilde y | \theta_{i}, \sigma^{2}) \ dy
+\end{equation}
+where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2})$ and is the pdf of a $N(\theta_{i}, \sigma^{2})$ at $\tilde y$ with $\sigma^{2} = 4$.
+For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ where $ f(\tilde y |\theta_{i}, \sigma_{i}^{2})$ is again a normal pdf and  $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
+$M$ denotes either the full normal theory model \eqref{fullsim2} or one of the two restricted likelihood versions discussed above, where conditioning is only on the summary statistics (not the complete $\by_{k}$).
+For the classical robust fits, we set $f_{i}(\tilde y | M, \by_{k})$ a $N(\hat\theta_{i}, \hat\sigma^{2}_{i})$ at  $\tilde y$ as a plug in estimator for the predictive distribution.
+The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models with $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{K}{K-1}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ used to summarize sampling variation.
+
+Figure \ref{} displays the results for each $a_{s} = 1.25,  5, 10,$ and $c_{s} = 1/2, 1, 2$ over $K = ?? $ data sets.
 
@@
 \centering
-\includegraphics[scale = .3]{mse_sim2_facet_scale.png}
+\includegraphics[width = 6in, height = 4in]{kl_sim2_facet_scale.png}
 \end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[scale = .3]{mse_sim2_facet_as.png}
-\end{figure}
-
-Big picture - restricted methods beating corresponding robust regressions (labeled rlm). MSE robustness to prior on $\sigma_{i}^{2}$
-
-Results for KL (plots are average of the KLs computed for each group):
-\begin{figure}[H]
-\centering
-\includegraphics[scale = .3]{kl_sim2_facet_scale.png}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[scale = .3]{kl_sim2_facet_as.png}
-\end{figure}
+%
+%\begin{figure}[H]
+%\centering
+%\includegraphics[scale = .3]{kl_sim2_facet_as.png}
+%\end{figure}
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[scale = .3]{hist_sig2_ests.png}
-\end{figure}
+%\begin{figure}[H]
+%\centering
+%\includegraphics[scale = .3]{hist_sig2_ests.png}
+%\end{figure}
 

### 2018-08-18 revision_1/code/simulation/hierarchical_sim/1_simulation.R

@@ -4,37 +4,34 @@
 
 # 'Complete' represents full data posteriors
 # 'Incomplete' represents our restricted versions
+library(parallel)
+
+
 
 date() # SteveMod
 
 # rm(list=ls())
 # source('//trad/profs$/maceachern.1/Desktop/LEWIS.LEE/codeForPaper/codeForPaper/simulation/StevesimulationSourceCode.R')
 source('SimulationSourceCode.R')
-st<-Sys.time()
-set.seed(123) # for reproducible results
+st <- Sys.time()
 
-#concTau2Near1<-0 #1: then concentrate tau^2 prior near 1. 0: then don't and a=b=0
+a<-0; b<-0
 
-# if(concTau2Near1){
-#   mu<-1
-#   v<-.00001
-#   a<-mu^2/v-2 #most prob between .99 and 1.01
-#   b<-mu*(a-1)
-# } else {
-  a<-0; b<-0
-# }
 
 
 sigma2True<- 4 #true values of sigma2 to try for #the generation of data
 #sigma2True <- 4  # SteveMod
 #ass <- 1.25 # SteveMod
-ass.vec <- c(1.25, 2.5,5,10,20) #values of shape parameter (alpha) on sigma_i^2 to use.
-scale_vec <- c(0.5, 1/sqrt(2),1, sqrt(2), 2) #values of scale to use to define the scale parameter on sigma_i^2 where  beta_ss = alpha_ss * sig2True * scale. A value of 1 shrinks to the correct value of sigma2.  
+ass.vec <- c(1.25, 5 , 10) #values of shape parameter (alpha) on sigma_i^2 to use. #c(1.25, 2.5, 5 , 10, 20)
+scale_vec <- c(0.5,1, 2) #c(0.5, 1/sqrt(2),1, sqrt(2), 2) #values of scale to use to define the scale parameter on sigma_i^2 where  beta_ss = alpha_ss * sig2True * scale. A value of 1 shrinks to the correct value of sigma2.  
 
 #size of MCMC chain
-nburn <- 1000
-nkeep <- 1000
-  
+nburn <- 1500
+nkeep <- 1500
+
+sims <- 21:30
+set.seed(min(sims)) # for reproducible results
+
 #print progess after printEach interations
 printEach <- floor(nkeep/2)
 #max number of iterations for the rlm fit
@@ -47,12 +44,14 @@ for(sig2True in sigma2True){
 #sigma2True <- 4  # SteveMod
[…]

### 2018-08-18 revision_1/code/simulation/hierarchical_sim/2_summarizeSimulations.R

@@ -3,15 +3,16 @@
 #
 library('tidyverse')
 
-
+sims <- 1:10
+dfs_all <- vector('list', length(sims))
+for(data_sim in sims){
 # load the data, along with the factor levels, and true values of theta
-data <- read_rds(file.path(getwd(),'data_sig2_4', 'data.rds'))
+data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
 n_groups <- length(data$theta)
 results_df <- file.path(getwd(), 'results')
 
-ass.vec <- c(1.25, 2.5,5,10,20) 
-scale_vec <- round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
-
+ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
+scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
 sig2 <- 4
 
 
@@ -22,7 +23,7 @@ i <- 1
 for(ss in sig2){
   for(as in ass.vec){
     for(sc in scale_vec){
-      rds_name <- paste0("__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
+      rds_name <- paste0("_",data_sim, "__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
     
     huber <- read_rds(file.path(results_df, paste0("huber", rds_name)))
     
@@ -77,31 +78,45 @@ for(ss in sig2){
   }
 }
 
-df_estimates <- bind_rows(dfs)
+dfs_all[[data_sim]] <- bind_rows(dfs)
 
+}
 
+df_estimates <- bind_rows(dfs_all, .id = 'simulation')
 
 df_mse <- df_estimates %>% 
+  group_by(simulation, statistic, method, a_s, scale_as, sigma2) %>% 
+  summarise(MSE = mean((theta - theta_hat)^2)) %>% 
+  ungroup() %>% 
   group_by(statistic, method, a_s, scale_as, sigma2) %>% 
-  summarise(MSE = mean((theta - theta_hat)^2))
+  summarise(mean_MSE = mean(MSE), sd_MSE = sd(MSE)) %>% ungroup() %>% 
+  mutate(a_s = as.character(a_s), scale_as = as.character(scale_as))
 
+labels_vals <- scale_color_discrete(name="Method/Statistic",
[…]

### 2018-08-18 revision_1/code/simulation/hierarchical_sim/convergence_checks.R

@@ -1,0 +1,55 @@
+#convergence checks -----
+
+library(MCMCpack)
+library(tidyverse)
+
+
+
+sims <- 1:10
+
+ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
+scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
+
+ss <- 4 #sigma2
+convergence_scores <- array(NA, c(length(sims),3,  length(ass.vec), length(scale_vec), 182)) #sims, models, ass.vec, scale_vec, parameters
+
+for(data_sim in sims){
+  # load the data, along with the factor levels, and true values of theta
+  data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
+  n_groups <- length(data$theta)
+  results_df <- file.path(getwd(), 'results')
+
+    for(as in ass.vec){
+      for(sc in scale_vec){
+        rds_name <- paste0("_",data_sim, "__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
+        
+        fit <- read_rds(file.path(results_df, paste0("huber", rds_name)))
+        th <-  geweke.diag(mcmc(fit$theta))$z
+        sig2 <-  geweke.diag(mcmc(fit$sigma2))$z
+        tauMu <- geweke.diag(mcmc(cbind(fit$mu, fit$tau2)))$z
+        convergence_scores[data_sim, 1, which(as == ass.vec), which(sc == scale_vec),] <- c(th, sig2, tauMu)
+        
+        fit <- read_rds(file.path(results_df, paste0("tukey", rds_name)))
+        th <-  geweke.diag(mcmc(fit$theta))$z
+        sig2 <-  geweke.diag(mcmc(fit$sigma2))$z
+        tauMu <- geweke.diag(mcmc(cbind(fit$mu, fit$tau2)))$z
+        convergence_scores[data_sim, 2, which(as == ass.vec), which(sc == scale_vec),] <- c(th, sig2, tauMu)
+
+        
+        fit <- read_rds(file.path(results_df, paste0("normal", rds_name)))
+        th <-  geweke.diag(mcmc(fit$theta))$z
+        sig2 <-  geweke.diag(mcmc(fit$sigma2))$z
+        tauMu <- geweke.diag(mcmc(cbind(fit$mu, fit$tau2)))$z
[…]

### 2018-08-18 revision_1/paper.tex
starting edits to data anlaysis section

@@
 \centering
-{\includegraphics[width = 4in]{figs/calls_predictive.png}}
+{\includegraphics[width = 6in]{figs/calls_predictive.png}}
 \caption{Predictive distribution of log(calls) under the Normal theory model fit to the non-outliers, the restricted likelihood model with  Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
@@
 %
-% Simulations
+% Applications
 %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Applications}
-In this section we apply the restricted likelihood to both simulated and real data.
-
-\subsection{Simulation}
-For this simulation, the true data comes from the following hierarchical data generating model:
+%\section{Applications}
+%In this section we apply the restricted likelihood to both simulated and real data.
+
+\section{Simulated Data}
+For this study, the simulated data comes from the following hierarchical data generating model:
 \begin{align}
@@
 & \theta_{i}  \sim   N(\mu, \tau^{2}),  \ i = 1, 2, \dots, 90  \\ 
-& y_{ij} \sim (1-p_{i})N(\theta_{i}, \sigma^{2}) + p_{i}N(\theta_{i}, m_{i}\sigma^{2}), j = 1, 2,..., n_{i}
+& y_{ij} \sim (1-p_{i})N(\theta_{i}, \sigma^{2}) + p_{i}N(\theta_{i}, m_{i}\sigma^{2}),\  j = 1, 2,..., n_{i}
 \end{split}
@@
 
-One explaination for the idea that 'shrinking towards smaller values' may do slightly better than shrinking toward the true value is the fact that we used default tuning parameters to define M-Estimators.
+%One explaination for the idea that 'shrinking towards smaller values' may do slightly better than shrinking toward the true value is the fact that we used default tuning parameters to define M-Estimators.
 For the amount of contaimination in each group, the expected value of the variance estimate (Huber's proposal 2) is larger that $\sigma^{2} = 4$.
@@
 %
-% Applications
+% Real data
 %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Applications}
-\label{Applications}
-We illustrate the methods developed in Sections~\ref{restrictedlikelihood} and \ref{BayesLinMod} with a pair of regression models for 
-data from Nationwide Insurance Company, which concern prediction of
-the performance of insurance agencies.
-The data contain outliers and are subject to model misspecification.  
-In particular, a group of the data do not follow the same generative process as the data of interest.  It would be 
-extremely challenging to model some features of the data.  
-In our analysis, we follow the standard practice when demonstrating the benefits of robust 
-methods.  We work with a naive model for the data which ignores certain features of the problem.  We
-do this both to create a situation where all can agree that the model for the full data $\by$ is imperfect
-and to preserve the confidentiality of selected aspects of modelling done by Nationwide.  
-We wish to provide inference for the `good' portion of the data.  The two models we fit either treat the analysis
-as a single regression or as a collection of related regressions.  Details of the models, prior distributions, 
-and conditioning statistics are given in the next two subsections.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%NW data
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Nationwide Data}
-The Nationwide Insurance Company sells many of its insurance policies through agencies which provide direct service to policy holders.  
+\section{Real Data}
+\label{Real Data}
+We illustrate our methods with a pair of regression models for data from Nationwide Insurance Company, which concern prediction of the performance of insurance agencies.
+%The data contain many outliers and are subject to model misspecification.  
+%In particular, a group of the data do not follow the same generative process as the data of interest.  It would be 
+%extremely challenging to model some features of the data.  
+%In our analysis, we follow the standard practice when demonstrating the benefits of robust 
+%methods.  We work with a naive model for the data which ignores certain features of the problem.  We
+%do this both to create a situation where all can agree that the model for the full data $\by$ is imperfect
+%and to preserve the confidentiality of selected aspects of modeling done by Nationwide.  
+%We wish to provide inference for the `good' portion of the data.  %The two models we fit either treat the analysis
+%as a single regression or as a collection of related regressions.  % Details of the models, prior distributions, 
+%and conditioning statistics are given in the next two subsections.  
+%%%%%%%%%%%%%%%%%%%%%%%%
+%%NW data
+%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%\subsection{Nationwide Data}
+Nationwide sells many of its insurance policies through agencies which provide direct service to policy holders.  
 The contractual agreements between Nationwide and these agencies vary.
-Of major interest to Nationwide is the prediction of future performance of agencies where, for our purposes,  performance is measured by the total number of households an agency services (`household count').
-A serviced household is one in which at least one person living at that residence has at least one policy written through the agency.
+Our interest is the prediction of future performance of agencies where  performance is measured by the total number of households an agency services (`household count').
+%A serviced household is one in which at least one person living at that residence has at least one policy written through the agency. 
 We used data from previous years to build a model to forecast future household count.
-In particular, we use agency characteristics, as measured during a single month in $2010$, to predict household counts in the corresponding month in $2012$.
+In particular, we use household count  as measured during a single month in $2010$, to predict household counts in the corresponding month in $2012$.
+%In particular, we use agency characteristics, as measured during a single month in $2010$, to predict household counts in the corresponding month in $2012$.
 The characteristics used are household count and two measurements of agency size/experience.
 The two measurements of agency size/experience are, roughly, the number of employed persons at the agency and the length of time the agency has been affiliated with Nationwide.
-The household counts (response and predictor) have been square rooted to stabilize variance.
-The data are
-proprietary, and to mask them all variables have been individually centered and scaled and identifiers (agency/agent names and state
-labels) have been removed. 
-All subsequent analysis is done on this scale.  As an exploratory view, a plot of the square root of count in 2012, against that in 2010 
-is shown in Figure \ref{fig:ctVct}.
-The different colors represent the varying contractual agreements as they stood in 2010.
-`Type 1' agencies are of special interest.
-Among the open agencies, a strong linear correlation exists.
-The specific linear relationship
-depends on agency type.
-The data are characterized by a large number of agencies which were open in 2010 but closed sometime before 2012, as represented by the horizontal band at $0$.
-We use these data as a test bed for our techniques, fitting models that do not account for agency closures or contract type.
-Our expectation is that \green{\sout{the incomplete} restricting the} likelihood will facilitate prediction for the good part of the data.
-
-\begin{figure}[t]
+%The household counts (response and predictor) have been square rooted to stabilize variance. 
+The data a grouped by states with a varying number of agencies by state.
+Identifiers such as agency/agent names are removed.
+State labels and agency types (identifying the varying contractual agreements) have been made generic to protect the proprietary nature of the data.
+%The data are proprietary, and to mask them all variables have been individually centered and scaled and identifiers (agency/agent names and state labels) have been removed.All subsequent analysis is done on this scale.
+As an exploratory view, a plot of the square root of household count in 2012, against that in 2010 
+is shown in Figure \ref{fig:ctVct} for three states.
+Each state has a varying number of agencies and  the different colors represent the varying contractual agreements as they stood in 2010.
+Among the open agencies, linear correlations exists with strength depending on agency type and state.
+`Type 1' agencies are of special interest and one could easily subset the analysis to only these agencies, removing the others.
+Additionally, a large number of agencies closed sometime before 2012, as represented by the many $0$ counts for 2012.
+The other agency types and the zero counts are `outliers' and could arguably just be removed prior to analysis.
+However,  we leave them and us the data as a test bed for our techniques by fitting models that do not account for agency closures or contract type.
+Our expectation is that the restricting likelihood will facilitate prediction for the `good' part of the data (i.e.
+open, `type 1' agencies).
+
+\begin{figure}[H]
 \centering
-\includegraphics[width=4in]{countvcount.pdf}
+\includegraphics[width=6in]{scatter_by_state.png}
 \caption{The square root of count in 2012 versus that in 2010 (after centering and scaling).
@@
 \label{regModelNW}
-The first analysis that we consider is based on a single regression.  We use 
-the following standard normal theory regression model 
+The first analysis considered is based on individual regressions fit separately within a state.  The following normal theory regression model is used as the full model 
 \begin{equation}
 \label{eq:regModel}
-\bbeta\sim N_p(\bmu_0, \Sigma_0);\ \ \sigma^2\sim IG(a_0,b_0);\ \  
-y_{i}=\bx_{i}^\top\bbeta+\epsilon_{i},\ \ \epsilon_{i}\iid N(0, \sigma^2),\ i=1,\dots, n, 
+\beta\sim N(\mu_0, \sigma^{2}_0);\ \ \sigma^2\sim IG(a_0,b_0);\ \  
+y_{i}=\beta x_{i} +\epsilon_{i},\ \ \epsilon_{i}\iid N(0, \sigma^2),\ i=1,\dots, n, 
 \end{equation}
-where $\bbeta$ is a four dimensional vector ($p=4$) of regression coefficients for the intercept, square root of count in 2010, and the two size/experience measures, and $y_{i}$ is the square rooted household count in 2012 for the $i^{th}$ agency with covariate vector $\bx_{i}$.
-Although the mean of covariates and response have been removed, we include the intercept as fitting is done on a holdout set to evaluate predictive performance.
-The hyper-parameters $a_0, b_0, \bmu_0$ and $\Sigma_0$ are all fixed and set from a 
-robust regression fit to the data from the time period two years
+%where $\beta$ is a four dimensional vector ($p=4$) of regression coefficients for the intercept, square root of count in 2010, and the two size/experience measures, and 
+where $y_{i}$ and $x_{i}$ are the square rooted household count in 2012 and 2010 for the $i^{th}$ agency, respectively. 
+%with covariate vector $\bx_{i}$.  Although the mean of covariates and response have been removed, we include the intercept as fitting is done on a holdout set to evaluate predictive performance.  
+The hyper-parameters $a_0, b_0, \mu_0$ and $\sigma^{2}_0$ are all fixed and set from a 
+robust regression fit to the corresponding state's data from the time period two years
 before.
-Letting $\hat\bbeta$ represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
+Specifically, Let $\hat\beta$ and $\hat\sigma^{2}$ be estimates from the robust linear regression of 2010 counts on 2012 counts.
+We fix $a_0 = 5$ and set $b_0 = \hat\sigma^{2}(a_0 - 1)$.
+We set $\mu_0 = \hat\beta$ and $\sigma^{2}_0 =  fn_{p}se(\hat\beta)^{2}$ where $n_{p}$ is the number of agencies in the prior data set and $se(\hat\beta)$ is the standard error of $\hat\beta$ derived from the robust regression.
+The value of $f$ is varied, controlling the prior certainty on $\beta$, with smaller values corresponding to a more certain prior.
+We take $f = 0.05, 0.1, 0.5, 1$ and note the prior is in the spirit of the Zellner's $g$-prior \citep{zellner1986, liang2008}; scaling the prior variance $se(\hat\beta)^{2}$ by a factor $g = fn_{p}$.
+$f = 1$ is analogous to the unit-information prior \citep{kass1995reference}.
+%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
 %corresponding to  a unit information prior for $\bbeta$.
-The hyperparameters for $\sigma^2$ are set so that the prior mean is $s^2$, the estimated variance from the robust regression, and the spread of the prior covers the range of plausible values with high probability.
+%The hyperparameters for $\sigma^2$ are set so that the prior mean is $s^2$, the estimated variance from the robust regression, and the spread of the prior covers the range of plausible values with high probability.
 All values are then transformed appropriately to match the current scale of the data.

### 2018-08-18 revision_1/code/data_analysis/single_group_reg_analysis.R

@@ -15,14 +15,15 @@ ns <- c(10, 25, 50) #percent sample size for training set
 states <- c(2,3,27)
 v_inflate <- c(5, 10, 50, 100)
 
-reps <- 20 # number of training sets
+sims <-1:20
+reps <-  length(sims)# number of training sets
 
 nburn <- 1000 #set length of mcmc chains
 nkeep <- 1000
 nkeept <- 1000 #for the t-model.
 nu <- 3
 #set seed 
-set.seed(123)
+set.seed(min(sims))
 
 for(State_keep in states){
 #prior -----
@@ -65,7 +66,7 @@ analysis_data <- analysis_data %>%
 N <- nrow(analysis_data)
 p <- length(coef(prior_fit))
 
-for(n_percent in ns){
+for(n_percent in ns){ # percent to use as training set. 
   n <- floor(n_percent*N/100)
   # Set storing objects -----
   
@@ -130,7 +131,7 @@ for(n_percent in ns){
   
   # simulation -----
   system.time(  
-    for(i in 1:reps){
+    for(i in sims){
       
       trainIndices <- sort(sample(1:N, n))
       holdIndices <- c(1:N)[-trainIndices]

### 2018-08-18 revision_1/code/data_analysis/summarize_single_reg_analysis.R

@@ -7,6 +7,33 @@ ns <- c(10, 25, 50) #sample size for training set
 states <- c(2,3,27)
 v_inflate <- c(5, 10, 50, 100)
 
+# plots ---- 
+analysis_data <- read_rds(file.path(here::here(), 'data', 'analysis_data.rds'))
+
+analysis_data <- analysis_data %>% 
+  mutate(sqrt_count_2010 = sqrt(Count_2010), sqrt_count_2012 = sqrt(Count_2012)) %>% filter(State %in% states)
+
+
+ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, col = Type), size = 1, alpha = .5) +
+  theme_bw() + 
+  labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
+  theme(text = element_text(family = 'Times'))
+ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_all.png'), width = 6, height = 4)
+
+
+
+analysis_data %>% group_by(State) %>% 
+  summarise(n = n())
+
+ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, col = Type), size = 1, alpha = .25) +
+  facet_wrap(~State, labeller = label_bquote(State ~ .(State)))+ 
+  theme_bw() + 
+  labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
+  theme(text = element_text(family = 'Times'))
+ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+
+
+
 
 logical_ytibble <- function(y_open, colname){
   #works on y_open, y_type1 logical matrices

### 2018-08-18 revision_1/code/simulation/hierarchical_sim/convergence_checks.R

@@ -5,7 +5,7 @@ library(tidyverse)
 
 
 
-sims <- 1:10
+sims <- c(1)
 
 ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
 scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)

### 2018-08-19 revision_1/paper.tex
finishing up hiearchical simulation example

@@
 \section{Simulated Data}
-For this study, the simulated data comes from the following hierarchical data generating model:
+We study the performance of the restricted likelihood in a hierarchical setting contaminated with outliers. Specifically, simulated data come from the following data generating model:
 \begin{align}
@@
 The values of $p_{i}, m_{i}$, and $n_{i}$ depend on the group and are formed using 5 replicates of the full factorial design over factors $p_{i},m_{i},n_{i}$ with levels $p_{i} = .1, .2, .3$, $m_{i} = 9, 25$, and $n_{i} = 25, 50, 100$.
-Thus, the 90 groups have a varying level of outlier contamination and sample size.
+This results in 90 groups that have varying levels of outlier contamination and sample size.
 We wish to build models that offer good prediction for the good portion of data within each group.
@@
 & \theta_{i}\sim N(\mu, \tau^{2}), \  \sigma^{2}_{i} \sim IG(a_{s}, b_{s}),  \ i = 1, 2, \dots, 90, \\ 
-& y_{ij}\sim  N(\theta_{i},\sigma^{2}_{i}), \ j = 1, 2, \dots, n_{i}
+& y_{ij}\sim  N(\theta_{i},\sigma^{2}_{i}), \ j = 1, 2, \dots, n_{i}.
 \end{split}
@@
 The two versions use Huber's and Tukey's $\psi$ function, while both versions use Huber's $\chi$ function in $\eqref{Mest}$.
+These estimators are implemented in the R function \texttt{MASS::rlm} and \ref{huber2009} provides further details on them.
 
@@
 For each we set $b_{s} = 4a_{s}c_{s}$ resulting in a prior mean for each $\sigma^{2}_{i}$ of $\frac{4c_{s}a_{s}}{a_{s}-1}, \ a_{s} >1$.
-The larger $a_{s}$, the more informative the prior.
+The precision is $\frac{(a_{s} -1)^{2}(a_{s}-2)}{(4c_{s}a_{s})^{2}}$; meaning the larger $a_{s}$, the more informative the prior.
 With $c_{s} = 1$ the shrinkage (for large $a_{s}$) is to the true value of $\sigma^{2} = 4$ of the variance of the good component of data in the data generating model.
-We consider $a_{s} = 1.25,  5, 10,$ and $c_{s} = 1/2, 1, 2$.
-Values of $c_{s} \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$.
+We consider $a_{s} = 1.25,  5, 10$ and $c_{s} = 1/2, 1, 2$.
+%Values of $c_{s} \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$.
 
@@
 The models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution in order to assess the predictive capability of the models for the good part of the data.
-Specifically, the $i^{th}$ group of the $k^{th}$ simulated data set $\by_{k}$ compute:
+Specifically, for the $i^{th}$ group of the $k^{th}$ simulated data set $\by_{k}$ compute:
 \begin{equation}
@@
 \end{equation}
-where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2})$ and is the pdf of a $N(\theta_{i}, \sigma^{2})$ at $\tilde y$ with $\sigma^{2} = 4$.
-For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ where $ f(\tilde y |\theta_{i}, \sigma_{i}^{2})$ is again a normal pdf and  $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
+where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2})$ is the pdf of a $N(\theta_{i}, \sigma^{2})$ at $\tilde y$ with $\sigma^{2} = 4$.
+For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ where $ f(\tilde y |\theta_{i}, \sigma_{i}^{2})$ is  $N(\theta_{i}, \sigma_{i}^{2})$ pdf and  $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
 $M$ denotes either the full normal theory model \eqref{fullsim2} or one of the two restricted likelihood versions discussed above, where conditioning is only on the summary statistics (not the complete $\by_{k}$).
-For the classical robust fits, we set $f_{i}(\tilde y | M, \by_{k})$ a $N(\hat\theta_{i}, \hat\sigma^{2}_{i})$ at  $\tilde y$ as a plug in estimator for the predictive distribution.
-The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models with $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{K}{K-1}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ used to summarize sampling variation.
-
-Figure \ref{} displays the results for each $a_{s} = 1.25,  5, 10,$ and $c_{s} = 1/2, 1, 2$ over $K = ?? $ data sets.
+$M$ also specifies the hyperparameter values $a_{s}$ and $c_{s}$.
+For the classical robust fits, we set $f_{i}(\tilde y | M, \by_{k})$ to a $N(\hat\theta_{i}, \hat\sigma^{2}_{i})$ at  $\tilde y$ as a groupwise plug-in estimator for the predictive distribution.
+Thus the classical fits are done separately for each group - with no consideration of the hierarchical structure between the groups.
+The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models.
+Sampling variation is summarized with $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
+
+Figure \ref{kl_sim} displays the results for each $a_{s} = 1.25,  5, 10$ and $c_{s} = 1/2, 1, 2$ over $K = 30$ data sets.
+The panels are for $c_{s} = 1/2, 1, 2$ with $a_{s} = 1.25,  5, 10$ on the abscissa.
+For each panel, the KL results for the classical robust linear model fits are the same since the priors have no effect on these fits.
+The normal theory model results are left out as they perform poorly.
+Overall, the results are strikingly in favor of the restricted likelihood methods for the range of hyper-parameter values studied.
+Undoubtably, the most precise and accurate prior studied is  $c_{s} = 1$ and $a_{s} = 10$ and this results in the lowest (and best) average KL for both the Tukey and Huber restricted likelihood versions.
+$c_{s} = 0.5$ performs the worst, but still better than the classical fits.
+There is evidence that performance starts to degrade as $a_{s} = 10$ as reflected in a larger average KL for $a_{s} = 10$.
+Here, the prior mean and precision are $2.22$ and $1.62$ and we suspect this is starting to put too much mass on $\sigma^{2}_{i}$ values much smaller than $\sigma^{2}=4$.
+For $c_{s} = 2$, the performance still improves from $a_{s} = 5$ to $a_{s} = 10$.
+Here the mean is $8.89$ and precision is only $0.1$; not yet large enough to degrade the performance due to an incorrect mean.
 
@@
 \includegraphics[width = 6in, height = 4in]{kl_sim2_facet_scale.png}
+\label{kl_sim}
+\caption{summary of simulation}
 \end{figure}
+
+It is also interesting to look at the effects of $n_{i}$, $p_{i}$, and $m_{i}$. For this, the  $KL^{(M)}_{ik}$ are grouped by
+
 %

### 2018-08-19 revision_1/code/simulation/hierarchical_sim/2_summarizeSimulations.R

@@ -3,7 +3,7 @@
 #
 library('tidyverse')
 
-sims <- 1:10
+sims <- 1:30
 dfs_all <- vector('list', length(sims))
 for(data_sim in sims){
 # load the data, along with the factor levels, and true values of theta
@@ -297,7 +297,81 @@ ggsave(file.path(getwd(), "..", "..", "..", "figs", 'kl_sim2_facet_as.png'), wid
 saveRDS(list(df_kl, df_estimates), file = 'summarize_data_frames.rds')
 # investigate convergence of variance estimators in mixture model ---
 
+# Effects of n, p, or m
 
+#note the rlm results are simply repeated for each a_s and scale_as - when grouping by n (or p, or m) - the averages for each simulation are computed over the repeated results too - but these averages are the same as if one result was used. The SE are computed as the sd of these averages - so it doesn't change the calculation if I subset the rlm results to get rid of the repeats
+# n ----
+df_kl %>% filter(method == 'rlm', statistic == 'Huber', simulation == '1')
+df_kl %>% filter(method == 'restricted', statistic == 'Huber', simulation == '1')
+
+
+df_kl_mean_n <- df_kl %>% #filter(method != 'rlm') %>% 
+  group_by(simulation, n, statistic, method, sigma2) %>% 
+  summarise(KL = mean(KL)) %>% 
+  ungroup() %>% 
+  group_by(n, statistic, method, sigma2) %>% 
+  summarise(mean_KL = mean(KL), sd_KL = sd(KL), num = n())
+
+# df_kl_mean_n_rlm  <- df_kl %>% filter(method == 'rlm', a_s == '5', scale_as == '2') %>% group_by(simulation, n, statistic, method, sigma2) %>%
+#   summarise(KL = mean(KL)) %>%
+#   ungroup() %>%
+#   group_by(n, statistic, method, sigma2) %>%
+#   summarise(mean_KL = mean(KL), sd_KL = sd(KL), num = n())
+
+
+#bind_rows(df_kl_mean_n, df_kl_mean_n_rlm)
+ggplot(df_kl_mean_n %>% filter(method != 'Normal', statistic != 'Normal') , aes(x = as.factor(n), y = mean_KL, col = interaction(method,statistic), group = interaction(method,statistic))) + 
[…]

### 2018-08-19 revision_1/code/simulation/hierarchical_sim/convergence_checks.R

@@ -5,11 +5,10 @@ library(tidyverse)
 
 
 
-sims <- c(1)
+sims <- 1:30
 
 ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
 scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
-
 ss <- 4 #sigma2
 convergence_scores <- array(NA, c(length(sims),3,  length(ass.vec), length(scale_vec), 182)) #sims, models, ass.vec, scale_vec, parameters
 
@@ -53,3 +52,41 @@ mean(abs(convergence_scores)>2)
 range(convergence_scores[,1,,,])
 range(convergence_scores[,2,,,])
 range(convergence_scores[,3,,,])
+saveRDS(convergence_scores, "summarize_convergence.rds")
+
+
+
+library(MCMCpack)
+summary(rinvgamma(1000, 10, 4*2*10))
+summary(rinvgamma(1000, 10, 4*.5*10))
+
+f1 <- function(x){
+  a <- 10
+  c <- 2
+  b <- 4*a*c
+  dinvgamma(x, a, b)
+}
+
+f2 <- function(x){
+  a <- 10
+  c <- 0.5
+  b <- 4*a*c
+  dinvgamma(x, a, b)
+}
+
+integrate(f1, 4, Inf)
+integrate(f2, 4, Inf)
+
+
+curve(f2, from = 0, to = 20, col = 2)
+curve(f1, from = 0, to = 20, add = TRUE)
+abline(v = 4)
+
+
+a <- 100
+c <- 2
+b <- 4*a*c
+
+
+b/(a -1)
+(b^2/((a-1)^2*(a-2)))^-1

### 2018-08-19 revision_1/paper.tex
edits to simulation section, added ba laTeX templet

@@
-\documentclass[12pt]{article}
-%\documentclass[ba]{imsart}
-
-\usepackage{fullpage,amsmath}% mathtools}
-\usepackage{setspace}
+\RequirePackage{etoolbox}
+\csdef{input@path}{%
+ {sty/}% cls, sty files
+ {img/}% eps files
+}%
+\csgdef{bibdir}{bib/}% bst, bib files
+
+\documentclass[ba]{imsart}
+%
+\pubyear{0000}
+\volume{00}
+\issue{0}
+\doi{0000}
+\firstpage{1}
+\lastpage{1}
+
+%
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{natbib}
+\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
+\usepackage{graphicx}
+
+\startlocaldefs
+
+\endlocaldefs
+
+%\usepackage{fullpage,amsmath}% mathtools}
+%\usepackage{setspace}
 \usepackage{graphicx, psfrag, amsfonts, float}
@@
 %\usepackage{color}
-\usepackage[position=t,singlelinecheck=off]{subcaption}
-\usepackage{caption, setspace}
+%\usepackage[position=t,singlelinecheck=off]{subcaption}
+%\usepackage{caption, setspace}
 %\usepackage[position=t,singlelinecheck=off]{subfigure}
@@
 %\newpage
-\title{Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression}
-\author{John R. Lewis, Steven N. MacEachern and  Yoonkyung Lee \\
-{\small \it Department of Statistics, The Ohio State University, Columbus, Ohio 43210}\\
-{\small lewis.865@osu.edu, snm@stat.osu.edu and yklee@stat.osu.edu}
-\thanks{This research has been supported by Nationwide Insurance Company and by the NSF under grant numbers DMS-1007682 and DMS-1209194.
-The views in this paper are not necessarily those of Nationwide Insurance or the NSF.}}
+
 \begin{document}
-\date{}
-\maketitle
+
+\begin{frontmatter}
+\title{Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression\thanksref{T1}}
+\runtitle{Bayesian Restricted Likelihood Methods}
+\thankstext{T1}{This research has been supported by Nationwide Insurance Company and by the NSF under grant numbers DMS-1007682 and DMS-1209194.
+The views in this paper are not necessarily those of Nationwide Insurance or the NSF.}
+
+\begin{aug}
+\author{\fnms{John R.} \snm{Lewis}\thanksref{addr1,m1}\ead[label=e1]{lewis.865@osu.edu}}, 
+\author{\fnms{Steven N.} \snm{MacEachern}\thanksref{addr1,m1}\ead[label=e2]{snm@stat.osu.edu}}, 
+\and  
+\author{\fnms{Yoonkyung} \snm{Lee}\thanksref{addr1,m1}\ead[label=e3]{yklee@stat.osu.edu}} \\
+%{\small \it Department of Statistics, The Ohio State University, Columbus, Ohio 43210}\\
+%{\small lewis.865@osu.edu, snm@stat.osu.edu and yklee@stat.osu.edu}
+\runauthor{J. Lewis et al}
+
+\address[addr1]{Department of Statistics, The Ohio State University, Columbus, Ohio 43210 
+    \printead{e1}, % print email address of "e1"
+    \printead*{e2},
+    \printead*{e3}
+}
+\end{aug}
 
@@
 for conditioning statistics. With these choices, the method can be thought of as a
-blend of classical robust estimation and Bayesian methods.
-
-A major contribution of this work is the development of a data 
+blend of classical robust estimation and Bayesian methods. A major contribution of this work is the development of a data 
 augmented Markov chain Monte Carlo (MCMC) algorithm
@@
 methods.
-
-\noindent KEYWORDS: Approximate Bayesian computation, Markov chain
-Monte Carlo, M-estimation, Robust regression.
-
 \end{abstract}
+%\noindent KEYWORDS: Approximate Bayesian computation, Markov chain
+%Monte Carlo, M-estimation, Robust regression.
+
+%\begin{keyword}[class=MSC]
+%\kwd[Primary ]{60K35}
+%\kwd{60K35}
+%\kwd[; secondary ]{60K35}
+%\end{keyword}
+
+\begin{keyword}
+\kwd{Approximate Bayesian computation}
+\kwd{Markov chain Monte Carlo}
+\kwd{M-estimation}
+\kwd{Robust regression}
+\end{keyword}
+
+\end{frontmatter}
 
@@
 Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)  Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
-Associated tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \cite{huber1964} and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+Associated tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
 Additionally, two other common approaches to outlier handling are fit: 1) replacing the normal distribution with a t-distribution and, 2) replacing the normal distribution with a mixture of two normals.
@@
 The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models.
-The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ assuming the prior $p \sim beta(20,1)$ on the probability of belonging to the `good' component.
-
-The posteriors of $\beta$ under each model appear in top of Figure \ref{fig:newcomb_post}.
+The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ assuming the prior $p \sim \beta(20,1)$ on the probability of belonging to the `good' component.
+
+The posteriors of $\beta$ under each model appear in Figure \ref{fig:newcomb_post}.
 As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy tailed model provides robustness against them.
@@
 The M-estimators provide the most precise posteriors in this case.
-This is reflected in more precise predictions than the heavy-tailed and mixture model as illustrated by the predictive distributions displayed in the bottom of Figure \ref{fig:newcomb_post}.
-
-\begin{figure}
+This is reflected in more precise predictions than the heavy-tailed and mixture model as illustrated by the predictive distributions displayed in  Figure \ref{fig:newcomb_predictive}.
+\begin{figure}[t]
 \centering
-\begin{subfigure}{\textwidth}
-{\includegraphics[width = 6in]{figs/speed_of_light_beta.png}}
-%\caption{}
-%\label{fig:newcomb_beta}
-\end{subfigure}
-\centering
-\begin{subfigure}{\textwidth}
-{\includegraphics[width = 6in]{figs/speed_of_light_predictive.png}}
-%\caption{}
-%\label{fig:newcomb_predictive}
-\end{subfigure}
-\caption{Top: Posteriors of the location parameter $\beta$ under the normal theory model, the t-model, and four restricted likelihood models for Newcomb's speed of light measurements.
-Bottom: Posterior predictive distribution of the speed of light under the normal theory model, the t-model, and four restricted likelihood models.}
+{\includegraphics[width = 4in]{figs/speed_of_light_beta.png}}
+{\includegraphics[width = 4in]{figs/speed_of_light_predictive.png}}
+\caption{asdfdfa}
 \label{fig:newcomb_post}
 \end{figure}
+
+%\begin{figure}[t]
+%\centering
+%{\includegraphics[width = 4in]{figs/speed_of_light_predictive.png}}
+%\caption{dfsfsa}
+%\label{fig:newcomb_predictive}
+%\end{figure}
+%\caption{Top: Posteriors of the location parameter $\beta$ under the normal theory model, the t-model, and four restricted likelihood models for Newcomb's speed of light measurements.
+Bottom: Posterior predictive distribution of the speed of light under the normal theory model, the t-model, and four restricted likelihood models.}
+%\label{fig:newcomb_post}
+%\end{figure}
 
@@
 In particular, $\Sigma_{0} = g\sigma_{0}^2 (X^{\top}X)^{-1}$, with $\sigma_{0} = 0.03$ and $\mu_{0} = (1.87,  0.03)^{\top}$; the MLEs fit to the first three data points.
-There are $n=21$ remaining data points and the parameter $g$ is set to $21$ reflecting a unit information prior \cite{}.
+There are $n=21$ remaining data points and the parameter $g$ is set to $21$ reflecting a unit information prior \citep{kass1995reference}.
 Finally $a = 2$ and $b =1$ for the normal theory and restricted likelihood models.
@@
 The mixture model assumes different mean regression functions and variances for each component, but keeps the same, relatively non-informative priors.
-The probability of belonging to the first component is given a $beta(5,1)$ prior.
+The probability of belonging to the first component is given a $\beta(5,1)$ prior.
 The heavy-tailed model fixes the degrees of freedom to 5 with the same adjustment to the prior on $\sigma^{2}$ as above.
@@
 Like classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
-
-\begin{figure}
+\begin{figure}[t]
 \centering
-{\includegraphics[width = 6in]{figs/calls_predictive.png}}
+{\includegraphics[width = 4in]{figs/calls_predictive.png}}
 \caption{Predictive distribution of log(calls) under the Normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
@@
  The Gibbs sampler \citep{gelfand1990} iteratively samples from the
- full conditionals 
- \begin{enumerate}
- \item $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ 
- \item $f(\by|\bth, T(\by)=T(\by_{obs}))$.  
- \end{enumerate}
-When $\by$ has the summary statistic $T(\by) = T(\by_{obs})$,
+ full conditionals 1) $\pi(\bth|\by, T(\by)=T(\by_{obs}))$ and 2) $f(\by|\bth, T(\by)=T(\by_{obs}))$.  When $\by$ has the summary statistic $T(\by) = T(\by_{obs})$,
 the first full conditional is the same as the full data posterior $\pi(\bth|\by)$.
@@
 \begin{eqnarray*}
-f(\by | \bth, \by \in \mathcal{A}) & = & \frac{f(\by | \bth) I(\by \in \mathcal{A} | \by, \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} \\
-     & = & \frac{f(\by | \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} 
+f(\by | \bth, \by \in \mathcal{A}) =  \frac{f(\by | \bth) I(\by \in \mathcal{A} | \by, \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} 
+      = \frac{f(\by | \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} 
 \end{eqnarray*}
@@
 \centering
-\includegraphics[width=4in]{minSS3dSampleSpace.jpg}
+\includegraphics[width=2.75in]{minSS3dSampleSpace.jpg}
 \caption{A depiction of $\mathcal{A}$, $\Pi(\mathcal{A})$, and the
@@
 
-\begin{sidewaysfigure}[t]
+%\begin{sidewaysfigure}[t]
+%\centering
+%\captionsetup{justification=centering}
+%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace3.pdf}}\quad
+%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
+%\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
+%  to $\bz$. The adjustment for the stretch transforms the density
+%  along the unit circle to the density along the circle of radius
+%  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
+%  deformation from the distribution along the circle to the
+%  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
+%  be the cosine of the angle between the normals to each manifold.}
+%\label{fig:stretchDeform}
+%\end{sidewaysfigure}
+
+\begin{figure}[t]
 \centering
-\captionsetup{justification=centering}
-\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace3.pdf}}\quad
-\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
-\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
-  to $\bz$. The adjustment for the stretch transforms the density
-  along the unit circle to the density along the circle of radius
-  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
-  deformation from the distribution along the circle to the
-  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
-  be the cosine of the angle between the normals to each manifold.}
+{\includegraphics[width=2.9in]{minSSZSpace3.pdf}}
+{\includegraphics[width=2.9in]{minSSZSpace5.pdf}}
 \label{fig:stretchDeform}
-\end{sidewaysfigure}
+\caption{sdasfda}
+\end{figure}
+
+%\begin{figure}[t]
+%\centering
+%{\includegraphics[width=2in]{minSSZSpace5.pdf}}
+%\label{fig:stretchDeform}
+%\caption{sdassfsadfda}
+%\end{figure}
+%%
+%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
+%\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
+%  to $\bz$. The adjustment for the stretch transforms the density
+%  along the unit circle to the density along the circle of radius
+%  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
+%  deformation from the distribution along the circle to the
+%  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
+%  be the cosine of the angle between the normals to each manifold.}
+%\label{fig:stretchDeform}
+%\end{sidewaysfigure}
 
@@
 \end{equation}
-For the restricted likelihood versions we condition on robust M-estimators of location and scale in each group: $T_{i}(\by_{i}) = (\hat\theta_{i}, \hat\sigma^{2}_{i}), i = 1, 2, ..., 90$.
+For the restricted likelihood versions we condition on robust M-estimators (see,$\eqref{Mest}$) of location and scale in each group: $T_{i}(y_{i1}, \dots, y_{in_{i}}) = (\hat\theta_{i}, \hat\sigma^{2}_{i}), i = 1, 2, ..., 90$.
 The two versions use Huber's and Tukey's $\psi$ function, while both versions use Huber's $\chi$ function in $\eqref{Mest}$.
-These estimators are implemented in the R function \texttt{MASS::rlm} and \ref{huber2009} provides further details on them.
-
-To complete the specification of model \eqref{fullsim2} we must specify $a_{s}$ and $b_{s}$.
-For this we use a variety of values representing different levels of prior knowledge.
-For each we set $b_{s} = 4a_{s}c_{s}$ resulting in a prior mean for each $\sigma^{2}_{i}$ of $\frac{4c_{s}a_{s}}{a_{s}-1}, \ a_{s} >1$.
-The precision is $\frac{(a_{s} -1)^{2}(a_{s}-2)}{(4c_{s}a_{s})^{2}}$; meaning the larger $a_{s}$, the more informative the prior.
-With $c_{s} = 1$ the shrinkage (for large $a_{s}$) is to the true value of $\sigma^{2} = 4$ of the variance of the good component of data in the data generating model.
-We consider $a_{s} = 1.25,  5, 10$ and $c_{s} = 1/2, 1, 2$.
-%Values of $c_{s} \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$.
-
-For each simulated data set, the Bayesian models are fit using MCMC.
+The tuning parameters are chosen so that the estimators are $95\%$ efficient under normally distributed data \citep{huber2009}.
+%We will see that his choice has some interesting effects on the results.
+%These estimators are implemented in the R function \texttt{MASS::rlm} with \cite{huber2009} providing further details.
+
+To complete the specification of model \eqref{fullsim2},  $a_{s}$ and $b_{s}$ are fixed to a variety of values representing different levels of prior knowledge.
+For each we set $b_{s} = 4a_{s}c$ resulting in a prior mean for each $\sigma^{2}_{i}$ of $\frac{4ca_{s}}{a_{s}-1}, \ a_{s} >1$.
+The precision is $\frac{(a_{s} -1)^{2}(a_{s}-2)}{(4ca_{s})^{2}}$; meaning the larger $a_{s}$, the more informative the prior.
+With $c = 1$ the shrinkage (for large $a_{s}$) is to the true value of $\sigma^{2} = 4$.
+We consider $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$.
+%Values of $c \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$.
+
+$K = 30$ data sets are generated from \eqref{gensim2}.
+For each data set and each pair $(a_{s}, c)$, the Bayesian models are fit using MCMC.
 The MCMC for the restricted likelihood version requires no further computational details other than those described for the traditional Bayesian model in Section \ref{BayesLinMod}.
@@
 
-The models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution in order to assess the predictive capability of the models for the good part of the data.
+To assess the predictive capability, the models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution.
 Specifically, for the $i^{th}$ group of the $k^{th}$ simulated data set $\by_{k}$ compute:
@@
 \end{equation}
-where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2})$ is the pdf of a $N(\theta_{i}, \sigma^{2})$ at $\tilde y$ with $\sigma^{2} = 4$.
-For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ where $ f(\tilde y |\theta_{i}, \sigma_{i}^{2})$ is  $N(\theta_{i}, \sigma_{i}^{2})$ pdf and  $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
-$M$ denotes either the full normal theory model \eqref{fullsim2} or one of the two restricted likelihood versions discussed above, where conditioning is only on the summary statistics (not the complete $\by_{k}$).
-$M$ also specifies the hyperparameter values $a_{s}$ and $c_{s}$.
-For the classical robust fits, we set $f_{i}(\tilde y | M, \by_{k})$ to a $N(\hat\theta_{i}, \hat\sigma^{2}_{i})$ at  $\tilde y$ as a groupwise plug-in estimator for the predictive distribution.
-Thus the classical fits are done separately for each group - with no consideration of the hierarchical structure between the groups.
+where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2}) = N(\tilde y | \theta_{i}, \sigma^{2})$; the mean $\theta_{i}$, variance $\sigma^{2}$ normal pdf evaluated at $\tilde y$.
+For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})d\theta_{i}d\sigma^{2}_{i}$ where $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
+$M$ denotes either the full normal theory model \eqref{fullsim2} or one of the two restricted likelihood versions, along with $a_{s}$ and $c$.
+For the classical robust fits, we set $f_{i}(\tilde y | M, \by_{k}) = N(\tilde y|\hat\theta_{i}, \hat\sigma^{2}_{i})$ as a groupwise plug-in estimator for the predictive distribution.
+The classical fits are done separately for each group with no consideration of the hierarchical structure between the groups.
 The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models.
-Sampling variation is summarized with $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
-
-Figure \ref{kl_sim} displays the results for each $a_{s} = 1.25,  5, 10$ and $c_{s} = 1/2, 1, 2$ over $K = 30$ data sets.
-The panels are for $c_{s} = 1/2, 1, 2$ with $a_{s} = 1.25,  5, 10$ on the abscissa.
-For each panel, the KL results for the classical robust linear model fits are the same since the priors have no effect on these fits.
-The normal theory model results are left out as they perform poorly.
+Sampling variation is summarized with the standard error $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
+
+Figure \ref{kl_sim} displays $\overline{KL}^{(M)}_{{\cdot}{\cdot}}$  with errors-bars plus/minus one $SE(\overline{KL}^{(M)}_{{\cdot} k})$ for each $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$.
+%The panels are for $c = 0.5, 1, 2$ with $a_{s} = 1.25,  5, 10$ on the abscissa.
+The values of $a_{s}$ and $c$, do not effect the classical robust linear models.
+The normal theory model results are left out as they perform significant worse.
 Overall, the results are strikingly in favor of the restricted likelihood methods for the range of hyper-parameter values studied.
-Undoubtably, the most precise and accurate prior studied is  $c_{s} = 1$ and $a_{s} = 10$ and this results in the lowest (and best) average KL for both the Tukey and Huber restricted likelihood versions.
-$c_{s} = 0.5$ performs the worst, but still better than the classical fits.
+Undoubtably, the most precise and accurate prior studied is  $c = 1$ and $a_{s} = 10$  and this results in the lowest (and best) average KL for both the Tukey and Huber restricted likelihood versions ((shown in the middle panel).
+$c = 0.5$ performs the worst, but still better than the classical fits.
 There is evidence that performance starts to degrade as $a_{s} = 10$ as reflected in a larger average KL for $a_{s} = 10$.
 Here, the prior mean and precision are $2.22$ and $1.62$ and we suspect this is starting to put too much mass on $\sigma^{2}_{i}$ values much smaller than $\sigma^{2}=4$.
-For $c_{s} = 2$, the performance still improves from $a_{s} = 5$ to $a_{s} = 10$.
-Here the mean is $8.89$ and precision is only $0.1$; not yet large enough to degrade the performance due to an incorrect mean.
-
-\begin{figure}[H]
+For $c = 2$, the performance still improves from $a_{s} = 5$ to $a_{s} = 10$.
+Here the mean is $8.89$ and precision is only $0.1$; apparently not yet large enough to degrade the performance due to an incorrect mean.
+Lastly, Tukey's statistic performs marginally better than Huber's.
+This is likely due to the fact that Tukey's estimator trims extreme outliers completely in the estimation procedure \citep{huber2009}.
+
+\begin{figure}[t]
 \centering
-\includegraphics[width = 6in, height = 4in]{kl_sim2_facet_scale.png}
+\includegraphics[width = 4in]{kl_sim2_facet_scale.png}
 \label{kl_sim}
-\caption{summary of simulation}
+\caption{Average KL - divergence plus/minus one standard error for each value of $a_{s}$ and $c$.
+The panels correspond to $c = 0.5$ (left), $c=1$ (middle), and $c=2$ (right) with the values of $a_{s}$ on the horizontal axis.}
 \end{figure}
 
-It is also interesting to look at the effects of $n_{i}$, $p_{i}$, and $m_{i}$. For this, the  $KL^{(M)}_{ik}$ are grouped by
+It is also interesting to consider the effects of factors $n_{i}$, $p_{i}$, and $m_{i}$.
+For a given factor and simulation, the $KL^{(M)}_{ik}$  are averaged by factor level.
+For the Bayesian models, the averages are also taken over the different values of $a_{s}$ and $c$.
+Figure \ref{kl_mnp} displays these averages for $m,n,$ and $p$ with error bars plus/minus one standard error.
+The restricted likelihood versions consistently perform better than their classical counterparts.
+Intuitively, as the amount of contamination ($p$) increases performance degrades as it becomes more difficult to identify the good data.
+Likewise, as $n$ increases, the performance for the Bayesian methods become closer to that of the their classical counterparts reflecting the diminishing effect of the prior.
+However, the decrease of KL-diveregence with $m$ and increase with $n$ is somewhat surprising.
+To investigate, Figure \ref{boxTheta} and \ref{boxSigma} display boxplots of $(\theta_{i} - \hat\theta_{i})$ and $\hat\sigma_{i}$ for each simulated data set.
+The $\hat\theta_{i}$'s have no systematic bias however the $\hat\sigma_{i}$'s do; consistently biased upward from the value of $\sigma = 2$ for the good portion of data.
+As $n$ increases, the bias remains the same and the variation in the estimates gets smaller.
+Thus, the estimates are getting more certain about an incorrect value; explaining the degradation of the KL - divergence.
+As $m$ increases, the variance in the estimates gets larger and there is a marginal increase in the bias.
+Thus, for $m=9$ there is more certainty about an incorrect value and  the increased uncertainty at $m=25$ helps to improve the KL-divergence.
+%Finally, as $p$ grows the bias of the estimates gets significantly larger; resulting in poorer estimation and poorer KL-divergences.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width = 4in]{kl_sim2_mnp.png}
+\caption{Average KL - divergence plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right)}
+\label{kl_mnp}
+\end{figure}
+\begin{figure}[t]
+\centering
+\includegraphics[width = 4in]{rlm_mnp_theta.png}
+\caption{Boxplots $(\theta_{i} - \hat\theta_{i})$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right) where $\hat\theta_{i}$ are the classical robust estimators (Huber's and Tukey's).}
+\label{boxTheta}
+\end{figure}
+\begin{figure}[t]
+\centering
+\includegraphics[width = 4in]{rlm_mnp_sigma.png}
+\caption{Boxplots of the classical robust estimators (Huber's and Tukey's) for $\sigma_{i}$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right).
+The horizontal line at $\sigma = 2$ highlights the true standard deviation of the `good' data.}
+\label{boxSigma}
+\end{figure}
+
+This simulation shows the potential of the restricted likelihood while highlighting some interesting observations.
+Specifically, the choice of summary statistics, along with corresponding tuning parameters is important.
+The parameters chosen to be $95\%$ at the normal result in bias estimates of the variance under the data generating model.
+Such bias can result in undesirable properties, such as poorer prediction as the sample size grows.
+These choices must be made in both the classical and Bayesian settings.
+The Bayesian setting allows for the incorporation of informative prior information which, as shown in this example, can dramatically improve prediction.
+The amount of improvement, of course, depends on the prior but here we have observed good relative improvement over the classical counterparts for a range of prior choices.
 
@@
 
-\begin{figure}[H]
+\begin{figure}[t]
 \centering
-\includegraphics[width=6in]{scatter_by_state.png}
+\includegraphics[width=5in]{scatter_by_state.png}
 \caption{The square root of count in 2012 versus that in 2010 (after centering and scaling).
@@
 
-\begin{sidewaysfigure}
-\centering
-\captionsetup{justification=centering}
-%\subcaptionbox{}{\includegraphics[width=\textwidth,page=1]{logMargType1AgenciesBaseModelt}}\quad
-%\subcaptionbox{}{\includegraphics[width=\textwidth,page=2]{logMargType1AgenciesBaseModelt}}\quad
-%\subcaptionbox{}{\includegraphics[width=\textwidth,page=3]{logMargType1AgenciesBaseModelt}}
-\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in, page=1]{logMargType1AgenciesBaseModelt}}\quad
-\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=2]{logMargType1AgenciesBaseModelt}}\quad
-\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=3]{logMargType1AgenciesBaseModelt}}
-\caption{Model evaluation for `Type 1' agencies for training sample
-  sizes of $n=25,100$, and $1000$. The $t$-model is used as the base
-  method to compute TLM. Plotted are the mean TLM for each model
-  against the trimming fraction across the $100$ cross-validation
-  samples. Error bars correspond to one standard deviation of TLM
-  above and below the mean. Models are labeled with the following
-  abbreviations: `rlm' corresponds to a classical robust fit, `restr.'
-  corresponds to our restricted likelihood method, and `t' corresponds to the
-  heavy-tailed $t$-distribution model. The letters `T' and `H'
-  appearing after `rlm' and `restr.' correspond to the use of  Tukey's
-  and Huber's $\psi$ respectively.  
-}
-\label{fig:Type1Marg}
-\end{sidewaysfigure}
+%\begin{sidewaysfigure}
+%\centering
+%\captionsetup{justification=centering}
+%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=1]{logMargType1AgenciesBaseModelt}}\quad
+%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=2]{logMargType1AgenciesBaseModelt}}\quad
+%%\subcaptionbox{}{\includegraphics[width=\textwidth,page=3]{logMargType1AgenciesBaseModelt}}
+%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in, page=1]{logMargType1AgenciesBaseModelt}}\quad
+%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=2]{logMargType1AgenciesBaseModelt}}\quad
+%\subcaptionbox{}{\includegraphics[width=3.4in,height=3.3in,page=3]{logMargType1AgenciesBaseModelt}}
+%\caption{Model evaluation for `Type 1' agencies for training sample
+%  sizes of $n=25,100$, and $1000$. The $t$-model is used as the base
+%  method to compute TLM. Plotted are the mean TLM for each model
+%  against the trimming fraction across the $100$ cross-validation
+%  samples. Error bars correspond to one standard deviation of TLM
+%  above and below the mean. Models are labeled with the following
+%  abbreviations: `rlm' corresponds to a classical robust fit, `restr.'
+%  corresponds to our restricted likelihood method, and `t' corresponds to the
+%  heavy-tailed $t$-distribution model. The letters `T' and `H'
+%  appearing after `rlm' and `restr.' correspond to the use of  Tukey's
+%  and Huber's $\psi$ respectively.  
+%}
+%\label{fig:Type1Marg}
+%\end{sidewaysfigure}
+%
 
@@
 
-\begin{sidewaysfigure}[t]
-%\subcaptionbox{}{\includegraphics[width=2.75in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
-%\subcaptionbox{}{\includegraphics[width=2.75in,page=2]{hierlogMargType1AgenciesBaseModelt}}
-\subcaptionbox{}{\includegraphics[width=4in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
-\subcaptionbox{}{\includegraphics[width=4in,page=2]{hierlogMargType1AgenciesBaseModelt}}
-\caption{Model evaluation for `Type 1' agencies under the hierarchical model for $n=1000$ and $2000$.
+%\begin{sidewaysfigure}[t]
+%%\subcaptionbox{}{\includegraphics[width=2.75in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
+%%\subcaptionbox{}{\includegraphics[width=2.75in,page=2]{hierlogMargType1AgenciesBaseModelt}}
+%\subcaptionbox{}{\includegraphics[width=4in,page=1]{hierlogMargType1AgenciesBaseModelt}}\quad
+%\subcaptionbox{}{\includegraphics[width=4in,page=2]{hierlogMargType1AgenciesBaseModelt}}
+%\caption{Model evaluation for `Type 1' agencies under the hierarchical model for $n=1000$ and $2000$.
 The $t$-model is used as the base method to compute TLM.
@@
 Only the relevant trimming fractions ($\alpha\geq .15$) are pictured.
-}
-\label{fig:hierType1Marg}
-\end{sidewaysfigure}
-
-\subsection{Comparison of hierarchical and non-hierarchical fits}
-
-The performance of the methods for the hierarchical and non-hierarchical models can be contrasted through our cross validations studies.
+%}
+%\label{fig:hierType1Marg}
+%\end{sidewaysfigure}
+%
+
+%
+%\subsection{Comparison of hierarchical and non-hierarchical fits}
+%
+%The performance of the methods for the hierarchical and non-hierarchical models can be contrasted through our cross validations studies.
 We focus on Tukey's and Huber's conditioning statistic and concentrate our evaluation on the `Type 1' agencies.
@@
 Our summary below focuses exclusively on realistic trimming fractions, $\alpha \geq 0.15$, and Tukey's conditioning statistic.
-
-We first note that for the non-hierarchical model, there is little difference between mean TLM for $n=1000$ and $n=2000$, with 
-the numbers differing only in the third decimal place (see rows 1 and 3 of the table).  This is due to the posterior predictive distributions having stabilized.  The
-mean TLMs for the hierarchical model show a greater change with increases of about $0.05$ to $0.08$ as the training sample size changes
-from $1000$ to $2000$ (see rows 2 and 4 of the table).  For calibration, the mean TLM for a normal with mean $0.5$ and variance $1$ is approximately this size
-when trimming is done under a standard normal base model.  Thus, the increase in mean TLM is substantial.  
-We attribute the change for the hierarchical model to the 
-improvement in fits, particularly for states with fewer agencies.
-
-Direct comparison of the hierarchical and non-hierarchical models shows that, for $n=1000$, the non-hierarchical model has uniformly 
-(for $\alpha$ of interest) better mean TLM (rows 1 and 2).
+%
+%We first note that for the non-hierarchical model, there is little difference between mean TLM for $n=1000$ and $n=2000$, with 
+%the numbers differing only in the third decimal place (see rows 1 and 3 of the table).  This is due to the posterior predictive distributions having stabilized.  The
+%mean TLMs for the hierarchical model show a greater change with increases of about $0.05$ to $0.08$ as the training sample size changes
+%from $1000$ to $2000$ (see rows 2 and 4 of the table).  For calibration, the mean TLM for a normal with mean $0.5$ and variance $1$ is approximately this size
+%when trimming is done under a standard normal base model.  Thus, the increase in mean TLM is substantial.  
+%We attribute the change for the hierarchical model to the 
+%improvement in fits, particularly for states with fewer agencies.  
+%
+%Direct comparison of the hierarchical and non-hierarchical models shows that, for $n=1000$, the non-hierarchical model has uniformly 
+%(for $\alpha$ of interest) better mean TLM (rows 1 and 2).
 The differences are substantial, and the summaries primarily reflect greater stability of fits on a state-by-state basis under the non-hierarchical model.
@@
 We attribute the better performance of the non-hierarchical model for the largest trimming fractions to variation in the evaluation.
-
-\begin{table}[!tbp]
-{\small
-\begin{center}
-\begin{tabular}{lllll}
-\hline\hline
-& \multicolumn{4}{c}{Trimming fraction ($\alpha$)}\\
-\multicolumn{1}{l}{}&\multicolumn{1}{c}{$0.15$}&\multicolumn{1}{c}{$0.2$}&\multicolumn{1}{c}{$0.25$}&\multicolumn{1}{c}{$0.3$}\tabularnewline
-\hline
-{\mdseries Tukey ($n=1000$)}&&&&\tabularnewline
-~~Non-Hier.&1.072 (0.014)&1.179 (0.022)&1.226 (0.029)&1.255 (0.033)\tabularnewline
-~~Hier.&1.021 (0.063)&1.110 (0.070)&1.157 (0.067)&1.187 (0.065)\tabularnewline
-\hline
-{\mdseries Tukey ($n=2000$) }&&&&\tabularnewline
-~~Non-Hier.&1.068 (0.029)&1.178 (0.007)&1.225 (0.011)&1.254 (0.014)\tabularnewline
-~~Hier.&1.094 (0.041)&1.189 (0.036)&1.221 (0.033)&1.242 (0.028)\tabularnewline
-\hline
-{\mdseries Huber  ($n=1000$)}&&&&\tabularnewline
-~~Non-Hier.&1.020 (0.020)&1.114 (0.035)&1.157 (0.041)&1.184 (0.045)\tabularnewline
-~~Hier.&0.861 (0.073)&0.937 (0.079)&1.001 (0.074)&1.063 (0.064)\tabularnewline
-\hline
-{\mdseries Huber ($n=2000$)}&&&&\tabularnewline
-~~Non-Hier.&1.015 (0.021)&1.112 (0.014)&1.154 (0.019)&1.181 (0.023)\tabularnewline
-~~Hier.&0.930 (0.041)&1.014 (0.043)&1.080 (0.035)&1.148 (0.027)\tabularnewline
-\hline
-\end{tabular}
-\end{center}
-\caption{Mean (standard deviation) of TLM for `Type 1' agencies for the Bayesian restricted likelihood non-hierarchical and hierarchical models for $n=1000$ and $2000$.} \label{tab:tlmTable}
-}
-\end{table}
+%
+%\begin{table}[!tbp]
+%{\small
+%\begin{center}
+%\begin{tabular}{lllll}
+%\hline\hline
+%& \multicolumn{4}{c}{Trimming fraction ($\alpha$)}\\
+%\multicolumn{1}{l}{}&\multicolumn{1}{c}{$0.15$}&\multicolumn{1}{c}{$0.2$}&\multicolumn{1}{c}{$0.25$}&\multicolumn{1}{c}{$0.3$}\tabularnewline
+%\hline
+%{\mdseries Tukey ($n=1000$)}&&&&\tabularnewline
+%~~Non-Hier.&1.072 (0.014)&1.179 (0.022)&1.226 (0.029)&1.255 (0.033)\tabularnewline
+%~~Hier.&1.021 (0.063)&1.110 (0.070)&1.157 (0.067)&1.187 (0.065)\tabularnewline
+%\hline
+%{\mdseries Tukey ($n=2000$) }&&&&\tabularnewline
+%~~Non-Hier.&1.068 (0.029)&1.178 (0.007)&1.225 (0.011)&1.254 (0.014)\tabularnewline
+%~~Hier.&1.094 (0.041)&1.189 (0.036)&1.221 (0.033)&1.242 (0.028)\tabularnewline
+%\hline
+%{\mdseries Huber  ($n=1000$)}&&&&\tabularnewline
+%~~Non-Hier.&1.020 (0.020)&1.114 (0.035)&1.157 (0.041)&1.184 (0.045)\tabularnewline
+%~~Hier.&0.861 (0.073)&0.937 (0.079)&1.001 (0.074)&1.063 (0.064)\tabularnewline
+%\hline
+%{\mdseries Huber ($n=2000$)}&&&&\tabularnewline
+%~~Non-Hier.&1.015 (0.021)&1.112 (0.014)&1.154 (0.019)&1.181 (0.023)\tabularnewline
+%~~Hier.&0.930 (0.041)&1.014 (0.043)&1.080 (0.035)&1.148 (0.027)\tabularnewline
+%\hline
+%\end{tabular}
+%\end{center}
+%\caption{Mean (standard deviation) of TLM for `Type 1' agencies for the Bayesian restricted likelihood non-hierarchical and hierarchical models for $n=1000$ and $2000$.} \label{tab:tlmTable}
+%}
+%\end{table}
+%
 
@@
 
-\bibliographystyle{apalike}
+\bibliographystyle{ba}
 \bibliography{refPaper1}

### 2018-08-24 revision_1/paper.tex
commite before running long hierarchical analysis run.

@@
 \section{Simulated Data}
+\label{simData}
 We study the performance of the restricted likelihood in a hierarchical setting contaminated with outliers. Specifically, simulated data come from the following data generating model:
@@
 \end{equation}
-For the restricted likelihood versions we condition on robust M-estimators (see,$\eqref{Mest}$) of location and scale in each group: $T_{i}(y_{i1}, \dots, y_{in_{i}}) = (\hat\theta_{i}, \hat\sigma^{2}_{i}), i = 1, 2, ..., 90$.
-The two versions use Huber's and Tukey's $\psi$ function, while both versions use Huber's $\chi$ function in $\eqref{Mest}$.
-The tuning parameters are chosen so that the estimators are $95\%$ efficient under normally distributed data \citep{huber2009}.
+For the restricted likelihood versions we condition on robust M-estimators of location and scale in each group: $T_{i}(y_{i1}, \dots, y_{in_{i}}) = (\hat\theta_{i}, \hat\sigma^{2}_{i}), i = 1, 2, ..., 90$.
+These estimators are solutions to equation \eqref{Mest} (where $x_{i}\equiv 1$) with user specified $\psi$ and $\chi$ functions designed to discount outliers.
+The two versions use Huber's and Tukey's $\psi$ function, while both versions use Huber's $\chi$ function.
+The tuning parameters associate with these functions are chosen so that the estimators are $95\%$ efficient under normally distributed data.
+Both of these are well known M-estimators used in robust regression settings  \citep{huber2009}.
 %We will see that his choice has some interesting effects on the results.
@@
 The classical fits are done separately for each group with no consideration of the hierarchical structure between the groups.
-The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models.
+The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models where smaller means correspond to better fits.
 Sampling variation is summarized with the standard error $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
 
-Figure \ref{kl_sim} displays $\overline{KL}^{(M)}_{{\cdot}{\cdot}}$  with errors-bars plus/minus one $SE(\overline{KL}^{(M)}_{{\cdot} k})$ for each $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$.
+Figure \ref{kl_sim} displays $\overline{KL}^{(M)}_{{\cdot}{\cdot}}$  with error-bars plus/minus one $SE(\overline{KL}^{(M)}_{{\cdot} k})$ for each $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$.
 %The panels are for $c = 0.5, 1, 2$ with $a_{s} = 1.25,  5, 10$ on the abscissa.
@@
 Specifically, the choice of summary statistics, along with corresponding tuning parameters is important.
-The parameters chosen to be $95\%$ at the normal result in bias estimates of the variance under the data generating model.
-Such bias can result in undesirable properties, such as poorer prediction as the sample size grows.
+For the tuning parameters, the standard choice of $95\%$ efficiency at the normal was used.
+Under the data generating model here, this choice results in bias in the scale estimation which affects the performance of the method.
 These choices must be made in both the classical and Bayesian settings.
 The Bayesian setting allows for the incorporation of informative prior information which, as shown in this example, can dramatically improve prediction.
-The amount of improvement, of course, depends on the prior but here we have observed good relative improvement over the classical counterparts for a range of prior choices.
+The results are sensitive to the prior, but here we have observed good relative improvement over the classical counterparts for a range of prior choices.
 
@@
 %A serviced household is one in which at least one person living at that residence has at least one policy written through the agency. 
-We used data from previous years to build a model to forecast future household count.
+%We used data from previous years to build a model to forecast future household count.
 In particular, we use household count  as measured during a single month in $2010$, to predict household counts in the corresponding month in $2012$.
@@
 Identifiers such as agency/agent names are removed.
-State labels and agency types (identifying the varying contractual agreements) have been made generic to protect the proprietary nature of the data.
+Likewise, state labels and agency types (identifying the varying contractual agreements) have been made generic to protect the proprietary nature of the data.
 %The data are proprietary, and to mask them all variables have been individually centered and scaled and identifiers (agency/agent names and state labels) have been removed.All subsequent analysis is done on this scale.
 As an exploratory view, a plot of the square root of household count in 2012, against that in 2010 
-is shown in Figure \ref{fig:ctVct} for three states.
-Each state has a varying number of agencies and  the different colors represent the varying contractual agreements as they stood in 2010.
+is shown in Figure \ref{fig:ctVct} for four states.
+The states have varying number of agencies and  the different colors represent the varying types of contractual agreements as they stood in 2010 (`Type').
+A significant number of agencies closed sometime before 2012, as represented by the $0$ counts for 2012.
 Among the open agencies, linear correlations exists with strength depending on agency type and state.
-`Type 1' agencies are of special interest and one could easily subset the analysis to only these agencies, removing the others.
-Additionally, a large number of agencies closed sometime before 2012, as represented by the many $0$ counts for 2012.
-The other agency types and the zero counts are `outliers' and could arguably just be removed prior to analysis.
-However,  we leave them and us the data as a test bed for our techniques by fitting models that do not account for agency closures or contract type.
+`Type 1' agencies open in 2012 are of special interest and one could easily subset the analysis to only these agencies, removing the others.
+However,  we leave them and use the data as a test bed for our techniques by fitting models that do not account for agency closures or contract type.
 Our expectation is that the restricting likelihood will facilitate prediction for the `good' part of the data (i.e.
@@
 
-\subsection{Regression model}
+\subsection{State Level Regression model}
 \label{regModelNW}
-The first analysis considered is based on individual regressions fit separately within a state.  The following normal theory regression model is used as the full model 
+The first analysis considered is based on individual regressions fit separately within states.  The following normal theory regression model is used as the full model for a single state:
 \begin{equation}
@@
 before.
-Specifically, Let $\hat\beta$ and $\hat\sigma^{2}$ be estimates from the robust linear regression of 2010 counts on 2012 counts.
-We fix $a_0 = 5$ and set $b_0 = \hat\sigma^{2}(a_0 - 1)$.
-We set $\mu_0 = \hat\beta$ and $\sigma^{2}_0 =  fn_{p}se(\hat\beta)^{2}$ where $n_{p}$ is the number of agencies in the prior data set and $se(\hat\beta)$ is the standard error of $\hat\beta$ derived from the robust regression.
-The value of $f$ is varied, controlling the prior certainty on $\beta$, with smaller values corresponding to a more certain prior.
-We take $f = 0.05, 0.1, 0.5, 1$ and note the prior is in the spirit of the Zellner's $g$-prior \citep{zellner1986, liang2008}; scaling the prior variance $se(\hat\beta)^{2}$ by a factor $g = fn_{p}$.
-$f = 1$ is analogous to the unit-information prior \citep{kass1995reference}.
-%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
+Specifically, Let $\hat\beta$ and $\hat\sigma^{2}$ be estimates from the robust linear regression of 2010 counts on 2008 counts.
+We fix $a_0 = 5$ and set $b_0 = \hat\sigma^{2}(a_0 - 1)$ so the prior mean is $\hat\sigma^{2}$.
+We set $\mu_0 = \hat\beta$ and $\sigma^{2}_0 =  n_{p}se(\hat\beta)^{2}$ where $n_{p}$ is the number of agencies in the prior data set and $se(\hat\beta)$ is the standard error of $\hat\beta$ derived from the robust regression.
+%The value of $f$ is varied, controlling the prior certainty on $\beta$, with smaller values corresponding to a more certain prior.
+This prior is in the spirit of the Zellner's $g$-prior \citep{zellner1986, liang2008}; in general scaling the prior variance $se(\hat\beta)^{2}$ by a factor $g$.
+$g = n_{p}$ is analogous to the unit-information prior \citep{kass1995reference}, with the difference that we are using a prior data set, not the current data set, to set the prior.
+%$f = 0.05, 0.1, 0.5, 1$ and%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
 %corresponding to  a unit information prior for $\bbeta$.
@@
 We compare four Bayesian models: the standard Bayesian normal theory model, two restricted likelihood models, both with simultaneous M-estimators, and a heavy-tailed model.
-For the restricted likelihood methods we use the same simultaneous M-estimators as in Section \ref{darwinAnalysis} adapted to linear regression.
-The heavy-tailed model replaces the normal sampling density in \eqref{eq:regModel} with a $t$-distribution with $\nu = 3$ degrees of freedom.
-%We have used the default tuning parameter settings for the {\tt rlm} function in the R package {\tt MASS} \citep{venables2002}.
-Both use Huber's scale estimator as in the {\tt rlm} implementation.
+For the restricted likelihood methods we use the same simultaneous M-estimators as in the simulation of Section \ref{simData} adapted to linear regression.
+The heavy-tailed model replaces the normal sampling density in \eqref{eq:regModel} with a $t$-distribution with $\nu = 5$ degrees of freedom.
+The Bayesian models are all fit using MCMC, with the restricted versions using the algorithm presented in Section \ref{highDim}.
 We also fit the corresponding classical robust regressions and a least squares regression.
@@
 problem.  Since we are concerned with outliers and model 
-misspecification, we understand that our models are imperfect and so prefer to use an out-of-sample measure of fit.  
+misspecification, we understand that our models are imperfect and prefer to use an out-of-sample measure of fit.  
 This leads us to cross-validation.  We repeatedly split the data into training
-and validation sets.  We fit the model to the training data and assess its performance on the validation data.
+and holdout data sets; fitting the model to the training data and assessing performance on the holdout data.
 
@@
 
-The trimmed evaluation proceeds as follows in our context.  The evaluation function for case $i$ in the hold-out data
+The trimmed evaluation proceeds as follows in our context.  The evaluation function for case $i$ in the holdout data
 is the log predictive density, say
@@
 we first identify a base method. Denote the predictive density under this method by $f_{b}(y)$.  Under the base method, $\log(f_{b}(y_i))$ is computed for each case in the 
-validation sample, say $i = 1, \ldots, M$.  Order the validation
-sample according to the ordering of $\log(f_{b}(y_i))$ and denote this
+holdout sample, say $i = 1, \ldots, M$.  Order the holdout sample according to the ordering of $\log(f_{b}(y_i))$ and denote this
 ordering by $y_{(1)}^b, y_{(2)}^b, \dots, y_{(M)}^b$. That is, for $i<j$
-$\log(f_{b}(y_{(i)}^b))<\log(f_{b}(y_{(j)}^b))$. All of the methods are then scored on the validation sample with the mean trimmed log marginal pseudo likelihood, 
+$\log(f_{b}(y_{(i)}^b))<\log(f_{b}(y_{(j)}^b))$. All of the methods are then scored on the holdout sample with the mean trimmed log marginal pseudo likelihood, 
 \[TLM_b(A) = (M - [\alpha M])^{-1} \sum_{i=[\alpha M]+1}^{M}
@@
 removed from the validation sample and all of the methods are scored using only the
-remaining $M - [\alpha M]$ observations. This process is advantageous to the base method.  A method
-that performs poorly when it is the base method is discredited.  For a complete evaluation, we allow each method
-to appear as the base method.  For brevity, we present only a selection of results in our subsequent analyses.
+remaining $M - [\alpha M]$ observations. This process is advantageous to the base method since the smallest scores from this method are guarenteed to be trimmed.  A method
+that performs poorly when it is the base method is discredited.  %For a complete evaluation, we allow each method
+%to appear as the base method.  For brevity, we present only a selection of results in our subsequent analyses.
 
 \subsubsection{Comparison of predictive performance}
-Model performance is assessed
-using the mean and standard deviation of the TLM 
-across $100$ different splits into training and validation samples. First, we include all observations
-in each validation sample to calculate TLM for each split. We then
-repeat the evaluation using only certain subsets of the validation
-sample that are of special interest. Subsets include open agencies,
-open `Type 1' agencies, and `Type 1' agencies. For brevity, we include
-results for the `Type 1' agencies only. As noted, assessing model
-predictions on this set of agencies is of special interest to the
-company.  A range of training sample sizes was used and we include
-results from $n=25,100,1000,$ and $2000$ out of a total of $3180$ agencies.
-The trimming fraction, $\alpha$, ranges from $0$ to $0.3$.
+%Model performance is assessed using the mean and standard deviation of the TLM 
+%across $K = 50$ different splits into training and holdout samples. 
+`Type 1' agencies are of special interest to the company and so the evaluation of the TLM is done on only holdout samples of `Type 1', wheres the training is done on agencies of all types.
+This is intended to demonstrate the robustness properties of the various methods.
+%First, we include all observations
+%in each validation sample to calculate TLM for each split. We then
+%repeat the evaluation using only certain subsets of the validation
+%sample that are of special interest. Subsets include open agencies,
+%open `Type 1' agencies, and `Type 1' agencies. For brevity, we include
+%results for the `Type 1' agencies only. As noted, assessing model
+%predictions on this set of agencies is of special interest to the
+%company.  A range of training sample sizes was used and we include
+%results from $n=25,100,1000,$ and $2000$ out of a total of $3180$ agencies. 
+%The trimming fraction, $\alpha$, ranges from $0$ to $0.3$.
 A classical robust regression to the prior data assigns zero weight to around $16\%$ of observations; in essence removing these from the analysis.
 This informed the range of trimming fractions chosen.
-In practice, we would set $\alpha$ slightly larger than $0.16$.
+%In practice, we would set $\alpha$ slightly larger than $0.16$.  
+Models are fit to four states labelled State 2, 15, 27, and 36, with $n = 222, 40, 117,$ and $46$, representing a range of sample sizes.
+Training sample sizes are taken to be $.25n$ and $0.50n$ with holdout evaluation done on the remaining (`Type 1`) samples.
+The average $TLM_b(A)$ over $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student - t model and $\alpha = 0.3$.
+Similar results are observed for other base models, with this one being most advantageous to the Student - t model.
+The error-bars are plus/minus one standard deviation of the average $TLM_b(A)$ over the $K = 50$  training/holdout samples.
+It is clear the normal Bayesian model used as the base model (Normal) and the classical ordinary least squares fits (OLS) have poor performance, as expected, due to the significant amount of outlier contamination in the data.
+In comparing are restricted methods to their corresponding classical methods, there is small, but consistent improvement across the states and training sample size.
+For state 2, the largest state with $n = 222$, the restricted and classical robust methods have similar performance especially for larger training sample size.
+This reflects the diminishing effect of the prior as the sample size grows.
+Notably, the Student - t model performs poorly in comparison for this state.
+The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good` data (i.e.
+the Type 1 agencies).
+Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.
+For the other states, the Student-t performs similarly to our restricted methods for the smaller states (State 15 and 36) and smaller training size (25\% of the sample).
+However, the performance is worse for the larger training size (50\% of the sample).
+Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model; detrimental for prediction.
+The relative performance of the models are similar for various values $\alpha$.
+Figure \ref{fig:tlmbyAlpha} shows the results for one state (State 27) with training sample size $0.5n$ as an example.
+
+%A mixture model could replace the heavy-tailed model.
+We assert it is more difficult to refine a mixture model in this setting reflecting the different types of outliers including the zero counts and agency types.
+The appeal of the restricted likelihood (and the classical robust approaches) is the avoidance of refining the model to capture (potentially transient) outlier generating mechanisms.
+Instead, the modeler focuses on estimating quantities of interest via statistics $T(\by)$.
+The improvement in our restricted likelihood versions over the classical robust fits is due to the informative prior distributions.
+In this case, similar data from previous years was used to formulate the prior.
+Like all Bayesian methods, performance is affected by the prior and it is important the prior accurately reflects the prior state of knowledge.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=6in]{tlm_base_Student-t.png}
+\caption{Average TLM plus/minus one standard deviation over $K = 50$ splits into training and holdout samples.
+The panels are for the different states  2, 15, 27, and 36, with $n = 222, 40, 117,$ and $46$, respectively.
+The horizontal axis is the percent of $n$ used in each training set.
+The color corresponds to the fitting model.
+}
+\label{fig:tlm}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=6in]{tlm_base_Student-tbyTrimming.png}
+\caption{Average TLM plus/minus one standard deviation over $K = 50$ splits into training and holdout samples for several values of the trimming fraction $\alpha$.
+The training sample size used is $0.5n$.}
+\label{fig:tlmbyAlpha}
+\end{figure}
 
@@
 
-Model evaluation for `Type 1' agencies is shown in Figure
-\ref{fig:Type1Marg} for training sample sizes $n=25, 100,$ and $1000$.
-The $t$-model is used as the base
-  method to compute TLM.
-The models pictured are: classical robust regression with Tukey's $\psi$ function (rlm-T), restricted likelihood with Tukey $\psi$ (restr.-T), classical robust regression with Huber's $\psi$ function (rlm-H), restricted likelihood  with Huber's $\psi$ (restr.-H), and the thick tailed $t$-model (t).
+%Model evaluation for `Type 1' agencies is shown in Figure
+%\ref{fig:Type1Marg} for training sample sizes $n=25, 100,$ and $1000$.
+%The $t$-model is used as the base
+%  method to compute TLM.
+%The models pictured are: classical robust regression with Tukey's $\psi$ function (rlm-T), restricted likelihood with Tukey $\psi$ (restr.-T), classical robust regression with Huber's $\psi$ function (rlm-H), restricted likelihood  with Huber's $\psi$ (restr.-H), and the thick tailed $t$-model (t).
 The normal theory models perform poorly due to the numerous outliers
-and are left out of the figures. Appearing in the figures are the mean TLM across
-validations set for each model and each trimming fraction, $\alpha$ (along the $x$-axis).
+%and are left out of the figures. Appearing in the figures are the mean TLM across
+%validations set for each model and each trimming fraction, $\alpha$ (along the $x$-axis).
 The error bars depicted are one standard deviation of the TLM above and below the mean.
@@
 For sample sizes as low as $n=100$, the restricted likelihood methods outperform the heavy-tailed model with the Tukey version performing the best.
-The stronger performance of restricted likelihood based on Tukey's method and the t model is to be expected, as many of the 
-residuals are so extreme that trimming is better than winsorizing (as Huber's method effectively does).  
-As expected, with enough data,  the Bayesian methods and their classical counterparts perform similarly, although there
-is a persistent slight edge in favor of the Bayesian restricted likelihood methods.  We attribute this advantage to the weakly informative
-prior distribution which pulls the estimates slightly toward better values.  The similarity occurs as early as $n=100$.
+%The stronger performance of restricted likelihood based on Tukey's method and the t model is to be expected, as many of the 
+%residuals are so extreme that trimming is better than winsorizing (as Huber's method effectively does).  
+%As expected, with enough data,  the Bayesian methods and their classical counterparts perform similarly, although there
+%is a persistent slight edge in favor of the Bayesian restricted likelihood methods.  We attribute this advantage to the weakly informative
+%prior distribution which pulls the estimates slightly toward better values.  The similarity occurs as early as $n=100$. 
+%
 
@@
 \label{hierRegNW}
-Nationwide agencies span many states and insurance regulations and the competitive environment varies between states.
-A natural extension to the previous analysis is a hierarchical regression model, grouping agencies within each state to reflect similar business environments.
-Using the same study design with the same training and validation splits, we re-analyze the data using the following hierarchical regression model:
+The previous analysis treated states independently. A natural extension is to  reflect similar business environments between states using a hierarchical regression. The proposed model is:
 \begin{align}
@@
 \label{eq:hierModel}
-&\bbeta\sim N_p(\bmu_0, a\Sigma_0);\ \ 
-\bbeta_j\iid N_p(\bbeta, b\Sigma_0); \ \  
+&\beta\sim N_p(\mu_0, a\sigma_0^{2});\ \ 
+\beta_j\iid N_p(\beta, b\sigma_0^{2}); \ \  
 \sigma_j^2\sim IG(a_0,b_0);  & \\ \nonumber
-& \by_{ij}=\bx_{ij}^\top\bbeta_j+\epsilon_{ij},\ \ \epsilon_{ij}\iid N(0, \sigma_j^2),\ i=1,\dots, n_j,\ j=1,\dots, J &
+& y_{ij}=x_{ij}\beta_j+\epsilon_{ij},\ \ \epsilon_{ij}\iid N(0, \sigma_j^2),\ i=1,\dots, n_j,\ j=1,\dots, J &
 %\end{split}
 \end{align}
-where $y_{ij}$  represents the $i^{th}$ observation in the $j^{th}$
-state, $n_j$ is the total number of agencies in each state, and $J$ is
-the number of states. $\bx_{ij}$ is a four dimensional vector
-comprised of the same covariates as above. $\bbeta_j$ represents the
-individual regression coefficient vector for state $j$.  We match this
-model to the non-hierarchical model in several ways. First, $\bmu_0$,
+where $y_{ij}$ is the $i^{th}$ observation of square rooted household count in 2012 in the $j^{th}$
+state, is the total number of agencies in state $j$, and $J$ is
+the number of states. $x_{ij}$ is the square rooted household count in 2010 and $\beta_j$ represents the individual regression coefficient vector for state $j$.
+
+We match this model to the non-hierarchical model in several ways. First, $\bmu_0$,
 $\Sigma_0$, $a_0$, and $b_0$ are fixed as before. We constrain $a+b=1$
@@
 Since $\text{var}(\rho|\mu_{\rho}, \psi_{\rho})=\mu_{\rho} (1-\mu_{p})/(\psi_{\rho}+1)$ we replace $\mu_{\rho}$ with $\hat\rho_{mle}$, $\text{var}(\rho|\mu_{\rho}, \psi_{\rho})$ with $2I^{-1}(\hat\rho_{mle})$, and set the mean of the gamma prior on $\psi_{\rho}$ equal to $\hat\rho_{mle} (1-\hat\rho_{mle})/(2I^{-1}(\hat\rho_{mle}))-1$.
-Finally, we arbitrarily set the variance of the gamma prior to be approximately the same as the mean.
+Finally, we  set the rate parameter to 1 implying the variance of the gamma prior is equal to its the mean.
 %The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$

### 2018-08-29 revision_1/paper.tex
wrote up hieararchical section

@@
 removed from the validation sample and all of the methods are scored using only the
-remaining $M - [\alpha M]$ observations. This process is advantageous to the base method since the smallest scores from this method are guarenteed to be trimmed.  A method
+remaining $M - [\alpha M]$ observations. This process is advantageous to the base method since the smallest scores from this method are guaranteed to be trimmed.  A method
 that performs poorly when it is the base method is discredited.  %For a complete evaluation, we allow each method
@@
 where $y_{ij}$ is the $i^{th}$ observation of square rooted household count in 2012 in the $j^{th}$
-state, is the total number of agencies in state $j$, and $J$ is
-the number of states. $x_{ij}$ is the square rooted household count in 2010 and $\beta_j$ represents the individual regression coefficient vector for state $j$.
-
-We match this model to the non-hierarchical model in several ways. First, $\bmu_0$,
-$\Sigma_0$, $a_0$, and $b_0$ are fixed as before. We constrain $a+b=1$
+state, $n_{j}$ is the total number of agencies in state $j$, and $J$ is
+the number of states.
+$x_{ij}$ is the square rooted household count in 2010 and $\beta_j$ represents the individual regression coefficient vector for state $j$.
+As with the state level regression, the parameters $\mu_0$,
+$\sigma^{2}_0$, $a_0$, and $b_0$ are fixed.
+Specifically we set $\mu_{0} = \hat\beta$ and $n_{p}\hat\sigma^{2}_{0}$ where $n_{p}$ is the number of observations in the prior data set and the estimates are from a robust fit of $y_{ij}=x_{ij}\beta+\epsilon_{ij}$ on the prior data.
+For $\sigma^{2}_{j}$, $a_{0}=5$ and $b_{0} = \bar\sigma^{2}(a_{0} -1)$ where $\bar\sigma^{2}$ is a weighted (by number of observation) average of individual estimates of each $\sigma_{j}^{2}$ from the previous data set.
+We constrain $a+b=1$
 in an attempt to partition the total variance between the individual
-$\bbeta_j$'s and the overall $\bbeta$. We take $b\sim
-\text{beta}(v_1,v_2)$. Using the previous data set, we assess the
+$\beta_j$'s and the overall $\beta$. We take $b\sim
+\text{beta}(v_1,v_2)$. Using the prior data set, we assess the
 variation between individual estimates of the $\beta_j$ to set $v_1$
@@
 $(z_1,\dots,z_J)\sim N_J(\mathbf{0}, \Sigma_\rho)$ with
-$\Sigma_\rho=(1-\rho)I+\rho \mb{1}\mb{1}^{\top}$. Then we set
+$\Sigma_\rho=(1-\rho)\mb{I}+\rho \mb{1}\mb{1}^{\top}$. Then we set
 $\sigma^2_j=H^{-1}(\Phi(z_j))$ where $H$ is the cdf of an
@@
 $\psi_\rho=a_\rho+b_\rho$. The parameters $\mu_\rho$ and
-$\psi_{\rho}$  are given beta and gamma distributions, respectively.
-We fix the parameters of these distributions by again considering fits to individual states from the previous data set.
-More precise details on setting $v_{1}, v_{2}$ and the the priors on $\mu_{\rho}$ and $\psi_{\rho}$ are given in the appendix.
-We note that we tried a range of other fixed hyper-parameters resulting in negligible differences in the results.
+$\psi_{\rho}$  are given beta and gamma distributions, with fixed hyperparameters. More details on setting prior parameters are given in the appendix.
 
 Using the same techniques as in the previous section, 
-we fit the normal theory hierarchical model above, a thick tailed $t$ version with $\nu = 3$ d.f., and two restricted likelihood versions (Huber's and Tukey's) of the model.
+we fit the normal theory hierarchical model above, a thick-tailed $t$ version with $\nu = 3$ d.f., and two restricted likelihood versions (Huber's and Tukey's) of the model.
 For the incomplete restricted methods, we condition on robust regression estimates fit separately within each state.
 We also fit classical robust regression counterparts and a least squares regression separately within each state.
-
-We digress briefly to note that for the restricted likelihood methods no additional computational strategies outside of those discussed in Section~\ref{highDim} are needed to fit the hierarchical models described here.
+Hierarchical models naturally require more
+data and so we include states having at least 25 agencies resulting in 22 states and $n = \sum_{j} n_{j} =  3180$ total agencies.
+For training data we take a stratified (by state) sample of size $3180/2 = 1590$ where the strata sizes are $n_{j}/2$ (rounded to the nearest integer).
+The remaining data is used for a holdout evaluation using TLM computed separately within each state: $TLM_b(A)_{j} = (M_{j} - [\alpha M_{j}])^{-1} \sum_{i=[\alpha M_{j}]+1}^{M_{j}} \log(f_A(y_{(i)j}^b))$ where $y_{(1)j}^b, y_{(2)j}^b,..., y_{(M_{j})j}^b$ is the ordering of the $M_{j}$ holdout observations within state $j$ according to the log marginals under the base model $b$.
+For the non-Bayesian models,  $f_A(y_{(i)j}^b$ is estimated using plug-in estimators for the parameters for state $j$.
+$TLM_b(A)_{j}$ is computed for each state for $K=50$ splits into training and holdout sets.
+For each fit the Bayesian models are fit using MCMC with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} adapted to the hierarchical setting as described in Section \ref{simData}.
+
+%We digress briefly to note that for the restricted likelihood methods no additional computational strategies outside of those discussed in Section~\ref{highDim} are needed to fit the hierarchical models described here.
 Since we condition on statistics which are computed within each state, the model's conditional independence between the states allows the data augmentation described earlier to be performed independently within each state.
@@
 
-Selected results for the hierarchical fits appear in Figure
-\ref{fig:hierType1Marg}. Hierarchical models naturally require more
-data and so we consider only training sizes of $n=1000$ and
-$2000$.  Again, the $t$-model is used as the base
-method for computing TLM.
-Trimming fractions between $0.15$ and $0.3$ are displayed, as patterns for smaller trimming fractions are similar to those from the non-hierarchical fits.
-That is, without sufficient trimming, the Bayesian restricted likelihood fits' evaluation measure is poor.
-Again, the normal theory fits, both Bayesian and classical, perform poorly and are left out of the figures.
-We see that the restricted likelihood with Tukey's estimator performs best in each case (assuming sufficient trimming).
+The average over states, $\overline{TLM}_b(A)$ for each of the $K$ repetitions is summarized in Figure
+\ref{fig:hierTLM} for several trimming fractions using the Student-t as the base model.
+The points are the average of the $\overline{TLM}_b(A)$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$.
+Again, the normal theory fits, both Bayesian and classical, perform poorly.
+We also see, that even using it as the base model to compute TLM, the Student-t doesn't perform well in comparison to the robust regressions.
+On average, the classical robust regressions fit separately within each state slightly outperform the restricted likelihood hierarchical models.
+The hierarchical model does however, reduce variance in predictions at the cost of an increase in bias induced by the prior distributions.
+This can be seen in Figure \ref{fig:hierTLMsd} which shows the standard deviation of $\overline{TLM}_b(A)$ relative to the mean over the $K=50$ repetitions.
+The results displayed are for the two restricted likelihood versions of the hierarchical model and their corresponding robust regression models fit separately within each state.
+It is clear that the hierarchical model reduces sample-to-sample variation in comparison the the classical robust model counterparts.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=6in]{hier_average_tlm.png}
+\caption{Hierarchical model results: $\overline{TLM}_b(A)$  plus/minus one standard deviation over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$.}
+\label{fig:hierTLM}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=6in]{hier_sd_tlm.png}
+\caption{Hierarchical model results: standard deviation of $\overline{TLM}_b(A)$ relative to the mean over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$.
+Results are given for the two restricted likelihood versions of the hierarchical model and their corresponding robust regression models fit separately within each state.}
+\label{fig:hierTLMsd}
+\end{figure}
+
+It is also interesting to examine the individual results within each state.
+Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ for each state where the points and errorbars are the averages and plus/minus one standard deviation over the $K = 50$ repetitions.
+The results are only given for the models using Tukey's M-estimators since, in general, these models performed the best.
+The states are ordered along the x-axis according to number of agencies with the state (shown in parentheses).
+In several of the smaller states, the restricted hierarchical model performs better on average with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior.
+It is clear that the prior is having the affect of pooling information across states; this is beneficial for average TLM in some states but detrimental in others.
+However, for each state, the sample-to-sample variance in smaller under the restricted likelihood model.
+This is shown in Figure \ref{fig:hierTLMstateSD} of the standard deviation of ${TLM}_b(A)_{j}$ relative to the mean for each.
+The general trend in the figure is that the standard deviation decreases as the number of observations within a state increases.
+Additionally, the differences between the restricted likelihood hierarchical and classical robust version is larger for smaller states with virtually identical standard deviations for the larger states.
+
+\begin{figure}[t]
+\includegraphics[width=7in]{hier_ave_tlm_state.png}
+\caption{Hierarchical model results: ${TLM}_b(A)_{j}$  plus/minus one standard deviation over $K = 50$ repetitions for each state and $\alpha = 0.3$.
+The states are ordered along the x-axis according to number of agencies with the state (shown in parentheses).
+Results displayed are for the robust models using Tukey's M-estimators.}
+\label{fig:hierTLMstate}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[width=7in]{hier_sd_tlm_state.png}
+\caption{Hierarchical model results: Standard deviation of ${TLM}_b(A)_{j}$  relative to the mean over $K = 50$ repetitions for each state and $\alpha = 0.3$.
+The states are ordered along the x-axis according to number of agencies with the state (shown in parentheses).
+Results displayed are for the robust models using Tukey's M-estimators.}
+\label{fig:hierTLMstateSD}
+\end{figure}
+
+%We see that the restricted likelihood with Tukey's estimator performs best in each case (assuming sufficient trimming).
 Huber's version also tops the thick tailed model for $n=2000$.

### 2018-08-29 revision_1/code/data_analysis/summarize_hier_reg_analysis.R

@@ -137,16 +137,20 @@ summary_tibble <- get_tlm_tibble(hier_marginals, base_model = 'Student-t', trimm
 #by rep - average over states, then average over reps
 overall_average <- summary_tibble %>% 
   group_by(Model, Repetition, n, `Trimming Fraction`) %>%
-  summarise(mean_tlm = mean(tlm)) %>% 
-  ungroup() %>% group_by(Model, n,  `Trimming Fraction`) %>% 
+  summarise(mean_tlm = mean(tlm)) %>% #ave over states
+  ungroup() %>% 
+  group_by(Model, n,  `Trimming Fraction`) %>% #ave/sd over reps
   summarize(mean = mean(mean_tlm), sd = sd(mean_tlm))
   
 
 
 theme_set(theme_bw(base_family = 'Times'))
 ggplot(overall_average, aes(x = `Trimming Fraction` , y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1) 
+ggsave(file.path(getwd(), "..", "..", "figs", 'hier_average_tlm.png'), width = 6, height = 4)
+
 
 ggplot(overall_average %>%  filter(!Model %in% c('OLS', 'Normal', 'Student-t')), aes(x = `Trimming Fraction` , y = sd/mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .0))  + geom_line(position  = position_dodge(width = .0), linetype = 1) 
+ggsave(file.path(getwd(), "..", "..", "figs", 'hier_sd_tlm.png'), width = 6, height = 4)
 
 
 
@@ -157,35 +161,49 @@ average_by_state <- summary_tibble %>%
   summarise(mean = mean(tlm), sd = sd(tlm)) %>% 
   ungroup() 
 
-theme_set(theme_bw(base_family = 'Times'))
-ggplot(average_by_state  %>% filter(`Trimming Fraction` == '0.3'), aes(x = State , y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1) 
+state_count <- analysis_data %>% group_by(State) %>% 
+  summarize(state_count = n())
+
[…]

### 2018-08-29 revision_1/response.tex
addressing referees comments - still need to do the discussion

\documentclass[12pt]{article}
\usepackage{fullpage,amsmath}% mathtools}
\usepackage{setspace}
\usepackage{graphicx, psfrag, amsfonts}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{hhline}
%\usepackage{color}
\usepackage{caption, setspace}
%\usepackage{subcaption}

\def\bgam{\mbox{\boldmath $\gamma$}}
\def\bth{\mbox{\boldmath $\theta$}}
\def\bbeta{\mbox{\boldmath $\beta$}}
\def\blam{\mbox{\boldmath $\lambda$}}
\def\bmu{\mbox{\boldmath $\mu$}}

\newcommand{\bx}{\mbox{\boldmath $x$}}
\newcommand{\bu}{\mbox{\boldmath $u$}}
\newcommand{\bc}{\mbox{\boldmath $c$}}
\newcommand{\bs}{\mbox{\boldmath $s$}}
\newcommand{\by}{\mbox{\boldmath $y$}}
\newcommand{\bz}{\mbox{\boldmath $z$}}
\newcommand{\bv}{\mbox{\boldmath $v$}}
\newcommand{\bb}{\mbox{\boldmath $b$}}
\newcommand{\thstarj}{\mbox{$\bth^\star_j$}}
\newcommand{\bths}{\mbox{$\bth^\star$}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\uI}{\mathrm{I}}
\newcommand{\uP}{\mathrm{P}}
\newcommand{\up}{\mathrm{p}}
\newcommand{\mb}{\mathbf}
\newcommand{\mc}{\mathcal}

\newcommand{\Bern}{\mbox{Bern}}
\newcommand{\Nor}{\mbox{N}}
\newcommand{\Ga}{\mbox{Gamma}}
\newcommand{\Dir}{\mbox{Dir}}
\newcommand{\Ber}{\mbox{Ber}}
\newcommand{\Be}{\mbox{Be}}
\newcommand{\Unif}{\mbox{Unif}}
\newcommand{\Binom}{\mbox{Bin}}
\newcommand{\IG}{\mbox{IG}}

\newcommand{\Xs}{X^\star}
\newcommand{\Lc}{{\cal L}}

\usepackage[dvipsnames,usenames]{color}
\newcommand{\yy}{\color{magenta}\it}
\newcommand{\jj}{\color{Black}\rm}
\newcommand{\yjnote}[1]{\footnote{\color{Brown}\rm #1 \color{Black}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{\bf Definition}
\newtheorem{lemma}[theorem]{\bf Lemma}
\newtheorem{corollary}[theorem]{\bf Corollary}
\newtheorem{proposition}[theorem]{\bf Proposition}
\newtheorem{assumption}[theorem]{\bf Assumption}
\newtheorem{example}[theorem]{\bf Example}
\newtheorem{remark}[theorem]{\bf Remark}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\stackrel{indep}{\sim}}

\doublespacing
\setlength{\textwidth}{6 in}

\title{Response to Referees' Comments on ``Bayesian Restricted Likelihood Methods'' by John Lewis, Steven M. MacEachern, and Yoonkyung Lee.} 
\date{}
\begin{document}
\maketitle

The authors thank the AE and the two referees for their thoughtful comments and suggestions. Our responses are listed as bullets.

\section*{Comments from the AE}
Summary:
This is a thought provoking paper that pursues a novel idea how to perform Bayesian inference under the assumption that only part of the data are so- called good data, while the rest are bad data or outliers in the sense that they are generated by a probability law different from the good data.
I agree with both reviewers that this is an interesting issue and that the paper provides a novel and ingenious contribution in this context. However, both referees raise several concerns which I share:

\begin{enumerate}
\item The exposition of the material in the paper needs to be improved considerably and reading of the paper has to be made easier. One of the reviewer made very detailed suggestions how this could be achieved. Like this reviewer, I found the exposition of the MH algorithm on p. 12 particularly obscure, see also Comment 7 below.
\begin{itemize}
\item A substantial revision/reorganization of the entire manuscript has been done including special attention paid to the explanation of the MCMC algorithm 
\end{itemize}
\item I agree that the term ``restricted” is misleading. How about a term such as “Bayesian inference for data with incompletely specified likeilihood”, or something similar?
\begin{itemize}
\item %In efforts to come up with a different term for the method, similar concerns arise. We have previously used the term `Blended Paradigm', for example, but this doesn't seem descriptive enough in its own right. 
In efforts to come up with a different name for the method, we feel similar concerns arise. We have used restricted likelihood for some time now and so we hope to stick with it. In an effort to reduce confusion we have given the paper a more descriptive title. 
\end{itemize}

\item I found the discussion how the suggested approach is related to ABC methods very vague and would appreciate more details.
\begin{itemize}
\item We have provide more details.
\end{itemize}

\item  There are several references to unpublished material such as Jung et al. (2014) which makes it hard to evaluate the value added by the corresponding material in the present paper.
\begin{itemize}
\item 
\end{itemize}

\item As for ABC methods, the suggested approach heavily relies on choosing appropriate statistics of the data. Since robustness to ``bad” data is the major concern of the authors, they should pursue one reviewer’s advice go beyond M-estimators and consider high-break down estimators such as LMS and LTS. Also the choice of a suitable statistic for the scale is an important issue that should be discussed in more detail.
\begin{itemize}
\item We agree that the choice of statistic is paramount and doesn't have to be restricted to M-estimation. We included two simple examples utilizing LMS and LTS. And added dialogue of the choice of statistic to the discussion. 
\end{itemize}

\item  As noted by one referee, the gain in performance of the suggested approach for the two models discussed in the paper is not terribly convincing. Hence, I strongly encourage the authors to include an additional example that shows a significant edge of their method over classical ones, or at least to provide artificial data, where this is the case.
\begin{itemize}
\item We have added a simulation study showing the enhance performance of our method in a situation where the data generating model is known. We have also made some refinements to the data analysis section to help highlight some of the advantages of out approach. 
\end{itemize}

\item  One reason for this performance could be that, strictly speaking, the model is not only misspecified for the “bad” part of the data, but also for the “good” part of the data which are count data, rather than genuinely Gaussian. In particular, if these outcomes are small counts (there is not scale on Figure 3, so it is difficult to say), the square root transformation might not be enough to ensure normality of the outcomes in regression (14) and its generalization in Section 4.3. Apart from non-Gaussianity, also the assumption of homoscedasticity of the error term might be misspecified. I wonder, how robust the whole approach is to model misspecification also for the “good” part of the data, since the acceptance rate of the MH algorithm in (7) and (8) seems to be based on the (potentially misspecified) outcome regression.
\begin{itemize}
\item Yes, homeoscedasticity is certainly one piece contributing to model misspecification and we added this comment to the data analysis section. We have not seen problems in the MH acceptance rates across many examples and added the acceptance rates we've observed in the data analyses sections. 
\end{itemize}

\vspace{.1in}

\end{enumerate}

\newpage

\section*{Comments from Referee 1}
Major Points:
The writing in this paper is very smooth; it reads easily. This is good but I’m worried this is achieved by not providing enough detail and reasoning. Hence the bulk of my comments below are efforts to quantify what further details the authors almost certainly know and would be well advised to include.
\begin{enumerate}
\item The Introduction and Sec. 2 are too long and detract from the focus of the paper: The authors basically want to give (3) and two examples of it, namely (1) and (2). Then they want to explain how they generate (y|T (y), ?). The central idea is strong enough to stand on its own without the elaborate discussion. The discussion points seem more appropriate for a concluding section on the conceptual implications of using a restricted likelihood. I suggest this because the conceptual implications are not the focus of the paper, they result from the methodology. The discussion material in the early part of the paper could be moved to the last section and made more focused. There are also a good number of references that the authors might want to read and possibly cite in the general area of model uncertainty outside the across-model prior setting. In no particular order, some are: Zhu, Ibrahim, Tang 2011 BKA, Barnardo and Smith 2000 (for M-closed, complete, and open), Gustafson and Clarke 2004 CJS, Clarke 2010 BA, Draper 1996 JRSSB, Yuan and Clarke 1999 CJS, Clyde and Iverson 2013 (M-open, proceedings volume) and Clarke, Clarke and Yu 2013 (M-complete) BA.

\begin{itemize}
\item We have re-organized and shortened Sections 1 and 2 and moved some of the commentary to the discussion. 
\end{itemize}

2) The paper should be more self-contained: Even after several readings I do not understand the procedure on p. 12 satisfactorily. Details are left out, e.g., how (7) follows from (8); the one sentence explanation on l. 8-9 is not enough. Why is it OK to drop the conditioning on T (yp) = T (yc) = T (yobs)? Some notation seems odd e.g., what is the relationship amongst yp, yc, and yobs? Where is the expression p(·)? Or do the authors mean p(·|?)? Also, I thought the idea of Metropolis-Hastings was to generate a sample from a distribution for which direct generation was difficult. If evaluation of f(y|?) is straighforward (as stated on p. 12, l. 10) and f (y|T (y), ?) is available, why is the author’s procedure important? I think the answer is that the authors want to compare f(y|?) to the use of a f(T(y)|?) corrected by an estimate of f(y|T(y),?) so that one can use the authors procedure without having f(y|?) but this should be stated explicitly.
A related point is that the discussion in Sec. 3.2.1 was also hard to follow because too many details were left out. The role of z? needs to be explained better. While the words in the last two lines of p. 12 may be obvious to those who know the methodology, giving the mathematical formalities and the motivations for the various steps would make them and p. 13, 14 easier to follow. In particular, where does y? come from? Why would one want to transform y? into y as in Theorem 1? How does the expression in Theorem 1 lead to the set in (9)? I have no doubts that the authors can provide more formality and motivation for each step in the procedure; it’s just a matter of doing it.
\begin{itemize}
\item We have made substantial revisions to the paper, especially the MH algorithm in an to make the details more clear including: more detail on the simplification of the the MH ratio R in (7) and (8); the fact that  $f(y|T (y), \theta)$ is not available in closed form (only up to a proportionality constant), so direct generation is difficult.
\end{itemize}

3) The intuition should be better explicated: The authors have clearly thought carefully about the intuition behind their procedure, but some how it doesn’t 2 come across in Figs. 1 and 2 which I am unable to link to the formalities they do present. The authors have not yet found a good way to express their ideas so that they can be readily assimilated by some one who does not already understand. I don’t understand the steps in the reasoning in Sec. 3.2.2. It’s OK to relegate proofs to an Appendix, but the reasoning should be clearer in the main text.
\begin{itemize}
\item We agree that this section was difficult to follow. We have made substantial effort to re-organize the section and explain the steps and reasonings more clearly. 
\end{itemize}

4) The results for the application need better labeling/exposition: It would be helpful if the authors could write out exactly and explicitly what cross-validation type of evaluation is being calculated. This is described at the bottom of p. 24, top of p. 25 in words, but the mathematical expressions should be given fully as well. This would clarify the role of the base method and the comment on p. 27, l. 3-4. The same sort of comment applies to p. 27-28: Please give the mathematical expressions rather than just the words. (This would make the last lines on p. 29 easier to follow.) Maybe it’s just the way that my copy printed, but in Figs. 3, 4, and 5 the ranges/dots are hard to distinguish from each other so it’s hard to tell which is what. Could the different cases have different symbols that would be easier to tell apart? Even making the figures larger would help. To make it easier for the reader could the discussion of Table 1 p. 31 refer to the rows in the table? That would make it easier for the reader to tell which comparisons the discussion was commenting on. A related question: What does Fig. 1 show that is essential to the discussion?

\begin{itemize}
\item The results sections has been refined substantially. The models were simplified and more focused to elucidate some of the advantages of our method. A more complete description with mathematical expressions is provided for how the TLM is calculated. We paid more attention to the clarity of the new figures. The purpose of Figure 1 is explained better in Section on the MCMC algorithm (now section 4).
\end{itemize}

5) Gather and organize your thoughts on model misspecification in Sec. 5: This is a sort of repeat of item \#1, but there are many places where the authors comment on various aspects of their analysis, the comments are valid and helpful, but they detract from the flow of the paper. If these were gathered and organized in the Discussion section the authors points would be more effectively made. For instance, the paragraph beginning In addition to... on p. 4, the first part of the paragraph beginning Further examples... on p. 6, middle paragraph on p.8, the discussion of instability in the first two paragraphs of Sec. 3.2, the paragraph beginning We digress...on p. 28. There are other cases where re- marks are valid but maybe they are not in the right place and would be more effectively made in the Discussion.

\begin{itemize}
\item We have moved these remarks to the discussion. 
\end{itemize}
\end{enumerate}

Minor Points:
Here are a few specific points. Some are picky, some are more substantive, but they are all smaller than those above. If I had more time, I’d probably find more suggestions, but I’m sure the authors can see the general tenor of my points is to encourage them to be clearer about the details.
\begin{enumerate}
\item p. 3, para. beginning The focus of this work...: State this more formally with mathematical notation.
\begin{itemize}
\item  added $f(\by|\bth)$
\end{itemize}

\item p. 3, l. -2: The word restricted likelihood is OK, but if the authors could use some other word it would be better. The term restricted is already used in the sense of restricted MLE and that’s not the same as the authors mean here. This would help avoid possible confusion.

\begin{itemize}
\item Addressed above.
\end{itemize}

\item p. 4, l. 11: Wong and Clarke CJS 2004 shows a case where using less but well chosen data gives better prediction.

\begin{itemize}
\item  NEED TO ADD TO DISCUSSION
\end{itemize}

\item p. 4, l. -8: The authors might want to have a look at Bernardo and Smith 2000 for their discussion on M-closed, -complete, -open problems. Maybe mention variance-bias decompositions for MSE?

\begin{itemize}
\item  NEED TO ADD TO DISCUSSION
\end{itemize}

\item p. 4, l. -4,-5: Yes, mis-specification and outliers somehow represent the same problem...Could this point be made with more clarity?
\begin{itemize}
\item  NEED TO ADD TO DISCUSSION
\end{itemize}
\item p. 5, l. -4: term should be factor.
\begin{itemize}
\item  done
\end{itemize}
\item p. 6, l. 7: Alternatively should be Hence (for instance).
\begin{itemize}
\item  Changed
\end{itemize}
\item Keep the ordering of conditioning variables the same e.g., (3) p. 6 uses
(y|T (y), ?) while p. 1, l. -2 uses (y|?, T (y)).
\begin{itemize}
\item  We made this change. 
\end{itemize}
\item p. 23, l. -1: ‘tunning’ should be ‘tuning’
\begin{itemize}
\item  done.
\end{itemize}
\end{enumerate}

\newpage
\section*{Comments from Referee 2}

The manuscript develops a new methodology for using a restricted likelihood in a Bayesian context. It derives an ingenious way of generating complete data samples that match the observed data as far as the conditioning statistics is concerned. The resulting algorithm is presented in sufficient detail to be useful to the practitioner. In view of these qualities, the manuscript deserves to be published.
However, in the example chosen by the authors the gain in performance as compared to classical methods is marginal at best, at the price of a presum- ably much larger computational complexity. In the simple regression model the restricted likelihood is outperformed by the heavy-tailed model for the small sample size, whereas for larger sample sizes its performance is virtually identical to the classical robust estimators. In the hierarchical model, it is indeed slightly better than the classical estimators, but I wonder whether this slight gain justifies the additional effort of finding reasonable priors for the hyperparameters and the much more involved computation of the estimates. If the priors are not chosen carefully, the results could even be worse than the ones from the classical estimators. The authors should therefore provide an additional example where the superiority of their approach shows more clearly. 
\begin{itemize}
\item We have provided additional examples as well as revised the data analysis section to better explicate the advantages of our method. 
\end{itemize}

It would also be useful to tell the reader whether the code used in the example is already publicly available, and how it compares in terms of computational load with the classical M-estimators and also with other robust estimators such as LMS (least median of squares) and LTS (least trimmed squares).
\begin{itemize}
\item information on acquiring code and current capabilities of it are now given in Section 4.1. Currently the MCMC algorithm is coded for the M-Estimators discussed. LMS, LTS, and others can theoretically be implemented using MCMC, but the software currently isn't generalizable enough for it. The package implements methods effective in lower dimensional settings that can be used for these estimators.

It is correct to assume the computational load for the restricted likelihood is larger - not just in computing the estimators but also in the additional steps of computing the gradients and linear systems of equations described in Section 4.

ADD TO THE DISCUSSION

\end{itemize}

In addition to the usual concerns about the sensitivity of the results on the prior in the Bayesian context, the method as presented here raises the problem of choosing the type of the M-estimator, to which the example data seem to be quite sensitive. It is not difficult to understand why Tukey’s redescending M-estimator performs better than the Huber-type M-estimator, but maybe not so easy why the difference is much more pronounced in the hierarchical model as compared to the simple model. If the authors have an explanation for this effect it should be given in the paper. For other data sets, however, a good choice of the M-estimator could well be different, so some guidelines would be welcome to the practitioner.
The authors should also discuss in more detail whether it is possible to go beyond M-estimators and to use high breakdown-point estimators such as LMS and LTS as the conditioning statistic, and which scale estimators could or should be used as companions. As the LMS regression has no tunable parameters, and the LTS regression has only a single one, the user would be relieved from studying the sensitivity to the choice of the M-estimator from an infinite number of possibilities.
\begin{itemize}
\item ADD TO THE DISCUSSION
\end{itemize}

Finally, I have to remark that the first sentence of the Discussion is dangerously close to an insult to the numerous researchers and practitioners who have applied Bayesian methods in data analysis for years, even decades. The approach chosen by the authors is certainly innovative and in my opinion potentially fruitful, but it can hardly claim to begin to reconcile the two fields. I think it is fair to ask that the authors find a slightly more modest expression of their enthusiasm.

\begin{itemize}
\item Thank you. We certainly did not intend for this statement to be interpreted this way and we have removed it, significantly updating the discussion. 
\end{itemize}

In summary, I recommend publication of the manuscript under the provision that the authors submit a revised version which addresses the points raised above. It should contain an additional example that shows a significant edge of their method over the classical ones. In this new example robust estimators with high breakdown point (LMS and LTS) should be studied along with suitable M-estimators. As is well known, the LMS-estimator has worse asymptotic properties than M-estimators and LTS, and it will be interesting to see whether this is visible in the results.

\begin{itemize}
\item We have included additional examples including a simulation. The simple example include LMS and LTS and we added some discussion on the choice of estimators. 
\end{itemize}

Minor comment:
\begin{enumerate}
\item Figure 4 is very hard to read, the panels should have the same size as the ones in Figure 5.
\begin{itemize}
\item The hard-to-read figures have been updated. 
\end{itemize}
\end{enumerate}

\end{document}

### 2018-08-29 revision_1/paper.tex
addressing referees comments - still need to do the discussion

@@
 having been demonstrated both empirically and theoretically.
-In simple settings, the success of the methods is often attributed to formal optimality properties, sometimes derived
-through the laws of subjective probability 
-and sometimes through admissibility and the complete class
-theorems of decision theory.  In complex settings, the hierarchical model allows one to create 
-and fit sophisticated models that may, for example, pool information across similar problems.
-
-The development of Bayesian inference relies on a complete Bayesian model consisting of 
-three elements:  the prior distribution, the loss function, and the likelihood or sampling density.
+Bayesian inference relies on a complete Bayesian model consisting of three elements:  the prior distribution, the loss function, and the likelihood or sampling density.
 While formal optimality of Bayesian methods is unquestioned if one accepts the validity of all three of these elements, a healthy skepticism encourages us to question each of them.
@@
 
-The focus of this work is the development of techniques to handle imperfections in the likelihood.  These imperfections often show themselves through the presence of outliers--cases 
-not reflecting the phenomenon under study. There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling
-density with a mixture model which includes one component for the ``good'' data and a second 
-component for the ``bad'' data.
-With this approach, the prior distribution is updated with the  mixture model likelihood to obtain the complete-data posterior distribution and  the good component of the sampling density is used for prediction of future good data.
+The focus of this work is the development of techniques to handle imperfections in the likelihood $f(\by|\bth)$.
+These imperfections often show themselves through the presence of outliers--cases not reflecting the phenomenon under study.
+There are three main solutions to Bayesian outlier-handling.
+The first is to replace the basic sampling density with a mixture model which includes one component for the ``good'' data and a second component for the ``bad'' data.
+With this approach, the good component of the sampling density is used for prediction of future good data.
 The second approach replaces the
@@
 The third approach fits a flexible (typically nonparametric) model to  the data, producing a Bayesian version of a density estimate for both good and bad data.
-In recent development, inference
-is made through the use of robust inference functions \citep{lee2014}.
-
-The traditional strategies for handling outliers all have their drawbacks.  While we view the sampling density for the good data as stable, the outlier-generating processes 
+In recent development, inference is made through the use of robust inference functions \citep{lee2014}.
+
+These traditional strategies  all have their drawbacks.  The outlier-generating processes 
 may be transitory in nature, constantly shifting as the source of bad data changes.
@@
 In a nutshell, we begin with a complete model  as if all of the data are good.
-Rather than driving the move from prior to posterior  by the full likelihood, we use only the likelihood
-driven by a few summary statistics which typically target inferential quantities
+Rather than driving the move from prior to posterior  by the full likelihood, we use only the likelihood driven by a few summary statistics which typically target inferential quantities
 of interest.
-We call this likelihood a restricted because conditioning is done on a restricted set of data; the set which satisfies the observed summary statistics.
+We call this likelihood a restricted likelihood because conditioning is done on a restricted set of data; the set which satisfies the observed summary statistics.
 This is a formal update of the prior distribution based on the sampling density of the summary statistics.
-The novelty of the work is twofold.
-We make use of classical robust estimators as  summary statistics in a formal
-Bayesian framework, using the sampling density of the estimators as a replacement for the 
-sampling density of the data.
+%The novelty of the work is twofold.
+We make use of classical robust estimators as  summary statistics in a formal Bayesian framework, using the sampling density of the estimators as a replacement for the  sampling density of the data.
 Second, we advance the argument that conditioning on an insufficient summary of the data is sound practice, rather than merely being done for computational and modelling convenience.
@@
 \end{eqnarray}
-We wish to keep the first piece and drop the second for better inference on $\bth$.
+where the second factor may not actually depend on $\bth$. We wish to keep the first factor and drop the second for better inference on $\bth$.
 
@@
 The M-estimators provide the most precise posteriors in this case.
-This is reflected in more precise predictions than the heavy-tailed and mixture model as illustrated by the predictive distributions displayed in  Figure \ref{fig:newcomb_predictive}.
+This is reflected in more precise predictions than the heavy-tailed and mixture model as illustrated by the predictive distributions also shown  in  Figure \ref{fig:newcomb_post}.
 \begin{figure}[t]
@@
 {\includegraphics[width = 4in]{figs/speed_of_light_predictive.png}}
-\caption{asdfdfa}
+\caption{Results from the analysis of the speed of light data. Top: Posterior distributions of $\beta$ under each model. Bottom: Log posterior predictive distributions under each model.}
 \label{fig:newcomb_post}
@@
 The full model is a standard normal Bayesian linear regression:
-
 \begin{equation}
@@
 \end{equation}
-where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and X is the $n\times 2$ design matrix.
+where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and X is the $n\times 2$ design matrix with a vector of 1's in the first column in the year covariate in the second.
 Prior parameters are fixed via a fit to the first 3 data points.
@@
 There are $n=21$ remaining data points and the parameter $g$ is set to $21$ reflecting a unit information prior \citep{kass1995reference}.
-Finally $a = 2$ and $b =1$ for the normal theory and restricted likelihood models.
+Finally $a = 2$ and $b =1$.
 
@@
 The mixture model involves explicitly modeling the outlier generating mechanism.
-In more more complex situations where the outlier generating mechanism is transient (i.e.
+In more complex situations where the outlier generating mechanism is transient (i.e.
 ever changing and more complex than just a unit error in the recording), modeling the outliers becomes more difficult.
@@
 For low-dimensional statistics $T(\by)$ and parameters $\bth$, direct computational strategies described in \cite{lewis2014} can be used to estimate the restricted posterior conditioned on essentially any statistic.
-These strategies rely on density estimation $f(T(\by)|\theta)$ using samples of $T(\by)$ for many values of $\theta$; a strategy which breaks down in higher dimensions.
+These strategies rely on density estimation $f(T(\by)|\theta)$ using samples of $T(\by)$ for many values of $\bth$; a strategy which breaks down in higher dimensions.
 This section outlines a data-augmented MCMC algorithm that can be applied to the Bayesian linear model when $T(\by)$ consists of estimates of the regression coefficients and scale parameter.
@@
 $g = n_{p}$ is analogous to the unit-information prior \citep{kass1995reference}, with the difference that we are using a prior data set, not the current data set, to set the prior.
-%$f = 0.05, 0.1, 0.5, 1$ and%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
+The obvious reason this model is misspecified is due to the numerous outliers.
+Additionally, the model assumes equal variance within each state which is arguably in question (see Figure \ref{fig:ctVct}) %$f = 0.05, 0.1, 0.5, 1$ and%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
 %corresponding to  a unit information prior for $\bbeta$.
@@
 state, $n_{j}$ is the total number of agencies in state $j$, and $J$ is
-the number of states.
-$x_{ij}$ is the square rooted household count in 2010 and $\beta_j$ represents the individual regression coefficient vector for state $j$.
-As with the state level regression, the parameters $\mu_0$,
-$\sigma^{2}_0$, $a_0$, and $b_0$ are fixed.
-Specifically we set $\mu_{0} = \hat\beta$ and $n_{p}\hat\sigma^{2}_{0}$ where $n_{p}$ is the number of observations in the prior data set and the estimates are from a robust fit of $y_{ij}=x_{ij}\beta+\epsilon_{ij}$ on the prior data.
-For $\sigma^{2}_{j}$, $a_{0}=5$ and $b_{0} = \bar\sigma^{2}(a_{0} -1)$ where $\bar\sigma^{2}$ is a weighted (by number of observation) average of individual estimates of each $\sigma_{j}^{2}$ from the previous data set.
+the number of states. $x_{ij}$ is the square rooted household count in 2010 and $\beta_j$ represents the individual regression coefficient vector for state $j$. The parameters $\mu_0$,
+$\sigma^{2}_0$, $a_0$, and $b_0$ are fixed by fitting  the regression $y_{ij}=x_{ij}\beta+\epsilon_{ij}$ using Huber's M-estimators to the prior data set from two years before.
+Using the estimates from this model, we set $\mu_{0} = \hat\beta$, $\sigma_{0}^{2} = n_{p}se(\hat\beta)^{2}$ ($n_{p} = 2996$ is the number of observations in the prior data set), $a_{0}=5$ and $b_{0} = \hat\sigma^{2}(a_{0} -1)$.
 We constrain $a+b=1$
@@
 Using the same techniques as in the previous section, 
-we fit the normal theory hierarchical model above, a thick-tailed $t$ version with $\nu = 3$ d.f., and two restricted likelihood versions (Huber's and Tukey's) of the model.
+we fit the normal theory hierarchical model above, a thick-tailed $t$ version with $\nu = 5$ d.f., and two restricted likelihood versions (Huber's and Tukey's) of the model.
 For the incomplete restricted methods, we condition on robust regression estimates fit separately within each state.
@@
 The remaining data is used for a holdout evaluation using TLM computed separately within each state: $TLM_b(A)_{j} = (M_{j} - [\alpha M_{j}])^{-1} \sum_{i=[\alpha M_{j}]+1}^{M_{j}} \log(f_A(y_{(i)j}^b))$ where $y_{(1)j}^b, y_{(2)j}^b,..., y_{(M_{j})j}^b$ is the ordering of the $M_{j}$ holdout observations within state $j$ according to the log marginals under the base model $b$.
-For the non-Bayesian models,  $f_A(y_{(i)j}^b$ is estimated using plug-in estimators for the parameters for state $j$.
-$TLM_b(A)_{j}$ is computed for each state for $K=50$ splits into training and holdout sets.
-For each fit the Bayesian models are fit using MCMC with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} adapted to the hierarchical setting as described in Section \ref{simData}.
+For the non-Bayesian models,  $f_A(y_{(i)j})^b$ is estimated using plug-in estimators for the parameters for state $j$.
+$TLM_b(A)_{j}$ is computed for each state for $K=50$ splits of training and holdout sets.
+The Bayesian models are fit using MCMC with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} and adapted to the hierarchical setting as described in Section \ref{simData}.
+For the MH-step proposing augmented data,  the acceptance rates for the two restricted likelihood models across all states and repetitions ranges from $0.24$ to  $0.74$.
 
@@
 The points are the average of the $\overline{TLM}_b(A)$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$.
-Again, the normal theory fits, both Bayesian and classical, perform poorly.
-We also see, that even using it as the base model to compute TLM, the Student-t doesn't perform well in comparison to the robust regressions.
+The normal theory fits, both Bayesian and classical, perform poorly and are left out of the figures.
+As the trimming fraction used for the TLM increases, so does TLM since more outliers are being trimmed.
+Similar patterns were seen in the individual state level regressions in Section \ref{regModelNW}.
+Despite being used as the base model to compute TLM, the Student-t doesn't perform well in comparison to the robust regressions.
+We attribute this to the assumption of heavier tails resulting in smaller log marginal values on average; emphasizing again that the t-model will do well to discount outlying observations but doesn't provide a natural mechanism for only predicting `good' (i.e.
+non-outlying) data.
 On average, the classical robust regressions fit separately within each state slightly outperform the restricted likelihood hierarchical models.
@@
 This can be seen in Figure \ref{fig:hierTLMsd} which shows the standard deviation of $\overline{TLM}_b(A)$ relative to the mean over the $K=50$ repetitions.
-The results displayed are for the two restricted likelihood versions of the hierarchical model and their corresponding robust regression models fit separately within each state.
-It is clear that the hierarchical model reduces sample-to-sample variation in comparison the the classical robust model counterparts.
+It is clear that the hierarchical model reduces sample-to-sample variation in comparison the the classical robust model counterparts, but this reduced variation comes at the cost of increase bias in the predictions.
 
@@
 
-It is also interesting to examine the individual results within each state.
-Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ for each state where the points and errorbars are the averages and plus/minus one standard deviation over the $K = 50$ repetitions.
-The results are only given for the models using Tukey's M-estimators since, in general, these models performed the best.
+It is also interesting to examine the results within each state.
+Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ for each state where the points and errorbars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions.
+The results are only given for the models using Tukey's M-estimators since, in general, these models performed the best on average.
+This is attributed to the corresponding $psi$-function used in the M-estimation which trims large outliers from the data completely.
+Huber's version down-weights outliers, but never completely trims them.
 The states are ordered along the x-axis according to number of agencies with the state (shown in parentheses).
 In several of the smaller states, the restricted hierarchical model performs better on average with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior.
-It is clear that the prior is having the affect of pooling information across states; this is beneficial for average TLM in some states but detrimental in others.
-However, for each state, the sample-to-sample variance in smaller under the restricted likelihood model.
-This is shown in Figure \ref{fig:hierTLMstateSD} of the standard deviation of ${TLM}_b(A)_{j}$ relative to the mean for each.
-The general trend in the figure is that the standard deviation decreases as the number of observations within a state increases.
+It is clear that the prior is having the affect of pooling information across states; this is beneficial for reducing the sample-to-sample variance.
+Figure \ref{fig:hierTLMstateSD} shows this benefit by plotting the standard deviation of ${TLM}_b(A)_{j}$ relative to the mean for each state.
+The general trend in the figure is that the standard deviation decreases as $n_{j}$ increases.
 Additionally, the differences between the restricted likelihood hierarchical and classical robust version is larger for smaller states with virtually identical standard deviations for the larger states.
+Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.
 
@@
 We first show that $\nabla s(X,\by)\in \mc{C}^\perp(X)$. Recall that
-$H=I-Q$. By the regression invariance property \ref{regIn} of $s$, we have
+$H=I-Q$. By the regression invariance property \ref{regIn}, we have
 \label{perpGradReg}
@@
 \subsection{Setting the hierarchical prior values}
-In setting the priors we use the same previous data set used to set the priors for the non-hierarchical model (Section \ref{regModelNW}) and several heuristic arguments.
+%In setting the priors we use the same previous data set used to set the priors for the non-hierarchical model (Section \ref{regModelNW}) and several heuristic arguments.
 While the analyses in Section \ref{hierRegNW} set the hyper-parameters using what is described here, the results were not sensitive to these choices.
-This section describes the heuristics used in setting these prior parameters and is given for completeness.
-Using the previous data set we fit separate (robust) regressions to each state and a  regression to the \green{\sout{entire} entirety of the} data at once.
+This section describes the how the prior parameters are set in  Section \ref{hierRegNW}.
+Using the previous data set from two years prior, we fit separate (robust) regressions to each state and a  regression to the entirety of the data at once.
 Let the estimates for the fits to each state be $\hat{\beta_{1}}, \dots, \hat \beta_{J}, \hat \sigma_{1}, \dots, \hat \sigma_{J}$ and the estimates from the single regression be $\hat \beta$ and $\hat \sigma$.
 These are classical robust estimates using Tukey's regression and Huber's scale.
-Let $n_{j}$ denote the number of observations in the $j^{th}$ state and set $n=\sum n_{j}$.
+For this sections, let $n_{j}$ denote the number of observations in the $j^{th}$ state (of the previous data set) and set $n_{p}=\sum n_{j}$.
 
 First, consider $v_{1}$ and $v_{2}$ in the prior $b\sim\text{beta}(v_{1},v_{2})$.
-In the hierarchical model \eqref{eq:hierModel}, $b=0$ implies all the $\bbeta_{j}'s$ are equal (no variation between states) and $b=1$ implies the $\bbeta_{j}'s$ vary about $\mu_{0}$ according to $\Sigma_{0}=n\cdot \mbox{var}(\hat\beta)$ (see Section \ref{regModelNW}).
+In the hierarchical model \eqref{eq:hierModel}, $b=0$ implies all the $\beta_{j}'s$ are equal (no variation between states) and $b=1$ implies the $\beta_{j}'s$ vary about $\mu_{0}$ according to $\Sigma_{0}=n_{p}\cdot \mbox{se}(\hat\beta)^{2}$ (see Section \ref{regModelNW}).
 We seek a prior measure for what we think $b$ should be.
-In other words, how much prior uncertainty should we allow in $\bbeta$ as opposed to the uncertainty amongst the $\bbeta_{j}'s$?
-Using the prior fit, a measure for  uncertainty for $\bbeta$ is $\Sigma_{\hat\beta}=\mbox{var}(\hat\beta)$, the estimate of the covariance from the single regression.
-For the $\bbeta_{j}'s$, take $\delta_{j}=\hat\beta_{j}-\hat\beta$ and set the prior uncertainty to $\Sigma_{\delta}=n^{-1}\sum n_{j}\delta_{j}\delta_{j}^{\top}$.
-Consider the value $g= \left(|\Sigma_{\delta}|/|\Sigma_{\hat\beta}|\right)^{1/p}$.
-Heuristically, $g$ is measure of the amount of uncertainty between the $\bbeta_{j}'s$ to the amount of uncertainty in $\bbeta$.
-Now in the prior, we heuristically set the uncertainty in the $\bbeta_{j}'s$ ($b\Sigma_{0}$) to be approximately equal to $g\cdot\mbox{var}(\hat\beta)$.
-That is, $b\Sigma_{0}\approx g\cdot\mbox{var}(\hat\beta)= \frac{g}{n} \Sigma_{0}$, suggesting $b\approx  \frac{g}{n}$.
-Hence we set $E[b]=\frac{g}{n}$.
-The precision, $v_{1}+v_{2}$, is set to be relatively high at $20$, completing the specification for the prior on $b$.
+Using the prior fit, a measure for  uncertainty for $\beta$ is $\Sigma_{\hat\beta}=\mbox{se}(\hat\beta)^{2}$, the estimate of the variance from the single regression.
+For the $\beta_{j}'s$, take $\delta_{j}=\hat\beta_{j}-\hat\beta$ and set the prior uncertainty to $\Sigma_{\delta}=n_{p}^{-1}\sum_{j} n_{j}\delta_{j}^{2}$.
+Consider  $g= \Sigma_{\delta}/\Sigma_{\hat\beta}$ measuring of the amount of uncertainty between the $\beta_{j}'s$ relative to that of $\beta$.
+Now in the prior, we heuristically set the uncertainty in the $\beta_{j}'s$ ($b\Sigma_{0}$) to be approximately equal to $g\cdot\Sigma_{\hat\beta}$.
+That is, $b\Sigma_{0}\approx g\cdot\Sigma_{\hat\beta}= \frac{g}{n} \Sigma_{0}$, suggesting $b\approx  \frac{g}{n}$.
+Thus, we set $E[b]=\frac{g}{n}$.
+The precision, $v_{1}+v_{2}$, is set to $10$, completing the specification for the prior on $b$.
 
@@
 As in the prior we assume $(\hat z_1,\dots,\hat z_J)\sim N_J(\mathbf{0}, \Sigma_\rho)$ with
-$\Sigma_\rho=(1-\rho)I+\rho \mb{1}\mb{1}^{\top}$ and find the MLE, $\hat\rho_{mle}$, and observed inverse Fisher information, $I^{-1}(\rho_{mle})$.
+$\Sigma_\rho=(1-\rho)\mb{I}+\rho \mb{1}\mb{1}^{\top}$ and find the MLE, $\hat\rho_{mle}$, and observed inverse Fisher information, $I^{-1}(\rho_{mle})$.
 The mean of the beta prior on $\mu_{\rho}$ is set to $\hat\rho_{mle}$.

### 2018-08-29 revision_1/code/data_analysis/prior.R

@@ -37,7 +37,7 @@ write_rds(parms_prior, "parms_prior.rds")
 
 by_state <- prior_data %>% 
   group_by(State) %>% 
-  filter(n() >= 10) %>% 
+  filter(n() >= 40) %>% #use state with plenty of data
   nest() 
   
 state_model <- function(df){
@@ -75,6 +75,7 @@ abline(h = beta_0)
 
 plot(sigma2Hats)
 abline(h = sigma2_hat)
+sigma2Hats <- sigma2Hats[-which(sigma2Hats > 4)] #get rid of large estimates
 
 X <-model.matrix(prior_fit)
 p <- ncol(X)
@@ -83,24 +84,11 @@ p <- ncol(X)
 
 nStates <- nrow(by_state)
 
-cbind(sigma2Hats,n_is)
 
-wts <- n_is/sum(n_is)
-beta_0_mean <- mean(betaHats)
-#abline(h = beta_0_mean, lty = 2)
-# beta_0 ~ N(mu_0, a*Sigma_0)
-# beta_i ~ N(beta_0, b*Sigma_0)
-mu_0 <- coef(prior_fit) # when a = 1, b = 0, then there is only one regression (no State effect). Set mu_0 to the estimate from this regression
-Sigma_beta_0_hat <- vcov(prior_fit)
-
-Sigma_0 <- nrow(prior_data)*Sigma_beta_0_hat #set variance to the variance of beta_0_hat - scaled by the number of point --- unit information
 
 # prior for beta_i's
-
-# nrow(prior_data)
-# vcov(prior_fit)
+wts <- n_is/sum(n_is)
 p <- nrow(vcov(prior_fit))
-#Sigma_0 <-  var(betaHats)/length(betaHats) #se_beta_0^2 
 
 delta_is <- sapply(betaHats, FUN=function(x) x - beta_0)
 delta_is <- matrix(delta_is, p, nStates)
@@ -117,22 +105,15 @@ for(i in 1:length(dList)){
 SigmaDelta  
 K <-length(n_is)
 
-# #another way?
-# SigmaDelta2 <-matrix(rep(0, p*p), p,p)
-# for(i in 1:length(models)){
[…]

### 2018-08-29 revision_1/code/data_analysis/summarize_hier_reg_analysis.R

@@ -145,7 +145,7 @@ overall_average <- summary_tibble %>%
 
 
 theme_set(theme_bw(base_family = 'Times'))
-ggplot(overall_average, aes(x = `Trimming Fraction` , y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1) 
+ggplot(overall_average %>% filter(!Model %in% c('OLS', 'Normal')), aes(x = `Trimming Fraction` , y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1) 
 ggsave(file.path(getwd(), "..", "..", "figs", 'hier_average_tlm.png'), width = 6, height = 4)
 
 

### 2018-08-31 revision_1/response.tex
completed first draft of revision, needs proof reading

@@
 2 are too long and detract from the focus of the paper: The authors basically want to give (3) and two examples of it, namely (1) and (2).
-Then they want to explain how they generate (y|T (y), ?).
+Then they want to explain how they generate $(y|T (y), \theta)$.
 The central idea is strong enough to stand on its own without the elaborate discussion.
@@
 \begin{itemize}
-\item We have re-organized and shortened Sections 1 and 2 and moved some of the commentary to the discussion. 
+\item We have re-organized and shortened Sections 1 and 2 and moved some of the commentary to the discussion. Several of the suggested references were added in the introduction.
 \end{itemize}
@@
 8-9 is not enough.
-Why is it OK to drop the conditioning on T (yp) = T (yc) = T (yobs)?
+Why is it OK to drop the conditioning on $T (y_{p}) = T (y_{c}) = T (y_{obs})$?
 Some notation seems odd e.g., what is the relationship amongst yp, yc, and yobs?
@@
 Also, I thought the idea of Metropolis-Hastings was to generate a sample from a distribution for which direct generation was difficult.
-If evaluation of f(y|?) is straighforward (as stated on p.
+If evaluation of $f(y|\theta)$ is straighforward (as stated on p.
 12, l.
-10) and f (y|T (y), ?) is available, why is the author’s procedure important?
-I think the answer is that the authors want to compare f(y|?) to the use of a f(T(y)|?) corrected by an estimate of f(y|T(y),?) so that one can use the authors procedure without having f(y|?) but this should be stated explicitly.
+10) and $f(y|T (y), \theta)$ is available, why is the author’s procedure important?
+I think the answer is that the authors want to compare $f(y|\theta)$ to the use of a $f(T(y)|\theta)$ corrected by an estimate of $f(y|T(y),\theta)$ so that one can use the authors procedure without having $f(y|\theta)$ but this should be stated explicitly.
 A related point is that the discussion in Sec.
@@
 \begin{itemize}
-\item We have moved these remarks to the discussion. 
+\item We have moved many of the remarks originally in the beginning to the discussion. 
 \end{itemize}
@@
 \begin{itemize}
-\item  added $f(\by|\bth)$
+\item  We've added  $f(\by|\bth) = L(\bth|\by)$ and some commentary on how such imperfections have traditionally been dealt with. 
 \end{itemize}
@@
 \begin{itemize}
-\item  NEED TO ADD TO DISCUSSION
+\item  Thanks for the reference, it was added to the literature review. 
 \end{itemize}
@@
 \begin{itemize}
-\item  NEED TO ADD TO DISCUSSION
+\item  We have added this reference. 
 \end{itemize}
@@
 \begin{itemize}
-\item  NEED TO ADD TO DISCUSSION
+\item  The first sentence of the literature review section now reads `Our motivation for the use of summary statistics in Bayesian inference is concern about outliers or, more generally, model misspecification.
+Specifically, the likelihood is not specified correctly and concentrating on using well chosen parts of the data can help improve the analysis'
 \end{itemize}
@@
 
-It is correct to assume the computational load for the restricted likelihood is larger - not just in computing the estimators but also in the additional steps of computing the gradients and linear systems of equations described in Section 4.
-
-ADD TO THE DISCUSSION
+The estimator must be computed at every MCMC iteration; and an orthonormal bases must be found. These do add cost to the MCMC for our method - we have added this to the discussion.
 
@@
 \begin{itemize}
-\item ADD TO THE DISCUSSION
+\item  Added to the discussion some commentary/recommendations for choosing an estimator. Also, as stated above we have added examples of LMS/LTS.  
 \end{itemize}
@@
 \begin{itemize}
-\item Thank you. We certainly did not intend for this statement to be interpreted this way and we have removed it, significantly updating the discussion. 
+\item We certainly did not intend for this statement to be interpreted this way and we have removed it. We have also updated the discussion to reflect the rest of your comments. 
 \end{itemize}

### 2018-08-31 revision_1/paper.tex
completed first draft of revision, needs proof reading

@@
 with outliers and dealing with model misspecification. We outline the
-drawbacks of previous solutions to both of these problems (e.g., use of
-heavy-tailed likelihoods) and propose a new method as an
-alternative.  When working with the new method, we summarize
-the data through a set of insufficient statistics,
-targeting inferential quantities of interest, and update the prior
-distribution with the summary statistics rather than the complete
+drawbacks of previous solutions to both of these problems and propose a new method as an
+alternative.  When working with the new method, the data is summarized
+through a set of insufficient statistics, targeting inferential quantities of interest, and the prior
+distribution is updated with the summary statistics rather than the complete
 data.  By careful choice of conditioning statistics, we
@@
 classical robust estimators (e.g., M-estimators) are natural choices
-for conditioning statistics. With these choices, the method can be thought of as a
-blend of classical robust estimation and Bayesian methods. A major contribution of this work is the development of a data 
+for conditioning statistics. %With these choices, the method can be thought of as a blend of classical robust estimation and Bayesian methods. 
+A major contribution of this work is the development of a data 
 augmented Markov chain Monte Carlo (MCMC) algorithm
-for the linear model and a wide range of choices for
-summary statistics. We demonstrate the method on an
-insurance agency data set containing many outliers and subject to model
+for the linear model and a large class of
+summary statistics. We demonstrate the method on simulated and real data sets containing outliers and subject to model
 misspecification. Success is manifested in better predictive
@@
 \begin{keyword}
-\kwd{Approximate Bayesian computation}
+%\kwd{Approximate Bayesian computation}
 \kwd{Markov chain Monte Carlo}
@@
 having been demonstrated both empirically and theoretically.
-Bayesian inference relies on a complete Bayesian model consisting of three elements:  the prior distribution, the loss function, and the likelihood or sampling density.
+Bayesian inference relies on a model consisting of three elements:  the prior distribution, the loss function, and the likelihood or sampling density.
 While formal optimality of Bayesian methods is unquestioned if one accepts the validity of all three of these elements, a healthy skepticism encourages us to question each of them.
 Concern about the prior distribution has been addressed through the development of techniques for subjective elicitation \citep{garthwaite2005, ohagan2006} and objective Bayesian methods \citep{berger2006}.
-Concern about the loss function is reflected in, for example, the
-extensive literature on Bayesian hypothesis tests \citep{kass1995}.  
+Concern about the loss function is reflected in, for example, the extensive literature on Bayesian hypothesis tests \citep{kass1995}.
 %This work focus on the likelihood.
@@
 
-The focus of this work is the development of techniques to handle imperfections in the likelihood $f(\by|\bth)$.
-These imperfections often show themselves through the presence of outliers--cases not reflecting the phenomenon under study.
+The focus of this work is the development of techniques to handle imperfections in the likelihood $f(\by|\bth) = L(\bth|\by)$.
+Concern for imperfections in the likelihood are reflected in work considering minimally informative likelihoods \citep{yuan1999minimally}, sensitivities of inferences to perturbations in the model \citep{zhu2011}, the specification of a class of models and the use of Bayesian model averaging over the class \citep{clyde2004}, and considerations of such averaging when the specified class may not contain the so-called true data generating model \citep{bernardo2000, clyde2013, clarke2013Complete}.
+In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers--cases not reflecting the phenomenon under study.
 There are three main solutions to Bayesian outlier-handling.
@@
 basic sampling density with a thick-tailed density in an attempt to discount outliers, yielding techniques that 
-often provide solid estimates of the center of the distribution but 
-do not easily translate to predictive densities for further good data.
+often provide solid estimates of the center of the distribution but do not easily translate to predictive densities for further good data.
 The third approach fits a flexible (typically nonparametric) model to  the data, producing a Bayesian version of a density estimate for both good and bad data.
@@
 This is a formal update of the prior distribution based on the sampling density of the summary statistics.
-%The novelty of the work is twofold.
+The spirit of the approach  %The novelty of the work is twofold.
 We make use of classical robust estimators as  summary statistics in a formal Bayesian framework, using the sampling density of the estimators as a replacement for the  sampling density of the data.
@@
 
-The remainder of the paper develops....
-%Bayesian restricted likelihood (Section~\ref{restrictedlikelihood}), shows how it can be applied to a Bayesian linear model (Section~\ref{BayesLinMod}), illustrates its use on an insurance agencies data set with a novel twist on model evaluation (Section~\ref{Applications}), and wraps up with a discussion (Section~\ref{Conclusions}).
-A major contribution of this work is the computational strategy whose legitimacy is established in Section~\ref{BayesLinMod}.
-The technical proofs are in the appendix.
+The remainder of the paper is as follows: Section~\ref{restrictedlikelihood} introduces the Bayesian restricted likelihood and provides context with previous work, Section~\ref{illustrations} demonstrates some advantages of the methods on simple examples, and Section~\ref{BayesLinMod} details a MCMC algorithm to apply the method to Bayesian linear models.
+This is a major contribution to the work providing an approach to apply the method on realistic examples.
+Many of the the technical proofs are in the Appendix \ref{sec:appendix} with R code available from the authors.
+Section \ref{Applications} illustrates the method on a messy insurance industry data set with a novel twist on model evaluation.
+A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method.
 
@@
 \subsection{Literature review}
-Direct use of restricted likelihood appears in many areas of the literature.  The motivation is often similar to ours:   
-concern about outliers or, more generally, model misspecification.
+
+Our motivation for the use of summary statistics in Bayesian inference is concern about outliers or, more generally, model misspecification.
+Specifically, the likelihood is not specified correctly and concentrating on using well chosen parts of the data can help improve the analysis \citep[e.g.,][]{wong2004}.
+Direct use of restricted likelihood for this reason appears in many areas of the literature.
 For example, the use of rank likelihoods is discussed by \cite{savage1969}, \cite{pettitt1983, pettitt1982}, and more recently by \cite{hoff2013}.
 \cite{lewis2012} make use order statistics and robust estimators for $T(\by)$ in the location-scale setting. 
-Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}. The tenor of these asymptotic 
-results is that, for a variety of conditioning statistics with non-trivial regularity conditions on prior, model, and likelihood, the
+Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}.
+The tenor of these asymptotic results is that, for a variety of conditioning statistics with non-trivial regularity conditions on prior, model, and likelihood, the
 posterior distribution resembles the asymptotic sampling distribution of the conditioning statistic.
@@
 
-This work extends the development of Bayesian restricted likelihood by arguing that deliberate choice of $T(\by)$ is sound practice and also by expanding the class of conditioning statistics in which exact conditioning can be achieved.
+This work extends the development of Bayesian restricted likelihood by arguing that deliberate choice of $T(\by)$ on which to guide inference is sound practice.
+We also expand the class of conditioning statistics in which a formal Bayesian update can be achieved.
 Our methods do not rely on asymptotic properties, nor do they rely on approximate conditioning.%, \green{nor do they need to correspond to artificial censoring to create incomplete or missing data}  \citep[e.g.,][]{albert1988, hoffwakefield2013}.
@@
 
-%In this work, we have presented an approach which begins to reconcile Bayesian methods with the practice of data analysis.
+%This work describes the concept of conditioning on insufficient statistics in Bayesian models, a method we term the restricted likelihood.
+The examples demonstrate the potential predictive improvement over competing methods in outlier-prone settings where the conditioning statistic targets the mean of the non-outlying data (e.g.
+M-estimators).
+%Attempting to model outliers can be seen as a special case of  misspecification of the original model for the non-outlying data.
+The traditional view is that, if the model is inadequate, one should build a better model.
+In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model.
+We ask the question Òby attempting to improve our model through elaboration, will the overall performance of the model suffer?Ó If yes, we avoid the elaboration, retaining a model with some level of misspecification.
+Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present.
+In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this problem.
 Many routine choices in an analysis react to the gap between reality and the
@@
 restricted likelihood presented here, lending them more formality and facilitating
-development of theoretical results.  But a much greater benefit of our
-framework is that it leads us to blend classical estimation with
-Bayesian methods.  Here, we use the likelihood from robust regression
-estimators to move from prior distribution to posterior distribution.
-Conditioning on the estimator, the update follows Bayes' Theorem
-exactly.
-Computation is driven by MCMC methods, requiring only a modest supplement to existing algorithms.
-In another context, we might condition on the results of a set of estimating equations, designed to enforce lexical preferences for those features of the analysis considered most important, yet still producing inferences for secondary aspects of the problem.
-For example, the computational strategies we devised here allow us to apply the method to inference on quantiles of a regression model.
-In other settings, we envision conditioning on a mix of estimators and some of the observed data.
-
-The framework we propose allows us to retain many benefits of Bayesian methods:  it requires a full and complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.
-
-This same framework retains many of the benefits of classical estimation.
-Great ingenuity has been used to create a wide variety of estimators in this tradition, many of which are designed to handle specific flaws in the model.
+development of theoretical results. A greater benefit of our framework is that it leads us to blend classical estimation with
+Bayesian methods.
+Here, we concentrate on outlier-prone settings where natural choices for conditioning statistic are classical robust estimators targeting the mean of the non-outlying data (e.g., M-estimators).
+The likelihood conditioned on these estimators is used to move from prior to posterior.
+The update follows Bayes' Theorem, conditioning on the observed estimators exactly.
+Computation is driven by MCMC methods, requiring only a supplement to existing algorithms by adding a Gibbs step to sample from the space of data sets satisfying the observed statistic.
+This step has additional computation costs.
+The estimator must be computed at every iteration to propose a new $\by$.
+This cost, as well as the need to find orthonormal bases derived from gradients of the estimators, adds some computational time compared to the full likelihood MCMC.
+The cost of finding the bases can be driven down by an understanding of the geometric space from which the samples are drawn as described in Section~\ref{highDim}.
+Additionally, we have seen good mixing of the MCMC chains across a wide-variety of examples.
+
+Outside of outlier-prone settings, we might condition on the results of a set of estimating equations, designed to enforce lexical preferences for those features of the analysis considered most important, yet still producing inferences for secondary aspects of the problem.
+For example, the computational strategies we devised here allow us to apply the method to inference on quantiles of a regression model by, for example, conditioning on estimates of these quantiles.
+This leads to questions regarding the choice of summary statistic to apply.
+For outliers, we have applied some obvious choices (M-estimators, LMS, LTS) which have shown value in classical robust estimation.
+Properties of such estimators are well known and can be used as a basis for selecting one.
+In general, great ingenuity has been used to create a wide variety of estimators designed to handle specific manifestations of a misspecified model; where outliers are just a specific case.
 The estimators are typically accompanied by asymptotic results on consistency and distribution.
-Many of these results carry over to our blend of classical and Bayesian methods, although regularity conditions differ.
+These results can be used as starting point for choosing appropriate statistics in specific settings.
+In general, we recommend a choice based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.
+%In our words, to provide desirable inference, we recommend use of robust and relevant summary statistics in conjunction with Bayesian models.
+
+%Many of these results carry over to our blend of classical and Bayesian methods, although regularity conditions differ.
 We expect our procedures to have strong large sample performance, especially in settings where
-pooling of information is of value.
-
-This framework opens a number of questions, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.
-Perhaps the biggest question is which summary statistic to choose.
+%pooling of information is of value.
+
+The most general setting, of which outliers are a subset, is model misspecification.
+The traditional view is that, if the model is inadequate, one should build a better model.
+In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model.
+We ask the question Òby attempting to improve our model through elaboration, will the overall performance of the model suffer?Ó If yes, we avoid the elaboration, retaining a model with some level of misspecification.
+Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present.
+In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this more general problem.
+
+The framework allows us to retain many benefits of Bayesian methods:  it requires a complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.
+The work does open a number of questions open to further work, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.
+
+%Perhaps the biggest question is which summary statistic to choose.
 For this, we recommend a choice based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.

### 2018-09-06 revision_1/paper.tex
minor edits

@@
 Concern for imperfections in the likelihood are reflected in work considering minimally informative likelihoods \citep{yuan1999minimally}, sensitivities of inferences to perturbations in the model \citep{zhu2011}, the specification of a class of models and the use of Bayesian model averaging over the class \citep{clyde2004}, and considerations of such averaging when the specified class may not contain the so-called true data generating model \citep{bernardo2000, clyde2013, clarke2013Complete}.
-In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers--cases not reflecting the phenomenon under study.
+In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study.
 There are three main solutions to Bayesian outlier-handling.
@@
 This is a formal update of the prior distribution based on the sampling density of the summary statistics.
-The spirit of the approach  %The novelty of the work is twofold.
+%The spirit of the approach  %The novelty of the work is twofold.
 We make use of classical robust estimators as  summary statistics in a formal Bayesian framework, using the sampling density of the estimators as a replacement for the  sampling density of the data.
@@
 This is a major contribution to the work providing an approach to apply the method on realistic examples.
-Many of the the technical proofs are in the Appendix \ref{sec:appendix} with R code available from the authors.
-Section \ref{Applications} illustrates the method on a messy insurance industry data set with a novel twist on model evaluation.
+Many of the the technical proofs are in the Appendix \ref{sec:appendix} with \texttt{R} code available from the authors.
+Section \ref{RealData} illustrates the method on a messy insurance industry data set containing many outliers with a novel twist on model evaluation.
 A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method.
@@
 Consequently, effort is made to choose an approximately sufficient $T(\by)$ and update to the ABC posterior by using the likelihood $L(\bth| \mathcal{B}(\by))$, where $\mathcal{B}(\by)=\{\by^{*}|\rho(T(\by),T(\by^{*}))<\epsilon\}$, $\rho$ is a metric, and $\epsilon$ is a tolerance level.
-This is the likelihood ``conditioned'' on the collection of data sets which result in a $T(\cdot)$ within $\epsilon$ of the observed $T(\by)$.
+This is the likelihood conditioned on the collection of data sets which result in a $T(\cdot)$ within $\epsilon$ of the observed $T(\by)$.
 %Hence, we can see that, as in our method, conditioning is done on a summary of the complete data.
@@
 The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models.
-The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ assuming the prior $p \sim \beta(20,1)$ on the probability of belonging to the `good' component.
+The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ assuming the prior $p \sim \text{beta}(20,1)$ on the probability of belonging to the `good' component.
 
@@
 As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
-The outliers in this case are due to a change in units on which calls were recorded for part of the dataset.
+The outliers in this case are due to a change in units on which calls were recorded for part of the data set.
 The full model is a standard normal Bayesian linear regression:
@@
 The mixture model assumes different mean regression functions and variances for each component, but keeps the same, relatively non-informative priors.
-The probability of belonging to the first component is given a $\beta(5,1)$ prior.
+The probability of belonging to the first component is given a $\text{beta}(5,1)$ prior.
 The heavy-tailed model fixes the degrees of freedom to 5 with the same adjustment to the prior on $\sigma^{2}$ as above.
@@
 These strategies rely on density estimation $f(T(\by)|\theta)$ using samples of $T(\by)$ for many values of $\bth$; a strategy which breaks down in higher dimensions.
-This section outlines a data-augmented MCMC algorithm that can be applied to the Bayesian linear model when $T(\by)$ consists of estimates of the regression coefficients and scale parameter.
+This section outlines a data augmented MCMC algorithm that can be applied to the Bayesian linear model when $T(\by)$ consists of estimates of the regression coefficients and scale parameter.
 
@@
 where $x_i$ and $\bbeta \in \mathbb{R}^p$, $\sigma^2 \in \mathbb{R}^+$, 
-and the $\epsilon_i$ are independent draws from a distribution with center $0$ and scale $\sigma$. $X$ denotes the design matrix whose rows are  $x_i^\top$.
-
+and the $\epsilon_i$ are independent draws from a distribution with center $0$ and scale $\sigma$.
+$X$ denotes the design matrix whose rows are  $x_i^\top$.
 For the restricted likelihood model,  conditioning statistics are assumed to be of the form $T(\by) = (\bb(X, \by), s(X, \by))$ where $\bb(X, \by)= (b_1(X,\by), \dots,b_p(X,\by))^\top\in \mathbb R^{p}$ is an estimator for the regression coefficients and $s(X, \by)\in \{0\} \cup {\mathbb R}^+$ is an estimator of the scale.
@@
 \textit{regression} and \textit{scale equivariance},
-respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
+respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} are called \textit{regression invariance}
 and \textit{scale equivariance}. 
@@
 %\end{theorem}
-Using the theorem, the general idea is to first start with an initial vector $\bz^*$ drawn from a known distribution, say $p(\bz^*)$, and transform via $h(\cdot)$ to $\by \in \mathcal{A}$.
+\noindent Using the theorem, the general idea is to first start with an initial vector $\bz^*$ drawn from a known distribution, say $p(\bz^*)$, and transform via $h(\cdot)$ to $\by \in \mathcal{A}$.
 The proposal density $p(\by|\bth)$ is then a change-of-variables adjustment on $p(\bz^*)$ derived from $h(\cdot)$.
@@
 The final proposal distribution including the complete Jacobian is given in equation \eqref{dens:ystst} with details in the next section.
-Before giving these details we provide a visualization  in Figure~\ref{fig:sampSpace} of each of the sets described above to aid in the understanding of the strategy we are taking.
+Before giving these details we provide a visualization  in Figure~\ref{fig:sampSpace} of each of the sets described above using a notional example to aid in the understanding of the strategy we are taking.
 In the figure, $n = 3$, $p=1$, and the conditioning statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$.
@@
 where $\gamma$ is the angle between the two normal vectors.
-This step is visualized in Figure~\ref{fig:stretchDeform} for the artificial
+This step is visualized in Figure~\ref{fig:stretchDeform} for the notional
 location-scale example.  The figure pictures only the $\mathcal{C}^{\perp}(X)$,
@@
 \label{fig:stretchDeform}
-\caption{sdasfda}
+\caption{Visualization of the scaling from $z^{*}$ to $z$.
+Left: the first substep scales $z^{*}$ on the unit circle to the circle of radius $r = ||z||$; resulting in a change-of-variables transformation for the unit circle to that of radius $r$.
+The contribution to the Jacobian of this transformation is $r^{-(n-p-1)}$.
+Right: The second substep accounts for the the change-of-variables transformation from the circle of radius $r$ to $\Pi(\mathcal{A})$.
+The normal vectors to these two sets are used to calculated the contribution to the Jacobian of this part of the transformation are shown in the figure.}
 \end{figure}
@@
 \end{equation}
-where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2}) = N(\tilde y | \theta_{i}, \sigma^{2})$; the mean $\theta_{i}$, variance $\sigma^{2}$ normal pdf evaluated at $\tilde y$.
+where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2}) = N(\tilde y | \theta_{i}, \sigma^{2})$; the mean $\theta_{i}$ and variance $\sigma^{2}$ normal pdf evaluated at $\tilde y$.
 For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})d\theta_{i}d\sigma^{2}_{i}$ where $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
@@
 The values of $a_{s}$ and $c$, do not effect the classical robust linear models.
-The normal theory model results are left out as they perform significant worse.
+The normal theory model results are left out as they perform significantly worse.
 Overall, the results are strikingly in favor of the restricted likelihood methods for the range of hyper-parameter values studied.
-Undoubtably, the most precise and accurate prior studied is  $c = 1$ and $a_{s} = 10$  and this results in the lowest (and best) average KL for both the Tukey and Huber restricted likelihood versions ((shown in the middle panel).
+Undoubtably, the most precise and accurate prior studied is  $c = 1$ and $a_{s} = 10$  and this results in the lowest (and best) average KL for both the Tukey and Huber restricted likelihood versions (shown in the middle panel).
 $c = 0.5$ performs the worst, but still better than the classical fits.
-There is evidence that performance starts to degrade as $a_{s} = 10$ as reflected in a larger average KL for $a_{s} = 10$.
+There is evidence that performance starts to degrade in this case when $a_{s} = 10$ as reflected in a larger average KL.
 Here, the prior mean and precision are $2.22$ and $1.62$ and we suspect this is starting to put too much mass on $\sigma^{2}_{i}$ values much smaller than $\sigma^{2}=4$.
@@
 As $n$ increases, the bias remains the same and the variation in the estimates gets smaller.
-Thus, the estimates are getting more certain about an incorrect value; explaining the degradation of the KL - divergence.
+Thus, the estimates are getting more certain about an incorrect value; explaining the degradation of the KL-divergence.
 As $m$ increases, the variance in the estimates gets larger and there is a marginal increase in the bias.
@@
 \section{Real Data}
-\label{Real Data}
+\label{RealData}
 We illustrate our methods with a pair of regression models for data from Nationwide Insurance Company, which concern prediction of the performance of insurance agencies.
@@
 \includegraphics[width=5in]{scatter_by_state.png}
-\caption{The square root of count in 2012 versus that in 2010 (after centering and scaling).
-The colors represent the varying contractual agreements as they stood in 2010.
-Agencies that closed during the 2010-2012 period are represented by the zero counts for 2012.
-Scalings on the axes are purposely left off for proprietary reasons.}
+\caption{The square root of count in 2012 versus that in 2010 for four states.
+The colors represent the varying contractual agreements as they stood in 2010 (`Type').
+Agencies that closed during the 2010-2012 period are represented by the zero counts for 2012.}
 \label{fig:ctVct}
@@
 removed from the validation sample and all of the methods are scored using only the
-remaining $M - [\alpha M]$ observations. This process is advantageous to the base method since the smallest scores from this method are guaranteed to be trimmed.  A method
+remaining $M - [\alpha M]$ observations.
+Larger values of $TLM_b(A)$ indicate better predictive performance.
+This process is advantageous to the base method since the smallest scores from this method are guaranteed to be trimmed.
+A method
 that performs poorly when it is the base method is discredited.  %For a complete evaluation, we allow each method
@@
 Models are fit to four states labelled State 2, 15, 27, and 36, with $n = 222, 40, 117,$ and $46$, representing a range of sample sizes.
-Training sample sizes are taken to be $.25n$ and $0.50n$ with holdout evaluation done on the remaining (`Type 1`) samples.
-The average $TLM_b(A)$ over $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student - t model and $\alpha = 0.3$.
-Similar results are observed for other base models, with this one being most advantageous to the Student - t model.
+Fitting is done on $K = 50$ training/holdout samples with training sample sizes taken to be $.25n$ and $0.50n$.
+Holdout evaluation is done on the remaining (`Type 1') samples.
+For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.15$ $0.76$ across the states, repetitions, and two versions of the model.
+The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
+Similar results are observed for other base models, with this one being most advantageous to the Student-t model.
 The error-bars are plus/minus one standard deviation of the average $TLM_b(A)$ over the $K = 50$  training/holdout samples.
-It is clear the normal Bayesian model used as the base model (Normal) and the classical ordinary least squares fits (OLS) have poor performance, as expected, due to the significant amount of outlier contamination in the data.
-In comparing are restricted methods to their corresponding classical methods, there is small, but consistent improvement across the states and training sample size.
+It is clear the normal Bayesian model used as the full model (Normal) and the classical ordinary least squares fits (OLS) have poor performance due to the significant amount of outlier contamination in the data.
+In comparing our restricted methods to their corresponding classical methods, there is small, but consistent improvement across the states and training sample size.
 For state 2, the largest state with $n = 222$, the restricted and classical robust methods have similar performance especially for larger training sample size.
 This reflects the diminishing effect of the prior as the sample size grows.
-Notably, the Student - t model performs poorly in comparison for this state.
-The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good` data (i.e.
-the Type 1 agencies).
+Notably, the Student-t model performs poorly in comparison for this state.
+The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good` data (i.e., the Type 1 agencies).
 Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.
@@
 Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model; detrimental for prediction.
-The relative performance of the models are similar for various values $\alpha$.
-Figure \ref{fig:tlmbyAlpha} shows the results for one state (State 27) with training sample size $0.5n$ as an example.
+The relative performance of the models are similar for various values $\alpha$ as seen in Figure \ref{fig:tlmbyAlpha} which shows results for training sample size $0.5n$.
 
@@
 Hierarchical models naturally require more
-data and so we include states having at least 25 agencies resulting in 22 states and $n = \sum_{j} n_{j} =  3180$ total agencies.
+data and so we include states having at least 25 agencies resulting in 22 states in total and $n = \sum_{j} n_{j} =  3180$ total agencies.
 For training data we take a stratified (by state) sample of size $3180/2 = 1590$ where the strata sizes are $n_{j}/2$ (rounded to the nearest integer).
@@
 
-The average over states, $\overline{TLM}_b(A)$ for each of the $K$ repetitions is summarized in Figure
+The average over states, $\overline{TLM}_b(A)_{\cdot}= \frac{1}{22} \sum_{j =1}^{22} TLM_b(A)_{j}$ for each of the $K$ repetitions is summarized in Figure
 \ref{fig:hierTLM} for several trimming fractions using the Student-t as the base model.
-The points are the average of the $\overline{TLM}_b(A)$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$.
+The points are the average of the $\overline{TLM}_b(A)_{\cdot}$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$.
 The normal theory fits, both Bayesian and classical, perform poorly and are left out of the figures.
@@
 On average, the classical robust regressions fit separately within each state slightly outperform the restricted likelihood hierarchical models.
-The hierarchical model does however, reduce variance in predictions at the cost of an increase in bias induced by the prior distributions.
-This can be seen in Figure \ref{fig:hierTLMsd} which shows the standard deviation of $\overline{TLM}_b(A)$ relative to the mean over the $K=50$ repetitions.
-It is clear that the hierarchical model reduces sample-to-sample variation in comparison the the classical robust model counterparts, but this reduced variation comes at the cost of increase bias in the predictions.
+The hierarchical model does however reduce variance in predictions at the cost of an increase in bias induced by the prior distributions.
+This can be seen in Figure \ref{fig:hierTLMsd} which shows the standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over the $K=50$ repetitions.
+It is clear that the hierarchical model reduces sample-to-sample variation in comparison the the classical robust model counterparts.
 
@@
 \includegraphics[width=6in]{hier_average_tlm.png}
-\caption{Hierarchical model results: $\overline{TLM}_b(A)$  plus/minus one standard deviation over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$.}
+\caption{Hierarchical model results: $\overline{TLM}_b(A)_{\cdot}$  plus/minus one standard deviation over $K = 50$ splits into training and holdout sets with the Student-t as the base model and several values of the trimming fraction $\alpha$.}
 \label{fig:hierTLM}
@@
 \includegraphics[width=6in]{hier_sd_tlm.png}
-\caption{Hierarchical model results: standard deviation of $\overline{TLM}_b(A)$ relative to the mean over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$.
+\caption{Hierarchical model results: standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$.
 Results are given for the two restricted likelihood versions of the hierarchical model and their corresponding robust regression models fit separately within each state.}
@@
 The results are only given for the models using Tukey's M-estimators since, in general, these models performed the best on average.
-This is attributed to the corresponding $psi$-function used in the M-estimation which trims large outliers from the data completely.
+This is attributed to the corresponding $\psi$-function used in the M-estimation which trims large outliers from the data completely.
 Huber's version down-weights outliers, but never completely trims them.
-The states are ordered along the x-axis according to number of agencies with the state (shown in parentheses).
+The states are ordered along the $x$-axis according to number of agencies with the state (shown in parentheses).
 In several of the smaller states, the restricted hierarchical model performs better on average with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior.
-It is clear that the prior is having the affect of pooling information across states; this is beneficial for reducing the sample-to-sample variance.
+It is clear that the prior is having the effect of pooling information across states; beneficial for reducing the sample-to-sample variance.
 Figure \ref{fig:hierTLMstateSD} shows this benefit by plotting the standard deviation of ${TLM}_b(A)_{j}$ relative to the mean for each state.
 The general trend in the figure is that the standard deviation decreases as $n_{j}$ increases.
-Additionally, the differences between the restricted likelihood hierarchical and classical robust version is larger for smaller states with virtually identical standard deviations for the larger states.
+Additionally, the differences between the models is larger for smaller states with virtually identical standard deviations for the larger states.
 Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.
@@
 \caption{Hierarchical model results: ${TLM}_b(A)_{j}$  plus/minus one standard deviation over $K = 50$ repetitions for each state and $\alpha = 0.3$.
-The states are ordered along the x-axis according to number of agencies with the state (shown in parentheses).
+The states are ordered along the $x$-axis according to number of agencies with the state (shown in parentheses).
 Results displayed are for the robust models using Tukey's M-estimators.}
@@
 \caption{Hierarchical model results: Standard deviation of ${TLM}_b(A)_{j}$  relative to the mean over $K = 50$ repetitions for each state and $\alpha = 0.3$.
-The states are ordered along the x-axis according to number of agencies with the state (shown in parentheses).
+The states are ordered along the $x$-axis according to number of agencies with the state (shown in parentheses).
 Results displayed are for the robust models using Tukey's M-estimators.}

### 2018-10-31 revision_1/code/calls/calls.R
manual merging edits from paper Oct 18.tex into paper.tex

@@ -1,6 +1,7 @@
 # Analyze the Belgium Calls Data
 
 library(tidyverse)
+#devtools::install_github('jrlewi/brlm')
 library(brlm)
 library(MASS)
 
@@ -76,7 +77,7 @@ rl_fit <- rl_importance(y, X_fit, statistic = rlm_tukey, mu0 = mu0, Sigma0 = Sig
 plot(rl_fit$w, cex = .2)
 
 
-write_rds(rl_fit, path = file.path(here::here(), 'rl_fit.rds'))
+write_rds(rl_fit, path = file.path(here::here(), 'out', 'rl_fit.rds'))
 
 
 
@@ -89,16 +90,28 @@ t_fit <-bayesTdistLm(y=y, X_fit, mu0, Sigma0, a0=a0, b0=((nu-2)/nu)*b0, parInit=
 
 coda::traceplot(t_fit$mcmc)
 
-write_rds(t_fit, path = file.path(here::here(), 't_fit.rds'))
+write_rds(t_fit, path = file.path(here::here(), 'out', 't_fit.rds'))
 
 # fit normal model on subset of the data.
 nkeep <- 1e4
 nburn <- 2e3
-normal_ind <- c(4:13,21:24)
+normal_ind <- c(4:13,22:24)
 y_normal <- phones$calls[normal_ind]
 X_normal <- cbind(1, phones$year[normal_ind])
 set.seed(127)
 normal_fit <- bayesLm(y_normal, X_normal, mu0, Sigma0, a0, b0, sigma2Int = rlm_fit$s^2, nkeep = nkeep, nburn = nburn)
 
 coda::traceplot(normal_fit$mcmc,smooth = TRUE)
-write_rds(normal_fit, path = file.path(here::here(), 'normal_fit.rds'))
+write_rds(normal_fit, path = file.path(here::here(), 'out', 'normal_fit.rds'))
+
+
+
+# fit normal model to all data.
+nkeep <- 1e4
+nburn <- 2e3
+set.seed(127)
+normal_fit_all <- bayesLm(y, X_fit, mu0, Sigma0, a0, b0, sigma2Int = rlm_fit$s^2, nkeep = nkeep, nburn = nburn)
+
+coda::traceplot(normal_fit_all$mcmc,smooth = TRUE)
+write_rds(normal_fit_all, path = file.path(here::here(), 'out', 'normal_fit_all.rds'))
+

### 2018-10-31 revision_1/code/calls/mix.data.R

@@ -1,20 +1,22 @@
 N <- 21
 y <- 
-c(1.77495235091167, 1.88706964903238, 1.98787434815435,
-2.09186406167839, 2.17475172148416, 2.36085400111802,
-2.484906649788, 2.60268968544438, 2.70136121295141,
-2.77881927199042, 3.05400118167797, 4.77912349311153,
-4.82028156560504, 4.95582705760126, 5.06890420222023,
-5.2040066870768, 5.35658627467201, 3.76120011569356,
-3.17805383034795, 3.29583686600433, 3.36729582998647)
+c(-0.555520423880492, -0.45409063421027,
+-0.375325065475225, -0.303736167223768, -0.2524249642909,
+-0.151959094900659, -0.0940523684788975,
+-0.0444270215906998, -0.00626377764661846,
+0.0217870444656814, 0.110156331678157, 0.44741105318946,
+0.452878033816443, 0.470356109365662, 0.484353094306456,
+0.50042907382809, 0.517797394274967, 0.281214769091591,
+0.145198447682626, 0.176186204188251, 0.19401129636889)
 x <- 
-c(-8.5, -7.5, -6.5, -5.5, -4.5, -3.5, -2.5, -1.5, -0.5,
-0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5, 10.5, 11.5)
+c(-8.5, -7.5, -6.5, -5.5, -4.5, -3.5, -2.5, -1.5,
+-0.5, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,
+10.5, 11.5)
 mu0 <- 
-c(1.87185585035901, 0.0329789838958981)
+c(-0.311938510987452, 0.052536970789296)
 Sigma0 <- 
-structure(c(0.844441154194554, 0.0799395833422342,
-0.0799395833422342, 0.00761329365164136),
+structure(c(2.14301349612066, 0.202869797529078,
+0.202869797529078, 0.0193209330980075),
 .Dim = c(2, 2))
 a0 <- 2
 b0 <- 1

### 2018-10-31 revision_1/code/data_analysis/data/nw_data_clean.R

@@ -119,30 +119,78 @@ prior_data <- prior_data %>% dplyr::rename(Count_2008 = Ending_HH_Count2008, Cou
 
 analysis_data <- analysis_data %>% dplyr::rename(Count_2010 = Ending_HH_Count2010, Count_2012 = Ending_HH_Count2012)
 
+# Center and Scale -------- 
+
+
+cs <- function(x){
+  cs <- (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
+  cs + abs(min(cs))
+  }
+
+Count_2008 <- cs(prior_data$Count_2008)
+Count_2010 <- cs(c(prior_data$Count_2010, analysis_data$Count_2010))
+Count_2012 <- cs(analysis_data$Count_2012)
+
+prior_data2 <- prior_data
+nr_prior <- nrow(prior_data2)
+prior_data2$Count_2008 <- Count_2008
+prior_data2$Count_2010 <- Count_2010[1:nr_prior]
+
+analysis_data2 <- analysis_data
+nr_analyses <- nrow(analysis_data2)
+analysis_data2$Count_2010 <- Count_2010[(nr_prior + 1):(nr_prior + nr_analyses)]
+analysis_data2$Count_2012 <- Count_2012
+
+
+
+plot(prior_data$Count_2008, prior_data2$Count_2008)
+plot(prior_data$Count_2010, prior_data2$Count_2010)
+plot(analysis_data$Count_2010, analysis_data2$Count_2010)
+plot(analysis_data$Count_2012, analysis_data2$Count_2012)
+
+
+summary(fit1 <- lm(Count_2010 ~ Count_2008, data = prior_data))
+summary(fit2 <- lm(Count_2010 ~ Count_2008, data = prior_data2))
+plot(residuals(fit1))
+plot(residuals(fit2))
+
+summary(fit1 <- lm(Count_2012 ~ Count_2010, data = analysis_data))
+summary(fit2 <- lm(Count_2012 ~ Count_2010, data = analysis_data2))
+plot(residuals(fit1))
+plot(residuals(fit2))
+
+
+
 # plots ----
 theme_set(theme_bw())
 
 #by Agency Type
[…]

### 2018-10-31 revision_1/code/data_analysis/hier_reg_analysis.R

@@ -195,7 +195,7 @@ converge <- array(NA, c(nModels, 5, reps))
   # tdensity<-function(y, mean, sigma, nu){
   #   (gamma(.5*(nu+1))/(gamma(.5*nu)*sigma*sqrt(nu*pi)))*(1+((y-mean)/sigma)^2/nu)^(-.5*(nu+1))
   # }
-  fits<-function(betahats, X){X%*%betahats}
+  fits <- function(betahats, X){X%*%betahats}
   
  
 # simulation -----
@@ -388,7 +388,7 @@ marginals[ols_ind, i, ] <- olsMarginals %>% unlist()
 ################################################
 # normal theory bayes model ----
 ################################################
-      
+swSq <- 1      
 
 #tunning parameters for MH step on bstar, mu_rho, psi_rho, and rho
       step_logbstar <- abs(log(mu_bstr/(sqrt(mu_bstr*(1-mu_bstr)/(psi_bstr+1))))) #abs log(mean/sd)
@@ -505,7 +505,7 @@ if(any(is.na(step_Z))){
                                         b0,
                                         mu_bstr,
                                         psi_bstr,
-                                        swSq=1,
+                                        swSq = 1,
                                         w1,
                                         w2, 
                                         a_psir,
@@ -605,7 +605,7 @@ if(any(is.na(step_Z))){
                                                b0,
                                                mu_bstr,
                                                psi_bstr,
-                                               swSq=1,
+                                               swSq = 1,
                                                w1,
                                                w2, 
                                                a_psir,
@@ -762,7 +762,7 @@ marginals_sd[t_ind, i,] <- t_marg_sd %>% unlist()
 ################################################
 print(i)
 end <- Sys.time() - strt
-print(end) 
+print(end)
     }
  end <- Sys.time() - strt
  print(end)  

### 2018-10-31 revision_1/code/data_analysis/prior.R

@@ -16,7 +16,8 @@ prior_fit <- MASS::rlm(sqrt_count_2010 ~ sqrt_count_2008 - 1, scale.est = 'Huber
 # MASS::rlm(sqrt_count_2012 ~ sqrt_count_2010 - 1, scale.est = 'Huber', data =  analysis_data )
 
 theme_set(theme_bw(base_family = 'Times'))
-ggplot(prior_data, aes(x = sqrt_count_2008, y = sqrt_count_2010, col = Type)) + geom_point(size = .3) + xlim(c(0,150)) +  ylim(c(0, 130)) + stat_smooth(method = "rlm", formula = y ~ x -1, method.args = list(scale.est = 'Huber'), size = .5, lty = 2, se = FALSE, col = 1) + guides(col = guide_legend(title = 'Agency Type'))
+#+ xlim(c(0,150)) +  ylim(c(0, 130)) +
+ggplot(prior_data, aes(x = sqrt_count_2008, y = sqrt_count_2010, col = Type)) + geom_point(size = .3) + stat_smooth(method = "rlm", formula = y ~ x -1, method.args = list(scale.est = 'Huber'), size = .5, lty = 2, se = FALSE, col = 1) + guides(col = guide_legend(title = 'Agency Type'))
 
 
 summary(prior_fit)
@@ -27,7 +28,7 @@ sigma2_hat <- prior_fit$s^2
 
 a_0 <- 5
 b_0 <- sigma2_hat*(a_0 - 1)
-curve(dinvgamma(x, a_0,b_0), from=0, to=20)
+curve(dinvgamma(x, a_0,b_0), from=0, to=.01)
 
 
 parms_prior <- list(beta_0 = beta_0, se_beta_0 = se_beta_0, sigma2_hat = sigma2_hat, a_0 = a_0, b_0 = b_0, beta_var_inflate = beta_var_inflate )
@@ -61,7 +62,7 @@ var_betaHats <-
 
 sigma2Hats <-
   models %>% 
-  map(.f = function(m) summary(m)$sigma) %>%
+  map(.f = function(m) summary(m)$sigma^2) %>%
   unlist()
 
 n_is <- by_state$data %>% 
@@ -75,9 +76,12 @@ abline(h = beta_0)
 
 plot(sigma2Hats)
[…]

### 2018-10-31 revision_1/code/data_analysis/summarize_single_reg_analysis.R

@@ -18,7 +18,7 @@ label_vals <- c('2' = 'State 2', '15' = 'State 15', '27' = 'State 27', '36' = 'S
 ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, col = Type), size = 1, alpha = .5) +
   theme_bw() + facet_wrap(~State, labeller = labeller(State = label_vals)) + labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
   theme(text = element_text(family = 'Times'))
-ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+#ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
 
 
 
@@ -30,7 +30,7 @@ cnts <- analysis_data %>% group_by(State) %>%
 #   theme_bw() + 
 #   labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
 #   theme(text = element_text(family = 'Times'))
-# ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+# #ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
 # 
 
 
@@ -197,7 +197,7 @@ theme_set(theme_bw(base_family = 'Times'))
 ggplot(filter(summary_tibble, var_inflate == 100, `Trimming Fraction` == 0.3), aes(x = n, y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + #geom_line(position = position_dodge(width = .5)) +
   geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1)  + 
   facet_wrap(~State, drop = FALSE, scales = 'free', labeller = labeller(State = label_vals)) + xlab('Percent of sample used in training set') + ylab('Average TLM')
-ggsave(file.path(getwd(), "..", "..", "figs", paste0('tlm_base_',base_model, '.png')), width = 6, height = 4)
+#ggsave(file.path(getwd(), "..", "..", "figs", paste0('tlm_base_',base_model, '.png')), width = 6, height = 4)
 
 
[…]

### 2018-10-31 revision_1/code/simulation/hierarchical_sim/2_summarizeSimulations.R

@@ -2,8 +2,11 @@
 # Summarize the simulations ---
 #
 library('tidyverse')
+New_results <- TRUE
 
+if(New_results){
 sims <- 1:30
+
 dfs_all <- vector('list', length(sims))
 for(data_sim in sims){
 # load the data, along with the factor levels, and true values of theta
@@ -96,6 +99,11 @@ dfs_all[[data_sim]] <- bind_rows(dfs)
 
 df_estimates <- bind_rows(dfs_all, .id = 'simulation')
 
+} else {
+summarize_data_frames <- readRDS(file.path(here::here(), "summarize_data_frames.rds")) 
+ df_estimates <- summarize_data_frames[[2]]
+}
+sims <- 1:length(unique(df_estimates$simulation))
 df_mse <- df_estimates %>% dplyr::select(-p,-n,-m) %>%  
   group_by(simulation, statistic, method, a_s, scale_as, sigma2) %>% 
   summarise(MSE = mean((theta - theta_hat)^2)) %>% 
@@ -104,9 +112,17 @@ df_mse <- df_estimates %>% dplyr::select(-p,-n,-m) %>%
   summarise(mean_MSE = mean(MSE), sd_MSE = sd(MSE)) %>% ungroup() %>% 
   mutate(a_s = as.character(a_s), scale_as = as.character(scale_as))
 
-labels_vals <- scale_color_discrete(name="Method/Statistic",
-                                   breaks= c("restricted.Huber","rlm.Huber","restricted.Tukey","rlm.Tukey"),
-                                   labels=c("Restricted/Huber", "Rlm/Huber", "Restricted/Tukey", "Rlm/Tukey"))  
+labels_vals <- scale_color_discrete(
+                name="Method/Statistic",
+                breaks= c("restricted.Huber",
+                          "restricted.Tukey",
+                          "rlm.Huber",
+                          "rlm.Tukey"),
+                labels=c("Restricted/Huber", 
+                         "Restricted/Tukey", 
+                         "Rlm/Huber", 
+                         "Rlm/Tukey"))  
+
 
 theme_set(theme_bw())
[…]

### 2018-10-31 revision_1/code/speed_of_light/summarize_speed_of_light.R

@@ -157,10 +157,10 @@ predictive_distributions <- predictive_distributions %>%
   mutate(log_density = log(pred_dist))
 
 
-
+#xlim(c(-10, 60))
 
 # plot posterior predictive ----
-ggplot(predictive_distributions, aes(x = y_tilde, y = log_density, col = Model)) + geom_line() + xlim(c(-10, 60)) + ylim(c(-25,-2)) + theme_bw() + scale_color_brewer(palette = 'Set2') + xlab(expression(y)) + ylab(expression(log('predictive density')))
+ggplot(predictive_distributions, aes(x = y_tilde, y = log_density, col = Model)) + geom_line() + ylim(c(-25,-2)) + theme_bw() + scale_color_brewer(palette = 'Set2') + xlab(expression(y)) + ylab(expression(log('predictive density'))) + scale_x_continuous(limits = c(-10,60),breaks = c(-10,20, 25, 30, 35,60))
 ggsave(file.path(fig_path, 'speed_of_light_predictive.png'))
 
 

### 2018-11-02 revision_1/paper.tex
minor edits
fixed bug in summarizing simulations. some edits to paper

@@
 For example, the use of rank likelihoods is discussed by \cite{savage1969}, \cite{pettitt1983, pettitt1982}, and more recently by \cite{hoff2013}.
-\cite{lewis2012} make use order statistics and robust estimators for $T(\by)$ in the location-scale setting. 
+\cite{lewis2012} make use of order statistics and robust estimators as choices for $T(\by)$ in the location-scale setting. 
 Asymptotic properties of restricted posteriors are studied by \cite{doksum1990}, \cite{clarke1995}, \cite{yuan2004},  and \cite{hwang2005}.
@@
 Consequently, effort is made to choose an approximately sufficient $T(\by)$ and update to the ABC posterior by using the likelihood $L(\bth| \mathcal{B}(\by))$, where $\mathcal{B}(\by)=\{\by^{*}|\rho(T(\by),T(\by^{*}))<\epsilon\}$, $\rho$ is a metric, and $\epsilon$ is a tolerance level.
-This is the likelihood conditioned on the collection of data sets which result in a $T(\cdot)$ within $\epsilon$ of the observed $T(\by)$.
+This is the likelihood conditioned on the collection of data sets that result in a $T(\cdot)$ within $\epsilon$ of the observed $T(\by)$.
 %Hence, we can see that, as in our method, conditioning is done on a summary of the complete data.
@@
 Consequently, the ABC posterior approximates the full data posterior and efforts have been made to formalize what is meant by  approximate sufficiency \citep[e.g.,][]{joyce2008}.
-ABC is related to our method in that the ``conditioning'' is on something other than the data $\by$.
+ABC is related to our method in that the conditioning is on something other than the data $\by$.
 However, we specifically seek to condition on an insufficient statistic to guard against misspecification in parts of the likelihood.
@@
 
-The first example is an analysis of Simon Necomb's 66 measurements of the speed of light; two of which are significant outliers in the lower tail.
-The full model is a standard location-scale Bayesian model:
+The first example is an analysis of Simon Necomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
+The full model is a standard location-scale Bayesian model also used in \cite{lee2014}:
 \begin{equation}
@@
 \end{equation}
-where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light. $\beta$ is interpreted as the passage time of light with $\sigma^{2}$ representing measurement error.
+where $y_{i}$ denotes the $i^{th}$ (recoded) measurement of the passage time of light.
+$\beta$ is interpreted as the passage time of light with the deviations $y_i - \beta_i$ representing measurement error.
 Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)  Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
-Associated tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
-Additionally, two other common approaches to outlier handling are fit: 1) replacing the normal distribution with a t-distribution and, 2) replacing the normal distribution with a mixture of two normals.
+The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+Two additional approaches to outlier handling are fit: 1) the normal distribution is replaced with a t-distribution and, 2) the normal distribution is replaced with a mixture of two normals.
 The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$.
-The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models.
-The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ assuming the prior $p \sim \text{beta}(20,1)$ on the probability of belonging to the `good' component.
-
-The posteriors of $\beta$ under each model appear in Figure \ref{fig:newcomb_post}.
-As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy tailed model provides robustness against them.
+The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ ensures that the prior on the variance is the same as the other models.
+The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ with the prior $p \sim \text{beta}(20,1)$ on the probability of belonging to the `good' component.
+
+%The posteriors of $\beta$ under each model appear in Figure \ref{fig:newcomb_post}.
+As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy-tailed model provides robustness against them.
 The restricted likelihood methods using the M-estimators and LTS statistics also achieve robustness against the outliers.
@@
 This is reflected in more precise predictions than the heavy-tailed and mixture model as illustrated by the predictive distributions also shown  in  Figure \ref{fig:newcomb_post}.
+The posterior of $\beta$ under each model appears in Figure \ref{fig:newcomb_post}.
+The posteriors group into two batches.
+The normal model and restricted likelihood with LMS do not discount the outliers and have posteriors centered at low values of $\beta$.
+These posteriors are also quite diffuse.
+In contrast, the t model and the other restricted likelihood methods discount the outliers and have posterior centered at higher values.
+There is modest variation among these centers.
+Posteriors in this second group have less dispersion than those in the first group.
 \begin{figure}[t]
@@
 {\includegraphics[width = 4in]{figs/speed_of_light_predictive.png}}
-\caption{Results from the analysis of the speed of light data. Top: Posterior distributions of $\beta$ under each model. Bottom: Log posterior predictive distributions under each model.}
+\caption{Results from the analysis of the speed of light data.
+Top: Posterior distributions of $\beta$ under each model.
+Bottom: Log posterior predictive distributions under each model.
+The differences in the tails are emphasized in the bottom plot.
+The horizontal axis is strategically labeled to help compare the centers of the distributions in each of the plots.}
 \label{fig:newcomb_post}
 \end{figure}
+
+The pattern for predictive distributions differs (see bottom plot in Figure \ref{fig:newcomb__post}).
+The normal and t models have widely dispersed predictive distributions.
+The other predictive distributions show much greater concentration.
+The restricted likelihood fits based on M-estimators (Tukey's and Huber's) are centered appropriately and are concentrated.
+The LMS predictive is concentrated, but it is poorly centered.
+
+Overall, we find that the restricted likelihood methods based on M-estimators provide the most attractive analysis for these data.
+They provide sharp and appropriate inference for parameters ($\beta$) and for prediction.
 
@@
 As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
-The outliers in this case are due to a change in units on which calls were recorded for part of the data set.
+The outliers in this case are due to a change in measurement units on which calls were recorded for part of the data set.
+Specifically, for years 1964-1969 and parts of 1963 and 1970, the length of calls in minutes were recorded rather than the total number \citep{rousseeuw1987}.
 The full model is a standard normal Bayesian linear regression:
@@
 Prior parameters are fixed via a fit to the first 3 data points.
-In particular, $\Sigma_{0} = g\sigma_{0}^2 (X^{\top}X)^{-1}$, with $\sigma_{0} = 0.03$ and $\mu_{0} = (1.87,  0.03)^{\top}$; the MLEs fit to the first three data points.
-There are $n=21$ remaining data points and the parameter $g$ is set to $21$ reflecting a unit information prior \citep{kass1995reference}.
+In particular, the prior covariance for $\beta$ is set to $\Sigma_{0} = g\sigma_{0}^2 (X_{p}^{\top}X_{p})^{-1}$, with $X_{p}$ the $3\times 2$ design matrix for the first $3$ data points, $g=n=21$, and $\sigma_{0} = 0.03$ and $\mu_{0} = (1.87,  0.03)^{\top}$; the MLEs fit to the first three data points.
+This has the spirit of a unit information prior \citep{kass1995reference} but uses a design matrix for prior data not used in the fit.
 Finally $a = 2$ and $b =1$.
@@
 Four models are compared: 1) the normal theory base model 2) A two component normal mixture model, 3) a t-model, and 4) a restricted likelihood model conditioning on Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
+Each model is fit to the remaining 21 data points.
+The normal theory model is also fit a second time after removing observations 14-21 (years 1963 - 1970).
+This includes the obvious large outliers as well as the two smaller outliers at the beginning and end of this sequence of points caused by the change in measurement units.
 The mixture model assumes different mean regression functions and variances for each component, but keeps the same, relatively non-informative priors.
@@
 The data and  $95\%$ credible bands of the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}.
-The normal theory model is only fit to the obvious non-outlying points.
-Since the t-model assumes the data are heavy-tailed, the posterior predictive distribution is much wider.
-On the other hand, the predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit that discards the outliers.
+The normal model fit to all cases results in a very wide posterior predictive distribution due to an inflated estimate of the variance.
+Since the t-model assumes the data are heavy-tailed, the posterior predictive distribution is also wide.
+Additionally, both of these are biased upward by the outliers in the upper tail of the assumed data distribution.
+On the other hand, the predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit to the non-outlying cases.
 It is also close to the two component mixture results where the predictive distribution is formulated using only the good component.
@@
 ever changing and more complex than just a unit error in the recording), modeling the outliers becomes more difficult.
-Like classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
+As in classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
 \begin{figure}[t]
@@
 {\includegraphics[width = 4in]{figs/calls_predictive.png}}
-\caption{Predictive distribution of log(calls) under the Normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
-The first three data points were used to specify the prior with the remaining points used in the posterior fits.
-See details in the Appendix.}
+\caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
+The first three data points were used to specify the prior with each model using the remaining 21 for fitting.
+The normal theory model was also fit after removing observations 14-20 (years 1963 - 1970).}
 \label{fig:calls_predictive}
 \end{figure}
+%{\bf For the figure, add fit of normal model to all cases}
 
@@
 %a Jacobian when deriving the proposal density.  
-We handle this point by first noticing that the set $\mathcal{A}$ is an $n - p - 1$ dimensional space:  there are $p$ constraints imposed by the regression coefficients and one further constraint imposed by the scale.
+We handle this by first noticing that the set $\mathcal{A}$ is an $n - p - 1$ dimensional space:  there are $p$ constraints imposed by the regression coefficients and one further constraint imposed by the scale.
 Hence, we restrict the initial $\bz^*$ to an easily understood $n - p - 1$ dimensional space.
 Specifically, this space is  the unit sphere in the orthogonal complement of the column space of the design matrix: $\mathbb{S} := \{\bz^* \in \mathcal{C}^{\perp}(X)\  |\  ||\bz^*|| = 1\}$, where $\mathcal{C}(X)$ and  $\mathcal{C}^{\perp}(X)$ are the column space of $X$ and its orthogonal complement, respectively.
-With $\bz^{*}\in \mathbb{S}$, $c\bz^{*} + X\bv$ is not (unless $c=1$ and $\bv = \mathbf{0})$; the scaling by $c$ and/or the affine transformation in the direction of $\mathcal{C}(X)$ takes the point off $\mathbb{S}$.
+The mapping $h: \mathbb{S} \rightarrow \mathcal{A}$ is one-to-one and onto.
+The one-to-one property makes the change of variables more feasible.
+The onto property is important so that the support of the proposal distribution (i.e.
+the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
+A formal theorem and proof is provided in the appendix.
+
+%With $\bz^{*}\in \mathbb{S}$, $c\bz^{*} + X\bv$ is not (unless $c=1$ and $\bv = \mathbf{0})$; the scaling by $c$ and/or the affine transformation in the direction of $\mathcal{C}(X)$ takes the point off $\mathbb{S}$.
 The mapping $h: \mathbb{S} \rightarrow \mathcal{A}$ is one-to-one making the change of variables more feasible.
 
-With the domain of $h(\cdot)$ restricted to  $\mathbb{S}$, the range is still the entirety of $\mathcal{A}$.
-This is important so that the support of the proposal distribution (which is the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
+%With the domain of $h(\cdot)$ restricted to  $\mathbb{S}$, the range is still the entirety of $\mathcal{A}$.
+This is important so that the support of the proposal distribution (i.e.
+the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
 To see that the range of $h(\cdot)$ is $\mathcal{A}$, consider any $\by \in \mathcal{A}$ and its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$.
@@
 \begin{enumerate}
-\item Scale from $\mathbb{S}$ to the set $\Pi(\mathcal{A}):= \{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\ s.t.\ \bz=Q \by \}$.
-$\Pi(\mathcal{A})$ is the projection of $\mathcal{A}$ onto $\mathcal{C}^{\perp}(X)$ and, by condition \ref{regIn}, every element of this set has $s(X, \bz) = s(X, \by_{obs})$.
+\item Scale from $\mathbb{S}$ to the set $\Pi(\mathcal{A}):= \{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\ s.t.\ \bz=Q \by \}$ with $Q = I - XX^{\top}$.
+\footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).} $\Pi(\mathcal{A})$ is the projection of $\mathcal{A}$ onto $\mathcal{C}^{\perp}(X)$ and, by condition \ref{regIn}, every element of this set has $s(X, \bz) = s(X, \by_{obs})$.
 Specifically, set $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$.
@@
 \label{simData}
-We study the performance of the restricted likelihood in a hierarchical setting contaminated with outliers. Specifically, simulated data come from the following data generating model:
-\begin{align}
+We study the performance of restricted likelihood methods in a hierarchical setting where the data are contaminated with outliers.
+Specifically, simulated data come from the following model:\begin{align}
 \label{gensim2}
@@
 The two versions use Huber's and Tukey's $\psi$ function, while both versions use Huber's $\chi$ function.
-The tuning parameters associate with these functions are chosen so that the estimators are $95\%$ efficient under normally distributed data.
-Both of these are well known M-estimators used in robust regression settings  \citep{huber2009}.
+The tuning parameters associated with these functions are chosen so that the estimators are $95\%$ efficient under normally distributed data.
+These classical M-estimators are commonly used in robust regression settings  \citep{huber2009}.
 %We will see that his choice has some interesting effects on the results.
@@
 For each data set and each pair $(a_{s}, c)$, the Bayesian models are fit using MCMC.
-The MCMC for the restricted likelihood version requires no further computational details other than those described for the traditional Bayesian model in Section \ref{BayesLinMod}.
+The MCMC for the restricted likelihood version requires no computational details other than those described for the traditional Bayesian model in Section \ref{BayesLinMod}.
 This is because there are conditioning statistics for each group and the model's conditional independence between the groups allows the data augmentation described earlier to be performed independently within each group.
-That is, there is a separate Gibbs step for each group  generating group level data matching the statistics for that group.
-
-To assess the predictive capability, the models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution.
+That is, there is a separate Gibbs step for each group to generate the group level data matching the statistics for that group.
+
+To assess predictive capability, the models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution.
 Specifically, for the $i^{th}$ group of the $k^{th}$ simulated data set $\by_{k}$ compute:
@@
 \end{equation}
-where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2}) = N(\tilde y | \theta_{i}, \sigma^{2})$; the mean $\theta_{i}$ and variance $\sigma^{2}$ normal pdf evaluated at $\tilde y$.
+where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2}) = N(\tilde y | \theta_{i}, \sigma^{2})$; the normal density function with mean $\theta_{i}$ and variance $\sigma^{2}$, evaluated at $\tilde y$.
 For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})d\theta_{i}d\sigma^{2}_{i}$ where $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
@@
 The classical fits are done separately for each group with no consideration of the hierarchical structure between the groups.
-The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models where smaller means correspond to better fits.
-Sampling variation is summarized with the standard error $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
+The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models, where smaller means correspond to better fits.
+Sampling variation is summarized with the standard error between the $K=30$ replicates in the simulation:  $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
 
@@
 The values of $a_{s}$ and $c$, do not effect the classical robust linear models.
-The normal theory model results are left out as they perform significantly worse.
+The average KL  for the normal theory model ranges between $0.31$ and $0.37$ which is much worse than the robust methods and hence these are left out of the figure.
 Overall, the results are strikingly in favor of the restricted likelihood methods for the range of hyper-parameter values studied.
@@
 \label{kl_sim}
-\caption{Average KL - divergence plus/minus one standard error for each value of $a_{s}$ and $c$.
-The panels correspond to $c = 0.5$ (left), $c=1$ (middle), and $c=2$ (right) with the values of $a_{s}$ on the horizontal axis.}
+\caption{Average KL - divergence plus/minus one standard error for each value of $a_{s}$ and $c$ ($\overline{KL}^{(M)}_{{\cdot}{\cdot}} \pm SE(\overline{KL}^{(M)}_{{\cdot} k})$).
+Smaller values represent better fits.
+The panels correspond to $c = 0.5$ (left), $c=1$ (middle), and $c=2$ (right) with the values of $a_{s}$ on the horizontal axis.
+The average KL  for the normal theory model ranges between $0.31$ and $0.37$ and are left out of the figure.}
 \end{figure}
 
-It is also interesting to consider the effects of factors $n_{i}$, $p_{i}$, and $m_{i}$.
+%% DELETE?
+%It is also interesting to consider the effects of factors $n_{i}$, $p_{i}$, and $m_{i}$.
 For a given factor and simulation, the $KL^{(M)}_{ik}$  are averaged by factor level.
@@
 %Finally, as $p$ grows the bias of the estimates gets significantly larger; resulting in poorer estimation and poorer KL-divergences.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width = 4in]{kl_sim2_mnp.png}
-\caption{Average KL - divergence plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right)}
-\label{kl_mnp}
-\end{figure}
-\begin{figure}[t]
-\centering
-\includegraphics[width = 4in]{rlm_mnp_theta.png}
-\caption{Boxplots $(\theta_{i} - \hat\theta_{i})$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right) where $\hat\theta_{i}$ are the classical robust estimators (Huber's and Tukey's).}
-\label{boxTheta}
-\end{figure}
-\begin{figure}[t]
-\centering
-\includegraphics[width = 4in]{rlm_mnp_sigma.png}
-\caption{Boxplots of the classical robust estimators (Huber's and Tukey's) for $\sigma_{i}$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right).
+% 
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width = 4in]{kl_sim2_mnp.png}
+%\caption{Average KL - divergence plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right)}
+%\label{kl_mnp}
+%\end{figure}
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width = 4in]{rlm_mnp_theta.png}
+%\caption{Boxplots $(\theta_{i} - \hat\theta_{i})$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right) where $\hat\theta_{i}$ are the classical robust estimators (Huber's and Tukey's).}
+%\label{boxTheta}
+%\end{figure}
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width = 4in]{rlm_mnp_sigma.png}
+%\caption{Boxplots of the classical robust estimators (Huber's and Tukey's) for $\sigma_{i}$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right).
 The horizontal line at $\sigma = 2$ highlights the true standard deviation of the `good' data.}
-\label{boxSigma}
-\end{figure}
-
-This simulation shows the potential of the restricted likelihood while highlighting some interesting observations.
+%\label{boxSigma}
+%\end{figure}
+%% --------
+{EDIT THIS} This simulation shows the potential of the restricted likelihood while highlighting some interesting observations.
 Specifically, the choice of summary statistics, along with corresponding tuning parameters is important.
@@
 %The household counts (response and predictor) have been square rooted to stabilize variance. 
-The data a grouped by states with a varying number of agencies by state.
+The data are grouped by states with a varying number of agencies by state.
 Identifiers such as agency/agent names are removed.
@@
 Among the open agencies, linear correlations exists with strength depending on agency type and state.
-`Type 1' agencies open in 2012 are of special interest and one could easily subset the analysis to only these agencies, removing the others.
+`Type 1' agencies open in 2012 are of special interest.
+One could easily subset the analysis to only these agencies, removing the others.
 However,  we leave them and use the data as a test bed for our techniques by fitting models that do not account for agency closures or contract type.
-Our expectation is that the restricting likelihood will facilitate prediction for the `good' part of the data (i.e.
+Our expectation is that the restricted likelihood will facilitate prediction for the `good' part of the data (i.e.
 open, `type 1' agencies).
@@
 $g = n_{p}$ is analogous to the unit-information prior \citep{kass1995reference}, with the difference that we are using a prior data set, not the current data set, to set the prior.
-The obvious reason this model is misspecified is due to the numerous outliers.
-Additionally, the model assumes equal variance within each state which is arguably in question (see Figure \ref{fig:ctVct}) %$f = 0.05, 0.1, 0.5, 1$ and%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
+The obvious reason this model is misspecified is due to omission of the contract type and agency closure information.
+Closing our eyes to these variables, many of the cases appear as outliers.
+Additionally, the model assumes equal variance within each state, an assumption whose worth is arguable (see Figure \ref{fig:ctVct}).
+%$f = 0.05, 0.1, 0.5, 1$ and%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
 %corresponding to  a unit information prior for $\bbeta$.
@@
 to retain the desired evaluation function and trim cases \citep{jung2014}.  Here,
-we pursue the trimming approach with log predictive density for the Bayesian models and log plug-in 
+we pursue the trimming approach with log predictive density for the Bayesian models and log density from plug-in 
 maximum likelihood for the classical fits used as the evaluation function.
@@
 Holdout evaluation is done on the remaining (`Type 1') samples.
-For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.15$ $0.76$ across the states, repetitions, and two versions of the model.
+For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.15$ to $0.76$ across the states, repetitions, and two versions of the model.
 The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
@@
 Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.
-For the other states, the Student-t performs similarly to our restricted methods for the smaller states (State 15 and 36) and smaller training size (25\% of the sample).
-However, the performance is worse for the larger training size (50\% of the sample).
-Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model; detrimental for prediction.
-The relative performance of the models are similar for various values $\alpha$ as seen in Figure \ref{fig:tlmbyAlpha} which shows results for training sample size $0.5n$.
+For the other states, the Student-t performs similarly to our restricted methods for the smaller states (State 15 and 36) and smaller training sample size (25\% of the sample).
+However, the performance is worse for the larger training sample size (50\% of the sample).
+Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model which is detrimental for prediction.
+The relative performance of the models are similar for various values of $\alpha$ as seen in Figure \ref{fig:tlmbyAlpha} which shows results for training sample size $0.5n$.
 
@@
 The color corresponds to the fitting model.
-}
+Larger values of TLM are better.}
 \label{fig:tlm}
@@
 \caption{Average TLM plus/minus one standard deviation over $K = 50$ splits into training and holdout samples for several values of the trimming fraction $\alpha$.
-The training sample size used is $0.5n$.}
+The training sample size used is $0.5n$.
+Larger values of TLM are better.}
 \label{fig:tlmbyAlpha}
@@
 we fit the normal theory hierarchical model above, a thick-tailed $t$ version with $\nu = 5$ d.f., and two restricted likelihood versions (Huber's and Tukey's) of the model.
-For the incomplete restricted methods, we condition on robust regression estimates fit separately within each state.
+For the restricted methods, we condition on robust regression estimates fit separately within each state.
 We also fit classical robust regression counterparts and a least squares regression separately within each state.
@@
 $TLM_b(A)_{j}$ is computed for each state for $K=50$ splits of training and holdout sets.
-The Bayesian models are fit using MCMC with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} and adapted to the hierarchical setting as described in Section \ref{simData}.
+The Bayesian models are fit using MCMC, with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} and adapted to the hierarchical setting as described in Section \ref{simData}.
 For the MH-step proposing augmented data,  the acceptance rates for the two restricted likelihood models across all states and repetitions ranges from $0.24$ to  $0.74$.
@@
 This can be seen in Figure \ref{fig:hierTLMsd} which shows the standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over the $K=50$ repetitions.
-It is clear that the hierarchical model reduces sample-to-sample variation in comparison the the classical robust model counterparts.
+It is clear that the hierarchical model reduces sample-to-sample variation in comparison to the classical robust model counterparts.
 
@@
 \includegraphics[width=6in]{hier_average_tlm.png}
-\caption{Hierarchical model results: $\overline{TLM}_b(A)_{\cdot}$  plus/minus one standard deviation over $K = 50$ splits into training and holdout sets with the Student-t as the base model and several values of the trimming fraction $\alpha$.}
+\caption{Hierarchical model results: $\overline{TLM}_b(A)_{\cdot}$  plus/minus one standard deviation over $K = 50$ splits into training and holdout sets with the Student-t as the base model and several values of the trimming fraction $\alpha$.
+Larger values of TLM are better.}
 \label{fig:hierTLM}
@@
 Huber's version down-weights outliers, but never completely trims them.
-The states are ordered along the $x$-axis according to number of agencies with the state (shown in parentheses).
+The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses).
 In several of the smaller states, the restricted hierarchical model performs better on average with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior.
@@
 \caption{Hierarchical model results: ${TLM}_b(A)_{j}$  plus/minus one standard deviation over $K = 50$ repetitions for each state and $\alpha = 0.3$.
-The states are ordered along the $x$-axis according to number of agencies with the state (shown in parentheses).
-Results displayed are for the robust models using Tukey's M-estimators.}
+The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses).
+Results displayed are for the robust models using Tukey's M-estimators.
+Larger values of TLM are better.}
 \label{fig:hierTLMstate}
@@
 \caption{Hierarchical model results: Standard deviation of ${TLM}_b(A)_{j}$  relative to the mean over $K = 50$ repetitions for each state and $\alpha = 0.3$.
-The states are ordered along the $x$-axis according to number of agencies with the state (shown in parentheses).
+The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses).
 Results displayed are for the robust models using Tukey's M-estimators.}
@@
 In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model.
-We ask the question Òby attempting to improve our model through elaboration, will the overall performance of the model suffer?Ó If yes, we avoid the elaboration, retaining a model with some level of misspecification.
+We ask the question ``by attempting to improve our model through elaboration, will the overall performance of the model suffer?'' If yes, we avoid the elaboration, retaining a model with some level of misspecification.
 Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present.
@@
 \end{eqnarray}
+\end{proof}
+
+\noindent
+\begin{theorem}
+The mapping $h:  \mathbb{S} \rightarrow \mathcal{A}$ with $h$ defined in Theorem \ref{Transformation} is one-to-one and onto. 
+\end{theorem}
+\begin{proof} 
+\noindent 
+\textit{one-to-one}: Let $z_{1}, z_{2} \in \mathbb{S}$ with $h(z_{1}) = h(z_{2})$.
+Rearrangement implies $z_{1} = cz_{2} + Xv$ for known $c\in \mathbb{R}$ and $v\in \mathbb{R}^{p}$ depending on $\bb(X,\by_{obs})$, $s(X,\by_{obs})$, $\bb(X,z_{1})$, $s(X,z_{1})$, $\bb(X,z_{2})$, $s(X,z_{2})$.
+Given $z_{2}\in \mathbb{S}$, $v\neq 0$ implies $z\notin \mathcal{C}^{\perp}(X)$ and $c\neq 1$ implies $||z_{1}|| \neq 1$.
+Thus $z_{1} \in \mathbb{S}$ implies $c=1$ and $v =0$.
+
+\noindent \textit{Onto:} Let $\by \in \mathcal{A}$ and consider its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$.
+It is easy to show that $\bz^{*} = Q\by/||Q\by|| \in \mathbb{S}$ and $h(\bz^{*}) = \by$.
 \end{proof}
@@
 
-In setting the parameters for the beta prior on $\mu_{\rho}$ and gamma prior on  $\psi_\rho$ we first take $\hat z_{j}= \Phi^{-1} (H(\hat\sigma_{j}^{2}))$.
+Finally, recall $\rho\sim\text{beta}(a_\rho,b_\rho)$ with mean $\mu_\rho=a_\rho/(a_\rho+b_\rho)$ given a beta prior and precision
+$\psi_\rho=a_\rho+b_\rho$ given a gamma prior.
+There is little evidence of any strong correlation amongst estimates of $\sigma^{2}_{j}$ in the prior data set and we set the prior mean of $\mu_{\rho}$ equal to $0.2$ and prior variance to $.01$.
+Noting $\text{var}(\rho|\mu_{\rho}, \psi_{\rho})=\mu_{\rho} (1-\mu_{p})/(\psi_{\rho}+1)$ we plug in $\mu_{\rho} = 0.2$ and $\text{var}(\rho|\mu_{\rho}, \psi_{\rho}) = 0.01$.
+Solving for $\psi_{\rho}$ results in a value of $15$.
+This is taken to be the mean of the gamma prior on $\psi_{\rho}$.
+Finally, we  set the rate parameter for to 1 implying the variance of the gamma prior is equal to its the mean.
+With this specification, the prior on $\rho$ has 80\% of the central mass between roughly $0.03$ and $0.42$ and reflects our prior believe that there is likely only weak correlation amongst the $\sigma^{2}_{j}$'s.
+%%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$
+
+%In setting the parameters for the beta prior on $\mu_{\rho}$ and gamma prior on  $\psi_\rho$ we first take $\hat z_{j}= \Phi^{-1} (H(\hat\sigma_{j}^{2}))$.
 As in the prior we assume $(\hat z_1,\dots,\hat z_J)\sim N_J(\mathbf{0}, \Sigma_\rho)$ with
-$\Sigma_\rho=(1-\rho)\mb{I}+\rho \mb{1}\mb{1}^{\top}$ and find the MLE, $\hat\rho_{mle}$, and observed inverse Fisher information, $I^{-1}(\rho_{mle})$.
+%$\Sigma_\rho=(1-\rho)\mb{I}+\rho \mb{1}\mb{1}^{\top}$ and find the MLE, $\hat\rho_{mle}$, and observed inverse Fisher information, $I^{-1}(\rho_{mle})$.
 The mean of the beta prior on $\mu_{\rho}$ is set to $\hat\rho_{mle}$.
@@
 Finally, we  set the rate parameter to 1 implying the variance of the gamma prior is equal to its the mean.
-%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$
+%%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$
 

### 2018-11-02 revision_1/code/data_analysis/prior.R

@@ -28,6 +28,10 @@ sigma2_hat <- prior_fit$s^2
 
 a_0 <- 5
 b_0 <- sigma2_hat*(a_0 - 1)
+
+b_0/(a_0 - 1)
+b_0^2/((a_0-1)^2*(a_0-2))
+
 curve(dinvgamma(x, a_0,b_0), from=0, to=.01)
 
 
@@ -76,7 +80,7 @@ abline(h = beta_0)
 
 plot(sigma2Hats)
 abline(h = sigma2_hat)
-sigma2Hats <- sigma2Hats[-which(sigma2Hats > .01)] #get rid of large estimates
+sigma2Hats <- sigma2Hats #[-which(sigma2Hats > .01)] #get rid of large estimates
 plot(sigma2Hats)
 abline(h = sigma2_hat)
 
@@ -159,38 +163,38 @@ Z <- sapply(sort(sigma2Hats), FUN=fn.compute.Z, a_0 = a_0, b_0 = b_0)
 K <- length(Z)
 J <- matrix(1, K,K)
 
-# log.like.rho<-function(rho){
-#   K*log(1-rho)+log(1+K*rho/(1-rho))+(1-rho)*t(Z)%*%Z+rho*t(Z)%*%J%*%Z
-# }
-
-# K*log(1-rho)+log(1+K*rho/(1-rho))+(1-rho)*t(Z)%*%Z+rho*t(Z)%*%J%*%Z  
-# log.like.rho<-function(rho){
-#   #K*log(1-rho)+log(1+K*rho/(1-rho))+(1-rho)*t(Z)%*%Z+rho*t(Z)%*%J%*%Z  
-#   K*log(1-rho)+log(1+K*rho/(1-rho))+t(Z)%*%solve((1-rho)*diag(K) + rho*J)%*%Z
-# }
-
+log.like.rho<-function(rho){
+  Sigma_rho <- ((1-rho)*diag(K) + rho*J)
+  Sigma_rho_inv <- solve(Sigma_rho)
+  K*log(1-rho)+log(1+K*rho/(1-rho))+t(Z)%*%Sigma_rho_inv%*%Z
+}
 
 log.like.rho2 <-function(rho){
   Sigma_rho <- ((1-rho)*diag(K) + rho*J)
   Sigma_rho_inv <- solve(Sigma_rho)
-  .5*log(det(2*pi*Sigma_rho)) + .5*t(Z)%*%Sigma_rho_inv%*%(Z)
[…]

### 2018-11-02 revision_1/code/simulation/hierarchical_sim/2_summarizeSimulations.R

@@ -6,21 +6,17 @@ New_results <- TRUE
 
 if(New_results){
 sims <- 1:30
-
+ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
+scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
+sig2 <- 4
 dfs_all <- vector('list', length(sims))
+results_df <- file.path(getwd(), 'results')
 for(data_sim in sims){
 # load the data, along with the factor levels, and true values of theta
 data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
 n_groups <- length(data$theta)
-results_df <- file.path(getwd(), 'results')
 factor_list <- as.data.frame(do.call(rbind, data$factorsList))  
 names(factor_list) <- c('p', 'n','m')
-
-
-ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
-scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
-sig2 <- 4
-
 
 # MSE evaluation metric -----
 
@@ -125,7 +121,7 @@ labels_vals <- scale_color_discrete(
 
 
 theme_set(theme_bw())
-ggplot(df_mse %>%  filter(method != 'Normal' & statistic != 'Normal'), aes(x = as.factor(a_s), y = mean_MSE, col = interaction(method,statistic), group = interaction(method,statistic))) + geom_errorbar(aes(ymin = mean_MSE - sd_MSE/sqrt(length(sims)), ymax = mean_MSE + sd_MSE/sqrt(length(sims))), linetype = 2, width = .1, position = position_dodge(width = .5)) + geom_point(position = position_dodge(width = .5)) +
+ggplot(df_mse %>%  filter(method != 'Normal' & statistic != 'Normal'), aes(x = as.factor(a_s), y = mean_MSE, col = interaction(method,statistic), group = interaction(method,statistic))) + geom_errorbar(aes(ymin = mean_MSE - sd_MSE/sqrt(length(sims)), ymax = mean_MSE + sd_MSE/sqrt(length(sims))), linetype = 1, width = .1, position = position_dodge(width = .5)) + geom_point(position = position_dodge(width = .5)) +
[…]

### 2018-11-02 revision_1/code/simulation/hierarchical_sim/kl_check.R

@@ -1,0 +1,125 @@
+# checking calculation of kl_divergence for the classical models.
+
+library(tidyverse)
+library(MASS)
+
+
+fn.gen.data <- function(sigma2) {
+  p <- c(.1,.2,.3)
+  n <- c(25,50, 100)
+  m <- c(9, 25)
+  factors <- expand.grid(p,n,m)
+  yList <- list()
+  factorsList <- list()
+  theta <- numeric(nrow(factors)*5)
+  for (nfac in 1:nrow(factors)) {
+    p <- factors[nfac,1] 
+    n <- factors[nfac,2]
+    m <- factors[nfac,3]
+    for (j in 1:5) { 
+      thetai <- rnorm(1) #muTrue=0, tau2True=1
+      theta[5*(nfac - 1) + j] <- thetai
+      ps <- rbinom(n,1,p)
+      vars <- ifelse(ps, m, 1)*sigma2
+      yList[[5*(nfac - 1) + j]] <- rnorm(n, thetai, sqrt(vars))
+      factorsList[[5*(nfac - 1) + j]] <- c(p,n,m)
+    }
+  }
+  out <- list()
+  out$factorsList <- factorsList
+  out$yList <- yList
+  out$theta <- theta
+  out
+}
+
+
+#exact: for use with the robust regression methods
+KL_twoNormals <- function(mu1,sigma2_1, mu2, sigma2_2){
+  #KL(p,q) where p~N(mu_1,sigma2_1),q~N(mu_2, sigma2_2)
+  sig_1 <- sqrt(sigma2_1)
+  sig_2 <- sqrt(sigma2_2)
+  log(sig_2/sig_1) + (sigma2_1 + (mu1 - mu2)^2)/(2*sigma2_2)-1/2  
+}
+
+
+
+
+sig2True <- 4 
+n_sim <- 100
+results_list <- lapply(1:n_sim, function(i){
+YList <- fn.gen.data(sig2True)
+factorsList <- YList$factorsList
+factorsMat <- as.data.frame(matrix(unlist(factorsList), nrow = 90, ncol = 3, byrow = TRUE))
+names(factorsMat) <- c("p", "n", "m")
+thetaTrue <- YList$theta
+factorsMat$theta <- thetaTrue
+YList <- YList$yList
+ests <- sapply(YList, function(y){
+  fit <- rlm(y ~ 1,  psi = psi.huber, scale.est = 'Huber')
[…]

### 2018-11-03 revision_1/paper.tex
fixes to simulation post-processing code and corresponding edits to the simulation section of paper

@@
 For each we set $b_{s} = 4a_{s}c$ resulting in a prior mean for each $\sigma^{2}_{i}$ of $\frac{4ca_{s}}{a_{s}-1}, \ a_{s} >1$.
-The precision is $\frac{(a_{s} -1)^{2}(a_{s}-2)}{(4ca_{s})^{2}}$; meaning the larger $a_{s}$, the more informative the prior.
+The precision is $\frac{(a_{s} -1)^{2}(a_{s}-2)}{(4ca_{s})^{2}}$; meaning larger $a_{s}$ and smaller $c$ result in a more informative prior.
 With $c = 1$ the shrinkage (for large $a_{s}$) is to the true value of $\sigma^{2} = 4$.
-We consider $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$.
-%Values of $c \neq 1$ will result in shrinkage towards the wrong value of $\sigma^{2}$.
+We consider $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$ for a total of nine different priors whose densities are displayed in Figure \ref{fig:priors}.
+The vertical dashed line is at the known true value of $\sigma^{2} = 4$.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width = 4in]{priors_sigma2.png}
+\label{fig:priors}
+\caption{The nine different inverse gamma priors used for the group level variance parameters $\sigma_{j}^{2}$ in the simulation.
+The shape parameter values are $a_{s} = 1.25, 5, 10$.
+The scale parameter values are $b_{s} = 4a_{s}c$ with $c = 0.5, 1, 2$.
+The vertical dashed line in each panel is at the true value of $\sigma^{2} = 4$ and is the variance of the good portion of the data in the simulation.}
+\end{figure}
 
@@
 For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})d\theta_{i}d\sigma^{2}_{i}$ where $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
-$M$ denotes either the full normal theory model \eqref{fullsim2} or one of the two restricted likelihood versions, along with $a_{s}$ and $c$.
+$M$ denotes either the full normal theory model \eqref{fullsim2} or one of the two restricted likelihood versions, along with specified $a_{s}$ and $c$.
 For the classical robust fits, we set $f_{i}(\tilde y | M, \by_{k}) = N(\tilde y|\hat\theta_{i}, \hat\sigma^{2}_{i})$ as a groupwise plug-in estimator for the predictive distribution.
@@
 Figure \ref{kl_sim} displays $\overline{KL}^{(M)}_{{\cdot}{\cdot}}$  with error-bars plus/minus one $SE(\overline{KL}^{(M)}_{{\cdot} k})$ for each $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$.
-%The panels are for $c = 0.5, 1, 2$ with $a_{s} = 1.25,  5, 10$ on the abscissa.
 The values of $a_{s}$ and $c$, do not effect the classical robust linear models.
-The average KL  for the normal theory model ranges between $0.31$ and $0.37$ which is much worse than the robust methods and hence these are left out of the figure.
-Overall, the results are strikingly in favor of the restricted likelihood methods for the range of hyper-parameter values studied.
-Undoubtably, the most precise and accurate prior studied is  $c = 1$ and $a_{s} = 10$  and this results in the lowest (and best) average KL for both the Tukey and Huber restricted likelihood versions (shown in the middle panel).
-$c = 0.5$ performs the worst, but still better than the classical fits.
-There is evidence that performance starts to degrade in this case when $a_{s} = 10$ as reflected in a larger average KL.
-Here, the prior mean and precision are $2.22$ and $1.62$ and we suspect this is starting to put too much mass on $\sigma^{2}_{i}$ values much smaller than $\sigma^{2}=4$.
-For $c = 2$, the performance still improves from $a_{s} = 5$ to $a_{s} = 10$.
-Here the mean is $8.89$ and precision is only $0.1$; apparently not yet large enough to degrade the performance due to an incorrect mean.
-Lastly, Tukey's statistic performs marginally better than Huber's.
+The average KL  for the normal theory models range between $0.22$ and $0.3$ which is much worse than the robust methods and hence are left out of the figure.
+For $c = 0.5$ and $c = 1$, the results are in favor of the restricted likelihood methods with perhaps a slight advantage to the use of Tukey's location estimator over Huber's.
 This is likely due to the fact that Tukey's estimator trims extreme outliers completely in the estimation procedure \citep{huber2009}.
+For $c = 2$, the classical methods win, again with a slight advantage to Tukey's statistic.
+It is clear that the priors picture in Figure \ref{fig:priors} matter.
+For $c = 2$, the priors subsequently add more mass significantly above $\sigma^{2} = 4$ as $a_{s}$ gets larger.
+Additionally the tuning parameters chosen for the location and scale estimators result in an upward bias in the estimate of $\sigma^{2}$.
+This bias depends on $m$ and $p$.
+For example, for $m = 9$ and $p = .1$, Huber's version converges to roughly $4.8$ asymptotically with $n$ under the data generating model.
+This bias gets worse for more severe contamination levels in the simulation.
+For $c = 0.5$ and $c = 1$, the priors place more mass on smaller values as $a_{s}$ grows.
+The larger values of $a_{s}$ also result in  better (smaller) average KL divergence.
+For $c = 1$ the prior concentration is roughly around the true $\sigma^{2} = 4$.
+For $c = 0.5$ the prior concentration is roughly around half $\sigma^{2} = 2$.
+Interestingly, this prior performs better in terms of KL divergence than having the seemingly more correct prior with $c = 1$.
+This prior does not capture good prior information on $\sigma^{2}$, but does compensates more for the upward bias in the estimates of scale.
+This highlights one potential effect of the choice of statistic and associated tuning parameters when applying the restricted likelihood.
 
@@
 
-%% DELETE?
-%It is also interesting to consider the effects of factors $n_{i}$, $p_{i}$, and $m_{i}$.
-For a given factor and simulation, the $KL^{(M)}_{ik}$  are averaged by factor level.
-For the Bayesian models, the averages are also taken over the different values of $a_{s}$ and $c$.
-Figure \ref{kl_mnp} displays these averages for $m,n,$ and $p$ with error bars plus/minus one standard error.
-The restricted likelihood versions consistently perform better than their classical counterparts.
-Intuitively, as the amount of contamination ($p$) increases performance degrades as it becomes more difficult to identify the good data.
-Likewise, as $n$ increases, the performance for the Bayesian methods become closer to that of the their classical counterparts reflecting the diminishing effect of the prior.
-However, the decrease of KL-diveregence with $m$ and increase with $n$ is somewhat surprising.
-To investigate, Figure \ref{boxTheta} and \ref{boxSigma} display boxplots of $(\theta_{i} - \hat\theta_{i})$ and $\hat\sigma_{i}$ for each simulated data set.
-The $\hat\theta_{i}$'s have no systematic bias however the $\hat\sigma_{i}$'s do; consistently biased upward from the value of $\sigma = 2$ for the good portion of data.
-As $n$ increases, the bias remains the same and the variation in the estimates gets smaller.
-Thus, the estimates are getting more certain about an incorrect value; explaining the degradation of the KL-divergence.
-As $m$ increases, the variance in the estimates gets larger and there is a marginal increase in the bias.
-Thus, for $m=9$ there is more certainty about an incorrect value and  the increased uncertainty at $m=25$ helps to improve the KL-divergence.
-%Finally, as $p$ grows the bias of the estimates gets significantly larger; resulting in poorer estimation and poorer KL-divergences.
-% 
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width = 4in]{kl_sim2_mnp.png}
-%\caption{Average KL - divergence plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right)}
-%\label{kl_mnp}
-%\end{figure}
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width = 4in]{rlm_mnp_theta.png}
-%\caption{Boxplots $(\theta_{i} - \hat\theta_{i})$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right) where $\hat\theta_{i}$ are the classical robust estimators (Huber's and Tukey's).}
-%\label{boxTheta}
-%\end{figure}
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width = 4in]{rlm_mnp_sigma.png}
-%\caption{Boxplots of the classical robust estimators (Huber's and Tukey's) for $\sigma_{i}$ across all simulations separated by the values for $m$ (left), $n$ (middle), $p$ (right).
-The horizontal line at $\sigma = 2$ highlights the true standard deviation of the `good' data.}
-%\label{boxSigma}
-%\end{figure}
-%% --------
-{EDIT THIS} This simulation shows the potential of the restricted likelihood while highlighting some interesting observations.
+It is also interesting to consider the effects of factors $n$, $p$, and $m$.
+We subset the results to a single prior ($a_s = 5$ and $c = 1$) to not confound the effects of the different priors.
+For each simulation $k$, the main effect averages of $KL^{(M)}_{ik}$  are found for each factor $n$, $p$, and $m$.
+Figure \ref{kl_mnp} displays the average of these main effects over the $K = 30$ simulations along  with error bars plus/minus one standard error.
+For each group $n$, $p$, and $m$ the restricted versions have better (lower) average KL divergences.
+The patterns also makes sense: average KL with get larger (worse) as the contamination gets more severe (larger $m$ or larger $p$) and average KL gets smaller (better) as the sample size $n$ grows.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width = 4in]{kl_sim2_mnp.png}
+\caption{Average KL - divergence plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right).
+Results for a single prior ($a_s = 5$ and $c = 1$) are displayed to not confound the effects of the different priors.}
+\label{kl_mnp}
+\end{figure}
+
+This simulation shows the potential of the restricted likelihood while highlighting some interesting observations.
 Specifically, the choice of summary statistics, along with corresponding tuning parameters is important.
-For the tuning parameters, the standard choice of $95\%$ efficiency at the normal was used.
-Under the data generating model here, this choice results in bias in the scale estimation which affects the performance of the method.
-These choices must be made in both the classical and Bayesian settings.
-The Bayesian setting allows for the incorporation of informative prior information which, as shown in this example, can dramatically improve prediction.
-The results are sensitive to the prior, but here we have observed good relative improvement over the classical counterparts for a range of prior choices.
+For the tuning parameters, we applied the default choice of $95\%$ efficiency at the normal.
+Under the simulation model here, this choice results in bias in the scale estimation which affects the performance of the method.
+These choices must be made when using both the classical and Bayesian methods.
+The Bayesian setting allows for the incorporation of informative prior information which, as shown in this example, can improve prediction if chosen wisely.
+%In this severe outlier contamination setting, the better performance of the priors that shrink towards too small of values for $\sigma^{2}$ ($c = 0.5$) is an artifact of the fact that the tuning parameters on the estimators were non-optimal for this setting and more shrinkage was needed.
+However, a good choice for a prior on $\sigma^{2}$ ($c = 1$) still performs well.
+%A more refined model could have different tuning parameters for the groups representing different levels of contamination.
+However, a prior knowledge for
+
+%The results are sensitive to the prior, but here we have observed good relative improvement over the classical counterparts for a range of prior choices.
 
@@
 It is clear that the prior is having the effect of pooling information across states; beneficial for reducing the sample-to-sample variance.
-Figure \ref{fig:hierTLMstateSD} shows this benefit by plotting the standard deviation of ${TLM}_b(A)_{j}$ relative to the mean for each state.
-The general trend in the figure is that the standard deviation decreases as $n_{j}$ increases.
-Additionally, the differences between the models is larger for smaller states with virtually identical standard deviations for the larger states.
+Generally,  the standard deviations are smaller for the hierarchical model for smaller states with virtually identical standard deviations for the larger states.
 Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.
@@
 
-\begin{figure}[t]
-\includegraphics[width=7in]{hier_sd_tlm_state.png}
-\caption{Hierarchical model results: Standard deviation of ${TLM}_b(A)_{j}$  relative to the mean over $K = 50$ repetitions for each state and $\alpha = 0.3$.
+%\begin{figure}[t]
+%\includegraphics[width=7in]{hier_sd_tlm_state.png}
+%\caption{Hierarchical model results: Standard deviation of ${TLM}_b(A)_{j}$  relative to the mean over $K = 50$ repetitions for each state and $\alpha = 0.3$.
 The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses).
 Results displayed are for the robust models using Tukey's M-estimators.}
-\label{fig:hierTLMstateSD}
-\end{figure}
+%\label{fig:hierTLMstateSD}
+%\end{figure}
 

### 2018-11-03 revision_1/code/data_analysis/hier_reg_analysis.R

@@ -474,7 +474,7 @@ swSq <- 1
  
   
 #computing marginal likelihoods for each element in holdout sample
-nTheory_marg_mn_sd <-fn.compute.marginals.hierModelNormal(betal, nTheory$sigma2s, yhold,Xhold)
+nTheory_marg_mn_sd <- fn.compute.marginals.hierModelNormal(betal, nTheory$sigma2s, yhold,Xhold)
 nTheory_marg <- lapply(nTheory_marg_mn_sd, function(x) x[,1])
 marginals[norm_ind, i,] <- nTheory_marg %>% unlist() 
 nTheory_marg_sd <- lapply(nTheory_marg_mn_sd, function(x) x[,2])

### 2018-11-09 revision_1/response.tex
edits bug fix for data analysis section

@@
 We have also made some refinements to the data analysis section to help highlight some of the advantages of out approach.
+In particular, we present results for individual state-level regressions for states of various sizes.
+We also streamline the presentation of the hierarchical model by including a single training sample size, as the differences before were not that meaningful with the different training sample sizes.
 \end{itemize}
@@
 \begin{itemize}
-\item We have made substantial revisions to the paper, especially the MH algorithm in an to make the details more clear including: more detail on the simplification of the the MH ratio R in (7) and (8); the fact that  $f(y|T (y), \theta)$ is not available in closed form (only up to a proportionality constant), so direct generation is difficult.
+\item We have made substantial revisions to the paper, especially the MH algorithm in an attempt to make the details more clear including: more detail on the simplification of the the MH ratio R in (7) and (8); the fact that  $f(y|T (y), \theta)$ is not available in closed form (only up to a proportionality constant), so direct generation is difficult.
 \end{itemize}
@@
 We paid more attention to the clarity of the new figures.
-The purpose of Figure 1 is explained better in Section on the MCMC algorithm (now section 4).
+The purpose of Figure 1 (now Figure 3) is explained better in Section on the MCMC algorithm (now section 4).
 \end{itemize}

### 2018-11-09 revision_1/paper.tex
edits bug fix for data analysis section

@@
 Likewise, state labels and agency types (identifying the varying contractual agreements) have been made generic to protect the proprietary nature of the data.
+Additionally, the counts scaled to have standard deviation one before anlaysis.
 %The data are proprietary, and to mask them all variables have been individually centered and scaled and identifiers (agency/agent names and state labels) have been removed.All subsequent analysis is done on this scale.
-As an exploratory view, a plot of the square root of household count in 2012, against that in 2010 
+As an exploratory view, a plot of the square root of (scaled) household count in 2012, against that in 2010 
 is shown in Figure \ref{fig:ctVct} for four states.
@@
 \includegraphics[width=5in]{scatter_by_state.png}
-\caption{The square root of count in 2012 versus that in 2010 for four states.
+\caption{The square root of (scaled) count in 2012 versus that in 2010 for four states.
 The colors represent the varying contractual agreements as they stood in 2010 (`Type').
@@
 Holdout evaluation is done on the remaining (`Type 1') samples.
-For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.15$ to $0.76$ across the states, repetitions, and two versions of the model.
+For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.16$ to $0.76$ across the states, repetitions, and two versions of the model.
 The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
-Similar results are observed for other base models, with this one being most advantageous to the Student-t model.
+Similar results are observed for other base models.
 The error-bars are plus/minus one standard deviation of the average $TLM_b(A)$ over the $K = 50$  training/holdout samples.
@@
 Notably, the Student-t model performs poorly in comparison for this state.
-The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good` data (i.e., the Type 1 agencies).
+The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good' data (i.e., the Type 1 agencies).
 Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.
-For the other states, the Student-t performs similarly to our restricted methods for the smaller states (State 15 and 36) and smaller training sample size (25\% of the sample).
-However, the performance is worse for the larger training sample size (50\% of the sample).
-Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model which is detrimental for prediction.
-The relative performance of the models are similar for various values of $\alpha$ as seen in Figure \ref{fig:tlmbyAlpha} which shows results for training sample size $0.5n$.
+For the other states (State 15 and 36), the Student-t performs similarly to our restricted methods for smaller training sample size (25\% of the sample).
+However, the performance is slightly worse for the larger training sample size (50\% of the sample).
+Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model; an assumption which is detrimental for prediction.
+Comparisons of the models depend on $\alpha$ as seen in Figure \ref{fig:tlmbyAlpha} which shows results for different $\alpha$ for training sample size $0.5n$.
+For smaller $\alpha$ (in this case $\alpha = 0.1$), many outliers are left untrimmed resulting in lower TLM  for all methods and noticeably larger standard deviation for the classical robust methods and our restricted likelihood.
+Larger values of $\alpha$ ensure the predictive performance assessment excludes the majority of outliers.
+The proportion of $0$ counts in the data is roughly $0.14$, suggesting $\alpha$ should be at least this large.
 
@@
 \ref{fig:hierTLM} for several trimming fractions using the Student-t as the base model.
-The points are the average of the $\overline{TLM}_b(A)_{\cdot}$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$.
-The normal theory fits, both Bayesian and classical, perform poorly and are left out of the figures.
+The points are the average of the $\overline{TLM}_b(A)_{\cdot}$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$ with larger values representing better predictive performance.
 As the trimming fraction used for the TLM increases, so does TLM since more outliers are being trimmed.
@@
 non-outlying) data.
-On average, the classical robust regressions fit separately within each state slightly outperform the restricted likelihood hierarchical models.
-The hierarchical model does however reduce variance in predictions at the cost of an increase in bias induced by the prior distributions.
-This can be seen in Figure \ref{fig:hierTLMsd} which shows the standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over the $K=50$ repetitions.
-It is clear that the hierarchical model reduces sample-to-sample variation in comparison to the classical robust model counterparts.
+For each trimming fraction, our restricted likelihood hierarchical models outperform the classical robust regressions fit separately within each state.
+The hierarchical model also reduce variance in predictions resulting in smaller error bars.
+This improvement decreases with $\alpha$ but is still noticeable for $\alpha = 0.3$.
+Both the Tukey and Huber versions perform similarly.
 
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=6in]{hier_sd_tlm.png}
-\caption{Hierarchical model results: standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$.
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=6in]{hier_sd_tlm.png}
+%\caption{Hierarchical model results: standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$.
 Results are given for the two restricted likelihood versions of the hierarchical model and their corresponding robust regression models fit separately within each state.}
-\label{fig:hierTLMsd}
-\end{figure}
+%\label{fig:hierTLMsd}
+%\end{figure}
 
 It is also interesting to examine the results within each state.
-Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ for each state where the points and errorbars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions.
-The results are only given for the models using Tukey's M-estimators since, in general, these models performed the best on average.
-This is attributed to the corresponding $\psi$-function used in the M-estimation which trims large outliers from the data completely.
-Huber's version down-weights outliers, but never completely trims them.
+Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ with $\alpha = 0.3$ for each state where the points and errorbars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions.
+The results are only given for the models using Tukey's M-estimators (Huber's version looks similar).
 The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses).
-In several of the smaller states, the restricted hierarchical model performs better on average with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior.
-It is clear that the prior is having the effect of pooling information across states; beneficial for reducing the sample-to-sample variance.
-Generally,  the standard deviations are smaller for the hierarchical model for smaller states with virtually identical standard deviations for the larger states.
+In several of the smaller states, the restricted hierarchical model performs better with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior.
+It is clear the hierarchical structure is having the effect of pooling information across states; beneficial for improving performance in some of the smaller states.
+The standard deviations are smaller for the hierarchical model in smaller states with virtually identical standard deviations for the larger states.
 Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.
@@
 In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this problem.
-Many routine choices in an analysis react to the gap between reality and the
-statistical model, where a bit of set-up work improves inferential
-performance.  Often, these choices can be recast in the framework of
-restricted likelihood presented here, lending them more formality and facilitating
-development of theoretical results. A greater benefit of our framework is that it leads us to blend classical estimation with
-Bayesian methods.
+This paper discusses the restricted likelihood where posterior inference is conducted by conditioning on a summary statistic rather than the complete data. 
+The framework leads us to blend classical estimation with Bayesian methods.
+%Many routine choices in an analysis react to the gap between reality and the
+%statistical model, where a bit of set-up work improves inferential
+%performance.  Often, these choices can be recast in the framework of
+%restricted likelihood presented here, lending them more formality and facilitating
+%development of theoretical results. 
+%A greater benefit of our framework is that it leads us to blend classical estimation with Bayesian methods. 
 Here, we concentrate on outlier-prone settings where natural choices for conditioning statistic are classical robust estimators targeting the mean of the non-outlying data (e.g., M-estimators).
@@
 Computation is driven by MCMC methods, requiring only a supplement to existing algorithms by adding a Gibbs step to sample from the space of data sets satisfying the observed statistic.
-This step has additional computation costs.
-The estimator must be computed at every iteration to propose a new $\by$.
-This cost, as well as the need to find orthonormal bases derived from gradients of the estimators, adds some computational time compared to the full likelihood MCMC.
-The cost of finding the bases can be driven down by an understanding of the geometric space from which the samples are drawn as described in Section~\ref{highDim}.
+This step has additional computation costs driven by  the need to compute the estimator and an orthonormal basis derived from gradients of the estimator at each iteration.
+The cost of finding the basis can be driven down by an understanding of the geometric space from which the samples are drawn as described in Section~\ref{highDim}.
 Additionally, we have seen good mixing of the MCMC chains across a wide-variety of examples.
@@
 In general, we recommend a choice based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.
-%In our words, to provide desirable inference, we recommend use of robust and relevant summary statistics in conjunction with Bayesian models.
-
-%Many of these results carry over to our blend of classical and Bayesian methods, although regularity conditions differ.
-We expect our procedures to have strong large sample performance, especially in settings where
-%pooling of information is of value.
-
-The most general setting, of which outliers are a subset, is model misspecification.
+
+In general, this framework can be used to address model misspecification, of which the presence of outliers is an example.
 The traditional view is that, if the model is inadequate, one should build a better model.
@@
 In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this more general problem.
-
 The framework allows us to retain many benefits of Bayesian methods:  it requires a complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.
-The work does open a number of questions open to further work, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.
+The work does open a number of questions for further work, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.
 
@@
 Finally, we  set the rate parameter for to 1 implying the variance of the gamma prior is equal to its the mean.
-With this specification, the prior on $\rho$ has 80\% of the central mass between roughly $0.03$ and $0.42$ and reflects our prior believe that there is likely only weak correlation amongst the $\sigma^{2}_{j}$'s.
+With this specification, the prior on $\rho$ has 80\% of the central mass between roughly $0.03$ and $0.42$ and reflects our prior belief that there is likely only weak positive correlation amongst the $\sigma^{2}_{j}$'s.
 %%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$

### 2018-11-09 revision_1/code/data_analysis/single_group_reg_analysis.R

@@ -41,7 +41,7 @@ prior_data <- prior_data %>%
 prior_fit <- MASS::rlm(sqrt_count_2010 ~ sqrt_count_2008 - 1 , scale.est = 'Huber', data =  prior_data, maxit = 100)
 
 # theme_set(theme_bw(base_family = 'Times'))
-# ggplot(prior_data, aes(x = sqrt_count_2008, y = sqrt_count_2010)) + geom_point(size = 1) + xlim(c(0,150)) +  ylim(c(0, 130)) + stat_smooth(method = "rlm", formula = y ~ x - 1, method.args = list(scale.est = 'Huber', maxit = 100), size = .5, lty = 2, se = FALSE, col = 1) + guides(col = guide_legend(title = 'Agency Type'))
+# ggplot(prior_data, aes(x = sqrt_count_2008, y = sqrt_count_2010)) + geom_point(size = 1) + stat_smooth(method = "rlm", formula = y ~ x - 1, method.args = list(scale.est = 'Huber', maxit = 100), size = .5, lty = 2, se = FALSE, col = 1) + guides(col = guide_legend(title = 'Agency Type'))
 
 #load analysis data -------
 
@@ -53,8 +53,7 @@ analysis_data <- read_rds(file.path(here::here(), 'data', 'analysis_data.rds'))
 analysis_data <- analysis_data %>% 
   mutate(sqrt_count_2010 = sqrt(Count_2010), sqrt_count_2012 = sqrt(Count_2012)) %>% filter(State == State_keep)
 
-ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012)) + xlim(c(0,100))
-
+#ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012))
 #MASS::rlm(sqrt_count_2012 ~ sqrt_count_2010 - 1 , scale.est = 'Huber', data =  analysis_data, maxit = 100)
 
 N <- nrow(analysis_data)
@@ -200,7 +199,7 @@ v_ind <- which(beta_var_inflate == v_inflate)
             
       #normal theory bayes model ----
       
-      nTheory <- brlm::bayesLm(y, X , 
+      nTheory <- brlm::bayesLm(y, X, 
                                mu0 = beta_0, 
                                Sigma0 = var_beta_0, 
                                a0 = a_0, 

### 2018-11-09 revision_1/code/data_analysis/summarize_single_reg_analysis.R

@@ -18,7 +18,7 @@ label_vals <- c('2' = 'State 2', '15' = 'State 15', '27' = 'State 27', '36' = 'S
 ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, col = Type), size = 1, alpha = .5) +
   theme_bw() + facet_wrap(~State, labeller = labeller(State = label_vals)) + labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
   theme(text = element_text(family = 'Times'))
-#ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
 
 
 
@@ -30,7 +30,7 @@ cnts <- analysis_data %>% group_by(State) %>%
 #   theme_bw() + 
 #   labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
 #   theme(text = element_text(family = 'Times'))
-# #ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+# ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
 # 
 
 
@@ -147,8 +147,10 @@ pooled_marginals <- bind_rows(pooled_marginals %>% filter(!is.na(var_inflate)), 
 base_model <- 'Student-t' 
 get_tlm_tibble <- function(marginals_tibble, base_model = base_model, trimming_fractions = c(0, .1, .2, .3)){
 
-marginals_open_type1 <- marginals_tibble %>% 
+marginals_open_type1 <- marginals_tibble  %>% 
   filter(Type1 == TRUE)
+
+# marginals_open_type1 <- marginals_open_type1 %>% mutate(var_inflate = ifelse(is.na(var_inflate), 'NotApp', var_inflate)) #so NA's don't get droped on splits
 
 base_model_marg <-  marginals_open_type1 %>% 
   filter(Model == base_model) 
@@ -177,7 +179,8 @@ marg_split <- marginals_open_type1 %>%
 
   marg_split %>% 
   group_by(Repetition, Model, n, State, var_inflate) %>% 
-  summarise(tlm_mean = mean(Marginal), tlm_sd = sd(Marginal)/tlm_mean) %>% 
[…]

### 2019-06-04 revision_2/code/calls/call_t.R
revision_2 branch to work on BA revisions

@@ -1,0 +1,70 @@
+# Analyze the Belgium Calls Data
+
+library(tidyverse)
+library(MASS)
+library(rstan)
+
+log_scale  <- 1
+
+phones$year<- phones$year - mean(phones$year)
+phones <- bind_cols(phones)
+if(log_scale) phones$calls <- log(phones$calls)
+plot(phones$year, phones$calls)
+
+# mn_sd <- summarise_all(phones, funs(mean, sd))
+# phones <- as_tibble(scale(phones))
+
+
+# Restricted fit with Tukey locataion and MAD for scale-----
+
+n_prior <- 3
+(fit <- lm(calls ~ year, data = phones[1:n_prior,]))
+
+
+(lm_fit <- lm(calls ~ year, data = phones))
+# prior parameters -----
+g <- nrow(phones) - n_prior
+mu0 <- fit$coefficients
+X <- model.matrix(fit)
+Sigma0 <- g*sigma(fit)^2*solve(t(X)%*%X)
+a0 <- 2
+b0 <- 1 
+
+
+y <- phones$calls[-c(1:n_prior)]
+X_fit <- cbind(1, phones$year[-c(1:n_prior)])
+x <- X_fit[,2]
+N <- length(y)
+stan_rdump(c("N", "y", 'x', 'mu0', 'Sigma0', 'a0', 'b0'), file = "t.data.R")
+input_data <- read_rdump("t.data.R")
+fit_t <- stan(file='t_stan.stan', data=input_data,
+                chains=4, seed=123, iter = 1e4, refresh=2000)
+
+saveRDS(fit_t, 'out/t_stan.rds')
+fit_t <- readRDS('out/t_stan.rds')
+rstan::get_posterior_mean(fit_t)
+
+plot(fit_t)
+stan_trace(fit_t, window = c(9000,10000))
+# stan_scat(fit_t, pars = c("beta0[1]", "beta0[2]"))
+# stan_scat(fit_t, pars = c("beta1[1]", "beta1[2]"))
+# stan_scat(fit_t, pars = c("sigma[1]", "sigma[2]"))
+
+# stan_scat(fit_t, pars = c("sigma", "beta[2]"))
+# stan_scat(fit_t, pars = c("p", "sigma"))
+stan_dens(fit_t, fill = 'white')
+rlmf <- rlm(y~x, psi = psi.bisquare)
+summary(lm(y~x))
[…]

### 2019-06-04 revision_2/code/calls/calls.R

@@ -1,0 +1,117 @@
+# Analyze the Belgium Calls Data
+
+library(tidyverse)
+#devtools::install_github('jrlewi/brlm')
+library(brlm)
+library(MASS)
+
+library(mvtnorm)
+library(coda)
+library(MCMCpack)
+
+log_scale  <- 1
+
+phones$year<- phones$year - mean(phones$year)
+phones <- bind_cols(phones)
+if(log_scale) phones$calls <- log(phones$calls)
+plot(phones$year, phones$calls)
+
+# mn_sd <- summarise_all(phones, funs(mean, sd))
+# phones <- as_tibble(scale(phones))
+
+
+# Restricted fit with Tukey locataion and MAD for scale-----
+
+n_prior <- 3
+(fit <- lm(calls ~ year, data = phones[1:n_prior,]))
+
+
+(lm_fit <- lm(calls ~ year, data = phones))
+# prior parameters -----
+g <- nrow(phones) - n_prior
+mu0 <- fit$coefficients
+X <- model.matrix(fit)
+Sigma0 <- g*sigma(fit)^2*solve(t(X)%*%X)
+a0 <- 2
+b0 <- 1 
+
+
+y <- phones$calls[-c(1:n_prior)]
+X_fit <- cbind(1, phones$year[-c(1:n_prior)])
+
+# Importance Sampling 
+# define statistic
+rlm_tukey <- function(y, X){
+  fit <- rlm(X, y, psi = psi.bisquare,  scale.est = 'MAD', maxit=1e4)
+  c(fit$coefficients, fit$s)
+}
+# importance distribution parameters 
+rlm_tukey(y, X_fit)
+
+rlm_fit <- rlm(calls ~ year, data = phones[-c(1:n_prior),], psi = psi.bisquare, scale.est = 'MAD')
+c(rlm_fit$coefficients, rlm_fit$s)
+plot(phones$year, phones$calls)
+lines(phones$year[-c(1:n_prior)], fitted(rlm_fit))
+
+
+i <- 2
+par(mfrow = c(2,1))
+smp1 <- rnorm(1000, mu0[i], sqrt(Sigma0[i,i]))
+smp2 <- rnorm(1000, rlm_fit$coefficients[i], sqrt(vcov(rlm_fit)[i,i]))
+hist(smp1, xlim = range(smp1, smp2))
[…]

### 2019-06-04 revision_2/code/calls/calls_summarize.R

@@ -1,0 +1,225 @@
+# summarize calls data and make plots
+library(tidyverse)
+library(MASS)
+fig_path <- file.path('..', '..', 'figs')
+log_scale  <- read_rds(path = file.path(here::here(), 'out', 'log_scale.rds'))
+n_prior  <- read_rds(path = file.path(here::here(), 'out', 'n_prior.rds'))
+phones
+#phones$year<- phones$year - mean(phones$year)
+phones <- bind_cols(phones)
+if(log_scale) phones$calls <- log(phones$calls)
+plot(phones$year, phones$calls, ylab = if_else(as.logical(log_scale), 'log calls', 'calls'))
+
+x <- phones$year- mean(phones$year)
+y <- phones$calls
+rl_fit <- read_rds(file.path(here::here(), 'out', 'rl_fit.rds'))
+t_fit <- read_rds(file.path(here::here(), 'out', 't_fit.rds'))
+nu <- 5
+normal_fit <- read_rds(file.path(here::here(), 'out', 'normal_fit.rds'))
+normal_fit_all <- read_rds(file.path(here::here(), 'out', 'normal_fit_all.rds'))
+mixture_fit <- read_rds(file.path(here::here(), 'out', 'mixture_fit.rds'))
+# samples from 'good' part of model
+mixture_fit_good <- cbind(mixture_fit$beta0[,1],mixture_fit$beta1[,1], mixture_fit$sigma[,1])
+apply(mixture_fit_good, 2, mean)
+rl_fit$fit
+#plot(log(rl_fit$w + 1e-20), cex = .2)
+
+
+#functions needed posteriors ----
+
+#plot posteriors
+plot_post_imp <- function(rl_fit, variable = 1, xlim = NULL){
+  plot(density(rl_fit$impSamps[,variable], weights = rl_fit$w), xlim = xlim)
+}
+
+# random sample from ppd for rl_fit
+rpd_rl <- function(rl_fit,x, n){
+  # x = scalar, 
+  # y_tilde = vector of ys to eval pdd 
+  # n number of samples
+  w <- rl_fit$w/sum(rl_fit$w)
+  n_imps <- nrow(rl_fit$impSamps)
+  betas <- rl_fit$impSamps[,1:2]
+  means <-c(1, x)%*%t(betas)
+  sig <- sqrt(rl_fit$impSamps[,3])
[…]

### 2019-06-04 revision_2/code/calls/mix.data.R

@@ -1,0 +1,22 @@
+N <- 21
+y <- 
+c(-0.555520423880492, -0.45409063421027,
+-0.375325065475225, -0.303736167223768, -0.2524249642909,
+-0.151959094900659, -0.0940523684788975,
+-0.0444270215906998, -0.00626377764661846,
+0.0217870444656814, 0.110156331678157, 0.44741105318946,
+0.452878033816443, 0.470356109365662, 0.484353094306456,
+0.50042907382809, 0.517797394274967, 0.281214769091591,
+0.145198447682626, 0.176186204188251, 0.19401129636889)
+x <- 
+c(-8.5, -7.5, -6.5, -5.5, -4.5, -3.5, -2.5, -1.5,
+-0.5, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,
+10.5, 11.5)
+mu0 <- 
+c(-0.311938510987452, 0.052536970789296)
+Sigma0 <- 
+structure(c(2.14301349612066, 0.202869797529078,
+0.202869797529078, 0.0193209330980075),
+.Dim = c(2, 2))
+a0 <- 2
+b0 <- 1

### 2019-06-04 revision_2/code/data_analysis/data/nw_data_clean.R

@@ -1,0 +1,199 @@
+library(MASS)
+library(tidyverse)
+
+load('/Users/john/Dropbox/school/osu/dissertationResearch/snm/linearRegression/nwPaper1upDate/workSpaces/nwdataPrepPaper1DataCleanWorkspace.RData')
+
+analysisSet <- as_tibble(analysisSet)
+priorDataSet <-  as_tibble(priorDataSet)
+
+analysisSet <- analysisSet %>% 
+  dplyr::select(Agency_Type, Primary_Agency_State, Ending_HH_Count2010, Ending_HH_Count2012)
+
+
+
+priorDataSet <- priorDataSet %>% 
+  dplyr::select(Agency_Type, Primary_Agency_State, Ending_HH_Count2008, Ending_HH_Count2010)
+
+
+#Change State Level Names -----
+set.seed(124)
+perm <- sample(1:(length(levels(analysisSet$Primary_Agency_State))-1))
+
+analysisSet <- analysisSet %>% 
+  mutate(State = factor(Primary_Agency_State, labels = perm ))
+
+priorDataSet <- priorDataSet %>% 
+  mutate(State = factor(Primary_Agency_State, labels = perm ))
+
+ind_check1 <- with(analysisSet, table(Primary_Agency_State, State)) %>% 
+  apply(., 2, function(x) which(x != 0))
+ind_check2 <- with(priorDataSet, table(Primary_Agency_State, State))%>% 
+  apply(., 2, function(x) which(x != 0))
+all.equal(ind_check1, ind_check2)
+all.equal(names(ind_check1), names(ind_check2))
+  
+# View(analysisSet %>% dplyr::select(Primary_Agency_State, State))
+# View(priorDataSet %>% dplyr::select(Primary_Agency_State, State))
+(unique(priorDataSet$State))
+
+# Change Agency Type Level Names ----
+types <- unique(c(levels(analysisSet$Agency_Type),levels(priorDataSet$Agency_Type)))
+
+type1 <- which(types == 'CAREER')
+type12 <- which(types == 'PASPORT2')
+set.seed(124)
+perm <- sample(seq_along(types))
+perm <- sapply(perm, function(x){
+  if(x == perm[which(perm == perm[type1])]){
+    1
+  } else {
+    if(x == perm[which(perm == 1)]){
+      perm[type1]
+    } else {
[…]

### 2019-06-04 revision_2/code/data_analysis/hier_reg_analysis.R

@@ -1,0 +1,789 @@
+# Hierarchical regression - i.e., grouped by states. 
+
+# download brlm package if needed
+# library(devtools)
+# install_github('jrlewi/brlm')
+library(sampling) #for stratified sampling
+library(MCMCpack)
+library(MASS)
+library(brlm)
+library(tidyverse)
+
+
+# aux funcitons ----
+
+fn.compute.marginals.hierModelNormal<-function(betalsamples, sigma2lsamples, yhold,Xhold){
+  
+  
+  fits<-function(betahats, X){X%*%betahats}
+  
+  betalSampsList <- lapply(1:dim(betalsamples)[3],function(x) betalsamples[,,x])
+  names(betalSampsList) <- names(yhold)
+  #holdout means
+  
+  nMuList<-mapply(fits, betalSampsList, Xhold)
+  
+  #sd's across samples for each holdout set
+  nSigmaList<-split(sqrt(sigma2lsamples), rep(1:ncol(sigma2lsamples), each = nrow(sigma2lsamples)))
+  names(nSigmaList)<-names(yhold)
+  
+  mapply(FUN=function(yh,mean,sd){
+    pdfs <- dnorm(yh,mean,matrix(rep(sd, length(yh)), length(yh), length(sd),byrow=TRUE))
+    mns <- rowMeans(pdfs)
+    sds <- apply(pdfs, 1, sd)
+    cbind(mns, sds)
+  }
+  ,yhold,nMuList,nSigmaList)
+  
+}
+
+fn.compute.marginals.hierModelTmodel <- function(betalsamples, sigma2lsamples, yhold,Xhold){
+  
+  fits<-function(betahats, X){X%*%betahats}
+  
+  betalSampsList<-lapply(1:dim(betalsamples)[3],function(x) betalsamples[,,x])
+  names(betalSampsList)<-names(yhold)
+  #holdout means
+  nMuList<-mapply(fits, betalSampsList, Xhold)
+  
+  #sd's across samples for each houldout set
+  nSigmaList<-split(sqrt(sigma2lsamples), rep(1:ncol(sigma2lsamples), each = nrow(sigma2lsamples)))
+  names(nSigmaList)<-names(yhold)
+  
+  mapply(FUN=function(yh,mean,sd){
+    # rowMeans(tdensity(yh,mean,matrix(rep(sd, length(yh)), length(yh), length(sd),byrow=TRUE), nu = nu))
[…]

### 2019-06-04 revision_2/code/data_analysis/hier_reg_analysis_normal.R

@@ -1,0 +1,262 @@
+###########################
+#Normal Hierarchical Model Analysis
+###########################
+
+n <- 1000
+# run 
+reps <- 2
+nburn <- 200
+nkeep <- 400
+
+
+Sys.info()
+
+# #run multiple runs
+# seeds <- c(3,4,5,6,7)
+#set seed after this load it brings in a seed already
+set.seed(123)
+
+
+p<-length(mu0Star)
+#for run in run....
+
+
+#-------------------
+#outputs to save
+#--------------------
+nTheoryGroupBetaMeans<-array(NA, c(p,nGroups, reps))
+nTheoryGroupBetaSDs<-array(NA, c(p,nGroups, reps))
+nTheorybetalConverge<-array(NA, c(p,nGroups, reps))
+
+nTheoryBetaMeans<-array(NA, c(p, reps))
+nTheoryBetaSDs<-array(NA, c(p, reps))
+nTheoryBETAconverge<-array(NA, c(p, reps))
+
+nTheorySigma2Means<-array(NA, c(nGroups, reps))
+nTheorySigma2SDs<-array(NA, c(nGroups, reps))
+nTheorySigma2Converge<-array(NA, c(nGroups, reps))
+
+nTheorybstarConverge<-numeric(reps)
+nTheoryMuRhoConverge<-numeric(reps)
+nTheoryPsiRhoConverge<-numeric(reps)
+nTheoryRhoConverge<-numeric(reps)
+
+#predictions: This is a list of lists: For each rep there is a list of the predictions for each state (list length ==22) split by state
+nTheoryPredListofLists<-replicate(reps, list()) 
+
+#marginals
+nTheoryMarginalsListofLists<-replicate(reps, list())
+
+
+
+olsPredListofLists<-replicate(reps, list()) 
+
+#marginals
+olsMarginalsListofLists<-replicate(reps, list())
+
+
+stateCountsList<-list();length(stateCountsList)<-reps
+
+#------------------------------------
+
+
+
+
+system.time(  
+  for(i in 1:reps){
+    
+    
+    trainIndices <- sort(sample(1:N, n))
+    holdIndices <- c(1:N)[-trainIndices]
+    holdIndicesMatrix[i,] <- holdIndices
+    train <- analysis_data[trainIndices,]
+    hold <- analysis_data[holdIndices,]
+    yholdout <- hold$sqrt_count_2012
+    y_hold[i,] <- yholdout
+    
+    
+    
[…]

### 2019-06-04 revision_2/code/data_analysis/prior.R

@@ -1,0 +1,256 @@
+# Script to set up prior distributions ----
+
+library(MASS)
+library(tidyverse)
+library(MCMCpack)
+
+prior_data <- read_rds(file.path(here::here(), 'data', 'prior_data.rds'))
+prior_data <- prior_data %>% 
+  mutate(sqrt_count_2008 = sqrt(Count_2008), sqrt_count_2010 = sqrt(Count_2010))  %>% filter(Type == 1)
+
+
+# pooled regression analysis ----
+prior_fit <- MASS::rlm(sqrt_count_2010 ~ sqrt_count_2008 - 1, scale.est = 'Huber', data =  prior_data)
+
+
+# MASS::rlm(sqrt_count_2012 ~ sqrt_count_2010 - 1, scale.est = 'Huber', data =  analysis_data )
+
+theme_set(theme_bw(base_family = 'Times'))
+#+ xlim(c(0,150)) +  ylim(c(0, 130)) +
+ggplot(prior_data, aes(x = sqrt_count_2008, y = sqrt_count_2010, col = Type)) + geom_point(size = .3) + stat_smooth(method = "rlm", formula = y ~ x -1, method.args = list(scale.est = 'Huber'), size = .5, lty = 2, se = FALSE, col = 1) + guides(col = guide_legend(title = 'Agency Type'))
+
+
+summary(prior_fit)
+beta_0 <- coef(prior_fit)
+se_beta_0 <- vcov(prior_fit)^.5
+beta_var_inflate <- nrow(prior_data)
+sigma2_hat <- prior_fit$s^2
+
+a_0 <- 5
+b_0 <- sigma2_hat*(a_0 - 1)
+
+b_0/(a_0 - 1)
+b_0^2/((a_0-1)^2*(a_0-2))
+
+curve(dinvgamma(x, a_0,b_0), from=0, to=.01)
+
+
+parms_prior <- list(beta_0 = beta_0, se_beta_0 = se_beta_0, sigma2_hat = sigma2_hat, a_0 = a_0, b_0 = b_0, beta_var_inflate = beta_var_inflate )
+write_rds(parms_prior, "parms_prior.rds")
+
+#hierarchcical regression analysis -----
+
+by_state <- prior_data %>% 
+  group_by(State) %>% 
+  filter(n() >= 40) %>% #use state with plenty of data
[…]

### 2019-06-04 revision_2/code/data_analysis/summarize_hier_reg_analysis.R

@@ -1,0 +1,358 @@
+# Summarize the output from pooled regression analysis.
+library(tidyverse)
+library(MASS)
+
+ns <- c(1590)
+
+analysis_data <- read_rds(file.path(here::here(), 'data', 'analysis_data.rds'))
+analysis_data <- analysis_data %>% 
+  mutate(sqrt_count_2010 = sqrt(Count_2010), sqrt_count_2012 = sqrt(Count_2012)) %>%
+  group_by(State) %>% 
+  filter(n() >= 25) %>% ungroup() %>% 
+  mutate(State = factor(State)) %>% #filter(!State %in% c(14, 30)) %>% 
+  arrange(State)
+
+# tmp <- readRDS("~/Dropbox/school/osu/dissertationResearch/snm/journal_papers/brlm_paper/revision_1/code/data_analysis/hier_reg_n1590.rds")
+# holdIndices <- tmp$holdIndices
+
+#creates a dataframe with holdout indices and states for each rep
+holdout_tibble <- function(holdIndices){
+  holdIndices <- t(holdIndices)
+  rownames(holdIndices) <- 1:nrow(holdIndices)
+  holdIndices <- as_tibble(holdIndices, rownames = 'holdout sample')
+  
+  holdIndices <- holdIndices %>% 
+    rename_at(vars(contains('V')), funs(sub('V', '', .))) %>% 
+    gather('Repetition','holdout index', -"holdout sample") %>% 
+    mutate(Repetition = as.numeric(Repetition), `holdout sample` = as.numeric(`holdout sample`))
+  
+  #grab the state
+  holdIndices %>%
+    split(list(.$Repetition)) %>% 
+    map(.f = function(x){
+      holddata <- analysis_data[x$`holdout index`,]
+      x %>% mutate(State = holddata$State, Type =holddata$Type, Open = holddata$Count_2012 > 0)
+    }) %>% 
+    bind_rows() 
+}
+
+
+get_marginals <- function(hier_results, n){
+  
+hold_index <- holdout_tibble(hier_results$holdIndices)  
+
+margs <- apply(hier_results$marginals, 1, function(marg) {
+  marg <- t(marg)
+  rownames(marg) <- 1:nrow(marg)
+  marg <- as_tibble(marg, rownames = 'holdout sample')
+  marg <- marg %>% 
+    rename_at(vars(contains('V')), funs(sub('V', '', .))) %>% 
+    gather('Repetition','Marginal', -"holdout sample") %>% 
[…]

### 2019-06-04 revision_2/code/data_analysis/summarize_pooled_reg_analysis.R

@@ -1,0 +1,153 @@
+# Summarize the output from pooled regression analysis.
+library(tidyverse)
+library(MASS)
+ns <- c(25, 100) #, 1000)
+
+# pooled_results <- readRDS("~/Dropbox/school/osu/dissertationResearch/snm/journal_papers/bayes_rest_like_methods/revision_1/code/data_analysis/pooled_reg_n25.rds")
+
+
+logical_ytibble <- function(y_open, colname){
+  #works on y_open, y_type1 logical matrices
+  #creates a tibble
+  y_open <- t(y_open)
+  rownames(y_open) <- 1:nrow(y_open)
+  y_open <- as_tibble(y_open, rownames = 'holdout sample')
+  
+  y_open %>% 
+    rename_at(vars(contains('V')), funs(sub('V', '', .))) %>% 
+    gather('Repetition',!!colname, -"holdout sample") %>% 
+    mutate(Repetition = as.numeric(Repetition), `holdout sample` = as.numeric(`holdout sample`))
+}
+
+
+single_marginal_tibble <- function(pooled_results, MargName, ModelName){
+  # given pooled_results and the marginal name, creates tibble with holdoutsample, repetition number, marginal value, model name and indicator columns for open and type 1 agencies:
+  #holdout sample is nested within repetition. 
+  
+tmp <- t(pooled_results[[MargName]])
+rownames(tmp) <- 1:nrow(tmp)
+tmp <- as_tibble(tmp, rownames = 'holdout sample')
+tmp <- tmp %>% 
+  rename_at(vars(contains('V')), funs(sub('V', '', .))) %>% 
+  gather('Repetition', 'Marginal', -"holdout sample") %>% 
+  mutate(Model = ModelName, Repetition = as.numeric(Repetition), `holdout sample` = as.numeric(`holdout sample`))
+
+y_open <- logical_ytibble(pooled_results$y_open, colname = 'Open')
+y_type1 <- logical_ytibble(pooled_results$y_type1, colname = 'Type1')
+
+full_join(tmp, y_open) %>% full_join(., y_type1)
+
+}
+
+
+marginals_tibble <- function(pooled_results){
+  #pooled results is the list of output for a set of runs from the pooled regression - there is one for each sample size. 
[…]

### 2019-06-04 revision_2/code/data_analysis/summarize_single_reg_analysis.R

@@ -1,0 +1,251 @@
+# Summarize the output from single regression per state analyses.
+library(tidyverse)
+library(MASS)
+
+
+ns <- c(25, 50) #sample size for training set
+states <- c(2, 15, 27, 36)
+v_inflate <- c(100)
+
+# plots ---- 
+analysis_data <- read_rds(file.path(here::here(), 'data', 'analysis_data.rds'))
+
+analysis_data <- analysis_data %>% 
+  mutate(sqrt_count_2010 = sqrt(Count_2010), sqrt_count_2012 = sqrt(Count_2012)) %>% filter(State %in% states) %>% 
+  mutate(State = droplevels(State))
+
+label_vals <- c('2' = 'State 2', '15' = 'State 15', '27' = 'State 27', '36' = 'State 36')
+ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, col = Type), size = 1, alpha = .5) +
+  theme_bw() + facet_wrap(~State, labeller = labeller(State = label_vals)) + labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
+  theme(text = element_text(family = 'Times'))
+ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+
+
+
+cnts <- analysis_data %>% group_by(State) %>% 
+  summarise(n = n())
+# 
+# ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, col = Type), size = 1, alpha = .25) +
+#   facet_wrap(~State, labeller = label_bquote(State ~ .(State)))+ 
+#   theme_bw() + 
+#   labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
+#   theme(text = element_text(family = 'Times'))
+# ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+# 
+
+
+
+logical_ytibble <- function(y_open, colname){
+  #works on y_open, y_type1 logical matrices
+  y_open <- t(y_open)
+  rownames(y_open) <- 1:nrow(y_open)
+  y_open <- as_tibble(y_open, rownames = 'holdout sample')
+  y_open %>% 
+    rename_at(vars(contains('V')), funs(sub('V', '', .))) %>% 
+    gather('Repetition',!!colname, -"holdout sample") %>% 
[…]

### 2019-06-04 revision_2/code/simulation/hierarchical_sim/2_summarizeSimulations.R

@@ -1,0 +1,533 @@
+#
+# Summarize the simulations ---
+#
+library('tidyverse')
+New_results <- FALSE
+
+
+sims <- 1:30
+ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
+scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
+sig2 <- 4
+
+if(New_results){
+
+dfs_all <- vector('list', length(sims))
+results_df <- file.path(getwd(), 'results')
+for(data_sim in sims){
+# load the data, along with the factor levels, and true values of theta
+data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
+n_groups <- length(data$theta)
+factor_list <- as.data.frame(do.call(rbind, data$factorsList))  
+names(factor_list) <- c('p', 'n','m')
+
+# MSE evaluation metric -----
+
+dfs <- vector('list', length(ass.vec)*length(scale_vec)*length(sig2))
+i <- 1
+for(ss in sig2){
+  for(as in ass.vec){
+    for(sc in scale_vec){
+      rds_name <- paste0("_",data_sim, "__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
+    
+    huber <- read_rds(file.path(results_df, paste0("huber", rds_name)))
+    
+    #computes the estimates --- 
+    theta_huber_rest <- apply(huber$theta, 2, mean)
+    theta_huber_rlm  <- sapply(huber$robustFits, function(x) x$coefficients)
+    sigma2_huber_rest <- apply(huber$sigma2, 2, mean)
+    sigma2_huber_rlm  <- sapply(huber$robustFits, function(x) summary(x)$sigma^2)
+    
+    huber_df <- as_tibble(cbind(factor_list, theta = rep(data$theta,2), 
+                       theta_hat = c(theta_huber_rest, theta_huber_rlm), 
+                       sigma2_hat = c(sigma2_huber_rest,  sigma2_huber_rlm),
+                       statistic = rep('Huber', 2*n_groups), 
+                       method = c(rep('restricted', n_groups), rep('rlm', n_groups)),
+                       a_s = rep(as, 2*n_groups),
+                       scale_as = rep(sc, 2*n_groups),
+                       sigma2 = rep(ss, 2*n_groups)
+                       ))
+    
+    
[…]

### 2019-06-04 revision_2/code/simulation/hierarchical_sim/SimulationSourceCode.R

@@ -1,0 +1,432 @@
+#
+# Simulation ------- 
+#
+
+#requires sourcing linearRegressionHuberAndProposal2.R #path may need to be changed
+# Adjust source for Steve's directories at work
+source('linearRegressionHuberAndProposal2.R')
+# source('//trad/profs$/maceachern.1/Desktop/LEWIS.LEE/codeForPaper/codeForPaper/linearRegressionHuberAndProposal2.R')
+
+
+#
+# Complete Model ----
+# theta_i \sim N(mu, tau^2)
+# Y_ij | \theta_i \sim N(\theta_i, sigma_i^2)  
+# with a fairly flat distribution on mu, tau^2 and sigma_i^2.
+# mu \propto 1, \tau^2 \propto 1/\tau^2 = IG(0,0), sigma_i^2 \~ IG(ass, bss)
+# i runs from 1 to 90
+#
+
+#
+# Data Generation ----
+# see fn.gen.data
+# theta_i~N(0,1) i=1,...,90
+# Y_ij | \theta_i \sim (1-p) N(theta_i, sigma2)+ p N(theta_i,m*sigma2), j=1,...,n_i
+
+#90 groups formed by factorial stucture of the 3 factors
+# n_i=25, 50, 100
+# p= .1,.2,.3
+# m= 9, 25
+# each combination observed in five groups
+# sigma2 also will vary: .5, 1, 4, 10
+
+#
+# 
+# Sampling functions---
+#
+#
+
+# [tau^2 | rest ] ----
+
+# tau^2 \sim IG(a,b) in functional form with a=b=0
+fn.sample.tau2<-function(theta, mu, a=0, b=0){
+  #theta is the vector of theta_i
+  K<-length(theta)
+  anew<-0.5*K+a
+  bnew<-0.5*sum((theta-mu)^2)+b
+  1/rgamma(1, shape=anew, rate=bnew)
+}
+
+# [mu | rest ] ----
+
+fn.sample.mu<-function(theta, tau2){
+  K<-length(theta)
+  rnorm(1, mean(theta),sqrt(tau2/K))
+}
+
+# [sigma2_i| rest ] ----
+# sigma2_i \sim IG(a,b) in functional form with a=b=0
+
+# fn.sample.sigma2.i<-function(Yi, thetai, a=0,b=0){
+fn.sample.sigma2.i<-function(Yi, thetai, ass , bss){  # SteveMod
[…]

### 2019-06-04 revision_2/code/simulation/hierarchical_sim/old_3_summarizeSimulations.R

@@ -1,0 +1,413 @@
+#
+# Summaries of Evaluation Metrics ---
+#
+library('plyr')
+library('reshape2')
+rm(list=ls())
+concTau2Near1<-0
+
+#if(concTau2Near1){
+#  load('simPostProcessed_concTau2Near1.RData')
+#  #load('simPostProcessed2_concTau2Near1.RData')
+#} else {
+#  load('simPostProcessed.RData')
+#  #load('simPostProcessed2.RData')
+#}
+load('//trad/profs$/maceachern.1/Desktop/LEWIS.LEE/codeForPaper/codeForPaper/StevesimPostProc.RData') # SteveMod
+
+
+#load('simPostProcessed2_sampleVersion.RData')
+sumNames<-c('Full', 'RestHuber', 'RestTukey', 'RlmHuber','RlmTukey')
+#get(paste0('mse', sumNames[1],'Sig2_', sigma2True[1]))
+
+
+#combine the results into data.frame
+mseDf<-matrix(NA, ncol=9)
+klDf<-matrix(NA, ncol=9)
+#trimMspeDf<-matrix(NA, ncol=9)
+#tlmDf<-matrix(NA, ncol=9)
+
+for(i in 1:length(sigma2True)){
+mseDfTemp<-cbind(factorsMat, sigma2True[i])
+klDfTemp<-cbind(factorsMat, sigma2True[i])
+#trimMspeDfTemp<-cbind(factorsMat, sigma2True[i])
+#tlmDfTemp<-cbind(factorsMat, sigma2True[i])
+
+#meanTlmDfTemp<-cbind(factorsMat, sigma2True[i])
+ for(j in 1:5){
+   mseDfTemp<-cbind(mseDfTemp, get(paste0('mse', sumNames[j],'Sig2_', sigma2True[i])))
+   klDfTemp<-cbind(klDfTemp, get(paste0('kl', sumNames[j],'Sig2_', sigma2True[i])))
+ #  trimMspeDfTemp<-cbind(trimMspeDfTemp, get(paste0('trimMspe', sumNames[j],'Sig2_', sigma2True[i]))/sigma2True[i]) 
+  # tlmDfTemp<-cbind(tlmDfTemp, get(paste0('tlm', sumNames[j],'Sig2_', sigma2True[i]))) 
[…]

### 2019-06-04 revision_2/code/simulation/simulation_location_scale/1_simulation1.R

@@ -1,0 +1,200 @@
+# Simulation
+  # simulate data from a 'true model'
+  # fit various models. 
+  # estimate mean
+  # repeat
+
+
+
+#Note - when re-run, previous results are deleted
+
+library(brlm)
+library(rstan)
+library(tidyverse)
+library(MASS)
+library(MCMCpack)
+
+set.seed(123)
+
+# choose true model ----
+#either normal, mixture 1, mixture 2, or t
+# true_model <- 't'
+
+
+source('source.R')
+#simulation parameters ----
+n_sim <- 25
+samp_sizes <- c(50, 100, 200)
+
+
+# prior parameters ----
+eta <- 0
+tau <- 4
+a <- 3
+b <- 2
+ngridpts <- 500 #for KL computations
+
+iter <- 4000 #total length of MCMC iterations
+
+
+for(true_model in c("Recording Error")){#"Normal", "Mixture 1", "Mixture 2",, "Student-t"))
+
+p <- .1
+  
+# create data_gen function----
+#generates true data
+if(true_model == 'Normal'){
+data_gen <- function(n){
+  rnorm(n)
+}
+} else if(true_model == 'Mixture 1'){
+  data_gen <- function(n){
+    x <- rbinom(n, 1, 1-p)
+    sapply(x, function(a) ifelse(a, rnorm(1), rnorm(1, sd = 3)))
+  }
+} else if(true_model == 'Mixture 2'){
+  data_gen <- function(n){
+  x <- rbinom(n, 1, 1-p)
+  sapply(x, function(a) ifelse(a, rnorm(1), rnorm(1, mean = 3,  sd = 3)))
+  }
+} else if(true_model == 'Recording Error'){
+  data_gen <- function(n){
+  x <- rnorm(n)
+  ind <- sample(1:length(x), size = floor(n*p))
+  x[ind] <- 10*x
+   # end <- floor(length(ind)/2)
+   # x[ind[1:end]] <- -3
+   # x[ind[(end+1):length(ind)]] <- 4
+  # plot(x)
+  x
+  }
+}
+
+
+
+
+
+# set up empty tibbles to store results----
+empty_mat <- matrix(NA, n_sim, length(samp_sizes))
+colnames(empty_mat) <- samp_sizes
+empty_mat <- as_tibble(empty_mat)
+
[…]

### 2019-06-04 revision_2/code/speed_of_light/mix.data.R

@@ -1,0 +1,12 @@
+N <- 66
+y <- 
+c(28, -44, 29, 30, 24, 28, 37, 32, 36, 27, 26,
+28, 29, 26, 27, 22, 23, 20, 25, 25, 36, 23, 31, 32,
+24, 27, 33, 16, 24, 29, 36, 21, 28, 26, 27, 27, 32,
+25, 28, 24, 40, 21, 31, 32, 28, 26, 30, 27, 26, 24,
+32, 29, 34, -2, 25, 19, 36, 29, 30, 22, 28, 33, 39,
+25, 16, 23)
+eta <- 23.6
+tau <- 2.04
+a <- 5
+b <- 10

### 2019-06-04 revision_2/code/speed_of_light/speed_of_light.R

@@ -1,0 +1,97 @@
+# Fitting several models to speed of light data
+
+library(brlm)
+library(MASS)
+library(mvtnorm)
+library(coda)
+library(MCMCpack)
+
+data(newcomb)
+y <- newcomb
+
+# prior parameters ----
+eta <- 23.6; tau <- 2.04; alpha <- 5; beta <- 10;
+
+
+# fitting parameters for rl_direct ----
+mu_lims <- c(20, 35); length_mu <- 300;
+sigma2_lims <- c(1, 60); length_sigma2 <- 500;
+N <- 5000
+
+
+# Tukey Fit ---- 
+rlm_tukey <- function(y){
+  fit <- rlm(y~1,psi = psi.bisquare,  scale.est = 'proposal 2', maxit=50)
+  c(fit$coefficients, fit$s)
+}
+
+set.seed(1)
+fit_tukey <- brlm:::rl_direct(y, statistic = rlm_tukey, eta, tau, alpha, beta, mu_lims, sigma2_lims,length_mu, length_sigma2, smooth=1,N)
+
+saveRDS(fit_tukey, 'out/fit_tukey.rds')
+
+# Huber Fit ----
+rlm_huber <- function(y){
+  fit <- rlm(y~1,psi = psi.huber,  scale.est = 'proposal 2', maxit=50)
+  c(fit$coefficients, fit$s)
+}
+
+
+set.seed(1)
+fit_huber <- brlm:::rl_direct(y, statistic = rlm_huber, eta, tau, alpha, beta, mu_lims, sigma2_lims,length_mu, length_sigma2, smooth=1,N)
+saveRDS(fit_huber, 'out/fit_huber.rds')
+
+# LMS fit -----
+rlm_lms <- function(y){
+  fit <- lqs(y~1, method='lms')
+  c(fit$coefficients, fit$scale[1])
+}
+
+
+set.seed(1)
+fit_lms <- brlm:::rl_direct(y, statistic = rlm_lms, eta, tau, alpha, beta, mu_lims, sigma2_lims,length_mu, length_sigma2, smooth=1,N)
+saveRDS(fit_lms, 'out/fit_lms.rds')
+
+
+# LTS fit -----
+rlm_lts <- function(y){
+  n <- length(y)
+  quantile<-floor(.95*n)
[…]

### 2019-06-04 revision_2/code/speed_of_light/summarize_speed_of_light.R

@@ -1,0 +1,190 @@
+# summarize the speed of light fits
+library(tidyverse)
+fig_path <- file.path('..', '..', 'figs')
+nu <- 5
+
+# read results ---- 
+fit_tukey <- readRDS('out/fit_tukey.rds')
+fit_huber <- readRDS('out/fit_huber.rds')
+fit_lms <- readRDS('out/fit_lms.rds')
+fit_lts <- readRDS('out/fit_lts.rds')
+fit_normal <- readRDS('out/fit_normal.rds')
+fit_t <- readRDS('out/fit_t.rds')
+fit_mixture <- readRDS('out/fit_mixture.rds')
+
+extract_pdf <- function(fit, model){
+beta <- tibble(beta = fit$muPost[,1], posterior = fit$muPost[,2], Model = model)
+sigma2 <- tibble(sigma2 = fit$sigma2Post[,1], posterior = fit$sigma2Post[,2], Model = model)
+list(beta = beta, sigma2 = sigma2)
+}
+
+pdf_tukey <- extract_pdf(fit_tukey, 'Tukey')
+pdf_huber <- extract_pdf(fit_huber, 'Huber')
+pdf_lms <- extract_pdf(fit_lms, 'LMS')
+pdf_lts <- extract_pdf(fit_lts, 'LTS')
+
+
+
+compute_pdf <- function(samples, model){
+  pdf_beta <- density(samples[,1])
+  pdf_sigma2 <- density(samples[,2])
+  beta <- tibble(beta = pdf_beta$x, posterior = pdf_beta$y, Model = model)
+  sigma2 <- tibble(sigma2 = pdf_sigma2$x, posterior = pdf_sigma2$y, Model = model)
+  list(beta = beta, sigma2 = sigma2)
+}
+
+pdf_normal <- compute_pdf(fit_normal, 'Normal')
+pdf_t <- compute_pdf(fit_t, 't')
+fit_mix_good <- cbind(fit_mixture$beta, fit_mixture$sigma2)
+pdf_mixture <- compute_pdf(fit_mix_good, 'Mixture')
+
+model_order <- c('Normal', 't', 'Mixture', 'Tukey', 'Huber', 'LMS', 'LTS')
+beta_pdfs <- bind_rows(pdf_normal$beta, pdf_t$beta, pdf_mixture$beta, pdf_tukey$beta, pdf_huber$beta, pdf_lms$beta, pdf_lts$beta)
[…]

### 2019-06-04 revision_2/response/response.tex
added response folder to record our responses

\documentclass{article}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\usepackage{graphicx, psfrag, amsfonts, float}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{hhline}
 \pdfminorversion=4
\usepackage{rotating}
\def\bgam{\mbox{\boldmath $\gamma$}}
\def\bth{\mbox{\boldmath $\theta$}}
\def\bbeta{\mbox{\boldmath $\beta$}}
\def\blam{\mbox{\boldmath $\lambda$}}
\def\bmu{\mbox{\boldmath $\mu$}}

\newcommand{\bx}{\mbox{\boldmath $x$}}
\newcommand{\bu}{\mbox{\boldmath $u$}}
\newcommand{\bc}{\mbox{\boldmath $c$}}
\newcommand{\bs}{\mbox{\boldmath $s$}}
\newcommand{\by}{\mbox{\boldmath $y$}}
\newcommand{\bz}{\mbox{\boldmath $z$}}
\newcommand{\bv}{\mbox{\boldmath $v$}}
\newcommand{\bb}{\mbox{\boldmath $b$}}
\newcommand{\bzero}{\mbox{\boldmath $0$}}
\newcommand{\thstarj}{\mbox{$\theta^\star_j$}}
\newcommand{\bths}{\mbox{$\btheta^\star$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\uI}{\mathrm{I}}
\newcommand{\uP}{\mathrm{P}}
\newcommand{\up}{\mathrm{p}}
\newcommand{\mb}{\mathbf}
\newcommand{\mc}{\mathcal}

\newcommand{\Bern}{\mbox{Bern}}
\newcommand{\Nor}{\mbox{N}}
\newcommand{\Ga}{\mbox{Gamma}}
\newcommand{\Dir}{\mbox{Dir}}
\newcommand{\Ber}{\mbox{Ber}}
\newcommand{\Be}{\mbox{Be}}
\newcommand{\Unif}{\mbox{Unif}}
\newcommand{\Binom}{\mbox{Bin}}
\newcommand{\IG}{\mbox{IG}}

\newcommand{\Xs}{X^\star}
\newcommand{\Lc}{{\cal L}}

\usepackage[dvipsnames,usenames]{color}
\newcommand{\yy}{\color{magenta}\it}
\newcommand{\jj}{\color{Black}\rm}
\newcommand{\yjnote}[1]{\footnote{\color{Brown}\rm #1 \color{Black}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{\bf Definition}
\newtheorem{lemma}[theorem]{\bf Lemma}
\newtheorem{corollary}[theorem]{\bf Corollary}
\newtheorem{proposition}[theorem]{\bf Proposition}
\newtheorem{assumption}[theorem]{\bf Assumption}
\newtheorem{example}[theorem]{\bf Example}
\newtheorem{remark}[theorem]{\bf Remark}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\stackrel{indep}{\sim}}

\setlength{\textwidth}{6 in}
\usepackage{color}
\usepackage{ulem} % \sout
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\brown}[1]{{\color{brown}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\graphicspath{{figures/}{figs/}}

\begin{document}

\section{Reviewer 1 Comments}

\begin{enumerate}
\item The authors propose a broad class of the proposal density, but didn’t discuss the choice and tuning within the class. Tuning the proposal is crucial to the mixing and efficiency of the MH algorithm, epecially in the high-dimension space, n ? p-dimensional, that the paper is dealing with. There are two difficulties in tuning within the proposed class. First, since the proposal density is a complicated transformation of p(z?) in Rn?p?1, even if p(z?) belongs to a standard parametric family, p(yp|?) does not and it is not straightforward to assess the properties that are usually used in tuning MCMC algorithm, e.g. mode and
tails behaviour. Second, the proposed algorithm (11) is restrictive because it only works for independent proposal, not the random walk proposal. Random walk is more able to explore a non-standard parameter space like the manifold here, while it seems tricky to design the independent proposal that well covers the probability mass of the target density, which again due to the transformation.
\item The simulation studies didn’t report the choice of p(z?), acceptance rates of the MH, and mixing of the overall MCMC algorithm. Due to point 1, I think these issues would be of interest to readers.
\item The models studied in both the simulation and real data examples are just simple linear regression which is not realistic. Multiple linear regression with at least three independent variables should be studied.
\item What are the benefits of the proposed method over the classical robust point estimators, like Huber or Tukey estimators compared in the examples, to offset the additional compu- tational cost and tuning efforts? From the simulation studies, whether it has improvement or not depends on the prior distribution, which seems to be from comparing Bayesian and Frequentist methods. Actually, literatures on the asymptotic properties of f(?|T(yobs)) shows that, if T (yobs) is asymptotically unbiased, T (yobs) and E(? | T (yobs)) have the same asymptotic variance. Hence if the prior doesn’t matter, both methods have similar performance.
\item I think f(?|T(yobs)) might perform better in the following scenario: when T(yobs) is asymp- totically biased, E(?|T(yobs)) can still be asymptotically unbiased as long as the true pa- rameter is identifiable conditioning on the summary statistic, i.e the value of E(T(yobs)) is unique on the true parameter. One possible example is the robust ridge-regression estimator, but it needs further investigation whether this estimator satisfies C1-C8.
\item In page 14, should C?(X) n ? p-dimensional instead of n ? p ? 1-dimensional?
\end{enumerate}

\section{Reviewer 2 Comments}

\begin{enumerate}
\item Is the proposed framework useful for practitioners? The proposed framework targets scenario where (i) we know the data is a mixture of good and bad data, and (ii) we only want to “build models that offer good prediction for the good portion of the data” (from the 1st paragraph of Sec 5). Authors should provide real examples in which (i) and (ii) hold. In any real examples, (i) often holds, but (ii) doesn’t: if we already have had a contaminated training sample, why would we expect the test sample to contain only the good portion? In many real applications, learning the heterogeneity of the good and bad samples is precisely the goal of statistical data analysis.
For the insurance example analyzed in Sec 6, the authors should provide ev- idence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.
\item As a methodological paper, what’s the guideline/recommendation given by the authors? After reading this paper, I don’t know how to apply the suggested framework
on a simple regression model. Apparently, the choice of the likelihood func-
tion (for the good data) f(·|?) and the choice of the statistic T are related.
To make things more complicated, each has multiple choices. For example, f could be normal, student-t or other heavy-tailed distribution; T could be something named Huber or Tukey although the authors are not even bothered to provide any mathematical expression.

Instead of just reporting numerical performance, the authors should provide some guidelines/recommendation on how to apply their framework on linear regression models, e.g., what are the default choices for f and T ? Is there any- way to select which f or T to use based on cross-validation or other empirical methods?
\item What’s the real benefit of this computationally expensive approximation framework? The proposed framework replies on a good summary statistic T(yobs), which
has already provided a robust estimate of the target parameter. On the other
hand, the proposed MCMC algorithm is computationally expensive. In Sec
4.2, the authors only discussed the computation cost for their proposal dis- tribution, but ignored the computation cost for obtaining T(y) (see Theorem 4.1). Those statistics are M-estimators, i.e., they are maximizers of some objective functions involving n observations and p parameters. The authors should discuss the computation cost for T(y).
What’s the gain of all the extra computation? The authors compare KL diver- gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y?|M,yobs) is not available in closed-form; 2) since f(y?|M,yobs) is not available close-form, the KL divergence is approximated and it’s not clear to me how accurate the approximation is.
The authors should compare prediction and estimation accuracy, common met- rics used for regression models.
The simulation setup is too simple. Suggest to add some linear regression models with large p and/or large n.
\end{enumerate}

\subsection{Some minor issues.}
\begin{enumerate}
\item  Abstract “... handling data sets with outliers and dealing with model mis- specification. We outline the drawbacks ... and propose a new method as an alternative.” The proposed method cannot handle “model misspecification”, instead it assumes f is the true model (no misspecification) and what’s wrong is part of the data.
\item  Sec 2 and Sec 3 can be shortened or merged.
\item  Eq(2) in Sec 2.1, the notation f(yi|?,c(yi)) is not introduced yet; what’s introduced is f(y|?).

\item  Sec 4.1, C3 and C4: a maximizer may not be a continuous function of the data and it may not be unique. Instead of saying “Many estimators satisfy the above properties”, the authors should list those estimators and explain why those conditions are satisfied.
\item  Bottom of p14, ”Sample z? from a distribution with known density on S.” Any distribution? For example, can it be a point mass or its support has to be equal to S? What’s the sampling distribution for z? used in the simulation studies and real data analysis?
\item  Eq (18): change dy to dy?
\end{enumerate}

\section{AE Comments}
This paper proposes a Bayesian approach for making inference based on robust statistics of the data instead of the original observations. The conditioning robust statistics pass the desirable robustness (to outliers) to the posterior distribution of parameters, thus having the potential to improve inference and prediction. This paper addresses an important problem in statistics and contains interesting ideas. However, there are some major concerns.
The paper focuses on outliers. Although outliers automatically imply that the model is misspecified, model misspecification is much broader including the misspecification of the density of the good data. The paper does not appear to address model misspecification beyond the case when outliers are present. Please revise the scope of the paper as appropriate or provide more examples to ensure outliers and model misspecification are parallel contributions rather than one nested in another.
There are many implementation details that an interested user would like to learn more but feel difficult to find from the current paper. This includes but not limited to the selection of proposal, parameter tuning, recommendations when a practitioner is being faced with a real-world problem, and computational complexity of the entire procedure. See the two referee reports for more details. The authors are also suggested to possibly provide code that is available online with recommended choices as default.
It is unclear how the proposed method outperforms existing work, either conceptually or practically. Referees have provided some competing methods for the authors to consider. I'd like to add another existing strategy in addition to the three solutions mentioned in the bottom paragraph of page 2: Bayesian fractional inference, which uses a fractional likelihood function that raises a usual likelihood function to a fractional power. What is the advantage of the proposed restrictive likelihood approach over Bayesian fractional inference, even conceptually?
Overall, the paper deserves publication after careful and thorough revision. I hope the authors can address all concerns raised in this report and the two well-grounded referee reports.

\section{Editor Comments}

Report on ìBayesian restricted likelihoods: conditioning on in su¢ cient statistics in Bayesian regressionî
The paper has received a mixed reaction from the two referees and the AE. I have a similar reaction to the paper but agree with the other readers that the content is such that an opportunity to address the issues raised is appropriate. The AEís comments place the paper on the border between Reject with Resubmission and Major Revision. I mention this because it isnít clear that a revision will be successful as there are some significant criticisms in the reviews.
My concerns might be a little different than the others and perhaps are less technical in nature. It is generally agreed that *all* models are wrong. The incorrectness of the model can arise in a number of ways and some observations being outliers is one of these. The natural question then is: how are we supposed to deal with that? The answer is surely that we don't unless the discrepancy is so substantial that the inferences would be seriously in error if we proceeded using the assumed model. This part of a statistical analysis is the model checking aspect and the solution to any issue, whatever it might be, arises there. For example, for the problem being considered in this paper, I would want a model checking procedure that indicated that there is a serious problem because, no matter what distribution was used from the model, some observations are outlying and I would want the methodology to identify the observations in question. In that case there would several ways to deal with the issue, including modifying the model, but also sim- ply discarding the o§ending observations as part of "data cleaning". It is worth noting though that the answer isn't simple because notable scientific chievements have been obtained by looking carefully at observations that are clearly discrepant.
So there are some concerns that have relevance for me and that I think the paper needs to address. What method is used to identify that there is a problem with the model such that the inferences will be strongly affected and does it identify outlying observations? A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to chooseT: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isnít clear how to do this. I understand that there are
problems where reducing the data to some T (y) is necessary, perhaps because of computational problems associated with evaluating a likelihood, but this is clearly a compromised analysis and not one we would recommend unless forced to do so. So I don't agree with the statement made in the paper "that deliberate choice of an insufficient statistic T (y) guided by targeted inference is sound practice". There needs to be a much stronger argument for this at least for me.
The paper is well-written and thought-provoking so my hope is that a revision will be able to address the points raised.

\end{document}

### 2019-06-14 revision_2/response/response.tex
first pass at addressing comments

@@
 \newcommand{\magenta}[1]{{\color{magenta}#1}}
+\newcommand{\response}[1]{{\color{blue}#1}}
 \DeclareMathOperator*{\argmin}{\arg\!\min}
@@
 \item The authors propose a broad class of the proposal density, but didn’t discuss the choice and tuning within the class.
-Tuning the proposal is crucial to the mixing and efficiency of the MH algorithm, epecially in the high-dimension space, n ?
-p-dimensional, that the paper is dealing with.
+Tuning the proposal is crucial to the mixing and efficiency of the MH algorithm, epecially in the high-dimension space, $n-p$-dimensional, that the paper is dealing with.
 There are two difficulties in tuning within the proposed class.
-First, since the proposal density is a complicated transformation of p(z?) in Rn?p?1, even if p(z?) belongs to a standard parametric family, p(yp|?) does not and it is not straightforward to assess the properties that are usually used in tuning MCMC algorithm, e.g.
+First, since the proposal density is a complicated transformation of $p(z^{*})$ in $R^{n-p-1}$, even if $p(z^{*})$ belongs to a standard parametric family, $p(z^{*})$ does not and it is not straightforward to assess the properties that are usually used in tuning MCMC algorithm, e.g.
 mode and
@@
 Random walk is more able to explore a non-standard parameter space like the manifold here, while it seems tricky to design the independent proposal that well covers the probability mass of the target density, which again due to the transformation.
-\item The simulation studies didn’t report the choice of p(z?), acceptance rates of the MH, and mixing of the overall MCMC algorithm.
+
+\response{This is an astute observation - we have added the following text after Theorem 4.6:
+
+`This proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
+For all the examples in the paper we defined $p(z^{*})$ to simply be the uniform distribution on the $\mathbb{S}$.
+The advantage of this choice requires no further tuning parameters and we have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with reasonable probabilities.
+Additionally, with a long enough chain, the uniform start will cover the entirety of the plausible range of the transformation'
+
+As stated - we have not run into into the inefficiency issues here that you bring up.
+Additionally, note that a random walk on the manifold is not straightforward.
+It would be impossible to just move a single component of $z^{*}$ at a time since any single move would move the point off of the manifold.
+Hence, proposals would have to be in groups anyway, and random deviations of one component would affect the feasible moves of the other components.
+We do agree - that there could be cases where our choice is not optimal and more research would be need to explore this.
+}
+
+\item The simulation studies didn’t report the choice of $p(z^{*})$, acceptance rates of the MH, and mixing of the overall MCMC algorithm.
 Due to point 1, I think these issues would be of interest to readers.
+
+\response{Thanks. We report the choice of $p(z^{*})$ above and  we have added acceptance rates for the simulations.}
+
 \item The models studied in both the simulation and real data examples are just simple linear regression which is not realistic.
 Multiple linear regression with at least three independent variables should be studied.
-\item What are the benefits of the proposed method over the classical robust point estimators, like Huber or Tukey estimators compared in the examples, to offset the additional compu- tational cost and tuning efforts?
+
+\response{For the real data, we have included two additional covariates related to the number of employees at each agency.
+These were left out originally after some EDA revealed their effect sizes were small, but leaving them in is a good study as well.
+We have kept the first simulation as we feel it is a good and simple illustration of the ability to fit hierarchical models with our method.
+The real data examples now contains a hierarchical example with more covariates.
+Additionally, we have included a second simulation where the fitting model is a linear regression with 20 covariates and only 3 of them are active.}
+
+\item What are the benefits of the proposed method over the classical robust point estimators, like Huber or Tukey estimators compared in the examples, to offset the additional computational cost and tuning efforts?
 From the simulation studies, whether it has improvement or not depends on the prior distribution, which seems to be from comparing Bayesian and Frequentist methods.
-Actually, literatures on the asymptotic properties of f(?|T(yobs)) shows that, if T (yobs) is asymptotically unbiased, T (yobs) and E(?
-| T (yobs)) have the same asymptotic variance.
+Actually, literatures on the asymptotic properties of $f(\theta|T(yobs))$ shows that, if $T(yobs)$ is asymptotically unbiased, $T (yobs)$ and $E(\theta | T (yobs))$ have the same asymptotic variance.
 Hence if the prior doesn’t matter, both methods have similar performance.
-\item I think f(?|T(yobs)) might perform better in the following scenario: when T(yobs) is asymp- totically biased, E(?|T(yobs)) can still be asymptotically unbiased as long as the true pa- rameter is identifiable conditioning on the summary statistic, i.e the value of E(T(yobs)) is unique on the true parameter.
+
+\response{We fill the main benefits are in situations where the analysis involves substantial prior information.
+We agree that the additional computational burden is not worth it in situations where the amount of data overwhelms the prior, for exactly the reasons you state.
+We have added the following to the introduction of the paper:
+
+`The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
+The main advantages we have found so far come in situations we outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
+This is because, as with many traditional posteriors, the restricted likelihood posterior tends to the classical estimates as sample size grows.
+The main disadvantage over traditional robust estimate techniques are mainly computational.
+In Section 4 we detail a data-augmented MCMC algorithm to fit the models proposed in this paper.
+This requires an additional computational step for each iteration of the chain.
+Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden'
+
+We have also included in the discussion:
+
+`We have found the additional computational burden to be beneficial in situation where  substantial prior information that will impact the results is available.'
+
+}
+
+\item I think $f(\theta|T(yobs))$ might perform better in the following scenario: when $T(yobs)$ is asymptotically biased, $E(\theta|T(yobs))$ can still be asymptotically unbiased as long as the true pa- rameter is identifiable conditioning on the summary statistic, i.e the value of $E(T(yobs))$ is unique on the true parameter.
 One possible example is the robust ridge-regression estimator, but it needs further investigation whether this estimator satisfies C1-C8.
-\item In page 14, should C?(X) n ? p-dimensional instead of n ? p ? 1-dimensional?
+
+\response{Thank you for this is an interesting idea that we have not thought about before.
+We point out here, that  the example you gave does not satisfy all of C1-C8.
+For example, C5 is not satisfied with ridge regression $\hat\beta = (X'X +\lambda I)^{-1} X'y$ so that  $(X'X +\lambda I)^{-1} X'(y + Xv) \neq (X'X +\lambda I)^{-1} X'y + v$.
+Thus, new computational capabilities would have to be developed to explore this idea in substantial examples and we feel that would be worthy of another paper in the future.
+
+Bayesian priors offer a level of shrinkage like many of the bias estimators that would come to mind.
+So we are unsure how the effect of shrinking using both the prior and the conditional statistics would manifest itself.
+Again - a reason for further research.
+We have included some of this commentary in the discussion.
+
+}
+
+\item In page 14, should $C^\perp(X)$ n - p-dimensional instead of n - p - 1-dimensional?
+\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional, but we don't see where we mentioned otherwise on page 14.
+$\mathcal{A}$ is $n-p-1$ dimensional as one degree of freedom is lost for each coefficient estimate and the scale estimate.}
+
 \end{enumerate}
@@
 For the insurance example analyzed in Sec 6, the authors should provide ev- idence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.
+
+\response{
+We did not intend to mislead that we only want to predict the good portion of the data.
+Identification of outliers is also of concern and robust methods are well known to help identify outliers.
+As our method offers robust estimation of the the 'good' part of the model, it can also be used to identify outliers by, for example, examining residuals.
+In this sense, we feel we have provided several examples (in Section 2 under 'Examples' as well as through the simulations and the real data analysis).
+
+Several changes to address your valid concerns include:
+
+In the introduction:
+`In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study.
+\textit{By this definition, outliers are spurious however, identifying them so that better inference of the phenomenon under study is of importance}'.
+
+For the real data example: 
+The goal for the insurance example was derived from personal collaborations and we do not know of specific literature. However we have provided more detail of the goal.
+
+\response{It is of concern to the company to predict closures and future performance for agencies that remain open.
+It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies.
+Additionally, robust methods are more likely to identify such agencies.
+Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.}
+}
+
 \item As a methodological paper, what’s the guideline/recommendation given by the authors? After reading this paper, I don’t know how to apply the suggested framework
@@
 Is there any- way to select which f or T to use based on cross-validation or other empirical methods?
+
+\response{This is valid input. We have taken the following steps:
+
+\begin{enumerate}
+\item Point out that M-Estimators have been our default choice in the very first illustrative example:
+ \response{Details of these estimators can be found in many places, including \citep{huber2009}.
+We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers.
+For this reason we offer a quick review of these estimators in the Supplementary Material.}
+ \item Included a review of M-Estimators in the Supplement
+ \item Included a `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
+\end{enumerate}
+}
+
 \item What’s the real benefit of this computationally expensive approximation framework? The proposed framework replies on a good summary statistic T(yobs), which
@@
 What’s the gain of all the extra computation?
-The authors compare KL diver- gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y?|M,yobs) is not available in closed-form; 2) since f(y?|M,yobs) is not available close-form, the KL divergence is approximated and it’s not clear to me how accurate the approximation is.
+
+\response{At the end of section 4 we have included a paragraph:
+
+`
+Finally, we mention that in addition to the additional computation already mentioned, it is clear that the estimators themselves have must be computed for every iteration of the Markov Chain.
+We have found this burden to be marginal in with respect to computing the needed Jacobian.
+In the simulations and real data analyses presented below, we will see that the additional burden is of added value in situations where substantial prior information is available that is not swamped by current data.
+`
+Additionally we have included a paragraph in the introduction discussing advantages and disadvantges in response to a similar comment from the other reviewer.
+}
+
+\item The authors compare KL diver- gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y|M,yobs) is not available in closed-form; 2) since f(y|M,yobs) is not available close-form, the KL divergence is approximated and it’s not clear to me how accurate the approximation is.
 The authors should compare prediction and estimation accuracy, common met- rics used for regression models.
-The simulation setup is too simple. Suggest to add some linear regression models with large p and/or large n.
+
+\response{We have changed to the metric to address the estimation concern you bring up. The metric is $ 
+\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{2\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2}
+$
+which combines estimation error for both the $\theta_{i}$ and $\sigma$.
+For this simulation, estimation of $\theta_{i}$ is analogous to prediction.
+While we couldn't compute this metric in a real analysis since we wouldn't know the $\theta_{i}$ and $\sigma$, we feel it is best to make this direct comparison since we know them in the simulation.}
+
+\item The simulation setup is too simple. Suggest to add some linear regression models with large p and/or large n.
+
+\response{We feel the first hierarchical simulation example is a good introduction to how the method is conducted in a hierarchical setting.
+However, we have added 2 additional regression covariates to the real data analysis which also contains a hierarchical example.
+We have also included an additional simulation studying variable selection where only a few variables are active out of many  and hope this satisfies your suggestion.}
+
 \end{enumerate}
@@
 \item  Sec 2 and Sec 3 can be shortened or merged.
+\response{We have merged the sections and moved one of the illustrative examples to the Supplement}
+
 \item  Eq(2) in Sec 2.1, the notation f(yi|?,c(yi)) is not introduced yet; what’s introduced is f(y|?).
+\response{We have included a sentence for this notation after it's first use. }
 
@@
 Instead of saying “Many estimators satisfy the above properties”, the authors should list those estimators and explain why those conditions are satisfied.
+
+\response{We have added:
+
+`
+\response{These M-estimators satisfy C3 and C4 since they are optimizers of (almost surely) continuous and differentiable objective functions.
+Constraints C5-C8 are often satisfied by location and scale estimators but should be checked on a case by case basis.}
+`
+}
+
 \item  Bottom of p14, ”Sample z?
@@
 used in the simulation studies and real data analysis?
-\item  Eq (18): change dy to dy?
+
+\response{Thanks for noticing this detail.
+It should have full support on S since the transformation is 1-1 and onto A.
+We have now mentioned this.
+We have also included in discussion of what we used for p throughout based on a previous comment.
+This comment is after Theorem 4.6.}
+
+\item  Eq (18): change dy to d$\tilde{y}$?
+\response{Thanks for noticing this typo - based on the another reviewers comment we are using a different metric then KL divergence and so this equation is no longer in the paper.}
+
 \end{enumerate}
@@
 Please revise the scope of the paper as appropriate or provide more examples to ensure outliers and model misspecification are parallel contributions rather than one nested in another.
+
+\response{WILL TONE DONE THE MODEL MISSSPECIFICATION STUFF}
+
 There are many implementation details that an interested user would like to learn more but feel difficult to find from the current paper.
@@
 See the two referee reports for more details.
+
+\response{Thank you - we believe we have address each of these concerns based on the the 2 reviewer's comments. Detailed responses are given above}
+
 The authors are also suggested to possibly provide code that is available online with recommended choices as default.
+
+\response{We have included default choices in the paper and in the Supplement.
+We have included information for where to obtain code on Github (an R package as well as data and code for the examples) at the end of the Introduction}
+
 It is unclear how the proposed method outperforms existing work, either conceptually or practically.
+
+\response{we believe we have addressed similar concerns from the two reviewers - specifically we have included in several areas the advantages and disadvantages (e.g., see Introduction) we have found as well as practical recommendations (e.g.
+See Supplement)
+
 Referees have provided some competing methods for the authors to consider.
@@
 What is the advantage of the proposed restrictive likelihood approach over Bayesian fractional inference, even conceptually?
+
+\response{MUST ADDRESS STILL}
+
 Overall, the paper deserves publication after careful and thorough revision. I hope the authors can address all concerns raised in this report and the two well-grounded referee reports.
@@
 
-Report on ìBayesian restricted likelihoods: conditioning on in su¢ cient statistics in Bayesian regressionî
 The paper has received a mixed reaction from the two referees and the AE.
 I have a similar reaction to the paper but agree with the other readers that the content is such that an opportunity to address the issues raised is appropriate.
-The AEís comments place the paper on the border between Reject with Resubmission and Major Revision.
-I mention this because it isnít clear that a revision will be successful as there are some significant criticisms in the reviews.
+The AE's comments place the paper on the border between Reject with Resubmission and Major Revision.
+I mention this because it isn't clear that a revision will be successful as there are some significant criticisms in the reviews.
+
 My concerns might be a little different than the others and perhaps are less technical in nature.
@@
 For example, for the problem being considered in this paper, I would want a model checking procedure that indicated that there is a serious problem because, no matter what distribution was used from the model, some observations are outlying and I would want the methodology to identify the observations in question.
-In that case there would several ways to deal with the issue, including modifying the model, but also sim- ply discarding the o§ending observations as part of "data cleaning".
-It is worth noting though that the answer isn't simple because notable scientific chievements have been obtained by looking carefully at observations that are clearly discrepant.
+In that case there would several ways to deal with the issue, including modifying the model, but also simply discarding the offending observations as part of "data cleaning".
+It is worth noting though that the answer isn't simple because notable scientific achievements have been obtained by looking carefully at observations that are clearly discrepant.
+
 So there are some concerns that have relevance for me and that I think the paper needs to address.
 What method is used to identify that there is a problem with the model such that the inferences will be strongly affected and does it identify outlying observations?
-A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to chooseT: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isnít clear how to do this.
+
+A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to choose T: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isn't clear how to do this.
 I understand that there are
-problems where reducing the data to some T (y) is necessary, perhaps because of computational problems associated with evaluating a likelihood, but this is clearly a compromised analysis and not one we would recommend unless forced to do so.
-So I don't agree with the statement made in the paper "that deliberate choice of an insufficient statistic T (y) guided by targeted inference is sound practice".
+problems where reducing the data to some T(y) is necessary, perhaps because of computational problems associated with evaluating a likelihood, but this is clearly a compromised analysis and not one we would recommend unless forced to do so.
+So I don't agree with the statement made in the paper "that deliberate choice of an insufficient statistic T(y) guided by targeted inference is sound practice".
 There needs to be a much stronger argument for this at least for me.
+
 The paper is well-written and thought-provoking so my hope is that a revision will be able to address the points raised.

### 2019-06-14 revision_2/paper.tex
first pass at addressing comments

--- 2018-11-09 revision_1/paper.tex
@@
 \begin{aug}
-\author{\fnms{John R.} \snm{Lewis}\thanksref{addr1,m1}\ead[label=e1]{lewis.865@osu.edu}}, 
+\author{\fnms{John R.} \snm{Lewis}\thanksref{addr1,m1}\ead[label=e1]{lewis.865@buckeyemail.osu.edu}}, 
 \author{\fnms{Steven N.} \snm{MacEachern}\thanksref{addr1,m1}\ead[label=e2]{snm@stat.osu.edu}}, 
@@
 In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study.
+\response{By this definition, outliers are spurious however, identifying them so that better inference of the phenomenon under study is of importance}.
 There are three main solutions to Bayesian outlier-handling.
@@
 The second approach replaces the
-basic sampling density with a thick-tailed density in an attempt to discount outliers, yielding techniques that 
-often provide solid estimates of the center of the distribution but do not easily translate to predictive densities for further good data.
+basic sampling density with a thick-tailed density in an attempt to discount outliers, yielding techniques that often provide solid estimates of the center of the distribution but do not easily translate to predictive densities for further good data.
 The third approach fits a flexible (typically nonparametric) model to  the data, producing a Bayesian version of a density estimate for both good and bad data.
@@
 We call this likelihood a restricted likelihood because conditioning is done on a restricted set of data; the set which satisfies the observed summary statistics.
-This is a formal update of the prior distribution based on the sampling density of the summary statistics.
-%The spirit of the approach  %The novelty of the work is twofold.
-We make use of classical robust estimators as  summary statistics in a formal Bayesian framework, using the sampling density of the estimators as a replacement for the  sampling density of the data.
-Second, we advance the argument that conditioning on an insufficient summary of the data is sound practice, rather than merely being done for computational and modelling convenience.
-
-% \red{[Steve, just a reminder that a paragraph about model misspecification was here orginally but commented out by John following a referee's suggestion.
-I also agree with the referee in that model misspecification could be a much broader issue than having a fraction of bad data while the model for good data is correctly specified.]}
-%In addition to outlier-prone data, the 
-%\green{ The sampling density can err due to other forms of model misspecification.  
-%The traditional view is that, if the model is inadequate, one should build a better model.  In our
-%empirical work, as data sets have become larger and more complex, we have bumped into 
-%settings where we cannot realistically build the perfect model.  We ask the question ``by attempting
-%to improve our model through elaboration, will the overall performance of the model suffer?''  If yes,
-%we avoid the elaboration, retaining a model with some level of misspecification.  Acknowledging that
-%the model is misspecified implies acknowledging that the sampling density is incorrect, as
-%we do when outliers are present.  Thus, outliers are but one form of misspecified model.  
-%We recommend a common solution for dealing with outliers and more general forms of model misspecification.}
-
-The remainder of the paper is as follows: Section~\ref{restrictedlikelihood} introduces the Bayesian restricted likelihood and provides context with previous work, Section~\ref{illustrations} demonstrates some advantages of the methods on simple examples, and Section~\ref{BayesLinMod} details a MCMC algorithm to apply the method to Bayesian linear models.
-This is a major contribution to the work providing an approach to apply the method on realistic examples.
+This restricted likelihood leads to a formal update of the prior distribution based on the sampling density of the summary statistics.
+
+\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
+The main advantages we have found so far come in situations we outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
+This is because, as with many traditional posteriors, the restricted likelihood posterior tends to the classical estimates as sample size grows.
+The main disadvantage over traditional robust estimate techniques are mainly computational.
+In Section ~\ref{BayesLinMod} we detail a data-augmented MCMC algorithm to fit the models proposed in this paper.
+This requires an additional computational step for each iteration of the chain.
+Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden}
+
+The remainder of the paper is as follows: Section~\ref{restrictedlikelihood} introduces the Bayesian restricted likelihood, provides context with previous work, and demonstrates some advantages of the methods on simple examples.
+Section~\ref{BayesLinMod} details an MCMC algorithm to apply the method to Bayesian linear models.
+This computational strategy is a major contribution to the work, providing an approach to apply the method on realistic examples.
 Many of the the technical proofs are in the Appendix \ref{sec:appendix} with \texttt{R} code available from the authors.
-Section \ref{RealData} illustrates the method on a messy insurance industry data set containing many outliers with a novel twist on model evaluation.
+Sections \ref{simData} and \ref{RealData} illustrate the method with simulated data and a real insurance industry data set containing many outliers with a novel twist on model evaluation.
 A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method.
+\response{ An R package \texttt{brlm} is to implement our methods in available at \texttt{github.com/jrlewi/brlm}.
+Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/revision\char`_2}.}
 
@@
 L(\bth | \by)  
-= \left( \prod_{i=1}^{n-k} f(y_i | \bth) \right) \left( \prod_{i=n-k+1}^{n} f(y_i | \bth) \right) .  
+= \left( \prod_{i=1}^{n-k} f(y_i | \bth) \right) \left( \prod_{i=n-k+1}^{n} f(y_i | \bth) \right), 
 \end{eqnarray}
@@
 \end{eqnarray}
-Only the first part is retained the analysis. Several more examples are detailed in \cite{lewis2014}.
+
+$\prod_{i=1}^n f(y_i|\bth,c(y_i))$ is the likelihood of the data conditioned on parameters and the summary statistic $c(\cdot)$ and recovers the piece of the full likelihood not in $ \prod_{i=1}^n g(c(y_i)  | \bth)$.
+Only the first part is retained in the analysis.
+Several more examples are detailed in \cite{lewis2014}.
 
@@
 Interest typically lies in the full data posterior and ABC is used for computational convenience as an approximation.
-Consequently, effort is made to choose an approximately sufficient $T(\by)$ and update to the ABC posterior by using the likelihood $L(\bth| \mathcal{B}(\by))$, where $\mathcal{B}(\by)=\{\by^{*}|\rho(T(\by),T(\by^{*}))<\epsilon\}$, $\rho$ is a metric, and $\epsilon$ is a tolerance level.
+Consequently, effort is made to choose an approximately sufficient $T(\by)$ and update to the ABC posterior by using the likelihood $L(\bth| \mathcal{B}(\by))$, where $\mathcal{B}(\by)=\{\by^{*}|\rho(T(\by),T(\by^{*})) \leq \epsilon\}$, $\rho$ is a metric, and $\epsilon$ is a tolerance level.
 This is the likelihood conditioned on the collection of data sets that result in a $T(\cdot)$ within $\epsilon$ of the observed $T(\by)$.
@@
 
-This work extends the development of Bayesian restricted likelihood by arguing that deliberate choice of $T(\by)$ on which to guide inference is sound practice.
-We also expand the class of conditioning statistics in which a formal Bayesian update can be achieved.
+This work extends the development of Bayesian restricted likelihood by arguing that deliberate choice of an insufficient statistic $T(\by)$ guided by targeted inference is sound practice.
+We also expand the class of conditioning statistics for which a formal Bayesian update can be achieved.
 Our methods do not rely on asymptotic properties, nor do they rely on approximate conditioning.%, \green{nor do they need to correspond to artificial censoring to create incomplete or missing data}  \citep[e.g.,][]{albert1988, hoffwakefield2013}.
@@
 For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.
-\citep[for details see][]{huber2009}
-
-\section{Illustrative Examples}
+\citep[for details see][]{huber2009
+
+\subsection{An Illustrative Example}
 \label{illustrations}
 Before discussing computational details, the method is applied to two simple examples on well known data sets to demonstrate its effectiveness in situations where outliers are a major concern.
+The first example is presented here, with the second provided in the Supplementary Material.
 The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}.
@@
 
-The first example is an analysis of Simon Necomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
+The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
 The full model is a standard location-scale Bayesian model also used in \cite{lee2014}:
@@
 \end{equation}
-where $y_{i}$ denotes the $i^{th}$ (recoded) measurement of the passage time of light.
-$\beta$ is interpreted as the passage time of light with the deviations $y_i - \beta_i$ representing measurement error.
+where $y_{i}$ denotes the $i^{th}$ (recorded) measurement of the passage time of light.
+$\beta$ is interpreted as the passage time of light with the deviations $y_i - \beta$ representing measurement error.
 Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)  Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
-The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
-Two additional approaches to outlier handling are fit: 1) the normal distribution is replaced with a t-distribution and, 2) the normal distribution is replaced with a mixture of two normals.
+\response{Details of these estimators can be found in many places, including \citep{huber2009}.
+We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers.
+For this reason we offer a quick review of these estimators in the Supplementary Material.}  The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+Two additional approaches to outlier handling are considered: 1) the normal distribution is replaced with a t-distribution and, 2) the normal distribution is replaced with a mixture of two normals.
 The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$.
-The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ ensures that the prior on the variance is the same as the other models.
+The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ and ensures that the prior on the variance is the same as the other models.
 The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ with the prior $p \sim \text{beta}(20,1)$ on the probability of belonging to the `good' component.
@@
 These posteriors are also quite diffuse.
-In contrast, the t model and the other restricted likelihood methods discount the outliers and have posterior centered at higher values.
+In contrast, the t-model, mixture model, and the other restricted likelihood methods discount the outliers and have posteriors centered at higher values.
 There is modest variation among these centers.
@@
 
-The pattern for predictive distributions differs (see bottom plot in Figure \ref{fig:newcomb__post}).
-The normal and t models have widely dispersed predictive distributions.
+The pattern for predictive distributions differs (see bottom plot in Figure \ref{fig:newcomb_post}).
+The normal and t-models have widely dispersed predictive distributions.
 The other predictive distributions show much greater concentration.
 The restricted likelihood fits based on M-estimators (Tukey's and Huber's) are centered appropriately and are concentrated.
+The restricted likelihood based on LTS and the mixture model results are also centered appropriately, but comparatively less concentrated.
 The LMS predictive is concentrated, but it is poorly centered.
@@
 They provide sharp and appropriate inference for parameters ($\beta$) and for prediction.
-
-%\begin{figure}[t]
-%\centering
-%{\includegraphics[width = 4in]{figs/speed_of_light_predictive.png}}
-%\caption{dfsfsa}
-%\label{fig:newcomb_predictive}
-%\end{figure}
-%\caption{Top: Posteriors of the location parameter $\beta$ under the normal theory model, the t-model, and four restricted likelihood models for Newcomb's speed of light measurements.
-Bottom: Posterior predictive distribution of the speed of light under the normal theory model, the t-model, and four restricted likelihood models.}
-%\label{fig:newcomb_post}
-%\end{figure}
-
-As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
-The outliers in this case are due to a change in measurement units on which calls were recorded for part of the data set.
-Specifically, for years 1964-1969 and parts of 1963 and 1970, the length of calls in minutes were recorded rather than the total number \citep{rousseeuw1987}.
-The full model is a standard normal Bayesian linear regression:
-\begin{equation}
-{\boldsymbol{\beta}}\sim N_{2}(\boldsymbol{\mu}_{0}, \boldsymbol{\Sigma}_{0}),\  \sigma^{2} \sim IG(a, b), \by \sim N(X\boldsymbol{\beta}, \sigma^{2} I),
-\end{equation}
-where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and X is the $n\times 2$ design matrix with a vector of 1's in the first column in the year covariate in the second.
-Prior parameters are fixed via a fit to the first 3 data points.
-In particular, the prior covariance for $\beta$ is set to $\Sigma_{0} = g\sigma_{0}^2 (X_{p}^{\top}X_{p})^{-1}$, with $X_{p}$ the $3\times 2$ design matrix for the first $3$ data points, $g=n=21$, and $\sigma_{0} = 0.03$ and $\mu_{0} = (1.87,  0.03)^{\top}$; the MLEs fit to the first three data points.
-This has the spirit of a unit information prior \citep{kass1995reference} but uses a design matrix for prior data not used in the fit.
-Finally $a = 2$ and $b =1$.
-
-Four models are compared: 1) the normal theory base model 2) A two component normal mixture model, 3) a t-model, and 4) a restricted likelihood model conditioning on Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
-Each model is fit to the remaining 21 data points.
-The normal theory model is also fit a second time after removing observations 14-21 (years 1963 - 1970).
-This includes the obvious large outliers as well as the two smaller outliers at the beginning and end of this sequence of points caused by the change in measurement units.
-The mixture model assumes different mean regression functions and variances for each component, but keeps the same, relatively non-informative priors.
-The probability of belonging to the first component is given a $\text{beta}(5,1)$ prior.
-The heavy-tailed model fixes the degrees of freedom to 5 with the same adjustment to the prior on $\sigma^{2}$ as above.
-
-The data and  $95\%$ credible bands of the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}.
-The normal model fit to all cases results in a very wide posterior predictive distribution due to an inflated estimate of the variance.
-Since the t-model assumes the data are heavy-tailed, the posterior predictive distribution is also wide.
-Additionally, both of these are biased upward by the outliers in the upper tail of the assumed data distribution.
-On the other hand, the predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit to the non-outlying cases.
-It is also close to the two component mixture results where the predictive distribution is formulated using only the good component.
-The mixture model involves explicitly modeling the outlier generating mechanism.
-In more complex situations where the outlier generating mechanism is transient (i.e.
-ever changing and more complex than just a unit error in the recording), modeling the outliers becomes more difficult.
-As in classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
-\begin{figure}[t]
-\centering
-{\includegraphics[width = 4in]{figs/calls_predictive.png}}
-\caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
-The first three data points were used to specify the prior with each model using the remaining 21 for fitting.
-The normal theory model was also fit after removing observations 14-20 (years 1963 - 1970).}
-\label{fig:calls_predictive}
-\end{figure}
-%{\bf For the figure, add fit of normal model to all cases}
-
-%
-% and the development
-%of computational strategies that allow us to truly condition on the observed $T(\by)$ and 
-%fit the model in formal Bayesian fashion.  In this work, we focus
-%on robustness, and natural choices of $T(\by)$ for the one-sample problem include a set of middling order statistics, a trimmed
-%mean, or a classical robust estimator of location and/or scale.  
-%We have previously implemented several of these methods and have found them to perform well \citep[][]{lewis2012}.
-Versions most extensible to the linear model include the M-estimators in the tradition of \cite{huber1964}, least median squares (LMS), and least trimmed squares (LTS).
-For these choices the restricted likelihood is not available in closed form, making computation of the restricted posterior a challenge.
-For low-dimensional statistics $T(\by)$ and parameters $\bth$, the direct computational strategies described in \cite{lewis2014} can be used to estimate the incomplete posterior conditioned on essentially any statistic.
-These strategies rely on generation of complete data sets from different values of $\bth$.
-%Each complete data set leads to a statistic $T(\by)$ under $\bth$, and these generated statistics are used to estimate the density at $T(\by_{obs})$, where $\by_{obs}$ is the observed complete data.
-This estimate is fed into Bayes' theorem for the update from prior distribution to posterior distribution.
-%
-
-%\subsection{A first data analysis example} %\textcolor{blue}{ADDED}
-%\label{darwinAnalysis}
-%Before discussing computational details of finding restricted 
-%posteriors, we begin by analyzing a simple example involving
-%outliers. The data consists of well known measurements of the \green{passage time} of
-%light taken by Simon Newcomb in the late nineteenth century and
-%contain two clear outliers on the low end. Details and data are
-%available in the R package {\tt MASS} and previous analyses appear in
-%\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}. Letting
-%$y_{i}$ denote the $i^{th}$ coded measurement of the passage time of light, we
-%assume $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$. The
-%parameter $\beta$ can be interpreted as the passage time of light with
-%$\sigma^{2}$ representing measurement error. The outliers \green{are a clear indication} %make clear
-%that this normal model is misspecified.  \green{Also,} %Another reason for model misspecification is that 
-%the measurements are coarse, taking on only
-%integer values.  For a Bayesian analysis, we must specify prior
-%distributions on the parameters $\bth=(\beta, \sigma)$. For this we
-%assume an independent normal -- inverse gamma model. That is,
-%$\beta\sim N(\eta, \tau^{2})$ and $\sigma^{2}\sim IG(a, b)$. The
-%hyperparameters  are fixed for simplicity and taken to be $\eta=23.6$,
-%$\tau=2.04$, $a=5$,  and $b=10$. We note that our computational
-%strategy described in Section \ref{highDim} makes it feasible to fit
-%more complex model structures. The Bayesian model presented here is a
-%special case of the linear model in \eqref{LinearModel} presented below.
-%
-%As summary statistics for the restricted likelihood methods, we
-%consider robust simultaneous M-estimators of location and scale as
-%well as LMS (least median squares) and LTS (least trimmed squares) estimators.
-The simultaneous M-estimators $b(\by)$ and $s(\by)$ of $\beta$ and $\sigma$, respectively, are the solutions to the equations
-%\begin{eqnarray}
-%\label{Mest}
-% \sum_{i=1}^n \psi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 \\
-% \sum_{i=1}^n \chi\left(\frac{y_i - b(\by)}{s(\by)}\right)= & 0 . \nonumber 
-%\end{eqnarray} 
-%For the first equation we consider two $\psi$ functions: Huber's and Tukey's.
-These are both coupled with Huber's `proposal 2'  for the $\chi$ function in the second equation \citep[for details see][]{huber2009}.
-Tuning parameters for these functions are set to achieve $95\%$ efficiency under normally distributed data.
-%
-%LMS minimizes the median squared residual and LTS minimizes the sum of the $k$ smallest squared residuals where $k$ is chosen by the user.
-These estimators are considered because, unlike the M-estimators above, they can achieve high breakdown.
-%%These estimators are easily implemented by the {\tt rlm} function of the {\tt MASS} package in R. 
-%It is well known that LMS has highest possible breakdown but is inefficient.
-LTS is more efficient and its breakdown properties are determined by $k$, with highest possible breakdown occurring for $\left \lfloor{\frac{n+1}{2}}\right \rfloor\leq k\leq\left \lfloor{\frac{n+2}{2}}\right \rfloor$.
-%For the current data set $n=66$ and we take $k=34$ to achieve highest possible breakdown.
-%For the current analysis we do not choose $k$ to achieve highest possible breakdown. Instead, with $n=66$ and we choose $k=62$ (roughly $95\%$ of $n$) to be \green{more} %somewhat
-%comparable to the tuning parameters chosen for the M-estimators.
-The LMS and LTS \green{estimators} are also coupled with an estimator of scale for the conditioning.
-We set the scale estimator to the minimum of the corresponding objective function, appropriately scaled for consistency.
-%we use the scale estimator corresponding to the respective objective function.
-These are the median squared residual for LMS and sum of the smallest squared residuals for LTS multiplied by an appropriate correction factor chosen for consistency.
-%Computation of these estimators are also implemented in the {\tt MASS} package by the function {\tt lqs}.
-%
-%For comparison to a traditional Bayesian outlier approach we also fit a heavy-tailed model by changing the data distribution from a normal to a Student's $t$ with $\nu=5$ degrees of freedom.
-We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.
-For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.
-%
-%The marginal posteriors for $\beta$ and $\sigma^{2}$ as well as the
-%predictive distribution \eqref{RestrictedpredDist} under each model
-%are displayed in Figures
-%\ref{fig:newcombBeta}-\ref{fig:newcombPred}. Both of the two small
-%outliers and the normal prior on $\beta$ centered at $23.6$ are
-%influential in the results. The normal theory model is most
-%drastically affected with the posterior of $\beta$ being pulled
-%towards the prior and outliers. Inference on $\sigma^{2}$ under this
-%model is impacted by the outliers (see Figure
-%\ref{fig:newcombSig2}) \green{resulting in overestimation of $\sigma^{2}$}. 
-%The heavy-tailed model as well as the
-%restricted likelihood methods with LTS, Huber's, and Tukey's summary
-%statistics are less influenced by the outliers and priors. The
-%marginal posteriors for $\beta$ are closer to the center of the
-%non-outlying data. Inference on the variance parameter also more
-%closely reflects the variance information in this part of the data
-%(the mean and variance of the data without the two outliers are $27.8$
-%and $25.8$, respectively). The posterior of $\beta$ under LTS is
-%slightly more dispersed than under the two M-estimator methods. This is
-%also reflected in the variance parameter in that under LTS the posterior distribution \green{concentrates on 
-%slightly larger values of $\sigma^2$} % is slightly higher. 
-%While LMS has high breakdown, it has been more drastically affected by the normal prior centered at $23.6$ than the others. This is % likely 
-%because LMS achieves high breakdown by discounting much of the information in the data. 
-%
-%Though inference for the main parameter of interest ($\beta$) is
-%similar between the traditional heavy-tailed approach and the new
-%method with LTS, Huber's, and Tukey's summary statistics,  the
-%traditional heavy-tailed method has the disadvantage of less precise
-%predictive capability. This is reflected in the heavier tails of its
-%predictive distribution  \eqref{RestrictedpredDist} seen in Figure
-%\ref{fig:newcombPred} (plotted are the log predictive \green{densities} %distributions
-%under each method). The predictive distributions under each of the
-%restricted likelihood methods are comparable. Surprisingly, despite the poor
-%inference on $\beta$ under LMS, the predictive distribution is
-%\green{concentrated more sharply} than \green{under} the other restricted likelihood methods. This is
-%related to its posterior of $\sigma^{2}$ seen in
-%Figure \ref{fig:newcombSig2}  which is the tightest
-%distribution and shifted the most to the left. 
-%% However, this is likely a consequence of the scale estimator chosen for the conditioning.
-Recall it involves a correction factor which is chosen asymptotically.
-Even for $n=66$, this correction factor can contribute to underestimation (\textcolor{blue}{REFERENCE: I know I read something like this somewhere}).
-\red{[I don't know what exactly this correction factor is.
-Is it similar to the bending constant for $\psi$?]}
-%
-%%\red{[I suggest to omit the following paragraphs given that the second last paragraph in the previous section (``the key to the productive ...'') has similar discussions already.]} This simple example raises many questions regarding the proposed method.
-The first of which is how to choose the summary statistic.
-In principle, we may choose any summary and it doesn't have to be an estimator of location and scale.
-However, for outlier problems this choice seems logical and we use it for this paper.
-Further, estimator specific tuning parameters clearly effect the results.
-For example, we also looked at LTS with $k=34$ to achieve high breakdown.
-This resulted in a posterior for $\beta$ which closely resembled that of LMS.
-%
-%%Other questions may be posed by the reader and addressing each of these is beyond the scope of this paper.
-Instead we focus on introducing the method and deriving a computational strategy that will allow such models to be fit to higher dimensional problems with a large class of summary statistics.
-It is our hope that this computational strategy will facilitate the study of further questions regarding the method.
-%
-%\begin{sidewaysfigure}
-%\centering
-%\captionsetup{justification=centering}
-%\subcaptionbox{\label{fig:newcombBeta}}{\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}}\quad
-%\subcaptionbox{\label{fig:newcombSig2}}{\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}}\quad
-%\subcaptionbox{\label{fig:newcombPred}}{\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}}
-%\caption{Clockwise from top left: (a) marginal posteriors of $\beta$ (b) marginal posteriors for $\sigma^{2}$ (c) log predictive distributions.}
-%\label{fig:newcomb}
-%\end{sidewaysfigure}
-%
-%
-%%\begin{sidewaysfigure}
-%%\begin{subfigure}[b]{.5\linewidth}
-%%\captionsetup{justification=centering}
-%%\centering 
-%%\caption{}\label{fig:newcombBeta}
-%%\includegraphics[width=3.4in]{posteriorBetaNewcombDataParamSet2trim_2.pdf}
-%%\end{subfigure}
-%%\quad
-%%\begin{subfigure}[b]{.5\linewidth}
-%%\captionsetup{justification=centering}
-%%\centering
-%%\caption{}\label{fig:newcombSig2}
-%%\includegraphics[width=3.4in]{posteriorSigma2NewcombDataParamSet2trim_2.pdf}
-%%\end{subfigure}
-%%\quad
-%%\begin{subfigure}[b]{.5\linewidth}
-%%\captionsetup{justification=centering}
-%%\centering
-%%\caption{}\label{fig:newcombPred}
-%%\includegraphics[width=3.4in]{logpredDistParamset2nu5trim_2.pdf}
-%%\end{subfigure}
-%
-%%\caption{Clockwise from top left: (a) marginal posteriors of $\beta$. (b) marginal posteriors for $\sigma^{2}$. (c) log predictive distributions.}
-%%\label{fig:newcomb}
-%%\end{sidewaysfigure}
-%
-%
-%
-%%\textcolor{blue}{if we add the Newcomb and Belgium Calls data examples, this might be a good place to add them because they are low dimensional.
-I think it would be a good lead into the high dimensional computational strategies}
-%
-%
+A second example on well known data is provided in the Supplementary Material.
 
@@
 
-The simple examples in the previous section highlight that productive use of the restricted likelihood relies on a good choice of $T(\by)$.
+The simple examples in the previous section highlight the beneficial impact of a good choice of $T(\by)$ with the use of the restricted likelihood.
 This work focuses on robustness in linear models where natural choices include many used above:  M-estimators in the tradition of \cite{huber1964}, least median squares (LMS), and least trimmed squares (LTS).
 For these choices the restricted likelihood is not available in closed form, making computation of the restricted posterior a challenge.
-For low-dimensional statistics $T(\by)$ and parameters $\bth$, direct computational strategies described in \cite{lewis2014} can be used to estimate the restricted posterior conditioned on essentially any statistic.
-These strategies rely on density estimation $f(T(\by)|\theta)$ using samples of $T(\by)$ for many values of $\bth$; a strategy which breaks down in higher dimensions.
+For low-dimensional statistics $T(\by)$ and parameters $\bth$, the direct computational strategies described in \cite{lewis2014} can be used to estimate the restricted posterior conditioned on essentially any statistic.
+These strategies rely on estimation of the density of $f(T(\by)|\theta)$ using samples of $T(\by)$ for many values of $\bth$; a strategy which breaks down in higher dimensions.
 This section outlines a data augmented MCMC algorithm that can be applied to the Bayesian linear model when $T(\by)$ consists of estimates of the regression coefficients and scale parameter.
@@
 \textit{regression} and \textit{scale equivariance},
-respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} are called \textit{regression invariance}
+respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
 and \textit{scale equivariance}. 
-Many estimators satisfy the above properties, including simultaneous M-estimators \citep{huber2009, maronna2006} for which the R package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC described here.
-Further software development is required to extend the MCMC implementation beyond these M-estimators.
+Many estimators satisfy the above properties, including several traditional simultaneous M-estimators \citep{huber2009, maronna2006} for which the R package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC described here.
+\response{These M-estimators satisfy C3 and C4 since they are optimizers of (almost surely) continuous and differentiable objective functions.
+Constraints C5-C8 are often satisfied by location and scale estimators but should be checked on a case by case basis.}  Further software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
 The package also implements the direct computational methods described in \cite{lewis2014}.
-These methods are effective in lower dimensional problems and were used in several of the examples in Section \ref{illustrations}.
+These methods are effective in lower dimensional problems and were used in both examples in Section \ref{illustrations}.
 
@@
 In this case, the condition $T(\by) = T(\by_{obs})$ is redundant.
-This allows us to make use of conventional MCMC steps for this generation.
+This allows us to make use of conventional MCMC steps for generation of $\bth$ from the first full conditional.
 For typical regression models, algorithms abound.
@@
 \begin{eqnarray*}
-f(\by | \bth, \by \in \mathcal{A}) =  \frac{f(\by | \bth) I(\by \in \mathcal{A} | \by, \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} 
+f(\by | \bth, \by \in \mathcal{A}) =  \frac{f(\by | \bth) I(\by \in \mathcal{A})}{\int_\mathcal{A} f(\by | \bth) d\by} 
       = \frac{f(\by | \bth)}{\int_\mathcal{A} f(\by | \bth) d\by} 
 \end{eqnarray*}
-for $\by \in \mathcal{A}$.  This includes both $\by_p$ and $\by_c$.  The Metropolis-Hastings acceptance probability  is the minimum of 1 and $R$ where,
+for $\by \in \mathcal{A}$ and $I(\cdot)$ the indicator function.  This includes both $\by_p$ and $\by_c$.  The Metropolis-Hastings acceptance probability  is the minimum of 1 and $R$, where
 \begin{eqnarray}
@@
 For the models we consider, evaluation of $f(\by | \bth)$ is straightforward.
-Therefore, the difficulty in implementing this Metropolis-Hastings step manifests  itself in the ability to both simulate from and evaluate $p(\by_p | \bth)$; the well defined distribution with support $\mathcal{A}$.
+Therefore, the difficulty in implementing this Metropolis-Hastings step manifests  itself in the ability to both simulate from and evaluate $p(\by_p | \bth)$--the well defined distribution with support $\mathcal{A}$.
 We now discuss such an implementation method for the linear model in \eqref{LinearModel}.
@@
 Our computational strategy relies on proposing $\by$ such that $T(\by) = T(\by_{obs})$ where $T(\cdot) = (\bb(X, \cdot), s(X, \cdot))$ satisfies the conditions \ref{asb}-\ref{scaleEq2Reg}.
-It is not a simple matter to do this directly, but with the specified conditions, it is possible to scale and shift any $\bz^{*}$ which generates
-a positive scale estimate to such a $\by$ via the following Theorem, whose proof is in the appendix. 
+It is not a simple matter to do this directly, but with the specified conditions, it is possible to scale and shift any $\bz^{*} \in \mathbb{R}^{n}$ which generates
+a positive scale estimate to such a $\by$ via the following Theorem, whose proof is in the Supplementary Material. 
 \begin{theorem}
@@
 The mapping $h: \mathbb{S} \rightarrow \mathcal{A}$ is one-to-one and onto.
+A proof is provided by Theorem \ref{1to1onto} in the Supplementary Material.
 The one-to-one property makes the change of variables more feasible.
 The onto property is important so that the support of the proposal distribution (i.e.
-the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
-A formal theorem and proof is provided in the appendix.
-
+the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$, a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
 %With $\bz^{*}\in \mathbb{S}$, $c\bz^{*} + X\bv$ is not (unless $c=1$ and $\bv = \mathbf{0})$; the scaling by $c$ and/or the affine transformation in the direction of $\mathcal{C}(X)$ takes the point off $\mathbb{S}$.
 The mapping $h: \mathbb{S} \rightarrow \mathcal{A}$ is one-to-one making the change of variables more feasible.
-
 %With the domain of $h(\cdot)$ restricted to  $\mathbb{S}$, the range is still the entirety of $\mathcal{A}$.
@@
 \footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).} It is easy to show that $\bz^{*} = Q\by/||Q\by|| \in \mathbb{S}$ and $h(\bz^{*}) = \by$.
-
 Given the one-to-one and onto mapping $h: \mathbb{S} \rightarrow \mathcal{A}$, the general proposal strategy is summarized as follows:
 \begin{enumerate}
-\item Sample $\bz^*$ from a distribution with known density on $\mathbb{S}$.
+\item Sample $\bz^*$ from a distribution with known density \response{whose support is the entirety} $\mathbb{S}$.
 \item Set $\by = h(\bz^*)$ and calculate the Jacobian of this transformation in two steps.
@@
 \end{enumerate}
+
 The final proposal distribution including the complete Jacobian is given in equation \eqref{dens:ystst} with details in the next section.
-Before giving these details we provide a visualization  in Figure~\ref{fig:sampSpace} of each of the sets described above using a notional example to aid in the understanding of the strategy we are taking.
+Before giving these details we provide a visualization  in Figure~\ref{fig:sampSpace} of each of the sets described above using a notional example to aid in the understanding of the strategy we take.
 In the figure, $n = 3$, $p=1$, and the conditioning statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$.
@@
 vectors of the two sets at $\bz$.  The normal to the sphere is its radius vector $\bz$. The normal to
-$\Pi(\mathcal{A})$ is given in the following lemma.  
+$\Pi(\mathcal{A})$ is given in the following lemma with proof provided in the Appendix.  Gradients denoted by $\nabla$ are with respect to the data vector.
 \begin{lemma}
@@
 This step is visualized in Figure~\ref{fig:stretchDeform} for the notional
-location-scale example.  The figure pictures only the $\mathcal{C}^{\perp}(X)$,
+location-scale example.  The figure pictures only $\mathcal{C}^{\perp}(X)$,
 which in this case is a plane. The unit sphere (here, the
-solid circle) is stretched to the dashed sphere contributing
+solid circle) is stretched to the dashed sphere, contributing
 $r^{-(n-p-1)}$ to the Jacobian as seen in panel (a). In panel (b), the
-dashed circle is transformed onto $\Pi(\mc A)$ contributing
+dashed circle is transformed onto $\Pi(\mc A)$, contributing
 $\cos(\gamma)$ to the Jacobian. The normal vectors in panel (b) are
@@
 {\includegraphics[width=2.9in]{minSSZSpace5.pdf}}
-\label{fig:stretchDeform}
 \caption{Visualization of the scaling from $z^{*}$ to $z$.
-Left: the first substep scales $z^{*}$ on the unit circle to the circle of radius $r = ||z||$; resulting in a change-of-variables transformation for the unit circle to that of radius $r$.
+Left: the first substep scales $z^{*}$ on the unit circle to the circle of radius $r = ||z||$, resulting in a change-of-variables transformation for the unit circle to a circle of radius $r$.
 The contribution to the Jacobian of this transformation is $r^{-(n-p-1)}$.
 Right: The second substep accounts for the the change-of-variables transformation from the circle of radius $r$ to $\Pi(\mathcal{A})$.
-The normal vectors to these two sets are used to calculated the contribution to the Jacobian of this part of the transformation are shown in the figure.}
+The normal vectors to these two sets are used to calculate the contribution to the Jacobian of this part of the transformation are shown in the figure.}
+\label{fig:stretchDeform}
 \end{figure}
@@
 Computational details are
-given in the following lemmas and subsequent theorem. Throughout, let
+given in the following lemmas and subsequent theorem. Proofs of the lemmas are given in the appendix and the theorem is a direct result of the lemmas. Throughout, let
 $\mc T_{y}(\mc A)$ and $\mc T_{y}^{\perp}(\mc A)$ denote the tangent
-space to $\mc A$ at $\by$ and its orthogonal complement respectively. All gradients denote with $\nabla$ are with respect to the data vector.
+space to $\mc A$ at $\by$ and its orthogonal complement, respectively. %All gradients denoted by $\nabla$ are with respect to the data vector.
 \begin{lemma}
@@
 
+\response{This proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
+For all the examples in the paper we defined $p(z^{*})$ to simply be the uniform distribution on the $\mathbb{S}$.
+The advantage of this choice requires no further tuning parameters and we have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with reasonable probabilities.
+Additionally, with a long enough chain, the uniform start will cover the entirety of the plausible range of the transformation.}
+
 %In practice, computing $A$ directly to find $P$ and $\text{Vol} (P)$ is computationally intensive as it involves orthogonalization of $n$ vectors in $n$-dimensional space. 
-A few details for computingthe needed quantities are worth further explanation.
+Some details for computing the needed quantities are worth further explanation.
 Computing $\text{Vol} (P)$ involves finding an orthornormal matrix $A$ whose columns span $\mc T_{y}(\mc A)$.
-This matrix can be found by supplementing $B$ with a set of $n$ linearly independent columns on the right, and apply Gram-Schmidt orthonormalization.
-This is $\mc O(n^3)$ and is infeasibly slow when $n$ is large because it must be repeated at each iterate of the MCMC when a complete data set is drawn.
+This matrix can be found by supplementing $B$ with a set of $n$ linearly independent columns on the right, and applying Gram-Schmidt orthonormalization.
+The computational complexity of this step is $\mc O(n^3)$.
+This is infeasibly slow when $n$ is large because it must be repeated at each iterate of the MCMC when a complete data set is drawn.
 However, using results related to \textit{principal angles} found in \cite{miao1992} the volume \eqref{eq:volume} can be computed using only $B$.
-$B$ is constructed by Gram-Schmidt orthogonalization of $\nabla s(X,\by), \nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$, which is  $\mc O(np^2)$;  a
+$B$ is constructed by Gram-Schmidt orthogonalization of $\nabla s(X,\by), \nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$, reducing the computational complexity to $\mc O(np^2)$--a
 considerable reduction in computational burden when $n \gg p$. 
@@
 \end{corollary} 
-\noindent The lemma implies the $\text{Vol} (P)$ is the product of the singular values of $U^\top B$.
+\noindent The lemma implies that $\text{Vol} (P)$ is the product of the singular values of $U^\top B$.
 
@@
 where $\psi$ and $\chi$ are almost surely differentiable.
-Differentiating this system of equations with respect to each $y_{i}$ can be used to find the gradients.
-In theory, finite differences could also be used.
+The gradients can be found by differentiating this system of equations with respect to each $y_{i}$.
+In theory, finite differences could also be used as an approximation if needed.
+%{\bf John - for the finite differences, is this to approximate the gradient? }
+
+\response{Finally, we mention that in addition to the additional computation already mentioned, it is clear that the estimators themselves have must be computed for every iteration of the Markov Chain.
+We have found this burden to be marginal in with respect to computing the needed Jacobian.
+In the simulations and real data analyses presented below, we will see that the additional burden is of added value in situations where substantial prior information is available that is not swamped by current data.}
 
@@
 \label{simData}
-We study the performance of restricted likelihood methods in a hierarchical setting where the data are contaminated with outliers.
-Specifically, simulated data come from the following model:\begin{align}
+We study the performance of restricted likelihood methods in two simulation settings.
+The first is a hierarchical setting.
+The second is a variable selection setting where there are several potential covariates where only a few have non-zero effect sizes.
+
+\subsection{Simulation 1}
+The first is a hierarchical setting where the data are contaminated with outliers. Specifically, simulated data come from the following model:\begin{align}
 \label{gensim2}
@@
 \begin{split}
-& \mu \propto 1, \  \tau^{2} \propto \tau^{-2}, \\
+%& \mu \propto 1, \  \tau^{2} \propto \tau^{-2}, \\
 & \theta_{i}\sim N(\mu, \tau^{2}), \  \sigma^{2}_{i} \sim IG(a_{s}, b_{s}),  \ i = 1, 2, \dots, 90, \\ 
@@
 
-To complete the specification of model \eqref{fullsim2},  $a_{s}$ and $b_{s}$ are fixed to a variety of values representing different levels of prior knowledge.
-For each we set $b_{s} = 4a_{s}c$ resulting in a prior mean for each $\sigma^{2}_{i}$ of $\frac{4ca_{s}}{a_{s}-1}, \ a_{s} >1$.
-The precision is $\frac{(a_{s} -1)^{2}(a_{s}-2)}{(4ca_{s})^{2}}$; meaning larger $a_{s}$ and smaller $c$ result in a more informative prior.
+To complete the specification of model \eqref{fullsim2}, the hyperparameters $\mu, \tau^{2}, a_{s}$, and $b_{s}$ must be given priors or fixed.
+The joint prior density for $\mu$ and $\tau^{2}$ is improper and proportional to $\tau^{-2}$.
+The pair $a_{s}$ and $b_{s}$ are fixed to a variety of values representing different levels of prior knowledge.
+For each pair, we set $b_{s} = 4a_{s}c$ resulting in a prior mean for each $\sigma^{2}_{i}$ of $\frac{4ca_{s}}{a_{s}-1}, \ a_{s} >1$.
+The precision is $\frac{(a_{s} -1)^{2}(a_{s}-2)}{(4ca_{s})^{2}}$, meaning larger $a_{s}$ and smaller $c$ result in a more informative prior.
 With $c = 1$ the shrinkage (for large $a_{s}$) is to the true value of $\sigma^{2} = 4$.
-We consider $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$ for a total of nine different priors whose densities are displayed in Figure \ref{fig:priors}.
-The vertical dashed line is at the known true value of $\sigma^{2} = 4$.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width = 4in]{priors_sigma2.png}
-\label{fig:priors}
-\caption{The nine different inverse gamma priors used for the group level variance parameters $\sigma_{j}^{2}$ in the simulation.
+We consider $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$ for a total of nine different priors.
+
+%whose densities are displayed in Figure \ref{fig:priors}. The vertical dashed line is at the known true value of $\sigma^{2} = 4$.
+%
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width = 4in]{priors_sigma2.png}
+%\caption{The nine different inverse gamma priors used for the group level variance parameters $\sigma_{j}^{2}$ in the simulation.
 The shape parameter values are $a_{s} = 1.25, 5, 10$.
@@
 The vertical dashed line in each panel is at the true value of $\sigma^{2} = 4$ and is the variance of the good portion of the data in the simulation.}
-\end{figure}
+%\label{fig:priors}
+%\end{figure}
 
@@
 That is, there is a separate Gibbs step for each group to generate the group level data matching the statistics for that group.
-
-To assess predictive capability, the models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution.
+\response{The acceptance rates for newly generated data across all groups and simulations ranged from $0.57$ to $0.68$}
+
+\response{To asses the predictive capability, we seek a metric that takes into account both the estimation of $\theta_{i}$ and $\sigma^{2}$.
+In this model, estimation of $\theta_{i}$ and prediction are analogous.
+To this end we consider the expected value of  the log likelihood ratio between the true distribution of good data and a model estimate of this distribution
+\begin{equation}
+\label{sim1loss}
+E[\log f(y|\theta_{i}, \sigma^{2}) - \log f(y|\hat{\theta_{i}}, \hat{\sigma^{2}})] =
+\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{2\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2})
+\end{equation}
+The expectation is taken with respect to the true data distribution of the good data assuming fixed estimates.
+These estimates are the posterior means for the Bayesian methods and the standard point estimates for the classical methods.
+}
+
+%To assess predictive capability, the models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution.
 Specifically, for the $i^{th}$ group of the $k^{th}$ simulated data set $\by_{k}$ compute:
-\begin{equation}
-\label{kl}
-KL^{(M)}_{ik} = \int \log \frac{f(\tilde y | \theta_{i}, \sigma^{2})}{f_{i}(\tilde y | M, \by_{k})}  f(\tilde y | \theta_{i}, \sigma^{2}) \ dy
-\end{equation}
-where $M$ indexes the fitting model, $f(\tilde y | \theta_{i}, \sigma^{2}) = N(\tilde y | \theta_{i}, \sigma^{2})$; the normal density function with mean $\theta_{i}$ and variance $\sigma^{2}$, evaluated at $\tilde y$.
-For the Bayesian models ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})d\theta_{i}d\sigma^{2}_{i}$ where $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
+%\begin{equation}
+%\label{kl}
+%KL^{(M)}_{ik} = \int \log \frac{f(\tilde y | \theta_{i}, \sigma^{2})}{f_{i}(\tilde y | M, \by_{k})}  f(\tilde y | \theta_{i}, \sigma^{2}) \ dy
+%\end{equation}
+%where $M$ indexes the fitting model and $f(\tilde y | \theta_{i}, \sigma^{2}) = N(\tilde y | \theta_{i}, \sigma^{2})$, the normal density function with (known) mean $\theta_{i}$ and variance $\sigma^{2}$, evaluated at $\tilde y$.
+For the Bayesian models, ${f_{i}(\tilde y | M, \by_{k})} = \int f(\tilde y |\theta_{i}, \sigma_{i}^{2}) \pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})d\theta_{i}d\sigma^{2}_{i}$ where $\pi(\theta_{i}, \sigma^{2}_{i} | M, \by_{k})$ is the posterior for the $i^{th}$ group model parameters under model $M$ for the $k^{th}$ data set.
 $M$ denotes either the full normal theory model \eqref{fullsim2} or one of the two restricted likelihood versions, along with specified $a_{s}$ and $c$.
 For the classical robust fits, we set $f_{i}(\tilde y | M, \by_{k}) = N(\tilde y|\hat\theta_{i}, \hat\sigma^{2}_{i})$ as a groupwise plug-in estimator for the predictive distribution.
-The classical fits are done separately for each group with no consideration of the hierarchical structure between the groups.
+The classical fits are computed separately for each group with no consideration of the hierarchical structure between the groups.
 The overall mean $\overline{KL}^{(M)}_{{\cdot}{\cdot}} = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} KL^{(M)}_{ik}$ is used to compare the models, where smaller means correspond to better fits.
@@
 
-Figure \ref{kl_sim} displays $\overline{KL}^{(M)}_{{\cdot}{\cdot}}$  with error-bars plus/minus one $SE(\overline{KL}^{(M)}_{{\cdot} k})$ for each $a_{s} = 1.25,  5, 10$ and $c = 0.5, 1, 2$.
-The values of $a_{s}$ and $c$, do not effect the classical robust linear models.
-The average KL  for the normal theory models range between $0.22$ and $0.3$ which is much worse than the robust methods and hence are left out of the figure.
-For $c = 0.5$ and $c = 1$, the results are in favor of the restricted likelihood methods with perhaps a slight advantage to the use of Tukey's location estimator over Huber's.
-This is likely due to the fact that Tukey's estimator trims extreme outliers completely in the estimation procedure \citep{huber2009}.
-For $c = 2$, the classical methods win, again with a slight advantage to Tukey's statistic.
-It is clear that the priors picture in Figure \ref{fig:priors} matter.
-For $c = 2$, the priors subsequently add more mass significantly above $\sigma^{2} = 4$ as $a_{s}$ gets larger.
-Additionally the tuning parameters chosen for the location and scale estimators result in an upward bias in the estimate of $\sigma^{2}$.
+Figure \ref{kl_sim} displays the average of loss \ref{sim1loss} grouped by pairs of $a_{s}$ and $c$ with error bars plus/minus on standard error within the group.
+The values of $a_{s}$ and $c$, do not affect the classical robust linear models.
+The average loss for the normal theory models ranges from $1.19$ to $1.42$ and are left out of the figure.
+For $c = 0.5$ and $c = 1$ and the two larger values of $a_{s}$ the results favor the restricted likelihood methods.
+
+The choice of $c = 2$ corresponds to a particularly poor prior distribution.
+The prior has substantial mass above $\sigma^{2} = 4$, with prior means for $\sigma^2$ from $8.9$ to $32$ as $a_s$ varies.
+Additionally, the tuning parameters chosen for the location and scale estimators result in an upward bias in the estimate of $\sigma^{2}$.
 This bias depends on $m$ and $p$.
-For example, for $m = 9$ and $p = .1$, Huber's version converges to roughly $4.8$ asymptotically with $n$ under the data generating model.
-This bias gets worse for more severe contamination levels in the simulation.
-For $c = 0.5$ and $c = 1$, the priors place more mass on smaller values as $a_{s}$ grows.
-The larger values of $a_{s}$ also result in  better (smaller) average KL divergence.
-For $c = 1$ the prior concentration is roughly around the true $\sigma^{2} = 4$.
-For $c = 0.5$ the prior concentration is roughly around half $\sigma^{2} = 2$.
-Interestingly, this prior performs better in terms of KL divergence than having the seemingly more correct prior with $c = 1$.
-This prior does not capture good prior information on $\sigma^{2}$, but does compensates more for the upward bias in the estimates of scale.
-This highlights one potential effect of the choice of statistic and associated tuning parameters when applying the restricted likelihood.
+For example, for $m = 9$ and $p = .1$, Huber's version converges to roughly $4.8$ as $n$ grows.
+The bias is greater for more severe levels of contamination.
+The alignment of biases in prior distribution and in likelihood from the summary statistic (when applied to the contaminated data) inflates the estimate of scale.
+Not surprisingly, a poor prior distribution whose weakness matches the weakness in the likelihood results in poorer inference.
+In this case, poorer than the classical estimators.
 
@@
 \centering
-\includegraphics[width = 4in]{kl_sim2_facet_scale.png}
+\includegraphics[width = 5in]{mse_sim2_facet_scale.png}
+\caption{Average Loss plus/minus one standard error for each value of $a_{s}$ and $c$.
+Smaller values represent better fits.
+The panels correspond to $c = 0.5$ (left), $c=1$ (middle), and $c=2$ (right), with the values of $a_{s}$ on the horizontal axis.
+The average loss for the normal theory model ranges from $1.19$ to $1.42$ and is left out of the figure.}
 \label{kl_sim}
-\caption{Average KL - divergence plus/minus one standard error for each value of $a_{s}$ and $c$ ($\overline{KL}^{(M)}_{{\cdot}{\cdot}} \pm SE(\overline{KL}^{(M)}_{{\cdot} k})$).
-Smaller values represent better fits.
-The panels correspond to $c = 0.5$ (left), $c=1$ (middle), and $c=2$ (right) with the values of $a_{s}$ on the horizontal axis.
-The average KL  for the normal theory model ranges between $0.31$ and $0.37$ and are left out of the figure.}
 \end{figure}
@@
 It is also interesting to consider the effects of factors $n$, $p$, and $m$.
-We subset the results to a single prior ($a_s = 5$ and $c = 1$) to not confound the effects of the different priors.
-For each simulation $k$, the main effect averages of $KL^{(M)}_{ik}$  are found for each factor $n$, $p$, and $m$.
+We present the results for a single prior ($a_s = 5$ and $c = 1$).
+For each simulation $k$, the main effect average loss is found for each factor $n$, $p$, and $m$.
 Figure \ref{kl_mnp} displays the average of these main effects over the $K = 30$ simulations along  with error bars plus/minus one standard error.
-For each group $n$, $p$, and $m$ the restricted versions have better (lower) average KL divergences.
-The patterns also makes sense: average KL with get larger (worse) as the contamination gets more severe (larger $m$ or larger $p$) and average KL gets smaller (better) as the sample size $n$ grows.
+For each group $n$, $p$, and $m$, the Bayesian restricted likelihood versions have better (lower) average loss than do the classical methods.
+As expected, the average loss gets larger (worse) as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller (better) as the sample size $n$ grows.
+The advantage of the Bayesian method is greater for smaller sample sizes.
 
@@
 \centering
-\includegraphics[width = 4in]{kl_sim2_mnp.png}
-\caption{Average KL - divergence plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right).
-Results for a single prior ($a_s = 5$ and $c = 1$) are displayed to not confound the effects of the different priors.}
+\includegraphics[width = 5in]{MSE_sim2_mnp.png}
+\caption{Average loss plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right). These results are for the single prior  with $a_s = 5$ and $c = 1$.}
 \label{kl_mnp}
@@
 
-This simulation shows the potential of the restricted likelihood while highlighting some interesting observations.
+This simulation shows the potential of the restricted likelihood and conveys some cautions.
 Specifically, the choice of summary statistics, along with corresponding tuning parameters is important.
@@
 These choices must be made when using both the classical and Bayesian methods.
-The Bayesian setting allows for the incorporation of informative prior information which, as shown in this example, can improve prediction if chosen wisely.
-%In this severe outlier contamination setting, the better performance of the priors that shrink towards too small of values for $\sigma^{2}$ ($c = 0.5$) is an artifact of the fact that the tuning parameters on the estimators were non-optimal for this setting and more shrinkage was needed.
-However, a good choice for a prior on $\sigma^{2}$ ($c = 1$) still performs well.
-%A more refined model could have different tuning parameters for the groups representing different levels of contamination.
-However, a prior knowledge for
-
-%The results are sensitive to the prior, but here we have observed good relative improvement over the classical counterparts for a range of prior choices.
-
-%
-%\begin{figure}[H]
-%\centering
-%\includegraphics[scale = .3]{kl_sim2_facet_as.png}
-%\end{figure}
-
-%One explaination for the idea that 'shrinking towards smaller values' may do slightly better than shrinking toward the true value is the fact that we used default tuning parameters to define M-Estimators.
-For the amount of contaimination in each group, the expected value of the variance estimate (Huber's proposal 2) is larger that $\sigma^{2} = 4$.
-The histogram below demonstrates a sample of variaince estimates for data generated from one of the contamination groups....the estimates are consitently above 4.
-Thus it appears the prior mean must be smaller than the true value to get the `correct' amount of shrinkage.
-There is a suggestion that if the prior is too strong (large $a_{s}$), at some point, shrinking to too small a value degrades performance....which would be expected.
-
-%\begin{figure}[H]
-%\centering
-%\includegraphics[scale = .3]{hist_sig2_ests.png}
-%\end{figure}
+The Bayesian approach encourages use of a hierarchical model structure and allows one to incorporate prior information in the analysis.
+These features can improve predictive performance substantially.
+If poorly handled, they can, of course, harm performance.
+
+\subsection{\response{Simulation 2}}
+In this simulation the data are generated from the following mechanism: $y = \bbeta^{\top}x + \epsilon$
+where $\bbeta = (\beta_{1}, \beta_{2},\beta_{3})^{\top}$ with $\beta_{i} \iid N(0,1)$ and  $x \sim Uniform(0,1)$.
+The error $\epsilon \sim N(0,\sigma^{2})$ with probability $0.9$ and $\epsilon \sim Half-Normal(0,10\sigma^{2})$ with probability $0.1$.
+Finally, the variance $\sigma^{2} \sim IG(5,5)$.
+Thus, there are three active covariates, with one-sided outlier contamination.
+The regression model used for fitting contains 17 additional covariates generated uniformly on (0,1) representing the situation where several potential covariates are available and a goal is variable selection.
+For the simulation, $K = 50$ data sets of size $n = 500$ are generated from the true model and models including the additional non-active covariates are fit.
+We consider the classical robust regression using Tukey's estimator of location and Huber's estimator of scale, along with a corresponding restricted likelihood version.
+For the priors, denote $\bbeta_{all} = (\bbeta, \bbeta_{extra})^{\top}$ be the active coefficients augmented with the non-active extra coefficients.
+We take $\bbeta_{all}\sim N_{20}(\mb{0}, \sigma^{2}_{\beta}I)$ and $\sigma^{2}\sim IG(5,5)$.
+Hence, the prior for $\sigma^{2}$ is correct and the prior for $\bbeta$ is at least centered at the correct value as well.
+We also consider the Student-t model with compariable priors and fixed degrees of freedom $\nu = 5$.
+For each data set, we fit the models for $ \sigma_{\beta} = 0.2, 0.4, 0.6, 0.8,,1.0$.
+The acceptance rates for the restricted likelihood MCMC data-augmentation step range from ADDDDDDDD.
+
+To compare estimation performance we first consider the squared error SE$_{k} = ||\bbeta - \hat\bbeta||^{2} + ||\hat\bbeta_{extra}||^{2}$ for each simulation $k$.
+The mean squared error and standard errors over the simulations for each $\sigma^{2}_{\beta}$ are displayed in Figure \ref{mseSimMany}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width = 5in]{mse_sim_many_p.png}
+\caption{ADD}
+\label{mseSimMany}
+\end{figure}
+
+Additionally, we consider the log marginal distributions to understand predictive performance....
+FINISH
 
@@
 \label{RealData}
-We illustrate our methods with a pair of regression models for data from Nationwide Insurance Company, which concern prediction of the performance of insurance agencies.
-%The data contain many outliers and are subject to model misspecification.  
-%In particular, a group of the data do not follow the same generative process as the data of interest.  It would be 
-%extremely challenging to model some features of the data.  
-%In our analysis, we follow the standard practice when demonstrating the benefits of robust 
-%methods.  We work with a naive model for the data which ignores certain features of the problem.  We
-%do this both to create a situation where all can agree that the model for the full data $\by$ is imperfect
-%and to preserve the confidentiality of selected aspects of modeling done by Nationwide.  
-%We wish to provide inference for the `good' portion of the data.  %The two models we fit either treat the analysis
-%as a single regression or as a collection of related regressions.  % Details of the models, prior distributions, 
-%and conditioning statistics are given in the next two subsections.  
+We illustrate our methods with a pair of regression models for data from Nationwide Insurance Company that concern prediction of the performance of insurance agencies.
+
 %%%%%%%%%%%%%%%%%%%%%%%%
@@
 Our interest is the prediction of future performance of agencies where  performance is measured by the total number of households an agency services (`household count').
-%A serviced household is one in which at least one person living at that residence has at least one policy written through the agency. 
-%We used data from previous years to build a model to forecast future household count.
-In particular, we use household count  as measured during a single month in $2010$, to predict household counts in the corresponding month in $2012$.
-%In particular, we use agency characteristics, as measured during a single month in $2010$, to predict household counts in the corresponding month in $2012$.
-The characteristics used are household count and two measurements of agency size/experience.
-The two measurements of agency size/experience are, roughly, the number of employed persons at the agency and the length of time the agency has been affiliated with Nationwide.
-%The household counts (response and predictor) have been square rooted to stabilize variance. 
+
 The data are grouped by states with a varying number of agencies by state.
@@
 Likewise, state labels and agency types (identifying the varying contractual agreements) have been made generic to protect the proprietary nature of the data.
-Additionally, the counts scaled to have standard deviation one before anlaysis.
-%The data are proprietary, and to mask them all variables have been individually centered and scaled and identifiers (agency/agent names and state labels) have been removed.All subsequent analysis is done on this scale.
+Additionally, the counts were scaled to have standard deviation one before analysis.
+
 As an exploratory view, a plot of the square root of (scaled) household count in 2012, against that in 2010 
 is shown in Figure \ref{fig:ctVct} for four states.
-The states have varying number of agencies and  the different colors represent the varying types of contractual agreements as they stood in 2010 (`Type').
+The states have varying numbers of agencies and  the different colors represent the varying types of contractual agreements as they stood in 2010 (`Type').
 A significant number of agencies closed sometime before 2012, as represented by the $0$ counts for 2012.
@@
 However,  we leave them and use the data as a test bed for our techniques by fitting models that do not account for agency closures or contract type.
-Our expectation is that the restricted likelihood will facilitate prediction for the `good' part of the data (i.e.
-open, `type 1' agencies).
+Our expectation is that the restricted likelihood will facilitate prediction for the `good' part of the data (i.e., open, `type 1' agencies).
+\response{It is of concern to the company to predict closures and future performance for agencies that remain open.
+It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies.
+Additionally, robust methods are more likely to identify such agencies.
+Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.}
 
@@
 \subsection{State Level Regression model}
+%\response{included two more covariates in the regression}
+
 \label{regModelNW}
-The first analysis considered is based on individual regressions fit separately within states.  The following normal theory regression model is used as the full model for a single state:
+The first analysis is based on individual regressions fit separately within states.  The following normal theory regression model is used as the full model for a single state:
 \begin{equation}
 \label{eq:regModel}
-\beta\sim N(\mu_0, \sigma^{2}_0);\ \ \sigma^2\sim IG(a_0,b_0);\ \  
-y_{i}=\beta x_{i} +\epsilon_{i},\ \ \epsilon_{i}\iid N(0, \sigma^2),\ i=1,\dots, n, 
-\end{equation}
-%where $\beta$ is a four dimensional vector ($p=4$) of regression coefficients for the intercept, square root of count in 2010, and the two size/experience measures, and 
-where $y_{i}$ and $x_{i}$ are the square rooted household count in 2012 and 2010 for the $i^{th}$ agency, respectively. 
-%with covariate vector $\bx_{i}$.  Although the mean of covariates and response have been removed, we include the intercept as fitting is done on a holdout set to evaluate predictive performance.  
+\bbeta\sim N(\bmu_0, \Sigma_0);\ \ \sigma^2\sim IG(a_0,b_0);\ \  
+y_{i}=\bx_{i}^{\top}\bbeta+\epsilon_{i},\ \ \epsilon_{i}\iid N(0, \sigma^2),\ i=1,\dots, n, 
+\end{equation}
+where $\bbeta$ is a three dimensional vector ($p=3$) of regression coefficients for the covariate vector $\bx_{i}$ consisting of the square root of household count in 2010, and two different size/experience measures related to the number of employees associated with the agency.
+The response, $y_{i}$ is the square root of household count in 2012.
 The hyper-parameters $a_0, b_0, \mu_0$ and $\sigma^{2}_0$ are all fixed and set from a 
@@
 before.
-Specifically, Let $\hat\beta$ and $\hat\sigma^{2}$ be estimates from the robust linear regression of 2010 counts on 2008 counts.
+Specifically, Let $\hat\bbeta$ and $\hat\sigma^{2}$ be estimates from the robust linear regression of 2010 counts on 2008 counts.
 We fix $a_0 = 5$ and set $b_0 = \hat\sigma^{2}(a_0 - 1)$ so the prior mean is $\hat\sigma^{2}$.
-We set $\mu_0 = \hat\beta$ and $\sigma^{2}_0 =  n_{p}se(\hat\beta)^{2}$ where $n_{p}$ is the number of agencies in the prior data set and $se(\hat\beta)$ is the standard error of $\hat\beta$ derived from the robust regression.
-%The value of $f$ is varied, controlling the prior certainty on $\beta$, with smaller values corresponding to a more certain prior.
-This prior is in the spirit of the Zellner's $g$-prior \citep{zellner1986, liang2008}; in general scaling the prior variance $se(\hat\beta)^{2}$ by a factor $g$.
-$g = n_{p}$ is analogous to the unit-information prior \citep{kass1995reference}, with the difference that we are using a prior data set, not the current data set, to set the prior.
-The obvious reason this model is misspecified is due to omission of the contract type and agency closure information.
+We set $\bmu_0 = \hat\bbeta$ and $\Sigma_0 =  n_{p}\hat\Sigma_{0}$ where $n_{p}$ is the number of agencies in the prior data set and $\hat\Sigma_{0}$ is the estimated covariance matrix of $\hat\bbeta$ derived from the robust regression.
+This prior is in the spirit of the Zellner's $g$-prior \citep{zellner1986, liang2008}.
+In general, scaling the prior variance by a factor $g = n_{p}$ is analogous to the unit-information prior \citep{kass1995reference}, with the difference that we are using a prior data set, not the current data set, to set the prior.
+The obvious reason why this model is misspecified is due to omission of the contract type and agency closure information.
 Closing our eyes to these variables, many of the cases appear as outliers.
 Additionally, the model assumes equal variance within each state, an assumption whose worth is arguable (see Figure \ref{fig:ctVct}).
-%$f = 0.05, 0.1, 0.5, 1$ and%We fit the models separately for each $g^{*} = 0.05, 0.1, 0.5, 1$  %represent the estimate of the coefficients from this fit we  set $\bmu_0=\hat\bbeta$ and $ \Sigma_0=n\cdot \mbox{var}(\hat\bbeta)$ where here $n$ is the sample size of the prior data set.
-%corresponding to  a unit information prior for $\bbeta$.
-%The hyperparameters for $\sigma^2$ are set so that the prior mean is $s^2$, the estimated variance from the robust regression, and the spread of the prior covers the range of plausible values with high probability.
-All values are then transformed appropriately to match the current scale of the data.
-In the end we take $\bmu_0=(0.18,  0.81,0.01,-0.02)^\top$ and set the mean of $\sigma^2$ to $0.014$ and standard deviation to  $0.033$.
 
@@
 %across $K = 50$ different splits into training and holdout samples. 
-`Type 1' agencies are of special interest to the company and so the evaluation of the TLM is done on only holdout samples of `Type 1', wheres the training is done on agencies of all types.
+`Type 1' agencies are of special interest to the company and so the evaluation of the TLM is done on only holdout samples of `Type 1', whereas the training is done on agencies of all types.
 This is intended to demonstrate the robustness properties of the various methods.
@@
 Models are fit to four states labelled State 2, 15, 27, and 36, with $n = 222, 40, 117,$ and $46$, representing a range of sample sizes.
-Fitting is done on $K = 50$ training/holdout samples with training sample sizes taken to be $.25n$ and $0.50n$.
+Fitting is done on $K = 50$ training samples with training sample sizes taken to be $0.25n$ and $0.50n$.
 Holdout evaluation is done on the remaining (`Type 1') samples.
-For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.16$ to $0.76$ across the states, repetitions, and two versions of the model.
-The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
+For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates, \response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
+\response{The exception was a single training set from State 15 resulting in an usually small acceptance rate under Tukey's version.
+This case didn't effect the overall results of the simulations but emphasizes the need to check convergence on a case by case basis.} The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
 Similar results are observed for other base models.
-The error-bars are plus/minus one standard deviation of the average $TLM_b(A)$ over the $K = 50$  training/holdout samples.
-It is clear the normal Bayesian model used as the full model (Normal) and the classical ordinary least squares fits (OLS) have poor performance due to the significant amount of outlier contamination in the data.
+The error bars are plus/minus one standard deviation of the average $TLM_b(A)$ over the $K = 50$  training/holdout samples.
+It is clear that the normal Bayesian model used as the full model (Normal) and the classical ordinary least squares fits (OLS) have poor performance due to the significant amount of outlier contamination in the data.
 In comparing our restricted methods to their corresponding classical methods, there is small, but consistent improvement across the states and training sample size.
+Additionally, variance reduction for the Bayesian versions is evident, especially in State 15, highlighted by the smaller error bars.
 For state 2, the largest state with $n = 222$, the restricted and classical robust methods have similar performance especially for larger training sample size.
@@
 Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.
-For the other states (State 15 and 36), the Student-t performs similarly to our restricted methods for smaller training sample size (25\% of the sample).
-However, the performance is slightly worse for the larger training sample size (50\% of the sample).
+For the other states (State 15 and 36), the Student-t performs better to our restricted methods for smaller training sample size (25\% of the sample).
+However, this advantage goes away for the larger training sample size (50\% of the sample).
 Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model; an assumption which is detrimental for prediction.
@@
 For smaller $\alpha$ (in this case $\alpha = 0.1$), many outliers are left untrimmed resulting in lower TLM  for all methods and noticeably larger standard deviation for the classical robust methods and our restricted likelihood.
-Larger values of $\alpha$ ensure the predictive performance assessment excludes the majority of outliers.
-The proportion of $0$ counts in the data is roughly $0.14$, suggesting $\alpha$ should be at least this large.
+Larger values of $\alpha$ ensure that the predictive performance assessment excludes the majority of outliers.
+The proportion of $0$ counts in the data is roughly $0.14$, suggesting that $\alpha$ should be at least this large.
 
@@
 \label{eq:hierModel}
-&\beta\sim N_p(\mu_0, a\sigma_0^{2});\ \ 
-\beta_j\iid N_p(\beta, b\sigma_0^{2}); \ \  
-\sigma_j^2\sim IG(a_0,b_0);  & \\ \nonumber
-& y_{ij}=x_{ij}\beta_j+\epsilon_{ij},\ \ \epsilon_{ij}\iid N(0, \sigma_j^2),\ i=1,\dots, n_j,\ j=1,\dots, J &
+&\bbeta\sim N_p(\bmu_0, a\Sigma_0);\ \ 
+\bbeta_j\iid N_p(\bbeta, b\Sigma_0); \ \  
+\sigma_j^2\sim IG(a_0,b_0);  & \\ 
+& y_{ij}=\bx_{ij}^\top\bbeta_j+\epsilon_{ij},\ \ \epsilon_{ij}\iid N(0, \sigma_j^2),\ i=1,\dots, n_j,\ j=1,\dots, J &
 %\end{split}
@@
 state, $n_{j}$ is the total number of agencies in state $j$, and $J$ is
-the number of states. $x_{ij}$ is the square rooted household count in 2010 and $\beta_j$ represents the individual regression coefficient vector for state $j$. The parameters $\mu_0$,
-$\sigma^{2}_0$, $a_0$, and $b_0$ are fixed by fitting  the regression $y_{ij}=x_{ij}\beta+\epsilon_{ij}$ using Huber's M-estimators to the prior data set from two years before.
-Using the estimates from this model, we set $\mu_{0} = \hat\beta$, $\sigma_{0}^{2} = n_{p}se(\hat\beta)^{2}$ ($n_{p} = 2996$ is the number of observations in the prior data set), $a_{0}=5$ and $b_{0} = \hat\sigma^{2}(a_{0} -1)$.
+the number of states. $\bx_{ij}$ is same tree-dimensions covariate vector as before and $\bbeta_j$ represents the individual regression coefficient vector for state $j$. The parameters $\bmu_0$,
+$\Sigma_0$, $a_0$, and $b_0$ are fixed by fitting  the regression $y_{ij}=\bx_{ij}^{\top}\bbeta+\epsilon_{ij}$ using Huber's M-estimators to the prior data set from two years before.
+Using the estimates from this model, we set $\mu_{0} = \hat\beta$, $\Sigma_{0} = n_{p}\hat{\Sigma_{0}}$ ($n_{p} = 2996$ is the number of observations in the prior data set), $a_{0}=5$ and $b_{0} = \hat\sigma^{2}(a_{0} -1)$.
 We constrain $a+b=1$
 in an attempt to partition the total variance between the individual
-$\beta_j$'s and the overall $\beta$. We take $b\sim
+$\bbeta_j$'s and the overall $\bbeta$ and take $b\sim
 \text{beta}(v_1,v_2)$. Using the prior data set, we assess the
-variation between individual estimates of the $\beta_j$ to set $v_1$
+variation between individual estimates of the $\bbeta_j$ to set $v_1$
 and $v_2$ to allow for a reasonable amount of shrinkage. To allow for
@@
 $\psi_\rho=a_\rho+b_\rho$. The parameters $\mu_\rho$ and
-$\psi_{\rho}$  are given beta and gamma distributions, with fixed hyperparameters. More details on setting prior parameters are given in the appendix.
+$\psi_{\rho}$  are given beta and gamma distributions, with fixed hyperparameters. More details on setting prior parameters are given in the Supplementary Material.
 
@@
 Hierarchical models naturally require more
-data and so we include states having at least 25 agencies resulting in 22 states in total and $n = \sum_{j} n_{j} =  3180$ total agencies.
-For training data we take a stratified (by state) sample of size $3180/2 = 1590$ where the strata sizes are $n_{j}/2$ (rounded to the nearest integer).
+data and so we include states having at least 25 agencies with sufficient variation within each covariate, resulting in 20 states in total and $n = \sum_{j} n_{j} =  3094$ total agencies.
+For training data we take a stratified (by state) sample of size $3094/2 = 1547$ where the strata sizes are $n_{j}/2$ (rounded to the nearest integer).
 The remaining data is used for a holdout evaluation using TLM computed separately within each state: $TLM_b(A)_{j} = (M_{j} - [\alpha M_{j}])^{-1} \sum_{i=[\alpha M_{j}]+1}^{M_{j}} \log(f_A(y_{(i)j}^b))$ where $y_{(1)j}^b, y_{(2)j}^b,..., y_{(M_{j})j}^b$ is the ordering of the $M_{j}$ holdout observations within state $j$ according to the log marginals under the base model $b$.
-For the non-Bayesian models,  $f_A(y_{(i)j})^b$ is estimated using plug-in estimators for the parameters for state $j$.
+For the non-Bayesian models,  $f_A(y^b_{(i)j})$ is estimated using plug-in estimators for the parameters for state $j$.
 $TLM_b(A)_{j}$ is computed for each state for $K=50$ splits of training and holdout sets.
 The Bayesian models are fit using MCMC, with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} and adapted to the hierarchical setting as described in Section \ref{simData}.
-For the MH-step proposing augmented data,  the acceptance rates for the two restricted likelihood models across all states and repetitions ranges from $0.24$ to  $0.74$.
-
-%We digress briefly to note that for the restricted likelihood methods no additional computational strategies outside of those discussed in Section~\ref{highDim} are needed to fit the hierarchical models described here.
-Since we condition on statistics which are computed within each state, the model's conditional independence between the states allows the data augmentation described earlier to be performed independently within each state.
-Updates of hyperparameters follow conventional MCMC procedures.
-We note that different types of statistics could be chosen for each state, if desired, allowing for a large amount of flexibility.
+For the MH-step proposing augmented data,  \response{the acceptance rates for the two restricted likelihood models across all states and repetitions ranged from $0.01$ to  $0.75$, with only $7$ cases (out of 50*20*2 = 2000 chains) with rates below $0.1$}
 
@@
 \ref{fig:hierTLM} for several trimming fractions using the Student-t as the base model.
-The points are the average of the $\overline{TLM}_b(A)_{\cdot}$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$ with larger values representing better predictive performance.
+The points are the average of the $\overline{TLM}_b(A)_{\cdot}$ over the $K$ repetitions with error bars plus/minus one standard deviation over $K$ with larger values representing better predictive performance.
 As the trimming fraction used for the TLM increases, so does TLM since more outliers are being trimmed.
@@
 Despite being used as the base model to compute TLM, the Student-t doesn't perform well in comparison to the robust regressions.
-We attribute this to the assumption of heavier tails resulting in smaller log marginal values on average; emphasizing again that the t-model will do well to discount outlying observations but doesn't provide a natural mechanism for only predicting `good' (i.e.
-non-outlying) data.
+We attribute this to the assumption of heavier tails resulting in smaller log marginal values on average; emphasizing again that the t-model will do well to discount outlying observations but does not provide a natural mechanism for predicting non-outlying data.
 For each trimming fraction, our restricted likelihood hierarchical models outperform the classical robust regressions fit separately within each state.
-The hierarchical model also reduce variance in predictions resulting in smaller error bars.
-This improvement decreases with $\alpha$ but is still noticeable for $\alpha = 0.3$.
-Both the Tukey and Huber versions perform similarly.
+The hierarchical model also reduces variance in predictions resulting in smaller error bars.
 
@@
 It is also interesting to examine the results within each state.
-Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ with $\alpha = 0.3$ for each state where the points and errorbars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions.
-The results are only given for the models using Tukey's M-estimators (Huber's version looks similar).
+Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ with $\alpha = 0.3$ for each state where the points and error bars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions.
+The results are only given for the models using Tukey's M-estimators (Huber's version is qualitatively similar).
 The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses).
-In several of the smaller states, the restricted hierarchical model performs better with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior.
-It is clear the hierarchical structure is having the effect of pooling information across states; beneficial for improving performance in some of the smaller states.
-The standard deviations are smaller for the hierarchical model in smaller states with virtually identical standard deviations for the larger states.
+State 28 is removed from the figure as the error bars for the classical robust regression are excessively large and distort the comparison.
+In several of the smaller states, the restricted hierarchical model performs better with similar performance between the models in most of the larger states, a reflection of the decreased influence of the prior.
+The hierarchical structure pools information across states, improving performance in the smaller states.
+The standard deviations are smaller for the hierarchical model in smaller states than they are for the corresponding classical model.
+In larger states, the standard deviations are virtually identical.
 Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.
@@
 \begin{figure}[t]
-\includegraphics[width=7in]{hier_ave_tlm_state.png}
+\centering
+\includegraphics[width=6.8in]{hier_ave_tlm_state.png}
 \caption{Hierarchical model results: ${TLM}_b(A)_{j}$  plus/minus one standard deviation over $K = 50$ repetitions for each state and $\alpha = 0.3$.
@@
 
-%This work describes the concept of conditioning on insufficient statistics in Bayesian models, a method we term the restricted likelihood.
-The examples demonstrate the potential predictive improvement over competing methods in outlier-prone settings where the conditioning statistic targets the mean of the non-outlying data (e.g.
-M-estimators).
-%Attempting to model outliers can be seen as a special case of  misspecification of the original model for the non-outlying data.
-The traditional view is that, if the model is inadequate, one should build a better model.
-In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model.
-We ask the question Òby attempting to improve our model through elaboration, will the overall performance of the model suffer?Ó If yes, we avoid the elaboration, retaining a model with some level of misspecification.
-Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present.
-In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this problem.
-This paper discusses the restricted likelihood where posterior inference is conducted by conditioning on a summary statistic rather than the complete data. 
-The framework leads us to blend classical estimation with Bayesian methods.
+This paper develops a Bayesian version of restricted likelihood where posterior inference is conducted by conditioning on a summary statistic rather than the complete data.
+The framework blends classical estimation with Bayesian methods.
 %Many routine choices in an analysis react to the gap between reality and the
@@
 %A greater benefit of our framework is that it leads us to blend classical estimation with Bayesian methods. 
-Here, we concentrate on outlier-prone settings where natural choices for conditioning statistic are classical robust estimators targeting the mean of the non-outlying data (e.g., M-estimators).
+Here, we concentrate on outlier-prone settings where natural choices for the conditioning statistic are classical robust estimators targeting the mean of the non-outlying data (e.g., M-estimators).
 The likelihood conditioned on these estimators is used to move from prior to posterior.
@@
 Computation is driven by MCMC methods, requiring only a supplement to existing algorithms by adding a Gibbs step to sample from the space of data sets satisfying the observed statistic.
-This step has additional computation costs driven by  the need to compute the estimator and an orthonormal basis derived from gradients of the estimator at each iteration.
-The cost of finding the basis can be driven down by an understanding of the geometric space from which the samples are drawn as described in Section~\ref{highDim}.
-Additionally, we have seen good mixing of the MCMC chains across a wide-variety of examples.
-
-Outside of outlier-prone settings, we might condition on the results of a set of estimating equations, designed to enforce lexical preferences for those features of the analysis considered most important, yet still producing inferences for secondary aspects of the problem.
-For example, the computational strategies we devised here allow us to apply the method to inference on quantiles of a regression model by, for example, conditioning on estimates of these quantiles.
-This leads to questions regarding the choice of summary statistic to apply.
-For outliers, we have applied some obvious choices (M-estimators, LMS, LTS) which have shown value in classical robust estimation.
-Properties of such estimators are well known and can be used as a basis for selecting one.
-In general, great ingenuity has been used to create a wide variety of estimators designed to handle specific manifestations of a misspecified model; where outliers are just a specific case.
-The estimators are typically accompanied by asymptotic results on consistency and distribution.
-These results can be used as starting point for choosing appropriate statistics in specific settings.
-In general, we recommend a choice based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.
-
-In general, this framework can be used to address model misspecification, of which the presence of outliers is an example.
+This step has additional computation costs arising from the need to compute the estimator and an orthonormal basis derived from gradients of the estimator at each iteration.
+The cost of finding the basis can be reduced by exploiting properties of the geometric space from which the samples are drawn as described in Section~\ref{highDim}.
+We have seen good mixing of the MCMC chains across a wide-variety of examples.
+\response{We have found the additional computational burden to be beneficial in situation where  substantial prior information that will impact the results is available.}
+
+The Bayesian restricted likelihood framework can be used to address model misspecification, of which the presence of outliers is but one example.
 The traditional view is that, if the model is inadequate, one should build a better model.
@@
 Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present.
-In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this more general problem.
-The framework allows us to retain many benefits of Bayesian methods:  it requires a complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.
-The work does open a number of questions for further work, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.
+In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see restricted likelihood as a method for dealing with this more general problem.
+
+Outside of outlier-prone settings, we might condition on the results of a set of estimating equations designed to enforce a lexical preference for those features of the analysis considered most important, yet still producing inferences for secondary aspects of the problem.
+This leads to questions regarding the choice of summary statistic to apply.
+In the literature, great ingenuity has been used to create a wide variety of estimators designed to handle specific manifestations of a misspecified model.
+The estimators are typically accompanied by asymptotic results on consistency and limiting distribution.
+These results can be used as a starting point to choose appropriate conditioning statistics in specific settings.
+For example, a set of regression quantiles may be judged the most important feature of a model.
+It would then be natural to condition on the estimated regression quantiles and to use a flexible prior distribution to allow for nonlinearities in the quantiles.
+The computational strategies we have devised allow us to apply our methods in this setting and to make full predictive inference.
+In general, we recommend a choice of conditioning statistic based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.
+
+The framework we develop here allows us to retain many benefits of Bayesian methods:  it requires a complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.
+The work does open a number of questions for further work, including a need to investigate restricted likelihood methods as they relate to model selection, model averaging for predictive performance, and model diagnostics.
 
@@
 
-\section{Appendix}
+\section{Supplementary Material}
 \label{sec:appendix}
+
+\subsection{Practical Considerations for Using the Restricted Likelihood}
+We offer the following guidelines and recommendations for using these methods in practice. 
+\begin{itemize}
+\item we have found them most useful in outlier prone situations where good prior information can be encoded for the `good' part of the model.
+The additional computation burden may be too much when this is not the case.
+Traditional robust estimation techniques are often quicker and can provide comparable results.
+\item Currently, we recommend conditioning on classical robust estimators when pursing these methods.
+Default choices are Huber's and Tukey's estimators as outlined in the paper.
+We have found default choices (e.g.
+obtaining 95\% efficiency under normally distributed data) for the tuning parameters to work well in many situations.
+However, depending on the amount of contamination, some adjustment may be necessary.
+\item Comparisons amongst various choices of conditioning statistics can be made via standard cross-validation techniques like those done in this paper where models are fit to several training and holdout sets.
+One should take care in the method of evaluation.
+When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data.
+We introduce the TLM, however it may be simpler to simply identify outliers and exclude them from the evaluation stage explicitly.
+\end{itemize}
+
+\subsection{An Additional Illustrative Example}
+
+As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
+The outliers in this case are due to a change in measurement units on which calls were recorded for part of the data set.
+Specifically, for years 1964-1969 and parts of 1963 and 1970, the length of calls in minutes were recorded rather than the number of calls \citep{rousseeuw1987}.
+The full model is a standard normal Bayesian linear regression:
+\begin{equation}
+{\boldsymbol{\beta}}\sim N_{2}(\boldsymbol{\mu}_{0}, \boldsymbol{\Sigma}_{0}),\  \sigma^{2} \sim IG(a, b),\  \by \sim N(X\boldsymbol{\beta}, \sigma^{2} I),
+\end{equation}
+where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and $X$ is the $n\times 2$ design matrix with a vector of 1's in the first column and the year covariate in the second.
+Prior parameters are fixed via a maximum likelihood fit to the first 3 data points.
+In particular, the prior covariance for $\bbeta$ is set to $\Sigma_{0} = g\sigma_{0}^2 (X_{p}^{\top}X_{p})^{-1}$, with $X_{p}$ the $3\times 2$ design matrix for the first $3$ data points, $g=n=21$, $\sigma_{0} = 0.03$ and $\boldsymbol{\mu}_{0} = (1.87,  0.03)^{\top}$.
+This has the spirit of a unit information prior \citep{kass1995reference} but uses a design matrix for data not used in the fit.
+Finally $a = 2$ and $b =1$.
+
+Four models are compared: 1) the normal theory base model 2) a two component normal mixture model, 3) a t-model, and 4) a restricted likelihood model conditioning on Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
+Each model is fit to the remaining 21 data points.
+The normal theory model is also fit a second time after removing observations 14-21 (years 1963 - 1970).
+The omitted cases consist of the obvious large outliers as well as the two smaller outliers at the beginning and end of this sequence of points caused by the change in measurement units.
+The mixture model allows different mean regression functions and variances for each component.
+Both components have the same, relatively vague priors.
+The probability of belonging to the first component is given a $\text{beta}(5,1)$ prior.
+The heavy-tailed model fixes the degrees of freedom at 5 and uses the same prior on $\bbeta$.
+The prior on $\sigma^2$ is adjusted by a scale factor of $3/5$ to provide the same prior on the variance.
+
+The data and  $95\%$ credible bands for the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}.
+The normal model fit to all cases results in a very wide posterior predictive distribution due to an inflated estimate of the variance.
+The t-model provides a similar predictive distribution.
+The pocket of outliers from 1963 to 1970 overwhelms the natural robustness of the model and leads to wide prediction bands.
+The outliers, falling toward the end of the time period, lead to a relatively high slope for the regression.
+In contrast, the normal theory model fit to only the good data results in a smaller slope and narrower prediction bands.
+The predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit to the non-outlying cases.
+The two component mixture model provides similar results, where the predictive distribution is formulated using only the good component.
+For these data, the large outliers are easily identified as following a distinct regression, leaving the primary component of the mixture for non-outlying data.
+In a more complex situation where the outlier generating mechanism is transient (i.e., ever changing and more complex than for these data), modeling the outliers is more difficult.
+As in classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
+\begin{figure}[t]
+\centering
+{\includegraphics[width = 4in]{figs/calls_predictive.png}}
+\caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
+The first three data points were used to specify the prior with each model using the remaining 21 for fitting.
+The normal theory model was also fit after removing observations 14-20 (years 1963 - 1970).}
+\label{fig:calls_predictive}
+\end{figure}
+
 \subsection{Proofs}
@@
 \begin{theorem}
+\label{1to1onto}
 The mapping $h:  \mathbb{S} \rightarrow \mathcal{A}$ with $h$ defined in Theorem \ref{Transformation} is one-to-one and onto. 
@@
 \noindent 
-\textit{one-to-one}: Let $z_{1}, z_{2} \in \mathbb{S}$ with $h(z_{1}) = h(z_{2})$.
+\textit{One-to-one}: Let $z_{1}, z_{2} \in \mathbb{S}$ with $h(z_{1}) = h(z_{2})$.
 Rearrangement implies $z_{1} = cz_{2} + Xv$ for known $c\in \mathbb{R}$ and $v\in \mathbb{R}^{p}$ depending on $\bb(X,\by_{obs})$, $s(X,\by_{obs})$, $\bb(X,z_{1})$, $s(X,z_{1})$, $\bb(X,z_{2})$, $s(X,z_{2})$.
-Given $z_{2}\in \mathbb{S}$, $v\neq 0$ implies $z\notin \mathcal{C}^{\perp}(X)$ and $c\neq 1$ implies $||z_{1}|| \neq 1$.
+Given $z_{2}\in \mathbb{S}$, $v\neq 0$ implies $z_{1}\notin \mathcal{C}^{\perp}(X)$ and $c\neq 1$ implies $||z_{1}|| \neq 1$.
 Thus $z_{1} \in \mathbb{S}$ implies $c=1$ and $v =0$.
@@
 Using the previous data set from two years prior, we fit separate (robust) regressions to each state and a  regression to the entirety of the data at once.
-Let the estimates for the fits to each state be $\hat{\beta_{1}}, \dots, \hat \beta_{J}, \hat \sigma_{1}, \dots, \hat \sigma_{J}$ and the estimates from the single regression be $\hat \beta$ and $\hat \sigma$.
+Let the estimates for the fits to each state be $\hat{\bbeta_{1}}, \dots, \hat \bbeta_{J}, \hat \sigma_{1}, \dots, \hat \sigma_{J}$ and the estimates from the single regression be $\hat \bbeta$ and $\hat \sigma$.
 These are classical robust estimates using Tukey's regression and Huber's scale.
-For this sections, let $n_{j}$ denote the number of observations in the $j^{th}$ state (of the previous data set) and set $n_{p}=\sum n_{j}$.
+For this section, let $n_{j}$ denote the number of observations in the $j^{th}$ state (of the previous data set) and set $n_{p}=\sum n_{j}$.
 
 First, consider $v_{1}$ and $v_{2}$ in the prior $b\sim\text{beta}(v_{1},v_{2})$.
-In the hierarchical model \eqref{eq:hierModel}, $b=0$ implies all the $\beta_{j}'s$ are equal (no variation between states) and $b=1$ implies the $\beta_{j}'s$ vary about $\mu_{0}$ according to $\Sigma_{0}=n_{p}\cdot \mbox{se}(\hat\beta)^{2}$ (see Section \ref{regModelNW}).
+In the hierarchical model \eqref{eq:hierModel}, $b=0$ implies all $\bbeta_{j}$ are equal (no variation between states) and $b=1$ implies the $\bbeta_{j}$ vary about $\mu_{0}$ according to $\Sigma_{0} = n_{p}\hat{\Sigma_{0}}$ (see Section \ref{regModelNW}).
 We seek a prior measure for what we think $b$ should be.
-Using the prior fit, a measure for  uncertainty for $\beta$ is $\Sigma_{\hat\beta}=\mbox{se}(\hat\beta)^{2}$, the estimate of the variance from the single regression.
-For the $\beta_{j}'s$, take $\delta_{j}=\hat\beta_{j}-\hat\beta$ and set the prior uncertainty to $\Sigma_{\delta}=n_{p}^{-1}\sum_{j} n_{j}\delta_{j}^{2}$.
-Consider  $g= \Sigma_{\delta}/\Sigma_{\hat\beta}$ measuring of the amount of uncertainty between the $\beta_{j}'s$ relative to that of $\beta$.
+Using the prior fit, a measure for  uncertainty for $\bbeta$ is $\Sigma_{\hat\beta} = cov(\hat\bbeta)$, the estimate of the covariance from the single regression.
+For each $j$, take $\delta_{j}=\hat\bbeta_{j}-\hat\bbeta$ and set the prior uncertainty to $\Sigma_{\delta}=n_{p}^{-1}\sum_{j} n_{j}\delta_{j}\delta_{j}^{\top}$.
+Consider  $g= (|\Sigma_{\delta}|/|\Sigma_{\hat\beta}|)^{(1/p)}$ as a measure of the amount of uncertainty between the $\beta_{j}$ relative to that of $\bbeta$.
 Now in the prior, we heuristically set the uncertainty in the $\beta_{j}'s$ ($b\Sigma_{0}$) to be approximately equal to $g\cdot\Sigma_{\hat\beta}$.
@@
 Finally, we  set the rate parameter for to 1 implying the variance of the gamma prior is equal to its the mean.
-With this specification, the prior on $\rho$ has 80\% of the central mass between roughly $0.03$ and $0.42$ and reflects our prior belief that there is likely only weak positive correlation amongst the $\sigma^{2}_{j}$'s.
+With this specification, the prior on $\rho$ has 80\% of the central mass between roughly $0.03$ and $0.4$ and reflects our prior belief that there is likely only weak positive correlation amongst the $\sigma^{2}_{j}$'s.
 %%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$
@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+\section{M-estimators}
+\label{sec:Mestimators}
+%%%%%%%%%%%%%%%%%%%%%%%%
+M-estimators offer a natural choice for conditioning in restricted likelihood settings and they can be readily applied when conditioning on these estimators using the method described in this paper.
+This section gives a brief review
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{M-estimators of Location}
+\label{sec:Mlocation}
+%%%%%%%%%%%%%%%%%%%%%%%%
+To begin the review it is easiest to start with the location model 
+\begin{equation}
+\label{locMod}
+y_i= \mu+\epsilon_i, \ \ i=1,\dots, n,
+\end{equation}
+where we assume that $\epsilon_i$ are independent identically
+distributed random variables from the distribution $F_0$ having
+mean zero, constant (known) variance, and density $f_0$ with
+respect to Lebesgue measure. It follows that $y_i\iid
+F(y)=F_0(y-\mu)$ . The M-estimate for $\mu$ is defined by the criterion
+\begin{equation}
+\label{MrhoLoc}
+\hat\mu= \arg \min_\mu \sum_{i=1}^n \rho(y_i -\mu),
+\end{equation}
+where $\rho$ is a loss function.
+It is assumed that $\rho(x)$ is nondecreasing in $|x|$ and $\rho(0)=0$.
+If $F_0$ is standard normal, taking $\rho$ to be squared error loss ($\rho(x)=x^2$) results in the maximum likelihood estimator (MLE).
+In general, $\rho(x)=-\log f_{0}(x)$ corresponds to the MLE.
+In this sense, M-estimators are a generalization of MLEs.
+
+Assuming it exists, the derivative of $\rho$ is denoted by $\psi$ and $\hat\mu$  in  \eqref{MrhoLoc} satisfies the estimating equation
+\begin{equation}
+\label{MpsiLoc}
+\sum_{i=1}^n \psi(y_i-\hat\mu)=0.
+\end{equation}
+Putting $w_i=\frac{\psi(y_i-\hat \mu)}{y_i- \hat\mu}$, equation
+\eqref{MpsiLoc} can be rewritten as
+\begin{equation}
+\label{MpsiLocWeight}
+\sum_{i=1}^n w_i (y_i- \hat\mu)=0
+\end{equation}
+and an analytical expression for $\hat\mu$ is then the weighted average
+\begin{equation}
+\label{weightedAve}
+\hat\mu=\frac{\sum_{i} w_iy_i}{\sum_{i} w_i}.
+\end{equation}
+This weighted average cannot be used directly since the $w_i$
+depend on $\hat\mu$, but it provides a useful insight in how to choose a $\psi$ that downweights outlying observations. Two
+examples of commonly used $\rho$ functions whose derivatives $\psi$ achieve downweighting are
+\begin{equation}
+\label{Huber}
+\rho(x)=
+\begin{cases}
+x^2, & \  |x|\leq k \\
+2k|x|-k^2,&\ |x|\geq k 
+\end{cases}
+\end{equation}
+and 
+\begin{equation}
+\label{Tukey}
+\rho(x)=
+\begin{cases}
+1-[1-(x/k)^2]^3, & \  |x|\leq k \\
+1, &\ |x|\geq k .
+\end{cases}
+\end{equation}
+The first of these is known as Huber's loss.
+It offers a compromise to squared error loss, with the loss becoming linear for absolute residuals larger than $k$.
+\cite{huber2009} provide a theoretical justification of this choice based the \textit{least informative distribution} in a particular class of contaminated normal distributions.
+The $\rho$ in \eqref{Tukey} is known as Tukey's bisquare.
+
+A notable property of both of the $\psi$ functions here is that they are bounded.
+This implies a bounded \textit{influence function} (IF).
+The influence function is a measure of how much an estimator is
+affected by a small fraction of identical outliers in the
+sample. Boundedness is desirable because it
+implies that the effect of a small contamination on a
+statistical procedure cannot become arbitrarily large.
+More details on influence functions can be found in \cite{huber2009} and \cite{maronna2006}.
+Tukey's $\psi$ is \textit{re-descending} as it returns to zero outside of $(-k,k)$.
+As a result, Tukey's estimator downweights large residuals more than does Huber's estimator.
+Huber's estimator is akin to Winsorising whereas Tukey's is akin to complete trimming.
+
+Note that $k$ is a tuning constant which must be chosen.
+Under usually satisfied conditions, M-estimators are asymptotically normal and this property can be employed to choose $k$.
+The results for the location setting, which extend up to linear regression, are presented here.
+Again, more detailed results can be found in both \cite{huber2009} and \cite{maronna2006}.
+
+For a given distribution $F$, let $\mu_0$ be the value such that
+\begin{equation}
+\label{eq:Epsi}
+E_F\psi(x-\mu_0)=\int\psi(x-\mu_0)\ dF=0.
+\end{equation}
+Taking $\hat\mu$ to be the solution to \eqref{MpsiLoc} we have
+$\hat\mu\overset{p}\rightarrow \mu_0$ and
+\begin{equation}
+\label{eq:asyNormM}
+\sqrt{n}(\hat\mu-\mu_0)\overset{\mc D}\rightarrow N(0, v)\
+\text{with}\
+v=\frac{E_F(\psi(y-\mu_0)^2)}{(E_F\psi'(y-\mu_0))^2}
+\end{equation}
+as $n\rightarrow\infty$. The conditions for the above convergence properties to hold depend on $\psi$ and
+$F$. In particular, the numerator of $v$ must be finite and the
+denominator must exist and be nonzero. Re-descending $\psi$
+functions, such as Tukey's, require slightly stronger conditions than those for monotone $\psi$.
+
+Under the assumed model, the MLE is optimal in the sense of achieving the minimum asymptotic variance of $v_0=I(\mu)^{-1}$  where $I(\mu)$ is the Fisher information for $\mu$.
+Hence, $v\geq v_0$ and $k$ is typically chosen by considering the asymptotic relative efficiency of $\hat\mu$
+\begin{equation}
+\label{eq:Eff}
+\text{Eff}(\hat\mu)=\frac{v_0}{v}.
+\end{equation}
+The idea is for robust estimators to not perform badly compared
+to the optimal estimator, under the assumed model. To this end,
+$k$ is set so that $\text{Eff}(\hat\mu)$ is reasonably close to
+one. The standard default is to assume a normal model and set
+$\text{Eff}(\hat\mu)=0.95$. This leads to $k=1.345$ for Huber's $\rho$ and $k=4.685$ for Tukey's. Unless otherwise stated, these values are used for the applications in this dissertation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{M-estimators of Scale}
+\label{sec:Mscale}
+%%%%%%%%%%%%%%%%%%%%%%%%
+$M$-estimation naturally extends the scale model
+\begin{equation}
+\label{scaleMod}
+y_i= \sigma\epsilon_i, \ \ i=1,\dots, n,
+\end{equation}
+where $\epsilon_i$ are independent identically distributed with
+density $f_0$ and $\sigma>0$ is the unknown parameter. Then
+$y_i$ come from a scale family with density $f_\sigma(y)=
+\frac{1}{\sigma}f_0(\frac{y}{\sigma})$. %The MLE of $\sigma$ is
+%\begin{equation}
+%\label{mleSigma}
+%\hat\sigma= \arg \min_\sigma \prod_{i=1}^n
+%\frac{1}{\sigma}f_0\left(\frac{y_i}{\sigma}\right)
+%\end{equation}
+The M-estimator for $\sigma$ is defined through the estimating equation
+\begin{equation}
+\label{eq:Msigmachi}
+ \sum_{i=1}^n\chi \left(\frac{y_i}{\sigma}\right)=0,
+\end{equation}
+for some function $\chi$. Taking $\chi(x)=-x\frac{f'_0(x)}{f_0(x)}-\delta$ for $\delta=1$ corresponds to the MLE. This reduces to $\chi(x)=x^2-1$ for the standard normal yielding the estimate
+$\hat\sigma= \sqrt{\frac{1}{n}\sum{y_i^2}}$. Using the same idea as in
+the location case, a different $\chi$ can be chosen in an effort to achieve a robust estimate of
+ $\sigma$.
+ %for a given distribution
+%$F$, the estimate $\hat\sigma$ from \eqref{eq:Msigmachi}
+%converges in probability to the value $\sigma_0$ that satisfies
+%$E_{F}[\chi(\frac{x}{\sigma_0})]=\int\chi(\frac{x}{\sigma_0})\
+%dF=0$.
+\cite{huber1964} proposed the choice 
+\begin{equation}
+\label{HuberScale}
+\chi(x)=
+\begin{cases}
+x^2-\delta, &\ |x|\leq k\\
+k^2-\delta, &\ |x|> k .
+\end{cases}
+\end{equation}
+ For consistency when $F$ is
+$N(0,\sigma^2)$ we need $E_{\Phi}[\chi({x})]=\int\chi({x})\
+d\Phi=0$ where $\Phi$ is the standard normal distribution. This
+yields $\delta\approx 0.71016$ for the $\chi$ in \eqref{HuberScale}. For convenience,
+$k$ is often set to $1.345$, the value giving $95\%$ efficiency at the normal for
+Huber's location estimator. This is often
+referred to as Huber's `Proposal 2'.
+
+Another popular choice is the step function
+\begin{equation}
+\label{madchi}
+\chi(x)=I(|x|>c)-\delta.
+\end{equation}
+Fixing $\delta=0.5$ yields the aforementioned \textit{rescaled
+median absolute deviation}, written here as $\hat\sigma=K(\text{Med}(|x|))$ with $K=1/c$.
+%This is the  Recall, putting $K=1/\Phi^{-1}(3/4)\approx1.4826$ results in a constant estimator for $\sigma$ under normality.
+%Again $$ is typically chosen forconsistency at an assumed model which yields $c=0.6745$ for thenormal.
+%Still another option for robustness is Tukey's bisquare \eqref{Tukey} with $k=1$
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simultaneous M-estimators of Location and Scale}
+\label{sec:MlocScale}
+%%%%%%%%%%%%%%%%%%%%%%%%
+There are many ways to define $M$-estimates for multiple
+parameters but for convenience we concentrate on
+\textit{simultaneous estimators}. We first consider the location
+and scale setting
+\begin{equation}
+\label{locScaleMod}
+y_i= \mu+\sigma\epsilon_i, \ \ i=1,\dots, n,
+\end{equation}
+where $\epsilon_i$ are independent identically distributed with
+density $f_0$, $\mu$ and $\sigma>0$ unknown and $y_i$ has density $f(y)=\frac{1}{\sigma}f_0(\frac{y-\mu}{\sigma})$. Combining the equations in \eqref{MpsiLoc}
+and \eqref{eq:Msigmachi}, the simultaneous M-estimators of
+location and scale are the solutions to
+\begin{equation}
+\label{simM}
+\begin{aligned}
+&\sum \psi \left(\frac{y_i-\hat\mu}{\hat\sigma}\right)=0\\
+&\sum \chi \left(\frac{y_i-\hat\mu}{\hat\sigma}\right)=0.
+\end{aligned}
+\end{equation}
+
+The extension of $M$-estimators to linear regression is
+straightforward. Consider the standard regression model
+\begin{equation}
+\label{regM}
+y_i=\bx_i'\bbeta+\epsilon_i,
+\end{equation}
+where $\epsilon_i$ are independent random variables with mean zero and variance
+$\sigma^2$, $\bx_{i}\in\mathbb{R}^{p}$ is a vector of predictors, and  $\bbeta\in\mathbb{R}^{p}$ is a vector of regression parameters. The simultaneous M-estimators of $\bbeta$ and
+$\sigma$ are defined by
+\begin{equation}
+\label{simMreg}
+\begin{aligned}
+&\sum \psi
+\left(\frac{y_i-\bx_i'\widehat\bbeta}{\hat\sigma}\right)\bx_i=\mathbf{0}\\
+&\sum \chi \left(\frac{y_i-\bx_i'\widehat\bbeta}{\hat\sigma}\right)=0.
+\end{aligned}
+\end{equation}
+Common $\psi$ functions include Huber's and Tukey's mentioned earlier and common
+$\chi$ functions appear in \eqref{HuberScale} and \eqref{madchi}.
+Assuming the distribution of the errors is $F$, under standard conditions for $\psi$, $\chi$, the general result is again
+$\widehat\bbeta\overset{p}\rightarrow\bbeta_{0}$ and
+$\hat\sigma\overset{p}\rightarrow\sigma_{0}$ where $\bbeta_{0}$ and
+$\sigma_{0}$ satisfy
+\begin{equation}
+\label{ExpMreg}
+\begin{aligned}
+& E_F \psi
+\left(\frac{y_i-\bx_i'\bbeta_{0}}{\sigma_{0}}\right)\bx_i=\mathbf{0}\\
+& E_F \chi \left(\frac{y_i-\bx_i'\bbeta_{0}}{\sigma_{0}}\right)=0.
+\end{aligned}
+\end{equation}
+Further, the estimates are jointly asymptotically normal with a
+covariance matrix depending on the $\psi$ and $\chi$ functions.
+
 \bibliographystyle{ba}

### 2019-06-14 revision_2/code/data_analysis/3_hier_reg_analysis.R

@@ -98,6 +98,10 @@ analysis_data <- analysis_data %>%
   filter(!State %in% c('14', '30')) %>% 
   mutate(State = droplevels(State))
 
+# analysis_data %>%  group_by(State) %>% 
+#   summarize(sd1 = sd(Associate_Count), u1 = length(unique(Associate_Count)),  sd2 = sd(Office_Employee_Count),
+#             u2 = length(unique(Office_Employee_Count)),
+#             n())
 
 #defined globally.
 nGroups <<- length(unique(analysis_data$State))

### 2019-06-14 revision_2/code/data_analysis/4_summarize_hier_reg_analysis.R

@@ -210,8 +210,13 @@ average_by_state <- left_join(average_by_state, state_count, by = 'State') %>% u
 
 
 theme_set(theme_bw(base_family = 'Times'))
-ggplot(average_by_state  %>% filter(`Trimming Fraction` == '0.3', Model %in% c('Restricted - Tukey', 'Rlm - Tukey')), aes(x = `State(n)` , y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(y = "Average TLM")#+ scale_y_log10()
+ggplot(average_by_state  %>% filter(`Trimming Fraction` == '0.3', Model %in% c('Restricted - Tukey', 'Rlm - Tukey'), State != '28'), aes(x = `State(n)` , y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(y = "Average TLM") #+ scale_y_log10() + 
 ggsave(file.path(getwd(), "..", "..", "figs", 'hier_ave_tlm_state.png'), width = 7.5, height = 5)
+
+
+theme_set(theme_bw(base_family = 'Times'))
+ggplot(average_by_state  %>% filter(`Trimming Fraction` == '0.3', Model %in% c('Restricted - Huber', 'Rlm - Huber'), State != '28'), aes(x = `State(n)` , y = mean, col = Model, group = Model)) + geom_point(position = position_dodge(width = .5))  + geom_errorbar(mapping = aes(ymin = mean - sd, ymax = mean + sd), width = 0.05, position  = position_dodge(width = .5), linetype = 1) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(y = "Average TLM") #+ scale_y_log10() + 
+ggsave(file.path(getwd(), "..", "..", "figs", 'hier_ave_tlm_state_huber.png'), width = 7.5, height = 5)
 
 
 
[…]

### 2019-06-14 revision_2/code/simulation/simulation_many_p/1_simulation.R

@@ -6,19 +6,19 @@ library(brlm)
 library(MCMCpack)
 
 #Simulation Parameters ----- 
-n_sims <- 50
+n_sims <- 30
 n <- 500 #sample size
 p <- 3 #active covariates
-p_extra <- 20 - p #inactive covariates
+p_extra <- 30 - p #inactive covariates
 a_0 <- 5
 b_0 <- 5 
 prob_outlier <- .1
-outlier_contam <- 10
-mu_0 <-  rep(0, p+p_extra)
+outlier_contam <- 25
+mu_0 <-  rep(0, p + p_extra)
 prior_sd <- seq(.2, 1, by = .2) 
 # Sigma_0 = diag(p+p_extra),
 nkeep <- 1000
-nburn <- 2000
+nburn <- 1500
 maxit <- 1000
 nu <- 5 #df for t_fit
 
@@ -37,7 +37,7 @@ data_generation <- function(n, p, p_extra,
   y <- sapply(expected, function(mn){
     outlier <- rbinom(1,1, prob_outlier)
     err <- if (outlier) {
-      rnorm(1, 0, sd = sqrt(vr_out))
+      abs(rnorm(1, 0, sd = sqrt(vr_out)))
     } else {
       rnorm(1, 0, sd = sqrt(sigma2))
     }
@@ -52,26 +52,44 @@ data_generation <- function(n, p, p_extra,
 }
 
 #marginal computations ----
-get_marginal_rest <- function(y_gen, X_gen, mcmc){
+get_marginal_rest <- function(y_gen, X_gen, mcmc, point_est = FALSE){
   samps_coef <- t(mcmc[, 1:ncol(X_gen)])
-  mns <- X_gen%*%samps_coef
   samps_sigma <- as.numeric(mcmc[, (ncol(X_gen) + 1)])^0.5
+  if(!point_est){
+  mns <- X_gen %*% samps_coef
   sds <- matrix(samps_sigma, ncol = nkeep, nrow = nrow(X_gen),
                 byrow = TRUE) 
   
   pdfs <- dnorm(y_gen, mns, sds)
-  log(rowMeans(pdfs))
+  out <- log(rowMeans(pdfs))
+  } 
+  if(point_est){
+    post_mean_betas <- apply(samps_coef, 1, mean)
+    post_mn <- X_gen %*% post_mean_betas
+    post_mean_sigma <- mean(samps_sigma)
[…]

### 2019-06-14 revision_2/response/response.tex
continue edits to paper. need to polish second simulation

@@
 
-\response{This is an astute observation - we have added the following text after Theorem 4.6:
+\response{This is an astute observation - we have added the following text after Theorem 3.6:
 
-`This proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
-For all the examples in the paper we defined $p(z^{*})$ to simply be the uniform distribution on the $\mathbb{S}$.
-The advantage of this choice requires no further tuning parameters and we have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with reasonable probabilities.
-Additionally, with a long enough chain, the uniform start will cover the entirety of the plausible range of the transformation'
+`The proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
+For all the examples in the paper we defined $p(z^{*})$ to simply be the uniform distribution on $\mathbb{S}$.
+The advantage of this choice is that it requires no further tuning parameters and we have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with reasonable probabilities.
+To implement in practice, we simply generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$.
+Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$.
+Using simple algebra and conditions \ref{regEq}-\ref{scaleEq2Reg}, one can show $h(\cdot)$ is invariant to this projection and scaling.
+Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk.
+As we are proposing values on a complex manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$.
+This could provide some advantages in some situations, though we have yet to run into any serious issues with convergence using the independent proposal we utilize here.'
 
-As stated - we have not run into into the inefficiency issues here that you bring up.
-Additionally, note that a random walk on the manifold is not straightforward.
-It would be impossible to just move a single component of $z^{*}$ at a time since any single move would move the point off of the manifold.
-Hence, proposals would have to be in groups anyway, and random deviations of one component would affect the feasible moves of the other components.
 We do agree - that there could be cases where our choice is not optimal and more research would be need to explore this.
+Given the we are generating on a manifold, it's not entirely clear the best way to conduct an random walk - we offered a potential solution that would take additional effort to explore
 }
@@
 The real data examples now contains a hierarchical example with more covariates.
-Additionally, we have included a second simulation where the fitting model is a linear regression with 20 covariates and only 3 of them are active.}
+Additionally, we have included a second simulation where the fitting model is a linear regression with many covariates and only 3 of them are active.
+Additionally there is some correlation between some of the covariates - making it a more realistic variable selection-type problem.}
 
@@
 
-\response{We fill the main benefits are in situations where the analysis involves substantial prior information.
-We agree that the additional computational burden is not worth it in situations where the amount of data overwhelms the prior, for exactly the reasons you state.
-We have added the following to the introduction of the paper:
+\response{We have added the following to the introduction of the paper to address this comment:
 
-`The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
-The main advantages we have found so far come in situations we outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
-This is because, as with many traditional posteriors, the restricted likelihood posterior tends to the classical estimates as sample size grows.
+\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
+One conceptual advantage is that inferences and predictions are less sensitive to features of the data not captured by
+the conditioning statistics.
+Choosing statistics targeting main features of interest allows for more targeted inference on these features.
+The analysis can help to better understand other features, such as outliers, not capture by the conditioning statistics.}
+\response{The examples in the paper suggest advantages in situations where outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
 The main disadvantage over traditional robust estimate techniques are mainly computational.
-In Section 4 we detail a data-augmented MCMC algorithm to fit the models proposed in this paper.
+In Section ~\ref{BayesLinMod} we detail a data-augmented MCMC algorithm to fit the models proposed in this paper.
 This requires an additional computational step for each iteration of the chain.
-Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden'
+Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden.
+Since it is typically that the restricted likelihood posterior converges to the same expected value as the conditioning statistics as the sample size grows, it may not be practical to implement our method in all situations.}
 
@@
 
-\response{Thank you for this is an interesting idea that we have not thought about before.
+\response{Thank you for this is an interesting idea.
 We point out here, that  the example you gave does not satisfy all of C1-C8.
-For example, C5 is not satisfied with ridge regression $\hat\beta = (X'X +\lambda I)^{-1} X'y$ so that  $(X'X +\lambda I)^{-1} X'(y + Xv) \neq (X'X +\lambda I)^{-1} X'y + v$.
-Thus, new computational capabilities would have to be developed to explore this idea in substantial examples and we feel that would be worthy of another paper in the future.
+For example, C5 is not satisfied with ridge regression where $\hat\beta = (X'X +\lambda I)^{-1} X'y$:   $(X'X +\lambda I)^{-1} X'(y + Xv) \neq (X'X +\lambda I)^{-1} X'y + v$.
+Thus, new computational capabilities would have to be developed to explore this idea in substantial examples and we feel that would be worthy of another paper.
 
@@
 Again - a reason for further research.
-We have included some of this commentary in the discussion.
-
 }
@@
 In many real applications, learning the heterogeneity of the good and bad samples is precisely the goal of statistical data analysis.
-For the insurance example analyzed in Sec 6, the authors should provide ev- idence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.
+For the insurance example analyzed in Sec 6, the authors should provide evidence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.
 
-\response{
-We did not intend to mislead that we only want to predict the good portion of the data.
-Identification of outliers is also of concern and robust methods are well known to help identify outliers.
-As our method offers robust estimation of the the 'good' part of the model, it can also be used to identify outliers by, for example, examining residuals.
-In this sense, we feel we have provided several examples (in Section 2 under 'Examples' as well as through the simulations and the real data analysis).
+\response{We agree that understanding the heterogeneity in the data is often of concern and this is actually a reason to use robust regression methods.
+Our argument is that it is not always possible to build a complete model for both `good' and `bad' portions of the data.
+As we stated in our abstract - the method is intended to reduce `the
+sensitivity of the analysis to features of the data not captured by
+the conditioning statistics' (which, in a broad sense is the main argument for robust methods).
+For example, if outliers govern the inference, they will be less likely to be identified;  the proposed model will treat them as 'good' data and inferences will be distorted as a result.
+Comparing distorted predictions to new data will make it less likely to identify new outliers.
+So - in this sense, it seems obvious that (ii) is indeed often the case.
+If we can't (as we argue) build a perfect model for the outlying generating process, we will be better prepared to identify current and future outliers only if we can predict the good portion of the data well.
 
-Several changes to address your valid concerns include:
+We have added the following to the introduction to address part of this comment:
+\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
+One conceptual advantage is that inferences and predictions are less sensitive to features of the data not captured by
+the conditioning statistics.
+Choosing statistics targeting main features of interest allows for more targeted inference on these features.
+The analysis can help to better understand other features, such as outliers, not capture by the conditioning statistics.}
 
-In the introduction:
-`In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study.
-\textit{By this definition, outliers are spurious however, identifying them so that better inference of the phenomenon under study is of importance}'.
-
-For the real data example: 
-The goal for the insurance example was derived from personal collaborations and we do not know of specific literature. However we have provided more detail of the goal.
-
+For the real data example: The goal for the insurance example was derived from personal collaborations and we do not know of specific literature. However we have provided more detail of the goal. 
 \response{It is of concern to the company to predict closures and future performance for agencies that remain open.
 It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies.
-Additionally, robust methods are more likely to identify such agencies.
 Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.}
@@
 \item As a methodological paper, what’s the guideline/recommendation given by the authors? After reading this paper, I don’t know how to apply the suggested framework
-on a simple regression model. Apparently, the choice of the likelihood func-
-tion (for the good data) f(·|?) and the choice of the statistic T are related.
+on a simple regression model. Apparently, the choice of the likelihood function (for the good data) $f(y|\theta)$ and the choice of the statistic T are related.
 To make things more complicated, each has multiple choices.
@@
 
-\response{This is valid input. We have taken the following steps:
+\response{Thanks for pointing out this need. We have taken the following steps:
 
@@
 We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers.
-For this reason we offer a quick review of these estimators in the Supplementary Material.}
+A short review of these estimators is provided in the Supplementary Material.}
  \item Included a review of M-Estimators in the Supplement
@@
 hand, the proposed MCMC algorithm is computationally expensive. In Sec
-4.2, the authors only discussed the computation cost for their proposal dis- tribution, but ignored the computation cost for obtaining T(y) (see Theorem 4.1).
+4.2, the authors only discussed the computation cost for their proposal distribution, but ignored the computation cost for obtaining T(y) (see Theorem 4.1).
 Those statistics are M-estimators, i.e., they are maximizers of some objective functions involving n observations and p parameters.
@@
 `
-Finally, we mention that in addition to the additional computation already mentioned, it is clear that the estimators themselves have must be computed for every iteration of the Markov Chain.
-We have found this burden to be marginal in with respect to computing the needed Jacobian.
-In the simulations and real data analyses presented below, we will see that the additional burden is of added value in situations where substantial prior information is available that is not swamped by current data.
+\response{Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
+We have found this burden to be marginal in relation with respect to computing the needed Jacobian.
+In the simulations and real data analyses presented below, we will see that the additional burden is often of added value over traditional robust regression when substantial prior information is available that is not swamped by current data.}
 `
-Additionally we have included a paragraph in the introduction discussing advantages and disadvantges in response to a similar comment from the other reviewer.
+Additionally we have included a paragraph in the introduction discussing advantages and disadvantages.
 }
 
-\item The authors compare KL diver- gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y|M,yobs) is not available in closed-form; 2) since f(y|M,yobs) is not available close-form, the KL divergence is approximated and it’s not clear to me how accurate the approximation is.
+\item The authors compare KL diver-gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y|M,yobs) is not available in closed-form; 2) since f(y|M,yobs) is not available close-form, the KL divergence is approximated and it’s not clear to me how accurate the approximation is.
 The authors should compare prediction and estimation accuracy, common met- rics used for regression models.
@@
 which combines estimation error for both the $\theta_{i}$ and $\sigma$.
-For this simulation, estimation of $\theta_{i}$ is analogous to prediction.
 While we couldn't compute this metric in a real analysis since we wouldn't know the $\theta_{i}$ and $\sigma$, we feel it is best to make this direct comparison since we know them in the simulation.}
@@
 
-\subsection{Some minor issues.}
+\textbf{Some minor issues.}
 \begin{enumerate}
@@
 and propose a new method as an alternative.” The proposed method cannot handle “model misspecification”, instead it assumes f is the true model (no misspecification) and what’s wrong is part of the data.
+
+\response{We are taking a different view: the 'true' model would also have the correct model for the outliers or any other type of misspecification.
+$f$ is only a model for part of the overall data generating mechanism - hence, even it were exactly correct for this part, we would still have model misspecification}
+
 \item  Sec 2 and Sec 3 can be shortened or merged.
-\response{We have merged the sections and moved one of the illustrative examples to the Supplement}
+\response{We have merged the sections.}
 
@@
 \item  Eq (18): change dy to d$\tilde{y}$?
-\response{Thanks for noticing this typo - based on the another reviewers comment we are using a different metric then KL divergence and so this equation is no longer in the paper.}
+\response{Thanks for noticing this typo - based on your other comment we are using a different metric then KL divergence and so this equation is no longer in the paper.}
 
@@
 
-\response{WILL TONE DONE THE MODEL MISSSPECIFICATION STUFF}
+\response{HOW TO ADDRESS?}
 
@@
 
-\response{Thank you - we believe we have address each of these concerns based on the the 2 reviewer's comments. Detailed responses are given above}
+\response{Thank you - we believe we have addressed each of these concerns based on the the 2 reviewer's comments. Detailed responses are given above}
 
@@
 
-\response{We have included default choices in the paper and in the Supplement.
-We have included information for where to obtain code on Github (an R package as well as data and code for the examples) at the end of the Introduction}
+\response{We have included a default choices in the paper and in the Supplement.
+Information for where to obtain code on Github (an R package as well as data and code for the examples) is now provided in the Introduction}
 
@@
 \response{we believe we have addressed similar concerns from the two reviewers - specifically we have included in several areas the advantages and disadvantages (e.g., see Introduction) we have found as well as practical recommendations (e.g.
-See Supplement)
+See Supplement)}
 
@@
 
-\response{MUST ADDRESS STILL}
+\response{HOW TO ADDRESS?}
 
@@
 
-\section{Editor Comments}
+\section{Editor Comments} \response{unknown response at this point ???}
 

### 2019-06-14 revision_2/paper.tex
continue edits to paper. need to polish second simulation

@@
 Concern about the loss function is reflected in, for example, the extensive literature on Bayesian hypothesis tests \citep{kass1995}.
-%This work focus on the likelihood.
-% sampling density has been given less attention from a specificallyBayesian view, although the work on predictive diagnostics \citep{box1980} departs from classical traditions.
-
 The focus of this work is the development of techniques to handle imperfections in the likelihood $f(\by|\bth) = L(\bth|\by)$.
@@
 In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study.
-\response{By this definition, outliers are spurious however, identifying them so that better inference of the phenomenon under study is of importance}.
 There are three main solutions to Bayesian outlier-handling.
@@
 \response{The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
-The main advantages we have found so far come in situations we outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
-This is because, as with many traditional posteriors, the restricted likelihood posterior tends to the classical estimates as sample size grows.
+One conceptual advantage is that inferences and predictions are less sensitive to features of the data not captured by
+the conditioning statistics.
+Choosing statistics targeting main features of interest allows for more targeted inference on these features.
+The analysis can help to better understand other features, such as outliers, not capture by the conditioning statistics.}
+\response{The examples in the paper suggest advantages in situations where outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
 The main disadvantage over traditional robust estimate techniques are mainly computational.
@@
 This requires an additional computational step for each iteration of the chain.
-Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden}
+Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden.
+Since it is typically that the restricted likelihood posterior converges to the same expected value as the conditioning statistics as the sample size grows, it may not be practical to implement our method in all situations.}
 
@@
 
-\subsection{An Illustrative Example}
+\subsection{Illustrative Examples}
 \label{illustrations}
 Before discussing computational details, the method is applied to two simple examples on well known data sets to demonstrate its effectiveness in situations where outliers are a major concern.
-The first example is presented here, with the second provided in the Supplementary Material.
 The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}.
-%Specific details are left to the Appendix.
-
 The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
@@
 We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers.
-For this reason we offer a quick review of these estimators in the Supplementary Material.}  The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+A short review of these estimators is provided in the Supplementary Material.}  The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
 Two additional approaches to outlier handling are considered: 1) the normal distribution is replaced with a t-distribution and, 2) the normal distribution is replaced with a mixture of two normals.
@@
 
-%The posteriors of $\beta$ under each model appear in Figure \ref{fig:newcomb_post}.
-As expected, the posterior under the normal model is pulled downward by the two outliers while the heavy-tailed model provides robustness against them.
-The restricted likelihood methods using the M-estimators and LTS statistics also achieve robustness against the outliers.
-Conditioning on LMS however, results in a posterior similar to the one under the normal model.
-The M-estimators provide the most precise posteriors in this case.
-This is reflected in more precise predictions than the heavy-tailed and mixture model as illustrated by the predictive distributions also shown  in  Figure \ref{fig:newcomb_post}.
 The posterior of $\beta$ under each model appears in Figure \ref{fig:newcomb_post}.
@@
 \end{figure}
-
 The pattern for predictive distributions differs (see bottom plot in Figure \ref{fig:newcomb_post}).
@@
 
-Overall, we find that the restricted likelihood methods based on M-estimators provide the most attractive analysis for these data.
+%Overall, we find that the restricted likelihood methods based on M-estimators provide the most attractive analysis for these data.
 They provide sharp and appropriate inference for parameters ($\beta$) and for prediction.
@@
 
+As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
+The outliers in this case are due to a change in measurement units on which calls were recorded for part of the data set.
+Specifically, for years 1964-1969 and parts of 1963 and 1970, the length of calls in minutes were recorded rather than the number of calls \citep{rousseeuw1987}.
+The full model is a standard normal Bayesian linear regression:
+\begin{equation}
+{\boldsymbol{\beta}}\sim N_{2}(\boldsymbol{\mu}_{0}, \boldsymbol{\Sigma}_{0}),\  \sigma^{2} \sim IG(a, b),\  \by \sim N(X\boldsymbol{\beta}, \sigma^{2} I),
+\end{equation}
+where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and $X$ is the $n\times 2$ design matrix with a vector of 1's in the first column and the year covariate in the second.
+\response{In reality, the model should include a different piece for the part of the data with different units.
+The outliers are really just a manifestation of model misspecification.} Prior parameters are fixed via a maximum likelihood fit to the first 3 data points.
+In particular, the prior covariance for $\bbeta$ is set to $\Sigma_{0} = g\sigma_{0}^2 (X_{p}^{\top}X_{p})^{-1}$, with $X_{p}$ the $3\times 2$ design matrix for the first $3$ data points, $g=n=21$, $\sigma_{0} = 0.03$ and $\boldsymbol{\mu}_{0} = (1.87,  0.03)^{\top}$.
+This has the spirit of a unit information prior \citep{kass1995reference} but uses a design matrix for data not used in the fit.
+Finally $a = 2$ and $b =1$.
+
+Four models are compared: 1) the normal theory base model 2) a two component normal mixture model, 3) a t-model, and 4) a restricted likelihood model conditioning on Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
+Each model is fit to the remaining 21 data points.
+The normal theory model is also fit a second time after removing observations 14-21 (years 1963 - 1970).
+The omitted cases consist of the obvious large outliers as well as the two smaller outliers at the beginning and end of this sequence of points caused by the change in measurement units.
+The mixture model allows different mean regression functions and variances for each component.
+Both components have the same, relatively vague priors.
+The probability of belonging to the first component is given a $\text{beta}(5,1)$ prior.
+The heavy-tailed model fixes the degrees of freedom at 5 and uses the same prior on $\bbeta$.
+The prior on $\sigma^2$ is adjusted by a scale factor of $3/5$ to provide the same prior on the variance.
+
+The data and  $95\%$ credible bands for the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}.
+The normal model fit to all cases results in a very wide posterior predictive distribution due to an inflated estimate of the variance.
+The t-model provides a similar predictive distribution.
+The pocket of outliers from 1963 to 1970 overwhelms the natural robustness of the model and leads to wide prediction bands.
+The outliers, falling toward the end of the time period, lead to a relatively high slope for the regression.
+In contrast, the normal theory model fit to only the good data results in a smaller slope and narrower prediction bands.
+The predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit to the non-outlying cases.
+The two component mixture model provides similar results, where the predictive distribution is formulated using only the good component.
+For these data, the large outliers are easily identified as following a distinct regression, leaving the primary component of the mixture for non-outlying data.
+In a more complex situation where the outlier generating mechanism is transient (i.e., ever changing and more complex than for these data), modeling the outliers is more difficult.
+As in classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
+\begin{figure}[t]
+\centering
+{\includegraphics[width = 4in]{figs/calls_predictive.png}}
+\caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
+The first three data points were used to specify the prior with each model using the remaining 21 for fitting.
+The normal theory model was also fit after removing observations 14-20 (years 1963 - 1970).}
+\label{fig:calls_predictive}
+\end{figure}
+
 \section{Restricted Likelihood for the Linear Model}
 \label{BayesLinMod}
-
 The simple examples in the previous section highlight the beneficial impact of a good choice of $T(\by)$ with the use of the restricted likelihood.
@@
 model with a standard formulation: 
-%\begin{eqnarray}
-%\label{LinearModel}
-%\bbeta & \sim & \pi_1(\bbeta); \qquad \sigma^2  \sim  \pi_2(\sigma^2)
-%\nonumber\\
-%y_i  & =  & x_i^\top \bbeta + \epsilon_i , \mbox{ for } i = 1, \ldots, n 
-%\end{eqnarray}
 \begin{eqnarray}
@@
 Throughout, observed data and summary statistic is denoted by $\by_{obs}$ and $T(\by_{obs})=(\bb(X, \by_{obs}), s(X, \by_{obs}))$, respectively.
-% In particular, we demonstrate the method using simultaneous M-estimators defined by \eqref{Mest} for the one-sample setting and easily extended to the linear model in \eqref{LinearModel}.
-The estimator of the \green{regression} coefficients is denoted by $\bb(X, \by)\in \mathbb R^{p}$ and that of the scale by \green{\sout{$s(X, \by)\in \mathbb R$} $s(X, \by)\in \{0\} \cup {\mathbb R}^+$} .
-Thus, $T(\by)=(\bb(X, \by), s(X, \by))$.
 Several conditions are imposed on the model and statistic to ensure validity of the MCMC algorithm:
@@
 and \textit{scale equivariance}. 
-Many estimators satisfy the above properties, including several traditional simultaneous M-estimators \citep{huber2009, maronna2006} for which the R package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC described here.
-\response{These M-estimators satisfy C3 and C4 since they are optimizers of (almost surely) continuous and differentiable objective functions.
-Constraints C5-C8 are often satisfied by location and scale estimators but should be checked on a case by case basis.}  Further software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
-The package also implements the direct computational methods described in \cite{lewis2014}.
+Many estimators satisfy the above properties, including several traditional simultaneous M-estimators \citep{huber2009, maronna2006} for which the \texttt{R} package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC described here.
+\response{These M-estimators satisfy \ref{asb}-\ref{as} since they are optimizers of (almost surely) continuous and differentiable objective functions.
+Constraints  \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}  More software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
+The current version of the \texttt{R} package also implements the direct computational methods described in \cite{lewis2014}.
 These methods are effective in lower dimensional problems and were used in both examples in Section \ref{illustrations}.
@@
 
-%As examples, a normal
-%prior distribution and normal likelihood in the regression setting
-%allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
-%leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
-%in the style of the hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
-%$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
-%a scale parameter for each case and an extra stage where these scale parameters are generated.
-
-%\green{Alternative algorithms substitute other generations for the full conditionals, such as the Metropolis-Hastings propose and accept/reject framework.
-Our algorithms are based on the decomposition of the MCMC algorithm into conventional full data sampling steps where $\bth$ is generated given $\by$, and steps that allow us to complete the data set where $\by$ is generated given $\bth$ and $T(\by)$.
-The latter generation relies on the conditioning set $\mathcal{A}=\{\by\in \mathbb{R}^n|T(\by)=T(\by_{obs})\}$.
-The set $\mathcal{A}$ may contain more than one element (i.e., it is not degenerate) when $T(\by) : \by \rightarrow T(\by)$ is not a $1-1$ function.}
-
-%The other stage in the Gibbs sampler is the generation of complete data from the full conditional  $f(\by|\bth, T(\by)=T(\by_{obs}))$.
-%Condition \ref{supReal} above facilitates the extension of convergence proofs for the complete data algorithm to those for the incomplete data algorithm.
-%In this subsection, we focus exclusively this stage. 
-%we begin with any conventional complete data algorithm.  In the case of typical regression models, these algorithms abound.  Details of the algorithm depend on details of
-%the prior distribution and sampling density.  As examples, a normal
-%prior distribution and normal likelihood in the regression setting
-%allow one to alternate conditional generations of $\sigma^2$ and $\bbeta$, and blocking the generation of $\bbeta$ generally
-%leads to quicker convergence and mixing \citep{liu1994}; a thick-tailed scale mixture of normal distributions
-%in the style of the 
-%hyper-$g/n$ prior \citep{liang2008} necessitates an additional stage for the sampler where the scale 
-%$g/n$ is generated; a thick-tailed sampling density such as a $t$ distribution can be handled with the addition of 
-%a scale parameter for each case and an extra stage where these scale parameters are generated.  
-%The additional stage needed to implement the incomplete likelihood analysis via MCMC 
-%is a generation of the complete data given statistic ($T(\by_{obs})$) and parameter ($\bth$).
-Condition \ref{supReal} facilitates the extension of convergence proofs for the complete data algorithm to those for the incomplete data algorithm.
-%In this subsection, we focus exclusively on the additional stage
-%where we generate $\by | \bth, T(\by)$.  
 For a typical model and conditioning statistic, the second full conditional $f(\by|\bth, T(\by)=T(\by_{obs}))$ %\blue{ =f(\by|\bth, \by\in\mc A)}$ 
@@
 \end{eqnarray}
-%In the above expression, the second line follows from the first for
-%the following reason. The proposed \green{vector $\by$} is sampled from
-%  $\mathcal{A}$ so that
-%$T(\by_{p})=T(\by_{c})=T(\by_{obs})$. This implies 
-%\green{\sout{$f(\by |\bth,
-%T(\by)=T(\by_{obs}))=f(\by |\bth)\pi(\bth)/\red{f[?]}\pi(\bth, T(\by)=T(\by_{obs}))$}
-%\begin{eqnarray}
-%f(\by |\bth,\by \in \mathcal{A})) & = & \frac{f(\by | \bth) \pi(\bth) I(\by \in \mathcal{A})}{\int f(\by | \bth) \pi(\bth) I(\by \in \mathcal{A}) d\bth}
-%\end{eqnarray}}
-%where $\by$ represents either $\by_{p}$ or $\by_{c}$. %Further, the expressions $\pi(\bth)$ and $\red{f[?]}\pi(\bth, T(\by)=T(\by_{obs}))$ 
-%\green{The expressions $\pi(\bth)$ and $\int f(\by | \bth) \pi(\bth) I(\by \in \mathcal{A})  d\bth$} are the same for $\by_{p}$ and $\by_{c}$ and cancel in the ratio.
-%Similar expansions can be made for the proposal distribution.
-%\green{Further, the indicator functions can be dropped since $\by_p$ and $\by_c$ will both fall in $\mathcal{A}$.}  
-%\green{Note:  Check this argument carefully}
+
 For the models we consider, evaluation of $f(\by | \bth)$ is straightforward.
@@
 \]
-\end{theorem}% (details are given in Theorem \ref{Transformation} below). Hence, to obtain $\by \in\mathcal A$, we proceed in two steps:
-%\begin{enumerate}
-%\item Sample $\bz^*\in \mathbb{R}^{n}$ from a known distribution (examples of which are described later).
-%\item Transform $\bz^*$ to $\by =h(\bz^*)$ using Theorem \ref{Transformation} so that $T(\by)=T(\by_{obs})$. 
-%\end{enumerate}
-% To 
-%obtain data $\by$ for which $T(\by) = T(\by_{obs})$, we proceed in two
-%steps.  
-%First, a vector $\bz^*$ is generated from a simple manifold with known
-%density, for example, a uniform distribution
-%on the surface of the unit sphere in ${\mathbb R}^{n-1}$ (alternatively from
-%the model with current values of $\beta$ and $\sigma$).  This leads to 
-%$T(\bz^*) = (b(X,\bz^*), s(X,\bz^*))$.  The vector $\bz^*$ is mapped into a vector
-%$\by$ by rescaling and shifting appropriately to match the observed conditioning statistic.  For typical estimators, the appropriate scaling is 
-%$s(X,\by_{obs}) / s(X,\bz^*)$ with the shift trailing along as needed to match $b(X,\by_{obs})$.  
-%To evaluate the proposal density of $\by$,
-%we need to adjust the density of $\bz^*$ with a Jacobian.  In the sequel, we use this artificially low-dimensional
-%example to illustrate the method.  
-%The strategy described in the previous paragraph extends to full-blown regression models.
-Robust regression methods lead naturally to a conditioning statistic in the form of a classical M-estimator for $\bbeta$
-%and a companion estimator for $\sigma$.  We denote the resulting estimator which involves the covariates through
-%the design matrix and the response 
-%as $T(\by) = (\bb(X,\by), s(X,\by))$, with $\bb(X,\by) = (b_1(X,\by), \cdots,
-%b_p(X,\by))^\top$.  Simultaneous M-estimators have a number of standard properties \ref{asb}-\ref{scaleEq2Reg} which
-%prove useful in the sequel \citep{huber2009, maronna2006}.  
-%\begin{itemize}
-%\labitem{C3}{asb}$\bb(X,\by)$ is almost surely continuous and differentiable with respect to $\by$.  
-%\labitem{C4}{as} $s(X,\by)$ is almost surely positive, continuous, and differentiable with respect to $\by$.  
-%\labitem{C5}{regEq} $\bb(X,\by+X\bv)=\bb(X,\by)+\bv \ \ \text{for  all}\ \bv\in\mathbb{R}^p$. 
-%\labitem{C6}{scaleEqReg} $\bb(X,a\by)=a\bb(X,\by)\ \ \ \text{for all constants } a$.  
-%\labitem{C7}{regIn} $s(X,\by+X\bv)=s(X,\by) \ \ \text{for all}\ \bv\in\mathbb{R}^p$.  
-%\labitem{C8}{scaleEq2Reg} $s(X, a\by)=|a|s(X,\by) \ \ \text{for all constants } a$.  
-%\end{itemize}
-%Properties \ref{regEq} and \ref{scaleEqReg} of $\bb$ are called
-%\textit{regression} and \textit{scale equivariance},
-%respectively.  Properties \ref{regIn} and \ref{scaleEq2Reg} of $s$ are called \textit{regression invariance}
-%and \textit{scale equivariance}. 
-%Many other estimators satisfy these properties, and our subsequent results apply equally
-%well to them.  With more cumbersome statements, the upcoming results can be adjusted to handle 
-%a relaxation of \ref{as} that 
-%%$s(X,\by_{obs}) > 0$ and $P(s(X,\by)>0)>0$.  
-%To understand the Jacobian calculation, we start with the following Theorem whose proof is in the appendix. 
-%%We have stated that any vector $\bz^{*} \in \mathbb{R}^n$ can be transformed to a proposal
-%%$\by$ satisfying $T(\by) = T(\by_{obs})$.  The properties above ensure
-%%that this can be done through the mechanism presented in the following theorem.  The proof of this and other results appear in the appendix.
-%\begin{theorem}
-%\label{Transformation}
-%Assume that conditions \ref{as}-\ref{scaleEq2Reg} hold.  Then, any vector $\bz^* \in \mathbb{R}^n$ with conditioning statistic
-%$T(\bz^*)$ for which $s(X,\bz^*) > 0$ can be transformed into $\by$ with conditioning statistic $T(\by) = T(\by_{obs})$ 
-%through the transformation 
-%\[
-%\by = h(\bz^*) := \frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^* + X\left(\bb(X,\by_{obs}) - \bb(X,\frac{s(X,\by_{obs})}{s(X,\bz^*)} \bz^*)\right) .  
-%\]
-%\end{theorem}
+\end{theorem}%
+
 \noindent Using the theorem, the general idea is to first start with an initial vector $\bz^*$ drawn from a known distribution, say $p(\bz^*)$, and transform via $h(\cdot)$ to $\by \in \mathcal{A}$.
@@
 the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$, a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
-%With $\bz^{*}\in \mathbb{S}$, $c\bz^{*} + X\bv$ is not (unless $c=1$ and $\bv = \mathbf{0})$; the scaling by $c$ and/or the affine transformation in the direction of $\mathcal{C}(X)$ takes the point off $\mathbb{S}$.
-The mapping $h: \mathbb{S} \rightarrow \mathcal{A}$ is one-to-one making the change of variables more feasible.
-%With the domain of $h(\cdot)$ restricted to  $\mathbb{S}$, the range is still the entirety of $\mathcal{A}$.
-This is important so that the support of the proposal distribution (i.e.
-the range of $h(\cdot)$) contains the support of the target  $f(\by | \theta, y\in \mathcal{A})$; a necessary condition for convergence of the Metroplis-Hastings algorithm (in this case the supports are both $\mathcal{A}$).
-To see that the range of $h(\cdot)$ is $\mathcal{A}$, consider any $\by \in \mathcal{A}$ and its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$.
-\footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).} It is easy to show that $\bz^{*} = Q\by/||Q\by|| \in \mathbb{S}$ and $h(\bz^{*}) = \by$.
+
 Given the one-to-one and onto mapping $h: \mathbb{S} \rightarrow \mathcal{A}$, the general proposal strategy is summarized as follows:
@@
 
-%The \green{unit} sphere from
-%which the initial sample is taken is depicted as the red circle in this plane.  In general, this is the unit sphere in the $n-p$ dimensional space $\mc{C}^\perp(X)$.  
-%With the domain of $h(\dot)$ restricted to the unit sphere in $\mathcal{C}^{\perp}(X)$, the range is still the entirety of $\mathcal{A}$.
-This is important so that the support of the proposal distribution (i.e.
-the $h(\dot)$) is at least as large as the support of the target  $f(\by | \theta, y\in \mathcal{A})$, which is  $\mathcal{A}$; a necessary condition for convergence of the Metroplis-Hastings algorithm.
-To see that the range of $h(\dot)$ is $\mathcal{A}$, consider the any $\by \in \mathcal{A}$ and its projection onto $\mathcal{C}^{\perp}(X)$: $Q\by$ where $Q = I - XX^{\top}$ \footnote{We have used condition \ref{fullRank} to assume  without loss of generality  that the columns of $X$ form an orthonormal basis for $\mc{C}(X)$ (i.e., $X^\top X=I$).}.
-It is easy to show that $\bz^{*} = Q\by/||Q\by||$ is on the unit sphere and $h(\bz^{*}) = \by$.
-%
-%
-%
-%To see this, note that the theorem shows that any $\by$ expressed as in the theorem is an element of $\mc A$.
-Further, any $\by \in \mc A$ can be expressed as in the theorem by simply replacing $\bz^{*}$ with $\by$.
-The set $\mathcal{A}$ is an $n - p - 1$ dimensional space:  there are $p$ constraints imposed by the regression coefficients and one further constraint imposed by the scale.
-The form of the set is determined by the statistic $T(\cdot)$.
-
-%As an example, Figure~\ref{fig:sampSpace} provides an artificial low-dimensional visualization of such a set for a location-scale model.
-In the figure, $n = 3$, and the conditioning statistic is $T(\by)=(\min(\by), \sum (y_i - \min(\by))^2)$.
-The set $\mathcal{A}$ is depicted for $T(\by_{obs})=(0,1)$ which we describe as a ``warped triangle'' in light blue, with each side corresponding to a particular coordinate of $\by$ being the minimum
-%value of zero.
-The other two coordinates are restricted by the scale statistic to lie on the quarter circle of radius one in the positive orthant.
-In general, this set may be compact and given by a closed
-%curve, as in the figure, or it may be unbounded, depending on the choice of $T(\by)$.  The other sets labeled in the figure will be described shortly.
-%
-
-%Further, this reduced space is chosen so that the range of the map is the entirety of $\mathcal{A}$.
-%The Jacobian does not cancel in \eqref{MHRatio}, since the scaling depends on the initial proposal.
-
-%The reduced space from which the initial sample is taken is simply the
-%unit sphere \green{\sout{restricted to} in} the orthogonal complement of the column space of the design matrix (i.e., the least squares residual space).
-To help understand the density of the proposal derived from the transformation of this initial sample we introduce the following notation.
-Denote the column space of the design matrix $X$ by $\mathcal{C}(X)$ and its orthogonal complement by $\mc{C}^\perp(X)$.
-%\green{\sout{This} The latter} is the least squares residual space which we will often refer to as the `deviation space'.  The projection of the set $\mathcal{A}$ onto the deviation space is 
-%\begin{equation}
-%\label{sampleSpacePerp}
-%\Pi(\mathcal{A})=\{\bz\in \mathbb{R}^n |\ \exists\ \by\in \mathcal{A}\
-%s.t.\ \bz=Q \by \}
-%\end{equation} 
-%where $Q$ is the projection matrix onto  $\mc{C}^\perp(X)$. Explicitly, $Q=I-H$ with $H=XX^\top$ where we assume, without
-%loss of generality following condition \ref{fullRank},  that the
-%columns of $X$ form an orthonormal basis for $\mc{C}(X)$
-%(i.e., $X^\top X=I$).
-It will also be helpful at times to write $Q=WW^{\top}$ where the columns of $W$ form an orthonormal basis for $\mc{C}^\perp(X)$.
-This set has been introduced because we will first transform the initial distribution on the sphere to the distribution on this set.
-Then we will transform to the \green{\sout{sample space} set} $\mc A$.
-
-%Returning to the artificial example, Figure~\ref{fig:sampSpace}
-%depicts $\Pi(\mathcal{A})$ as well as the sphere from which we obtain
-%the initial sample. The column vector $X=\bf{1}$ spans $\mc{C}(X)$ and
-%is shown as a reference. The triangle with bowed sides in dark
-%  blue is  $\Pi(\mathcal{A})$, the projection of $\mc A$ onto the
-%plane orthogonal to $\mb 1$ (i.e., $\mc{C}^\perp(X)$). The \green{unit} sphere from
-%which the initial sample is taken is depicted as the red circle in this plane.  In general, this is the unit sphere in the $n-p$ dimensional space $\mc{C}^\perp(X)$.  
-%
-%For the transformation of the initial proposal $\bz^*$ on the surface of the sphere to $\by\in \mc A$ , we first move to a point on $\Pi(\mathcal{A})$ through a 
-%simple scaling of $\bz^*$.  This is followed by undoing the projection with a move from 
-%$\Pi(\mathcal{A})$ to its (unique) preimage on $\mathcal{A}$. Together, these two steps correspond to the
-%transformation in Theorem~\ref{Transformation}.  The introduction of
-%the sphere in $\mc {C}^\perp (X)$ as the initial proposal surface
-%along with properties \ref{regEq}-\ref{scaleEq2Reg} ensure that the mapping is
-%1-1. In particular, property
-%\ref{scaleEq2Reg} ensures the scaling to be unique and \ref{regIn}
-%implies that the scale statistic is unchanged when undoing the
-%projection. Property \ref{regEq} ensures the uniqueness of undoing the
-%projection.  The general proposal strategy is summarized as follows:
-%\begin{enumerate}
-%\item Sample $\bz^*$ from a distribution with known density on the unit sphere in $\mc{C}^\perp(X)$.
-%\item Calculate the Jacobian of \green{the} transformation in Theorem \ref{Transformation} in two steps.
-%\begin{enumerate}
-%\item Scale from unit sphere to $\Pi(\mathcal{A})$: $\bz=\frac{s(X,\boldsymbol{y}_{obs})}{s(X, \boldsymbol{z}^{*})}\bz^{*}$
-%\item Shift  from $\Pi(\mathcal{A})$ to $\mathcal{A}$: $\by=\bz+X\left(\bb(X, \by_{obs})-\bb(X, \bz)\right)$
-%\end{enumerate}
-%\end{enumerate}
 %
@@
 orthogonal to the tangent vectors of $\Pi(\mc A)$ and the circle.
-%As stated above, the Jacobian is the ratio of infinitesimal lengths along these tangent vectors.
-This is the same as the ratio of the infinitesimal lengths of the normal vectors (i.e., $\cos(\gamma)$).
-This generalization extends to higher dimensions where the `lengths' along the tangent vectors become volumes along the tangent spaces.
-
-%\begin{sidewaysfigure}[t]
-%\centering
-%\captionsetup{justification=centering}
-%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace3.pdf}}\quad
-%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
-%\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
-%  to $\bz$. The adjustment for the stretch transforms the density
-%  along the unit circle to the density along the circle of radius
-%  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
-%  deformation from the distribution along the circle to the
-%  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
-%  be the cosine of the angle between the normals to each manifold.}
-%\label{fig:stretchDeform}
-%\end{sidewaysfigure}
 
@@
 \end{figure}
-
-%\begin{figure}[t]
-%\centering
-%{\includegraphics[width=2in]{minSSZSpace5.pdf}}
-%\label{fig:stretchDeform}
-%\caption{sdassfsadfda}
-%\end{figure}
-%%
-%\subcaptionbox{}{\includegraphics[width=4in]{minSSZSpace5.pdf}}
-%\caption{Panel (a) contains a depiction of the stretch from $\bz^{*}$
-%  to $\bz$. The adjustment for the stretch transforms the density
-%  along the unit circle to the density along the circle of radius
-%  $\|\bz\|$ (dashed circle).  Panel (b) contains a depiction of the
-%  deformation from the distribution along the circle to the
-%  distribution along $\Pi(\mathcal{A})$. The adjustment can be seen to
-%  be the cosine of the angle between the normals to each manifold.}
-%\label{fig:stretchDeform}
-%\end{sidewaysfigure}
 
@@
 \end{theorem} 
-
-\response{This proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
-For all the examples in the paper we defined $p(z^{*})$ to simply be the uniform distribution on the $\mathbb{S}$.
-The advantage of this choice requires no further tuning parameters and we have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with reasonable probabilities.
-Additionally, with a long enough chain, the uniform start will cover the entirety of the plausible range of the transformation.}
+\response{The proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
+For all the examples in the paper we defined $p(z^{*})$ to simply be the uniform distribution on $\mathbb{S}$.
+The advantage of this choice is that it requires no further tuning parameters and we have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with reasonable probabilities.
+To implement in practice, we simply generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$.
+Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$.
+Using simple algebra and conditions \ref{regEq}-\ref{scaleEq2Reg}, one can show $h(\cdot)$ is invariant to this projection and scaling.
+Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk.
+As we are proposing values on a complex manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$.
+This could provide some advantages in some situations, though we have yet to run into any serious issues with convergence using the independent proposal we utilize here.}
 
@@
 
-Second, the gradients of $\nabla s(X,\by), \nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$ are easily computed. For example, below we consider M-estimators defined by the estimating equations:
+Second, the gradients of $\nabla s(X,\by), \nabla b_1(X,\by),\dots, \nabla b_p(X,\by)$ are easily computed in many cases.
+For example, below we consider M-estimators defined by the estimating equations:
 \begin{eqnarray}
 \label{Mest}
- \sum_{i=1}^n \psi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)= & 0 \\
- \sum_{i=1}^n \chi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)= & 0, \nonumber 
+ \sum_{i=1}^n \psi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)=0, \
+ \sum_{i=1}^n \chi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)=0, 
  \end{eqnarray} 
@@
 
-\response{Finally, we mention that in addition to the additional computation already mentioned, it is clear that the estimators themselves have must be computed for every iteration of the Markov Chain.
-We have found this burden to be marginal in with respect to computing the needed Jacobian.
-In the simulations and real data analyses presented below, we will see that the additional burden is of added value in situations where substantial prior information is available that is not swamped by current data.}
+\response{Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
+We have found this burden to be marginal in relation with respect to computing the needed Jacobian.
+In the simulations and real data analyses presented below, we will see that the additional burden is often of added value over traditional robust regression when substantial prior information is available that is not swamped by current data.}
 
@@
 
-%whose densities are displayed in Figure \ref{fig:priors}. The vertical dashed line is at the known true value of $\sigma^{2} = 4$.
-%
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width = 4in]{priors_sigma2.png}
-%\caption{The nine different inverse gamma priors used for the group level variance parameters $\sigma_{j}^{2}$ in the simulation.
-The shape parameter values are $a_{s} = 1.25, 5, 10$.
-The scale parameter values are $b_{s} = 4a_{s}c$ with $c = 0.5, 1, 2$.
-The vertical dashed line in each panel is at the true value of $\sigma^{2} = 4$ and is the variance of the good portion of the data in the simulation.}
-%\label{fig:priors}
-%\end{figure}
-
 $K = 30$ data sets are generated from \eqref{gensim2}.
@@
 \subsection{\response{Simulation 2}}
+
+\response{STILL NEED TO COMPLETE}
 In this simulation the data are generated from the following mechanism: $y = \bbeta^{\top}x + \epsilon$
@@
 It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies.
-Additionally, robust methods are more likely to identify such agencies.
 Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.}
@@
 Holdout evaluation is done on the remaining (`Type 1') samples.
-For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates, \response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
+The acceptance rates for  the data augmentation step,\response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
 \response{The exception was a single training set from State 15 resulting in an usually small acceptance rate under Tukey's version.
@@
 \begin{itemize}
-\item we have found them most useful in outlier prone situations where good prior information can be encoded for the `good' part of the model.
+\item We have the method useful in outlier prone situations where good prior information can be encoded for the `good' part of the model.
 The additional computation burden may be too much when this is not the case.
@@
 However, depending on the amount of contamination, some adjustment may be necessary.
-\item Comparisons amongst various choices of conditioning statistics can be made via standard cross-validation techniques like those done in this paper where models are fit to several training and holdout sets.
+\item The likelihood itself can indeed take many forms and, like the conditioning statistic, can depend on the application.
+We have developed methods for fitting these models under a large class of conditioning statistics.
+Currently the default choice in outlier prone situations is to use a normal likelihood model, with the conditioning intended to reduce the sensitivity of the analysis to the outliers.
+\item Comparisons amongst various choices of conditioning statistics and models can be made via standard cross-validation techniques like those done in this paper where models are fit to several training and holdout sets.
 One should take care in the method of evaluation.
-When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data.
-We introduce the TLM, however it may be simpler to simply identify outliers and exclude them from the evaluation stage explicitly.
+When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data or the metric should be adjusted to discount outlying data ins some way (such as the trimmed-log-marginal we introduced TLM).
 \end{itemize}
 
-\subsection{An Additional Illustrative Example}
-
-As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
+%\subsection{An Additional Illustrative Example}
+
+%As a second example, a data set measuring the number of telephone calls in Belgium from 1950-1973 is analyzed.
 The outliers in this case are due to a change in measurement units on which calls were recorded for part of the data set.
@@
 The full model is a standard normal Bayesian linear regression:
-\begin{equation}
-{\boldsymbol{\beta}}\sim N_{2}(\boldsymbol{\mu}_{0}, \boldsymbol{\Sigma}_{0}),\  \sigma^{2} \sim IG(a, b),\  \by \sim N(X\boldsymbol{\beta}, \sigma^{2} I),
-\end{equation}
-where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and $X$ is the $n\times 2$ design matrix with a vector of 1's in the first column and the year covariate in the second.
+%\begin{equation}
+%{\boldsymbol{\beta}}\sim N_{2}(\boldsymbol{\mu}_{0}, \boldsymbol{\Sigma}_{0}),\  \sigma^{2} \sim IG(a, b),\  \by \sim N(X\boldsymbol{\beta}, \sigma^{2} I),
+%\end{equation}
+%where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and $X$ is the $n\times 2$ design matrix with a vector of 1's in the first column and the year covariate in the second.
 Prior parameters are fixed via a maximum likelihood fit to the first 3 data points.
@@
 Finally $a = 2$ and $b =1$.
-
-Four models are compared: 1) the normal theory base model 2) a two component normal mixture model, 3) a t-model, and 4) a restricted likelihood model conditioning on Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
+%
+%Four models are compared: 1) the normal theory base model 2) a two component normal mixture model, 3) a t-model, and 4) a restricted likelihood model conditioning on Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale.
 Each model is fit to the remaining 21 data points.
@@
 The prior on $\sigma^2$ is adjusted by a scale factor of $3/5$ to provide the same prior on the variance.
-
-The data and  $95\%$ credible bands for the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}.
+%
+%The data and  $95\%$ credible bands for the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}.
 The normal model fit to all cases results in a very wide posterior predictive distribution due to an inflated estimate of the variance.
@@
 As in classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers.
-\begin{figure}[t]
-\centering
-{\includegraphics[width = 4in]{figs/calls_predictive.png}}
-\caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
+%\begin{figure}[t]
+%\centering
+%{\includegraphics[width = 4in]{figs/calls_predictive.png}}
+%\caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
 The first three data points were used to specify the prior with each model using the remaining 21 for fitting.
 The normal theory model was also fit after removing observations 14-20 (years 1963 - 1970).}
-\label{fig:calls_predictive}
-\end{figure}
+%\label{fig:calls_predictive}
+%\end{figure}
+%
+%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-\section{M-estimators}
+\subsection{M-estimators}
 \label{sec:Mestimators}

### 2019-06-14 revision_2/code/simulation/simulation_many_p/2_summarize_simulation.R

@@ -2,9 +2,9 @@ library(tidyverse)
 
 
 out <- read_rds(file.path(here::here(), 
-                    '1_simulation_out.rds'))
+                    '1_simulation_out_3.rds'))
 
-
+nu <- 5
 mse  <- out$estimates %>% filter(variable != 'sigma2') %>% 
   mutate(sq_error = (true_value - estimates)^2) %>% 
   group_by(simulation, prior_sd, method) %>% 
@@ -26,12 +26,32 @@ ggsave(file.path(getwd(),
                  "..", "..","..", "figs", 
                  'mse_sim_many_p.png'), width = 6, height = 4)
 
+#mse on just the active parameters
   
+mse_sub  <- out$estimates %>% filter(variable %in% c('1', '2', '3')) %>% 
+  mutate(sq_error = (true_value - estimates)^2) %>% 
+  group_by(simulation, prior_sd, method) %>% 
+  summarize(mse_sim = mean(sq_error)) %>% 
+  ungroup() %>% group_by(prior_sd, method) %>% 
+  summarize(mse = mean(mse_sim), se = sd(mse_sim)/sqrt(n())) %>% ungroup() %>% mutate(prior_sd = as_factor(as.character(prior_sd)))
+
+ggplot(mse_sub, aes(prior_sd, mse, group = method, col = method)) +
+  geom_point(position = position_dodge(width = .75)) + 
+  geom_errorbar(mapping = aes(ymin = (mse - se), 
+                              ymax = (mse + se)),
+                width = 0.05, position  = position_dodge(width = .75), 
+                linetype = 1) +
+  theme_bw() +  theme(text = element_text(family = 'Times')) + 
+  ylab('MSE') + xlab('Prior Standard Deviation') +
+  guides(col=guide_legend(title="Method"))
+ggsave(file.path(getwd(),
+                 "..", "..","..", "figs", 
+                 'mse_sub_sim_many_p.png'), width = 6, height = 4)
 
 
 ave_margs <- out$marginals %>% 
   group_by(prior_sd, method) %>% 
-  summarise(mn = mean(mean_log_predictive),
+  summarise(mn = mean(mean_log_predictive_point),
             se = sd(mean_log_predictive)/sqrt(n())) %>% 
   ungroup() %>%  mutate(prior_sd = as_factor(as.character(prior_sd)))
 
[…]

### 2019-06-21 revision_2/paper.tex
created new plots

@@
 In this model, estimation of $\theta_{i}$ and prediction are analogous.
-To this end we consider the expected value of  the log likelihood ratio between the true distribution of good data and a model estimate of this distribution
+To this end we consider
 \begin{equation}
 \label{sim1loss}
-E[\log f(y|\theta_{i}, \sigma^{2}) - \log f(y|\hat{\theta_{i}}, \hat{\sigma^{2}})] =
+E[\log f(y|\theta_{i}, \sigma^{2}) - \log f(y|\hat{\theta_{i}}, \hat{\sigma}^{2})] =
 \log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{2\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2})
@@
 
-\response{STILL NEED TO COMPLETE}
 In this simulation the data are generated from the following mechanism: $y = \bbeta^{\top}x + \epsilon$
-where $\bbeta = (\beta_{1}, \beta_{2},\beta_{3})^{\top}$ with $\beta_{i} \iid N(0,1)$ and  $x \sim Uniform(0,1)$.
-The error $\epsilon \sim N(0,\sigma^{2})$ with probability $0.9$ and $\epsilon \sim Half-Normal(0,10\sigma^{2})$ with probability $0.1$.
-Finally, the variance $\sigma^{2} \sim IG(5,5)$.
-Thus, there are three active covariates, with one-sided outlier contamination.
-The regression model used for fitting contains 17 additional covariates generated uniformly on (0,1) representing the situation where several potential covariates are available and a goal is variable selection.
-For the simulation, $K = 50$ data sets of size $n = 500$ are generated from the true model and models including the additional non-active covariates are fit.
-We consider the classical robust regression using Tukey's estimator of location and Huber's estimator of scale, along with a corresponding restricted likelihood version.
-For the priors, denote $\bbeta_{all} = (\bbeta, \bbeta_{extra})^{\top}$ be the active coefficients augmented with the non-active extra coefficients.
-We take $\bbeta_{all}\sim N_{20}(\mb{0}, \sigma^{2}_{\beta}I)$ and $\sigma^{2}\sim IG(5,5)$.
-Hence, the prior for $\sigma^{2}$ is correct and the prior for $\bbeta$ is at least centered at the correct value as well.
-We also consider the Student-t model with compariable priors and fixed degrees of freedom $\nu = 5$.
-For each data set, we fit the models for $ \sigma_{\beta} = 0.2, 0.4, 0.6, 0.8,,1.0$.
-The acceptance rates for the restricted likelihood MCMC data-augmentation step range from ADDDDDDDD.
-
-To compare estimation performance we first consider the squared error SE$_{k} = ||\bbeta - \hat\bbeta||^{2} + ||\hat\bbeta_{extra}||^{2}$ for each simulation $k$.
-The mean squared error and standard errors over the simulations for each $\sigma^{2}_{\beta}$ are displayed in Figure \ref{mseSimMany}.
+with $\bbeta = (\beta_{1}, \beta_{2},\beta_{3})^{\top}$ and the error $\epsilon \sim N(0,\sigma^{2})$ with probability $0.8$ and $\epsilon \sim \text{Half-Normal}(0,25\sigma^{2})$ with probability $0.2$ (i.e., there is a relatively large amount of one-sided outlier contamination).
+The components of $x = (x_{1}, x_{2}, x_{3})$ are correlated with $x_1 \sim N(0,1)$ and $x_{j} = x_{1} + \eta_{j}$ with $\eta_{j} \sim N(0, 4)$ for $j = 2,3$.
+This results in a theoretical correlation of $1/sqrt(5) \approx 0.44$ between $x_{1}$ and both $x_{j}, j = 2, 3$.
+The model used for fitting contains an additional 27 covariates, some of which are also correlated with $x_{1}$, $x_{2}$, and $x_{3}$.
+Specifically the fitting model is $y = \beta^{\top} x + \beta^{*\top} x^{*} + \epsilon$ where $x^{*}$ and $\beta^{*}$ are 27 dimensional vectors of extra covariates and slope parameters.
+Of these 27 covariates, 21 are generated independently from standard normal distributions.
+Of the remaining 6, two each are generated by adding standard normal noise to $x_{1}$, $x_{2}$, and $x_{3}$.
+This represents a common situation where several covariates with various levels of correlation amongst them are available for fitting, but only a few govern the data generating mechanism.
+
+For the simulation, $K = 30$ data sets (including the additional covariates) of size $n = 500$ are generated from the true model with true values $\bbeta = (1,1,1)^{\top}$ and $\sigma^{2} = 2$.
+We fit the model including all 30 covariates and consider the following methods for the fit 1) classical robust regression with Tukey's estimator of location and Huber's estimator of scale, 2) the corresponding restricted likelihood version 3) A heavy-tailed Bayesian model with a Student-t likelihood with $\nu = 5$ degrees of freedom.
+For the Bayesian models we take $\bbeta_{all}\sim N_{20}(\mb{0}, \sigma^{2}_{\beta}I)$ with $\bbeta_{all} = (\bbeta, \bbeta^{*})^{\top}$ and $\sigma^{2}\sim IG(5,8)$ under the restricted model and  $\sigma^{2}\sim IG(5,\frac{\nu-2}{\nu}8)$ under the Student-t model.
+For each data set, we fit the models for $ \sigma_{\beta} = 0.4, 0.6, 0.8,\dots, 1.4$.
+The acceptance rates for the restricted likelihood MCMC data-augmentation step range from $0.3$ to $0.36$ across all the data sets and values of $\sigma_{\beta}$.
+To compare performance we first consider the $MSE = (||\bbeta - \hat\bbeta||^{2} + ||\hat\bbeta^{*}||^{2})/30$ for each simulation where $\hat\bbeta$ and $\hat\bbeta^{*}$ are point estimates for the fitted model.
+For the Bayesian models, we use posterior means.
+The average MSE plus/minus one standard error over the simulations for each $\sigma^{2}_{\beta}$ are displayed in Figure \ref{mseSimMany}.
+The classical fit is labeled `rlm` and is the same for each value of the prior standard deviation $\sigma^{2}_{\beta}$.
+We see for most values of the the prior standard deviation, the Bayesian models (`restricted' and `t') outperform the classical fit.
+The correlation amongst the covariates causes a certain level of confounding and the prior shrinkage helps to improve estimation.
+However, too much shrinkage can be detrimental as demonstrated for $\sigma_{\beta} = 0.4$.
+While this will help for estimation of $\bbeta^{*} = 0$, the estimation of the active parameters $\bbeta$ can be hindered.
+The $t$ model seems more sensitive to this effect than the restricted model.
+The restricted model also has an additional advantage when it comes to prediction of the non-outlying data.
+To see this, for each simulation we consider the mean negative log-likelihood of the non-outlying data: $MNLL = -\frac{1}{N} \sum \log f(y_{i} |  \hat\bbeta, \hat\bbeta^{*}, \hat\sigma)$ where $f$ is the assumed likelihood and the average is taken over the $N$ non-outlying points $y_{i}$.
+For the classical and restricted fits, $f$ is the normal likelihood and for the `t' it is the heavy-tailed Student-t likelihood.
+The average MNLL plus/minus one standard error over the simulations for each $\sigma^{2}_{\beta}$ are displayed in Figure \ref{negllSimMany}.
+First, the restricted version has a small but consistent improvement over the classical method.
+Second, it is clear that that the heavy-tailed model suffers when trying to predict the non-outlying data since it assumes the entire data generating mechanism is heavy-tailed.
 
@@
 \includegraphics[width = 5in]{mse_sim_many_p.png}
-\caption{ADD}
+\caption{Average MSE plus/minus one standard error over the $K = 30$ simulations for each value of the prior standard deviation ($\sigma^{2}_{\beta}$) and each of the fitting methods.
+`Restricted' is our method conditioning on Tukey's estimator of location and Huber's estimator of scale.
+`rlm' refers to the classical robust linear model fit with the same estimators and `t' is the heavy-tailed Bayesian model with a Student-t likelihood.
+The `rlm' results are the same for each $\sigma^{2}_{\beta}$.}
 \label{mseSimMany}
@@
 
-Additionally, we consider the log marginal distributions to understand predictive performance....
-FINISH
+\begin{figure}[t]
+\centering
+\includegraphics[width = 5in]{negll_sim_many_p.png}
+\caption{Average MNLL plus/minus one standard error over the $K = 30$ simulations for each value of the prior standard deviation ($\sigma^{2}_{\beta}$) and each of the fitting methods.
+`Restricted' is our method conditioning on Tukey's estimator of location and Huber's estimator of scale.
+`rlm' refers to the classical robust linear model fit with the same estimators and `t' is the heavy-tailed Bayesian model with a Student-t likelihood.
+The `rlm' results are the same for each $\sigma^{2}_{\beta}$.}
+\label{negllSimMany}
+\end{figure}
 

### 2019-06-21 revision_2/code/simulation/simulation_many_p/2_summarize_simulation.R

@@ -1,9 +1,7 @@
 library(tidyverse)
-
-
+library(MCMCpack)
 out <- read_rds(file.path(here::here(), 
-                          '1_simulation_out_5.rds'))
-
+                          '1_simulation_out.rds'))
 nu <- 5
 mse  <- out$estimates %>% filter(variable != 'sigma2') %>% 
   mutate(sq_error = (true_value - estimates)^2) %>% 
@@ -28,7 +26,7 @@ ggsave(file.path(getwd(),
 
 #mse on just the active parameters
 
-mse_sub  <- out$estimates %>% filter(variable %in% c('1', '2', '3'), prior_sd != 0.2) %>% 
+mse_sub  <- out$estimates %>% filter(variable %in% c('1', '2', '3')) %>% 
   mutate(sq_error = (true_value - estimates)^2) %>% 
   group_by(simulation, prior_sd, method) %>% 
   summarize(mse_sim = mean(sq_error)) %>% 
@@ -57,7 +55,7 @@ ave_margs <- out$marginals %>%
 
 
 #, method != "rlm"
-ggplot(ave_margs %>% filter(prior_sd != 0.2), aes(prior_sd, -mn, group = method, 
+ggplot(ave_margs, aes(prior_sd, -mn, group = method, 
                       col = method)) +
   geom_point(position = position_dodge(width = .75)) + 
   geom_errorbar(mapping = aes(ymin = (-mn - se), 
@@ -72,180 +70,15 @@ ggsave(file.path(getwd(),
                  'negll_sim_many_p.png'), width = 6, height = 4)
 
 
-# Predictive MSE --------
-
-
-# gen_good_data <- function(true_value, n, p, p_extra, sd_slopes, num_corr){
-#   #true_value - vector c(betas, sigma2)
-#   # n - number of samples to generate. 
-#   X <- matrix(runif(n*p), n, p)
-#   
-#   if (num_corr > p_extra) { 
-#     num_corr <- p_extra 
-#   }
-#   X_extra <- matrix(NA, n, num_corr)
-#   which_active <- rep(1:p, length.out = num_corr)
-#   for (jj in 1:num_corr) {
-#     ind <- which_active[jj]
-#     slope  <- rnorm(1, 0, sd = sd_slopes)
-#     X_extra[,jj] <- X[,ind] * slope + rnorm(n, sd =  sd_slopes/3)
-#   }
[…]

### 2019-06-21 revision_2/paper.tex
edits right before sending to coauthors

@@
 \label{Mest}
- \sum_{i=1}^n \psi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)=0, \
+ \sum_{i=1}^n \psi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right) x_{ij}=0, \
  \sum_{i=1}^n \chi\left(\frac{y_i - x_{i}^{\top}\bb(\by,X)}{s(\by,X)}\right)=0, 
  \end{eqnarray} 
-where $\psi$ and $\chi$ are almost surely differentiable.
+for $j = 1, 2, \dots, p$, $x_{ij}$ are the components of $x_{j}$ and  $\psi$ and $\chi$ are almost surely differentiable.
 The gradients can be found by differentiating this system of equations with respect to each $y_{i}$.
@@
 In this model, estimation of $\theta_{i}$ and prediction are analogous.
-To this end we consider
+To this end we consider the loss:
 \begin{equation}
 \label{sim1loss}
-E[\log f(y|\theta_{i}, \sigma^{2}) - \log f(y|\hat{\theta_{i}}, \hat{\sigma}^{2})] =
-\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{2\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2})
+L((\hat\theta_{i}, \hat\sigma), (\theta_{i},\sigma)) =
+\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2})
 \end{equation}
-The expectation is taken with respect to the true data distribution of the good data assuming fixed estimates.
-These estimates are the posterior means for the Bayesian methods and the standard point estimates for the classical methods.
+Note, this loss is proportional to the Kullback-Leibler divergence between two normals with the base normal being the true distribution of the good portion of the data and the the other normal representing the estimate under the fitting method.
+We are using fixed point estimates $\hat\theta_{i}$ and $\hat\sigma$ which are posterior means under the Bayesian models and the standard point estimates for the classical methods.
 }
-
 %To assess predictive capability, the models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution.
@@
 Sampling variation is summarized with the standard error between the $K=30$ replicates in the simulation:  $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
-
 Figure \ref{kl_sim} displays the average of loss \ref{sim1loss} grouped by pairs of $a_{s}$ and $c$ with error bars plus/minus on standard error within the group.
 The values of $a_{s}$ and $c$, do not affect the classical robust linear models.
-The average loss for the normal theory models ranges from $1.19$ to $1.42$ and are left out of the figure.
-For $c = 0.5$ and $c = 1$ and the two larger values of $a_{s}$ the results favor the restricted likelihood methods.
-
+The average loss for the normal theory models ranges from $1.44$ to $1.66$ and are left out of the figure.
+For $c = 0.5$ and $c = 1$ the results favor the restricted likelihood methods as seen by the lower values of loss.
 The choice of $c = 2$ corresponds to a particularly poor prior distribution.
@@
 The panels correspond to $c = 0.5$ (left), $c=1$ (middle), and $c=2$ (right), with the values of $a_{s}$ on the horizontal axis.
-The average loss for the normal theory model ranges from $1.19$ to $1.42$ and is left out of the figure.}
+The average loss for the normal theory model ranges from $1.44$ to $1.66$ and is left out of the figure.}
 \label{kl_sim}
@@
 Figure \ref{kl_mnp} displays the average of these main effects over the $K = 30$ simulations along  with error bars plus/minus one standard error.
-For each group $n$, $p$, and $m$, the Bayesian restricted likelihood versions have better (lower) average loss than do the classical methods.
-As expected, the average loss gets larger (worse) as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller (better) as the sample size $n$ grows.
+For each group $n$, $p$, and $m$, the Bayesian restricted likelihood versions have better average loss than do the classical methods.
+As expected, the average loss gets larger as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller as the sample size $n$ grows.
 The advantage of the Bayesian method is greater for smaller sample sizes.
@@
 M-estimators offer a natural choice for conditioning in restricted likelihood settings and they can be readily applied when conditioning on these estimators using the method described in this paper.
-This section gives a brief review
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{M-estimators of Location}
-\label{sec:Mlocation}
-%%%%%%%%%%%%%%%%%%%%%%%%
-To begin the review it is easiest to start with the location model 
-\begin{equation}
-\label{locMod}
-y_i= \mu+\epsilon_i, \ \ i=1,\dots, n,
-\end{equation}
-where we assume that $\epsilon_i$ are independent identically
-distributed random variables from the distribution $F_0$ having
-mean zero, constant (known) variance, and density $f_0$ with
-respect to Lebesgue measure. It follows that $y_i\iid
-F(y)=F_0(y-\mu)$ . The M-estimate for $\mu$ is defined by the criterion
-\begin{equation}
-\label{MrhoLoc}
-\hat\mu= \arg \min_\mu \sum_{i=1}^n \rho(y_i -\mu),
-\end{equation}
-where $\rho$ is a loss function.
-It is assumed that $\rho(x)$ is nondecreasing in $|x|$ and $\rho(0)=0$.
-If $F_0$ is standard normal, taking $\rho$ to be squared error loss ($\rho(x)=x^2$) results in the maximum likelihood estimator (MLE).
-In general, $\rho(x)=-\log f_{0}(x)$ corresponds to the MLE.
-In this sense, M-estimators are a generalization of MLEs.
-
-Assuming it exists, the derivative of $\rho$ is denoted by $\psi$ and $\hat\mu$  in  \eqref{MrhoLoc} satisfies the estimating equation
-\begin{equation}
-\label{MpsiLoc}
-\sum_{i=1}^n \psi(y_i-\hat\mu)=0.
-\end{equation}
-Putting $w_i=\frac{\psi(y_i-\hat \mu)}{y_i- \hat\mu}$, equation
-\eqref{MpsiLoc} can be rewritten as
-\begin{equation}
-\label{MpsiLocWeight}
-\sum_{i=1}^n w_i (y_i- \hat\mu)=0
-\end{equation}
-and an analytical expression for $\hat\mu$ is then the weighted average
-\begin{equation}
-\label{weightedAve}
-\hat\mu=\frac{\sum_{i} w_iy_i}{\sum_{i} w_i}.
-\end{equation}
-This weighted average cannot be used directly since the $w_i$
-depend on $\hat\mu$, but it provides a useful insight in how to choose a $\psi$ that downweights outlying observations. Two
-examples of commonly used $\rho$ functions whose derivatives $\psi$ achieve downweighting are
+This section gives a brief review.
+General estimating equations for the simultaneous M-estimators used in this paper appear in equation \ref{Mest} of the main text.
+Taking $\psi = \rho'$, the two $\rho$ functions used in this paper are:
 \begin{equation}
@@
 \end{equation}
-The first of these is known as Huber's loss.
+The first of these is known as Huber's $\rho$.
 It offers a compromise to squared error loss, with the loss becoming linear for absolute residuals larger than $k$.
@@
 The $\rho$ in \eqref{Tukey} is known as Tukey's bisquare.
-
-A notable property of both of the $\psi$ functions here is that they are bounded.
-This implies a bounded \textit{influence function} (IF).
-The influence function is a measure of how much an estimator is
-affected by a small fraction of identical outliers in the
-sample. Boundedness is desirable because it
-implies that the effect of a small contamination on a
-statistical procedure cannot become arbitrarily large.
-More details on influence functions can be found in \cite{huber2009} and \cite{maronna2006}.
-Tukey's $\psi$ is \textit{re-descending} as it returns to zero outside of $(-k,k)$.
+Tukey's $\psi = \rho'$ is \textit{re-descending} as it returns to zero outside of $(-k,k)$.
 As a result, Tukey's estimator downweights large residuals more than does Huber's estimator.
 Huber's estimator is akin to Winsorising whereas Tukey's is akin to complete trimming.
-
 Note that $k$ is a tuning constant which must be chosen.
-Under usually satisfied conditions, M-estimators are asymptotically normal and this property can be employed to choose $k$.
-The results for the location setting, which extend up to linear regression, are presented here.
-Again, more detailed results can be found in both \cite{huber2009} and \cite{maronna2006}.
-
-For a given distribution $F$, let $\mu_0$ be the value such that
-\begin{equation}
-\label{eq:Epsi}
-E_F\psi(x-\mu_0)=\int\psi(x-\mu_0)\ dF=0.
-\end{equation}
-Taking $\hat\mu$ to be the solution to \eqref{MpsiLoc} we have
-$\hat\mu\overset{p}\rightarrow \mu_0$ and
-\begin{equation}
-\label{eq:asyNormM}
-\sqrt{n}(\hat\mu-\mu_0)\overset{\mc D}\rightarrow N(0, v)\
-\text{with}\
-v=\frac{E_F(\psi(y-\mu_0)^2)}{(E_F\psi'(y-\mu_0))^2}
-\end{equation}
-as $n\rightarrow\infty$. The conditions for the above convergence properties to hold depend on $\psi$ and
-$F$. In particular, the numerator of $v$ must be finite and the
-denominator must exist and be nonzero. Re-descending $\psi$
-functions, such as Tukey's, require slightly stronger conditions than those for monotone $\psi$.
-
-Under the assumed model, the MLE is optimal in the sense of achieving the minimum asymptotic variance of $v_0=I(\mu)^{-1}$  where $I(\mu)$ is the Fisher information for $\mu$.
-Hence, $v\geq v_0$ and $k$ is typically chosen by considering the asymptotic relative efficiency of $\hat\mu$
-\begin{equation}
-\label{eq:Eff}
-\text{Eff}(\hat\mu)=\frac{v_0}{v}.
-\end{equation}
-The idea is for robust estimators to not perform badly compared
-to the optimal estimator, under the assumed model. To this end,
-$k$ is set so that $\text{Eff}(\hat\mu)$ is reasonably close to
-one. The standard default is to assume a normal model and set
-$\text{Eff}(\hat\mu)=0.95$. This leads to $k=1.345$ for Huber's $\rho$ and $k=4.685$ for Tukey's. Unless otherwise stated, these values are used for the applications in this dissertation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{M-estimators of Scale}
-\label{sec:Mscale}
-%%%%%%%%%%%%%%%%%%%%%%%%
-$M$-estimation naturally extends the scale model
-\begin{equation}
-\label{scaleMod}
-y_i= \sigma\epsilon_i, \ \ i=1,\dots, n,
-\end{equation}
-where $\epsilon_i$ are independent identically distributed with
-density $f_0$ and $\sigma>0$ is the unknown parameter. Then
-$y_i$ come from a scale family with density $f_\sigma(y)=
-\frac{1}{\sigma}f_0(\frac{y}{\sigma})$. %The MLE of $\sigma$ is
-%\begin{equation}
-%\label{mleSigma}
-%\hat\sigma= \arg \min_\sigma \prod_{i=1}^n
-%\frac{1}{\sigma}f_0\left(\frac{y_i}{\sigma}\right)
-%\end{equation}
-The M-estimator for $\sigma$ is defined through the estimating equation
-\begin{equation}
-\label{eq:Msigmachi}
- \sum_{i=1}^n\chi \left(\frac{y_i}{\sigma}\right)=0,
-\end{equation}
-for some function $\chi$. Taking $\chi(x)=-x\frac{f'_0(x)}{f_0(x)}-\delta$ for $\delta=1$ corresponds to the MLE. This reduces to $\chi(x)=x^2-1$ for the standard normal yielding the estimate
-$\hat\sigma= \sqrt{\frac{1}{n}\sum{y_i^2}}$. Using the same idea as in
-the location case, a different $\chi$ can be chosen in an effort to achieve a robust estimate of
- $\sigma$.
- %for a given distribution
-%$F$, the estimate $\hat\sigma$ from \eqref{eq:Msigmachi}
-%converges in probability to the value $\sigma_0$ that satisfies
-%$E_{F}[\chi(\frac{x}{\sigma_0})]=\int\chi(\frac{x}{\sigma_0})\
-%dF=0$.
-\cite{huber1964} proposed the choice 
+We only consider `default' tuning parameters in this paper which have 95\% asymptotic efficiency under a normal distribution.
+More detailed results can be found in both \cite{huber2009} and \cite{maronna2006}.
+These values are $k=1.345$ for Huber's $\rho$ and $k=4.685$ for Tukey's.
+
+For the $\chi$ function, \cite{huber1964} proposed the choice 
 \begin{equation}
@@
 \end{equation}
- For consistency when $F$ is
-$N(0,\sigma^2)$ we need $E_{\Phi}[\chi({x})]=\int\chi({x})\
-d\Phi=0$ where $\Phi$ is the standard normal distribution. This
-yields $\delta\approx 0.71016$ for the $\chi$ in \eqref{HuberScale}. For convenience,
-$k$ is often set to $1.345$, the value giving $95\%$ efficiency at the normal for
-Huber's location estimator. This is often
-referred to as Huber's `Proposal 2'.
-
-Another popular choice is the step function
-\begin{equation}
-\label{madchi}
-\chi(x)=I(|x|>c)-\delta.
-\end{equation}
-Fixing $\delta=0.5$ yields the aforementioned \textit{rescaled
-median absolute deviation}, written here as $\hat\sigma=K(\text{Med}(|x|))$ with $K=1/c$.
-%This is the  Recall, putting $K=1/\Phi^{-1}(3/4)\approx1.4826$ results in a constant estimator for $\sigma$ under normality.
-%Again $$ is typically chosen forconsistency at an assumed model which yields $c=0.6745$ for thenormal.
-%Still another option for robustness is Tukey's bisquare \eqref{Tukey} with $k=1$
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Simultaneous M-estimators of Location and Scale}
-\label{sec:MlocScale}
-%%%%%%%%%%%%%%%%%%%%%%%%
-There are many ways to define $M$-estimates for multiple
-parameters but for convenience we concentrate on
-\textit{simultaneous estimators}. We first consider the location
-and scale setting
-\begin{equation}
-\label{locScaleMod}
-y_i= \mu+\sigma\epsilon_i, \ \ i=1,\dots, n,
-\end{equation}
-where $\epsilon_i$ are independent identically distributed with
-density $f_0$, $\mu$ and $\sigma>0$ unknown and $y_i$ has density $f(y)=\frac{1}{\sigma}f_0(\frac{y-\mu}{\sigma})$. Combining the equations in \eqref{MpsiLoc}
-and \eqref{eq:Msigmachi}, the simultaneous M-estimators of
-location and scale are the solutions to
-\begin{equation}
-\label{simM}
-\begin{aligned}
-&\sum \psi \left(\frac{y_i-\hat\mu}{\hat\sigma}\right)=0\\
-&\sum \chi \left(\frac{y_i-\hat\mu}{\hat\sigma}\right)=0.
-\end{aligned}
-\end{equation}
-
-The extension of $M$-estimators to linear regression is
-straightforward. Consider the standard regression model
-\begin{equation}
-\label{regM}
-y_i=\bx_i'\bbeta+\epsilon_i,
-\end{equation}
-where $\epsilon_i$ are independent random variables with mean zero and variance
-$\sigma^2$, $\bx_{i}\in\mathbb{R}^{p}$ is a vector of predictors, and  $\bbeta\in\mathbb{R}^{p}$ is a vector of regression parameters. The simultaneous M-estimators of $\bbeta$ and
-$\sigma$ are defined by
-\begin{equation}
-\label{simMreg}
-\begin{aligned}
-&\sum \psi
-\left(\frac{y_i-\bx_i'\widehat\bbeta}{\hat\sigma}\right)\bx_i=\mathbf{0}\\
-&\sum \chi \left(\frac{y_i-\bx_i'\widehat\bbeta}{\hat\sigma}\right)=0.
-\end{aligned}
-\end{equation}
-Common $\psi$ functions include Huber's and Tukey's mentioned earlier and common
-$\chi$ functions appear in \eqref{HuberScale} and \eqref{madchi}.
-Assuming the distribution of the errors is $F$, under standard conditions for $\psi$, $\chi$, the general result is again
-$\widehat\bbeta\overset{p}\rightarrow\bbeta_{0}$ and
-$\hat\sigma\overset{p}\rightarrow\sigma_{0}$ where $\bbeta_{0}$ and
-$\sigma_{0}$ satisfy
-\begin{equation}
-\label{ExpMreg}
-\begin{aligned}
-& E_F \psi
-\left(\frac{y_i-\bx_i'\bbeta_{0}}{\sigma_{0}}\right)\bx_i=\mathbf{0}\\
-& E_F \chi \left(\frac{y_i-\bx_i'\bbeta_{0}}{\sigma_{0}}\right)=0.
-\end{aligned}
-\end{equation}
-Further, the estimates are jointly asymptotically normal with a
-covariance matrix depending on the $\psi$ and $\chi$ functions.
+For consistency under the normal distribution the tuning parameter is set to $\delta\approx 0.71016$, taking $k = 1.345$ as above for Huber's $\psi$ is
+referred to as Huber's `Proposal 2'. This is estimator used throughout this this paper.
+
+%Another popular choice is the step function
+%\begin{equation}
+%\label{madchi}
+%\chi(x)=I(|x|>c)-\delta.
+%\end{equation}
+%Fixing $\delta=0.5$ yields the \textit{rescaled
+%median absolute deviation}.
 

### 2020-04-13 revision_2/paper.tex
minor typos

@@
 A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method.
-\response{ An R package \texttt{brlm} is to implement our methods in available at \texttt{github.com/jrlewi/brlm}.
+\response{ An R package \texttt{brlm} to implement our methods is available at \texttt{github.com/jrlewi/brlm}.
 Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/revision\char`_2}.}
@@
 Traditional robust estimation techniques are often quicker and can provide comparable results.
-\item Currently, we recommend conditioning on classical robust estimators when pursing these methods.
+\item Currently, we recommend conditioning on classical robust estimators when using these methods.
 Default choices are Huber's and Tukey's estimators as outlined in the paper.

### 2020-04-13 revision_2/paper.tex
more minor edits

@@
 \begin{itemize}
-\item We have the method useful in outlier prone situations where good prior information can be encoded for the `good' part of the model.
+\item We have shown the method to be useful in outlier prone situations where good prior information can be encoded for the `good' part of the model.
 The additional computation burden may be too much when this is not the case.
@@
 \item Currently, we recommend conditioning on classical robust estimators when using these methods.
-Default choices are Huber's and Tukey's estimators as outlined in the paper.
+Examples include Huber's and Tukey's estimators as outlined in the paper.
 We have found default choices (e.g.
@@
 We have developed methods for fitting these models under a large class of conditioning statistics.
-Currently the default choice in outlier prone situations is to use a normal likelihood model, with the conditioning intended to reduce the sensitivity of the analysis to the outliers.
+In outlier prone situations we have had success using a normal likelihood model, with the conditioning intended to reduce the sensitivity of the analysis to the outliers.
 \item Comparisons amongst various choices of conditioning statistics and models can be made via standard cross-validation techniques like those done in this paper where models are fit to several training and holdout sets.

### 2020-05-09 revision_2/paperV2.tex
Steve's edits from May 7th

--- 2020-04-13 revision_2/paper.tex
@@
 
-\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
-One conceptual advantage is that inferences and predictions are less sensitive to features of the data not captured by
-the conditioning statistics.
+%\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data.
+One conceptual advantage is that inferences and predictions are less sensitive to features of the data not captured by the conditioning statistics.
 Choosing statistics targeting main features of interest allows for more targeted inference on these features.
 The analysis can help to better understand other features, such as outliers, not capture by the conditioning statistics.}
-\response{The examples in the paper suggest advantages in situations where outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
+%\response{The examples in the paper suggest advantages in situations where outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
 The main disadvantage over traditional robust estimate techniques are mainly computational.
@@
 Since it is typically that the restricted likelihood posterior converges to the same expected value as the conditioning statistics as the sample size grows, it may not be practical to implement our method in all situations.}
+\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data.
+One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
+the conditioning statistics than are methods based on the complete likelihood.
+Choosing statistics targeting the main features of interest allows for inference that focuses on these features.
+The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.}
+
+\response{The examples in the paper provide a Bayesian analog of classical robust estimators.
+The main disadvantage of our methods relative to the classical estimators is computational.
+In Section~\ref{BayesLinMod} we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.
+The advantages are those of Bayesian methods.
+As is standard for Bayes-classical comparisons, the Bayesian method requires greater computational effort while providing better inference.
+As a referee notes, asymptotically, the Bayesian and classical parameter estimates are often very close and have the same limiting posterior variance / sampling variance.
+In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.}
 
@@
 Many estimators satisfy the above properties, including several traditional simultaneous M-estimators \citep{huber2009, maronna2006} for which the \texttt{R} package \texttt{brlm} (\texttt{github.com/jrlewi/brlm}) is available to implement the MCMC described here.
-\response{These M-estimators satisfy \ref{asb}-\ref{as} since they are optimizers of (almost surely) continuous and differentiable objective functions.
-Constraints  \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}  More software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
-The current version of the \texttt{R} package also implements the direct computational methods described in \cite{lewis2014}.
+%\response{These M-estimators satisfy \ref{asb}-\ref{as} since they are optimizers of (almost surely) continuous and differentiable objective functions.
+Constraints  \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}
+\response{These M-estimators satisfy \ref{abs} and \ref{as} since they are optimizers of continuous and differentiable objective functions.
+Constraints \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}
+More software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
+The current version of the \texttt{R} package also implements the direct methods described in \cite{lewis2014}.
 These methods are effective in lower dimensional problems and were used in both examples in Section \ref{illustrations}.
@@
 \end{theorem} 
-\response{The proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
+%\response{The proposal is governed by the choice of $p(z^{*})$ and a poor choice could cause concern about the efficiency of the convergence of the MCMC algorithm.
 For all the examples in the paper we defined $p(z^{*})$ to simply be the uniform distribution on $\mathbb{S}$.
@@
 This could provide some advantages in some situations, though we have yet to run into any serious issues with convergence using the independent proposal we utilize here.}
+\response{The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm.
+For all examples in this paper we defined $p(z^{*})$ to be the uniform distribution on $\mathbb{S}$.
+The advantage of this choice is that it requires no further tuning parameters.
+We have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with a reasonable probability.
+To implement the method in practice, we generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$.
+Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$.
+Using simple algebra and conditions \ref{regEq}-\ref{scaleEq2Reg}, one can show that $h(\cdot)$ is invariant to this projection and scaling.
+Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk.
+As we are proposing values on a complicated manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$.
+This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.}
 
@@
 
-\response{Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
+%\response{Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
 We have found this burden to be marginal in relation with respect to computing the needed Jacobian.
 In the simulations and real data analyses presented below, we will see that the additional burden is often of added value over traditional robust regression when substantial prior information is available that is not swamped by current data.}
+\response{Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
+We have found this burden to be marginal relative to computation of the needed Jacobian.
+In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.
+This is most evident when substantive prior information is available and information in the data is limited.}
 
@@
 We have seen good mixing of the MCMC chains across a wide-variety of examples.
-\response{We have found the additional computational burden to be beneficial in situation where  substantial prior information that will impact the results is available.}
+%\response{We have found the additional computational burden to be beneficial in situation where  substantial prior information that will impact the results is available.}
+\response{We have found the benefits of using our Bayesian technique to outweigh the additional computational burden (relative to a classical estimator) in the situation where substantive prior information that will impact the results is available.}
 

### 2020-05-09 revision_2/response/responseV5.tex
Steve's edits from May 7th

\documentclass{article}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\usepackage{graphicx, psfrag, amsfonts, float}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{hhline}
 \pdfminorversion=4
\usepackage{rotating}
\def\bgam{\mbox{\boldmath $\gamma$}}
\def\bth{\mbox{\boldmath $\theta$}}
\def\bbeta{\mbox{\boldmath $\beta$}}
\def\blam{\mbox{\boldmath $\lambda$}}
\def\bmu{\mbox{\boldmath $\mu$}}

\newcommand{\bx}{\mbox{\boldmath $x$}}
\newcommand{\bu}{\mbox{\boldmath $u$}}
\newcommand{\bc}{\mbox{\boldmath $c$}}
\newcommand{\bs}{\mbox{\boldmath $s$}}
\newcommand{\by}{\mbox{\boldmath $y$}}
\newcommand{\bz}{\mbox{\boldmath $z$}}
\newcommand{\bv}{\mbox{\boldmath $v$}}
\newcommand{\bb}{\mbox{\boldmath $b$}}
\newcommand{\bzero}{\mbox{\boldmath $0$}}
\newcommand{\thstarj}{\mbox{$\theta^\star_j$}}
\newcommand{\bths}{\mbox{$\btheta^\star$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\uI}{\mathrm{I}}
\newcommand{\uP}{\mathrm{P}}
\newcommand{\up}{\mathrm{p}}
\newcommand{\mb}{\mathbf}
\newcommand{\mc}{\mathcal}

\newcommand{\Bern}{\mbox{Bern}}
\newcommand{\Nor}{\mbox{N}}
\newcommand{\Ga}{\mbox{Gamma}}
\newcommand{\Dir}{\mbox{Dir}}
\newcommand{\Ber}{\mbox{Ber}}
\newcommand{\Be}{\mbox{Be}}
\newcommand{\Unif}{\mbox{Unif}}
\newcommand{\Binom}{\mbox{Bin}}
\newcommand{\IG}{\mbox{IG}}

\newcommand{\Xs}{X^\star}
\newcommand{\Lc}{{\cal L}}

\usepackage[dvipsnames,usenames]{color}
\newcommand{\yy}{\color{magenta}\it}
\newcommand{\jj}{\color{Black}\rm}
\newcommand{\yjnote}[1]{\footnote{\color{Brown}\rm #1 \color{Black}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{\bf Definition}
\newtheorem{lemma}[theorem]{\bf Lemma}
\newtheorem{corollary}[theorem]{\bf Corollary}
\newtheorem{proposition}[theorem]{\bf Proposition}
\newtheorem{assumption}[theorem]{\bf Assumption}
\newtheorem{example}[theorem]{\bf Example}
\newtheorem{remark}[theorem]{\bf Remark}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\stackrel{indep}{\sim}}

\setlength{\textwidth}{6 in}
\usepackage{color}
\usepackage{ulem} % \sout
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\brown}[1]{{\color{brown}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}
\newcommand{\response}[1]{{\color{blue}#1}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\graphicspath{{figures/}{figs/}}

\begin{document}

\section{Reviewer 1 Comments}

\begin{enumerate}
\item The authors propose a broad class of the proposal density, but didn't discuss the choice and tuning within the class. Tuning the proposal is crucial to the mixing and efficiency of the MH algorithm, epecially in the high-dimension space, $n-p$-dimensional, that the paper is dealing with. There are two difficulties in tuning within the proposed class. First, since the proposal density is a complicated transformation of $p(z^{*})$ in $R^{n-p-1}$, even if $p(z^{*})$ belongs to a standard parametric family, $p(z^{*})$ does not and it is not straightforward to assess the properties that are usually used in tuning MCMC algorithm, e.g. mode and
tails behaviour. Second, the proposed algorithm (11) is restrictive because it only works for independent proposal, not the random walk proposal. Random walk is more able to explore a non-standard parameter space like the manifold here, while it seems tricky to design the independent proposal that well covers the probability mass of the target density, which again due to the transformation.

\response{This is an astute observation - we have added the following text after Theorem 3.6:

`The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm. For all examples in this paper we defined $p(z^{*})$ to be the uniform distribution on $\mathbb{S}$. The advantage of this choice is that it requires no further tuning parameters.  We have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with a reasonable probability. To implement the method in practice, we generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$. Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$. Using simple algebra and conditions \ref{regEq}-\ref{scaleEq2Reg}, one can show that $h(\cdot)$ is invariant to this projection and scaling. Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk. As we are proposing values on a complicated manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$. This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.'

There are undoubtedly cases where our choice is not optimal.  Here, we generate proposals for the complete data on a manifold that (in our examples and typically) is of much higher dimension than the conditioning statistic.  The independence proposals have reasonably large acceptance probabilities.  Random walk proposals are generally used to ensure that proposals are ``near'' the current state of the Markov chain, reducing proposed movement in exchange for a greater acceptance probability.  Our take on our algorithm is that we offer one solution that has provided effective MCMC in the cases we have explored.  The method applies to a large class of models that are in common use and to a large class of conditioning statistics.  We note that the independence proposals for the complete data are but one part of a larger algorithm.  Given the complete data, generation of the regression parameters may or may not make use of random walk proposals, block proposals, Gibbs steps involving generation from full conditionals, or other techniques.

With the basic paradigm and one implementation in place, we look forward to many future developments.  Further research is needed to produce these developments.  For computation, the development of random walk proposals on (nonlinear) manifolds is an interesting problem.  
}

\item The simulation studies didn't report the choice of $p(z^{*})$, acceptance rates of the MH, and mixing of the overall MCMC algorithm. Due to point 1, I think these issues would be of interest to readers.

\response{Thanks. We report the choice of $p(z^{*})$ above and  we have added acceptance rates for the simulations.}

\item The models studied in both the simulation and real data examples are just simple linear regression which is not realistic. Multiple linear regression with at least three independent variables should be studied.

\response{For the real data, we have included two additional covariates related to the number of employees at each agency. These were left out originally after EDA revealed their effect sizes were small, but leaving them in makes for a good study as well. We have kept the first simulation as we feel it is a good and simple illustration of the ability to fit hierarchical models with our method. The real data examples now contain a hierarchical example with more covariates. Additionally, we have included a second simulation where the ground truth is a linear regression model with 3 active covariates.  A model with 30 covariates (27 inactive) is fit.  There is correlation amongst some of the covariates, making this problem more realistic.}

\item What are the benefits of the proposed method over the classical robust point estimators, like Huber or Tukey estimators compared in the examples, to offset the additional computational cost and tuning efforts? From the simulation studies, whether it has improvement or not depends on the prior distribution, which seems to be from comparing Bayesian and Frequentist methods. Actually, literatures on the asymptotic properties of $f(\theta|T(yobs))$ shows that, if $T(yobs)$ is asymptotically unbiased, $T (yobs)$ and $E(\theta | T (yobs))$ have the same asymptotic variance. Hence if the prior doesn't matter, both methods have similar performance.

\response{As you note, one major advantage is that our method is {\em exactly} a Bayesian method, with $T(y_{obs})$ used in Bayes Theorem to move from prior to posterior.  In a typical setting, under relatively mild conditions on the prior distribution and estimator, Bayesian and frequentist methods will agree asymptotically.  This is reflected in the large-sample central limit theorems (Bayesian and frequentist versions) and is not specially connected to our work.  In this paper, our interest is not in these asymptotic settings where we could simply use a limiting normal distribution as the posterior over the parameters, but rather for the finite sample setting where Bayesian and frequentist methods yield different answers.  The simulations and data analyses document this differential performance.  The standard advantages of Bayes apply -- a guarantee of admissibility from a decision-theoretic view; the ability to combine information across a collection of problems (e.g., the hierarchical setting); and the transition from moment-based methods to likelihood-based methods, for example.  The weaknesses are also there -- a really bad prior distribution produces poor finite-sample performance.  There is a greater computational cost (standard for Bayes vs frequentist), but, given our MCMC routine, no real effort is needed to tune the computation.}

\response{We have added the following to the introduction of the paper to address this comment:}

\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data. One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
the conditioning statistics than are methods based on the complete likelihood. Choosing statistics targeting the main features of interest allows for inference that focuses on these features. The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.}

\response{The examples in the paper provide a Bayesian analog of classical robust estimators.  The main disadvantage of our methods relative to the classical estimators is computational.  In Section~3 we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.  The advantages are those of Bayesian methods.  As is standard for Bayes-classical comparisons, the Bayesian method requires greater computational effort while providing better inference.  As a referee notes, asymptotically, the Bayesian and classical parameter estimates are often very close and have the same limiting posterior variance / sampling variance.  In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.'}

\response{We have also included in the discussion:

`We have found the benefits of using our Bayesian technique to outweigh the additional computational burden (relative to a classical estimator) in the situation where substantive prior information that will impact the results is available.'
}

\item I think $f(\theta|T(yobs))$ might perform better in the following scenario: when $T(yobs)$ is asymptotically biased, $E(\theta|T(yobs))$ can still be asymptotically unbiased as long as the true pa- rameter is identifiable conditioning on the summary statistic, i.e the value of $E(T(yobs))$ is unique on the true parameter. One possible example is the robust ridge-regression estimator, but it needs further investigation whether this estimator satisfies C1-C8.

\response{This idea is in perfect alignment with our work.  You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).  It is merely a statistic upon which we condition when using Bayes Theorem.

Our computational strategy provides an implementation for a big variety of conditioning statistics that are also estimators.  The ridge regression estimator does not satisfy property C5 and so, on the surface, would need a new computational development ($\hat\beta = (X'X +\lambda I)^{-1} X'y$:   $(X'X +\lambda I)^{-1} X'(y + Xv) \neq (X'X +\lambda I)^{-1} X'y + v$). But the ridge regression estimator for full rank $X'X$ is equivalent to least squares regression for conditioning.  And the least squares estimator does satisfy C1-C8.

For any hope of consistency, the models would need to distinguish between different values of $\theta$, and so a condition along the lines of uniqueness of $E(T(yobs)|\theta)$ in $\theta$ is important.  
}

\item In page 14, should $C^\perp(X)$ n - p-dimensional instead of n - p - 1-dimensional?

\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional.  $\mathcal{A}$ is $n-p-1$ dimensional as one degree of freedom is lost for each coefficient estimate and another degree of freedom is lost for the scale estimate.}

\end{enumerate}

\section{Reviewer 2 Comments}

\begin{enumerate}
\item Is the proposed framework useful for practitioners? The proposed framework targets scenario where (i) we know the data is a mixture of good and bad data, and (ii) we only want to 'build models that offer good prediction for the good portion of the data' (from the 1st paragraph of Sec 5). Authors should provide real examples in which (i) and (ii) hold. In any real examples, (i) often holds, but (ii) doesn't: if we already have had a contaminated training sample, why would we expect the test sample to contain only the good portion? In many real applications, learning the heterogeneity of the good and bad samples is precisely the goal of statistical data analysis.
For the insurance example analyzed in Sec 6, the authors should provide evidence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.

\response{I think we are in agreement that it is common to encounter data sets where a portion of the data is 'good' and a portion of the data is 'bad' (your point (i)).  The 'bad' data may be bad for many reasons, including a breakdown of the measurement process, misrecorded data, and cases that simply aren't relevant to the problem at hand.  The ability to perform a decent analysis for such data sets is important.  And the typical decent analysis focuses on (ii).  We would have little interest in predicting misrecorded test data in a typical situation or in predicting the recorded values when the measurement process has broken down.

Developing an understanding of sources of variation in the data is important.  In settings where the mechanism that produces bad data is stable, we might even entertain building a model for the bad data as is one tradition in Bayesian statistics.  But there are many instances where modelling the bad data is of little interest.

When we are in a situation where (i) and (ii) hold -- we would argue that this is the usual situation and not the exception -- and we have test data available, there would rarely be any reason to believe that the test data would be pure, consisting only of good data.  This is an important motivator of this work as described in the introduction to our paper.

We have added the following to the introduction in response to your comment and a comment from the other referee.

\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data. One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
the conditioning statistics than are methods based on the complete likelihood. Choosing statistics targeting the main features of interest allows for inference that focuses on these features. The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.'}

For the real data example:  The goal for the insurance example was derived from personal collaborations with those in the insurance industry. Privacy concerns and a turnover of executives in the company from which the data come limit our ability to provide a full description and limit our ability to provide the data themselves.  However we have expanded slightly on the goal of the analysis.   
\response{It is of concern to the company to predict closures and future performance for agencies that remain open. It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies. Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.} 
}

\item As a methodological paper, what's the guideline/recommendation given by the authors? After reading this paper, I don't know how to apply the suggested framework
on a simple regression model. Apparently, the choice of the likelihood function (for the good data) $f(y|\theta)$ and the choice of the statistic T are related.
To make things more complicated, each has multiple choices. For example, f could be normal, student-t or other heavy-tailed distribution; T could be something named Huber or Tukey although the authors are not even bothered to provide any mathematical expression.

Instead of just reporting numerical performance, the authors should provide some guidelines/recommendation on how to apply their framework on linear regression models, e.g., what are the default choices for f and T ? Is there any- way to select which f or T to use based on cross-validation or other empirical methods?

\response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.  We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults in a heavy-handed fashion.  This would be much like specifying a default likelihood if one wishes to build a regression model.  Inthe usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.  As you note, choice of the likelihood is part of the analysis when building a Bayesian model.  To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.  Omission of the formal description of the particular M-estimators that we use is an oversight.

We have taken the following steps to address your comment.  We now

\begin{enumerate}
\item Point out that M-estimators have been our default choice in the very first illustrative example:
 \response{Details of these estimators can be found in many places, including \citep{huber2009}. We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers. A short review of these estimators is provided in the Supplementary Material.}
 \item Include a short review of M-estimators in the Supplement
 \item Include `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
\end{enumerate}
}

\item What's the real benefit of this computationally expensive approximation framework? The proposed framework replies on a good summary statistic T(yobs), which
has already provided a robust estimate of the target parameter. On the other
hand, the proposed MCMC algorithm is computationally expensive. In Sec
4.2, the authors only discussed the computation cost for their proposal distribution, but ignored the computation cost for obtaining T(y) (see Theorem 4.1). Those statistics are M-estimators, i.e., they are maximizers of some objective functions involving n observations and p parameters. The authors should discuss the computation cost for T(y).
What's the gain of all the extra computation?

\response{At the end of Section 3 (note renumbering of sections) we have included a paragraph:}

\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal relative to computation of the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

\response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
}

\item The authors compare KL diver-gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y|M,yobs) is not available in closed-form; 2) since f(y|M,yobs) is not available close-form, the KL divergence is approximated and it's not clear to me how accurate the approximation is.
The authors should compare prediction and estimation accuracy, common met- rics used for regression models.

\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to a closed form version of KL divergence.  We use the KL divergence between two normals: $ 
\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2}
$
While we wouldn't be able to compute this in a real application, it does combines estimation error for both the $\theta_{i}$ and $\sigma$ and is a decent metric to compare the methods under the simulation setup. }
John - I'm puzzled by this one.  I'll have to check the paper when I get dropbox up and running again.  (Steve)

\item The simulation setup is too simple. Suggest to add some linear regression models with large p and/or large n.

\response{We feel that the first hierarchical simulation example shows how to use the method in a hierarchical setting. We have added 2 more regression covariates to the real data analysis which also contains a hierarchical example. We have also included an additional simulation studying variable selection where only a few variables are active out of many.  We hope this satisfies your suggestion.}

\end{enumerate}

\textbf{Some minor issues.}
\begin{enumerate}
\item  Abstract '... handling data sets with outliers and dealing with model mis- specification. We outline the drawbacks ... and propose a new method as an alternative.' The proposed method cannot handle 'model misspecification', instead it assumes f is the true model (no misspecification) and what's wrong is part of the data.

\response{We stand by the abstract.  The insurance company example is along the lines of a number of examples in the literature on robust regression.  Outliers -- best defined as cases which do not reflect the mechanism under study -- often have large residuals.  This does not mean that outliers are independent of one another.  They often reflect model misspecification.  The tradition of robust regression is to provide a model that discounts the outliers (that discounts the deficiencies in the model) and results in a sensible, practical analysis of the data set.  The robust analysis often points the way to an understanding of why the model fits some cases well and others poorly.  Our paper is about model misspecification as well as what some feel the word 'outlier' captures.}

\item  Sec 2 and Sec 3 can be shortened or merged.

\response{We have merged the sections.}

\item  Eq(2) in Sec 2.1, the notation f(yi|?,c(yi)) is not introduced yet; what's introduced is f(y|?).

\response{We have included a sentence for this notation after it's first use.}

\item  Sec 4.1, C3 and C4: a maximizer may not be a continuous function of the data and it may not be unique. Instead of saying 'Many estimators satisfy the above properties', the authors should list those estimators and explain why those conditions are satisfied.

\response{We have added:

\response{'These M-estimators satisfy C3 and C4 since they are optimizers of continuous and differentiable objective functions. Constraints C5-C8 are often satisfied by location and scale estimators but should be checked on a case by case basis.'}
}

\item  Bottom of p14, 'Sample z? from a distribution with known density on S.' Any distribution? For example, can it be a point mass or its support has to be equal to S? What's the sampling distribution for z? used in the simulation studies and real data analysis?

\response{Thanks for noticing this detail. It is most natural if it is mutually absolutely continuous with respect to the distribution induced by the model on S.  For the cases we discuss, this is mutually absolutely continuous with respect to the uniform distribution on S.  We now mention the importance of the support.  We have also included a description of what we use for p throughout based on a previous comment. This comment is after Theorem 4.6.}

\item  Eq (18): change dy to d$\tilde{y}$?

\response{Thanks for noticing this typo - based on your other comment on KL divergence, this formula was taken out and now is a closed form version. }

\end{enumerate}

\section{AE Comments}
This paper proposes a Bayesian approach for making inference based on robust statistics of the data instead of the original observations. The conditioning robust statistics pass the desirable robustness (to outliers) to the posterior distribution of parameters, thus having the potential to improve inference and prediction. This paper addresses an important problem in statistics and contains interesting ideas. However, there are some major concerns.
The paper focuses on outliers. Although outliers automatically imply that the model is misspecified, model misspecification is much broader including the misspecification of the density of the good data. The paper does not appear to address model misspecification beyond the case when outliers are present. Please revise the scope of the paper as appropriate or provide more examples to ensure outliers and model misspecification are parallel contributions rather than one nested in another.

\response{Model misspecification covers broad territory.  It includes traditional outliers (retaining the independence of observations, but assuming some have greater variance, for example), misspecification of the mean function in a regression setting, missed covariates for regression, missed dependence among cases, misspecified functional form for the `good' data (one reason for the growth of nonparametric Bayesian methods), and much, much more.  Box' famous aphorism is one direct statement that all models are misspecified.

Our own belief is that it would be impossible to address {\em all} forms of model misspecification, yet discussion of the issue is important.  Our paper illustrates misspecification in the real data example on the insurance companies.  The inclusion of closed agencies and agencies with different types of contracts represent model misspecification. These `outliers' are not merely the result of a huge chance error, a faulty measurement process, or a failed experimental run.  They are unusual for a reason and the analysis helps to uncover this reason (we are limited in the commentary that we can attach to the analysis).  As with many of the examples used to illustrate robust regression techniques, these data are best described as having a misspecified model.}

There are many implementation details that an interested user would like to learn more but feel difficult to find from the current paper. This includes but not limited to the selection of proposal, parameter tuning, recommendations when a practitioner is being faced with a real-world problem, and computational complexity of the entire procedure. See the two referee reports for more details.

\response{Thank you - we believe we have addressed each of these concerns based on the two reviewer's comments. Detailed responses are given above.}

The authors are also suggested to possibly provide code that is available online with recommended choices as default.

\response{We have included some 'default choices' in the paper and in the Supplement.  Information for where to obtain code on Github (an R package as well as data and code for the examples) is now provided in the Introduction.  As noted in our response to Referee 2, we hesitate to push the notion of a default likelihood and default conditioning statistic.  The paper provides a conceptual framework for data analysis and develops the methodology and computation needed to implement the analysis.  We do not view the work as developing an algorithm into which one should just feed data.}

It is unclear how the proposed method outperforms existing work, either conceptually or practically.

\response{We believe we have addressed similar concerns from the two reviewers - specifically we have included commentary on the advantages and disadvantages of the new method in several places (e.g., see Introduction) as well as some practical recommendations (e.g. See Supplement).}

Referees have provided some competing methods for the authors to consider. I'd like to add another existing strategy in addition to the three solutions mentioned in the bottom paragraph of page 2: Bayesian fractional inference, which uses a fractional likelihood function that raises a usual likelihood function to a fractional power. What is the advantage of the proposed restrictive likelihood approach over Bayesian fractional inference, even conceptually?

\response{The central advantage of our method compared to the fractional Bayes methods is that our method uses Bayes Theorem!  It is exactly Bayesian in that the posterior distribution is a rescaled version of prior distribution times likelihood (of a statistic).  This means that the method inherits a host of properties from Bayesian methods.

In contrast, the fractional Bayesian methods do not actually follow Bayes Theorem (there are exceptions in special cases).  Fractional Bayes methods use the theorem as an analogy and so miss many of the benefits of Bayes.  The fractional methods are interesting and they deserve study, but they are not the only solution to Bayesian model misspecification.

In the long run, we suspect that robust and effective Bayesian analyses will make use of ideas from a variety of perspectives that are currently under study.  The various lines of research need groups of researchers investigating them, need time to develop, and they need visibility for the community to appreciate the different perspectives and to develop an understanding of what each brings to the table.}

Overall, the paper deserves publication after careful and thorough revision. I hope the authors can address all concerns raised in this report and the two well-grounded referee reports.

\response{ Thanks!}

\section{Editor Comments}

The paper has received a mixed reaction from the two referees and the AE. I have a similar reaction to the paper but agree with the other readers that the content is such that an opportunity to address the issues raised is appropriate. The AE's comments place the paper on the border between Reject with Resubmission and Major Revision. I mention this because it isn't clear that a revision will be successful as there are some significant criticisms in the reviews.

My concerns might be a little different than the others and perhaps are less technical in nature. It is generally agreed that *all* models are wrong. The incorrectness of the model can arise in a number of ways and some observations being outliers is one of these. The natural question then is: how are we supposed to deal with that? The answer is surely that we don't unless the discrepancy is so substantial that the inferences would be seriously in error if we proceeded using the assumed model. This part of a statistical analysis is the model checking aspect and the solution to any issue, whatever it might be, arises there. For example, for the problem being considered in this paper, I would want a model checking procedure that indicated that there is a serious problem because, no matter what distribution was used from the model, some observations are outlying and I would want the methodology to identify the observations in question. In that case there would several ways to deal with the issue, including modifying the model, but also simply discarding the offending observations as part of "data cleaning". It is worth noting though that the answer isn't simple because notable scientific achievements have been obtained by looking carefully at observations that are clearly discrepant.

So there are some concerns that have relevance for me and that I think the paper needs to address. What method is used to identify that there is a problem with the model such that the inferences will be strongly affected and does it identify outlying observations?

\response{Our own training in regression is in the style of ``case analysis'' that has been written about so convincingly by Sandy Weisberg, Dennis Cook, and others.  This training matches your view of strong model diagnostics to identify deficiencies in the model.  A competing type of regression analysis common at the time was developed by Peter Huber, Peter Rousseeuw, and others.  These ``robust regression'' methods seek to automatically discount unusual cases.  Though generally described as a means of handling outliers, many of the popular examples used to illustrate the methods are clearly examples of model misspecification.  The robust methods provide excellent fits for the good (or non-to-mildly misspecified data) when there is misspecification.  Much is known and much has been written about the relative merits of the two styles of regression in various settings.

In the early 1980s, case analysis became the dominant paradigm (though robust regression retained many adherents).  Our natural inclinations match yours for the reasons you give--we would always prefer to build the perfect model.  However, there are a number of reasons why we cannot do so.  These range from the perils of overmodelling (particularly dangerous for Bayesians) to limitations on our ability to identify outliers (from Huber's book, imagine sliding the "y" value for a case from a ridiculous value--surely and outlier--to its case-deleted mean--a zero residual and not identified as an outlier; somewhere along the way, the subjective probability of the case being an outlier must be 0.5 and we would be unable to decide whether the case is an outlier), to our inability to detect modest model misspecification.  Accepting that there are limitations on case analysis and our ability to build the perfect model suggests that we need to develop alternative strategies.  These alternative strategies can even become part of our diagnostic framework:  a discrepancy between the restricted likelihood fit and the traditional Bayesian fit (or predictions) indicates a need for the case-analysis analyst to do more work.

The modern world revolves around large data sets, often with a hierarchical structure.  While case analysis works with data sets of moderate size, it breaks down when one has thousands to millions of cases.  It also breaks down when one is interested in model selection (among a class of models that are, of course, misspecified to some extent) or model averaging.  Robust methods scale much better than case analysis methods do.

The tension between case analysis methods and robust methods is not limited to the regression setting, nor is it limited to merely looking at the fits from the model.  In this work, we lay out the restricted likelihood perspective, develop a computational implementation (as referees and AE note, this development is not trivial), implement the method with code that is available on GitHub, and illustrate some of the benefits of this method relative to standard Bayesian and classical methods.  We view this as an early effort and look to tackle further problems in subsequent papers--in fact, we have given talks about issues such as Bayesian hypothesis testing and model averaging in this framework--and we see a clear path forward for a variety of problems.}

A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to choose T: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isn't clear how to do this. I understand that there are
problems where reducing the data to some T(y) is necessary, perhaps because of computational problems associated with evaluating a likelihood, but this is clearly a compromised analysis and not one we would recommend unless forced to do so. So I don't agree with the statement made in the paper "that deliberate choice of an insufficient statistic T(y) guided by targeted inference is sound practice". There needs to be a much stronger argument for this at least for me.

\response{We understand your point of view.  It focuses on dangerous territory for classical statisticans and Bayesians alike.  In keeping with your statement above that *all* models are misspecified (we agree except for a few very simple exceptions--say a single Bernoulli trial), we believe that *all* analyses are compromised.  It is also true that, as soon as one uses diagnostics that have the potential to change the model or the data (removing outliers, for example), the analysis is compromised.  The appropriate likelihood would need to account for all decisions that one might make.  These are two of the arguments made for the use of robust methods (i) that robust estimators reduce the impact of model misspecification, and (ii) that data cleaning and data-based model adjustment destroys the properties of classical tests and Bayesian methods.  It is difficult to quantify these effects, but we have seen them in the practice of data analysis.}

The paper is well-written and thought-provoking so my hope is that a revision will be able to address the points raised.

\end{document}

### 2020-05-11 revision_2/response/responseV5.tex
re-compile to get references

@@
 \response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
-}
+%}
 
@@
 \response{To address the concern you have raised, we have changed our evaluation metric in the simulation to a closed form version of KL divergence.  We use the KL divergence between two normals: $ 
-\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2}
+\log(\hat\sigma_{i}^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma_{i}^{2}}(\sigma^{2} + (\theta_{i} - \hat{\theta_{i}})^{2}
 $
@@
 
+\bibliographystyle{plain}
+\bibliography{../bib/refPaper1}
+
 \end{document}

### 2020-06-20 revision_2/paper.tex
clean up to output mse results for revision_2, minor edits to paper.:

@@
 Choosing statistics targeting main features of interest allows for more targeted inference on these features.
-The analysis can help to better understand other features, such as outliers, not capture by the conditioning statistics.}
+The analysis can help to better understand other features, such as outliers, not captured by the conditioning statistics.}
 \response{The examples in the paper suggest advantages in situations where outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data.
-The main disadvantage over traditional robust estimate techniques are mainly computational.
+The main disadvantage over traditional robust estimation techniques are mainly computational.
 In Section ~\ref{BayesLinMod} we detail a data-augmented MCMC algorithm to fit the models proposed in this paper.
@@
 Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden.
-Since it is typically that the restricted likelihood posterior converges to the same expected value as the conditioning statistics as the sample size grows, it may not be practical to implement our method in all situations.}
+Since the restricted likelihood posterior typically converges to the same expected value as the conditioning statistics, it may not be practical to implement our method in all situations.}
 
@@
 \response{ An R package \texttt{brlm} to implement our methods is available at \texttt{github.com/jrlewi/brlm}.
-Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/revision\char`_2}.}
+Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper}.}
 
@@
 \response{These M-estimators satisfy \ref{asb}-\ref{as} since they are optimizers of (almost surely) continuous and differentiable objective functions.
-Constraints  \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}  More software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
+Constraints  \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case-by-case basis.}  More software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
 The current version of the \texttt{R} package also implements the direct computational methods described in \cite{lewis2014}.
@@
 \response{Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
-We have found this burden to be marginal in relation with respect to computing the needed Jacobian.
-In the simulations and real data analyses presented below, we will see that the additional burden is often of added value over traditional robust regression when substantial prior information is available that is not swamped by current data.}
+We have found this burden to be marginal in comparison to computing the needed Jacobian.
+In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.
+This is most evident when substantive prior information is available and information in the data is limited.}
 
@@
 The first is a hierarchical setting.
-The second is a variable selection setting where there are several potential covariates where only a few have non-zero effect sizes.
+The second is a variable selection setting where there are several potential covariates but only a few have non-zero effect sizes.
 
@@
 The components of $x = (x_{1}, x_{2}, x_{3})$ are correlated with $x_1 \sim N(0,1)$ and $x_{j} = x_{1} + \eta_{j}$ with $\eta_{j} \sim N(0, 4)$ for $j = 2,3$.
-This results in a theoretical correlation of $1/sqrt(5) \approx 0.44$ between $x_{1}$ and both $x_{j}, j = 2, 3$.
+This results in a theoretical correlation of $1/\sqrt{5} \approx 0.44$ between $x_{1}$ and both $x_{j}, j = 2, 3$.
 The model used for fitting contains an additional 27 covariates, some of which are also correlated with $x_{1}$, $x_{2}$, and $x_{3}$.
@@
 We fit the model including all 30 covariates and consider the following methods for the fit 1) classical robust regression with Tukey's estimator of location and Huber's estimator of scale, 2) the corresponding restricted likelihood version 3) A heavy-tailed Bayesian model with a Student-t likelihood with $\nu = 5$ degrees of freedom.
-For the Bayesian models we take $\bbeta_{all}\sim N_{20}(\mb{0}, \sigma^{2}_{\beta}I)$ with $\bbeta_{all} = (\bbeta, \bbeta^{*})^{\top}$ and $\sigma^{2}\sim IG(5,8)$ under the restricted model and  $\sigma^{2}\sim IG(5,\frac{\nu-2}{\nu}8)$ under the Student-t model.
+For the Bayesian models we take $\bbeta_{all}\sim N_{30}(\mb{0}, \sigma^{2}_{\beta}I)$ with $\bbeta_{all} = (\bbeta, \bbeta^{*})^{\top}$ and $\sigma^{2}\sim IG(5,8)$ under the restricted model and  $\sigma^{2}\sim IG(5,\frac{\nu-2}{\nu}8)$ under the Student-t model.
 For each data set, we fit the models for $ \sigma_{\beta} = 0.4, 0.6, 0.8,\dots, 1.4$.
@@
 The average MSE plus/minus one standard error over the simulations for each $\sigma^{2}_{\beta}$ are displayed in Figure \ref{mseSimMany}.
-The classical fit is labeled `rlm` and is the same for each value of the prior standard deviation $\sigma^{2}_{\beta}$.
+The classical fit is labeled `rlm' and is the same for each value of the prior standard deviation $\sigma^{2}_{\beta}$.
 We see for most values of the the prior standard deviation, the Bayesian models (`restricted' and `t') outperform the classical fit.
@@
 \includegraphics[width = 5in]{mse_sim_many_p.png}
-\caption{Average MSE plus/minus one standard error over the $K = 30$ simulations for each value of the prior standard deviation ($\sigma^{2}_{\beta}$) and each of the fitting methods.
+\caption{Average MSE plus/minus one standard error over the $K = 30$ simulations for each value of the prior standard deviation ($\sigma_{\beta}$) and each of the fitting methods.
 `Restricted' is our method conditioning on Tukey's estimator of location and Huber's estimator of scale.
 `rlm' refers to the classical robust linear model fit with the same estimators and `t' is the heavy-tailed Bayesian model with a Student-t likelihood.
-The `rlm' results are the same for each $\sigma^{2}_{\beta}$.}
+The `rlm' results are the same for each $\sigma_{\beta}$.}
 \label{mseSimMany}
@@
 \includegraphics[width = 5in]{negll_sim_many_p.png}
-\caption{Average MNLL plus/minus one standard error over the $K = 30$ simulations for each value of the prior standard deviation ($\sigma^{2}_{\beta}$) and each of the fitting methods.
+\caption{Average MNLL plus/minus one standard error over the $K = 30$ simulations for each value of the prior standard deviation ($\sigma_{\beta}$) and each of the fitting methods.
 `Restricted' is our method conditioning on Tukey's estimator of location and Huber's estimator of scale.
 `rlm' refers to the classical robust linear model fit with the same estimators and `t' is the heavy-tailed Bayesian model with a Student-t likelihood.
-The `rlm' results are the same for each $\sigma^{2}_{\beta}$.}
+The `rlm' results are the same for each $\sigma_{\beta}$.}
 \label{negllSimMany}
@@
 Holdout evaluation is done on the remaining (`Type 1') samples.
-The acceptance rates for  the data augmentation step,\response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
+The acceptance rates for  the data augmentation step, \response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
 \response{The exception was a single training set from State 15 resulting in an usually small acceptance rate under Tukey's version.
-This case didn't effect the overall results of the simulations but emphasizes the need to check convergence on a case by case basis.} The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
+This case didn't effect the overall results of the simulations but emphasizes the need to check convergence on a case-by-case basis.} The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
 Similar results are observed for other base models.
@@
 One should take care in the method of evaluation.
-When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data or the metric should be adjusted to discount outlying data ins some way (such as the trimmed-log-marginal we introduced TLM).
+When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data or the metric should be adjusted to discount outlying data in some way (such as the trimmed-log-marginal we introduced).
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-M-estimators offer a natural choice for conditioning in restricted likelihood settings and they can be readily applied when conditioning on these estimators using the method described in this paper.
+M-estimators offer a natural choice for conditioning in restricted likelihood settings and the methods described in this paper can be readily applied when conditioning on these estimators.
 This section gives a brief review.
@@
 For consistency under the normal distribution the tuning parameter is set to $\delta\approx 0.71016$, taking $k = 1.345$ as above for Huber's $\psi$ is
-referred to as Huber's `Proposal 2'. This is estimator used throughout this this paper.
+referred to as Huber's `Proposal 2'. This estimator is used throughout this paper.
 

### 2020-06-20 revision_2/code/simulation/hierarchical_sim/2_summarizeSimulations.R

@@ -112,29 +112,29 @@ summarize_data_frames <- readRDS(file.path(here::here(), "summarize_data_frames.
 }
 
 # get acceptance rates ------
-# results_df <- file.path(getwd(), 'results')
-# accept_rates <- array(NA, c(2,length(sims), length(sig2), length(ass.vec), length(scale_vec)))
-# for(data_sim in sims){
-#   # load the data, along with the factor levels, and true values of theta
-#   data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
-#   for(ss in sig2){
-#     for(as in ass.vec){
-#       for(sc in scale_vec){
-#         rds_name <- paste0("_",data_sim, "__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
-# 
-#         huber <- read_rds(file.path(results_df, paste0("huber", rds_name)))
-# 
-#         accept_rates[1, data_sim, which(ss == sig2),which(as == ass.vec), which(sc == scale_vec)] <- mean(huber$yAccept)
-# 
-# 
-# 
-#         tukey <- read_rds(file.path(results_df, paste0("tukey", rds_name)))
-# 
-#         accept_rates[2,data_sim, which(ss == sig2),which(as == ass.vec), which(sc == scale_vec)] <- mean(tukey$yAccept)
-#       }
-#     }
-#   }
-# }
+results_df <- file.path(getwd(), 'results')
+accept_rates <- array(NA, c(2,length(sims), length(sig2), length(ass.vec), length(scale_vec)))
+for(data_sim in sims){
+  # load the data, along with the factor levels, and true values of theta
+  data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
+  for(ss in sig2){
+    for(as in ass.vec){
+      for(sc in scale_vec){
+        rds_name <- paste0("_",data_sim, "__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
+
+        huber <- read_rds(file.path(results_df, paste0("huber", rds_name)))
+
[…]

### 2020-08-15 revision_2/response/responseV3.tex
Revision 2 (#1)
* revision_2 branch to work on BA revisions

* edit ignore file

* added response folder to record our responses

* cleaned aanalysis data to include additional covariates

* edited prior parameters for single group reg. analysis with additional covatiates

* edited prior script for heirarchical set up as well

* clean up prior script to reference a general trend formula for input into lm models

* edited single group reg script to include more covariates

* started simulation with many p

* edits to hierarchical data anlaysis to include extra covariates

* edits to do batch jo

--- 2020-05-09 revision_2/response/responseV5.tex
@@
 Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk.
-As we are proposing values on a complicated manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$.
-This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.'
+As we are proposing values on a complex manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$.
+This could provide some advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.'
 
@@
 \response{For the real data, we have included two additional covariates related to the number of employees at each agency.
-These were left out originally after EDA revealed their effect sizes were small, but leaving them in makes for a good study as well.
+These were left out originally after EDA revealed their effect sizes were small, but leaving them in is a good study as well.
 We have kept the first simulation as we feel it is a good and simple illustration of the ability to fit hierarchical models with our method.
@@
 In this paper, our interest is not in these asymptotic settings where we could simply use a limiting normal distribution as the posterior over the parameters, but rather for the finite sample setting where Bayesian and frequentist methods yield different answers.
-The simulations and data analyses document this differential performance.
+The simulations and document this differential performance.
 The standard advantages of Bayes apply -- a guarantee of admissibility from a decision-theoretic view; the ability to combine information across a collection of problems (e.g., the hierarchical setting); and the transition from moment-based methods to likelihood-based methods, for example.
@@
 The main disadvantage of our methods relative to the classical estimators is computational.
-In Section~3 we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.
+In Section~\ref{BayesLinMod} we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.
 The advantages are those of Bayesian methods.
@@
 
-\response{This idea is in perfect alignment with our work.
+\response{This is idea is in perfect alignment with our work.
 You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).
@@
 
-For any hope of consistency, the models would need to distinguish between different values of $\theta$, and so a condition along the lines of uniqueness of $E(T(yobs)|\theta)$ in $\theta$ is important.
+For any hope of consistency, the models would need to distinguish between different values of $\theta$, and so a condition along the lines of uniqueness of $E(T(yobs))$ in $\theta$ is important.  
 }
@@
 
-\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional.
+\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional, but we don't see where we mentioned otherwise on page 14.
 $\mathcal{A}$ is $n-p-1$ dimensional as one degree of freedom is lost for each coefficient estimate and another degree of freedom is lost for the scale estimate.}
@@
 In settings where the mechanism that produces bad data is stable, we might even entertain building a model for the bad data as is one tradition in Bayesian statistics.
-But there are many instances where modelling the bad data is of little interest.
+But there are many instances where this is of little interest.
 
-When we are in a situation where (i) and (ii) hold -- we would argue that this is the usual situation and not the exception -- and we have test data available, there would rarely be any reason to believe that the test data would be pure, consisting only of good data.
+When we are in a situation where (i) and (ii) hold -- we would argue that this is the typical situation and not the exception -- and we have test data available, there would rarely be any reason to believe that the test data would be pure, consisting only of good data.
 This is an important motivator of this work as described in the introduction to our paper.
@@
 Choosing statistics targeting the main features of interest allows for inference that focuses on these features.
-The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.'}
+The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.}
 
@@
 \response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.
-We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults in a heavy-handed fashion.
+We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults so heavy-handedly.
 This would be much like specifying a default likelihood if one wishes to build a regression model.
-Inthe usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.
 As you note, choice of the likelihood is part of the analysis when building a Bayesian model.
 To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.
-Omission of the formal description of the particular M-estimators that we use is an oversight.
+Omission of the formal description of the particular M-estimators we use is an oversight.
 
-We have taken the following steps to address your comment.  We now
+We have taken the following steps to address your comment:
 
 \begin{enumerate}
-\item Point out that M-estimators have been our default choice in the very first illustrative example:
+\item Point out that M-Estimators have been our default choice in the very first illustrative example:
  \response{Details of these estimators can be found in many places, including \citep{huber2009}.
@@
 A short review of these estimators is provided in the Supplementary Material.}
- \item Include a short review of M-estimators in the Supplement
- \item Include `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
+ \item Included a short review of M-Estimators in the Supplement
+ \item Included a `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
 \end{enumerate}
@@
 
-\response{At the end of Section 3 (note renumbering of sections) we have included a paragraph:}
+\response{At the end of section 4 we have included a paragraph:}
 
@@
 
-\response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
+Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages.
 }
@@
 This comment is after Theorem 4.6.}
+John - a little puzzled by what was intended here.  (Steve)
 
@@
 
-\response{Thank you - we believe we have addressed each of these concerns based on the two reviewer's comments. Detailed responses are given above.}
+\response{Thank you - we believe we have addressed each of these concerns based on the the 2 reviewer's comments. Detailed responses are given above.}
 
@@
 
-\response{We believe we have addressed similar concerns from the two reviewers - specifically we have included commentary on the advantages and disadvantages of the new method in several places (e.g., see Introduction) as well as some practical recommendations (e.g.
+\response{We believe we have addressed similar concerns from the two reviewers - specifically we have included in several areas the advantages and disadvantages (e.g., see Introduction) we have found as well as practical recommendations (e.g.
 See Supplement).}
@@
 In contrast, the fractional Bayesian methods do not actually follow Bayes Theorem (there are exceptions in special cases).
-Fractional Bayes methods use the theorem as an analogy and so miss many of the benefits of Bayes.
+The use the theorem as an analogy and so miss many of the benefits of Bayes.
 The fractional methods are interesting and they deserve study, but they are not the only solution to Bayesian model misspecification.
@@
 In the long run, we suspect that robust and effective Bayesian analyses will make use of ideas from a variety of perspectives that are currently under study.
-The various lines of research need groups of researchers investigating them, need time to develop, and they need visibility for the community to appreciate the different perspectives and to develop an understanding of what each brings to the table.}
+But the various lines of research need time and effort to develop, and they need visibility for the community to appreciate the perspectives and to develop an understanding of what each brings to the table.}
 
@@
 
-\response{ Thanks!}
-
-\section{Editor Comments}
+\section{Editor Comments} \response{unknown response at this point ???}
 
@@
 
-\response{Our own training in regression is in the style of ``case analysis'' that has been written about so convincingly by Sandy Weisberg, Dennis Cook, and others.
-This training matches your view of strong model diagnostics to identify deficiencies in the model.
-A competing type of regression analysis common at the time was developed by Peter Huber, Peter Rousseeuw, and others.
-These ``robust regression'' methods seek to automatically discount unusual cases.
-Though generally described as a means of handling outliers, many of the popular examples used to illustrate the methods are clearly examples of model misspecification.
-The robust methods provide excellent fits for the good (or non-to-mildly misspecified data) when there is misspecification.
-Much is known and much has been written about the relative merits of the two styles of regression in various settings.
-
-In the early 1980s, case analysis became the dominant paradigm (though robust regression retained many adherents).
-Our natural inclinations match yours for the reasons you give--we would always prefer to build the perfect model.
-However, there are a number of reasons why we cannot do so.
-These range from the perils of overmodelling (particularly dangerous for Bayesians) to limitations on our ability to identify outliers (from Huber's book, imagine sliding the "y" value for a case from a ridiculous value--surely and outlier--to its case-deleted mean--a zero residual and not identified as an outlier; somewhere along the way, the subjective probability of the case being an outlier must be 0.5 and we would be unable to decide whether the case is an outlier), to our inability to detect modest model misspecification.
-Accepting that there are limitations on case analysis and our ability to build the perfect model suggests that we need to develop alternative strategies.
-These alternative strategies can even become part of our diagnostic framework:  a discrepancy between the restricted likelihood fit and the traditional Bayesian fit (or predictions) indicates a need for the case-analysis analyst to do more work.
-
-The modern world revolves around large data sets, often with a hierarchical structure.
-While case analysis works with data sets of moderate size, it breaks down when one has thousands to millions of cases.
-It also breaks down when one is interested in model selection (among a class of models that are, of course, misspecified to some extent) or model averaging.
-Robust methods scale much better than case analysis methods do.
-
-The tension between case analysis methods and robust methods is not limited to the regression setting, nor is it limited to merely looking at the fits from the model.
-In this work, we lay out the restricted likelihood perspective, develop a computational implementation (as referees and AE note, this development is not trivial), implement the method with code that is available on GitHub, and illustrate some of the benefits of this method relative to standard Bayesian and classical methods.
-We view this as an early effort and look to tackle further problems in subsequent papers--in fact, we have given talks about issues such as Bayesian hypothesis testing and model averaging in this framework--and we see a clear path forward for a variety of problems.}
-
 A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to choose T: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isn't clear how to do this.
@@
 
-\response{We understand your point of view.
-It focuses on dangerous territory for classical statisticans and Bayesians alike.
-In keeping with your statement above that *all* models are misspecified (we agree except for a few very simple exceptions--say a single Bernoulli trial), we believe that *all* analyses are compromised.
-It is also true that, as soon as one uses diagnostics that have the potential to change the model or the data (removing outliers, for example), the analysis is compromised.
-The appropriate likelihood would need to account for all decisions that one might make.
-These are two of the arguments made for the use of robust methods (i) that robust estimators reduce the impact of model misspecification, and (ii) that data cleaning and data-based model adjustment destroys the properties of classical tests and Bayesian methods.
-It is difficult to quantify these effects, but we have seen them in the practice of data analysis.}
-
 The paper is well-written and thought-provoking so my hope is that a revision will be able to address the points raised.

### 2020-08-15 revision_2/code/calls/t.data.R

@@ -1,0 +1,22 @@
+N <- 21
+y <- 
+c(1.77495235091167, 1.88706964903238,
+1.98787434815435, 2.09186406167839, 2.17475172148416,
+2.36085400111802, 2.484906649788, 2.60268968544438,
+2.70136121295141, 2.77881927199042, 3.05400118167797,
+4.77912349311153, 4.82028156560504, 4.95582705760126,
+5.06890420222023, 5.2040066870768, 5.35658627467201,
+3.76120011569356, 3.17805383034795, 3.29583686600433,
+3.36729582998647)
+x <- 
+c(-8.5, -7.5, -6.5, -5.5, -4.5, -3.5, -2.5, -1.5,
+-0.5, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,
+10.5, 11.5)
+mu0 <- 
+c(1.87185585035901, 0.0329789838958981)
+Sigma0 <- 
+structure(c(0.844441154194554, 0.0799395833422342,
+0.0799395833422342, 0.00761329365164136),
+.Dim = c(2, 2))
+a0 <- 2
+b0 <- 1

### 2020-08-15 revision_2/code/data_analysis/0_prior.R

@@ -1,0 +1,272 @@
+# Script to set up prior distributions ----
+
+library(MASS)
+library(tidyverse)
+library(MCMCpack)
+
+prior_data <- read_rds(file.path(here::here(), 'data', 'prior_data.rds'))
+prior_data <- prior_data %>% 
+  mutate(sqrt_count_2008 = sqrt(Count_2008), 
+         sqrt_count_2010 = sqrt(Count_2010))  %>% filter(Type == 1)
+
+trend <- sqrt_count_2010 ~ sqrt_count_2008 - 1 + 
+  Associate_Count +
+  Office_Employee_Count
+# pooled regression analysis ----
+prior_fit <- MASS::rlm(trend, 
+                       scale.est = 'Huber', data =  prior_data)
+
+
+# MASS::rlm(sqrt_count_2012 ~ sqrt_count_2010 - 1, scale.est = 'Huber', data =  analysis_data )
+
+theme_set(theme_bw(base_family = 'Times'))
+#+ xlim(c(0,150)) +  ylim(c(0, 130)) +
+ggplot(prior_data, aes(x = sqrt_count_2008, y = sqrt_count_2010, 
+                       col = Type)) + geom_point(size = .3) + 
+  stat_smooth(method = "rlm", formula = y ~ x -1, 
+              method.args = list(scale.est = 'Huber'), 
+              size = .5, lty = 2, se = FALSE, col = 1) + 
+  guides(col = guide_legend(title = 'Agency Type'))
+
+
+summary(prior_fit)
+beta_0 <- coef(prior_fit)
+sigma_beta_0 <- vcov(prior_fit)
+beta_var_inflate <- nrow(prior_data)
+sigma2_hat <- prior_fit$s^2
+
+a_0 <- 5
+b_0 <- sigma2_hat*(a_0 - 1)
+
+b_0/(a_0 - 1)
+b_0^2/((a_0-1)^2*(a_0-2))
+
+curve(dinvgamma(x, a_0,b_0), from=0, to=.01)
+
+
+parms_prior <- list(beta_0 = beta_0, sigma_beta_0 = sigma_beta_0, 
+                    sigma2_hat = sigma2_hat, 
+                    a_0 = a_0, b_0 = b_0, 
+                    beta_var_inflate = beta_var_inflate,
[…]

### 2020-08-15 revision_2/code/data_analysis/1_single_group_reg_analysis.R

@@ -1,0 +1,397 @@
+# Regressions within a single state 
+
+# download brlm package if needed
+# library(devtools)
+# install_github('brlm', 'jrlewi')
+library(MCMCpack)
+library(MASS)
+library(brlm)
+library(tidyverse)
+
+
+strt <- Sys.time()
+
+states <- c(2, 15, 27, 36)
+ns <- c(25, 50) 
+v_inflate <- c(100)
+
+sims <- 1:50
+reps <-  length(sims)# number of training sets
+
+nburn <- 1e4 #set length of mcmc chains
+nkeep <- 1e4
+nkeept <- 1e4
+nburnt <- 2e4 #for the t-model.
+nu <- 5
+#set seed 
+set.seed(min(sims))
+
+trend_prior <- sqrt_count_2010 ~ sqrt_count_2008 - 1 + 
+  Associate_Count +
+  Office_Employee_Count
+
+trend <- sqrt_count_2012 ~ sqrt_count_2010 - 1 + 
+  Associate_Count +
+  Office_Employee_Count
+
+for(State_keep in states){
+  
+#prior -----
+prior_data <- read_rds(file.path(here::here(), 'data', 
+                                 'prior_data.rds'))
+# cnts <- prior_data %>%  group_by(State) %>% summarize(n = n())
+# View(cnts)
+prior_data <- prior_data %>% 
+  mutate(sqrt_count_2008 = sqrt(Count_2008), 
+         sqrt_count_2010 = sqrt(Count_2010))  %>% 
+    filter(State == State_keep, Type == 1, Count_2010 > 0)
+
+# ggplot(prior_data) + geom_point(aes(x = sqrt_count_2008, y = sqrt_count_2010)) + xlim(c(0,100)) +ylim(c(0,100))
+
+# pooled regression analysis ----
+prior_fit <- MASS::rlm(trend_prior, 
+                        scale.est = 'Huber', 
+                        data =  prior_data, maxit = 100)
+
+# theme_set(theme_bw(base_family = 'Times'))
+# ggplot(prior_data, aes(x = sqrt_count_2008, y = sqrt_count_2010)) + geom_point(size = 1) + stat_smooth(method = "rlm", formula = y ~ x - 1, method.args = list(scale.est = 'Huber', maxit = 100), size = .5, lty = 2, se = FALSE, col = 1) + guides(col = guide_legend(title = 'Agency Type'))
+
+#load analysis data -------
+
[…]

### 2020-08-15 revision_2/code/data_analysis/2_summarize_single_reg_analysis.R

@@ -1,0 +1,282 @@
+# Summarize the output from single regression per state analyses.
+library(tidyverse)
+library(MASS)
+
+
+ns <- c(25, 50) #sample size for training set
+states <- c(2, 15, 27, 36)
+v_inflate <- c(100)
+
+# plots ---- 
+analysis_data <- read_rds(file.path(here::here(), 'data', 
+                                    'analysis_data.rds'))
+
+analysis_data <- analysis_data %>% 
+  mutate(sqrt_count_2010 = sqrt(Count_2010), 
+         sqrt_count_2012 = sqrt(Count_2012)) %>% 
+  filter(State %in% states) %>% 
+  mutate(State = droplevels(State))
+
+label_vals <- c('2' = 'State 2', '15' = 'State 15', 
+                '27' = 'State 27', '36' = 'State 36')
+ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, 
+                        col = Type), size = 1, alpha = .5) + 
+  theme_bw() + 
+  facet_wrap(~State, labeller = labeller(State = label_vals)) + 
+  labs(x = 'square root of 2010 houshold count', 
+       y = 'square root of 2012 houshold count') +
+  theme(text = element_text(family = 'Times'))
+ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+
+
+
+cnts <- analysis_data %>% group_by(State) %>% 
+  summarise(n = n())
+# 
+# ggplot(analysis_data) + geom_point(aes(x = sqrt_count_2010, y = sqrt_count_2012, col = Type), size = 1, alpha = .25) +
+#   facet_wrap(~State, labeller = label_bquote(State ~ .(State)))+ 
+#   theme_bw() + 
+#   labs(x = 'square root of 2010 houshold count', y = 'square root of 2012 houshold count') +
+#   theme(text = element_text(family = 'Times'))
+# ggsave(file.path(getwd(), "..", "..", "figs", 'scatter_by_state.png'), width = 6, height = 4)
+# 
+
+
+
+logical_ytibble <- function(y_open, colname){
+  #works on y_open, y_type1 logical matrices
+  y_open <- t(y_open)
+  rownames(y_open) <- 1:nrow(y_open)
+  y_open <- as_tibble(y_open, rownames = 'holdout sample')
+  y_open %>% 
[…]

### 2020-08-15 revision_2/code/data_analysis/3_hier_reg_analysis.R

@@ -1,0 +1,866 @@
+# Hierarchical regression - i.e., grouped by states. 
+
+# download brlm package if needed
+# library(devtools)
+# install_github('jrlewi/brlm')
+library(sampling) #for stratified sampling
+library(MCMCpack)
+library(MASS)
+library(brlm)
+library(tidyverse)
+
+sim_number <- 5 #for batch processing
+nburn <- 2e3 #set length of mcmc chains
+nkeep <- 2e3
+nburnt <- 1e4
+nkeept <- 2e3 #for the t-model.
+maxit <- 1000 #parameter in MASS::rlm
+
+# aux funcitons ----
+
+fn.compute.marginals.hierModelNormal<-function(betalsamples, sigma2lsamples, yhold,Xhold){
+  
+  
+  fits<-function(betahats, X){X%*%betahats}
+  
+  betalSampsList <- lapply(1:dim(betalsamples)[3],function(x) betalsamples[,,x])
+  names(betalSampsList) <- names(yhold)
+  #holdout means
+  
+  nMuList<-mapply(fits, betalSampsList, Xhold)
+  
+  #sd's across samples for each holdout set
+  nSigmaList<-split(sqrt(sigma2lsamples), rep(1:ncol(sigma2lsamples), each = nrow(sigma2lsamples)))
+  names(nSigmaList)<-names(yhold)
+  
+  mapply(FUN=function(yh,mean,sd){
+    pdfs <- dnorm(yh,mean,matrix(rep(sd, length(yh)), length(yh), length(sd),byrow=TRUE))
+    mns <- rowMeans(pdfs)
+    sds <- apply(pdfs, 1, sd)
+    cbind(mns, sds)
+  }
+  ,yhold,nMuList,nSigmaList)
+  
+}
+
+fn.compute.marginals.hierModelTmodel <- function(betalsamples, sigma2lsamples, yhold,Xhold){
+  
+  fits<-function(betahats, X){X%*%betahats}
+  
+  betalSampsList<-lapply(1:dim(betalsamples)[3],function(x) betalsamples[,,x])
+  names(betalSampsList)<-names(yhold)
+  #holdout means
+  nMuList<-mapply(fits, betalSampsList, Xhold)
+  
+  #sd's across samples for each houldout set
+  nSigmaList<-split(sqrt(sigma2lsamples), rep(1:ncol(sigma2lsamples), each = nrow(sigma2lsamples)))
+  names(nSigmaList)<-names(yhold)
+  
+  mapply(FUN=function(yh,mean,sd){
[…]

### 2020-08-15 revision_2/code/data_analysis/4_summarize_hier_reg_analysis.R

@@ -1,0 +1,405 @@
+# Summarize the output from pooled regression analysis.
+library(tidyverse)
+library(MASS)
+library(abind)
+
+ns <- c(1547)
+#process in batches? combine results first
+num_batch <- 5
+rds_path <- "~/Dropbox/school/osu/dissertationResearch/snm/journal_papers/brlm_paper/revision_2/code/data_analysis/hier_reg_n1547_sim_number_"
+tmp1 <- readRDS(file.path(paste0(rds_path, 1, '.rds')))
+
+#combine results into one
+for(i in 2:num_batch){
+  tmp <-  readRDS(file.path(paste0(rds_path, i, '.rds')))
+  
+  tmp1$y_hold <- rbind(tmp1$y_hold, tmp$y_hold)
+  tmp1$y_open <- rbind(tmp1$y_open, tmp$y_open)
+  tmp1$y_type1 <- rbind(tmp1$y_hold, tmp$y_type1)
+  tmp1$holdIndices <- rbind(tmp1$holdIndices, tmp$holdIndices)
+  tmp1$group_estimates <- abind(tmp1$group_estimates, tmp$group_estimates, along = 4)
+  tmp1$group_estimates_sds <- abind(tmp1$group_estimates_sds, tmp$group_estimates_sds, along = 4)
+  tmp1$estimates <- abind(tmp1$estimates, tmp$estimates, along = 3)
+  tmp1$estimates_sd <- abind(tmp1$estimates_sd, tmp$estimates_sd, along = 3)
+  tmp1$marginals <- abind(tmp1$marginals, tmp$marginals, along = 2)
+  tmp1$marginals_sd <- abind(tmp1$marginals_sd, tmp$marginals_sd, along = 2)
+  tmp1$predictions <- abind(tmp1$predictions, tmp$predictions, along = 2)
+  tmp1$acceptY <- abind(tmp1$acceptY, tmp$acceptY, along = 3)
+  tmp1$group_converge <- abind(tmp1$group_converge, tmp$group_converge, along = 4) 
+  tmp1$converge <- abind(tmp1$converge, tmp$converge, along = 3) 
+  
+  }
+
+#write combined results to rds.
+write_rds(tmp1, file.path(file.path(getwd(), paste0('hier_reg_n', ns,".rds"))))
+
+
+analysis_data <- read_rds(file.path(here::here(), 'data', 'analysis_data.rds'))
[…]

### 2020-08-15 revision_2/code/data_analysis/data/nw_data_clean.R

@@ -1,0 +1,263 @@
+library(MASS)
+library(tidyverse)
+
+load('/Users/john/Dropbox/school/osu/dissertationResearch/snm/linearRegression/nwPaper1upDate/workSpaces/nwdataPrepPaper1DataCleanWorkspace.RData')
+
+analysisSet <- as_tibble(analysisSet)
+priorDataSet <-  as_tibble(priorDataSet)
+
+analysisSet <- analysisSet %>% 
+  dplyr::select(Agency_Type, Primary_Agency_State, 
+                Ending_HH_Count2010, Ending_HH_Count2012, 
+                Associate_Count,
+                Office_Employee_Count)
+
+
+
+priorDataSet <- priorDataSet %>% 
+  dplyr::select(Agency_Type, Primary_Agency_State, 
+                Ending_HH_Count2008, Ending_HH_Count2010,
+                Associate_Count,
+                Office_Employee_Count)
+
+
+#Change State Level Names -----
+set.seed(124)
+perm <- sample(1:(length(levels(analysisSet$Primary_Agency_State))-1))
+
+analysisSet <- analysisSet %>% 
+  mutate(State = factor(Primary_Agency_State, labels = perm ))
+
+priorDataSet <- priorDataSet %>% 
+  mutate(State = factor(Primary_Agency_State, labels = perm ))
+
+ind_check1 <- with(analysisSet, table(Primary_Agency_State, State)) %>% 
+  apply(., 2, function(x) which(x != 0))
+ind_check2 <- with(priorDataSet, table(Primary_Agency_State, State))%>% 
+  apply(., 2, function(x) which(x != 0))
+all.equal(ind_check1, ind_check2)
+all.equal(names(ind_check1), names(ind_check2))
+  
+# View(analysisSet %>% dplyr::select(Primary_Agency_State, State))
+# View(priorDataSet %>% dplyr::select(Primary_Agency_State, State))
+(unique(priorDataSet$State))
+
+# Change Agency Type Level Names ----
+types <- unique(c(levels(analysisSet$Agency_Type),
+                  levels(priorDataSet$Agency_Type)))
+
+type1 <- which(types == 'CAREER')
+type12 <- which(types == 'PASPORT2')
+set.seed(124)
+perm <- sample(seq_along(types))
+perm <- sapply(perm, function(x){
+  if(x == perm[which(perm == perm[type1])]){
+    1
+  } else {
[…]

### 2020-08-15 revision_2/code/simulation/hierarchical_sim/2_summarizeSimulations.R

@@ -1,0 +1,659 @@
+#
+# Summarize the simulations ---
+#
+library('tidyverse')
+New_results <- FALSE
+
+
+sims <- 1:30
+ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
+scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
+sig2 <- 4
+results_df <- file.path(getwd(), 'results')
+if(New_results){
+
+dfs_all <- vector('list', length(sims))
+results_df <- file.path(getwd(), 'results')
+accept_rates <- array(NA, c(2,length(sims), length(sig2), length(ass.vec), length(scale_vec)))
+
+for(data_sim in sims){
+# load the data, along with the factor levels, and true values of theta
+data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
+n_groups <- length(data$theta)
+factor_list <- as.data.frame(do.call(rbind, data$factorsList))  
+names(factor_list) <- c('p', 'n','m')
+
+# MSE evaluation metric -----
+
+dfs <- vector('list', length(ass.vec)*length(scale_vec)*length(sig2))
+
+
+i <- 1
+for(ss in sig2){
+  for(as in ass.vec){
+    for(sc in scale_vec){
+      rds_name <- paste0("_",data_sim, "__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
+    
+    huber <- read_rds(file.path(results_df, paste0("huber", rds_name)))
+    
+    accept_rates[1, which(ss == sig2),which(as == ass.vec), which(sc == scale_vec)] <- mean(huber$yAccept)
+    
+    #computes the estimates --- 
+    theta_huber_rest <- apply(huber$theta, 2, mean)
+    theta_huber_rlm  <- sapply(huber$robustFits, function(x) x$coefficients)
+    sigma2_huber_rest <- apply(huber$sigma2, 2, mean)
+    sigma2_huber_rlm  <- sapply(huber$robustFits, function(x) summary(x)$sigma^2)
+    
+    huber_df <- as_tibble(cbind(factor_list, theta = rep(data$theta,2), 
+                       theta_hat = c(theta_huber_rest, theta_huber_rlm), 
+                       sigma2_hat = c(sigma2_huber_rest,  sigma2_huber_rlm),
+                       statistic = rep('Huber', 2*n_groups), 
[…]

### 2020-08-15 revision_2/code/simulation/hierarchical_sim/convergence_checks.R

@@ -1,0 +1,98 @@
+#convergence checks -----
+
+library(MCMCpack)
+library(tidyverse)
+
+
+
+sims <- 1:30
+
+ass.vec <- c(1.25, 5, 10) #c(1.25, 2.5,5,10,20) 
+scale_vec <- c(0.5,1, 2) #round(c(0.5, 1/sqrt(2),1, sqrt(2), 2),2)
+ss <- 4 #sigma2
+convergence_scores <- array(NA, c(length(sims),3,  length(ass.vec), length(scale_vec), 182)) #sims, models, ass.vec, scale_vec, parameters
+
+for(data_sim in sims){
+  # load the data, along with the factor levels, and true values of theta
+  data <- read_rds(file.path(getwd(),'data_sig2_4', paste0('data_', data_sim, '.rds')))
+  n_groups <- length(data$theta)
+  results_df <- file.path(getwd(), 'results')
+
+    for(as in ass.vec){
+      for(sc in scale_vec){
+        rds_name <- paste0("_",data_sim, "__as_", as,"__scale_as_", sc, "__sig2_", ss, ".rds")
+        
+        fit <- read_rds(file.path(results_df, paste0("huber", rds_name)))
+        th <-  geweke.diag(mcmc(fit$theta))$z
+        sig2 <-  geweke.diag(mcmc(fit$sigma2))$z
+        tauMu <- geweke.diag(mcmc(cbind(fit$mu, fit$tau2)))$z
+        convergence_scores[data_sim, 1, which(as == ass.vec), which(sc == scale_vec),] <- c(th, sig2, tauMu)
+        
+        fit <- read_rds(file.path(results_df, paste0("tukey", rds_name)))
+        th <-  geweke.diag(mcmc(fit$theta))$z
+        sig2 <-  geweke.diag(mcmc(fit$sigma2))$z
+        tauMu <- geweke.diag(mcmc(cbind(fit$mu, fit$tau2)))$z
+        convergence_scores[data_sim, 2, which(as == ass.vec), which(sc == scale_vec),] <- c(th, sig2, tauMu)
+
+        
+        fit <- read_rds(file.path(results_df, paste0("normal", rds_name)))
+        th <-  geweke.diag(mcmc(fit$theta))$z
[…]

### 2020-08-15 revision_2/code/simulation/simulation_location_scale/2_summarize_simulation1.R

@@ -1,0 +1,57 @@
+# summarize simulation 1
+library(tidyverse)
+library(stringr)
+
+results_dir <- str_subset(dir(getwd()), 'results_true_model')
+results_dir <- results_dir[[4]]
+results_all <- map(results_dir, function(dir){
+  tib <- read_rds(file.path(dir, "KL_all_long.rds"))
+  tib$true_model <- str_sub(dir, 20)
+  tib
+})
+
+results_all <- bind_rows(results_all)
+
+KL_means <- results_all %>% 
+  group_by(true_model, n, `Fitted Model`) %>% 
+  summarise(mean_KL = mean(KL), sd_KL = sd(KL), `# simulations` = n())
+KL_means$n <- factor(KL_means$n, levels = c("50", "100", "200"))
+
+# mse_all <- results_all %>% 
+#   group_by(true_model, n, `Fitted Model`) %>% 
+#   summarise(MSE = mean((mean-0)^2), sd_mean = sd(mean), bias = mean(mean), `# simulations` = n())
+# mse_all$n <- factor(mse_all$n, levels = c("25", "50"))#, "100"))
+
+# plot(sqrt(mse_all$MSE), mse_all$sd_mean)
+
+ggplot(KL_means, aes(x = n, y = mean_KL, col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 1, scales = 'free')
+
+ggplot(KL_means, aes(x = n, y = sd_KL, col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 1, scales = 'free')
+
+
+
+
+
+
+# 
+# ggplot(mse_all, aes(x = n, y = bias , col = `Fitted Model`, group = `Fitted Model`)) + geom_point(alpha = .5) + geom_line(alpha = .5) + facet_wrap(~true_model, nrow = 2, scales = 'free')
+
+# #plot relative MSE's
+# 
+# # make the levels of true_model match those of `Fitted Model`
+# mse_all$true_model <- factor(sapply(mse_all$true_model, function(x){
+#   if(x == 'mixture 1') {a <- 'Mixture 1'}
+#   if(x == 'mixture 2') {a <- 'Mixture 2'}
+#   if(x == 'normal') {a <- 'Normal'}
[…]

### 2020-08-15 revision_2/code/simulation/simulation_many_p/1_simulation.R

@@ -1,0 +1,468 @@
+# Consider regression problem with many p, larger n,
+# and outliers
+
+library(tidyverse)
+library(brlm)
+library(MCMCpack)
+set.seed(123)
+#Simulation Parameters ----- 
+n_sims <- 30
+n <- 500 #sample size
+p <- 3 #active covariates
+beta <- rep(1, p)
+sigma2 <- 2
+p_extra <- 30 - p #inactive covariates
+num_corr <- 6 # number of extra covariates to correlate with the active ones
+a_0 <- 5
+b_0 <- 8 
+sd_cor_1 <- 2 # sd for cor between the x's
+sd_cor_2 <- 1 # sd for cor between true x's and extra x's
+
+prob_outlier <- .2
+outlier_contam <- 25
+mu_0 <-  rep(0, p + p_extra)
+prior_sd <- seq(.4, 1.4, by = .2) # c(.4, 1) # 
+# Sigma_0 = diag(p+p_extra),
+nkeep <- 1000
+nburn <- 1500
+maxit <- 1000
+nu <- 5 #df for t_fit
+
+
+# helper functions -----
+data_generation <- function(n, p, p_extra,
+                               beta = NULL,
+                               sigma2 = NULL,
+                               a_0,
+                               b_0,
+                               prob_outlier,
+                               outlier_contam, 
+                               sd_cor_1,
+                               sd_cor_2,
+                               num_corr){
+  #num_corr is the number of X_extras to correlate with one of the active covariates
+  
+  if(is.null(beta)){
+  beta <- rnorm(p, 0, 1)
+  } else {
+    p <- length(beta)
+  }
+  if(is.null(sigma2)){
+  sigma2 <- rinvgamma(1, a_0, b_0)
+  }
+  
+  
+  
+  X <- matrix(NA, n, p)
+  x1 <- rnorm(n)
+  X[,1] <- x1
+  for(ii in 2:p){
+    X[,ii] <- x1 + rnorm(n, sd = sd_cor_1) 
+  }
+  # consider some correlation structure for the extra covariates
+  #n_groups <- floor(p_extra/p)
+  #extra <- lapply(1:n_groups, function(a){
+  
+  if (num_corr > p_extra) { 
+    num_corr <- p_extra 
+    }
+  X_extra <- matrix(NA, n, num_corr)
+which_active <- rep(1:p, length.out = num_corr)
+  for (jj in 1:num_corr) {
[…]

### 2020-11-02 revision_2/response/Drafts of response to referees/response.tex
clean up and add abc analysis script

--- 2019-06-14 revision_2/response/response.tex
@@
 A short review of these estimators is provided in the Supplementary Material.}
- \item Included a review of M-Estimators in the Supplement
+ \item Included a short review of M-Estimators in the Supplement
  \item Included a `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
@@
 
-\response{We have changed to the metric to address the estimation concern you bring up. The metric is $ 
-\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{2\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2}
+\response{We have changed to a closed form version of KL between two normals to address estimation concern you bring up: $ 
+\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2}
 $
-which combines estimation error for both the $\theta_{i}$ and $\sigma$.
-While we couldn't compute this metric in a real analysis since we wouldn't know the $\theta_{i}$ and $\sigma$, we feel it is best to make this direct comparison since we know them in the simulation.}
+While we wouldn't be able to compute this in a real application it does combines estimation error for both the $\theta_{i}$ and $\sigma$ and is a decent metric to compare the methods under the simulation setup.
+}
 
@@
 \item  Eq (18): change dy to d$\tilde{y}$?
-\response{Thanks for noticing this typo - based on your other comment we are using a different metric then KL divergence and so this equation is no longer in the paper.}
+\response{Thanks for noticing this typo - based on your other comment on KL divergence, this formula was taken out and now is a closed form version. }
 

### 2020-11-02 revision_2/response/response_to_editorial_comments.tex
clean up and add abc analysis script

\documentclass{article}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\usepackage{graphicx, psfrag, amsfonts, float}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{hhline}
 \pdfminorversion=4
\usepackage{rotating}
\def\bgam{\mbox{\boldmath $\gamma$}}
\def\bth{\mbox{\boldmath $\theta$}}
\def\bbeta{\mbox{\boldmath $\beta$}}
\def\blam{\mbox{\boldmath $\lambda$}}
\def\bmu{\mbox{\boldmath $\mu$}}

\newcommand{\bx}{\mbox{\boldmath $x$}}
\newcommand{\bu}{\mbox{\boldmath $u$}}
\newcommand{\bc}{\mbox{\boldmath $c$}}
\newcommand{\bs}{\mbox{\boldmath $s$}}
\newcommand{\by}{\mbox{\boldmath $y$}}
\newcommand{\bz}{\mbox{\boldmath $z$}}
\newcommand{\bv}{\mbox{\boldmath $v$}}
\newcommand{\bb}{\mbox{\boldmath $b$}}
\newcommand{\bzero}{\mbox{\boldmath $0$}}
\newcommand{\thstarj}{\mbox{$\theta^\star_j$}}
\newcommand{\bths}{\mbox{$\btheta^\star$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\uI}{\mathrm{I}}
\newcommand{\uP}{\mathrm{P}}
\newcommand{\up}{\mathrm{p}}
\newcommand{\mb}{\mathbf}
\newcommand{\mc}{\mathcal}

\newcommand{\Bern}{\mbox{Bern}}
\newcommand{\Nor}{\mbox{N}}
\newcommand{\Ga}{\mbox{Gamma}}
\newcommand{\Dir}{\mbox{Dir}}
\newcommand{\Ber}{\mbox{Ber}}
\newcommand{\Be}{\mbox{Be}}
\newcommand{\Unif}{\mbox{Unif}}
\newcommand{\Binom}{\mbox{Bin}}
\newcommand{\IG}{\mbox{IG}}

\newcommand{\Xs}{X^\star}
\newcommand{\Lc}{{\cal L}}

\usepackage[dvipsnames,usenames]{color}
\newcommand{\yy}{\color{magenta}\it}
\newcommand{\jj}{\color{Black}\rm}
\newcommand{\yjnote}[1]{\footnote{\color{Brown}\rm #1 \color{Black}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{\bf Definition}
\newtheorem{lemma}[theorem]{\bf Lemma}
\newtheorem{corollary}[theorem]{\bf Corollary}
\newtheorem{proposition}[theorem]{\bf Proposition}
\newtheorem{assumption}[theorem]{\bf Assumption}
\newtheorem{example}[theorem]{\bf Example}
\newtheorem{remark}[theorem]{\bf Remark}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\stackrel{indep}{\sim}}

\setlength{\textwidth}{6 in}
\usepackage{color}
\usepackage{ulem} % \sout
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\brown}[1]{{\color{brown}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}
\newcommand{\response}[1]{{\color{blue}#1}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\graphicspath{{figures/}{figs/}}

\begin{document}

\section{Reviewer 1 Comments}

\begin{enumerate}
\item The authors propose a broad class of the proposal density, but didn't discuss the choice and tuning within the class. Tuning the proposal is crucial to the mixing and efficiency of the MH algorithm, epecially in the high-dimension space, $n-p$-dimensional, that the paper is dealing with. There are two difficulties in tuning within the proposed class. First, since the proposal density is a complicated transformation of $p(z^{*})$ in $R^{n-p-1}$, even if $p(z^{*})$ belongs to a standard parametric family, $p(z^{*})$ does not and it is not straightforward to assess the properties that are usually used in tuning MCMC algorithm, e.g. mode and
tails behaviour. Second, the proposed algorithm (11) is restrictive because it only works for independent proposal, not the random walk proposal. Random walk is more able to explore a non-standard parameter space like the manifold here, while it seems tricky to design the independent proposal that well covers the probability mass of the target density, which again due to the transformation.

\response{This is an astute observation - we have added the following text after Theorem 3.6:

`The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm. For all examples in this paper we defined $p(z^{*})$ to be the uniform distribution on $\mathbb{S}$. The advantage of this choice is that it requires no further tuning parameters.  We have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with a reasonable probability. To implement the method in practice, we generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$. Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$. Using simple algebra and conditions C5-C8, one can show that $h(\cdot)$ is invariant to this projection and scaling. Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk. As we are proposing values on a complicated manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$. This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.'

There are undoubtedly cases where our choice is not optimal.  Here, we generate proposals for the complete data on a manifold that (in our examples and typically) is of much higher dimension than the conditioning statistic.  The independence proposals have reasonably large acceptance probabilities.  Random walk proposals are generally used to ensure that proposals are ``near'' the current state of the Markov chain, reducing proposed movement in exchange for a greater acceptance probability.  Our take on our algorithm is that we offer one solution that has provided effective MCMC in the cases we have explored.  The method applies to a large class of models that are in common use and to a large class of conditioning statistics.  We note that the independence proposals for the complete data are but one part of a larger algorithm.  Given the complete data, generation of the regression parameters may or may not make use of random walk proposals, block proposals, Gibbs steps involving generation from full conditionals, or other techniques.

With the basic paradigm and one implementation in place, we look forward to many future developments.  Further research is needed to produce these developments.  For computation, the development of random walk proposals on (nonlinear) manifolds is an interesting problem.  
}

\item The simulation studies didn't report the choice of $p(z^{*})$, acceptance rates of the MH, and mixing of the overall MCMC algorithm. Due to point 1, I think these issues would be of interest to readers.

\response{Thanks. We report the choice of $p(z^{*})$ above and  we have added acceptance rates for the simulations.}

\item The models studied in both the simulation and real data examples are just simple linear regression which is not realistic. Multiple linear regression with at least three independent variables should be studied.

\response{For the real data, we have included two additional covariates related to the number of employees at each agency. These were left out originally after EDA revealed their effect sizes were small, but leaving them in makes for a good study as well. We have kept the first simulation as we feel it is a good and simple illustration of the ability to fit hierarchical models with our method. The real data examples now contain a hierarchical example with more covariates. Additionally, we have included a second simulation where the ground truth is a linear regression model with 3 active covariates.  A model with 30 covariates (27 inactive) is fit.  There is correlation amongst some of the covariates, making this problem more realistic.}

\item What are the benefits of the proposed method over the classical robust point estimators, like Huber or Tukey estimators compared in the examples, to offset the additional computational cost and tuning efforts? From the simulation studies, whether it has improvement or not depends on the prior distribution, which seems to be from comparing Bayesian and Frequentist methods. Actually, literatures on the asymptotic properties of $f(\theta|T(yobs))$ shows that, if $T(yobs)$ is asymptotically unbiased, $T (yobs)$ and $E(\theta | T (yobs))$ have the same asymptotic variance. Hence if the prior doesn't matter, both methods have similar performance.

\response{As you note, one major advantage is that our method is {\em exactly} a Bayesian method, with $T(y_{obs})$ used in Bayes Theorem to move from prior to posterior.  In a typical setting, under relatively mild conditions on the prior distribution and estimator, Bayesian and frequentist methods will agree asymptotically.  This is reflected in the large-sample central limit theorems (Bayesian and frequentist versions) and is not specially connected to our work.  In this paper, our interest is not in these asymptotic settings where we could simply use a limiting normal distribution as the posterior over the parameters, but rather for the finite sample setting where Bayesian and frequentist methods yield different answers.  The simulations and data analyses document this differential performance.  The standard advantages of Bayes apply -- a guarantee of admissibility from a decision-theoretic view; the ability to combine information across a collection of problems (e.g., the hierarchical setting); and the transition from moment-based methods to likelihood-based methods, for example.  The weaknesses are also there -- a really bad prior distribution produces poor finite-sample performance.  There is a greater computational cost (standard for Bayes vs frequentist), but, given our MCMC routine, no real effort is needed to tune the computation.}

\response{We have added the following to the introduction of the paper to address this comment:}

\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data. One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
the conditioning statistics than are methods based on the complete likelihood. Choosing statistics targeting the main features of interest allows for inference that focuses on these features. The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.}

\response{The examples in the paper provide a Bayesian analog of classical robust estimators.  The main disadvantage of our methods relative to the classical estimators is computational.  In Section~3 we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.  The advantages are those of Bayesian methods.  As is standard for Bayes-classical comparisons, the Bayesian method requires greater computational effort while providing better inference.  As a referee notes, asymptotically, the Bayesian and classical parameter estimates are often very close and have the same limiting posterior variance / sampling variance.  In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.'}

\response{We have also included in the discussion:

`We have found the benefits of using our Bayesian technique to outweigh the additional computational burden (relative to a classical estimator) in the situation where substantive prior information that will impact the results is available.'
}

\item I think $f(\theta|T(yobs))$ might perform better in the following scenario: when $T(yobs)$ is asymptotically biased, $E(\theta|T(yobs))$ can still be asymptotically unbiased as long as the true pa- rameter is identifiable conditioning on the summary statistic, i.e the value of $E(T(yobs))$ is unique on the true parameter. One possible example is the robust ridge-regression estimator, but it needs further investigation whether this estimator satisfies C1-C8.

\response{This idea is in perfect alignment with our work.  You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).  It is merely a statistic upon which we condition when using Bayes Theorem.

Our computational strategy provides an implementation for a big variety of conditioning statistics that are also estimators.  The ridge regression estimator does not satisfy property C5 and so, on the surface, would need a new computational development ($\hat\beta = (X'X +\lambda I)^{-1} X'y$:   $(X'X +\lambda I)^{-1} X'(y + Xv) \neq (X'X +\lambda I)^{-1} X'y + v$). But the ridge regression estimator for full rank $X'X$ is equivalent to least squares regression for conditioning.  And the least squares estimator does satisfy C1-C8.

For any hope of consistency, the models would need to distinguish between different values of $\theta$, and so a condition along the lines of uniqueness of $E(T(yobs)|\theta)$ in $\theta$ is important.  
}

\item In page 14, should $C^\perp(X)$ n - p-dimensional instead of n - p - 1-dimensional?

\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional.  $\mathcal{A}$ is $n-p-1$ dimensional as one degree of freedom is lost for each coefficient estimate and another degree of freedom is lost for the scale estimate.}

\end{enumerate}

\section{Reviewer 2 Comments}

\begin{enumerate}
\item Is the proposed framework useful for practitioners? The proposed framework targets scenario where (i) we know the data is a mixture of good and bad data, and (ii) we only want to 'build models that offer good prediction for the good portion of the data' (from the 1st paragraph of Sec 5). Authors should provide real examples in which (i) and (ii) hold. In any real examples, (i) often holds, but (ii) doesn't: if we already have had a contaminated training sample, why would we expect the test sample to contain only the good portion? In many real applications, learning the heterogeneity of the good and bad samples is precisely the goal of statistical data analysis.
For the insurance example analyzed in Sec 6, the authors should provide evidence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.

\response{I think we are in agreement that it is common to encounter data sets where a portion of the data is 'good' and a portion of the data is 'bad' (your point (i)).  The 'bad' data may be bad for many reasons, including a breakdown of the measurement process, misrecorded data, and cases that simply aren't relevant to the problem at hand.  The ability to perform a decent analysis for such data sets is important.  And the typical decent analysis focuses on (ii).  We would have little interest in predicting misrecorded test data in a typical situation or in predicting the recorded values when the measurement process has broken down.

Developing an understanding of sources of variation in the data is important.  In settings where the mechanism that produces bad data is stable, we might even entertain building a model for the bad data as is one tradition in Bayesian statistics.  But there are many instances where modelling the bad data is of little interest.

When we are in a situation where (i) and (ii) hold -- we would argue that this is the usual situation and not the exception -- and we have test data available, there would rarely be any reason to believe that the test data would be pure, consisting only of good data.  This is an important motivator of this work as described in the introduction to our paper.

We have added the following to the introduction in response to your comment and a comment from the other referee.

\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data. One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
the conditioning statistics than are methods based on the complete likelihood. Choosing statistics targeting the main features of interest allows for inference that focuses on these features. The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.'}

For the real data example:  The goal for the insurance example was derived from personal collaborations with those in the insurance industry. Privacy concerns and a turnover of executives in the company from which the data come limit our ability to provide a full description and limit our ability to provide the data themselves.  However we have expanded slightly on the goal of the analysis.   
\response{It is of concern to the company to predict closures and future performance for agencies that remain open. It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies. Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.} 
}

\item As a methodological paper, what's the guideline/recommendation given by the authors? After reading this paper, I don't know how to apply the suggested framework
on a simple regression model. Apparently, the choice of the likelihood function (for the good data) $f(y|\theta)$ and the choice of the statistic T are related.
To make things more complicated, each has multiple choices. For example, f could be normal, student-t or other heavy-tailed distribution; T could be something named Huber or Tukey although the authors are not even bothered to provide any mathematical expression.

Instead of just reporting numerical performance, the authors should provide some guidelines/recommendation on how to apply their framework on linear regression models, e.g., what are the default choices for f and T ? Is there any- way to select which f or T to use based on cross-validation or other empirical methods?

\response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.  We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults in a heavy-handed fashion.  This would be much like specifying a default likelihood if one wishes to build a regression model.  Inthe usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.  As you note, choice of the likelihood is part of the analysis when building a Bayesian model.  To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.  Omission of the formal description of the particular M-estimators that we use is an oversight.

We have taken the following steps to address your comment.  We now

\begin{enumerate}
\item Point out that M-estimators have been our default choice in the very first illustrative example:
 \response{Details of these estimators can be found in many places, including \citep{huber2009}. We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers. A short review of these estimators is provided in the Supplementary Material.}
 \item Include a short review of M-estimators in the Supplement
 \item Include `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
\end{enumerate}
}

\item What's the real benefit of this computationally expensive approximation framework? The proposed framework replies on a good summary statistic T(yobs), which
has already provided a robust estimate of the target parameter. On the other
hand, the proposed MCMC algorithm is computationally expensive. In Sec
4.2, the authors only discussed the computation cost for their proposal distribution, but ignored the computation cost for obtaining T(y) (see Theorem 4.1). Those statistics are M-estimators, i.e., they are maximizers of some objective functions involving n observations and p parameters. The authors should discuss the computation cost for T(y).
What's the gain of all the extra computation?

\response{At the end of Section 3 (note renumbering of sections) we have included a paragraph:}

\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal in comparison to computing the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

\response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
%}

\item The authors compare KL diver-gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y|M,yobs) is not available in closed-form; 2) since f(y|M,yobs) is not available close-form, the KL divergence is approximated and it's not clear to me how accurate the approximation is.
The authors should compare prediction and estimation accuracy, common met- rics used for regression models.

\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to mean squared error (MSE).  Evaluation via MSE shows a uniform advantage for our restricted likelihood methods relative to classical robust estimators.  We have rewritten the summary of the simulation section.  In doing so, we describe the pattern apparent in the MSE and retain a link to the evaluation via KL-divergence.  We retain this link because the comparisons under KL-divergence do not show uniform superiority of our methods as do those based on MSE.}

\item The simulation setup is too simple. Suggest to add some linear regression models with large p and/or large n.

\response{We feel that the first hierarchical simulation example shows how to use the method in a hierarchical setting. We have added 2 more regression covariates to the real data analysis which also contains a hierarchical example. We have also included an additional simulation studying variable selection where only a few variables are active out of many.  We hope this satisfies your suggestion.}

\end{enumerate}

\textbf{Some minor issues.}
\begin{enumerate}
\item  Abstract '... handling data sets with outliers and dealing with model mis- specification. We outline the drawbacks ... and propose a new method as an alternative.' The proposed method cannot handle 'model misspecification', instead it assumes f is the true model (no misspecification) and what's wrong is part of the data.

\response{We stand by the abstract.  The insurance company example is along the lines of a number of examples in the literature on robust regression.  Outliers -- best defined as cases which do not reflect the mechanism under study -- often have large residuals.  This does not mean that outliers are independent of one another.  They often reflect model misspecification.  The tradition of robust regression is to provide a model that discounts the outliers (that discounts the deficiencies in the model) and results in a sensible, practical analysis of the data set.  The robust analysis often points the way to an understanding of why the model fits some cases well and others poorly.  Our paper is about model misspecification as well as what some feel the word 'outlier' captures.}

\item  Sec 2 and Sec 3 can be shortened or merged.

\response{We have merged the sections.}

\item  Eq(2) in Sec 2.1, the notation f(yi|?,c(yi)) is not introduced yet; what's introduced is f(y|?).

\response{We have included a sentence for this notation after it's first use.}

\item  Sec 4.1, C3 and C4: a maximizer may not be a continuous function of the data and it may not be unique. Instead of saying 'Many estimators satisfy the above properties', the authors should list those estimators and explain why those conditions are satisfied.

\response{We have added:

\response{'These M-estimators satisfy C3 and C4 since they are optimizers of continuous and differentiable objective functions. Constraints C5-C8 are often satisfied by location and scale estimators but should be checked on a case by case basis.'}
}

\item  Bottom of p14, 'Sample z? from a distribution with known density on S.' Any distribution? For example, can it be a point mass or its support has to be equal to S? What's the sampling distribution for z? used in the simulation studies and real data analysis?

\response{Thanks for noticing this detail. It is most natural if it is mutually absolutely continuous with respect to the distribution induced by the model on S.  For the cases we discuss, this is mutually absolutely continuous with respect to the uniform distribution on S.  We now mention the importance of the support.  We have also included a description of what we use for p throughout based on a previous comment. This comment is after Theorem 4.6.}

\item  Eq (18): change dy to d$\tilde{y}$?

\response{Thanks for noticing this typo - based on your other comment on KL divergence, this formula was taken out and now is a closed form version. }

\end{enumerate}

\section{AE Comments}
This paper proposes a Bayesian approach for making inference based on robust statistics of the data instead of the original observations. The conditioning robust statistics pass the desirable robustness (to outliers) to the posterior distribution of parameters, thus having the potential to improve inference and prediction. This paper addresses an important problem in statistics and contains interesting ideas. However, there are some major concerns.
The paper focuses on outliers. Although outliers automatically imply that the model is misspecified, model misspecification is much broader including the misspecification of the density of the good data. The paper does not appear to address model misspecification beyond the case when outliers are present. Please revise the scope of the paper as appropriate or provide more examples to ensure outliers and model misspecification are parallel contributions rather than one nested in another.

\response{Model misspecification covers broad territory.  It includes traditional outliers (retaining the independence of observations, but assuming some have greater variance, for example), misspecification of the mean function in a regression setting, missed covariates for regression, missed dependence among cases, misspecified functional form for the `good' data (one reason for the growth of nonparametric Bayesian methods), and much, much more.  Box' famous aphorism is one direct statement that all models are misspecified.

Our own belief is that it would be impossible to address {\em all} forms of model misspecification, yet discussion of the issue is important.  Our paper illustrates misspecification in the real data example on the insurance companies.  The inclusion of closed agencies and agencies with different types of contracts represent model misspecification. These `outliers' are not merely the result of a huge chance error, a faulty measurement process, or a failed experimental run.  They are unusual for a reason and the analysis helps to uncover this reason (we are limited in the commentary that we can attach to the analysis).  As with many of the examples used to illustrate robust regression techniques, these data are best described as having a misspecified model.}

There are many implementation details that an interested user would like to learn more but feel difficult to find from the current paper. This includes but not limited to the selection of proposal, parameter tuning, recommendations when a practitioner is being faced with a real-world problem, and computational complexity of the entire procedure. See the two referee reports for more details.

\response{Thank you - we believe we have addressed each of these concerns based on the two reviewer's comments. Detailed responses are given above.}

The authors are also suggested to possibly provide code that is available online with recommended choices as default.

\response{We have included some 'default choices' in the paper and in the Supplement.  Information for where to obtain code on Github (an R package as well as data and code for the examples) is now provided in the Introduction.  As noted in our response to Referee 2, we hesitate to push the notion of a default likelihood and default conditioning statistic.  The paper provides a conceptual framework for data analysis and develops the methodology and computation needed to implement the analysis.  We do not view the work as developing an algorithm into which one should just feed data.}

It is unclear how the proposed method outperforms existing work, either conceptually or practically.

\response{We believe we have addressed similar concerns from the two reviewers - specifically we have included commentary on the advantages and disadvantages of the new method in several places (e.g., see Introduction) as well as some practical recommendations (e.g. See Supplement).}

Referees have provided some competing methods for the authors to consider. I'd like to add another existing strategy in addition to the three solutions mentioned in the bottom paragraph of page 2: Bayesian fractional inference, which uses a fractional likelihood function that raises a usual likelihood function to a fractional power. What is the advantage of the proposed restrictive likelihood approach over Bayesian fractional inference, even conceptually?

\response{The central advantage of our method compared to the fractional Bayes methods is that our method uses Bayes Theorem!  It is exactly Bayesian in that the posterior distribution is a rescaled version of prior distribution times likelihood (of a statistic).  This means that the method inherits a host of properties from Bayesian methods.

In contrast, the fractional Bayesian methods do not actually follow Bayes Theorem (there are exceptions in special cases).  Fractional Bayes methods use the theorem as an analogy and so miss many of the benefits of Bayes.  The fractional methods are interesting and they deserve study, but they are not the only solution to Bayesian model misspecification.

In the long run, we suspect that robust and effective Bayesian analyses will make use of ideas from a variety of perspectives that are currently under study.  The various lines of research need groups of researchers investigating them, need time to develop, and they need visibility for the community to appreciate the different perspectives and to develop an understanding of what each brings to the table.}

Overall, the paper deserves publication after careful and thorough revision. I hope the authors can address all concerns raised in this report and the two well-grounded referee reports.

\response{ Thanks!}

\section{Editor Comments}

The paper has received a mixed reaction from the two referees and the AE. I have a similar reaction to the paper but agree with the other readers that the content is such that an opportunity to address the issues raised is appropriate. The AE's comments place the paper on the border between Reject with Resubmission and Major Revision. I mention this because it isn't clear that a revision will be successful as there are some significant criticisms in the reviews.

My concerns might be a little different than the others and perhaps are less technical in nature. It is generally agreed that *all* models are wrong. The incorrectness of the model can arise in a number of ways and some observations being outliers is one of these. The natural question then is: how are we supposed to deal with that? The answer is surely that we don't unless the discrepancy is so substantial that the inferences would be seriously in error if we proceeded using the assumed model. This part of a statistical analysis is the model checking aspect and the solution to any issue, whatever it might be, arises there. For example, for the problem being considered in this paper, I would want a model checking procedure that indicated that there is a serious problem because, no matter what distribution was used from the model, some observations are outlying and I would want the methodology to identify the observations in question. In that case there would several ways to deal with the issue, including modifying the model, but also simply discarding the offending observations as part of "data cleaning". It is worth noting though that the answer isn't simple because notable scientific achievements have been obtained by looking carefully at observations that are clearly discrepant.

So there are some concerns that have relevance for me and that I think the paper needs to address. What method is used to identify that there is a problem with the model such that the inferences will be strongly affected and does it identify outlying observations?

\response{Our own training in regression is in the style of ``case analysis'' that has been written about so convincingly by Sandy Weisberg, Dennis Cook, and others.  This training matches your view of strong model diagnostics to identify deficiencies in the model.  A competing type of regression analysis common at the time was developed by Peter Huber, Peter Rousseeuw, and others.  These ``robust regression'' methods seek to automatically discount unusual cases.  Though generally described as a means of handling outliers, many of the popular examples used to illustrate the methods are clearly examples of model misspecification.  The robust methods provide excellent fits for the good (or non-to-mildly misspecified data) when there is misspecification.  Much is known and much has been written about the relative merits of the two styles of regression in various settings.

In the early 1980s, case analysis became the dominant paradigm (though robust regression retained many adherents).  Our natural inclinations match yours for the reasons you give--we would always prefer to build the perfect model.  However, there are a number of reasons why we cannot do so.  These range from the perils of overmodelling (particularly dangerous for Bayesians) to limitations on our ability to identify outliers (from Huber's book, imagine sliding the "y" value for a case from a ridiculous value--surely and outlier--to its case-deleted mean--a zero residual and not identified as an outlier; somewhere along the way, the subjective probability of the case being an outlier must be 0.5 and we would be unable to decide whether the case is an outlier), to our inability to detect modest model misspecification.  Accepting that there are limitations on case analysis and our ability to build the perfect model suggests that we need to develop alternative strategies.  These alternative strategies can even become part of our diagnostic framework:  a discrepancy between the restricted likelihood fit and the traditional Bayesian fit (or predictions) indicates a need for the case-analysis analyst to do more work.

The modern world revolves around large data sets, often with a hierarchical structure.  While case analysis works with data sets of moderate size, it breaks down when one has thousands to millions of cases.  It also breaks down when one is interested in model selection (among a class of models that are, of course, misspecified to some extent) or model averaging.  Robust methods scale much better than case analysis methods do.

The tension between case analysis methods and robust methods is not limited to the regression setting, nor is it limited to merely looking at the fits from the model.  In this work, we lay out the restricted likelihood perspective, develop a computational implementation (as referees and AE note, this development is not trivial), implement the method with code that is available on GitHub, and illustrate some of the benefits of this method relative to standard Bayesian and classical methods.  We view this as an early effort and look to tackle further problems in subsequent papers--in fact, we have given talks about issues such as Bayesian hypothesis testing and model averaging in this framework--and we see a clear path forward for a variety of problems.}

A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to choose T: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isn't clear how to do this. I understand that there are
problems where reducing the data to some T(y) is necessary, perhaps because of computational problems associated with evaluating a likelihood, but this is clearly a compromised analysis and not one we would recommend unless forced to do so. So I don't agree with the statement made in the paper "that deliberate choice of an insufficient statistic T(y) guided by targeted inference is sound practice". There needs to be a much stronger argument for this at least for me.

\response{We understand your point of view.  It focuses on dangerous territory for classical statisticans and Bayesians alike.  In keeping with your statement above that *all* models are misspecified (we agree except for a few very simple exceptions--say a single Bernoulli trial), we believe that *all* analyses are compromised.  It is also true that, as soon as one uses diagnostics that have the potential to change the model or the data (removing outliers, for example), the analysis is compromised.  The appropriate likelihood would need to account for all decisions that one might make.  These are two of the arguments made for the use of robust methods (i) that robust estimators reduce the impact of model misspecification, and (ii) that data cleaning and data-based model adjustment destroys the properties of classical tests and Bayesian methods.  It is difficult to quantify these effects, but we have seen them in the practice of data analysis.}

The paper is well-written and thought-provoking so my hope is that a revision will be able to address the points raised.

\bibliographystyle{plain}
\bibliography{../bib/refPaper1}

\end{document}

### 2020-11-02 revision_2/Work on the revision early files/paperV3.tex
clean up and add abc analysis script

--- 2020-05-09 revision_2/paperV2.tex
@@
 \runtitle{Bayesian Restricted Likelihood Methods}
-\thankstext{T1}{This research has been supported by Nationwide Insurance Company and by the NSF under grant numbers DMS-1007682 and DMS-1209194.
+\thankstext{T1}{This research has been supported by Nationwide Insurance Company and by the NSF under grant numbers DMS-1007682, DMS-1209194, DMS-15-13566, and DMS-16-13110.
 The views in this paper are not necessarily those of Nationwide Insurance or the NSF.}
@@
 \response{ An R package \texttt{brlm} to implement our methods is available at \texttt{github.com/jrlewi/brlm}.
-Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/revision\char`_2}.}
+Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/}.}
 
@@
 \end{eqnarray}
-
 $\prod_{i=1}^n f(y_i|\bth,c(y_i))$ is the likelihood of the data conditioned on parameters and the summary statistic $c(\cdot)$ and recovers the piece of the full likelihood not in $ \prod_{i=1}^n g(c(y_i)  | \bth)$.
@@
 Constraints  \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}
-\response{These M-estimators satisfy \ref{abs} and \ref{as} since they are optimizers of continuous and differentiable objective functions.
+\response{These M-estimators satisfy \ref{asb} and \ref{as} since they are optimizers of continuous and differentiable objective functions.
 Constraints \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}
@@
 \begin{enumerate}
-\item Sample $\bz^*$ from a distribution with known density \response{whose support is the entirety} $\mathbb{S}$.
+\item Sample $\bz^*$ from a distribution with known density \response{whose support is the entirety of} $\mathbb{S}$.
 \item Set $\by = h(\bz^*)$ and calculate the Jacobian of this transformation in two steps.
@@
 
-\response{To asses the predictive capability, we seek a metric that takes into account both the estimation of $\theta_{i}$ and $\sigma^{2}$.
+\response{The performance of the methods can be evaluated in many ways.
+For these simulations, we know the true data generating mechanism, and this allows us to make direct comparisons between the fitted model and the truth.
+The Bayesian methods provide a full predictive distribution for the response, given group while the classical methods provide only point estimates of parameters.
+Our comparisons have focused on two main summaries.
+One summary, not presented here, is the average Kullback-Liebler divergence from the good portion of the true distribution of $Y$ given group to the predictive distribution (Bayes) or distribution with point estimates plugged in (classical).
+For the Bayesian models, the divergence does not have a closed form and must be evaluated numerically.
+The second summary, preferred by a referee, is the mean squared error (MSE), averaged across groups.
+Results are presented in Figures \ref{mse_sim} and \ref{mse_mnp}.
+Formally, with the superscript $M$ indicating the method and the additional subscript $k$ indexing the data set,
+%\begin{equation}
+\begin{align}
+\label{MSE}
+\mbox{MSE}^{(M)}_{ik} & = (\hat\theta^{(M)}_{ik} - \theta_{ik})^2,  \\ 
+\mbox{MSE}^{(M)} & = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} \mbox{MSE}^{(M)}_{ik}
+\end{align}
+%\end{equation}
+
+The Bayesian restricted likelihood methods show superior performance under both summaries, but especially for MSE.
+Figure \ref{mse_sim} displays the MSE grouped by pairs $a_{s}$ and $c$ with error bars plus/minus one standard error within the group.
+The values of $a_{s}$ and $c$, do not affect the classical robust linear models.
+The average MSEs for the normal theory models ranges from $0.24$ to $0.25$ and are left out of the figure.
+The results uniformly favor the Bayesian restricted likelihood methods, as seen by substantially lower values of MSE.
+For both classical and restricted likelihood methods, Tukey's $\psi$ function leads to better performance than does Huber's $\psi$ function.
+}
+%For $c = 0.5$ and $c = 1$ the results favor the restricted likelihood methods as seen by the lower values of loss.
+The choice of $c = 2$ corresponds to a particularly poor prior distribution.
+The prior has substantial mass above $\sigma^{2} = 4$, with prior means for $\sigma^2$ from $8.9$ to $32$ as $a_s$ varies.
+Additionally, the tuning parameters chosen for the location and scale estimators result in an upward bias in the estimate of $\sigma^{2}$.
+This bias depends on $m$ and $p$.
+For example, for $m = 9$ and $p = .1$, Huber's version converges to roughly $4.8$ as $n$ grows.
+The bias is greater for more severe levels of contamination.
+The alignment of biases in prior distribution and in likelihood from the summary statistic (when applied to the contaminated data) inflates the estimate of scale.
+Not surprisingly, a poor prior distribution whose weakness matches the weakness in the likelihood results in poorer inference.
+In this case, poorer than the classical estimators.
+.
+}
+
+%\response{To asses the predictive capability, we seek a metric that takes into account both the estimation of $\theta_{i}$ and $\sigma^{2}$.
 In this model, estimation of $\theta_{i}$ and prediction are analogous.
 To this end we consider the loss:
-\begin{equation}
-\label{sim1loss}
-L((\hat\theta_{i}, \hat\sigma), (\theta_{i},\sigma)) =
-\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2})
-\end{equation}
-Note, this loss is proportional to the Kullback-Leibler divergence between two normals with the base normal being the true distribution of the good portion of the data and the the other normal representing the estimate under the fitting method.
+%\begin{equation}
+%\label{sim1loss}
+%L((\hat\theta_{i}, \hat\sigma_{i}), (\theta_{i},\sigma)) =
+%\log(\hat\sigma_{i}^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma_{i}^{2}}(\sigma^{2} + (\theta_{i} - \hat{\theta_{i}})^{2})
+%\end{equation}
+%Note, this loss is proportional to the Kullback-Leibler divergence between two normals with the base normal being the true distribution of the good portion of the data and the the other normal representing the estimate under the fitting method.
 We are using fixed point estimates $\hat\theta_{i}$ and $\hat\sigma$ which are posterior means under the Bayesian models and the standard point estimates for the classical methods.
-}
+%}
 %To assess predictive capability, the models are compared using Kullback-Leibler (KL) divergence from the distribution of good data to the posterior predictive distribution.
@@
 Sampling variation is summarized with the standard error between the $K=30$ replicates in the simulation:  $SE(\overline{KL}^{(M)}_{{\cdot} k}) = \sqrt{\frac{1}{K(K-1)}\sum_{k = 1}^{K} (\overline{KL}^{(M)}_{{\cdot} k} - \overline{KL}^{(M)}_{{\cdot}{\cdot}})^{2}}$ where $\overline{KL}^{(M)}_{{\cdot} k} = \frac{1}{90}\sum_{i = 1}^{90} KL^{(M)}_{ik}$.
-Figure \ref{kl_sim} displays the average of loss \ref{sim1loss} grouped by pairs of $a_{s}$ and $c$ with error bars plus/minus on standard error within the group.
+
+%Figure \ref{kl_sim} displays the average of loss \ref{sim1loss} grouped by pairs of $a_{s}$ and $c$ with error bars plus/minus on standard error within the group.
 The values of $a_{s}$ and $c$, do not affect the classical robust linear models.
@@
 \includegraphics[width = 5in]{mse_sim2_facet_scale.png}
-\caption{Average Loss plus/minus one standard error for each value of $a_{s}$ and $c$.
+\caption{Average MSE plus/minus one standard error for each value of $a_{s}$ and $c$.
 Smaller values represent better fits.
 The panels correspond to $c = 0.5$ (left), $c=1$ (middle), and $c=2$ (right), with the values of $a_{s}$ on the horizontal axis.
-The average loss for the normal theory model ranges from $1.44$ to $1.66$ and is left out of the figure.}
-\label{kl_sim}
+The average MSE for the normal theory model ranges from $0.24$ to $0.25$ and is left out of the figure.}
+\label{mse_sim}
 \end{figure}
 
-It is also interesting to consider the effects of factors $n$, $p$, and $m$.
+\response{It is also interesting to consider the effects of factors $n$, $p$, and $m$.
 We present the results for a single prior ($a_s = 5$ and $c = 1$).
-For each simulation $k$, the main effect average loss is found for each factor $n$, $p$, and $m$.
-Figure \ref{kl_mnp} displays the average of these main effects over the $K = 30$ simulations along  with error bars plus/minus one standard error.
+For each simulation $k$, the main effect average MSE is found for each factor $n$, $p$, and $m$.
+Figure \ref{mse_mnp} displays the average MSE over the $K = 30$ simulations along with error bars plus/minus one standard error.
 For each group $n$, $p$, and $m$, the Bayesian restricted likelihood versions have better average loss than do the classical methods.
-As expected, the average loss gets larger as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller as the sample size $n$ grows.
-The advantage of the Bayesian method is greater for smaller sample sizes.
+As expected, the average MSE gets larger as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller as the sample size $n$ grows.
+The advantage of the Bayesian methods is greater for smaller sample sizes and for less severe contamination.}
 
@@
 \includegraphics[width = 5in]{MSE_sim2_mnp.png}
-\caption{Average loss plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right). These results are for the single prior with $a_s = 5$ and $c = 1$.}
-\label{kl_mnp}
+\caption{Average MSE plus/minus one standard error grouped by the factors $m$ (left), $n$ (middle), and $p$ (right). These results are for the single prior with $a_s = 5$ and $c = 1$.}
+\label{mse_mnp}
 \end{figure}
 
-This simulation shows the potential of the restricted likelihood and conveys some cautions.
+\response{This simulation shows the potential of the restricted likelihood methods to dramatically improve estimation.
+The simulation also conveys some cautions that are apparent from consideration of KL divergence but not MSE.
 Specifically, the choice of summary statistics, along with corresponding tuning parameters is important.
@@
 If poorly handled, they can, of course, harm performance.
+}
 
@@
 For the simulation, $K = 30$ data sets (including the additional covariates) of size $n = 500$ are generated from the true model with true values $\bbeta = (1,1,1)^{\top}$ and $\sigma^{2} = 2$.
-We fit the model including all 30 covariates and consider the following methods for the fit 1) classical robust regression with Tukey's estimator of location and Huber's estimator of scale, 2) the corresponding restricted likelihood version 3) A heavy-tailed Bayesian model with a Student-t likelihood with $\nu = 5$ degrees of freedom.
+We fit the model including all 30 covariates and consider the following methods for the fit 1) classical robust regression with Tukey's estimator of location and Huber's estimator of scale, 2) the corresponding restricted likelihood version 3) a heavy-tailed Bayesian model with a Student-t likelihood with $\nu = 5$ degrees of freedom.
 For the Bayesian models we take $\bbeta_{all}\sim N_{20}(\mb{0}, \sigma^{2}_{\beta}I)$ with $\bbeta_{all} = (\bbeta, \bbeta^{*})^{\top}$ and $\sigma^{2}\sim IG(5,8)$ under the restricted model and  $\sigma^{2}\sim IG(5,\frac{\nu-2}{\nu}8)$ under the Student-t model.
@@
 For the Bayesian models, we use posterior means.
-The average MSE plus/minus one standard error over the simulations for each $\sigma^{2}_{\beta}$ are displayed in Figure \ref{mseSimMany}.
+The average MSEs plus/minus one standard error over the simulations for each $\sigma^{2}_{\beta}$ are displayed in Figure \ref{mseSimMany}.
 The classical fit is labeled `rlm` and is the same for each value of the prior standard deviation $\sigma^{2}_{\beta}$.
@@
 However,  we leave them and use the data as a test bed for our techniques by fitting models that do not account for agency closures or contract type.
-Our expectation is that the restricted likelihood will facilitate prediction for the `good' part of the data (i.e., open, `type 1' agencies).
+Our expectation is that the restricted likelihood will facilitate prediction for the `good' part of the data (i.e., open, `Type 1' agencies).
 \response{It is of concern to the company to predict closures and future performance for agencies that remain open.
@@
 Holdout evaluation is done on the remaining (`Type 1') samples.
-The acceptance rates for  the data augmentation step,\response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
+The acceptance rates for  the data augmentation step, \response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
 \response{The exception was a single training set from State 15 resulting in an usually small acceptance rate under Tukey's version.
@@
 Notably, the Student-t model performs poorly in comparison for this state.
-The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good' data (i.e., the Type 1 agencies).
+The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good' data (i.e., the 'Type 1' agencies).
 Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.
@@
 state, $n_{j}$ is the total number of agencies in state $j$, and $J$ is
-the number of states. $\bx_{ij}$ is same tree-dimensions covariate vector as before and $\bbeta_j$ represents the individual regression coefficient vector for state $j$. The parameters $\bmu_0$,
+the number of states. $\bx_{ij}$ is same three-dimensional covariate vector as before and $\bbeta_j$ represents the individual regression coefficient vector for state $j$. The parameters $\bmu_0$,
 $\Sigma_0$, $a_0$, and $b_0$ are fixed by fitting  the regression $y_{ij}=\bx_{ij}^{\top}\bbeta+\epsilon_{ij}$ using Huber's M-estimators to the prior data set from two years before.
@@
 The Bayesian models are fit using MCMC, with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} and adapted to the hierarchical setting as described in Section \ref{simData}.
-For the MH-step proposing augmented data,  \response{the acceptance rates for the two restricted likelihood models across all states and repetitions ranged from $0.01$ to  $0.75$, with only $7$ cases (out of 50*20*2 = 2000 chains) with rates below $0.1$}
+For the MH-step proposing augmented data,  \response{the acceptance rates for the two restricted likelihood models across all states and repetitions ranged from $0.01$ to  $0.75$, with only $7$ cases (out of 50*20*2 = 2000 chains) with rates below $0.1$.}
 
@@
 One should take care in the method of evaluation.
-When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data or the metric should be adjusted to discount outlying data ins some way (such as the trimmed-log-marginal we introduced TLM).
+When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data or the metric should be adjusted to discount outlying data in some way (such as the trimmed-log-marginal we introduced TLM).
 \end{itemize}

### 2020-11-02 revision_2/response/Drafts of response to referees/responseV4.tex
clean up and add abc analysis script

--- 2020-05-09 revision_2/response/responseV5.tex
@@
 
-We have taken the following steps to address your comment.  We now
+We have taken the following steps to address your comment:
 
 \begin{enumerate}
-\item Point out that M-estimators have been our default choice in the very first illustrative example:
+\item Point out that M-Estimators have been our default choice in the very first illustrative example:
  \response{Details of these estimators can be found in many places, including \citep{huber2009}.
@@
 A short review of these estimators is provided in the Supplementary Material.}
- \item Include a short review of M-estimators in the Supplement
- \item Include `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
+ \item Included a short review of M-Estimators in the Supplement
+ \item Included `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
 \end{enumerate}

### 2020-11-02 revision_2/response/Drafts of response to referees/responseV6.tex
clean up and add abc analysis script

--- 2020-05-11 revision_2/response/responseV5.tex
@@
 \response{This idea is in perfect alignment with our work.
-You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).
+You are right that $T(y_{obs})$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).
 It is merely a statistic upon which we condition when using Bayes Theorem.
@@
 
-\response{I think we are in agreement that it is common to encounter data sets where a portion of the data is 'good' and a portion of the data is 'bad' (your point (i)).
-The 'bad' data may be bad for many reasons, including a breakdown of the measurement process, misrecorded data, and cases that simply aren't relevant to the problem at hand.
+\response{I think we are in agreement that it is common to encounter data sets where a portion of the data is `good' and a portion of the data is `bad' (your point (i)).
+The `bad' data may be bad for many reasons, including a breakdown of the measurement process, misrecorded data, and cases that simply aren't relevant to the problem at hand.
 The ability to perform a decent analysis for such data sets is important.
@@
 
-\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data.
+\response{`The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data.
 One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
@@
 This would be much like specifying a default likelihood if one wishes to build a regression model.
-Inthe usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.
+In the usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.
 As you note, choice of the likelihood is part of the analysis when building a Bayesian model.
@@
 
-\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
+\response{`Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
 We have found this burden to be marginal relative to computation of the needed Jacobian.
@@
 
-\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to a closed form version of KL divergence.  We use the KL divergence between two normals: $ 
-\log(\hat\sigma_{i}^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma_{i}^{2}}(\sigma^{2} + (\theta_{i} - \hat{\theta_{i}})^{2}
-$
-While we wouldn't be able to compute this in a real application, it does combines estimation error for both the $\theta_{i}$ and $\sigma$ and is a decent metric to compare the methods under the simulation setup.
-}
-John - I'm puzzled by this one.  I'll have to check the paper when I get dropbox up and running again.  (Steve)
+\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to mean squared error (MSE).
+Evaluation via MSE shows a uniform advantage for our restricted likelihood methods relative to classical robust estimators.
+We have rewritten the summary of the simulation section.
+In doing so, we describe the pattern apparent in the MSE and retain a link to the evaluation via KL-divergence.
+We retain this link because the comparisons under KL-divergence do not uniform superiority of our methods as do those based on MSE.}
 
@@
 We have also included a description of what we use for p throughout based on a previous comment.
-This comment is after Theorem 4.6.}
+This comment is after Theorem 3.6.}
 
@@
 
-\response{Thanks for noticing this typo - based on your other comment on KL divergence, this formula was taken out and now is a closed form version. }
+\response{Thanks for noticing this typo - based on the comment on KL divergence, this formula was taken out in favor of MSE. }
 
@@
 
-\response{We have included some 'default choices' in the paper and in the Supplement.
+\response{We have included some `default choices' in the paper and in the Supplement.
 Information for where to obtain code on Github (an R package as well as data and code for the examples) is now provided in the Introduction.

### 2020-11-02 revision_2/revision_Jun2020.tex
clean up and add abc analysis script

--- 2020-11-02 revision_2/Work on the revision early files/paperV3.tex
@@
 For these simulations, we know the true data generating mechanism, and this allows us to make direct comparisons between the fitted model and the truth.
-The Bayesian methods provide a full predictive distribution for the response, given group while the classical methods provide only point estimates of parameters.
+The Bayesian methods provide a full predictive distribution for the response, given group, while the classical methods provide only point estimates of parameters.
 Our comparisons have focused on two main summaries.
-One summary, not presented here, is the average Kullback-Liebler divergence from the good portion of the true distribution of $Y$ given group to the predictive distribution (Bayes) or distribution with point estimates plugged in (classical).
+One summary, not presented here, is the average Kullback-Liebler divergence from the good portion of the true distribution of $Y$ given group to the predictive distribution (Bayes) or to the distribution with point estimates plugged in (classical).
 For the Bayesian models, the divergence does not have a closed form and must be evaluated numerically.
@@
 \mbox{MSE}^{(M)}_{ik} & = (\hat\theta^{(M)}_{ik} - \theta_{ik})^2,  \\ 
-\mbox{MSE}^{(M)} & = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} \mbox{MSE}^{(M)}_{ik}
+\mbox{MSE}^{(M)} & = \frac{1}{90K} \sum_{k = 1}^{K} \sum_{i=1}^{90} \mbox{MSE}^{(M)}_{ik}.  
 \end{align}
@@
 Figure \ref{mse_sim} displays the MSE grouped by pairs $a_{s}$ and $c$ with error bars plus/minus one standard error within the group.
-The values of $a_{s}$ and $c$, do not affect the classical robust linear models.
+The values of $a_{s}$ and $c$ do not affect the classical robust linear models.
 The average MSEs for the normal theory models ranges from $0.24$ to $0.25$ and are left out of the figure.
@@
 As expected, the average MSE gets larger as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller as the sample size $n$ grows.
-The advantage of the Bayesian methods is greater for smaller sample sizes and for less severe contamination.}
+The advantage of the Bayesian methods is greater for smaller sample sizes and for more severe contamination.}
 
@@
 The simulation also conveys some cautions that are apparent from consideration of KL divergence but not MSE.
-Specifically, the choice of summary statistics, along with corresponding tuning parameters is important.
-For the tuning parameters, we applied the default choice of $95\%$ efficiency at the normal.
+Specifically, the choice of summary statistic along with the corresponding tuning parameters is important.
+For the tuning parameters for the $\psi$ functions, we applied the default choice of $95\%$ efficiency at the normal.
 Under the simulation model here, this choice results in bias in the scale estimation which affects the performance of the method.
-These choices must be made when using both the classical and Bayesian methods.
+Tuning parameters must be set when using both classical and Bayesian methods.
 The Bayesian approach encourages use of a hierarchical model structure and allows one to incorporate prior information in the analysis.

### 2020-11-02 revision_2/code/data_analysis/3_abc_hier_reg_analysis.R

@@ -1,0 +1,346 @@
+# ABC Hierarchical regression - i.e., grouped by states. 
+
+# download brlm package if needed
+# library(devtools)
+# install_github('jrlewi/brlm')
+library(MCMCpack)
+library(MASS)
+library(parallel)
+lib.loc = file.path("/Users", "john", "Dropbox",
+                    "school", "osu", "dissertationResearch",
+                    "snm", "rPackage", "brlm", "packrat", "lib",
+                    "x86_64-apple-darwin15.6.0", "3.4.3")
+library(brlm, lib.loc = lib.loc)
+library(tidyverse)
+
+nburn <- 2e3
+nkeep <- 2e3
+maxit <- 1000 #parameter in MASS::rlm
+
+
+# aux funcitons ----
+
+fn.compute.marginals.hierModelNormal<-function(betalsamples, sigma2lsamples, yhold,Xhold){
+  
+  
+  fits<-function(betahats, X){X%*%betahats}
+  
+  betalSampsList <- lapply(1:dim(betalsamples)[3],function(x) betalsamples[,,x])
+  names(betalSampsList) <- names(yhold)
+  #holdout means
+  
+  nMuList<-mapply(fits, betalSampsList, Xhold)
+  
+  #sd's across samples for each holdout set
+  nSigmaList<-split(sqrt(sigma2lsamples), rep(1:ncol(sigma2lsamples), each = nrow(sigma2lsamples)))
+  names(nSigmaList)<-names(yhold)
+  
+  mapply(FUN=function(yh,mean,sd){
+    pdfs <- dnorm(yh,mean,matrix(rep(sd, length(yh)), length(yh), length(sd),byrow=TRUE))
+    mns <- rowMeans(pdfs)
+    sds <- apply(pdfs, 1, sd)
+    cbind(mns, sds)
+  }
+  ,yhold,nMuList,nSigmaList)
+  
+}
+
+
+# load data and prior information ----
+analysis_data <- read_rds(file.path(here::here(), 'data', 'analysis_data.rds'))
+
+analysis_data <- analysis_data %>% 
+  mutate(sqrt_count_2010 = sqrt(Count_2010), sqrt_count_2012 = sqrt(Count_2012)) %>%
+  group_by(State) %>% 
+  filter(n() >= 25) %>% ungroup() %>% 
+  mutate(State = factor(State)) %>% #filter(!State %in% c(14, 30)) %>% 
+  arrange(State)
+
[…]

### 2021-02-01 revision_2/response_Dec2020 Dec 30.tex
git cleanup

--- 2020-11-02 revision_2/response/response_to_editorial_comments.tex
@@
 \begin{document}
+Thank you for the additional comments on our paper.
+As with the earlier comments, they are interesting.
+We have taken all of them seriously and have worked on them in putting the revision together.
+For the revision itself, we have tried to keep our edits (and new material) focused to avoid adding too much to a paper that is already lengthy.
 
-\section{Reviewer 1 Comments}
+The new parts for this round of edits appear in blue, including text that has been stricken (lined out in the text).
 
-\begin{enumerate}
-\item The authors propose a broad class of the proposal density, but didn't discuss the choice and tuning within the class.
-Tuning the proposal is crucial to the mixing and efficiency of the MH algorithm, epecially in the high-dimension space, $n-p$-dimensional, that the paper is dealing with.
-There are two difficulties in tuning within the proposed class.
-First, since the proposal density is a complicated transformation of $p(z^{*})$ in $R^{n-p-1}$, even if $p(z^{*})$ belongs to a standard parametric family, $p(z^{*})$ does not and it is not straightforward to assess the properties that are usually used in tuning MCMC algorithm, e.g.
-mode and
-tails behaviour.
-Second, the proposed algorithm (11) is restrictive because it only works for independent proposal, not the random walk proposal.
-Random walk is more able to explore a non-standard parameter space like the manifold here, while it seems tricky to design the independent proposal that well covers the probability mass of the target density, which again due to the transformation.
+Specifically, we have done the following:
 
-\response{This is an astute observation - we have added the following text after Theorem 3.6:
+\begin{itemize}
+\item We have slightly restructured the introduction and added a quote from a vintage paper on robustness.
+We hope that this serves to clarify a long-standing tradition in robust statistics--namely that the techniques address both model misspecification and outlyingness, though descriptions often fall back to the "code word" outliers.
+We could add many more references here, but we went with a single one to avoid detracting from the focus of the paper.
+The Belgian call data (Section 2.4) is decidedly in the camp of model misspecification.
 
-`The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm.
-For all examples in this paper we defined $p(z^{*})$ to be the uniform distribution on $\mathbb{S}$.
-The advantage of this choice is that it requires no further tuning parameters.
-We have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with a reasonable probability.
-To implement the method in practice, we generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$.
-Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$.
-Using simple algebra and conditions C5-C8, one can show that $h(\cdot)$ is invariant to this projection and scaling.
-Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk.
-As we are proposing values on a complicated manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$.
-This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.'
+\item We have expanded commentary on the connection to ABC methods in the literature review in Section 2.3.
 
-There are undoubtedly cases where our choice is not optimal.
-Here, we generate proposals for the complete data on a manifold that (in our examples and typically) is of much higher dimension than the conditioning statistic.
-The independence proposals have reasonably large acceptance probabilities.
-Random walk proposals are generally used to ensure that proposals are ``near'' the current state of the Markov chain, reducing proposed movement in exchange for a greater acceptance probability.
-Our take on our algorithm is that we offer one solution that has provided effective MCMC in the cases we have explored.
-The method applies to a large class of models that are in common use and to a large class of conditioning statistics.
-We note that the independence proposals for the complete data are but one part of a larger algorithm.
-Given the complete data, generation of the regression parameters may or may not make use of random walk proposals, block proposals, Gibbs steps involving generation from full conditionals, or other techniques.
+\item We have coded up an ABC-MCMC method for the real application in Section 5.3.
+The method was recommended to us by our local faculty (van Zandt and Turner) who work with ABC and MCMC methods.
+Perhaps surprisingly, our method is only a little (1.6 times) slower per iterate, yet appears to mix better than ABC-MCMC.
+To our eyes, the results of the data analysis look better for restricted likelihood than for ABC-MCMC.
 
-With the basic paradigm and one implementation in place, we look forward to many future developments.
-Further research is needed to produce these developments.
-For computation, the development of random walk proposals on (nonlinear) manifolds is an interesting problem.
-}
-
-\item The simulation studies didn't report the choice of $p(z^{*})$, acceptance rates of the MH, and mixing of the overall MCMC algorithm.
-Due to point 1, I think these issues would be of interest to readers.
-
-\response{Thanks. We report the choice of $p(z^{*})$ above and  we have added acceptance rates for the simulations.}
-
-\item The models studied in both the simulation and real data examples are just simple linear regression which is not realistic.
-Multiple linear regression with at least three independent variables should be studied.
-
-\response{For the real data, we have included two additional covariates related to the number of employees at each agency.
-These were left out originally after EDA revealed their effect sizes were small, but leaving them in makes for a good study as well.
-We have kept the first simulation as we feel it is a good and simple illustration of the ability to fit hierarchical models with our method.
-The real data examples now contain a hierarchical example with more covariates.
-Additionally, we have included a second simulation where the ground truth is a linear regression model with 3 active covariates.
-A model with 30 covariates (27 inactive) is fit.
-There is correlation amongst some of the covariates, making this problem more realistic.}
-
-\item What are the benefits of the proposed method over the classical robust point estimators, like Huber or Tukey estimators compared in the examples, to offset the additional computational cost and tuning efforts?
-From the simulation studies, whether it has improvement or not depends on the prior distribution, which seems to be from comparing Bayesian and Frequentist methods.
-Actually, literatures on the asymptotic properties of $f(\theta|T(yobs))$ shows that, if $T(yobs)$ is asymptotically unbiased, $T (yobs)$ and $E(\theta | T (yobs))$ have the same asymptotic variance.
-Hence if the prior doesn't matter, both methods have similar performance.
-
-\response{As you note, one major advantage is that our method is {\em exactly} a Bayesian method, with $T(y_{obs})$ used in Bayes Theorem to move from prior to posterior.
-In a typical setting, under relatively mild conditions on the prior distribution and estimator, Bayesian and frequentist methods will agree asymptotically.
-This is reflected in the large-sample central limit theorems (Bayesian and frequentist versions) and is not specially connected to our work.
-In this paper, our interest is not in these asymptotic settings where we could simply use a limiting normal distribution as the posterior over the parameters, but rather for the finite sample setting where Bayesian and frequentist methods yield different answers.
-The simulations and data analyses document this differential performance.
-The standard advantages of Bayes apply -- a guarantee of admissibility from a decision-theoretic view; the ability to combine information across a collection of problems (e.g., the hierarchical setting); and the transition from moment-based methods to likelihood-based methods, for example.
-The weaknesses are also there -- a really bad prior distribution produces poor finite-sample performance.
-There is a greater computational cost (standard for Bayes vs frequentist), but, given our MCMC routine, no real effort is needed to tune the computation.}
-
-\response{We have added the following to the introduction of the paper to address this comment:}
-
-\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data.
-One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
-the conditioning statistics than are methods based on the complete likelihood.
-Choosing statistics targeting the main features of interest allows for inference that focuses on these features.
-The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.}
-
-\response{The examples in the paper provide a Bayesian analog of classical robust estimators.
-The main disadvantage of our methods relative to the classical estimators is computational.
-In Section~3 we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.
-The advantages are those of Bayesian methods.
-As is standard for Bayes-classical comparisons, the Bayesian method requires greater computational effort while providing better inference.
-As a referee notes, asymptotically, the Bayesian and classical parameter estimates are often very close and have the same limiting posterior variance / sampling variance.
-In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.'}
-
-\response{We have also included in the discussion:
-
-`We have found the benefits of using our Bayesian technique to outweigh the additional computational burden (relative to a classical estimator) in the situation where substantive prior information that will impact the results is available.'
-}
-
-\item I think $f(\theta|T(yobs))$ might perform better in the following scenario: when $T(yobs)$ is asymptotically biased, $E(\theta|T(yobs))$ can still be asymptotically unbiased as long as the true pa- rameter is identifiable conditioning on the summary statistic, i.e the value of $E(T(yobs))$ is unique on the true parameter.
-One possible example is the robust ridge-regression estimator, but it needs further investigation whether this estimator satisfies C1-C8.
-
-\response{This idea is in perfect alignment with our work.
-You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).
-It is merely a statistic upon which we condition when using Bayes Theorem.
-
-Our computational strategy provides an implementation for a big variety of conditioning statistics that are also estimators.
-The ridge regression estimator does not satisfy property C5 and so, on the surface, would need a new computational development ($\hat\beta = (X'X +\lambda I)^{-1} X'y$:   $(X'X +\lambda I)^{-1} X'(y + Xv) \neq (X'X +\lambda I)^{-1} X'y + v$).
-But the ridge regression estimator for full rank $X'X$ is equivalent to least squares regression for conditioning.
-And the least squares estimator does satisfy C1-C8.
-
-For any hope of consistency, the models would need to distinguish between different values of $\theta$, and so a condition along the lines of uniqueness of $E(T(yobs)|\theta)$ in $\theta$ is important.
-}
-
-\item In page 14, should $C^\perp(X)$ n - p-dimensional instead of n - p - 1-dimensional?
-
-\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional.
-$\mathcal{A}$ is $n-p-1$ dimensional as one degree of freedom is lost for each coefficient estimate and another degree of freedom is lost for the scale estimate.}
-
-\end{enumerate}
-
-\section{Reviewer 2 Comments}
-
-\begin{enumerate}
-\item Is the proposed framework useful for practitioners?
-The proposed framework targets scenario where (i) we know the data is a mixture of good and bad data, and (ii) we only want to 'build models that offer good prediction for the good portion of the data' (from the 1st paragraph of Sec 5).
-Authors should provide real examples in which (i) and (ii) hold.
-In any real examples, (i) often holds, but (ii) doesn't: if we already have had a contaminated training sample, why would we expect the test sample to contain only the good portion?
-In many real applications, learning the heterogeneity of the good and bad samples is precisely the goal of statistical data analysis.
-For the insurance example analyzed in Sec 6, the authors should provide evidence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.
-
-\response{I think we are in agreement that it is common to encounter data sets where a portion of the data is 'good' and a portion of the data is 'bad' (your point (i)).
-The 'bad' data may be bad for many reasons, including a breakdown of the measurement process, misrecorded data, and cases that simply aren't relevant to the problem at hand.
-The ability to perform a decent analysis for such data sets is important.
-And the typical decent analysis focuses on (ii).
-We would have little interest in predicting misrecorded test data in a typical situation or in predicting the recorded values when the measurement process has broken down.
-
-Developing an understanding of sources of variation in the data is important.
-In settings where the mechanism that produces bad data is stable, we might even entertain building a model for the bad data as is one tradition in Bayesian statistics.
-But there are many instances where modelling the bad data is of little interest.
-
-When we are in a situation where (i) and (ii) hold -- we would argue that this is the usual situation and not the exception -- and we have test data available, there would rarely be any reason to believe that the test data would be pure, consisting only of good data.
-This is an important motivator of this work as described in the introduction to our paper.
-
-We have added the following to the introduction in response to your comment and a comment from the other referee.
-
-\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data.
-One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
-the conditioning statistics than are methods based on the complete likelihood.
-Choosing statistics targeting the main features of interest allows for inference that focuses on these features.
-The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.'}
-
-For the real data example:  The goal for the insurance example was derived from personal collaborations with those in the insurance industry.
-Privacy concerns and a turnover of executives in the company from which the data come limit our ability to provide a full description and limit our ability to provide the data themselves.
-However we have expanded slightly on the goal of the analysis.
-\response{It is of concern to the company to predict closures and future performance for agencies that remain open.
-It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies.
-Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.}
-}
-
-\item As a methodological paper, what's the guideline/recommendation given by the authors? After reading this paper, I don't know how to apply the suggested framework
-on a simple regression model. Apparently, the choice of the likelihood function (for the good data) $f(y|\theta)$ and the choice of the statistic T are related.
-To make things more complicated, each has multiple choices.
-For example, f could be normal, student-t or other heavy-tailed distribution; T could be something named Huber or Tukey although the authors are not even bothered to provide any mathematical expression.
-
-Instead of just reporting numerical performance, the authors should provide some guidelines/recommendation on how to apply their framework on linear regression models, e.g., what are the default choices for f and T ?
-Is there any- way to select which f or T to use based on cross-validation or other empirical methods?
-
-\response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.
-We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults in a heavy-handed fashion.
-This would be much like specifying a default likelihood if one wishes to build a regression model.
-Inthe usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.
-As you note, choice of the likelihood is part of the analysis when building a Bayesian model.
-To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.
-Omission of the formal description of the particular M-estimators that we use is an oversight.
-
-We have taken the following steps to address your comment.  We now
-
-\begin{enumerate}
-\item Point out that M-estimators have been our default choice in the very first illustrative example:
- \response{Details of these estimators can be found in many places, including \citep{huber2009}.
-We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers.
-A short review of these estimators is provided in the Supplementary Material.}
- \item Include a short review of M-estimators in the Supplement
- \item Include `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
-\end{enumerate}
-}
-
-\item What's the real benefit of this computationally expensive approximation framework? The proposed framework replies on a good summary statistic T(yobs), which
-has already provided a robust estimate of the target parameter. On the other
-hand, the proposed MCMC algorithm is computationally expensive. In Sec
-4.2, the authors only discussed the computation cost for their proposal distribution, but ignored the computation cost for obtaining T(y) (see Theorem 4.1).
-Those statistics are M-estimators, i.e., they are maximizers of some objective functions involving n observations and p parameters.
-The authors should discuss the computation cost for T(y).
-What's the gain of all the extra computation?
-
-\response{At the end of Section 3 (note renumbering of sections) we have included a paragraph:}
-
-\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
-We have found this burden to be marginal in comparison to computing the needed Jacobian.
-In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.
-This is most evident when substantive prior information is available and information in the data is limited.'}
-
-\response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
-%}
-
-\item The authors compare KL diver-gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y|M,yobs) is not available in closed-form; 2) since f(y|M,yobs) is not available close-form, the KL divergence is approximated and it's not clear to me how accurate the approximation is.
-The authors should compare prediction and estimation accuracy, common met- rics used for regression models.
-
-\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to mean squared error (MSE).
-Evaluation via MSE shows a uniform advantage for our restricted likelihood methods relative to classical robust estimators.
-We have rewritten the summary of the simulation section.
-In doing so, we describe the pattern apparent in the MSE and retain a link to the evaluation via KL-divergence.
-We retain this link because the comparisons under KL-divergence do not show uniform superiority of our methods as do those based on MSE.}
-
-\item The simulation setup is too simple. Suggest to add some linear regression models with large p and/or large n.
-
-\response{We feel that the first hierarchical simulation example shows how to use the method in a hierarchical setting.
-We have added 2 more regression covariates to the real data analysis which also contains a hierarchical example.
-We have also included an additional simulation studying variable selection where only a few variables are active out of many.
-We hope this satisfies your suggestion.}
-
-\end{enumerate}
-
-\textbf{Some minor issues.}
-\begin{enumerate}
-\item  Abstract '...
-handling data sets with outliers and dealing with model mis- specification.
-We outline the drawbacks ...
-and propose a new method as an alternative.' The proposed method cannot handle 'model misspecification', instead it assumes f is the true model (no misspecification) and what's wrong is part of the data.
-
-\response{We stand by the abstract.
-The insurance company example is along the lines of a number of examples in the literature on robust regression.
-Outliers -- best defined as cases which do not reflect the mechanism under study -- often have large residuals.
-This does not mean that outliers are independent of one another.
-They often reflect model misspecification.
-The tradition of robust regression is to provide a model that discounts the outliers (that discounts the deficiencies in the model) and results in a sensible, practical analysis of the data set.
-The robust analysis often points the way to an understanding of why the model fits some cases well and others poorly.
-Our paper is about model misspecification as well as what some feel the word 'outlier' captures.}
-
-\item  Sec 2 and Sec 3 can be shortened or merged.
-
-\response{We have merged the sections.}
-
-\item  Eq(2) in Sec 2.1, the notation f(yi|?,c(yi)) is not introduced yet; what's introduced is f(y|?).
-
-\response{We have included a sentence for this notation after it's first use.}
-
-\item  Sec 4.1, C3 and C4: a maximizer may not be a continuous function of the data and it may not be unique.
-Instead of saying 'Many estimators satisfy the above properties', the authors should list those estimators and explain why those conditions are satisfied.
-
-\response{We have added:
-
-\response{'These M-estimators satisfy C3 and C4 since they are optimizers of continuous and differentiable objective functions.
-Constraints C5-C8 are often satisfied by location and scale estimators but should be checked on a case by case basis.'}
-}
-
-\item  Bottom of p14, 'Sample z?
-from a distribution with known density on S.' Any distribution?
-For example, can it be a point mass or its support has to be equal to S?
-What's the sampling distribution for z?
-used in the simulation studies and real data analysis?
-
-\response{Thanks for noticing this detail.
-It is most natural if it is mutually absolutely continuous with respect to the distribution induced by the model on S.
-For the cases we discuss, this is mutually absolutely continuous with respect to the uniform distribution on S.
-We now mention the importance of the support.
-We have also included a description of what we use for p throughout based on a previous comment.
-This comment is after Theorem 4.6.}
-
-\item  Eq (18): change dy to d$\tilde{y}$?
-
-\response{Thanks for noticing this typo - based on your other comment on KL divergence, this formula was taken out and now is a closed form version. }
-
-\end{enumerate}
-
-\section{AE Comments}
-This paper proposes a Bayesian approach for making inference based on robust statistics of the data instead of the original observations.
-The conditioning robust statistics pass the desirable robustness (to outliers) to the posterior distribution of parameters, thus having the potential to improve inference and prediction.
-This paper addresses an important problem in statistics and contains interesting ideas.
-However, there are some major concerns.
-The paper focuses on outliers.
-Although outliers automatically imply that the model is misspecified, model misspecification is much broader including the misspecification of the density of the good data.
-The paper does not appear to address model misspecification beyond the case when outliers are present.
-Please revise the scope of the paper as appropriate or provide more examples to ensure outliers and model misspecification are parallel contributions rather than one nested in another.
-
-\response{Model misspecification covers broad territory.
-It includes traditional outliers (retaining the independence of observations, but assuming some have greater variance, for example), misspecification of the mean function in a regression setting, missed covariates for regression, missed dependence among cases, misspecified functional form for the `good' data (one reason for the growth of nonparametric Bayesian methods), and much, much more.
-Box' famous aphorism is one direct statement that all models are misspecified.
-
-Our own belief is that it would be impossible to address {\em all} forms of model misspecification, yet discussion of the issue is important.
-Our paper illustrates misspecification in the real data example on the insurance companies.
-The inclusion of closed agencies and agencies with different types of contracts represent model misspecification.
-These `outliers' are not merely the result of a huge chance error, a faulty measurement process, or a failed experimental run.
-They are unusual for a reason and the analysis helps to uncover this reason (we are limited in the commentary that we can attach to the analysis).
-As with many of the examples used to illustrate robust regression techniques, these data are best described as having a misspecified model.}
-
-There are many implementation details that an interested user would like to learn more but feel difficult to find from the current paper.
-This includes but not limited to the selection of proposal, parameter tuning, recommendations when a practitioner is being faced with a real-world problem, and computational complexity of the entire procedure.
-See the two referee reports for more details.
-
-\response{Thank you - we believe we have addressed each of these concerns based on the two reviewer's comments. Detailed responses are given above.}
-
-The authors are also suggested to possibly provide code that is available online with recommended choices as default.
-
-\response{We have included some 'default choices' in the paper and in the Supplement.
-Information for where to obtain code on Github (an R package as well as data and code for the examples) is now provided in the Introduction.
-As noted in our response to Referee 2, we hesitate to push the notion of a default likelihood and default conditioning statistic.
-The paper provides a conceptual framework for data analysis and develops the methodology and computation needed to implement the analysis.
-We do not view the work as developing an algorithm into which one should just feed data.}
-
-It is unclear how the proposed method outperforms existing work, either conceptually or practically.
-
-\response{We believe we have addressed similar concerns from the two reviewers - specifically we have included commentary on the advantages and disadvantages of the new method in several places (e.g., see Introduction) as well as some practical recommendations (e.g.
-See Supplement).}
-
-Referees have provided some competing methods for the authors to consider.
-I'd like to add another existing strategy in addition to the three solutions mentioned in the bottom paragraph of page 2: Bayesian fractional inference, which uses a fractional likelihood function that raises a usual likelihood function to a fractional power.
-What is the advantage of the proposed restrictive likelihood approach over Bayesian fractional inference, even conceptually?
-
-\response{The central advantage of our method compared to the fractional Bayes methods is that our method uses Bayes Theorem!
-It is exactly Bayesian in that the posterior distribution is a rescaled version of prior distribution times likelihood (of a statistic).
-This means that the method inherits a host of properties from Bayesian methods.
-
-In contrast, the fractional Bayesian methods do not actually follow Bayes Theorem (there are exceptions in special cases).
-Fractional Bayes methods use the theorem as an analogy and so miss many of the benefits of Bayes.
-The fractional methods are interesting and they deserve study, but they are not the only solution to Bayesian model misspecification.
-
-In the long run, we suspect that robust and effective Bayesian analyses will make use of ideas from a variety of perspectives that are currently under study.
-The various lines of research need groups of researchers investigating them, need time to develop, and they need visibility for the community to appreciate the different perspectives and to develop an understanding of what each brings to the table.}
-
-Overall, the paper deserves publication after careful and thorough revision. I hope the authors can address all concerns raised in this report and the two well-grounded referee reports.
-
-\response{ Thanks!}
-
-\section{Editor Comments}
-
-The paper has received a mixed reaction from the two referees and the AE.
-I have a similar reaction to the paper but agree with the other readers that the content is such that an opportunity to address the issues raised is appropriate.
-The AE's comments place the paper on the border between Reject with Resubmission and Major Revision.
-I mention this because it isn't clear that a revision will be successful as there are some significant criticisms in the reviews.
-
-My concerns might be a little different than the others and perhaps are less technical in nature.
-It is generally agreed that *all* models are wrong.
-The incorrectness of the model can arise in a number of ways and some observations being outliers is one of these.
-The natural question then is: how are we supposed to deal with that?
-The answer is surely that we don't unless the discrepancy is so substantial that the inferences would be seriously in error if we proceeded using the assumed model.
-This part of a statistical analysis is the model checking aspect and the solution to any issue, whatever it might be, arises there.
-For example, for the problem being considered in this paper, I would want a model checking procedure that indicated that there is a serious problem because, no matter what distribution was used from the model, some observations are outlying and I would want the methodology to identify the observations in question.
-In that case there would several ways to deal with the issue, including modifying the model, but also simply discarding the offending observations as part of "data cleaning".
-It is worth noting though that the answer isn't simple because notable scientific achievements have been obtained by looking carefully at observations that are clearly discrepant.
-
-So there are some concerns that have relevance for me and that I think the paper needs to address.
-What method is used to identify that there is a problem with the model such that the inferences will be strongly affected and does it identify outlying observations?
-
-\response{Our own training in regression is in the style of ``case analysis'' that has been written about so convincingly by Sandy Weisberg, Dennis Cook, and others.
-This training matches your view of strong model diagnostics to identify deficiencies in the model.
-A competing type of regression analysis common at the time was developed by Peter Huber, Peter Rousseeuw, and others.
-These ``robust regression'' methods seek to automatically discount unusual cases.
-Though generally described as a means of handling outliers, many of the popular examples used to illustrate the methods are clearly examples of model misspecification.
-The robust methods provide excellent fits for the good (or non-to-mildly misspecified data) when there is misspecification.
-Much is known and much has been written about the relative merits of the two styles of regression in various settings.
-
-In the early 1980s, case analysis became the dominant paradigm (though robust regression retained many adherents).
-Our natural inclinations match yours for the reasons you give--we would always prefer to build the perfect model.
-However, there are a number of reasons why we cannot do so.
-These range from the perils of overmodelling (particularly dangerous for Bayesians) to limitations on our ability to identify outliers (from Huber's book, imagine sliding the "y" value for a case from a ridiculous value--surely and outlier--to its case-deleted mean--a zero residual and not identified as an outlier; somewhere along the way, the subjective probability of the case being an outlier must be 0.5 and we would be unable to decide whether the case is an outlier), to our inability to detect modest model misspecification.
-Accepting that there are limitations on case analysis and our ability to build the perfect model suggests that we need to develop alternative strategies.
-These alternative strategies can even become part of our diagnostic framework:  a discrepancy between the restricted likelihood fit and the traditional Bayesian fit (or predictions) indicates a need for the case-analysis analyst to do more work.
-
-The modern world revolves around large data sets, often with a hierarchical structure.
-While case analysis works with data sets of moderate size, it breaks down when one has thousands to millions of cases.
-It also breaks down when one is interested in model selection (among a class of models that are, of course, misspecified to some extent) or model averaging.
-Robust methods scale much better than case analysis methods do.
-
-The tension between case analysis methods and robust methods is not limited to the regression setting, nor is it limited to merely looking at the fits from the model.
-In this work, we lay out the restricted likelihood perspective, develop a computational implementation (as referees and AE note, this development is not trivial), implement the method with code that is available on GitHub, and illustrate some of the benefits of this method relative to standard Bayesian and classical methods.
-We view this as an early effort and look to tackle further problems in subsequent papers--in fact, we have given talks about issues such as Bayesian hypothesis testing and model averaging in this framework--and we see a clear path forward for a variety of problems.}
-
-A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to choose T: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isn't clear how to do this.
-I understand that there are
-problems where reducing the data to some T(y) is necessary, perhaps because of computational problems associated with evaluating a likelihood, but this is clearly a compromised analysis and not one we would recommend unless forced to do so.
-So I don't agree with the statement made in the paper "that deliberate choice of an insufficient statistic T(y) guided by targeted inference is sound practice".
-There needs to be a much stronger argument for this at least for me.
-
-\response{We understand your point of view.
-It focuses on dangerous territory for classical statisticans and Bayesians alike.
-In keeping with your statement above that *all* models are misspecified (we agree except for a few very simple exceptions--say a single Bernoulli trial), we believe that *all* analyses are compromised.
-It is also true that, as soon as one uses diagnostics that have the potential to change the model or the data (removing outliers, for example), the analysis is compromised.
-The appropriate likelihood would need to account for all decisions that one might make.
-These are two of the arguments made for the use of robust methods (i) that robust estimators reduce the impact of model misspecification, and (ii) that data cleaning and data-based model adjustment destroys the properties of classical tests and Bayesian methods.
-It is difficult to quantify these effects, but we have seen them in the practice of data analysis.}
-
-The paper is well-written and thought-provoking so my hope is that a revision will be able to address the points raised.
-
-\bibliographystyle{plain}
-\bibliography{../bib/refPaper1}
+\end{itemize}
 

### 2021-02-01 revision_2/Bayesian Restricted Likelihood Dec 30 2020.tex
git cleanup

--- 2020-11-02 revision_2/revision_Jun2020.tex
@@
 \runtitle{Bayesian Restricted Likelihood Methods}
-\thankstext{T1}{This research has been supported by Nationwide Insurance Company and by the NSF under grant numbers DMS-1007682, DMS-1209194, DMS-15-13566, and DMS-16-13110.
+\thankstext{T1}{This research has been supported by Nationwide Insurance Company and by the NSF under grant numbers DMS-10-07682, DMS-12-09194, DMS-15-13566, DMS-16-13110, SBE 19-21523, DMS-20-15490, and DMS-20-15552.
 The views in this paper are not necessarily those of Nationwide Insurance or the NSF.}
@@
 Concern for imperfections in the likelihood are reflected in work considering minimally informative likelihoods \citep{yuan1999minimally}, sensitivities of inferences to perturbations in the model \citep{zhu2011}, the specification of a class of models and the use of Bayesian model averaging over the class \citep{clyde2004}, and considerations of such averaging when the specified class may not contain the so-called true data generating model \citep{bernardo2000, clyde2013, clarke2013Complete}.
-In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study.
+
+Imperfection in the likelihood has also been widely discussed in the classical robustness literature.
+\cite{hampel1971}, writing on the motivation for studies of robustness, provides a concise description of three mismatches between data and the model that purportedly gives rise to the data:  ``(i) rounding of the observations; (ii) the occurrence of gross errors; (iii) the model itself may only be an approximation to the underlying chance mechanism''.
+In a Bayesian setting, the first is easily handled with MCMC methods through the introduction of a latent, unrounded variable into the model.
+We do not consider it here.
+The second and third are duals.
+Misspecification of the model (iii) will often make observations appear to be outliers (ii).
+The literature on robust methods is replete with examples described in terms of ``outliers'' where the central problem is model misspecification.
+In the sequel, we follow the tradition of referring to cases that are discordant with the stated model as ``outliers'', whether this discordance is due to gross error or a consequence of model misspecification.
+
+In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- whether due to local misspecification of the model or due to gross error.
 There are three main solutions to Bayesian outlier-handling.
@@
 Since it is typically that the restricted likelihood posterior converges to the same expected value as the conditioning statistics as the sample size grows, it may not be practical to implement our method in all situations.}
-\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data.
+The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data.
 One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
@@
 Choosing statistics targeting the main features of interest allows for inference that focuses on these features.
-The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.}
-
-\response{The examples in the paper provide a Bayesian analog of classical robust estimators.
+The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.
+
+The examples in the paper provide a Bayesian analog of classical robust estimators.
 The main disadvantage of our methods relative to the classical estimators is computational.
@@
 As a referee notes, asymptotically, the Bayesian and classical parameter estimates are often very close and have the same limiting posterior variance / sampling variance.
-In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.}
+In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.
 
@@
 A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method.
-\response{ An R package \texttt{brlm} to implement our methods is available at \texttt{github.com/jrlewi/brlm}.
-Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/}.}
+An R package \texttt{brlm} to implement our methods is available at \texttt{github.com/jrlewi/brlm}.
+Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/}.
 
@@
 Approximate sufficiency is also appealed to in the use of Approximate Bayesian Computation (ABC), which is related to our method.
-ABC is a collection of posterior approximation methods which has recently experienced success in applications to epidemiology, genetics, and quality control \citep[see, for example,][]{tavare1997, pritchard1999,  marjoram2003, fearnhead2012}.
+ABC is a collection of posterior approximation methods which has recently experienced success in applications to epidemiology, genetics, and quality control \citep[see, for example,][]{tavare1997, pritchard1999, beaumont2002, marjoram2003, fearnhead2012, drovandi2015}.
 Interest typically lies in the full data posterior and ABC is used for computational convenience as an approximation.
@@
 Consequently, the ABC posterior approximates the full data posterior and efforts have been made to formalize what is meant by approximate sufficiency \citep[e.g.,][]{joyce2008}.
-ABC is related to our method in that the conditioning is on something other than the data $\by$.
-However, we specifically seek to condition on an insufficient statistic to guard against misspecification in parts of the likelihood.
-Additionally, we develop methods where the conditioning is exact (i.e.
-$\epsilon = 0$).
+
+Our method can be viewed as ABC with $\epsilon = 0$ and it is natural to compare it to ABC.
+This paper develops sampling methods for fitting Bayesian linear models conditioning exactly on a set of summary statistics ($\epsilon = 0$), even when the statistics follow a continuous distribution.
+Traditional ABC sampling methods are flexible and will, in general, apply to a broader class of models.
+The basic sampling method for ABC is the rejection sampling algorithm \citep{pritchard1999} which proposes a sample $\bth^{*}$ from the prior, then new data $\by^{*}$ from the data-model given $\bth^{*}$.
+The value $\bth^{*}$ is accepted as a draw from the ABC posterior if $\rho(T(\by),T(\by^{*})) \leq \epsilon$.
+Acceptance rates of this algorithm can be intolerably low and several extensions have been proposed to improve efficiency \citep[see, for example,][]{beaumont2009, turner2012}.
+The inefficiency of ABC algorithms is especially problematic in high-dimensional settings since generating high-dimensional statistics that are close to the observed values is difficult.
+Recently, \cite{turner2014} developed the Gibbs ABC method which improves efficiency in the hierarchical setting by making use of conditional independence of the model to make accept/reject decisions at the individual group-level, effectively reducing the dimension of the problem to the number of parameters within each group.
+We revisit this approach in our comparisons to ABC in Section \ref{hierRegNW}, finding that, for a modest increase in comptational cost, we obtain an algorithm with better convergence and mixing properties.
+We also retain the desired posterior distribution -- the posterior, having conditioned exactly on the summary statistics.
 
@@
 The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}.
+The first is an example (so far as we know) of gross error; the second is an example of model misspecification for a subset of the observations.
 The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
 The full model is a standard location-scale Bayesian model also used in \cite{lee2014}:
-\begin{equation}
+The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}.
+The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
+The full model is a standard location-scale Bayesian model also used in \cite{lee2014}:\begin{equation}
 \beta\sim N(23.6, 2.04^{2}),\  \sigma^{2}\sim IG(5, 10), \ y_{i}\iid N (\beta, \sigma^{2}), i=1,2,\dots, n=66,
@@
 Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)  Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale.
-\response{Details of these estimators can be found in many places, including \citep{huber2009}.
+Details of these estimators can be found in many places, including \citep{huber2009}.
 We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers.
-A short review of these estimators is provided in the Supplementary Material.}  The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
+A short review of these estimators is provided in the Supplementary Material.
+The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.
 Two additional approaches to outlier handling are considered: 1) the normal distribution is replaced with a t-distribution and, 2) the normal distribution is replaced with a mixture of two normals.
@@
 where $\bbeta = (\beta_{0}, \beta_{1})^{\top}$, $\by$ is the vector of the logarithm of the number of calls, and $X$ is the $n\times 2$ design matrix with a vector of 1's in the first column and the year covariate in the second.
-\response{In reality, the model should include a different piece for the part of the data with different units.
-The outliers are really just a manifestation of model misspecification.} Prior parameters are fixed via a maximum likelihood fit to the first 3 data points.
+In reality, the model should include a different piece for the part of the data with different units.
+The outliers are really just a manifestation of model misspecification.
+Prior parameters are fixed via a maximum likelihood fit to the first 3 data points.
 In particular, the prior covariance for $\bbeta$ is set to $\Sigma_{0} = g\sigma_{0}^2 (X_{p}^{\top}X_{p})^{-1}$, with $X_{p}$ the $3\times 2$ design matrix for the first $3$ data points, $g=n=21$, $\sigma_{0} = 0.03$ and $\boldsymbol{\mu}_{0} = (1.87,  0.03)^{\top}$.
@@
 Constraints  \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}
-\response{These M-estimators satisfy \ref{asb} and \ref{as} since they are optimizers of continuous and differentiable objective functions.
-Constraints \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.}
+These M-estimators satisfy \ref{asb} and \ref{as} since they are optimizers of continuous and differentiable objective functions.
+Constraints \ref{regEq}-\ref{scaleEq2Reg} are often satisfied by location and scale estimators but should be checked on a case by case basis.
 More software development is required to extend the MCMC implementation beyond the M-estimators discussed here.
@@
 \begin{enumerate}
-\item Sample $\bz^*$ from a distribution with known density \response{whose support is the entirety of} $\mathbb{S}$.
+\item Sample $\bz^*$ from a distribution with known density whose support is the entirety of $\mathbb{S}$.
 \item Set $\by = h(\bz^*)$ and calculate the Jacobian of this transformation in two steps.
@@
 This could provide some advantages in some situations, though we have yet to run into any serious issues with convergence using the independent proposal we utilize here.}
-\response{The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm.
+The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm.
 For all examples in this paper we defined $p(z^{*})$ to be the uniform distribution on $\mathbb{S}$.
@@
 As we are proposing values on a complicated manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$.
-This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.}
+This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.
 
@@
 In the simulations and real data analyses presented below, we will see that the additional burden is often of added value over traditional robust regression when substantial prior information is available that is not swamped by current data.}
-\response{Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
+Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain.
 We have found this burden to be marginal relative to computation of the needed Jacobian.
 In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.
-This is most evident when substantive prior information is available and information in the data is limited.}
+This is most evident when substantive prior information is available and information in the data is limited.
 
@@
 That is, there is a separate Gibbs step for each group to generate the group level data matching the statistics for that group.
-\response{The acceptance rates for newly generated data across all groups and simulations ranged from $0.57$ to $0.68$}
-
-\response{The performance of the methods can be evaluated in many ways.
+The acceptance rates for newly generated data across all groups and simulations ranged from $0.57$ to $0.68$.
+
+The performance of the methods can be evaluated in many ways.
 For these simulations, we know the true data generating mechanism, and this allows us to make direct comparisons between the fitted model and the truth.
@@
 For both classical and restricted likelihood methods, Tukey's $\psi$ function leads to better performance than does Huber's $\psi$ function.
-}
 %For $c = 0.5$ and $c = 1$ the results favor the restricted likelihood methods as seen by the lower values of loss.
@@
 
-\response{It is also interesting to consider the effects of factors $n$, $p$, and $m$.
+It is also interesting to consider the effects of factors $n$, $p$, and $m$.
 We present the results for a single prior ($a_s = 5$ and $c = 1$).
@@
 As expected, the average MSE gets larger as the contamination gets more severe (larger $m$ or larger $p$) and tends to get smaller as the sample size $n$ grows.
-The advantage of the Bayesian methods is greater for smaller sample sizes and for more severe contamination.}
+The advantage of the Bayesian methods is greater for smaller sample sizes and for more severe contamination.
 
@@
 
-\response{This simulation shows the potential of the restricted likelihood methods to dramatically improve estimation.
+This simulation shows the potential of the restricted likelihood methods to dramatically improve estimation.
 The simulation also conveys some cautions that are apparent from consideration of KL divergence but not MSE.
@@
 If poorly handled, they can, of course, harm performance.
-}
-
-\subsection{\response{Simulation 2}}
+
+\subsection{Simulation 2}
 
@@
 Our expectation is that the restricted likelihood will facilitate prediction for the `good' part of the data (i.e., open, `Type 1' agencies).
-\response{It is of concern to the company to predict closures and future performance for agencies that remain open.
+It is of concern to the company to predict closures and future performance for agencies that remain open.
 It is important for planning purposes that the predictions are not overly influenced by a handful of over/underperforming agencies.
-Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.}
+Our analysis focuses on one aspect of the business problem - the prediction of future performance for agencies, given they remain open.
 
@@
 Holdout evaluation is done on the remaining (`Type 1') samples.
-The acceptance rates for  the data augmentation step, \response{for all but one training set}, range from  \response{$0.10$ to $0.8$} across the states, repetitions, and two versions of the model.
-\response{The exception was a single training set from State 15 resulting in an usually small acceptance rate under Tukey's version.
-This case didn't effect the overall results of the simulations but emphasizes the need to check convergence on a case by case basis.} The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
+The acceptance rates for  the data augmentation step, for all but one training set, range from $0.10$ to $0.8$ across the states, repetitions, and two versions of the model.
+The exception was a single training set from State 15 resulting in an usually small acceptance rate under Tukey's version.
+This case didn't effect the overall results of the simulations but emphasizes the need to check convergence on a case by case basis.
+The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$.
 Similar results are observed for other base models.
@@
 We also fit classical robust regression counterparts and a least squares regression separately within each state.
-Hierarchical models naturally require more
-data and so we include states having at least 25 agencies with sufficient variation within each covariate, resulting in 20 states in total and $n = \sum_{j} n_{j} =  3094$ total agencies.
+Additionally, we compare our method to an ABC fit.
+The ABC version conditions on the Tukey statistics used in our restricted likelihood version.
+We choose the Tukey version for comparison to ABC since it naturally trims outliers and we expect it to perform the best in this situation.
+Recall, ABC will approximate the restricted posterior using $\pi(\bth | \rho(T(\by_{obs}), T(\by^{*})) < \epsilon)$.
+Due to the high-dimension of the parameters and statistics we use the MCMC method called Gibbs ABC developed by \cite{turner2014} to obtain samples from the ABC posterior.
+A brief description of this algorithm is as follows with theoretical details provided by  \cite{turner2014}.
+Let $\by_{j, obs}$ denote the observed data for state $j = 1,\dots, J$.
+The shared higher-level parameters are sampled as before since they are, {\em a posteriori} conditionally independent of the data.
+The state-level parameters $\bth_{j} = (\bbeta_{j}, \sigma_{j}), j = 1, 2, ..., J$ are sampled using Gibbs ABC.
+For each iterate of the chain, denote the current state-level parameters and data for state $j$ by $\bth_{j, curr}$ and $\by_{j, curr}$.
+A single update for the state-level parameters loops over $j$ as follows.
+Propose $\bth_{j, prop}$ from the prior and then propose new data $\by_{j, prop}$ from the normal model conditional on $\bth_{j, prop}$.
+The proposed parameters are accepted with Metropolis-Hastings acceptance probability
+\begin{align}
+\label{eq:mhabc}
+\alpha_{mh} = \min\{1, \frac{\phi(\rho(T(\by_{j, prop}), T(\by_{j, obs}))/\delta_{abc})}{\phi(\rho(T(\by_{j, curr}), T(\by_{j, obs}))/\delta_{abc})}\}
+\end{align}
+with $\phi(\cdot)$ the standard normal pdf and $\delta_{abc}$ a tolerance parameter.
+Here, we use $\rho(\cdot)$ for the standard Euclidean distance metric to conform to common ABC notation (this is not the $\rho$ of M-estimation).
+This method makes use of kernel-based ABC \citep{wilkinson2013}.
+Instead of checking whether the distance between the sampled and observed statistics is strictly below some threshold, this method computes the kernel value of the distance which offers a smoother transition between acceptance and rejection.
+We use a standard Gaussian kernel for this application.
+The smaller $\delta_{abc}$, the closer the statistics must be for acceptance.
+
+A few notes on our implementation are warranted.
+First, we are not restricted to sampling the parameters from their prior.
+A more general proposal distribution can be applied with standard adjustments to $\alpha_{mh}$ to adjust for the proposal \citep{turner2014}.
+We tried a few different options, including sampling from the full-conditional distributions, but found proposing from the priors was both the easiest to implement and provided the most satisfactory conversion results for this problem.
+Additionally, the choice of $\delta_{abc}$ is important and can be different for each state.
+For this we started with a small value for each state ($\delta_{abc} = 0.01$) and iteratively checked the within-state acceptance rate.
+After each check, if the rate was below $0.1$ we increased the $\delta_{abc}$ for that state by a factor of $1.2$.
+These choices were based on some experimentation in order to reach satisfactory convergence in a reasonable number of iterations.
+To reach satisfactory convergence we had to run the chains for a total of $40,000$ iterations which was $10$-fold more than were needed for the restricted likelihood algorithm.
+In our experimentation, our method takes only about $1.6$ times as long as ABC per iteration.
+We believe that this modest increase in per-iteration computational time is outweighed by apparently better convergence and mixing of the Markov chain.
+It is quite possible that better choices for the ABC algorithm could help improve its convergence, but we leave this for further research as computational efficiency is not the main focus of this paper.
+
+Hierarchical models naturally require more data and so we include states having at least 25 agencies with sufficient variation within each covariate, resulting in 20 states in total and $n = \sum_{j} n_{j} =  3094$ total agencies.
 For training data we take a stratified (by state) sample of size $3094/2 = 1547$ where the strata sizes are $n_{j}/2$ (rounded to the nearest integer).
@@
 The Bayesian models are fit using MCMC, with the restricted versions applying the algorithm laid out in Section \ref{BayesLinMod} and adapted to the hierarchical setting as described in Section \ref{simData}.
-For the MH-step proposing augmented data,  \response{the acceptance rates for the two restricted likelihood models across all states and repetitions ranged from $0.01$ to  $0.75$, with only $7$ cases (out of 50*20*2 = 2000 chains) with rates below $0.1$.}
+For the MH-step proposing augmented data, the acceptance rates for the two restricted likelihood models across all states and repetitions ranged from $0.01$ to  $0.75$, with only $7$ cases (out of 50*20*2 = 2000 chains) with rates below $0.1$.
 
@@
 The hierarchical model also reduces variance in predictions resulting in smaller error bars.
+On the surface, ABC performs quite well in comparison to the restricted likelihood.
+A table of the mean and standard deviation values for trimming fraction $0.3$ is provided in Table \ref{tab:tlmcompare} where we see that the average TLM for ABC is larger than that for restricted likelihood by $0.03$.
+Additionally, the standard deviation of TLM for ABC is half the size of that for restricted likelihood.
+A closer look at the results shows that the difference in average TLM can be attributed entirely to a single state with a relatively small sample size (see next paragraph).
+\begin{table}[H]
+
+\caption{\label{tab:tlmcompare}{Comparison of the average TLM over all states for Restricted and ABC methods with trimming fraction 0.3.}}
+\centering
+{
+\begin{tabular}[t]{c|c|c|c}
+\hline
+Model & Trimming Fraction & mean & std. deviation\\
+\hline
+Restricted - Tukey & 0.3 & 1.87 & 0.06\\
+\hline
+ABC - Tukey & 0.3 & 1.90 & 0.03\\
+\hline
+\end{tabular}
+}
+\end{table}
 
@@
 It is also interesting to examine the results within each state.
-Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ with $\alpha = 0.3$ for each state where the points and error bars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions.
+Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ with $\alpha = 0.3$ for each state where the points and error bars are the averages plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions.
 The results are only given for the models using Tukey's M-estimators (Huber's version is qualitatively similar).
@@
 State 28 is removed from the figure as the error bars for the classical robust regression are excessively large and distort the comparison.
-In several of the smaller states, the restricted hierarchical model performs better with similar performance between the models in most of the larger states, a reflection of the decreased influence of the prior.
+In several of the smaller states, the restricted hierarchical model performs better than the classical method, with similar performance between the models in most of the larger states, a reflection of the decreased influence of the prior.
 The hierarchical structure pools information across states, improving performance in the smaller states.
@@
 Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.
+Restricted likelihood performs better when considering the metric at the individual state-level.
+While there are a few small states that perform much better under ABC (especially state 31), the restricted likelihood average TLM is larger in 14 of the 20 states with a median difference (restricted minus ABC) of $0.04$.
 
@@
 %\response{We have found the additional computational burden to be beneficial in situation where  substantial prior information that will impact the results is available.}
-\response{We have found the benefits of using our Bayesian technique to outweigh the additional computational burden (relative to a classical estimator) in the situation where substantive prior information that will impact the results is available.}
+We have found the benefits of using our Bayesian technique to outweigh the additional computational burden (relative to a classical estimator) in the situation where substantive prior information that will impact the results is available.
 

### 2021-02-01 revision_2/revision_Dec2020 Dec 30.tex
git cleanup

--- 2021-02-01 revision_2/Bayesian Restricted Likelihood Dec 30 2020.tex
@@
 \DeclareMathOperator*{\argmin}{\arg\!\min}
-\graphicspath{{figures/}{figs/}}
+\graphicspath{{figures/}}
 
@@
 
-Imperfection in the likelihood has also been widely discussed in the classical robustness literature.
+\response{Imperfection in the likelihood has also been widely discussed in the classical robustness literature.
 \cite{hampel1971}, writing on the motivation for studies of robustness, provides a concise description of three mismatches between data and the model that purportedly gives rise to the data:  ``(i) rounding of the observations; (ii) the occurrence of gross errors; (iii) the model itself may only be an approximation to the underlying chance mechanism''.
@@
 The literature on robust methods is replete with examples described in terms of ``outliers'' where the central problem is model misspecification.
-In the sequel, we follow the tradition of referring to cases that are discordant with the stated model as ``outliers'', whether this discordance is due to gross error or a consequence of model misspecification.
-
-In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- whether due to local misspecification of the model or due to gross error.
+In the sequel, we follow the tradition of referring to cases that are discordant with the stated model as ``outliers'', whether this discordance is due to gross error or a consequence of model misspecification.}
+
+In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- \response{\sout{cases not reflecting the phenomenon under study,}} {\response {whether due to local misspecification of the model or due to gross error}}.
 There are three main solutions to Bayesian outlier-handling.
@@
 Consequently, the ABC posterior approximates the full data posterior and efforts have been made to formalize what is meant by approximate sufficiency \citep[e.g.,][]{joyce2008}.
+\response{
+\sout{ABC is related to our method in that the conditioning is on something other than the data $\by$.
+However, we specifically seek to condition on an insufficient statistic to guard against misspecification in parts of the likelihood.
+Additionally, we develop methods where the conditioning is exact (i.e.
+$\epsilon = 0$).}
 
@@
 We also retain the desired posterior distribution -- the posterior, having conditioned exactly on the summary statistics.
+}
 
@@
 The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}.
-The first is an example (so far as we know) of gross error; the second is an example of model misspecification for a subset of the observations.
-The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
+\response{The first is an example (so far as we know) of gross error; the second is an example of model misspecification for a subset of the observations.}  The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail.
 The full model is a standard location-scale Bayesian model also used in \cite{lee2014}:
@@
 \centering
-{\includegraphics[width = 4in]{figs/speed_of_light_beta.png}}
-{\includegraphics[width = 4in]{figs/speed_of_light_predictive.png}}
+{\includegraphics[width = 4in]{speed_of_light_beta.png}}
+{\includegraphics[width = 4in]{speed_of_light_predictive.png}}
 \caption{Results from the analysis of the speed of light data.
@@
 \centering
-{\includegraphics[width = 4in]{figs/calls_predictive.png}}
+{\includegraphics[width = 4in]{calls_predictive.png}}
 \caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model.
@@
 \begin{enumerate}
-\item Sample $\bz^*$ from a distribution with known density whose support is the entirety of $\mathbb{S}$.
+\item Sample $\bz^*$ from a distribution with known density \response{whose support is the entirety of} $\mathbb{S}$.
 \item Set $\by = h(\bz^*)$ and calculate the Jacobian of this transformation in two steps.
@@
 We also fit classical robust regression counterparts and a least squares regression separately within each state.
+\response{
 Additionally, we compare our method to an ABC fit.
@@
 Propose $\bth_{j, prop}$ from the prior and then propose new data $\by_{j, prop}$ from the normal model conditional on $\bth_{j, prop}$.
-The proposed parameters are accepted with Metropolis-Hastings acceptance probability
+The proposed parameters are accepted with Metroplis-Hastings acceptance probability
 \begin{align}
@@
 We believe that this modest increase in per-iteration computational time is outweighed by apparently better convergence and mixing of the Markov chain.
-It is quite possible that better choices for the ABC algorithm could help improve its convergence, but we leave this for further research as computational efficiency is not the main focus of this paper.
+It is quite possible that better choices for the ABC algorithm could help improve its convergence, but we leave this for further research as computational efficiency is not the main focus of this paper.}
 
@@
 The hierarchical model also reduces variance in predictions resulting in smaller error bars.
+\response{
 On the surface, ABC performs quite well in comparison to the restricted likelihood.
@@
 A closer look at the results shows that the difference in average TLM can be attributed entirely to a single state with a relatively small sample size (see next paragraph).
+}
 \begin{table}[H]
 
-\caption{\label{tab:tlmcompare}{Comparison of the average TLM over all states for Restricted and ABC methods with trimming fraction 0.3.}}
+\caption{\label{tab:tlmcompare}{\response{Comparison of the average TLM over all states for Restricted and ABC methods with 
+                                            trimming fraction 0.3.}}}
 \centering
-{
+{\response{
 \begin{tabular}[t]{c|c|c|c}
@@
 \end{tabular}
-}
+}}
 \end{table}
@@
 State 28 is removed from the figure as the error bars for the classical robust regression are excessively large and distort the comparison.
-In several of the smaller states, the restricted hierarchical model performs better than the classical method, with similar performance between the models in most of the larger states, a reflection of the decreased influence of the prior.
+In several of the smaller states, the restricted hierarchical model performs better \response{than the classical method}, with similar performance between the models in most of the larger states, a reflection of the decreased influence of the prior.
 The hierarchical structure pools information across states, improving performance in the smaller states.
@@
 Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.
+\response{
 Restricted likelihood performs better when considering the metric at the individual state-level.
 While there are a few small states that perform much better under ABC (especially state 31), the restricted likelihood average TLM is larger in 14 of the 20 states with a median difference (restricted minus ABC) of $0.04$.
+}
 

### 2021-02-01 revision_2/Bayesian Restricted Likelihood Dec 30 2020.tex
figure cleanup

@@
 \DeclareMathOperator*{\argmin}{\arg\!\min}
-\graphicspath{{figures/}{figs/}}
+\graphicspath{{figures_final/}}
 
